### 2016-01-18 paper/ms.tex
Added a skeleton for the paper and a couple tables.

%\documentclass[12pt,preprint]{aastex}
\documentclass{emulateapj}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{subfigure}
\usepackage{url}
\bibliographystyle{astroads}
\providecommand{\e}[1]{\ensuremath{\times 10^{#1}}}
\begin{document}

\title{The Inner Mass-Ratio Distribution of Intermediate-Mass Stars}

\author{Kevin Gullikson \altaffilmark{1}}
\author{Adam Kraus \altaffilmark{1}}
\author{Sarah Dodson-Robinson \altaffilmark{2}}

\altaffiltext{1}{University of Texas, Astronomy Department. 2515 Speedway, Stop C1400. Austin, TX 78712}
\altaffiltext{2}{University of Delaware, Department of Physics and Astronomy, 217 Sharp Lab, Newark, DE 19716}

\begin{abstract}
Young, intermediate-mass stars are experiencing renewed interest as targets for direct-imaging planet searches. However, these types of stars are part of multiple systems more often than not. Close stellar companions affect the formation and orbital evolution of any planets, and the properties of the companions can help constrain the binary formation mechanism. Unfortunately, close companions are difficult and expensive to detect with imaging techniques. In this paper, we describe the direct spectral detection method wherein a high-resolution spectrum of the primary is cross-correlated against a template for a companion star. Variants of this method have previously been used to search for stellar, brown dwarf, and even planetary companions. We show that the direct spectral detection method can detect companions as late as M-type orbiting A0 or earlier primary stars in a single epoch on small-aperture telescopes. In addition to estimating the detection limits, we determine the sources of uncertainty in characterizing the companion temperature, and find that large systematic biases can exist. After calibrating the systematic biases with synthetic binary star observations, we apply the method to a sample of 34 known binary systems with an A- or B-type primary star. We detect nine total companions, including four of the five known companions with literature temperatures between $4000$ K $ < T < 6000$ K, the temperature range for which our method is optimized. We additionally characterize the companion for the first time in two previously single-lined binary systems and one binary identified with speckle interferometry. This method provides an inexpensive way to use small-aperture telescopes to detect binary companions with moderate mass-ratios, and is competitive with high-resolution imaging techniques inside $\sim 100-200$ mas.
\end{abstract}

\maketitle

\section{Introduction}

\label{sec:intro}
There has recently been a revival of interest in the multiplicity properties of intermediate-mass stars,  spurred largely by the detection of planets orbiting nearby \mbox{$\sim2 M_{\odot}$} stars on both wide \citep[e.g.][]{Lagrange2010, Marois2008} and close \citep{Johnson2011} orbits. In this context, binary companions are contaminants; companions complicate radial velocity planet searches because they necessitate simultaneous modeling of both stellar motions \citep[e.g.][]{Bergmann2015}. Likewise, companions complicate direct imaging planet searches by requiring either extremely high-contrast instrumentation \citep{Thalmann2014} or specialized coronagraphs \citep{Crepp2010}.

However, known binary stars are typically avoided in planet search programs for a more fundamental reason: the binary companion depletes or destroys the planet-forming disk. By combining a binary census of the $\sim 2$ Myr Taurus-Auriga star-forming region with a disk census of the same, \cite{Kraus2012} showed that close ($\lesssim 40$ AU) binaries are about 2-3 times less likely to host a protoplanetary disk, and so hasten disk dispersal. Even if a disk survives, it tends to be depleted in mass by a factor of $\sim 25$ for binary separations $\lesssim 30$ AU \citep{Harris2012}.
%[CITE KRAUS PAPER] performed a search for binary companions among Kepler planet host stars, and found that the presence of a companion within 5-50AU suppresses planet formation by a factor of $\sim 4$.

Multiplicity is an inevitable outcome of star formation, especially for more massive stars where multiplicity is more common \citep{Zinnecker2007}, and so is important to study in its own right. Beyond the overall multiplicity rate, the mass ratio, period, and eccentricity distributions of a binary star population can place important constraints on the mode of binary star formation. Specifically, a mass-ratio distribution that changes with physical separation could indicate that secondary stars are either forming through disk fragmentation \citep[e.g.][]{Kratter2006, Stamatellos2011}  or are accreting a significant amount of their mass from the primary star disk. \cite{DeRosa2014} recently completed an imaging survey of nearby A-type stars, and found preliminary evidence that the mass-ratio distribution does in fact become flatter for closer companions. There is no evidence of such a change for solar-type or later stars \citep{Meyer2013}.

It is difficult to detect low-mass companions very near an intrinsically bright primary star and even more difficult to characterize the companion. There are three commonly used techniques for binary star searches: direct imaging with adaptive optics systems,  interferometry, and radial velocity monitoring. Imaging can easily detect low-mass companions at wide apparent separations, but loses sensitivity as the on-sky distance from the primary star decreases \citep[see][for typical sensitivity curves]{DeRosa2014}. Interferometry can usually achieve smaller working angles than imaging, but cannot achieve as high contrast \citep[see e.g.][]{Aldoretta2015}.

 Radial velocity monitoring can easily find companions on very short-period orbits, but its sensitivity to low-mass companions drops as the physical separation increases. This is especially true for A- and B-type stars, where radial velocity precision is typically limited to $\sim 1 \rm km \  s^{-1}$ by their rotationally broadened lines. Worse, radial velocity monitoring techniques cannot characterize the companion unless the inclination is known or if the companion spectral lines are also visible. All three techniques have separation-dependent sensitivity, which introduces observational bias in any search for a parameter that changes with physical separation.

 One technique that is separation independent is to search directly for the composite spectrum of two stars. \citet{Burgasser2007} used single-epoch low-resolution spectroscopy to identify and characterize a brown dwarf binary system by fitting both spectra simultaneously. This method only works if the stars have a similar brightness but very different spectra, such that the spectral features from both components are visible and distinguishable. If, as in the case of binary systems with very large flux ratios, the companion spectrum is buried within the noise of the primary star, a different method is needed.

The direct spectral detection method (hereafter referred to as the DSD method), and variations thereof, has been used to search for binary companions to early B-stars \citep{Gullikson2013}, main sequence FGK-stars \citep{Kolbl2015}, young K-M stars \citep{Prato2002}, and even `Hot Jupiter' type planets \citep{Snellen2010, Brogi2012, deKok2013} orbiting FGK-stars. The method relies on the cross-correlation function (CCF) of a high-spectral-resolution spectrum of the primary star with a model spectrum for the expected companion. The CCF uses every pixel in the spectrum, and more importantly every spectral line in the secondary spectrum. A simple experiment with synthetic spectra containing increasing numbers of spectral lines (N) in noisy data shows that the CCF peak significance increases as $\sim\sqrt{N}$. For high-resolution cross-dispersed \'echelle spectra, this amplification can reach several factors of 10, allowing the detection \emph{and characterization} of a secondary spectrum where the individual lines are completely buried in noise. Since the DSD method uses a seeing-limited spectrum of the primary star, its sensitivity is independent of separation inside $\sim 1 ''$ and can make use of small telescopes to detect high-contrast companions.

In this paper, we describe the DSD method in detail, and use it to detect the secondary star in nine known binary systems. We describe the method in Section \ref{sec:method}. We describe the observations and data reduction in Section \ref{sec:obs}, then use the observations to estimate the accuracy with which we can measure the companion temperature in Section \ref{subsec:systematics} and the sensitivity of the method in Section \ref{subsec:sensitivity}. In Section \ref{sec:results} we use the DSD method to search for known companions, and discuss the results in Section \ref{sec:conclusions}.

\section{Observations and Data Reduction}
\label{sec:obs}

\section{Stellar Parameters}
\label{sec:sp}

\section{Companion Search}
\label{sec:companions}

\section{Survey Completeness}
\label{sec:completeness}

\section{Mass-Ratio Distribution}
\label{sec:mrd}

\section{Discussion}
\label{sec:discussion}

\section*{Acknowledgements}
This research has made use of the SIMBAD database, operated at CDS, Strasbourg, France, and of Astropy, a community-developed core Python package for Astronomy (Astropy Collaboration, 2013).
It was supported by a start-up grant to Adam Kraus as well as a University of Texas Continuing Fellowship to Kevin Gullikson. J.-E. Lee was supported by the Basic Science Research Program through the National Research Foundation of Korea (NRF) (grant No. NRF-2015R1A2A2A01004769) and the Korea
Astronomy and Space Science Institute under the R\&D program (Project No. 2015-1-320-18) supervised by the Ministry of Science, ICT and Future Planning.

This work used the Immersion Grating Infrared Spectrograph (IGRINS) that was developed under a collaboration between the University of Texas at Austin and the Korea Astronomy and Space Science Institute (KASI) with the financial support of the US National Science Foundation under grant AST-1229522, of the University of Texas at Austin, and of the Korean GMT Project of KASI.

The Hobby-Eberly Telescope (HET) is a joint project of the University of Texas at Austin, the Pennsylvania State University, Stanford University, Ludwig-Maximilians-Universit\"at M\"unchen, and Georg-August-Universit\"at G\"ottingen. The HET is named in honor of its principal benefactors, William P. Hobby and Robert E. Eberly.

Based on observations at Cerro Tololo Inter-American Observatory, National Optical Astronomy Observatory (NOAO Prop. IDs: 13A-0139, 13B-0112, 2014A-0260, 14A-0260, 15A-0245; PI: Kevin Gullikson), which is operated by the Association of Universities for Research in Astronomy (AURA) under a cooperative agreement with the National Science Foundation.

We would like to thank Bill Cochran and Mike Endl for observing some of the spectra used in this project. . Finally, we would like to thank the anonymous referee for numerous comments that improved the paper.

\begin{longtable*}{|l|lllrlrr|}
\hline
              &                &                &                &          MJD &            &  exptime &     snr \\
         star &            SpT &             ra &            dec & (JD-2450000) & instrument &  (sec)   &         \\ \hline
\endhead
\hline
\multicolumn{3}{r}{{Continued on next page}} \\
\endfoot

\hline
\endlastfoot
     HIP 813 &           B9Vn &     00:10:2.20 &   +11:08:44.93 &  6618.58 &       TS23 &      557 &    1810 \\
    HIP 1191 &          B8.5V &    00:14:54.52 &   -09:34:10.45 &  6552.60 &     CHIRON &     1200 &     320 \\
    HIP 1366 &            A2V &     00:17:5.50 &   +38:40:53.89 &  6585.73 &       TS23 &      274 &    1790 \\
    HIP 1647 &            B9V &    00:20:39.04 &   -69:37:29.68 &  6510.74 &     CHIRON &     1105 &     630 \\
    HIP 2381 &            A3V &    00:30:22.65 &   -23:47:15.65 &  6874.71 &     CHIRON &      505 &     580 \\
    HIP 2505 &           B8Vn &    00:31:46.36 &   +54:31:20.23 &  6586.71 &       TS23 &      235 &    1700 \\
    HIP 2505 &           B8Vn &    00:31:46.36 &   +54:31:20.23 &  6962.71 &       TS23 &      804 &    1960 \\
    HIP 2505 &           B8Vn &    00:31:46.36 &   +54:31:20.23 &  6945.71 &     IGRINS &      224 &     450 \\
    HIP 2548 &          B9.5V &    00:32:23.78 &   +06:57:19.66 &  7240.93 &     IGRINS &      360 &     490 \\
    HIP 2548 &          B9.5V &    00:32:23.78 &   +06:57:19.66 &  6516.84 &        HRS &      412 &    1070 \\
    HIP 2912 &            B5V &    00:36:52.85 &    +33:43:9.64 &  7238.96 &     IGRINS &      367 &     790 \\
    HIP 2912 &            B5V &    00:36:52.85 &    +33:43:9.64 &  6583.78 &       TS23 &      199 &    2460 \\
    HIP 3300 &            B2V &     00:42:3.90 &   +50:30:45.09 &  6299.55 &       TS23 &      689 &    1010 \\
    HIP 3478 &            B5V &    00:44:26.19 &   +47:51:50.34 &  6963.63 &       TS23 &     1200 &    1020 \\
    HIP 3478 &            B5V &    00:44:26.19 &   +47:51:50.34 &  7288.82 &     IGRINS &      540 &     800 \\
    HIP 3478 &            B5V &    00:44:26.19 &   +47:51:50.34 &  6669.53 &       TS23 &      743 &    1870 \\
    HIP 3478 &            B5V &    00:44:26.19 &   +47:51:50.34 &  6945.72 &     IGRINS &      224 &     260 \\
    HIP 3741 &            B9V &     00:48:1.06 &   -21:43:20.99 &  7174.89 &     CHIRON &     3981 &     430 \\
    HIP 3741 &            B9V &     00:48:1.06 &   -21:43:20.99 &  7175.90 &     CHIRON &     3561 &     420 \\
    HIP 3881 &     F8IV-V+M4V &    00:49:48.85 &   +41:04:44.08 &  6585.70 &       TS23 &      222 &    1690 \\
    HIP 3881 &     F8IV-V+M4V &    00:49:48.85 &   +41:04:44.08 &  6964.60 &       TS23 &     1200 &     710 \\
    HIP 3881 &     F8IV-V+M4V &    00:49:48.85 &   +41:04:44.08 &  6945.74 &     IGRINS &      224 &     510 \\
    HIP 4436 &            A5V &    00:56:45.21 &   +38:29:57.64 &  6585.76 &       TS23 &      129 &    1940 \\
    HIP 5131 &           A1Vn &    01:05:40.96 &   +21:28:23.45 &  6587.70 &       TS23 &      655 &    1780 \\
    HIP 5131 &           A1Vn &    01:05:40.96 &   +21:28:23.45 &  7083.57 &     IGRINS &      930 &     130 \\
    HIP 5131 &           A1Vn &    01:05:40.96 &   +21:28:23.45 &  6847.89 &     IGRINS &     1600 &     490 \\
    HIP 5132 &           A0Vn &    01:05:41.71 &   +21:27:55.60 &  6587.77 &       TS23 &      535 &    1550 \\
    HIP 5132 &           A0Vn &    01:05:41.71 &   +21:27:55.60 &  6847.89 &     IGRINS &      480 &     490 \\
    HIP 5310 &            A3V &    01:07:57.16 &   +20:44:20.83 &  6945.75 &     IGRINS &      224 &     390 \\
    HIP 5348 &        B6V+B9V &    01:08:23.08 &   -55:14:44.73 &  6325.56 &     CHIRON &      186 &     390 \\
    HIP 5361 &            B8V &    01:08:33.47 &   +58:15:48.41 &  6523.84 &        HRS &     1000 &     810 \\
    HIP 5518 &          A0Vnn &    01:10:39.32 &   +68:46:43.04 &  7238.94 &     IGRINS &      540 &     750 \\
    HIP 5518 &          A0Vnn &    01:10:39.32 &   +68:46:43.04 &  6945.77 &     IGRINS &      224 &     370 \\
    HIP 5626 &            A3V &    01:12:16.82 &   +79:40:26.27 &  6945.88 &     IGRINS &      224 &     270 \\
    HIP 7345 &            A1V &    01:34:37.78 &   -15:40:34.90 &  6888.76 &     CHIRON &     1080 &     480 \\
    HIP 7345 &            A1V &    01:34:37.78 &   -15:40:34.90 &  6887.76 &     CHIRON &      706 &     540 \\
    HIP 8016 &            B9V &    01:42:55.86 &   +70:37:21.09 &  6522.96 &        HRS &      328 &     580 \\
    HIP 8704 &          B1.5V &    01:51:59.32 &   +55:08:50.58 &  6506.90 &        HRS &      365 &     420 \\
    HIP 8704 &          B1.5V &    01:51:59.32 &   +55:08:50.58 &  7084.57 &     IGRINS &      960 &     140 \\
    HIP 8704 &          B1.5V &    01:51:59.32 &   +55:08:50.58 &  7237.93 &     IGRINS &      720 &     630 \\
      HR 545 &         B9.5IV &    01:53:31.77 &   +19:17:46.27 &  6668.56 &       TS23 &      597 &    1920 \\
      HR 545 &         B9.5IV &    01:53:31.77 &   +19:17:46.27 &  6586.75 &       TS23 &      265 &    1710 \\
      HR 545 &         B9.5IV &    01:53:31.77 &   +19:17:46.27 &  6945.81 &     IGRINS &      224 &     540 \\
    HIP 9312 &           A0Vn &    01:59:38.04 &   +64:37:17.76 &  6586.78 &       TS23 &      419 &    1750 \\
    HIP 9564 &           A1Vn &    02:02:52.48 &    +64:54:5.27 &  6945.78 &     IGRINS &      224 &     180 \\
      HR 604 &        B8V+A0V &    02:03:54.72 &   +42:19:51.41 &  6585.86 &       TS23 &      349 &    1650 \\
   HIP 10320 &            B9V &    02:12:54.47 &   -30:43:25.77 &  6532.80 &     CHIRON &     1020 &     550 \\
   HIP 10670 &          A1Vnn &    02:17:18.87 &   +33:50:49.90 &  6618.68 &       TS23 &      141 &    1810 \\
   HIP 10732 &           A1Vn &     02:18:7.54 &    +19:54:4.19 &  6945.82 &     IGRINS &      224 &     290 \\
   HIP 10732 &           A1Vn &     02:18:7.54 &    +19:54:4.19 &  7083.56 &     IGRINS &      240 &     160 \\
   HIP 11345 &            A0V &    02:25:57.01 &   -12:17:25.71 &  6894.90 &     CHIRON &      540 &     520 \\
   HIP 12332 &            A7V &    02:38:48.99 &   +21:57:41.06 &  6677.54 &       TS23 &     1107 &    1530 \\
   HIP 12332 &            A7V &    02:38:48.99 &   +21:57:41.06 &  6947.79 &     IGRINS &      224 &     430 \\
   HIP 12706 &       A2Vn+F4V &    02:43:18.04 &    +03:14:8.94 &  6584.86 &       TS23 &      362 &     990 \\
   HIP 12706 &       A2Vn+F4V &    02:43:18.04 &    +03:14:8.94 &  6946.84 &     IGRINS &      224 &    2280 \\
   HIP 12719 &            B3V &    02:43:27.11 &   +27:42:25.72 &  6583.87 &       TS23 &      264 &    1720 \\
   HIP 12803 &           B9Vn &    02:44:32.97 &   +15:18:42.71 &  6676.53 &       TS23 &      452 &    1410 \\
   HIP 12803 &           B9Vn &    02:44:32.97 &   +15:18:42.71 &  6947.80 &     IGRINS &      224 &     450 \\
   HIP 12803 &           B9Vn &    02:44:32.97 &   +15:18:42.71 &  7240.95 &     IGRINS &      780 &    1120 \\
   HIP 13165 &            B6V &    02:49:17.56 &   +17:27:51.52 &  6518.91 &        HRS &      275 &     850 \\
   HIP 13202 &            A0V &    02:49:54.18 &   -27:56:31.14 &  6910.83 &     CHIRON &      580 &     570 \\
   HIP 13209 &           B8Vn &    02:49:59.03 &   +27:15:37.83 &  6618.66 &       TS23 &      143 &    1880 \\
   HIP 13327 &            B7V &    02:51:29.59 &   +15:04:55.45 &  6670.54 &       TS23 &     1200 &    1800 \\
   HIP 13717 &            A3V &    02:56:37.42 &   -03:42:44.35 &  6917.83 &     CHIRON &      644 &     550 \\
   HIP 13717 &            A3V &    02:56:37.42 &   -03:42:44.35 &  6970.75 &     CHIRON &      703 &     550 \\
   HIP 13879 &           A2Vn &    02:58:45.67 &   +39:39:45.81 &  6945.79 &     IGRINS &      224 &     620 \\
   HIP 13879 &           A2Vn &    02:58:45.67 &   +39:39:45.81 &  6681.68 &       TS23 &      930 &     230 \\
   HIP 13879 &           A2Vn &    02:58:45.67 &   +39:39:45.81 &  6618.70 &       TS23 &      265 &    1490 \\
   HIP 14043 &            B7V &    03:00:52.21 &    +52:21:6.22 &  6523.92 &        HRS &      400 &     620 \\
   HIP 14143 &            B7V &    03:02:22.52 &   +04:21:10.39 &  6518.94 &        HRS &      462 &     900 \\
   HIP 14293 &            A5V &    03:04:16.52 &    -07:36:3.08 &  6919.89 &     CHIRON &      800 &     240 \\
   HIP 14576 &            B8V &    03:08:10.13 &   +40:57:20.33 &  6583.83 &       TS23 &       40 &    1030 \\
   HIP 14576 &            B8V &    03:08:10.13 &   +40:57:20.33 &  6582.92 &       TS23 &       36 &    2050 \\
   HIP 14764 &            B8V &    03:10:38.79 &   +11:52:21.44 &  6679.53 &       TS23 &      532 &    1370 \\
   HIP 14764 &            B8V &    03:10:38.79 &   +11:52:21.44 &  6946.80 &     IGRINS &      360 &     410 \\
   HIP 14862 &          A2Vnn &    03:11:56.27 &   +74:23:37.17 &  6945.86 &     IGRINS &      224 &     500 \\
   HIP 14862 &          A2Vnn &    03:11:56.27 &   +74:23:37.17 &  7084.60 &     IGRINS &     1200 &     370 \\
   HIP 15110 &            A1V &    03:14:54.10 &   +21:02:40.01 &  6946.83 &     IGRINS &      224 &     630 \\
   HIP 15338 &            B8V &    03:17:47.35 &   +44:01:30.08 &  6523.90 &        HRS &      570 &     690 \\
   HIP 15404 &            B3V &    03:18:37.74 &   +50:13:19.83 &  6517.92 &        HRS &      205 &     620 \\
   HIP 15444 &            B5V &     03:19:7.64 &   +50:05:41.88 &  6582.94 &       TS23 &      340 &    1790 \\
   HIP 16147 &            B5V &     03:28:3.07 &   +49:03:46.32 &  6299.59 &       TS23 &      735 &    1300 \\
   HIP 16210 &           B6Vn &    03:28:52.33 &   +49:50:54.17 &  6676.58 &       TS23 &      406 &    1440 \\
   HIP 16210 &           B6Vn &    03:28:52.33 &   +49:50:54.17 &  6945.84 &     IGRINS &      224 &     430 \\
   HIP 16244 &            B3V &    03:29:22.05 &   +49:30:32.21 &  6583.84 &       TS23 &      311 &    1750 \\
   HIP 16244 &            B3V &    03:29:22.05 &   +49:30:32.21 &  6945.83 &     IGRINS &      224 &     430 \\
   HIP 16285 &            A5V &    03:29:55.15 &    -42:38:3.32 &  6933.84 &     CHIRON &      767 &     570 \\
   HIP 16322 &           A0Vn &    03:30:24.47 &   +11:20:11.19 &  6944.72 &     CHIRON &      680 &     410 \\
   HIP 16322 &           A0Vn &    03:30:24.47 &   +11:20:11.19 &  6946.82 &     IGRINS &      224 &     590 \\
   HIP 16340 &            B8V &    03:30:36.95 &   +48:06:12.95 &  6678.54 &       TS23 &      570 &    1410 \\
   HIP 16599 &            A3V &    03:33:39.06 &   +54:58:29.49 &  6945.85 &     IGRINS &      224 &     280 \\
   HIP 16611 &            B9V &    03:33:47.28 &   -21:37:58.38 &  6946.85 &     IGRINS &      224 &     420 \\
   HIP 16611 &            B9V &    03:33:47.28 &   -21:37:58.38 &  6522.88 &     CHIRON &      255 &     580 \\
   HIP 17457 &           B7IV &    03:44:30.51 &   -01:09:47.14 &  6531.82 &     CHIRON &     1005 &     520 \\
   HIP 17563 &            B3V &    03:45:40.44 &   +06:02:59.97 &  6538.82 &     CHIRON &     1088 &     400 \\
   HIP 17527 &            B8V &     03:45:9.74 &   +24:50:21.34 &  6947.82 &     IGRINS &      224 &     230 \\
   HIP 17527 &            B8V &     03:45:9.74 &   +24:50:21.34 &  6517.93 &        HRS &      429 &     670 \\
   HIP 17527 &            B8V &     03:45:9.74 &   +24:50:21.34 &  6963.91 &       TS23 &      818 &     470 \\
   HIP 18141 &            B8V &    03:52:41.66 &   -05:21:40.54 &  6678.59 &       TS23 &      605 &    1430 \\
   HIP 18396 &            B6V &    03:55:58.17 &   +47:52:17.12 &  6516.94 &        HRS &      259 &     510 \\
   HIP 18724 &        B3V+... &    04:00:40.82 &   +12:29:25.22 &  6299.62 &       TS23 &      226 &    1220 \\
   HIP 18788 &            B5V &    04:01:32.05 &   -01:32:58.78 &  6535.81 &     CHIRON &     1039 &     180 \\
   HIP 18805 &            B5V &    04:01:46.14 &   +09:59:52.84 &  6585.78 &       TS23 &      631 &    1760 \\
   HIP 19799 &           B9Vn &    04:14:36.23 &   +10:00:41.05 &  6668.63 &       TS23 &     1200 &    1900 \\
   HIP 19949 &           A2Vn &    04:16:43.09 &   +53:36:42.47 &  6945.90 &     IGRINS &      224 &     440 \\
   HIP 19949 &           A2Vn &    04:16:43.09 &   +53:36:42.47 &  7084.62 &     IGRINS &      960 &      80 \\
   HIP 19968 &            B7V &    04:16:53.56 &   +61:50:59.97 &  6676.62 &       TS23 &      524 &    1390 \\
   HIP 20264 &            A0V &    04:20:39.01 &   -20:38:22.64 &  6718.53 &     CHIRON &      860 &     410 \\
   HIP 20380 &            A3V &    04:21:51.81 &   +56:30:22.74 &  6945.89 &     IGRINS &      224 &     280 \\
   HIP 20380 &            A3V &    04:21:51.81 &   +56:30:22.74 &  7084.67 &     IGRINS &     1200 &     180 \\
   HIP 20430 &          B9Vnn &    04:22:34.94 &   +25:37:45.54 &  6520.95 &        HRS &      360 &     710 \\
   HIP 20507 &            A2V &    04:23:40.85 &   -03:44:43.68 &  6719.50 &     CHIRON &      715 &     470 \\
   HIP 20579 &            B8V &    04:24:29.16 &   +34:07:50.73 &  6517.96 &        HRS &      490 &     830 \\
   HIP 20789 &            B7V &    04:27:17.45 &   +22:59:46.80 &  6946.86 &     IGRINS &      224 &     250 \\
   HIP 20789 &            B7V &    04:27:17.45 &   +22:59:46.80 &  6586.83 &       TS23 &      524 &    1610 \\
   HIP 21589 &            A6V &     04:38:9.46 &   +12:30:39.01 &  6962.94 &       TS23 &      220 &    1020 \\
   HIP 21589 &            A6V &     04:38:9.46 &   +12:30:39.01 &  7065.63 &     CHIRON &      754 &     290 \\
   HIP 21589 &            A6V &     04:38:9.46 &   +12:30:39.01 &  6948.96 &     IGRINS &      112 &     670 \\
   HIP 21683 &           A5Vn &    04:39:16.50 &    +15:55:4.70 &  6948.98 &     IGRINS &      230 &     220 \\
   HIP 21683 &           A5Vn &    04:39:16.50 &    +15:55:4.70 &  6962.97 &       TS23 &      335 &    1040 \\
   HIP 21819 &            A2V &    04:41:19.76 &   +28:36:53.98 &  6679.64 &       TS23 &      466 &    1480 \\
   HIP 21928 &           A1Vn &    04:42:54.33 &   +43:21:54.53 &  6677.63 &       TS23 &     1124 &    1470 \\
   HIP 22028 &            A1V &     04:44:7.98 &   -18:39:59.71 &  6947.90 &     IGRINS &      240 &     260 \\
   HIP 22509 &           A1Vn &    04:50:36.72 &    +08:54:0.65 &  6667.62 &       TS23 &     1200 &    1100 \\
   HIP 22509 &           A1Vn &    04:50:36.72 &    +08:54:0.65 &  7126.51 &     CHIRON &     2612 &     440 \\
   HIP 22833 &            A3V &    04:54:46.90 &   +11:25:33.63 &  6679.60 &       TS23 &      521 &    1520 \\
   HIP 22833 &            A3V &    04:54:46.90 &   +11:25:33.63 &  6946.87 &     IGRINS &      224 &     420 \\
   HIP 22840 &            B5V &    04:54:50.71 &    +00:28:1.81 &  6678.64 &       TS23 &      528 &    1380 \\
   HIP 22913 &            B9V &    04:55:50.15 &   +15:02:25.00 &  6585.74 &     CHIRON &     1200 &     230 \\
   HIP 22958 &            B6V &    04:56:24.19 &   -05:10:16.87 &  6551.79 &     CHIRON &     1200 &     340 \\
   HIP 22958 &            B6V &    04:56:24.19 &   -05:10:16.87 &  6943.77 &     CHIRON &      650 &     320 \\
   HIP 23362 &            B9V &    05:01:25.58 &    -20:03:6.91 &  6548.87 &     CHIRON &      725 &     520 \\
   HIP 23362 &            B9V &    05:01:25.58 &    -20:03:6.91 &  6946.93 &     IGRINS &      240 &     290 \\
   HIP 23916 &          B8III &    05:08:20.19 &   -08:39:55.17 &  6555.82 &     CHIRON &     1200 &      40 \\
   HIP 23916 &          B8III &    05:08:20.19 &   -08:39:55.17 &  6946.95 &     IGRINS &      280 &     260 \\
   HIP 24244 &         B7.5Vn &    05:12:17.90 &    -11:52:9.19 &  6949.84 &     CHIRON &      370 &     560 \\
   HIP 24244 &         B7.5Vn &    05:12:17.90 &    -11:52:9.19 &  6554.91 &     CHIRON &      488 &     330 \\
   HIP 24327 &            B7V &    05:13:13.88 &   -12:56:28.65 &  6529.88 &     CHIRON &      277 &     560 \\
   HIP 24505 &            B9V &    05:15:24.37 &   -26:56:36.63 &  7036.69 &     CHIRON &     2045 &     480 \\
   HIP 24902 &            A3V &    05:20:14.67 &   +41:05:10.35 &  6946.88 &     IGRINS &      224 &     300 \\
   HIP 25048 &            B3V &    05:21:48.42 &   +41:48:16.46 &  6299.69 &       TS23 &      900 &     420 \\
 ADS 3962 AB &           B1Vn &    05:22:50.30 &   +03:32:52.00 &  6946.92 &     IGRINS &      280 &     330 \\
   HIP 25143 &            A3V &    05:22:50.31 &   +41:01:45.33 &  7084.65 &     IGRINS &      960 &     170 \\
   HIP 25143 &            A3V &    05:22:50.31 &   +41:01:45.33 &  6946.89 &     IGRINS &      224 &     290 \\
   HIP 25280 &            A0V &    05:24:28.49 &   -16:58:32.81 &  6950.75 &     CHIRON &      597 &     540 \\
   HIP 25280 &            A0V &    05:24:28.49 &   -16:58:32.81 &  6947.91 &     IGRINS &      240 &     250 \\
   HIP 25281 &        B1V+B2: &    05:24:28.62 &   -02:23:49.73 &  6299.71 &       TS23 &      583 &    1120 \\
   HIP 25555 &         B9.5Vn &    05:27:45.61 &   +15:52:26.58 &  6670.63 &       TS23 &      600 &    1950 \\
   HIP 25608 &            A1V &    05:28:15.34 &   -37:13:50.75 &  6718.62 &     CHIRON &     1030 &     360 \\
   HIP 25695 &           B9Vn &    05:29:16.50 &    +25:09:0.78 &  6669.65 &       TS23 &     1200 &    1860 \\
   HIP 25790 &           A3Vn &    05:30:26.16 &   +15:21:37.61 &  6946.90 &     IGRINS &      224 &     260 \\
   HIP 25813 &            B5V &    05:30:47.05 &   +05:56:53.29 &  7083.58 &     IGRINS &     1020 &     630 \\
   HIP 25813 &            B5V &    05:30:47.05 &   +05:56:53.29 &  6544.88 &     CHIRON &      384 &     260 \\
   HIP 26063 &            B1V &    05:33:31.45 &   -01:09:21.87 &  6582.80 &     CHIRON &     1139 &     250 \\
   HIP 26093 &            B3V &    05:33:54.28 &   +14:18:20.08 &  6946.91 &     IGRINS &      280 &     260 \\
   HIP 26093 &            B3V &    05:33:54.28 &   +14:18:20.08 &  6676.66 &       TS23 &      525 &    1380 \\
   HIP 26093 &            B3V &    05:33:54.28 &   +14:18:20.08 &  7084.72 &     IGRINS &     1800 &     370 \\
   HIP 26126 &            A2V &    05:34:16.77 &    +03:46:0.82 &  6946.96 &     IGRINS &      240 &     470 \\
   HIP 26126 &            A2V &    05:34:16.77 &    +03:46:0.82 &  6721.50 &     CHIRON &      507 &     450 \\
   HIP 26126 &            A2V &    05:34:16.77 &    +03:46:0.82 &  6948.81 &     CHIRON &      550 &     360 \\
     HR 1880 &          B0.5V &     05:35:8.48 &    +09:56:6.10 &  6594.74 &     CHIRON &      472 &     540 \\
   HIP 26563 &           A4Vn &    05:38:53.08 &   -07:12:46.18 &  6677.68 &       TS23 &      502 &    1550 \\
   HIP 27100 &            A7V &    05:44:46.38 &    -65:44:7.90 &  6692.59 &     CHIRON &      294 &     680 \\
   HIP 27100 &            A7V &    05:44:46.38 &    -65:44:7.90 &  6727.54 &     CHIRON &      177 &     560 \\
   HIP 27321 &            A6V &    05:47:17.09 &   -51:03:59.44 &  6696.62 &     CHIRON &      178 &     640 \\
   HIP 27713 &           A2Vn &     05:52:7.73 &   -09:02:30.84 &  6946.97 &     IGRINS &      240 &     270 \\
   HIP 28691 &            B8V &    06:03:27.37 &   +19:41:26.02 &  6298.78 &       TS23 &      646 &    1300 \\
   HIP 28756 &          B2.5V &    06:04:20.27 &   -32:10:20.74 &  6571.74 &     CHIRON &     1200 &     320 \\
   HIP 28910 &            A0V &     06:06:9.32 &    -14:56:6.92 &  6693.61 &     CHIRON &      343 &     560 \\
   HIP 29150 &            A0V &    06:08:57.87 &   -22:25:38.68 &  6697.63 &     CHIRON &      950 &     380 \\
   HIP 29151 &           A3Vn &    06:08:57.90 &   +02:29:58.89 &  6946.99 &     IGRINS &      264 &     340 \\
   HIP 29151 &           A3Vn &    06:08:57.90 &   +02:29:58.89 &  6953.82 &     CHIRON &      617 &     540 \\
   HIP 29735 &            B9V &    06:15:44.89 &    -13:43:6.29 &  6559.80 &     CHIRON &      803 &     380 \\
   HIP 29735 &            B9V &    06:15:44.89 &    -13:43:6.29 &  6946.98 &     IGRINS &      240 &     250 \\
   HIP 29997 &           A0Vn &    06:18:50.78 &   +69:19:11.23 &  6679.70 &       TS23 &      415 &    1460 \\
   HIP 30069 &            B9V &    06:19:40.96 &   -34:23:47.73 &  6573.75 &     CHIRON &     1200 &     250 \\
   HIP 30073 &          B2.5V &  06:19:42.7989 &  -07:49:22.473 &  6581.82 &     CHIRON &     1011 &     280 \\
   HIP 30666 &           A3Vn &    06:26:39.59 &   -01:30:26.41 &  6947.00 &     IGRINS &      280 &     310 \\
   HIP 30788 &            B4V &    06:28:10.21 &   -32:34:48.25 &  6574.75 &     CHIRON &      488 &     340 \\
   HIP 31278 &           B5Vn &    06:33:37.92 &   -01:13:12.55 &  7084.69 &     IGRINS &      960 &     350 \\
   HIP 31278 &           B5Vn &    06:33:37.92 &   -01:13:12.55 &  6668.71 &       TS23 &      797 &    1920 \\
   HIP 31278 &           B5Vn &    06:33:37.92 &   -01:13:12.55 &  6947.01 &     IGRINS &      280 &     390 \\
   HIP 31362 &            B8V &    06:34:35.33 &   -32:42:58.51 &  6598.72 &     CHIRON &     1200 &     250 \\
   HIP 31434 &          A0Vnn &    06:35:12.06 &   +28:01:20.32 &  6676.71 &       TS23 &      611 &    1480 \\
   HIP 32474 &          B9.5V &    06:46:39.02 &   -10:06:26.50 &  6592.74 &     CHIRON &     1200 &     340 \\
   HIP 32607 &        A8VnkA6 &    06:48:11.46 &   -61:56:29.00 &  7037.75 &     CHIRON &       56 &     210 \\
   HIP 32607 &        A8VnkA6 &    06:48:11.46 &   -61:56:29.00 &  7039.62 &     CHIRON &       49 &     210 \\
   HIP 32607 &        A8VnkA6 &    06:48:11.46 &   -61:56:29.00 &  6724.56 &     CHIRON &       67 &     560 \\
   HIP 33372 &           B8Vn &    06:56:25.83 &   +09:57:23.67 &  6948.00 &     IGRINS &      320 &     330 \\
   HIP 33372 &           B8Vn &    06:56:25.83 &   +09:57:23.67 &  6678.72 &       TS23 &      720 &    1380 \\
   HIP 33575 &            B2V &    06:58:35.90 &   -25:24:50.97 &  6599.72 &     CHIRON &     1200 &     390 \\
   HIP 34769 &            A2V &    07:11:51.86 &   -00:29:33.96 &  6677.75 &       TS23 &      279 &    1520 \\
   HIP 35180 &            A1V &    07:16:14.55 &    -15:35:8.49 &  6696.76 &     CHIRON &      925 &     290 \\
   HIP 35341 &           A5Vn &     07:18:2.22 &    +40:53:0.22 &  6680.75 &       TS23 &      833 &    1070 \\
   HIP 36393 &            A4V &    07:29:20.44 &    +28:07:5.79 &  6676.76 &       TS23 &      616 &    1550 \\
   HIP 36393 &            A4V &    07:29:20.44 &    +28:07:5.79 &  6670.76 &       TS23 &      494 &    1400 \\
   HIP 36760 &           A1Vn &    07:33:36.48 &   +15:49:35.98 &  7084.74 &     IGRINS &      720 &     760 \\
   HIP 36760 &           A1Vn &    07:33:36.48 &   +15:49:35.98 &  7037.76 &     CHIRON &     4284 &     370 \\
   HIP 36760 &           A1Vn &    07:33:36.48 &   +15:49:35.98 &  7039.68 &     CHIRON &     3127 &     480 \\
   HIP 36760 &           A1Vn &    07:33:36.48 &   +15:49:35.98 &  6668.79 &       TS23 &      836 &     700 \\
   HIP 36812 &          A0Vnn &    07:34:15.89 &   +03:22:18.19 &  6947.99 &     IGRINS &      280 &     320 \\
   HIP 36917 &            B7V &    07:35:22.89 &    -28:22:9.57 &  6583.81 &     CHIRON &      571 &     420 \\
   HIP 36917 &            B7V &    07:35:22.89 &    -28:22:9.57 &  6971.83 &     CHIRON &      435 &     690 \\
     HR 2948 &            B6V &    07:38:49.38 &    -26:48:6.49 &  6584.81 &     CHIRON &      576 &     370 \\
   HIP 37297 &          B2.5V &    07:39:27.34 &   -38:18:28.88 &  6698.74 &     CHIRON &      370 &     480 \\
   HIP 37297 &          B2.5V &    07:39:27.34 &   -38:18:28.88 &  6574.82 &     CHIRON &      686 &     340 \\
   HIP 37297 &          B2.5V &    07:39:27.34 &   -38:18:28.88 &  6729.53 &     CHIRON &      231 &     460 \\
   HIP 37322 &            B5V &    07:39:43.81 &   -38:08:21.44 &  6975.79 &     CHIRON &      817 &     540 \\
   HIP 37450 &            B5V &    07:41:15.81 &    -38:32:0.72 &  6600.74 &     CHIRON &     1171 &     450 \\
   HIP 38538 &           A5IV &    07:53:29.81 &   +26:45:56.82 &  6669.78 &       TS23 &      474 &    1990 \\
   HIP 38593 &            B2V &    07:54:11.01 &   -35:52:38.23 &  7039.70 &     CHIRON &      331 &     170 \\
   HIP 38593 &            B2V &    07:54:11.01 &   -35:52:38.23 &  6599.82 &     CHIRON &     1200 &     410 \\
   HIP 38593 &            B2V &    07:54:11.01 &   -35:52:38.23 &  6592.87 &     CHIRON &     1200 &     300 \\
   HIP 38846 &          B2.5V &    07:56:57.80 &    -43:30:1.48 &  6601.76 &     CHIRON &     1098 &     400 \\
   HIP 39095 &            A1V &    07:59:52.05 &   -18:23:57.23 &  6765.53 &     CHIRON &      430 &     450 \\
   HIP 39095 &            A1V &    07:59:52.05 &   -18:23:57.23 &  6757.56 &     CHIRON &      238 &     490 \\
   HIP 39095 &            A1V &    07:59:52.05 &   -18:23:57.23 &  6711.62 &     CHIRON &      288 &     500 \\
   HIP 39236 &         B9.5Vn &    08:01:30.29 &   +16:27:19.12 &  6679.73 &       TS23 &      730 &    1420 \\
   HIP 39567 &            A1V &     08:05:4.49 &    +13:07:5.58 &  6668.80 &       TS23 &      613 &    1940 \\
   HIP 39847 &            A2V &    08:08:27.45 &   +51:30:24.01 &  7084.68 &     IGRINS &      480 &     570 \\
   HIP 39847 &            A2V &    08:08:27.45 &   +51:30:24.01 &  6676.80 &       TS23 &      402 &    1500 \\
   HIP 39906 &            B5V &     08:09:1.64 &   -19:14:42.05 &  6580.86 &     CHIRON &      457 &     270 \\
   HIP 40429 &            A2V &    08:15:15.92 &   -62:54:56.32 &  6691.72 &     CHIRON &      710 &     560 \\
   HIP 40706 &            A8V &    08:18:33.31 &   -36:39:33.44 &  6327.64 &     CHIRON &      277 &     630 \\
   HIP 40881 &          B9.5V &    08:20:32.14 &   +24:01:20.32 &  6947.97 &     IGRINS &      240 &     310 \\
   HIP 41039 &            B1V &    08:22:31.69 &   -48:29:25.36 &  7039.73 &     CHIRON &     1728 &     530 \\
   HIP 41039 &            B1V &    08:22:31.69 &   -48:29:25.36 &  6330.77 &     CHIRON &      404 &     400 \\
   HIP 41307 &           A0Va &    08:25:39.63 &   -03:54:23.12 &  6667.82 &       TS23 &      700 &    1220 \\
   HIP 42090 &          A2Vnn &    08:34:43.88 &   +36:25:10.63 &  7124.62 &     IGRINS &      630 &     280 \\
   HIP 42129 &        B3V+... &    08:35:15.56 &   -58:13:29.05 &  6603.80 &     CHIRON &     1001 &     370 \\
   HIP 42313 &          A0Vnn &    08:37:39.37 &   +05:42:13.61 &  6681.81 &       TS23 &      489 &    1020 \\
   HIP 42334 &            A0V &    08:37:52.15 &   -26:15:18.01 &  6712.64 &     CHIRON &      381 &     480 \\
   HIP 43142 &            A3V &    08:47:14.99 &   -01:53:49.31 &  6670.79 &       TS23 &      647 &    1980 \\
   HIP 44127 &     A7V(n)+M1V &    08:59:12.45 &   +48:02:30.57 &  6677.88 &       TS23 &      239 &    1600 \\
   HIP 44307 &            A2V &    09:01:24.13 &    +32:15:8.26 &  6947.98 &     IGRINS &      280 &     500 \\
   HIP 45336 &    B9.5V+DA1.6 &    09:14:21.86 &   +02:18:51.34 &  6328.70 &     CHIRON &      171 &     290 \\
   HIP 45336 &    B9.5V+DA1.6 &    09:14:21.86 &   +02:18:51.34 &  7122.66 &     IGRINS &      270 &     230 \\
   HIP 45336 &    B9.5V+DA1.6 &    09:14:21.86 &   +02:18:51.34 &  7084.75 &     IGRINS &      240 &     330 \\
   HIP 45344 &            B4V &    09:14:24.48 &   -43:13:38.97 &  6612.79 &     CHIRON &     1001 &     320 \\
   HIP 45688 &            A1V &    09:18:50.64 &    +36:48:9.33 &  6299.93 &       TS23 &      600 &     880 \\
   HIP 46225 &            A4V &    09:25:27.23 &    -61:57:1.72 &  6679.84 &       TS23 &      933 &    1300 \\
   HIP 46283 &            B6V &    09:26:17.96 &   -53:22:44.07 &  6732.56 &     CHIRON &      357 &     490 \\
   HIP 46283 &            B6V &    09:26:17.96 &   -53:22:44.07 &  6619.80 &     CHIRON &      872 &     430 \\
   HIP 46283 &            B6V &    09:26:17.96 &   -53:22:44.07 &  6712.70 &     CHIRON &      352 &     450 \\
   HIP 46897 &          B9.5V &    09:33:26.05 &   -22:51:49.99 &  7084.78 &     IGRINS &     1200 &     230 \\
   HIP 46897 &          B9.5V &    09:33:26.05 &   -22:51:49.99 &  7139.59 &     IGRINS &      720 &     400 \\
   HIP 47006 &           A0Vn &    09:34:49.43 &    +52:03:5.32 &  6677.03 &       TS23 &      373 &    1590 \\
   HIP 47175 &            A7V &    09:36:49.54 &   -49:21:18.09 &  6424.56 &     CHIRON &      264 &     660 \\
   HIP 50303 &           A0Vn &    10:16:14.43 &   +29:18:37.81 &  6677.78 &       TS23 &     1200 &    1350 \\
   HIP 50860 &          A5IVn &     10:23:6.33 &   +33:54:29.31 &  6678.81 &       TS23 &     1151 &    1470 \\
   HIP 51362 &          B9.5V &    10:29:28.70 &   -02:44:20.69 &  7043.79 &     CHIRON &     1298 &     340 \\
   HIP 51362 &          B9.5V &    10:29:28.70 &   -02:44:20.69 &  6625.81 &     CHIRON &      947 &     200 \\
   HIP 51362 &          B9.5V &    10:29:28.70 &   -02:44:20.69 &  6673.75 &     CHIRON &      606 &     510 \\
   HIP 51362 &          B9.5V &    10:29:28.70 &   -02:44:20.69 &  7084.76 &     IGRINS &      720 &     240 \\
   HIP 51685 &           A2Vn &    10:33:30.91 &   +34:59:19.30 &  6677.90 &       TS23 &     1046 &    1460 \\
   HIP 52422 &           A4Vn &     10:43:1.88 &   +26:19:32.09 &  6676.87 &       TS23 &      522 &    1540 \\
   HIP 52457 &           A3Vn &    10:43:24.96 &   +23:11:18.25 &  6676.83 &       TS23 &      647 &    1500 \\
   HIP 52638 &           A1Vn &    10:45:51.89 &   +30:40:56.33 &  6669.83 &       TS23 &      711 &    1900 \\
   HIP 52678 &          B6Vnn &    10:46:16.56 &   -64:30:52.41 &  6748.56 &     CHIRON &      375 &     500 \\
   HIP 52678 &          B6Vnn &    10:46:16.56 &   -64:30:52.41 &  6690.70 &     CHIRON &      618 &     610 \\
   HIP 52736 &         B2.5Vn &    10:46:51.22 &    -64:23:0.50 &  6748.52 &     CHIRON &      530 &     540 \\
   HIP 52736 &         B2.5Vn &    10:46:51.22 &    -64:23:0.50 &  6713.70 &     CHIRON &      263 &     490 \\
   HIP 52911 &            A2V &    10:49:15.43 &   +10:32:42.73 &  6670.86 &       TS23 &      758 &    1950 \\
     HR 4259 &            A1V &    10:55:36.80 &   +24:44:59.00 &  6335.70 &     CHIRON &      304 &     330 \\
   HIP 54849 &            A0V &    11:13:45.55 &   -00:04:10.20 &  6670.94 &       TS23 &      797 &    2080 \\
   HIP 55266 &            A2V &     11:19:7.90 &    +38:11:8.03 &  6300.00 &       TS23 &      900 &     200 \\
   HIP 55434 &         B9.5Vs &  11:21:08.1934 &  +06:01:45.571 &  6332.77 &     CHIRON &      199 &     410 \\
   HIP 56034 &            A2V &     11:29:4.12 &   +39:20:13.11 &  6676.91 &       TS23 &      502 &    1460 \\
   HIP 56633 &          B9.5V &    11:36:40.91 &    -09:48:8.09 &  6669.91 &       TS23 &      447 &    1990 \\
   HIP 56633 &          B9.5V &    11:36:40.91 &    -09:48:8.09 &  6335.75 &     CHIRON &      358 &     470 \\
   HIP 57328 &            A4V &    11:45:17.04 &   +08:15:29.21 &  6338.68 &     CHIRON &      419 &     490 \\
   HIP 57328 &            A4V &    11:45:17.04 &   +08:15:29.21 &  6370.62 &     CHIRON &      419 &     450 \\
   HIP 58590 &            A5V &    12:00:52.39 &   +06:36:51.56 &  6338.72 &     CHIRON &      352 &     520 \\
   HIP 59394 &            A1V &     12:11:3.84 &    -23:36:8.72 &  6754.57 &     CHIRON &      815 &     500 \\
   HIP 59394 &            A1V &     12:11:3.84 &    -23:36:8.72 &  6690.78 &     CHIRON &      940 &     370 \\
   HIP 59449 &            B3V &    12:11:39.12 &    -52:22:6.44 &  6711.88 &     CHIRON &      186 &     440 \\
   HIP 59449 &            B3V &    12:11:39.12 &    -52:22:6.44 &  6641.76 &     CHIRON &      305 &     150 \\
   HIP 59819 &            A3V &     12:16:0.19 &   +14:53:56.65 &  6669.96 &       TS23 &      465 &    1940 \\
   HIP 60009 &          B2.5V &    12:18:26.25 &   -64:00:11.05 &  6370.66 &     CHIRON &      200 &     520 \\
   HIP 60009 &          B2.5V &    12:18:26.25 &   -64:00:11.05 &  7009.78 &     CHIRON &      206 &     510 \\
   HIP 60030 &           A5Vn &    12:18:40.32 &   -00:47:13.87 &  7084.81 &     IGRINS &     2400 &     230 \\
   HIP 60595 &            A1V &    12:25:11.76 &   -11:36:38.12 &  6676.94 &       TS23 &      746 &    1540 \\
   HIP 60710 &           B3Vn &    12:26:31.76 &    -51:27:2.29 &  7062.77 &     CHIRON &     1515 &     470 \\
   HIP 60957 &            A3V &    12:29:43.24 &   +20:53:45.99 &  6678.92 &       TS23 &      904 &    1500 \\
   HIP 61558 &            A3V &    12:36:47.35 &   -05:49:54.84 &  7139.67 &     IGRINS &     1440 &     390 \\
   HIP 61558 &            A3V &    12:36:47.35 &   -05:49:54.84 &  7084.84 &     IGRINS &     1200 &     130 \\
   HIP 61622 &         A1IVnn &    12:37:42.16 &   -48:32:28.69 &  6378.69 &     CHIRON &      167 &     620 \\
   HIP 62541 &            A1V &    12:48:54.21 &   +14:07:21.31 &  7124.80 &     IGRINS &      480 &     270 \\
   HIP 62541 &            A1V &    12:48:54.21 &   +14:07:21.31 &  7084.86 &     IGRINS &     1500 &     110 \\
   HIP 62576 &            A2V &    12:49:17.45 &    +27:33:8.57 &  7122.83 &     IGRINS &      546 &     290 \\
   HIP 63724 &            A0V &    13:03:33.31 &   -49:31:38.15 &  6338.76 &     CHIRON &      412 &     560 \\
   HIP 63724 &            A0V &    13:03:33.31 &   -49:31:38.15 &  6371.72 &     CHIRON &      412 &     630 \\
   HIP 63945 &            B5V &    13:06:16.70 &   -48:27:47.85 &  6371.68 &     CHIRON &      362 &     560 \\
   HIP 65198 &            A2V &    13:21:41.64 &   +02:05:14.07 &  7044.85 &     CHIRON &     3352 &     430 \\
   HIP 65477 &      A5V+M3-4V &    13:25:13.54 &   +54:59:16.65 &  6670.01 &       TS23 &      207 &    2520 \\
   HIP 65728 &           A1Vn &    13:28:27.09 &   +59:56:44.83 &  6677.98 &       TS23 &     1200 &    1710 \\
   HIP 66249 &          A2Van &    13:34:41.74 &   -00:35:45.38 &  6378.71 &     CHIRON &      110 &     520 \\
   HIP 66798 &            A2V &    13:41:29.89 &   +64:49:20.68 &  6377.82 &        HRS &      362 &     610 \\
   HIP 66821 &  B8.5Vn+A2.5Va &    13:41:44.77 &   -54:33:33.93 &  6718.75 &     CHIRON &      610 &     540 \\
   HIP 67143 &            A0V &    13:45:36.89 &   -26:06:57.63 &  7139.77 &     IGRINS &      480 &     270 \\
   HIP 67194 &            A5V &    13:46:13.55 &   +41:05:19.48 &  6389.70 &        HRS &      368 &     740 \\
   HIP 67782 &           A8IV &    13:53:10.28 &   +28:38:53.28 &  6394.92 &        HRS &      359 &     680 \\
   HIP 68092 &            A8V &    13:56:27.88 &    +01:03:2.09 &  7139.80 &     IGRINS &      840 &     640 \\
   HIP 68520 &            A3V &    14:01:38.79 &   +01:32:40.31 &  6403.59 &     CHIRON &      239 &     470 \\
   HIP 70327 &            A0V &    14:23:22.70 &   +08:26:47.84 &  7123.90 &     IGRINS &      420 &     300 \\
   HIP 70327 &            A0V &    14:23:22.70 &   +08:26:47.84 &  6681.98 &       TS23 &     1152 &     230 \\
   HIP 70327 &            A0V &    14:23:22.70 &   +08:26:47.84 &  6719.80 &     CHIRON &      368 &     460 \\
   HIP 70384 &            A3V &     14:24:0.88 &   +08:14:38.30 &  6403.73 &        HRS &      420 &     560 \\
   HIP 70400 &            A3V &    14:24:11.34 &   +05:49:12.47 &  6669.00 &       TS23 &      602 &    2000 \\
   HIP 70915 &           B8Vn &     14:30:8.63 &   -45:19:16.88 &  7136.63 &     CHIRON &     3281 &     480 \\
   HIP 70915 &           B8Vn &     14:30:8.63 &   -45:19:16.88 &  7090.71 &     CHIRON &     2985 &     460 \\
     HR 5476 &            A6V &    14:40:43.94 &    +16:25:3.90 &  6408.71 &        HRS &      305 &     660 \\
   HIP 71865 &            B3V &    14:41:57.59 &   -37:47:36.59 &  6383.71 &     CHIRON &      190 &     460 \\
   HIP 71865 &            B3V &    14:41:57.59 &   -37:47:36.59 &  7060.80 &     CHIRON &     1205 &     500 \\
   HIP 71974 &          B9.5V &    14:43:13.55 &   -24:59:51.91 &  7078.80 &     CHIRON &     3786 &     470 \\
   HIP 72104 &         A0IVnn &    14:44:59.20 &   -35:11:30.57 &  6720.86 &     CHIRON &      492 &     490 \\
   HIP 72154 &          B9.5V &    14:45:30.20 &    +00:43:2.19 &  6403.75 &        HRS &      300 &     470 \\
   HIP 72250 &            A1V &    14:46:28.99 &   -47:26:28.02 &  7070.72 &     CHIRON &     4025 &     490 \\
   HIP 72378 &            B9V &    14:47:57.56 &   -26:38:46.16 &  7139.82 &     IGRINS &      720 &     450 \\
   HIP 72552 &            A4V &    14:49:58.40 &   +28:36:57.00 &  7124.81 &     IGRINS &      600 &     200 \\
   HIP 73049 &            A0V &    14:55:44.71 &   -33:51:20.82 &  6715.73 &     CHIRON &      749 &     530 \\
     HR 5605 &            B5V &     15:05:7.18 &    -47:03:4.00 &  6383.74 &     CHIRON &      330 &     530 \\
   HIP 74117 &            B3V &    15:08:50.62 &   -45:16:47.49 &  6383.77 &     CHIRON &      204 &     370 \\
   HIP 74689 &            A4V &    15:15:49.08 &   +00:22:19.70 &  6872.52 &     CHIRON &      693 &     550 \\
   HIP 75178 &           B9Vn &    15:21:48.58 &    +32:56:1.30 &  6678.99 &       TS23 &      815 &    1620 \\
   HIP 75304 &            B4V &     15:23:9.35 &   -36:51:30.55 &  6427.78 &     CHIRON &      309 &     340 \\
   HIP 76267 &           A1IV &    15:34:41.27 &   +26:42:52.89 &  6380.88 &     CHIRON &       36 &     290 \\
   HIP 76600 &          B2.5V &    15:38:39.37 &   -29:46:39.89 &  6380.91 &     CHIRON &      137 &     500 \\
   HIP 76852 &            A1V &    15:41:33.05 &   +19:40:13.44 &  6426.65 &     CHIRON &      306 &     370 \\
   HIP 77233 &            A3V &    15:46:11.25 &   +15:25:18.59 &  6426.69 &     CHIRON &      140 &     320 \\
   HIP 77336 &            A3V &    15:47:17.32 &   +14:06:55.26 &  6396.79 &        HRS &      264 &     610 \\
   HIP 77336 &            A3V &    15:47:17.32 &   +14:06:55.26 &  7122.91 &     IGRINS &      480 &     230 \\
   HIP 77516 &            A0V &    15:49:37.21 &   -03:25:48.73 &  6380.89 &     CHIRON &      126 &     450 \\
   HIP 77635 &         B1.5Vn &    15:50:58.74 &    -25:45:4.66 &  6725.72 &     CHIRON &      288 &     420 \\
   HIP 77858 &            B5V &    15:53:53.92 &   -24:31:59.37 &  6733.75 &     CHIRON &      628 &     490 \\
   HIP 78105 &            A3V &    15:56:53.50 &   -33:57:58.01 &  6870.54 &     CHIRON &      655 &     590 \\
   HIP 78106 &            B9V &    15:56:54.12 &   -33:57:51.34 &  6736.70 &     CHIRON &      584 &     500 \\
   HIP 78265 &      B1V+B2:V: &  15:58:51.1132 &  -26:06:50.788 &  6766.77 &     CHIRON &       22 &     250 \\
   HIP 78554 &            A3V &    16:02:17.69 &   +22:48:16.03 &  6427.74 &     CHIRON &      408 &     270 \\
   HIP 78820 &            B1V &    16:05:26.23 &   -19:48:19.63 &  6380.93 &     CHIRON &       53 &     490 \\
   HIP 78820 &            B1V &    16:05:26.23 &   -19:48:19.63 &  7139.83 &     IGRINS &      120 &     840 \\
   HIP 78820 &            B1V &    16:05:26.23 &   -19:48:19.63 &  7060.85 &     CHIRON &      263 &     360 \\
   HIP 78820 &            B1V &    16:05:26.23 &   -19:48:19.63 &  7156.63 &     CHIRON &      164 &     390 \\
   HIP 78821 &            B2V &    16:05:26.57 &    -19:48:6.85 &  7139.84 &     IGRINS &      210 &     100 \\
     HR 6025 &           A0Vn &  16:06:19.6762 &  +67:48:36.480 &  6847.83 &     IGRINS &      600 &     610 \\
   HIP 78918 &         B2.5Vn &    16:06:35.55 &    -36:48:8.26 &  6718.86 &     CHIRON &      300 &     610 \\
   HIP 78933 &            B1V &  16:06:48.4269 &  -20:40:09.090 &  6737.76 &     CHIRON &       77 &     250 \\
   HIP 79005 &            B9V &    16:07:36.42 &   -12:44:43.46 &  7090.77 &     CHIRON &     4646 &     430 \\
   HIP 79007 &            A7V &    16:07:37.54 &   +09:53:30.27 &  6874.48 &     CHIRON &      659 &     550 \\
   HIP 79199 &            B8V &    16:09:52.59 &   -33:32:44.90 &  6734.71 &     CHIRON &      451 &     470 \\
   HIP 79404 &            B2V &    16:12:18.20 &   -27:55:34.95 &  6415.77 &     CHIRON &      324 &     470 \\
   HIP 79404 &            B2V &    16:12:18.20 &   -27:55:34.95 &  7076.81 &     CHIRON &     1307 &     430 \\
   HIP 79404 &            B2V &    16:12:18.20 &   -27:55:34.95 &  7090.88 &     CHIRON &     1135 &     450 \\
   HIP 79387 &            A4V &     16:12:7.32 &   -08:32:51.28 &  6746.75 &     CHIRON &      573 &     500 \\
   HIP 79653 &            B8V &    16:15:15.32 &   -47:22:19.27 &  6740.79 &     CHIRON &      469 &     490 \\
   HIP 80460 &            A5V &    16:25:24.17 &   +37:23:38.68 &  7122.93 &     IGRINS &      720 &     400 \\
   HIP 80815 &            B3V &    16:30:12.48 &   -25:06:54.80 &  6378.86 &     CHIRON &      393 &     530 \\
   HIP 80883 &           A1IV &    16:30:54.82 &    +01:59:2.12 &  6378.84 &     CHIRON &      174 &     550 \\
   HIP 80991 &            A2V &    16:32:25.68 &   +60:49:23.96 &  6389.86 &        HRS &      404 &     720 \\
   HIP 81126 &            B9V &     16:34:6.18 &   +42:26:13.34 &  7122.95 &     IGRINS &      720 &     620 \\
   HIP 81641 &            A1V &    16:40:38.69 &   +04:13:11.23 &  6404.83 &        HRS &      320 &     540 \\
   HIP 82350 &            A1V &    16:49:34.66 &   +13:15:40.10 &  6391.84 &        HRS &      404 &     660 \\
   HIP 82514 &     B1.5Vp+... &  16:51:52.2311 &  -38:02:50.569 &  6726.81 &     CHIRON &       34 &     250 \\
   HIP 82673 &            B8V &     16:54:0.47 &   +10:09:55.30 &  6871.58 &     CHIRON &      250 &     310 \\
   HIP 82673 &            B8V &     16:54:0.47 &   +10:09:55.30 &  6410.86 &     CHIRON &      272 &     180 \\
   HIP 83635 &            B1V &    17:05:32.26 &   -00:53:31.45 &  6407.86 &        HRS &      316 &     480 \\
   HIP 84606 &            A2V &    17:17:40.25 &   +37:17:29.40 &  6945.54 &     IGRINS &      224 &     460 \\
   HIP 85290 &           A1Vn &    17:25:41.35 &   +60:02:54.23 &  6946.56 &     IGRINS &      224 &     240 \\
   HIP 85379 &            A4V &    17:26:44.24 &   +48:15:36.23 &  6398.85 &        HRS &      330 &     740 \\
   HIP 85385 &            B5V &    17:26:49.13 &   +20:04:51.52 &  6848.83 &     IGRINS &      480 &   40390 \\
   HIP 85537 &           A8Vp &    17:28:49.65 &   +00:19:50.25 &  7096.88 &     CHIRON &     4227 &     570 \\
   HIP 85537 &           A8Vp &    17:28:49.65 &   +00:19:50.25 &  6792.73 &     CHIRON &      900 &     600 \\
   HIP 85537 &           A8Vp &    17:28:49.65 &   +00:19:50.25 &  6848.73 &     IGRINS &      240 &   68720 \\
   HIP 85727 &           B8Vn &     17:31:5.91 &    -60:41:1.85 &  6771.85 &     CHIRON &      175 &     570 \\
   HIP 85922 &     A4III-IVnn &    17:33:29.85 &   -05:44:41.29 &  6847.82 &     IGRINS &      480 &     760 \\
   HIP 85922 &     A4III-IVnn &    17:33:29.85 &   -05:44:41.29 &  7139.95 &     IGRINS &      240 &     290 \\
   HIP 85922 &     A4III-IVnn &    17:33:29.85 &   -05:44:41.29 &  6886.56 &     CHIRON &      791 &     590 \\
   HIP 85922 &     A4III-IVnn &    17:33:29.85 &   -05:44:41.29 &  7103.85 &     CHIRON &     2543 &     370 \\
   HIP 85922 &     A4III-IVnn &    17:33:29.85 &   -05:44:41.29 &  7104.82 &     CHIRON &     7386 &     360 \\
   HIP 85998 &            A2V &    17:34:36.69 &   +09:35:12.12 &  7122.96 &     IGRINS &      480 &     120 \\
   HIP 85998 &            A2V &    17:34:36.69 &   +09:35:12.12 &  7230.64 &     IGRINS &      720 &     700 \\
   HIP 85998 &            A2V &    17:34:36.69 &   +09:35:12.12 &  6407.84 &        HRS &      324 &     490 \\
   HIP 85998 &            A2V &    17:34:36.69 &   +09:35:12.12 &  7079.89 &     CHIRON &     1600 &     220 \\
   HIP 86019 &           B8Vn &    17:34:46.35 &   -11:14:31.19 &  6747.85 &     CHIRON &      228 &     510 \\
   HIP 86782 &            A2V &    17:43:59.18 &    +53:48:6.17 &  6404.85 &        HRS &      310 &     500 \\
   HIP 87108 &     A1VnkA0mA0 &    17:47:53.56 &   +02:42:26.20 &  6847.87 &     IGRINS &      120 &     630 \\
   HIP 87108 &     A1VnkA0mA0 &    17:47:53.56 &   +02:42:26.20 &  6445.79 &     CHIRON &      152 &     300 \\
   HIP 88116 &             A0 &    17:59:47.56 &   -23:48:58.09 &  6488.71 &     CHIRON &      373 &     590 \\
   HIP 88116 &             A0 &    17:59:47.56 &   -23:48:58.09 &  6876.54 &     CHIRON &      320 &     380 \\
   HIP 88290 &           A2Vn &    18:01:45.20 &   +01:18:18.28 &  6873.59 &     CHIRON &      365 &     540 \\
   HIP 88818 &            A3V &    18:07:49.45 &    +26:06:4.13 &  7122.98 &     IGRINS &      960 &     530 \\
   HIP 88818 &            A3V &    18:07:49.45 &    +26:06:4.13 &  7230.66 &     IGRINS &      600 &     830 \\
   HIP 88818 &            A3V &    18:07:49.45 &    +26:06:4.13 &  6397.85 &        HRS &      355 &     510 \\
   HIP 88817 &            A3V &    18:07:49.50 &   +26:05:50.40 &  7123.00 &     IGRINS &      960 &     430 \\
   HIP 88817 &            A3V &    18:07:49.50 &   +26:05:50.40 &  6405.84 &        HRS &      400 &     720 \\
   HIP 89156 &            A3V &    18:11:45.12 &   +33:26:49.41 &  6405.82 &        HRS &      470 &     610 \\
   HIP 89935 &            A7V &     18:21:1.02 &   +28:52:11.83 &  6848.85 &     IGRINS &      240 &   77520 \\
   HIP 89935 &            A7V &     18:21:1.02 &   +28:52:11.83 &  6945.56 &     IGRINS &      224 &     620 \\
   HIP 90052 &            A2V &    18:22:35.32 &   +12:01:46.85 &  6405.88 &        HRS &      500 &     760 \\
   HIP 90762 &            A2V &     18:31:4.45 &   +16:55:42.80 &  6848.85 &     IGRINS &      480 &   47190 \\
   HIP 90762 &            A2V &     18:31:4.45 &   +16:55:42.80 &  6945.57 &     IGRINS &      480 &     570 \\
   HIP 90887 &           A3Vn &    18:32:21.33 &   -39:42:14.40 &  6748.80 &     CHIRON &      710 &     560 \\
   HIP 91118 &           A0Vn &    18:35:12.60 &   +18:12:12.28 &  6945.58 &     IGRINS &      360 &     390 \\
   HIP 91875 &           A2Vn &    18:43:46.94 &   -38:19:24.39 &  6745.81 &     CHIRON &      680 &     580 \\
   HIP 92027 &        A1V+... &    18:45:28.36 &    +05:30:0.44 &  6405.91 &        HRS &      360 &     570 \\
   HIP 92312 &            A1V &    18:48:53.39 &   +19:19:43.40 &  6408.88 &        HRS &      390 &     650 \\
   HIP 92728 &          B2.5V &    18:53:43.56 &   +36:58:18.19 &  6405.86 &        HRS &      280 &     560 \\
   HIP 92855 &            B2V &    18:55:15.93 &   -26:17:48.21 &  6880.57 &     CHIRON &       30 &     550 \\
   HIP 92855 &            B2V &    18:55:15.93 &   -26:17:48.21 &  6415.80 &     CHIRON &       32 &     400 \\
   HIP 92946 &            A5V &    18:56:13.18 &   +04:12:12.91 &  6475.79 &     CHIRON &      339 &     500 \\
   HIP 93225 &            B4V &    18:59:23.80 &   -12:50:25.86 &  6946.54 &     IGRINS &      224 &     640 \\
   HIP 93225 &            B4V &    18:59:23.80 &   -12:50:25.86 &  6516.69 &     CHIRON &     1200 &     540 \\
   HIP 93225 &            B4V &    18:59:23.80 &   -12:50:25.86 &  6962.56 &       TS23 &      562 &    1430 \\
   HIP 93393 &            B5V &    19:01:17.36 &   +26:17:29.08 &  6404.88 &        HRS &      320 &     540 \\
   HIP 93580 &            A4V &    19:03:32.25 &    +01:49:7.57 &  7116.84 &     CHIRON &     5594 &     520 \\
   HIP 93580 &            A4V &    19:03:32.25 &    +01:49:7.57 &  6848.84 &     IGRINS &      480 &   55820 \\
   HIP 93713 &           A0Vn &    19:04:55.17 &   +53:23:47.96 &  6848.87 &     IGRINS &      600 &   42950 \\
   HIP 93747 &       A0IV-Vnn &    19:05:24.61 &   +13:51:48.52 &  6587.54 &       TS23 &       85 &    1880 \\
   HIP 93805 &           B9Vn &    19:06:14.94 &   -04:52:57.20 &  6852.82 &     IGRINS &     2640 &  188380 \\
   HIP 93805 &           B9Vn &    19:06:14.94 &   -04:52:57.20 &  7139.96 &     IGRINS &      120 &     280 \\
   HIP 93805 &           B9Vn &    19:06:14.94 &   -04:52:57.20 &  6775.78 &     CHIRON &      150 &     520 \\
   HIP 94620 &            A4V &    19:15:17.36 &   +21:13:55.62 &  6848.88 &     IGRINS &      480 &   69950 \\
   HIP 94720 &          B9.5V &    19:16:26.79 &   +14:32:40.62 &  6517.78 &        HRS &      400 &     880 \\
   HIP 95241 &            B9V &    19:22:38.30 &   -44:27:32.25 &  6869.63 &     CHIRON &      325 &     120 \\
   HIP 95241 &            B9V &    19:22:38.30 &   -44:27:32.25 &  6508.80 &     CHIRON &      294 &     600 \\
   HIP 95241 &            B9V &    19:22:38.30 &   -44:27:32.25 &  6459.89 &     CHIRON &      183 &     360 \\
   HIP 95560 &            A0V &    19:26:13.25 &   +20:05:51.84 &  6848.89 &     IGRINS &      480 &   57010 \\
   HIP 95619 &          B8.5V &    19:26:56.48 &   -29:44:35.62 &  7139.97 &     IGRINS &      480 &     310 \\
   HIP 95619 &          B8.5V &    19:26:56.48 &   -29:44:35.62 &  7118.79 &     CHIRON &     3451 &     320 \\
   HIP 95619 &          B8.5V &    19:26:56.48 &   -29:44:35.62 &  6523.61 &     CHIRON &      768 &     670 \\
   HIP 95853 &            A5V &    19:29:42.36 &   +51:43:47.21 &  6585.54 &       TS23 &      129 &    2010 \\
   HIP 96288 &            A2V &    19:34:41.26 &   +42:24:45.04 &  6585.56 &       TS23 &      489 &    1860 \\
   HIP 96840 &            B5V &     19:41:5.53 &   +13:48:56.45 &  6408.92 &        HRS &      552 &     940 \\
   HIP 97376 &           B8Vn &    19:47:27.78 &   +38:24:27.41 &  6848.90 &     IGRINS &     1680 &   35630 \\
   HIP 97496 &            A3V &    19:48:58.66 &   +19:08:31.35 &  6584.54 &       TS23 &      342 &    1820 \\
   HIP 97870 &            B5V &    19:53:17.38 &   +57:31:24.53 &  6517.81 &        HRS &      185 &     830 \\
   HIP 97966 &           B7Vn &    19:54:37.65 &   -08:13:38.24 &  6925.51 &     CHIRON &      655 &     380 \\
   HIP 97966 &           B7Vn &    19:54:37.65 &   -08:13:38.24 &  6881.70 &     CHIRON &     1158 &     660 \\
   HIP 98055 &           A4Vn &    19:55:37.79 &   +52:26:20.21 &  6586.54 &       TS23 &      320 &    1820 \\
   HIP 98194 &            B5V &    19:57:13.87 &    +40:22:4.17 &  6583.54 &       TS23 &      495 &    1750 \\
   HIP 98325 &           B9Vn &    19:58:37.98 &    +30:59:1.19 &  6587.56 &       TS23 &      543 &    1750 \\
   HIP 99080 &            B3V &    20:06:53.41 &   +23:36:51.93 &  6583.63 &       TS23 &      358 &    1740 \\
   HIP 99742 &           A1Va &    20:14:16.62 &   +15:11:51.39 &  6945.59 &     IGRINS &      224 &     540 \\
  HIP 100069 &  O9IV(n)+B1.5V &     20:18:6.99 &   +40:43:55.50 &  6409.91 &        HRS &      451 &     560 \\
  HIP 100221 &            B9V &    20:19:36.72 &   +62:15:26.90 &  7230.72 &     IGRINS &     1100 &     930 \\
  HIP 100221 &            B9V &    20:19:36.72 &   +62:15:26.90 &  6523.79 &        HRS &      874 &     830 \\
  HIP 100881 &            B4V &    20:27:19.21 &   -18:12:42.20 &  6511.69 &     CHIRON &     1011 &     570 \\
  HIP 100907 &            A3V &    20:27:34.26 &   +38:26:25.19 &  6946.57 &     IGRINS &      224 &     730 \\
  HIP 100907 &            A3V &    20:27:34.26 &   +38:26:25.19 &  7230.67 &     IGRINS &      600 &    1030 \\
  HIP 101123 &            A1V &    20:29:53.91 &   -18:34:59.48 &  6945.70 &     IGRINS &      224 &     810 \\
  HIP 101589 &            A3V &    20:35:18.54 &   +14:40:27.17 &  6448.83 &     CHIRON &      352 &     420 \\
  HIP 101716 &            B8V &     20:37:4.67 &   +26:27:43.01 &  6582.60 &       TS23 &      549 &    1260 \\
  HIP 101867 &            A0V &    20:38:31.34 &    +21:12:4.25 &  6489.78 &     CHIRON &      408 &     440 \\
  HIP 101909 &            B3V &     20:39:4.97 &   +15:50:17.52 &  6945.60 &     IGRINS &      360 &     280 \\
  HIP 101909 &            B3V &     20:39:4.97 &   +15:50:17.52 &  7230.69 &     IGRINS &      720 &     430 \\
  HIP 102487 &            A1V &     20:46:9.99 &   -21:30:50.52 &  6847.80 &     IGRINS &      480 &     530 \\
  HIP 103298 &            A5V &    20:55:38.57 &    +12:34:6.81 &  6946.58 &     IGRINS &      224 &     630 \\
  HIP 103298 &            A5V &    20:55:38.57 &    +12:34:6.81 &  7230.70 &     IGRINS &      600 &     870 \\
  HIP 103298 &            A5V &    20:55:38.57 &    +12:34:6.81 &  7155.93 &     CHIRON &     1141 &     290 \\
  HIP 104019 &            A5V &    21:04:24.30 &   -19:51:17.97 &  6474.90 &     CHIRON &      423 &     550 \\
  HIP 104105 &           B8Vn &    21:05:29.27 &   +78:07:35.02 &  6945.69 &     IGRINS &      280 &     310 \\
  HIP 104139 &            A1V &    21:05:56.83 &   -17:13:58.30 &  6448.90 &     CHIRON &      204 &     490 \\
  HIP 104365 &            A0V &    21:08:33.63 &   -21:11:37.22 &  6847.81 &     IGRINS &      480 &     710 \\
  HIP 104365 &            A0V &    21:08:33.63 &   -21:11:37.22 &  7237.82 &     IGRINS &      720 &    2150 \\
  HIP 105140 &            A1V &    21:17:56.28 &   -32:10:21.15 &  6485.90 &     CHIRON &      372 &     420 \\
  HIP 105282 &            B6V &    21:19:28.75 &   +49:30:37.06 &  6522.65 &        HRS &     1006 &     850 \\
  HIP 105891 &          B7III &    21:26:44.97 &   +52:53:54.73 &  6946.59 &     IGRINS &      224 &     210 \\
  HIP 105942 &            B3V &    21:27:21.37 &    +37:07:0.47 &  6523.87 &        HRS &      480 &     760 \\
  HIP 105966 &         A1VmA3 &    21:27:40.06 &   +27:36:30.94 &  6585.64 &       TS23 &      530 &    1800 \\
  HIP 105972 &            B7V &    21:27:46.14 &   +66:48:32.74 &  6507.82 &        HRS &      267 &     690 \\
  HIP 106711 &           A3Vn &    21:36:56.98 &   +40:24:48.67 &  6584.60 &       TS23 &      689 &     700 \\
  HIP 106711 &           A3Vn &    21:36:56.98 &   +40:24:48.67 &  6618.53 &       TS23 &      557 &    2010 \\
  HIP 106786 &            A7V &    21:37:45.11 &   -07:51:15.13 &  6945.64 &     IGRINS &      224 &     830 \\
  HIP 106786 &            A7V &    21:37:45.11 &   -07:51:15.13 &  6962.59 &       TS23 &      284 &    1620 \\
  HIP 106786 &            A7V &    21:37:45.11 &   -07:51:15.13 &  6794.81 &     CHIRON &      232 &     470 \\
  HIP 107517 &            A1V &    21:46:32.10 &   -11:21:57.44 &  6873.74 &     CHIRON &     1025 &     490 \\
  HIP 107608 &            A2V &    21:47:44.15 &   -30:53:53.90 &  6788.84 &     CHIRON &      620 &     470 \\
  HIP 108294 &           A2Vn &    21:56:22.77 &   -37:15:13.16 &  6790.81 &     CHIRON &      470 &     510 \\
  HIP 108339 &          A2Vnn &    21:56:56.37 &   +12:04:35.37 &  6945.65 &     IGRINS &      224 &     320 \\
  HIP 109056 &           B9Vn &    22:05:34.67 &   +28:57:50.32 &  6945.66 &     IGRINS &      240 &     280 \\
  HIP 109056 &           B9Vn &    22:05:34.67 &   +28:57:50.32 &  6948.56 &     IGRINS &     1156 &    1510 \\
  HIP 109056 &           B9Vn &    22:05:34.67 &   +28:57:50.32 &  6946.65 &     IGRINS &      784 &    1070 \\
  HIP 109056 &           B9Vn &    22:05:34.67 &   +28:57:50.32 &  6947.57 &     IGRINS &     1746 &     850 \\
  HIP 109139 &            B8V &    22:06:26.23 &   -13:52:10.86 &  6524.67 &     CHIRON &      207 &     590 \\
  HIP 109139 &            B8V &    22:06:26.23 &   -13:52:10.86 &  6447.91 &     CHIRON &      248 &     470 \\
  HIP 109521 &            A5V &     22:11:9.89 &   +50:49:24.26 &  6586.58 &       TS23 &      511 &    1860 \\
  HIP 109521 &            A5V &     22:11:9.89 &   +50:49:24.26 &  6962.60 &       TS23 &      587 &    1500 \\
  HIP 109521 &            A5V &     22:11:9.89 &   +50:49:24.26 &  6945.68 &     IGRINS &      224 &     590 \\
  HIP 109831 &          A2Vnn &    22:14:44.37 &   +42:57:14.07 &  6945.67 &     IGRINS &      224 &     380 \\
  HIP 109831 &          A2Vnn &    22:14:44.37 &   +42:57:14.07 &  7237.77 &     IGRINS &     1440 &     860 \\
  HIP 109831 &          A2Vnn &    22:14:44.37 &   +42:57:14.07 &  7288.73 &     IGRINS &      900 &    2560 \\
  HIP 110838 &       B9Vn+G0V &    22:27:19.97 &   -64:57:58.88 &  6543.82 &     CHIRON &      506 &     550 \\
  HIP 110838 &       B9Vn+G0V &    22:27:19.97 &   -64:57:58.88 &  6880.76 &     CHIRON &      354 &     780 \\
  HIP 110935 &            A4V &    22:28:37.67 &   -67:29:20.62 &  6896.67 &     CHIRON &      696 &     630 \\
  HIP 111056 &            A3V &    22:29:52.98 &   +78:49:27.43 &  7288.80 &     IGRINS &      180 &    1010 \\
  HIP 111056 &            A3V &    22:29:52.98 &   +78:49:27.43 &  6945.76 &     IGRINS &      224 &     380 \\
  HIP 111068 &          B9.5V &     22:30:1.81 &   +32:34:21.50 &  6512.74 &        HRS &      362 &     500 \\
  HIP 111169 &            A1V &    22:31:17.50 &   +50:16:56.97 &  6585.62 &       TS23 &      121 &    1900 \\
  HIP 111841 &            O9V &    22:39:15.68 &    +39:03:0.97 &  6583.68 &       TS23 &      267 &    1670 \\
  HIP 112029 &            B8V &    22:41:27.73 &   +10:49:52.64 &  6487.85 &     CHIRON &      109 &     460 \\
  HIP 112029 &            B8V &    22:41:27.73 &   +10:49:52.64 &  6892.74 &     CHIRON &       95 &     250 \\
  HIP 113788 &            A1V &    23:02:36.38 &   +42:45:28.06 &  6586.63 &       TS23 &      367 &    1830 \\
  HIP 114520 &           A5Vn &    23:11:44.19 &   +08:43:12.40 &  6587.64 &       TS23 &      541 &    1880 \\
  HIP 114822 &            A2V &    23:15:34.26 &   -03:29:46.96 &  6886.68 &     CHIRON &      715 &     550 \\
  HIP 114822 &            A2V &    23:15:34.26 &   -03:29:46.96 &  6884.68 &     CHIRON &      530 &     530 \\
  HIP 115115 &            A0V &    23:18:57.68 &   -09:36:38.70 &  7163.90 &     CHIRON &      600 &     190 \\
  HIP 115115 &            A0V &    23:18:57.68 &   -09:36:38.70 &  7230.95 &     IGRINS &      500 &    1040 \\
  HIP 115115 &            A0V &    23:18:57.68 &   -09:36:38.70 &  6797.87 &     CHIRON &      610 &     330 \\
  HIP 116247 &            A0V &    23:33:16.62 &   -20:54:52.21 &  6463.89 &     CHIRON &      368 &     560 \\
  HIP 116247 &            A0V &    23:33:16.62 &   -20:54:52.21 &  7237.94 &     IGRINS &      240 &     980 \\
  HIP 116582 &            B8V &    23:37:32.04 &   +44:25:44.37 &  6510.77 &        HRS &      534 &     670 \\
  HIP 116611 &           A0Vn &    23:37:56.80 &    +18:24:2.40 &  6946.61 &     IGRINS &      224 &     400 \\
  HIP 116631 &            B8V &     23:38:8.20 &    +43:16:5.06 &  6962.63 &       TS23 &      249 &    1980 \\
  HIP 116631 &            B8V &     23:38:8.20 &    +43:16:5.06 &  6946.78 &     IGRINS &      224 &     680 \\
  HIP 116631 &            B8V &     23:38:8.20 &    +43:16:5.06 &  6583.71 &       TS23 &      162 &    1740 \\
  HIP 116631 &            B8V &     23:38:8.20 &    +43:16:5.06 &  7288.80 &     IGRINS &      180 &    2150 \\
  HIP 116805 &            A0V &    23:40:24.51 &    +44:20:2.16 &  6528.84 &       TS23 &      158 &    1680 \\
  HIP 116971 &            B9V &    23:42:43.34 &   -14:32:41.65 &  6527.85 &       TS23 &      407 &    1650 \\
  HIP 116971 &            B9V &    23:42:43.34 &   -14:32:41.65 &  6487.88 &     CHIRON &      298 &     540 \\
  HIP 116971 &            B9V &    23:42:43.34 &   -14:32:41.65 &  6555.56 &     CHIRON &      497 &     430 \\
  HIP 116971 &            B9V &    23:42:43.34 &   -14:32:41.65 &  6869.76 &     CHIRON &      380 &     110 \\
  HIP 116971 &            B9V &    23:42:43.34 &   -14:32:41.65 &  6936.73 &     CHIRON &      344 &     600 \\
  HIP 117089 &            B9V &    23:44:12.08 &   -18:16:36.97 &  7288.81 &     IGRINS &      180 &    1130 \\
  HIP 117089 &            B9V &    23:44:12.08 &   -18:16:36.97 &  7237.95 &     IGRINS &      720 &    1610 \\
  HIP 117089 &            B9V &    23:44:12.08 &   -18:16:36.97 &  6513.86 &     CHIRON &      853 &     600 \\
  HIP 117371 &           A1Vn &    23:47:54.77 &   +67:48:24.51 &  6586.67 &       TS23 &      349 &    1760 \\
  HIP 117452 &          A0Vnp &    23:48:55.55 &   -28:07:48.97 &  6469.90 &     CHIRON &      327 &     540 \\
  HIP 118121 &            A1V &    23:57:35.08 &   -64:17:53.63 &  6795.86 &     CHIRON &      233 &     500 \\
  HIP 118243 &            B1V &     23:59:0.54 &   +55:45:17.74 &  6945.73 &     IGRINS &      224 &     370 \\
  HIP 118243 &            B1V &     23:59:0.54 &   +55:45:17.74 &  6583.74 &       TS23 &      351 &    1760 \\
\label{tab:observations}
\end{longtable*}

\begin{longtable*}{|l|lllll|}
\hline
            &        $T_\mathrm{eff}$ &      $\log{g}$ &             Mass &            Age & \\
       star &        (K)              &      (cgs)     &      ($M_{\odot}$) &          (Myr) & source \\
\hline
\endhead
\hline
\multicolumn{3}{r}{{Continued on next page}} \\
\endfoot

\hline
\endlastfoot
   HIP 2548 &   $11864 \pm 403$ &  $4.4 \pm 0.14$ &  $2.8^{+0.16}_{-0.15}$ &     $79^{+68}_{-53}$ &      DH2015 \\
   HIP 3478 &  $14250 \pm 1000$ &  $4.2 \pm 0.25$ &  $3.8^{+0.50}_{-0.45}$ &     $22^{+40}_{-15}$ &  This Study \\
   HIP 5310 &    $8611 \pm 293$ &  $4.4 \pm 0.14$ &  $1.8^{+0.10}_{-0.08}$ &  $306^{+236}_{-196}$ &      DH2015 \\
     HR 545 &  $11000 \pm 1000$ &  $4.3 \pm 0.25$ &  $2.5^{+0.39}_{-0.35}$ &    $37^{+105}_{-28}$ &  This Study \\
     HR 604 &  $11000 \pm 1000$ &  $4.5 \pm 0.25$ &  $2.4^{+0.37}_{-0.34}$ &     $28^{+87}_{-20}$ &  This Study \\
  HIP 10732 &    $9500 \pm 300$ &  $4.0 \pm 0.25$ &  $2.1^{+0.18}_{-0.16}$ &    $80^{+237}_{-70}$ &  This Study \\
  HIP 12332 &    $7750 \pm 300$ &  $3.5 \pm 0.25$ &  $1.9^{+0.37}_{-0.30}$ &  $687^{+218}_{-425}$ &  This Study \\
  HIP 12706 &    $8551 \pm 291$ &  $4.3 \pm 0.14$ &  $1.9^{+0.15}_{-0.12}$ &  $650^{+104}_{-180}$ &      DH2015 \\
  HIP 13165 &  $15000 \pm 1000$ &  $4.0 \pm 0.25$ &  $4.2^{+0.58}_{-0.50}$ &     $31^{+42}_{-22}$ &  This Study \\
  HIP 13327 &  $15000 \pm 1000$ &  $4.5 \pm 0.25$ &  $4.0^{+0.50}_{-0.45}$ &      $15^{+26}_{-9}$ &  This Study \\
  HIP 14576 &   $13070 \pm 444$ &  $4.0 \pm 0.14$ &  $3.6^{+0.29}_{-0.23}$ &    $139^{+17}_{-25}$ &      DH2015 \\
  HIP 14764 &  $11750 \pm 1000$ &  $4.2 \pm 0.25$ &  $2.8^{+0.42}_{-0.39}$ &     $35^{+91}_{-27}$ &  This Study \\
  HIP 16244 &  $16333 \pm 1000$ &  $4.3 \pm 0.25$ &  $4.7^{+0.57}_{-0.50}$ &      $15^{+22}_{-9}$ &  This Study \\
  HIP 16340 &  $12500 \pm 1000$ &  $4.0 \pm 0.25$ &  $3.1^{+0.51}_{-0.42}$ &     $49^{+92}_{-39}$ &  This Study \\
  HIP 16611 &   $12514 \pm 425$ &  $4.0 \pm 0.14$ &  $3.3^{+0.25}_{-0.20}$ &    $157^{+23}_{-46}$ &      DH2015 \\
  HIP 17563 &  $19000 \pm 1000$ &  $4.5 \pm 0.25$ &  $6.0^{+0.66}_{-0.59}$ &      $10^{+11}_{-4}$ &  This Study \\
  HIP 18396 &  $15000 \pm 1000$ &  $4.5 \pm 0.25$ &  $4.0^{+0.52}_{-0.47}$ &      $15^{+27}_{-9}$ &  This Study \\
  HIP 18724 &  $21000 \pm 1000$ &  $4.5 \pm 0.25$ &  $7.1^{+0.68}_{-0.64}$ &        $8^{+7}_{-3}$ &  This Study \\
  HIP 19949 &    $9825 \pm 334$ &  $3.8 \pm 0.14$ &  $2.2^{+0.11}_{-0.10}$ &  $198^{+136}_{-125}$ &      DH2015 \\
  HIP 20380 &    $8738 \pm 297$ &  $3.9 \pm 0.14$ &  $1.9^{+0.09}_{-0.08}$ &  $339^{+210}_{-207}$ &      DH2015 \\
  HIP 21589 &    $8591 \pm 292$ &  $3.9 \pm 0.14$ &  $1.8^{+0.09}_{-0.07}$ &  $302^{+225}_{-196}$ &      DH2015 \\
  HIP 22833 &    $8278 \pm 281$ &  $3.9 \pm 0.14$ &  $1.8^{+0.12}_{-0.09}$ &  $649^{+163}_{-295}$ &      DH2015 \\
  HIP 22958 &  $16000 \pm 1000$ &  $4.5 \pm 0.25$ &  $4.5^{+0.53}_{-0.50}$ &      $14^{+21}_{-8}$ &  This Study \\
  HIP 23362 &   $12450 \pm 423$ &  $4.3 \pm 0.14$ &  $3.2^{+0.20}_{-0.16}$ &    $147^{+29}_{-58}$ &      DH2015 \\
  HIP 23916 &  $16500 \pm 1000$ &  $4.2 \pm 0.25$ &  $4.8^{+0.56}_{-0.52}$ &     $16^{+26}_{-10}$ &  This Study \\
  HIP 24244 &   $13781 \pm 469$ &  $4.2 \pm 0.14$ &  $3.9^{+0.29}_{-0.23}$ &    $114^{+11}_{-23}$ &      DH2015 \\
  HIP 24902 &    $8275 \pm 281$ &  $4.0 \pm 0.14$ &  $1.7^{+0.10}_{-0.08}$ &  $466^{+252}_{-286}$ &      DH2015 \\
  HIP 25143 &    $8101 \pm 275$ &  $3.8 \pm 0.14$ &  $1.7^{+0.06}_{-0.06}$ &  $236^{+247}_{-160}$ &      DH2015 \\
  HIP 26126 &    $9542 \pm 324$ &  $3.9 \pm 0.14$ &  $2.1^{+0.09}_{-0.08}$ &  $175^{+148}_{-112}$ &      DH2015 \\
  HIP 32607 &    $7770 \pm 264$ &  $3.8 \pm 0.14$ &  $1.6^{+0.07}_{-0.06}$ &  $519^{+342}_{-335}$ &      DH2015 \\
  HIP 38538 &    $8551 \pm 291$ &  $4.0 \pm 0.14$ &  $1.9^{+0.14}_{-0.12}$ &  $637^{+109}_{-211}$ &      DH2015 \\
  HIP 38593 &  $21667 \pm 1000$ &  $4.5 \pm 0.25$ &  $7.6^{+0.74}_{-0.68}$ &        $8^{+6}_{-3}$ &  This Study \\
  HIP 38846 &  $22000 \pm 1000$ &  $4.5 \pm 0.25$ &  $7.8^{+0.74}_{-0.71}$ &        $8^{+6}_{-3}$ &  This Study \\
  HIP 39847 &   $10014 \pm 340$ &  $4.0 \pm 0.14$ &  $2.2^{+0.13}_{-0.12}$ &  $195^{+131}_{-121}$ &      DH2015 \\
  HIP 40881 &    $9500 \pm 300$ &  $4.0 \pm 0.25$ &  $2.1^{+0.17}_{-0.16}$ &    $71^{+239}_{-60}$ &  This Study \\
  HIP 42129 &  $18000 \pm 1000$ &  $4.5 \pm 0.25$ &  $5.4^{+0.63}_{-0.54}$ &      $11^{+14}_{-5}$ &  This Study \\
  HIP 51362 &   $10899 \pm 371$ &  $4.0 \pm 0.14$ &  $2.6^{+0.14}_{-0.12}$ &   $182^{+79}_{-102}$ &      DH2015 \\
  HIP 52678 &  $15000 \pm 1000$ &  $4.5 \pm 0.25$ &  $4.0^{+0.49}_{-0.50}$ &     $16^{+26}_{-10}$ &  This Study \\
  HIP 55266 &    $8720 \pm 296$ &  $4.5 \pm 0.14$ &  $1.9^{+0.09}_{-0.07}$ &  $346^{+209}_{-215}$ &      DH2015 \\
  HIP 63945 &  $18000 \pm 1000$ &  $4.5 \pm 0.25$ &  $5.4^{+0.60}_{-0.56}$ &      $11^{+14}_{-5}$ &  This Study \\
  HIP 72154 &  $10500 \pm 1000$ &  $4.5 \pm 0.25$ &  $2.3^{+0.36}_{-0.33}$ &    $32^{+101}_{-24}$ &  This Study \\
  HIP 76267 &   $10342 \pm 352$ &  $4.0 \pm 0.14$ &  $2.5^{+0.19}_{-0.16}$ &    $314^{+53}_{-99}$ &      DH2015 \\
  HIP 77336 &    $8917 \pm 303$ &  $4.0 \pm 0.14$ &  $2.9^{+0.23}_{-0.20}$ &    $404^{+73}_{-70}$ &      DH2015 \\
  HIP 77516 &    $9250 \pm 300$ &  $4.0 \pm 0.25$ &  $2.1^{+0.17}_{-0.16}$ &    $74^{+275}_{-64}$ &  This Study \\
  HIP 78820 &  $24062 \pm 1000$ &  $3.9 \pm 0.25$ &  $9.2^{+0.51}_{-0.64}$ &        $9^{+6}_{-4}$ &  This Study \\
  HIP 78821 &    $7250 \pm 300$ &  $4.0 \pm 0.25$ &  $9.1^{+0.65}_{-0.96}$ &        $8^{+6}_{-3}$ &  This Study \\
  HIP 79199 &  $12500 \pm 1000$ &  $4.5 \pm 0.25$ &  $3.0^{+0.42}_{-0.39}$ &     $23^{+55}_{-16}$ &  This Study \\
  HIP 79404 &  $21667 \pm 1000$ &  $4.5 \pm 0.25$ &  $7.6^{+0.75}_{-0.69}$ &        $8^{+6}_{-3}$ &  This Study \\
  HIP 80460 &    $7810 \pm 266$ &  $3.7 \pm 0.14$ &  $1.7^{+0.11}_{-0.08}$ &  $783^{+232}_{-394}$ &      DH2015 \\
  HIP 82673 &  $11750 \pm 1000$ &  $3.5 \pm 0.25$ &  $3.4^{+0.65}_{-0.57}$ &    $171^{+73}_{-64}$ &  This Study \\
  HIP 84606 &    $9702 \pm 330$ &  $4.0 \pm 0.14$ &  $2.1^{+0.10}_{-0.09}$ &   $154^{+137}_{-99}$ &      DH2015 \\
  HIP 85379 &    $8250 \pm 300$ &  $3.5 \pm 0.25$ &  $2.1^{+0.37}_{-0.34}$ &  $550^{+154}_{-260}$ &  This Study \\
  HIP 85998 &    $8812 \pm 300$ &  $4.0 \pm 0.25$ &  $1.9^{+0.16}_{-0.13}$ &    $95^{+332}_{-84}$ &  This Study \\
  HIP 88116 &    $9750 \pm 300$ &  $3.5 \pm 0.25$ &  $2.7^{+0.43}_{-0.39}$ &   $305^{+68}_{-150}$ &  This Study \\
  HIP 88818 &    $9162 \pm 312$ &  $4.3 \pm 0.14$ &  $2.7^{+0.24}_{-0.23}$ &    $441^{+86}_{-72}$ &      DH2015 \\
  HIP 88817 &    $9162 \pm 312$ &  $4.3 \pm 0.14$ &  $2.1^{+0.16}_{-0.12}$ &   $480^{+84}_{-168}$ &      DH2015 \\
  HIP 91118 &    $9500 \pm 300$ &  $4.0 \pm 0.25$ &  $2.1^{+0.19}_{-0.15}$ &    $70^{+244}_{-60}$ &  This Study \\
  HIP 93805 &   $11962 \pm 407$ &  $4.2 \pm 0.14$ &  $3.5^{+0.32}_{-0.26}$ &    $194^{+19}_{-21}$ &      DH2015 \\
 HIP 100221 &    $9750 \pm 300$ &  $4.5 \pm 0.25$ &  $2.2^{+0.15}_{-0.15}$ &    $34^{+110}_{-26}$ &  This Study \\
 HIP 100907 &    $9042 \pm 307$ &  $4.0 \pm 0.14$ &  $2.1^{+0.16}_{-0.13}$ &  $512^{+100}_{-168}$ &      DH2015 \\
 HIP 103298 &    $9093 \pm 309$ &  $4.1 \pm 0.14$ &  $2.0^{+0.13}_{-0.11}$ &  $399^{+146}_{-209}$ &      DH2015 \\
 HIP 109139 &   $12641 \pm 430$ &  $4.3 \pm 0.14$ &  $3.2^{+0.20}_{-0.16}$ &    $122^{+38}_{-61}$ &      DH2015 \\
 HIP 109521 &    $8420 \pm 286$ &  $4.2 \pm 0.14$ &  $2.0^{+0.19}_{-0.16}$ &  $728^{+109}_{-104}$ &      DH2015 \\
 HIP 115115 &   $10671 \pm 363$ &  $4.2 \pm 0.14$ &  $2.6^{+0.19}_{-0.16}$ &    $284^{+38}_{-81}$ &      DH2015 \\
\label{tab:primary}
\end{longtable*}

\newpage
\clearpage
\bibliography{references}

\end{document}

### 2016-01-19 MassRatioDistribution.py
Added histogram fitter classes to library.

@@ -1,13 +1,13 @@
 import logging
+from george import kernels, GP
 
 import numpy as np
 from scipy.optimize import minimize
 from scipy.stats import truncnorm, gaussian_kde
 from scipy.integrate import quad
+
 from HelperFunctions import BinomialErrors
-
 import Mamajek_Table
-
 import fitters
 
 
@@ -496,3 +496,165 @@ class Hist(object):
             import matplotlib.pyplot as plt 
             fig, ax = plt.subplots(1, 1)
         return ax.bar(left=self.bin_edges[:-1], height=vals, width=self.bin_widths, **hist_kwargs)
+
+
+class HistFitter(fitters.Bayesian_LS):
+    def __init__(self, qvals, bin_edges):
+        """
+        Histogram Inference a la Dan Foreman-Mackey
+
+        Parameters:
+        ===========
+        - qvals:      numpy array of shape (Nobs, Nsamples)
+                      The MCMC samples for the mass-ratio distribution of all companions
+
+        - bin_edges:  numpy array
+                      The edges of the histogram bins to use.
+
+        """
+        self.qvals = qvals
+        self.bin_edges = bin_edges
+        self.bin_centers = (self.bin_edges[:-1] + self.bin_edges[1:]) / 2
+        self.bin_widths = np.diff(self.bin_edges)
+        self.Nbins = self.bin_widths.size
+        self.Nobs = self.qvals.shape[0]
+
+        # Find which bin each q falls in
+        self.bin_idx = np.digitize(self.qvals, self.bin_edges) - 1
+
+        # Determine the censoring function for each bin (used in the integral)
+        self.censor_integrals = np.array([quad(func=self.censoring_fcn,
+                                               a=left, b=right)[0] for (left, right) in
+                                          zip(self.bin_edges[:-1], self.bin_edges[1:])])
+
+        # Set values needed for multinest fitting
+        self.n_params = self.Nbins
+        self.param_names = [r'$\theta_{}$'.format(i) for i in range(self.Nbins)]
+
+
+    def lnlike(self, pars):
+        # Pull theta out of pars
+        theta = pars[:self.Nbins]
+
+        # Normalize theta
+        # theta /= np.sum(theta * self.bin_widths)
+
+        # Generate the inner summation
+        gamma = np.ones_like(self.bin_idx) * np.nan
[…]

### 2016-01-21 paper/ms.tex
Added table with companion data
Updated paper

@@
 \begin{abstract}
-Young, intermediate-mass stars are experiencing renewed interest as targets for direct-imaging planet searches.
-However, these types of stars are part of multiple systems more often than not.
-Close stellar companions affect the formation and orbital evolution of any planets, and the properties of the companions can help constrain the binary formation mechanism.
-Unfortunately, close companions are difficult and expensive to detect with imaging techniques.
-In this paper, we describe the direct spectral detection method wherein a high-resolution spectrum of the primary is cross-correlated against a template for a companion star.
-Variants of this method have previously been used to search for stellar, brown dwarf, and even planetary companions.
-We show that the direct spectral detection method can detect companions as late as M-type orbiting A0 or earlier primary stars in a single epoch on small-aperture telescopes.
-In addition to estimating the detection limits, we determine the sources of uncertainty in characterizing the companion temperature, and find that large systematic biases can exist.
-After calibrating the systematic biases with synthetic binary star observations, we apply the method to a sample of 34 known binary systems with an A- or B-type primary star.
-We detect nine total companions, including four of the five known companions with literature temperatures between $4000$ K $ < T < 6000$ K, the temperature range for which our method is optimized.
-We additionally characterize the companion for the first time in two previously single-lined binary systems and one binary identified with speckle interferometry.
-This method provides an inexpensive way to use small-aperture telescopes to detect binary companions with moderate mass-ratios, and is competitive with high-resolution imaging techniques inside $\sim 100-200$ mas.
+Abstract here
 \end{abstract}
@@
 \label{sec:intro}
-There has recently been a revival of interest in the multiplicity properties of intermediate-mass stars,  spurred largely by the detection of planets orbiting nearby \mbox{$\sim2 M_{\odot}$} stars on both wide \citep[e.g.][]{Lagrange2010, Marois2008} and close \citep{Johnson2011} orbits.
+%There has recently been a revival of interest in the multiplicity properties of intermediate-mass stars,  spurred largely by the detection of planets orbiting nearby \mbox{$\sim2 M_{\odot}$} stars on both wide \citep[e.g.][]{Lagrange2010, Marois2008} and close \citep{Johnson2011} orbits.
 In this context, binary companions are contaminants; companions complicate radial velocity planet searches because they necessitate simultaneous modeling of both stellar motions \citep[e.g.][]{Bergmann2015}.
@@
 
-However, known binary stars are typically avoided in planet search programs for a more fundamental reason: the binary companion depletes or destroys the planet-forming disk.
+%However, known binary stars are typically avoided in planet search programs for a more fundamental reason: the binary companion depletes or destroys the planet-forming disk.
 By combining a binary census of the $\sim 2$ Myr Taurus-Auriga star-forming region with a disk census of the same, \cite{Kraus2012} showed that close ($\lesssim 40$ AU) binaries are about 2-3 times less likely to host a protoplanetary disk, and so hasten disk dispersal.
@@
 %[CITE KRAUS PAPER] performed a search for binary companions among Kepler planet host stars, and found that the presence of a companion within 5-50AU suppresses planet formation by a factor of $\sim 4$.
+
+Stellar multiplicity is an inevitable and common outcome of star formation, with roughly half of all solar-type field stars in binary or multiple systems \citep{Raghavan2010} and an even higher fraction as the stellar mass increases.
+Young stellar associations and clusters tend to have even higher multiplicity \citep{Duchene2013}, indicating that stars often form in multiple systems that are destroyed by dynamical interactions as the cluster dissociates.
+
+TODO: mass-ratio is the most dynamically stable orbital feature. Where did I see this?
+
+TODO: \citep{Carrier2002} and \citep{Vuissoz2004} look at Am/Ap stars and find a mass-ratio distribution with a broad peak near $q \sim 0.5$.
+This is coming mostly from SB1s, and assuming uniform inclinations to go from the mass function to the companion mass, and make simple assumptions about the primary mass.
+Still, it is interesting that my result is pretty similar for normal A-stars.
 
@@
 
+\begin{longtable*}{|l|lrrll|}
+\hline
+       star &      $T_\mathrm{eff}$ &   $v\sin{i}$ &  [Fe/H] &   Isochrone Mass &   Spectral Type Mass \\
+\hline
+\endhead
+\hline
+\multicolumn{3}{r}{{Continued on next page}} \\
+\endfoot
+
+\hline
+\endlastfoot
+   HIP 2548 &  $5732 \pm 112$ &      30 &    -0.5 &  $1.0^{+0.06}_{-0.04}$ &  $1.0^{+0.04}_{-0.03}$ \\
+   HIP 3478 &  $5524 \pm 150$ &       5 &    -0.5 &  $1.1^{+0.28}_{-0.13}$ &  $1.0^{+0.03}_{-0.04}$ \\
+   HIP 5310 &  $3343 \pm 154$ &      30 &     0.0 &  $0.3^{+0.13}_{-0.08}$ &  $0.4^{+0.12}_{-0.12}$ \\
+     HR 545 &   $4312 \pm 87$ &       5 &    -0.5 &  $0.8^{+0.11}_{-0.10}$ &  $0.7^{+0.01}_{-0.02}$ \\
+     HR 604 &  $4736 \pm 150$ &       5 &     0.5 &    $nan^{+nan}_{-nan}$ &  $0.8^{+0.02}_{-0.02}$ \\
+  HIP 10732 &  $5578 \pm 109$ &       5 &     0.0 &  $1.0^{+0.29}_{-0.04}$ &  $1.0^{+0.02}_{-0.04}$ \\
+  HIP 12332 &  $5551 \pm 107$ &      10 &     0.0 &    $nan^{+nan}_{-nan}$ &  $1.0^{+0.01}_{-0.04}$ \\
+  HIP 12706 &  $6051 \pm 107$ &      10 &     0.0 &  $1.1^{+0.03}_{-0.03}$ &  $1.1^{+0.04}_{-0.05}$ \\
+  HIP 13165 &  $5773 \pm 163$ &       5 &    -0.5 &  $1.1^{+0.31}_{-0.08}$ &  $1.0^{+0.10}_{-0.03}$ \\
+  HIP 13327 &  $5524 \pm 150$ &       5 &    -0.5 &  $1.2^{+0.20}_{-0.21}$ &  $1.0^{+0.03}_{-0.04}$ \\
+  HIP 14576 &  $6980 \pm 103$ &      10 &     0.0 &  $1.4^{+0.03}_{-0.03}$ &  $1.5^{+0.05}_{-0.03}$ \\
+  HIP 14764 &  $5601 \pm 108$ &      30 &     0.5 &    $nan^{+nan}_{-nan}$ &  $1.0^{+0.03}_{-0.03}$ \\
+  HIP 16244 &  $5592 \pm 107$ &       5 &    -0.5 &  $1.2^{+0.20}_{-0.22}$ &  $1.0^{+0.03}_{-0.03}$ \\
+  HIP 16340 &  $6214 \pm 150$ &       5 &    -0.5 &  $1.2^{+0.29}_{-0.07}$ &  $1.2^{+0.06}_{-0.05}$ \\
+  HIP 16611 &  $5476 \pm 154$ &       1 &     0.5 &  $0.9^{+0.04}_{-0.04}$ &  $0.9^{+0.04}_{-0.03}$ \\
+  HIP 17563 &  $8574 \pm 147$ &       5 &     0.5 &  $1.9^{+0.25}_{-0.11}$ &  $2.0^{+0.05}_{-0.06}$ \\
+  HIP 18396 &  $4492 \pm 162$ &      30 &    -0.5 &  $0.9^{+0.10}_{-0.12}$ &  $0.8^{+0.03}_{-0.02}$ \\
+  HIP 18724 &  $6831 \pm 154$ &      20 &     0.0 &  $1.7^{+0.13}_{-0.23}$ &  $1.4^{+0.04}_{-0.04}$ \\
+  HIP 19949 &  $6492 \pm 155$ &      20 &    -0.5 &  $1.3^{+0.06}_{-0.05}$ &  $1.3^{+0.06}_{-0.06}$ \\
+  HIP 20380 &  $6492 \pm 109$ &      20 &    -0.5 &  $1.3^{+0.04}_{-0.04}$ &  $1.3^{+0.03}_{-0.05}$ \\
+  HIP 21589 &  $4562 \pm 154$ &       5 &     0.0 &  $0.7^{+0.04}_{-0.03}$ &  $0.8^{+0.02}_{-0.03}$ \\
+  HIP 22833 &  $4745 \pm 107$ &      10 &     0.0 &  $0.8^{+0.02}_{-0.02}$ &  $0.8^{+0.02}_{-0.01}$ \\
+  HIP 22958 &  $6126 \pm 112$ &      30 &    -0.5 &  $1.4^{+0.22}_{-0.21}$ &  $1.2^{+0.04}_{-0.04}$ \\
+  HIP 23362 &  $6283 \pm 158$ &       5 &    -0.5 &  $1.2^{+0.06}_{-0.05}$ &  $1.2^{+0.07}_{-0.05}$ \\
+  HIP 23916 &  $5450 \pm 158$ &       5 &    -0.5 &  $1.1^{+0.20}_{-0.20}$ &  $0.9^{+0.04}_{-0.03}$ \\
+  HIP 24244 &  $4929 \pm 158$ &       5 &    -0.5 &  $0.8^{+0.04}_{-0.04}$ &  $0.8^{+0.02}_{-0.03}$ \\
+  HIP 24902 &  $5679 \pm 154$ &      30 &     0.0 &  $1.0^{+0.05}_{-0.04}$ &  $1.0^{+0.04}_{-0.03}$ \\
+  HIP 25143 &  $5883 \pm 109$ &      30 &     0.0 &  $1.1^{+0.04}_{-0.03}$ &  $1.1^{+0.05}_{-0.07}$ \\
+  HIP 26126 &   $5841 \pm 91$ &       5 &    -0.5 &  $1.0^{+0.03}_{-0.03}$ &  $1.0^{+0.05}_{-0.04}$ \\
+  HIP 32607 &   $5068 \pm 91$ &       5 &    -0.5 &  $0.8^{+0.02}_{-0.02}$ &  $0.9^{+0.01}_{-0.01}$ \\
+  HIP 37450 &   $nan \pm nan$ & \nodata & \nodata &    $nan^{+nan}_{-nan}$ &    $nan^{+nan}_{-nan}$ \\
+  HIP 38538 &  $6576 \pm 150$ &      30 &    -0.5 &  $1.3^{+0.05}_{-0.05}$ &  $1.3^{+0.10}_{-0.05}$ \\
+  HIP 38593 &  $5398 \pm 112$ &       5 &    -0.5 &  $1.3^{+0.08}_{-0.13}$ &  $0.9^{+0.03}_{-0.03}$ \\
+  HIP 38846 &  $6595 \pm 158$ &      10 &     0.0 &  $1.7^{+0.12}_{-0.21}$ &  $1.3^{+0.09}_{-0.05}$ \\
+  HIP 39847 &  $5750 \pm 107$ &      10 &    -0.5 &  $1.0^{+0.04}_{-0.03}$ &  $1.0^{+0.05}_{-0.03}$ \\
+  HIP 40881 &  $4562 \pm 154$ &      10 &    -0.5 &  $0.8^{+0.18}_{-0.05}$ &  $0.8^{+0.02}_{-0.03}$ \\
+  HIP 42129 &  $5241 \pm 158$ &      10 &    -0.5 &  $1.2^{+0.12}_{-0.18}$ &  $0.9^{+0.04}_{-0.02}$ \\
+  HIP 46283 &   $9268 \pm 85$ &      10 &     0.5 &    $nan^{+nan}_{-nan}$ &  $2.2^{+0.02}_{-0.02}$ \\
+  HIP 51362 &  $5033 \pm 158$ &       5 &    -0.5 &  $0.8^{+0.04}_{-0.04}$ &  $0.8^{+0.02}_{-0.03}$ \\
+  HIP 52678 &  $5033 \pm 112$ &      10 &    -0.5 &  $1.0^{+0.16}_{-0.19}$ &  $0.8^{+0.01}_{-0.02}$ \\
+  HIP 55266 &  $8483 \pm 139$ &      30 &    -0.5 &  $1.8^{+0.06}_{-0.04}$ &  $2.0^{+0.06}_{-0.05}$ \\
+  HIP 63945 &  $7038 \pm 162$ &      10 &    -0.5 &  $1.6^{+0.26}_{-0.16}$ &  $1.5^{+0.08}_{-0.06}$ \\
+  HIP 72154 &  $4918 \pm 162$ &      30 &    -0.5 &  $0.9^{+0.22}_{-0.09}$ &  $0.8^{+0.03}_{-0.03}$ \\
+  HIP 76267 &  $5449 \pm 158$ &       5 &    -0.5 &  $0.9^{+0.04}_{-0.04}$ &  $0.9^{+0.04}_{-0.03}$ \\
+  HIP 77336 &  $6407 \pm 112$ &      20 &     0.0 &  $1.2^{+0.04}_{-0.04}$ &  $1.3^{+0.04}_{-0.05}$ \\
+  HIP 77516 &  $6825 \pm 141$ &       5 &     0.5 &  $1.4^{+0.21}_{-0.06}$ &  $1.4^{+0.03}_{-0.04}$ \\
+  HIP 78820 &  $5658 \pm 158$ &       5 &    -0.5 &  $1.3^{+0.11}_{-0.13}$ &  $1.0^{+0.04}_{-0.04}$ \\
+  HIP 78821 &  $4968 \pm 154$ &      10 &    -0.5 &  $1.1^{+0.09}_{-0.10}$ &  $0.8^{+0.02}_{-0.03}$ \\
+  HIP 79199 &  $4616 \pm 158$ &       5 &    -0.5 &  $0.9^{+0.14}_{-0.14}$ &  $0.8^{+0.02}_{-0.03}$ \\
+  HIP 79404 &  $4773 \pm 112$ &      10 &    -0.5 &  $1.1^{+0.07}_{-0.08}$ &  $0.8^{+0.02}_{-0.01}$ \\
+  HIP 80460 &  $6391 \pm 155$ &      10 &     0.0 &  $1.2^{+0.06}_{-0.05}$ &  $1.3^{+0.06}_{-0.06}$ \\
+  HIP 82673 &  $4668 \pm 112$ &       5 &     0.5 &  $0.8^{+0.03}_{-0.03}$ &  $0.8^{+0.01}_{-0.02}$ \\
+  HIP 84606 &  $5476 \pm 154$ &      10 &    -0.5 &  $0.9^{+0.05}_{-0.04}$ &  $0.9^{+0.04}_{-0.03}$ \\
+  HIP 85379 &  $7590 \pm 151$ &      20 &     0.0 &    $nan^{+nan}_{-nan}$ &  $1.7^{+0.05}_{-0.03}$ \\
+  HIP 85998 &   $5460 \pm 91$ &       1 &    -0.5 &  $1.0^{+0.28}_{-0.03}$ &  $0.9^{+0.04}_{-0.01}$ \\
+  HIP 88116 &  $5293 \pm 112$ &       5 &     0.0 &  $0.9^{+0.03}_{-0.03}$ &  $0.9^{+0.02}_{-0.03}$ \\
+  HIP 88818 &   $5296 \pm 91$ &      20 &    -0.5 &  $0.9^{+0.02}_{-0.02}$ &  $0.9^{+0.02}_{-0.03}$ \\
+  HIP 88817 &  $3647 \pm 154$ &      20 &     0.0 &  $0.5^{+0.07}_{-0.10}$ &  $0.5^{+0.03}_{-0.05}$ \\
+  HIP 91118 &  $6492 \pm 155$ &      10 &    -0.5 &  $1.3^{+0.26}_{-0.07}$ &  $1.3^{+0.06}_{-0.06}$ \\
+  HIP 93805 &  $4054 \pm 109$ &       5 &    -0.5 &  $0.6^{+0.03}_{-0.03}$ &  $0.6^{+0.04}_{-0.02}$ \\
+  HIP 96840 &  $9942 \pm 152$ &      10 &     0.0 &    $nan^{+nan}_{-nan}$ &  $2.3^{+0.03}_{-0.01}$ \\
+ HIP 100221 &  $5273 \pm 154$ &      20 &    -0.5 &  $0.9^{+0.29}_{-0.07}$ &  $0.9^{+0.04}_{-0.03}$ \\
+ HIP 100907 &  $5222 \pm 109$ &      10 &     0.0 &  $0.9^{+0.03}_{-0.03}$ &  $0.9^{+0.04}_{-0.02}$ \\
+ HIP 103298 &   $4615 \pm 90$ &       5 &    -0.5 &  $0.7^{+0.02}_{-0.02}$ &  $0.8^{+0.01}_{-0.02}$ \\
+ HIP 109139 &  $5710 \pm 112$ &      20 &    -0.5 &  $1.0^{+0.04}_{-0.03}$ &  $1.0^{+0.03}_{-0.03}$ \\
+ HIP 109521 &   $4412 \pm 87$ &      10 &     0.0 &  $0.7^{+0.02}_{-0.02}$ &  $0.7^{+0.01}_{-0.01}$ \\
+ HIP 115115 &   $4943 \pm 91$ &       5 &    -0.5 &  $0.8^{+0.02}_{-0.02}$ &  $0.8^{+0.02}_{-0.02}$ \\
+ \label{tab:companions}
+\end{longtable*}
+
 \newpage

### 2016-01-21 paper/ms.tex
Wrote initial draft of paper introduction

@@
 
+Beyond the overall multiplicity rate, the mass ratio, period, and eccentricity distributions of a binary star population place important constraints on the mode of binary star formation.
+Most binary stars are thought to form via core fragmentation \citep{Boss1979, Boss1986, Bate1995}, in which a collapsing core fragments into two or more individual protostars.
+The number and initial masses of the fragments are set by the total core mass, as well as its rotation, turbulence, and its temperature and density structure.
+If the fragments are separated by $\gtrsim 1000$ AU, they will evolve relatively independently of each other, accreting mass from the core material onto their own protostellar disks and then onto the protostars themselves.
+However close fragments ($a \sim 100$ AU) will interact with each other; the protostellar disk may be truncated, destabilized, or even merge into a circumbinary disk if the separation is small enough.
+In addition, unstable disk can fragment to form low-mass companions \citep{Kratter2006, Stammatellos2011}.
+The mass ratios of close companions formed via either mechanism should be effected by preferential accretion.
+Most work has suggested that the disk material will preferentially accrete onto the lower mass companion \citep{Bate1997, BBB2002}; however, recent work has indicated that magnetic disk braking may result in preferential accretion onto the more massive component \citep{Zhao2013} instead.
+In either case, we would expect to find a different mass ratio distribution for companions inside a few $100$ AU and companions on wider orbits.
+
+The mass ratio, period, and eccentricity distributions are fairly well-known for solar type stars \citep{Duquennoy1991, Raghavan2010} and cooler stars \citep{Fischer1992, Delfosse2004}.
+Interestingly, the mass ratio distribution appears to be invariant to separation for these stars \citep{Meyer2013}, contrary to the theoretical expectations.
+All of the distributions are much less certain for more massive stars.
+The reason for this is two-fold: first, more massive stars tend to more rare and farther away, meaning many of the companions are angularly close to the very bright primaries.
+Second, the primary stars tend to be rapid rotators, which limits radial velocity precision to $\sim 1 \mathrm{km\ s}^{-1}$.
+Worse, radial velocity monitoring can only measure a mass ratio if spectral lines from both components are visible; this typically suffers from the same flux ratio difficulty as imaging techniques.
+Nonetheless, \citet{DeRosa2014} performed an adaptive optics imaging survey of nearby A-type stars and found initial evidence that the mass ratio distribution for companions inside $125$ AU is much flatter than that of wide companions.
+Unfortunately they had only very few detections at these near separations, and the result is complicated by the inherent difficulty of detecting close companions with low mass ratios in an imaging survey.
+
+In this paper, we describe a spectroscopic survey of nearby intermediate-mass stars.
+We search for companions using the direct spectral detection technique \citep{Gullikson2016}, which has a separation-invariant detection rate for all separations inside $\sim 1 ''$.
+We describe the stellar sample and data used for the survey in Section \ref{sec:obs}, as well as the data reduction steps in the same section.
+Next, we describe our estimation of the stellar parameters for the primary stars in our sample in Section \ref{sec:sp}.
+We then describe the direct spectroscopic detection and tabulate the companion detections in Section \ref{sec:companions}, and discuss the survey completeness in Section \ref{sec:completeness}.
+Finally, we end with a derivation of the mass ratio distribution from our sample in Section \ref{sec:mrd} and discuss its implications for binary formation in Section \ref{sec:discussion}.
+
 TODO: mass-ratio is the most dynamically stable orbital feature. Where did I see this?
@@
 Still, it is interesting that my result is pretty similar for normal A-stars.
-
-Multiplicity is an inevitable outcome of star formation, especially for more massive stars where multiplicity is more common \citep{Zinnecker2007}, and so is important to study in its own right.
-Beyond the overall multiplicity rate, the mass ratio, period, and eccentricity distributions of a binary star population can place important constraints on the mode of binary star formation.
-Specifically, a mass-ratio distribution that changes with physical separation could indicate that secondary stars are either forming through disk fragmentation \citep[e.g.][]{Kratter2006, Stamatellos2011}  or are accreting a significant amount of their mass from the primary star disk.
-\cite{DeRosa2014} recently completed an imaging survey of nearby A-type stars, and found preliminary evidence that the mass-ratio distribution does in fact become flatter for closer companions.
-There is no evidence of such a change for solar-type or later stars \citep{Meyer2013}.
-
-It is difficult to detect low-mass companions very near an intrinsically bright primary star and even more difficult to characterize the companion.
-There are three commonly used techniques for binary star searches: direct imaging with adaptive optics systems,  interferometry, and radial velocity monitoring.
-Imaging can easily detect low-mass companions at wide apparent separations, but loses sensitivity as the on-sky distance from the primary star decreases \citep[see][for typical sensitivity curves]{DeRosa2014}.
-Interferometry can usually achieve smaller working angles than imaging, but cannot achieve as high contrast \citep[see e.g.][]{Aldoretta2015}.
-
- Radial velocity monitoring can easily find companions on very short-period orbits, but its sensitivity to low-mass companions drops as the physical separation increases.
-This is especially true for A- and B-type stars, where radial velocity precision is typically limited to $\sim 1 \rm km \  s^{-1}$ by their rotationally broadened lines.
-Worse, radial velocity monitoring techniques cannot characterize the companion unless the inclination is known or if the companion spectral lines are also visible.
-All three techniques have separation-dependent sensitivity, which introduces observational bias in any search for a parameter that changes with physical separation.
-
- One technique that is separation independent is to search directly for the composite spectrum of two stars.
-\citet{Burgasser2007} used single-epoch low-resolution spectroscopy to identify and characterize a brown dwarf binary system by fitting both spectra simultaneously.
-This method only works if the stars have a similar brightness but very different spectra, such that the spectral features from both components are visible and distinguishable.
-If, as in the case of binary systems with very large flux ratios, the companion spectrum is buried within the noise of the primary star, a different method is needed.
-
-The direct spectral detection method (hereafter referred to as the DSD method), and variations thereof, has been used to search for binary companions to early B-stars \citep{Gullikson2013}, main sequence FGK-stars \citep{Kolbl2015}, young K-M stars \citep{Prato2002}, and even `Hot Jupiter' type planets \citep{Snellen2010, Brogi2012, deKok2013} orbiting FGK-stars.
-The method relies on the cross-correlation function (CCF) of a high-spectral-resolution spectrum of the primary star with a model spectrum for the expected companion.
-The CCF uses every pixel in the spectrum, and more importantly every spectral line in the secondary spectrum.
-A simple experiment with synthetic spectra containing increasing numbers of spectral lines (N) in noisy data shows that the CCF peak significance increases as $\sim\sqrt{N}$.
-For high-resolution cross-dispersed \'echelle spectra, this amplification can reach several factors of 10, allowing the detection \emph{and characterization} of a secondary spectrum where the individual lines are completely buried in noise.
-Since the DSD method uses a seeing-limited spectrum of the primary star, its sensitivity is independent of separation inside $\sim 1 ''$ and can make use of small telescopes to detect high-contrast companions.
-
-In this paper, we describe the DSD method in detail, and use it to detect the secondary star in nine known binary systems.
-We describe the method in Section \ref{sec:method}.
-We describe the observations and data reduction in Section \ref{sec:obs}, then use the observations to estimate the accuracy with which we can measure the companion temperature in Section \ref{subsec:systematics} and the sensitivity of the method in Section \ref{subsec:sensitivity}.
-In Section \ref{sec:results} we use the DSD method to search for known companions, and discuss the results in Section \ref{sec:conclusions}.
 

### 2016-01-21 Completeness.py
Fit histogram and log-normal distribution to actual data

@@ -378,7 +378,7 @@ class VelocityPDF(object):
         # Calculate approximate maxwellian parameters from the velocities.
         alpha = np.sqrt(np.nanvar(v_eq) * np.pi / (3*np.pi - 8))
         l = np.nanmedian(v_eq) - 2*alpha*np.sqrt(2/np.pi)
-
+          
         # Add a row to the dataframe with this information
         df.loc[df.index.max()+1] = [1.0, 1.24, 0, 25, 100, alpha*np.sqrt(2), l]
 
@@ -499,7 +499,7 @@ def get_completeness(starname, date):
 
     # Get the primary mass 
     spt = StarData.GetData(starname).spectype
-    primary_mass_samples = Priors.get_primary_mass(starname, spt)
+    primary_mass_samples, _ = Priors.get_primary_mass(starname, spt)
     comp_df['M1'] = np.median(primary_mass_samples)
 
     # Convert the companion temperature to mass using spectral type relations 

### 2016-01-21 paper/ms.tex
Wrote initial draft of observations/data reduction section

@@
 \label{sec:obs}
+
+The stellar sample for this survey is defined by the following criteria:
+
+\begin{itemize}
+\item $V < 6$
+\item $v\sin{i} > 80 \mathrm{km\ s}^{-1}$
+\item Spectral Type A or B with the following additional constraints
+\begin{itemize}
+  \item Main Sequence
+  \item No spectral peculiarities except for `n', which denotes broad lines.
+\end{itemize}
+\end{itemize}
+
+The first two criteria are to ensure that the direct spectral detection technique (Section \ref{sec:companions}) both works and is well-calibrated.
+The magnitude limit ensures that a sufficiently high signal-to-noise ratio can be achieved in a short period of time.
+It does introduce a Malmquist bias in the derived mass ratio, which we discuss and correct for in Section \ref{sec:mrd}.
+Likewise, the $v\sin{i}$ limit makes accounting for the primary star spectrum in the companion search trivial; since most A- or B-type stars are rapid rotators, it does not actually remove very many stars from the sample.
+Finally we only include normal, main sequence stars in the sample because the binary flux ratio would be even less favorable to companion detection in an evolved star.
+
+We use several high spectral resolution, cross-dispersed \'echelle spectrographs for this survey.
+We use the CHIRON spectrograph \citep{CHIRON} on the 1.5m telescope at Cerro Tololo Inter-American Observatory for most southern targets.
+This spectrograph is an $R\equiv \lambda / \Delta \lambda = 80000$ spectrograph with wavelength coverage from 450 - 850 nm, and is fed by a $2.7''$ optical fiber.
+The data are automatically reduced with a standard CHIRON data reduction pipeline, but the pipeline leaves residuals of strong lines in adjacent orders.
+We therefore bias-correct, flat-field and extract the spectra with the optimum extraction technique \citep{Horne1986} using standard IRAF\footnote{IRAF is distributed by the National Optical Astronomy Observatories, which are operated by the Association of Universities for Research in Astronomy, Inc., under cooperative agreement with the National Science Foundation.} tasks, and use the wavelength calibration from the pipeline reduced spectra.
+
+For the northern targets, we use a combination of the High Resolution Spectrograph \citep[HRS,][]{HRS} on the Hobby Eberly Telescope, and the Tull coud\'e \citep[TS23,][]{TS23} and IGRINS \citep{IGRINS} spectrographs, both on the 2.7m Harlan J.
+Smith Telescope.
+All three northern instruments are at McDonald Observatory.
+For the HRS, we use the $R = 60000$ setting with a $2''$ fiber, and with wavelength coverage from 410-780 nm.
+We bias-correct, flat-field, and extract the spectra using an IRAF pipeline.
+The HRS spectra are wavelength-calibrated using a Th-Ar lamp observed immediately before or after the science observations.
+
+For the TS23, we use a $1.2''$ slit in combination with the E2 \'echelle grating (53 grooves/mm, blaze angle $65^{\circ}$), yielding a resolving power of $R=60000$ and a wavelength coverage from 375-1020 nm.
+We reduce the data using an IRAF pipeline very similar to the one we use for the HRS, and wavelength calibrate using a Th-Ar lamp observed immediately before the science observations.
+
+IGRINS only has one setting with $R = 40000$.
+It has complete wavelength coverage from 1475-2480 nm, except for where telluric absorption is almost $100\%$ from 1810 - 1930 nm.
+Each star is observed in an ABBA nodding mode, and reduced using the standard IGRINS pipeline \citep{IGRINS_plp_v2}.
+The standard pipeline uses atmospheric OH emission lines as well as a Th-Ar calibration frame to calibrate the wavelengths; we further refine the wavelength solution using telluric absorption lines.
+
+After reducing the data, we fit and remove the telluric spectrum using the TelFit code \citep{Gullikson2014}.
+We fit each \'echelle order affected by telluric absorption independently from each other to get the best removal.
+The telluric correction is critical for IGRINS spectra, where every order is dominated by telluric absorption lines.
+For the optical spectra, it is less critical but allows us to use some of the redder orders than we otherwise would be able to.
+For unsaturated lines, the best-fit telluric model reproduces the data to within $\sim 1-5\%$ of the continuum level.
+
+TODO: MAKE THE SPECTRA AVAILABLE SOMEHOW...
 

### 2016-01-21 paper/ms.tex
Moved stellar parameter section until after the companion stuff

@@
 We describe the stellar sample and data used for the survey in Section \ref{sec:obs}, as well as the data reduction steps in the same section.
-Next, we describe our estimation of the stellar parameters for the primary stars in our sample in Section \ref{sec:sp}.
-We then describe the direct spectroscopic detection and tabulate the companion detections in Section \ref{sec:companions}, and discuss the survey completeness in Section \ref{sec:completeness}.
+Next, we describe the direct spectroscopic detection and tabulate the companion detections in Section \ref{sec:companions}, and discuss the survey completeness in Section \ref{sec:completeness}.
+We then describe our estimation of the stellar parameters for the primary stars in our sample in Section \ref{sec:sp}.
 Finally, we end with a derivation of the mass ratio distribution from our sample in Section \ref{sec:mrd} and discuss its implications for binary formation in Section \ref{sec:discussion}.
@@
 Finally we only include normal, main sequence stars in the sample because the binary flux ratio would be even less favorable to companion detection in an evolved star.
+The target list and observing details are given in Table \ref{tab:observations}.
 
@@
 
-\section{Stellar Parameters}
-\label{sec:sp}
-
 \section{Companion Search}
@@
 \label{sec:completeness}
+
+\section{Stellar Parameters}
+\label{sec:sp}
 

### 2016-01-21 paper/ms.tex
Added most of the companion search section (not done yet though...)

@@
 
+TODO: Describe imaging observations (band, observation time, etc). Add a table for this!
+
 \section{Companion Search}
 \label{sec:companions}
+
+We search for stellar companions to our sample stars using the direct spectroscopic detection technique, described in detail in \citet{Gullikson2016}.
+In short, we high-pass filter each of our spectra to remove the broad lines from the primary star, and cross-correlate each \'echelle order or each filtered spectrum against a large grid of Phoenix model spectra \citep{Husser2013_b} with the following parameters:
+
+\begin{itemize}
+\item $T_\mathrm{eff} = 3000-12000$ K, in steps of 100 K
+\item {[}Fe/H{]} = -0.5, 0.0, +0.5
+\item $v\sin{i} = 1, 5, 10, 20, 30 \ \mathrm{km\ s}^{-1}$
+\end{itemize}
+
+We then combine the cross-correlation functions for all orders using both a simple average and the maximum-likelihood weighting scheme \citep{Zucker2003}.
+A companion detection is denoted by a strong peak in the combined cross-correlation function (CCF).
+While the maximum-likelihood scheme produces detections with much higher significance, it also magnifies spurious peaks and so has a larger false-positive rate.
+For this reason, we use the simple average CCFs in all further analysis unless otherwise specified.
+
+The peak height in the CCF as a function of the stellar model acts in a similar way to the more typical $\chi^2$ map of parameter space.
+More concretely, as the stellar model template gets closer to the true companion spectrum, the CCF peak gets higher.
+We can therefore measure the companion temperature and, to a lesser degree its metallicity and $v\sin{i}$, in a single spectrum.
+Imperfect stellar models cause a bias between the true companion temperature and the temperature of the Phoenix model which produces the largest CCF peak.
+This bias is most pronounced at low temperatures, where molecular absorption becomes important.
+We correct for it by applying the calibrations developed in \citet{Gullikson2016}.
+These calibrations are only valid for companions with $3000 < T_\mathrm{eff} < 7000 K$; for detections at hotter temperatures we assume that the temperature which produces the maximum CCF peak is an \emph{unbiased} estimator of the true companion temperature.
+
+We list the companion detections in Table \ref{tab:companions}, and report the estimate of the companion temperature, $v\sin{i}$, and metallicity derived from the model parameters which produce the largest CCF peak.
+The $v\sin{i}$ and metallicity values do not have uncertainties and should only be taken as a rough estimate of the true value.
+TODO: Add columns to Table \ref{tab:companions} for the WDS designation if known, and mark the ones that are new.
+Also include imaging data (delta-magnitude) when I have it.
+Finally, include a column for the number of detections that went into the average.
+
+TODO: Make plots for all of the CCFs.
+
+Most of the detected companions have follow-up spectra to confirm the existence of the companion.
+[MENTION THAT YOU CAN SEE THEM ALL IN THE FIGURES].
+In most cases, there is a clear shift in the radial velocity of the companion, indicating that it is orbiting the target star and is not a foreground or background companion.
+In addition we obtained Gemini/NIRI adaptive optics imaging data for some of the northern companions.
 
@@
 
-\begin{longtable*}{|l|lllll|}
-\hline
-            &        $T_\mathrm{eff}$ &      $\log{g}$ &             Mass &            Age & \\
-       star &        (K)              &      (cgs)     &      ($M_{\odot}$) &          (Myr) & source \\
-\hline
-\endhead
-\hline
-\multicolumn{3}{r}{{Continued on next page}} \\
-\endfoot
-
-\hline
-\endlastfoot
-   HIP 2548 &   $11864 \pm 403$ &  $4.4 \pm 0.14$ &  $2.8^{+0.16}_{-0.15}$ &     $79^{+68}_{-53}$ &      DH2015 \\
-   HIP 3478 &  $14250 \pm 1000$ &  $4.2 \pm 0.25$ &  $3.8^{+0.50}_{-0.45}$ &     $22^{+40}_{-15}$ &  This Study \\
-   HIP 5310 &    $8611 \pm 293$ &  $4.4 \pm 0.14$ &  $1.8^{+0.10}_{-0.08}$ &  $306^{+236}_{-196}$ &      DH2015 \\
-     HR 545 &  $11000 \pm 1000$ &  $4.3 \pm 0.25$ &  $2.5^{+0.39}_{-0.35}$ &    $37^{+105}_{-28}$ &  This Study \\
-     HR 604 &  $11000 \pm 1000$ &  $4.5 \pm 0.25$ &  $2.4^{+0.37}_{-0.34}$ &     $28^{+87}_{-20}$ &  This Study \\
-  HIP 10732 &    $9500 \pm 300$ &  $4.0 \pm 0.25$ &  $2.1^{+0.18}_{-0.16}$ &    $80^{+237}_{-70}$ &  This Study \\
-  HIP 12332 &    $7750 \pm 300$ &  $3.5 \pm 0.25$ &  $1.9^{+0.37}_{-0.30}$ &  $687^{+218}_{-425}$ &  This Study \\
-  HIP 12706 &    $8551 \pm 291$ &  $4.3 \pm 0.14$ &  $1.9^{+0.15}_{-0.12}$ &  $650^{+104}_{-180}$ &      DH2015 \\
-  HIP 13165 &  $15000 \pm 1000$ &  $4.0 \pm 0.25$ &  $4.2^{+0.58}_{-0.50}$ &     $31^{+42}_{-22}$ &  This Study \\
-  HIP 13327 &  $15000 \pm 1000$ &  $4.5 \pm 0.25$ &  $4.0^{+0.50}_{-0.45}$ &      $15^{+26}_{-9}$ &  This Study \\
-  HIP 14576 &   $13070 \pm 444$ &  $4.0 \pm 0.14$ &  $3.6^{+0.29}_{-0.23}$ &    $139^{+17}_{-25}$ &      DH2015 \\
-  HIP 14764 &  $11750 \pm 1000$ &  $4.2 \pm 0.25$ &  $2.8^{+0.42}_{-0.39}$ &     $35^{+91}_{-27}$ &  This Study \\
-  HIP 16244 &  $16333 \pm 1000$ &  $4.3 \pm 0.25$ &  $4.7^{+0.57}_{-0.50}$ &      $15^{+22}_{-9}$ &  This Study \\
-  HIP 16340 &  $12500 \pm 1000$ &  $4.0 \pm 0.25$ &  $3.1^{+0.51}_{-0.42}$ &     $49^{+92}_{-39}$ &  This Study \\
-  HIP 16611 &   $12514 \pm 425$ &  $4.0 \pm 0.14$ &  $3.3^{+0.25}_{-0.20}$ &    $157^{+23}_{-46}$ &      DH2015 \\
-  HIP 17563 &  $19000 \pm 1000$ &  $4.5 \pm 0.25$ &  $6.0^{+0.66}_{-0.59}$ &      $10^{+11}_{-4}$ &  This Study \\
-  HIP 18396 &  $15000 \pm 1000$ &  $4.5 \pm 0.25$ &  $4.0^{+0.52}_{-0.47}$ &      $15^{+27}_{-9}$ &  This Study \\
-  HIP 18724 &  $21000 \pm 1000$ &  $4.5 \pm 0.25$ &  $7.1^{+0.68}_{-0.64}$ &        $8^{+7}_{-3}$ &  This Study \\
-  HIP 19949 &    $9825 \pm 334$ &  $3.8 \pm 0.14$ &  $2.2^{+0.11}_{-0.10}$ &  $198^{+136}_{-125}$ &      DH2015 \\
-  HIP 20380 &    $8738 \pm 297$ &  $3.9 \pm 0.14$ &  $1.9^{+0.09}_{-0.08}$ &  $339^{+210}_{-207}$ &      DH2015 \\
-  HIP 21589 &    $8591 \pm 292$ &  $3.9 \pm 0.14$ &  $1.8^{+0.09}_{-0.07}$ &  $302^{+225}_{-196}$ &      DH2015 \\
-  HIP 22833 &    $8278 \pm 281$ &  $3.9 \pm 0.14$ &  $1.8^{+0.12}_{-0.09}$ &  $649^{+163}_{-295}$ &      DH2015 \\
-  HIP 22958 &  $16000 \pm 1000$ &  $4.5 \pm 0.25$ &  $4.5^{+0.53}_{-0.50}$ &      $14^{+21}_{-8}$ &  This Study \\
-  HIP 23362 &   $12450 \pm 423$ &  $4.3 \pm 0.14$ &  $3.2^{+0.20}_{-0.16}$ &    $147^{+29}_{-58}$ &      DH2015 \\
-  HIP 23916 &  $16500 \pm 1000$ &  $4.2 \pm 0.25$ &  $4.8^{+0.56}_{-0.52}$ &     $16^{+26}_{-10}$ &  This Study \\
-  HIP 24244 &   $13781 \pm 469$ &  $4.2 \pm 0.14$ &  $3.9^{+0.29}_{-0.23}$ &    $114^{+11}_{-23}$ &      DH2015 \\
-  HIP 24902 &    $8275 \pm 281$ &  $4.0 \pm 0.14$ &  $1.7^{+0.10}_{-0.08}$ &  $466^{+252}_{-286}$ &      DH2015 \\
-  HIP 25143 &    $8101 \pm 275$ &  $3.8 \pm 0.14$ &  $1.7^{+0.06}_{-0.06}$ &  $236^{+247}_{-160}$ &      DH2015 \\
-  HIP 26126 &    $9542 \pm 324$ &  $3.9 \pm 0.14$ &  $2.1^{+0.09}_{-0.08}$ &  $175^{+148}_{-112}$ &      DH2015 \\
-  HIP 32607 &    $7770 \pm 264$ &  $3.8 \pm 0.14$ &  $1.6^{+0.07}_{-0.06}$ &  $519^{+342}_{-335}$ &      DH2015 \\
-  HIP 38538 &    $8551 \pm 291$ &  $4.0 \pm 0.14$ &  $1.9^{+0.14}_{-0.12}$ &  $637^{+109}_{-211}$ &      DH2015 \\
-  HIP 38593 &  $21667 \pm 1000$ &  $4.5 \pm 0.25$ &  $7.6^{+0.74}_{-0.68}$ &        $8^{+6}_{-3}$ &  This Study \\
-  HIP 38846 &  $22000 \pm 1000$ &  $4.5 \pm 0.25$ &  $7.8^{+0.74}_{-0.71}$ &        $8^{+6}_{-3}$ &  This Study \\
-  HIP 39847 &   $10014 \pm 340$ &  $4.0 \pm 0.14$ &  $2.2^{+0.13}_{-0.12}$ &  $195^{+131}_{-121}$ &      DH2015 \\
-  HIP 40881 &    $9500 \pm 300$ &  $4.0 \pm 0.25$ &  $2.1^{+0.17}_{-0.16}$ &    $71^{+239}_{-60}$ &  This Study \\
-  HIP 42129 &  $18000 \pm 1000$ &  $4.5 \pm 0.25$ &  $5.4^{+0.63}_{-0.54}$ &      $11^{+14}_{-5}$ &  This Study \\
-  HIP 51362 &   $10899 \pm 371$ &  $4.0 \pm 0.14$ &  $2.6^{+0.14}_{-0.12}$ &   $182^{+79}_{-102}$ &      DH2015 \\
-  HIP 52678 &  $15000 \pm 1000$ &  $4.5 \pm 0.25$ &  $4.0^{+0.49}_{-0.50}$ &     $16^{+26}_{-10}$ &  This Study \\
-  HIP 55266 &    $8720 \pm 296$ &  $4.5 \pm 0.14$ &  $1.9^{+0.09}_{-0.07}$ &  $346^{+209}_{-215}$ &      DH2015 \\
-  HIP 63945 &  $18000 \pm 1000$ &  $4.5 \pm 0.25$ &  $5.4^{+0.60}_{-0.56}$ &      $11^{+14}_{-5}$ &  This Study \\
-  HIP 72154 &  $10500 \pm 1000$ &  $4.5 \pm 0.25$ &  $2.3^{+0.36}_{-0.33}$ &    $32^{+101}_{-24}$ &  This Study \\
-  HIP 76267 &   $10342 \pm 352$ &  $4.0 \pm 0.14$ &  $2.5^{+0.19}_{-0.16}$ &    $314^{+53}_{-99}$ &      DH2015 \\
-  HIP 77336 &    $8917 \pm 303$ &  $4.0 \pm 0.14$ &  $2.9^{+0.23}_{-0.20}$ &    $404^{+73}_{-70}$ &      DH2015 \\
-  HIP 77516 &    $9250 \pm 300$ &  $4.0 \pm 0.25$ &  $2.1^{+0.17}_{-0.16}$ &    $74^{+275}_{-64}$ &  This Study \\
-  HIP 78820 &  $24062 \pm 1000$ &  $3.9 \pm 0.25$ &  $9.2^{+0.51}_{-0.64}$ &        $9^{+6}_{-4}$ &  This Study \\
-  HIP 78821 &    $7250 \pm 300$ &  $4.0 \pm 0.25$ &  $9.1^{+0.65}_{-0.96}$ &        $8^{+6}_{-3}$ &  This Study \\
-  HIP 79199 &  $12500 \pm 1000$ &  $4.5 \pm 0.25$ &  $3.0^{+0.42}_{-0.39}$ &     $23^{+55}_{-16}$ &  This Study \\
-  HIP 79404 &  $21667 \pm 1000$ &  $4.5 \pm 0.25$ &  $7.6^{+0.75}_{-0.69}$ &        $8^{+6}_{-3}$ &  This Study \\
-  HIP 80460 &    $7810 \pm 266$ &  $3.7 \pm 0.14$ &  $1.7^{+0.11}_{-0.08}$ &  $783^{+232}_{-394}$ &      DH2015 \\
-  HIP 82673 &  $11750 \pm 1000$ &  $3.5 \pm 0.25$ &  $3.4^{+0.65}_{-0.57}$ &    $171^{+73}_{-64}$ &  This Study \\
-  HIP 84606 &    $9702 \pm 330$ &  $4.0 \pm 0.14$ &  $2.1^{+0.10}_{-0.09}$ &   $154^{+137}_{-99}$ &      DH2015 \\
-  HIP 85379 &    $8250 \pm 300$ &  $3.5 \pm 0.25$ &  $2.1^{+0.37}_{-0.34}$ &  $550^{+154}_{-260}$ &  This Study \\
-  HIP 85998 &    $8812 \pm 300$ &  $4.0 \pm 0.25$ &  $1.9^{+0.16}_{-0.13}$ &    $95^{+332}_{-84}$ &  This Study \\
-  HIP 88116 &    $9750 \pm 300$ &  $3.5 \pm 0.25$ &  $2.7^{+0.43}_{-0.39}$ &   $305^{+68}_{-150}$ &  This Study \\
-  HIP 88818 &    $9162 \pm 312$ &  $4.3 \pm 0.14$ &  $2.7^{+0.24}_{-0.23}$ &    $441^{+86}_{-72}$ &      DH2015 \\
-  HIP 88817 &    $9162 \pm 312$ &  $4.3 \pm 0.14$ &  $2.1^{+0.16}_{-0.12}$ &   $480^{+84}_{-168}$ &      DH2015 \\
-  HIP 91118 &    $9500 \pm 300$ &  $4.0 \pm 0.25$ &  $2.1^{+0.19}_{-0.15}$ &    $70^{+244}_{-60}$ &  This Study \\
-  HIP 93805 &   $11962 \pm 407$ &  $4.2 \pm 0.14$ &  $3.5^{+0.32}_{-0.26}$ &    $194^{+19}_{-21}$ &      DH2015 \\
- HIP 100221 &    $9750 \pm 300$ &  $4.5 \pm 0.25$ &  $2.2^{+0.15}_{-0.15}$ &    $34^{+110}_{-26}$ &  This Study \\
- HIP 100907 &    $9042 \pm 307$ &  $4.0 \pm 0.14$ &  $2.1^{+0.16}_{-0.13}$ &  $512^{+100}_{-168}$ &      DH2015 \\
- HIP 103298 &    $9093 \pm 309$ &  $4.1 \pm 0.14$ &  $2.0^{+0.13}_{-0.11}$ &  $399^{+146}_{-209}$ &      DH2015 \\
- HIP 109139 &   $12641 \pm 430$ &  $4.3 \pm 0.14$ &  $3.2^{+0.20}_{-0.16}$ &    $122^{+38}_{-61}$ &      DH2015 \\
- HIP 109521 &    $8420 \pm 286$ &  $4.2 \pm 0.14$ &  $2.0^{+0.19}_{-0.16}$ &  $728^{+109}_{-104}$ &      DH2015 \\
- HIP 115115 &   $10671 \pm 363$ &  $4.2 \pm 0.14$ &  $2.6^{+0.19}_{-0.16}$ &    $284^{+38}_{-81}$ &      DH2015 \\
-\label{tab:primary}
-\end{longtable*}
-
 \begin{longtable*}{|l|lrrll|}
@@
 
+\begin{longtable*}{|l|lllll|}
+\hline
+            &        $T_\mathrm{eff}$ &      $\log{g}$ &             Mass &            Age & \\
+       star &        (K)              &      (cgs)     &      ($M_{\odot}$) &          (Myr) & source \\
+\hline
+\endhead
+\hline
+\multicolumn{3}{r}{{Continued on next page}} \\
+\endfoot
+
+\hline
+\endlastfoot
+   HIP 2548 &   $11864 \pm 403$ &  $4.4 \pm 0.14$ &  $2.8^{+0.16}_{-0.15}$ &     $79^{+68}_{-53}$ &      DH2015 \\
+   HIP 3478 &  $14250 \pm 1000$ &  $4.2 \pm 0.25$ &  $3.8^{+0.50}_{-0.45}$ &     $22^{+40}_{-15}$ &  This Study \\
+   HIP 5310 &    $8611 \pm 293$ &  $4.4 \pm 0.14$ &  $1.8^{+0.10}_{-0.08}$ &  $306^{+236}_{-196}$ &      DH2015 \\
+     HR 545 &  $11000 \pm 1000$ &  $4.3 \pm 0.25$ &  $2.5^{+0.39}_{-0.35}$ &    $37^{+105}_{-28}$ &  This Study \\
+     HR 604 &  $11000 \pm 1000$ &  $4.5 \pm 0.25$ &  $2.4^{+0.37}_{-0.34}$ &     $28^{+87}_{-20}$ &  This Study \\
+  HIP 10732 &    $9500 \pm 300$ &  $4.0 \pm 0.25$ &  $2.1^{+0.18}_{-0.16}$ &    $80^{+237}_{-70}$ &  This Study \\
+  HIP 12332 &    $7750 \pm 300$ &  $3.5 \pm 0.25$ &  $1.9^{+0.37}_{-0.30}$ &  $687^{+218}_{-425}$ &  This Study \\
+  HIP 12706 &    $8551 \pm 291$ &  $4.3 \pm 0.14$ &  $1.9^{+0.15}_{-0.12}$ &  $650^{+104}_{-180}$ &      DH2015 \\
+  HIP 13165 &  $15000 \pm 1000$ &  $4.0 \pm 0.25$ &  $4.2^{+0.58}_{-0.50}$ &     $31^{+42}_{-22}$ &  This Study \\
+  HIP 13327 &  $15000 \pm 1000$ &  $4.5 \pm 0.25$ &  $4.0^{+0.50}_{-0.45}$ &      $15^{+26}_{-9}$ &  This Study \\
+  HIP 14576 &   $13070 \pm 444$ &  $4.0 \pm 0.14$ &  $3.6^{+0.29}_{-0.23}$ &    $139^{+17}_{-25}$ &      DH2015 \\
+  HIP 14764 &  $11750 \pm 1000$ &  $4.2 \pm 0.25$ &  $2.8^{+0.42}_{-0.39}$ &     $35^{+91}_{-27}$ &  This Study \\
+  HIP 16244 &  $16333 \pm 1000$ &  $4.3 \pm 0.25$ &  $4.7^{+0.57}_{-0.50}$ &      $15^{+22}_{-9}$ &  This Study \\
+  HIP 16340 &  $12500 \pm 1000$ &  $4.0 \pm 0.25$ &  $3.1^{+0.51}_{-0.42}$ &     $49^{+92}_{-39}$ &  This Study \\
+  HIP 16611 &   $12514 \pm 425$ &  $4.0 \pm 0.14$ &  $3.3^{+0.25}_{-0.20}$ &    $157^{+23}_{-46}$ &      DH2015 \\
+  HIP 17563 &  $19000 \pm 1000$ &  $4.5 \pm 0.25$ &  $6.0^{+0.66}_{-0.59}$ &      $10^{+11}_{-4}$ &  This Study \\
+  HIP 18396 &  $15000 \pm 1000$ &  $4.5 \pm 0.25$ &  $4.0^{+0.52}_{-0.47}$ &      $15^{+27}_{-9}$ &  This Study \\
+  HIP 18724 &  $21000 \pm 1000$ &  $4.5 \pm 0.25$ &  $7.1^{+0.68}_{-0.64}$ &        $8^{+7}_{-3}$ &  This Study \\
+  HIP 19949 &    $9825 \pm 334$ &  $3.8 \pm 0.14$ &  $2.2^{+0.11}_{-0.10}$ &  $198^{+136}_{-125}$ &      DH2015 \\
+  HIP 20380 &    $8738 \pm 297$ &  $3.9 \pm 0.14$ &  $1.9^{+0.09}_{-0.08}$ &  $339^{+210}_{-207}$ &      DH2015 \\
+  HIP 21589 &    $8591 \pm 292$ &  $3.9 \pm 0.14$ &  $1.8^{+0.09}_{-0.07}$ &  $302^{+225}_{-196}$ &      DH2015 \\
+  HIP 22833 &    $8278 \pm 281$ &  $3.9 \pm 0.14$ &  $1.8^{+0.12}_{-0.09}$ &  $649^{+163}_{-295}$ &      DH2015 \\
+  HIP 22958 &  $16000 \pm 1000$ &  $4.5 \pm 0.25$ &  $4.5^{+0.53}_{-0.50}$ &      $14^{+21}_{-8}$ &  This Study \\
+  HIP 23362 &   $12450 \pm 423$ &  $4.3 \pm 0.14$ &  $3.2^{+0.20}_{-0.16}$ &    $147^{+29}_{-58}$ &      DH2015 \\
+  HIP 23916 &  $16500 \pm 1000$ &  $4.2 \pm 0.25$ &  $4.8^{+0.56}_{-0.52}$ &     $16^{+26}_{-10}$ &  This Study \\
+  HIP 24244 &   $13781 \pm 469$ &  $4.2 \pm 0.14$ &  $3.9^{+0.29}_{-0.23}$ &    $114^{+11}_{-23}$ &      DH2015 \\
+  HIP 24902 &    $8275 \pm 281$ &  $4.0 \pm 0.14$ &  $1.7^{+0.10}_{-0.08}$ &  $466^{+252}_{-286}$ &      DH2015 \\
+  HIP 25143 &    $8101 \pm 275$ &  $3.8 \pm 0.14$ &  $1.7^{+0.06}_{-0.06}$ &  $236^{+247}_{-160}$ &      DH2015 \\
+  HIP 26126 &    $9542 \pm 324$ &  $3.9 \pm 0.14$ &  $2.1^{+0.09}_{-0.08}$ &  $175^{+148}_{-112}$ &      DH2015 \\
+  HIP 32607 &    $7770 \pm 264$ &  $3.8 \pm 0.14$ &  $1.6^{+0.07}_{-0.06}$ &  $519^{+342}_{-335}$ &      DH2015 \\
+  HIP 38538 &    $8551 \pm 291$ &  $4.0 \pm 0.14$ &  $1.9^{+0.14}_{-0.12}$ &  $637^{+109}_{-211}$ &      DH2015 \\
+  HIP 38593 &  $21667 \pm 1000$ &  $4.5 \pm 0.25$ &  $7.6^{+0.74}_{-0.68}$ &        $8^{+6}_{-3}$ &  This Study \\
+  HIP 38846 &  $22000 \pm 1000$ &  $4.5 \pm 0.25$ &  $7.8^{+0.74}_{-0.71}$ &        $8^{+6}_{-3}$ &  This Study \\
+  HIP 39847 &   $10014 \pm 340$ &  $4.0 \pm 0.14$ &  $2.2^{+0.13}_{-0.12}$ &  $195^{+131}_{-121}$ &      DH2015 \\
+  HIP 40881 &    $9500 \pm 300$ &  $4.0 \pm 0.25$ &  $2.1^{+0.17}_{-0.16}$ &    $71^{+239}_{-60}$ &  This Study \\
+  HIP 42129 &  $18000 \pm 1000$ &  $4.5 \pm 0.25$ &  $5.4^{+0.63}_{-0.54}$ &      $11^{+14}_{-5}$ &  This Study \\
+  HIP 51362 &   $10899 \pm 371$ &  $4.0 \pm 0.14$ &  $2.6^{+0.14}_{-0.12}$ &   $182^{+79}_{-102}$ &      DH2015 \\
+  HIP 52678 &  $15000 \pm 1000$ &  $4.5 \pm 0.25$ &  $4.0^{+0.49}_{-0.50}$ &     $16^{+26}_{-10}$ &  This Study \\
+  HIP 55266 &    $8720 \pm 296$ &  $4.5 \pm 0.14$ &  $1.9^{+0.09}_{-0.07}$ &  $346^{+209}_{-215}$ &      DH2015 \\
+  HIP 63945 &  $18000 \pm 1000$ &  $4.5 \pm 0.25$ &  $5.4^{+0.60}_{-0.56}$ &      $11^{+14}_{-5}$ &  This Study \\
+  HIP 72154 &  $10500 \pm 1000$ &  $4.5 \pm 0.25$ &  $2.3^{+0.36}_{-0.33}$ &    $32^{+101}_{-24}$ &  This Study \\
+  HIP 76267 &   $10342 \pm 352$ &  $4.0 \pm 0.14$ &  $2.5^{+0.19}_{-0.16}$ &    $314^{+53}_{-99}$ &      DH2015 \\
+  HIP 77336 &    $8917 \pm 303$ &  $4.0 \pm 0.14$ &  $2.9^{+0.23}_{-0.20}$ &    $404^{+73}_{-70}$ &      DH2015 \\
+  HIP 77516 &    $9250 \pm 300$ &  $4.0 \pm 0.25$ &  $2.1^{+0.17}_{-0.16}$ &    $74^{+275}_{-64}$ &  This Study \\
+  HIP 78820 &  $24062 \pm 1000$ &  $3.9 \pm 0.25$ &  $9.2^{+0.51}_{-0.64}$ &        $9^{+6}_{-4}$ &  This Study \\
+  HIP 78821 &    $7250 \pm 300$ &  $4.0 \pm 0.25$ &  $9.1^{+0.65}_{-0.96}$ &        $8^{+6}_{-3}$ &  This Study \\
+  HIP 79199 &  $12500 \pm 1000$ &  $4.5 \pm 0.25$ &  $3.0^{+0.42}_{-0.39}$ &     $23^{+55}_{-16}$ &  This Study \\
+  HIP 79404 &  $21667 \pm 1000$ &  $4.5 \pm 0.25$ &  $7.6^{+0.75}_{-0.69}$ &        $8^{+6}_{-3}$ &  This Study \\
+  HIP 80460 &    $7810 \pm 266$ &  $3.7 \pm 0.14$ &  $1.7^{+0.11}_{-0.08}$ &  $783^{+232}_{-394}$ &      DH2015 \\
+  HIP 82673 &  $11750 \pm 1000$ &  $3.5 \pm 0.25$ &  $3.4^{+0.65}_{-0.57}$ &    $171^{+73}_{-64}$ &  This Study \\
+  HIP 84606 &    $9702 \pm 330$ &  $4.0 \pm 0.14$ &  $2.1^{+0.10}_{-0.09}$ &   $154^{+137}_{-99}$ &      DH2015 \\
+  HIP 85379 &    $8250 \pm 300$ &  $3.5 \pm 0.25$ &  $2.1^{+0.37}_{-0.34}$ &  $550^{+154}_{-260}$ &  This Study \\
+  HIP 85998 &    $8812 \pm 300$ &  $4.0 \pm 0.25$ &  $1.9^{+0.16}_{-0.13}$ &    $95^{+332}_{-84}$ &  This Study \\
+  HIP 88116 &    $9750 \pm 300$ &  $3.5 \pm 0.25$ &  $2.7^{+0.43}_{-0.39}$ &   $305^{+68}_{-150}$ &  This Study \\
+  HIP 88818 &    $9162 \pm 312$ &  $4.3 \pm 0.14$ &  $2.7^{+0.24}_{-0.23}$ &    $441^{+86}_{-72}$ &      DH2015 \\
+  HIP 88817 &    $9162 \pm 312$ &  $4.3 \pm 0.14$ &  $2.1^{+0.16}_{-0.12}$ &   $480^{+84}_{-168}$ &      DH2015 \\
+  HIP 91118 &    $9500 \pm 300$ &  $4.0 \pm 0.25$ &  $2.1^{+0.19}_{-0.15}$ &    $70^{+244}_{-60}$ &  This Study \\
+  HIP 93805 &   $11962 \pm 407$ &  $4.2 \pm 0.14$ &  $3.5^{+0.32}_{-0.26}$ &    $194^{+19}_{-21}$ &      DH2015 \\
+ HIP 100221 &    $9750 \pm 300$ &  $4.5 \pm 0.25$ &  $2.2^{+0.15}_{-0.15}$ &    $34^{+110}_{-26}$ &  This Study \\
+ HIP 100907 &    $9042 \pm 307$ &  $4.0 \pm 0.14$ &  $2.1^{+0.16}_{-0.13}$ &  $512^{+100}_{-168}$ &      DH2015 \\
+ HIP 103298 &    $9093 \pm 309$ &  $4.1 \pm 0.14$ &  $2.0^{+0.13}_{-0.11}$ &  $399^{+146}_{-209}$ &      DH2015 \\
+ HIP 109139 &   $12641 \pm 430$ &  $4.3 \pm 0.14$ &  $3.2^{+0.20}_{-0.16}$ &    $122^{+38}_{-61}$ &      DH2015 \\
+ HIP 109521 &    $8420 \pm 286$ &  $4.2 \pm 0.14$ &  $2.0^{+0.19}_{-0.16}$ &  $728^{+109}_{-104}$ &      DH2015 \\
+ HIP 115115 &   $10671 \pm 363$ &  $4.2 \pm 0.14$ &  $2.6^{+0.19}_{-0.16}$ &    $284^{+38}_{-81}$ &      DH2015 \\
+\label{tab:primary}
+\end{longtable*}
+
 \newpage

### 2016-01-26 paper/ms.tex
Added a few columns to the companion table
Added component and Nobs columns to companions table

@@
 
+As part of the follow-up effort, we used the NIRI instrument behind the Altair adaptive optics system at the Gemini North Telescope.
+We obtained 25 images in 5 dithering positions in the K-continuum band centered on $2.2718\ \mu m$, with a variety of exposure times and dates listed in Table \ref{tab:imaging_obs}.
+Because the targets are all extremely bright, we used the high read noise and high flux detector settings to allow for very short co-add exposure times.
+We reduced the data using the Gemini set of IRAF[TODO: Add iraf footnote] tasks, which include steps for nonlinearity correction, flat-fielding, sky subtraction, and co-addition of the dither frames.
+
 TODO: MAKE THE SPECTRA AVAILABLE SOMEHOW...
-
-TODO: Describe imaging observations (band, observation time, etc). Add a table for this!
 
@@
   HIP 118243 &            B1V &     23:59:0.54 &   +55:45:17.74 &  6945.73 &     IGRINS &      224 &     370 \\
-  HIP 118243 &            B1V &     23:59:0.54 &   +55:45:17.74 &  6583.74 &       TS23 &      351 &    1760 \\
+  HIP 118243 &            B1V &     23:59:0.54 &   +55:45:17.74 &  6583.74 &       TS23 &      351 &    1760
 \label{tab:observations}
@@
 
-\begin{longtable*}{|l|lrrll|}
-\hline
-       star &      $T_\mathrm{eff}$ &   $v\sin{i}$ &  [Fe/H] &   Isochrone Mass &   Spectral Type Mass \\
-\hline
-\endhead
-\hline
-\multicolumn{3}{r}{{Continued on next page}} \\
-\endfoot
+\begin{deluxetable}{|l|lll|}
+\tabletypesize{\small}
+\tablewidth{0pt}
+\tablecaption{NIRI Observation log}
+\tablehead{
+       \colhead{star} &  \colhead{Kmag} &        \colhead{date} & \colhead{Exposure}
+       }
 
-\hline
-\endlastfoot
-   HIP 2548 &  $5732 \pm 112$ &      30 &    -0.5 &  $1.0^{+0.06}_{-0.04}$ &  $1.0^{+0.04}_{-0.03}$ \\
-   HIP 3478 &  $5524 \pm 150$ &       5 &    -0.5 &  $1.1^{+0.28}_{-0.13}$ &  $1.0^{+0.03}_{-0.04}$ \\
-   HIP 5310 &  $3343 \pm 154$ &      30 &     0.0 &  $0.3^{+0.13}_{-0.08}$ &  $0.4^{+0.12}_{-0.12}$ \\
-     HR 545 &   $4312 \pm 87$ &       5 &    -0.5 &  $0.8^{+0.11}_{-0.10}$ &  $0.7^{+0.01}_{-0.02}$ \\
-     HR 604 &  $4736 \pm 150$ &       5 &     0.5 &    $nan^{+nan}_{-nan}$ &  $0.8^{+0.02}_{-0.02}$ \\
-  HIP 10732 &  $5578 \pm 109$ &       5 &     0.0 &  $1.0^{+0.29}_{-0.04}$ &  $1.0^{+0.02}_{-0.04}$ \\
-  HIP 12332 &  $5551 \pm 107$ &      10 &     0.0 &    $nan^{+nan}_{-nan}$ &  $1.0^{+0.01}_{-0.04}$ \\
-  HIP 12706 &  $6051 \pm 107$ &      10 &     0.0 &  $1.1^{+0.03}_{-0.03}$ &  $1.1^{+0.04}_{-0.05}$ \\
-  HIP 13165 &  $5773 \pm 163$ &       5 &    -0.5 &  $1.1^{+0.31}_{-0.08}$ &  $1.0^{+0.10}_{-0.03}$ \\
-  HIP 13327 &  $5524 \pm 150$ &       5 &    -0.5 &  $1.2^{+0.20}_{-0.21}$ &  $1.0^{+0.03}_{-0.04}$ \\
-  HIP 14576 &  $6980 \pm 103$ &      10 &     0.0 &  $1.4^{+0.03}_{-0.03}$ &  $1.5^{+0.05}_{-0.03}$ \\
-  HIP 14764 &  $5601 \pm 108$ &      30 &     0.5 &    $nan^{+nan}_{-nan}$ &  $1.0^{+0.03}_{-0.03}$ \\
-  HIP 16244 &  $5592 \pm 107$ &       5 &    -0.5 &  $1.2^{+0.20}_{-0.22}$ &  $1.0^{+0.03}_{-0.03}$ \\
-  HIP 16340 &  $6214 \pm 150$ &       5 &    -0.5 &  $1.2^{+0.29}_{-0.07}$ &  $1.2^{+0.06}_{-0.05}$ \\
-  HIP 16611 &  $5476 \pm 154$ &       1 &     0.5 &  $0.9^{+0.04}_{-0.04}$ &  $0.9^{+0.04}_{-0.03}$ \\
-  HIP 17563 &  $8574 \pm 147$ &       5 &     0.5 &  $1.9^{+0.25}_{-0.11}$ &  $2.0^{+0.05}_{-0.06}$ \\
-  HIP 18396 &  $4492 \pm 162$ &      30 &    -0.5 &  $0.9^{+0.10}_{-0.12}$ &  $0.8^{+0.03}_{-0.02}$ \\
-  HIP 18724 &  $6831 \pm 154$ &      20 &     0.0 &  $1.7^{+0.13}_{-0.23}$ &  $1.4^{+0.04}_{-0.04}$ \\
-  HIP 19949 &  $6492 \pm 155$ &      20 &    -0.5 &  $1.3^{+0.06}_{-0.05}$ &  $1.3^{+0.06}_{-0.06}$ \\
-  HIP 20380 &  $6492 \pm 109$ &      20 &    -0.5 &  $1.3^{+0.04}_{-0.04}$ &  $1.3^{+0.03}_{-0.05}$ \\
-  HIP 21589 &  $4562 \pm 154$ &       5 &     0.0 &  $0.7^{+0.04}_{-0.03}$ &  $0.8^{+0.02}_{-0.03}$ \\
-  HIP 22833 &  $4745 \pm 107$ &      10 &     0.0 &  $0.8^{+0.02}_{-0.02}$ &  $0.8^{+0.02}_{-0.01}$ \\
-  HIP 22958 &  $6126 \pm 112$ &      30 &    -0.5 &  $1.4^{+0.22}_{-0.21}$ &  $1.2^{+0.04}_{-0.04}$ \\
-  HIP 23362 &  $6283 \pm 158$ &       5 &    -0.5 &  $1.2^{+0.06}_{-0.05}$ &  $1.2^{+0.07}_{-0.05}$ \\
-  HIP 23916 &  $5450 \pm 158$ &       5 &    -0.5 &  $1.1^{+0.20}_{-0.20}$ &  $0.9^{+0.04}_{-0.03}$ \\
-  HIP 24244 &  $4929 \pm 158$ &       5 &    -0.5 &  $0.8^{+0.04}_{-0.04}$ &  $0.8^{+0.02}_{-0.03}$ \\
-  HIP 24902 &  $5679 \pm 154$ &      30 &     0.0 &  $1.0^{+0.05}_{-0.04}$ &  $1.0^{+0.04}_{-0.03}$ \\
-  HIP 25143 &  $5883 \pm 109$ &      30 &     0.0 &  $1.1^{+0.04}_{-0.03}$ &  $1.1^{+0.05}_{-0.07}$ \\
-  HIP 26126 &   $5841 \pm 91$ &       5 &    -0.5 &  $1.0^{+0.03}_{-0.03}$ &  $1.0^{+0.05}_{-0.04}$ \\
-  HIP 32607 &   $5068 \pm 91$ &       5 &    -0.5 &  $0.8^{+0.02}_{-0.02}$ &  $0.9^{+0.01}_{-0.01}$ \\
-  HIP 37450 &   $nan \pm nan$ & \nodata & \nodata &    $nan^{+nan}_{-nan}$ &    $nan^{+nan}_{-nan}$ \\
-  HIP 38538 &  $6576 \pm 150$ &      30 &    -0.5 &  $1.3^{+0.05}_{-0.05}$ &  $1.3^{+0.10}_{-0.05}$ \\
-  HIP 38593 &  $5398 \pm 112$ &       5 &    -0.5 &  $1.3^{+0.08}_{-0.13}$ &  $0.9^{+0.03}_{-0.03}$ \\
-  HIP 38846 &  $6595 \pm 158$ &      10 &     0.0 &  $1.7^{+0.12}_{-0.21}$ &  $1.3^{+0.09}_{-0.05}$ \\
-  HIP 39847 &  $5750 \pm 107$ &      10 &    -0.5 &  $1.0^{+0.04}_{-0.03}$ &  $1.0^{+0.05}_{-0.03}$ \\
-  HIP 40881 &  $4562 \pm 154$ &      10 &    -0.5 &  $0.8^{+0.18}_{-0.05}$ &  $0.8^{+0.02}_{-0.03}$ \\
-  HIP 42129 &  $5241 \pm 158$ &      10 &    -0.5 &  $1.2^{+0.12}_{-0.18}$ &  $0.9^{+0.04}_{-0.02}$ \\
-  HIP 46283 &   $9268 \pm 85$ &      10 &     0.5 &    $nan^{+nan}_{-nan}$ &  $2.2^{+0.02}_{-0.02}$ \\
-  HIP 51362 &  $5033 \pm 158$ &       5 &    -0.5 &  $0.8^{+0.04}_{-0.04}$ &  $0.8^{+0.02}_{-0.03}$ \\
-  HIP 52678 &  $5033 \pm 112$ &      10 &    -0.5 &  $1.0^{+0.16}_{-0.19}$ &  $0.8^{+0.01}_{-0.02}$ \\
-  HIP 55266 &  $8483 \pm 139$ &      30 &    -0.5 &  $1.8^{+0.06}_{-0.04}$ &  $2.0^{+0.06}_{-0.05}$ \\
-  HIP 63945 &  $7038 \pm 162$ &      10 &    -0.5 &  $1.6^{+0.26}_{-0.16}$ &  $1.5^{+0.08}_{-0.06}$ \\
-  HIP 72154 &  $4918 \pm 162$ &      30 &    -0.5 &  $0.9^{+0.22}_{-0.09}$ &  $0.8^{+0.03}_{-0.03}$ \\
-  HIP 76267 &  $5449 \pm 158$ &       5 &    -0.5 &  $0.9^{+0.04}_{-0.04}$ &  $0.9^{+0.04}_{-0.03}$ \\
-  HIP 77336 &  $6407 \pm 112$ &      20 &     0.0 &  $1.2^{+0.04}_{-0.04}$ &  $1.3^{+0.04}_{-0.05}$ \\
-  HIP 77516 &  $6825 \pm 141$ &       5 &     0.5 &  $1.4^{+0.21}_{-0.06}$ &  $1.4^{+0.03}_{-0.04}$ \\
-  HIP 78820 &  $5658 \pm 158$ &       5 &    -0.5 &  $1.3^{+0.11}_{-0.13}$ &  $1.0^{+0.04}_{-0.04}$ \\
-  HIP 78821 &  $4968 \pm 154$ &      10 &    -0.5 &  $1.1^{+0.09}_{-0.10}$ &  $0.8^{+0.02}_{-0.03}$ \\
-  HIP 79199 &  $4616 \pm 158$ &       5 &    -0.5 &  $0.9^{+0.14}_{-0.14}$ &  $0.8^{+0.02}_{-0.03}$ \\
-  HIP 79404 &  $4773 \pm 112$ &      10 &    -0.5 &  $1.1^{+0.07}_{-0.08}$ &  $0.8^{+0.02}_{-0.01}$ \\
-  HIP 80460 &  $6391 \pm 155$ &      10 &     0.0 &  $1.2^{+0.06}_{-0.05}$ &  $1.3^{+0.06}_{-0.06}$ \\
-  HIP 82673 &  $4668 \pm 112$ &       5 &     0.5 &  $0.8^{+0.03}_{-0.03}$ &  $0.8^{+0.01}_{-0.02}$ \\
-  HIP 84606 &  $5476 \pm 154$ &      10 &    -0.5 &  $0.9^{+0.05}_{-0.04}$ &  $0.9^{+0.04}_{-0.03}$ \\
-  HIP 85379 &  $7590 \pm 151$ &      20 &     0.0 &    $nan^{+nan}_{-nan}$ &  $1.7^{+0.05}_{-0.03}$ \\
-  HIP 85998 &   $5460 \pm 91$ &       1 &    -0.5 &  $1.0^{+0.28}_{-0.03}$ &  $0.9^{+0.04}_{-0.01}$ \\
-  HIP 88116 &  $5293 \pm 112$ &       5 &     0.0 &  $0.9^{+0.03}_{-0.03}$ &  $0.9^{+0.02}_{-0.03}$ \\
-  HIP 88818 &   $5296 \pm 91$ &      20 &    -0.5 &  $0.9^{+0.02}_{-0.02}$ &  $0.9^{+0.02}_{-0.03}$ \\
-  HIP 88817 &  $3647 \pm 154$ &      20 &     0.0 &  $0.5^{+0.07}_{-0.10}$ &  $0.5^{+0.03}_{-0.05}$ \\
-  HIP 91118 &  $6492 \pm 155$ &      10 &    -0.5 &  $1.3^{+0.26}_{-0.07}$ &  $1.3^{+0.06}_{-0.06}$ \\
-  HIP 93805 &  $4054 \pm 109$ &       5 &    -0.5 &  $0.6^{+0.03}_{-0.03}$ &  $0.6^{+0.04}_{-0.02}$ \\
-  HIP 96840 &  $9942 \pm 152$ &      10 &     0.0 &    $nan^{+nan}_{-nan}$ &  $2.3^{+0.03}_{-0.01}$ \\
- HIP 100221 &  $5273 \pm 154$ &      20 &    -0.5 &  $0.9^{+0.29}_{-0.07}$ &  $0.9^{+0.04}_{-0.03}$ \\
- HIP 100907 &  $5222 \pm 109$ &      10 &     0.0 &  $0.9^{+0.03}_{-0.03}$ &  $0.9^{+0.04}_{-0.02}$ \\
- HIP 103298 &   $4615 \pm 90$ &       5 &    -0.5 &  $0.7^{+0.02}_{-0.02}$ &  $0.8^{+0.01}_{-0.02}$ \\
- HIP 109139 &  $5710 \pm 112$ &      20 &    -0.5 &  $1.0^{+0.04}_{-0.03}$ &  $1.0^{+0.03}_{-0.03}$ \\
- HIP 109521 &   $4412 \pm 87$ &      10 &     0.0 &  $0.7^{+0.02}_{-0.02}$ &  $0.7^{+0.01}_{-0.01}$ \\
- HIP 115115 &   $4943 \pm 91$ &       5 &    -0.5 &  $0.8^{+0.02}_{-0.02}$ &  $0.8^{+0.02}_{-0.02}$ \\
+\startdata
+  HIP 22833 &  4.83 &  2015-03-29 &   50x0.3 \\
+  HIP 22958 &  5.79 &  2015-10-19 &   52x0.4 \\
+  HIP 23916 &  5.98 &  2015-04-05 &   18x1.1 \\
+  HIP 26093 &  5.96 &  2015-03-23 &   33x0.6 \\
+  HIP 26126 &  5.07 &  2015-03-29 &   40x0.4 \\
+  HIP 29735 &  5.10 &  2015-03-22 &   83x0.2 \\
+  HIP 31278 &  5.46 &  2015-03-28 &   29x0.6 \\
+  HIP 38538 &  4.66 &  2015-10-19 &   75x0.2 \\
+  HIP 39847 &  4.66 &  2015-03-27 &   50x0.3 \\
+  HIP 75178 &  5.49 &  2015-03-24 &   29x0.6 \\
+  HIP 88116 &  4.47 &  2015-03-22 &   50x0.3 \\
+  HIP 91118 &  5.67 &  2015-10-16 &   43x0.4 \\
+ HIP 100221 &  5.70 &  2015-10-18 &   26x0.7 \\
+ HIP 100907 &  5.41 &  2015-10-16 &   43x0.4 \\
+ HIP 101909 &  $6.47^{\dagger}$ &  2015-10-16 &   39x0.5 \\
+ HIP 109139 &  4.40 &  2015-04-26 &   50x0.3 \\
+ HIP 109521 &  4.96 &  2015-04-25 &   40x0.4 \\
+ HIP 115115 &  4.96 &  2015-10-18 &   40x0.4 \\
+ HIP 118243 &  $5.87^{\dagger}$ &  2015-07-23 &   58x0.3 \\
+\enddata
+\tablecomments{$\dagger$: There is no K-magnitude tabulated in the Simbad Database. The value quoted here is estimated from the spectral type of the star and its V-band magnitude.}
+\label{tab:imaging_obs}
+\end{deluxetable}
+
+\clearpage
+\newpage
+
+\LongTables
+\begin{deluxetable*}{|l|rrlrrrll|}
+\tabletypesize{\small}
+\tablewidth{0pt}
+\tablecaption{Companion Detections}
+\tablehead{
+       \colhead{star} & \colhead{component} & \colhead{$N_\mathrm{obs}$}   &   \colhead{$T_\mathrm{eff}$} &   \colhead{$v\sin{i}$} &  \colhead{[Fe/H]} & \colhead{$\Delta K$} &   \colhead{Isochrone Mass} &   \colhead{Spectral Type Mass}
+       }
+
+\startdata
+   HIP 2548 & Aa,Ab &     2 &  $5732 \pm 112$ &      30 &    -0.5 &          0 &  $1.0^{+0.06}_{-0.04}$ &  $1.0^{+0.04}_{-0.03}$ \\
+   HIP 5310 & AB &     1 &  $3343 \pm 154$ &      30 &     0.0 &          0 &  $0.3^{+0.13}_{-0.08}$ &  $0.4^{+0.12}_{-0.12}$ \\
+     HR 545 & Aa,Ab$^{\dagger}$ &     3 &   $4312 \pm 87$ &       5 &    -0.5 &          0 &  $0.8^{+0.11}_{-0.10}$ &  $0.7^{+0.01}_{-0.02}$ \\
+     HR 604 & AB &     1 &  $4736 \pm 150$ &       5 &     0.5 &          0 &    $nan^{+nan}_{-nan}$ &  $0.8^{+0.02}_{-0.02}$ \\
+  HIP 10732 & AB$^{\dagger}$ &     2 &  $5578 \pm 109$ &       5 &     0.0 &          0 &  $1.0^{+0.29}_{-0.04}$ &  $1.0^{+0.02}_{-0.04}$ \\
+  HIP 12332 & AB$^{\dagger}$ &     2 &  $5551 \pm 107$ &      10 &     0.0 &          0 &    $nan^{+nan}_{-nan}$ &  $1.0^{+0.01}_{-0.04}$ \\
+  HIP 12706 & AB &     2 &  $6051 \pm 107$ &      10 &     0.0 &          0 &  $1.1^{+0.03}_{-0.03}$ &  $1.1^{+0.04}_{-0.05}$ \\
+  HIP 13165 & AB? &     1 &  $5773 \pm 163$ &       5 &    -0.5 &          0 &  $1.1^{+0.31}_{-0.08}$ &  $1.0^{+0.10}_{-0.03}$ \\
+  HIP 13327 & AB$^{\dagger}$ &     1 &  $5524 \pm 150$ &       5 &    -0.5 &          0 &  $1.2^{+0.20}_{-0.21}$ &  $1.0^{+0.03}_{-0.04}$ \\
+  HIP 14576 & Aa,Ab &     2 &  $6980 \pm 103$ &      10 &     0.0 &          0 &  $1.4^{+0.03}_{-0.03}$ &  $1.5^{+0.05}_{-0.03}$ \\
+  HIP 14764 & AB$^{\dagger}$ &     2 &  $5601 \pm 108$ &      30 &     0.5 &          0 &    $nan^{+nan}_{-nan}$ &  $1.0^{+0.03}_{-0.03}$ \\
+  HIP 16244 & AB &     2 &  $5592 \pm 107$ &       5 &    -0.5 &          0 &  $1.2^{+0.20}_{-0.22}$ &  $1.0^{+0.03}_{-0.03}$ \\
+  HIP 16340 & AB$^{\dagger}$ &     1 &  $6214 \pm 150$ &       5 &    -0.5 &          0 &  $1.2^{+0.29}_{-0.07}$ &  $1.2^{+0.06}_{-0.05}$ \\
+  HIP 16611 & AB &     1 &  $5476 \pm 154$ &       1 &     0.5 &          0 &  $0.9^{+0.04}_{-0.04}$ &  $0.9^{+0.04}_{-0.03}$ \\
+  HIP 17563 & AB &     1 &  $8574 \pm 147$ &       5 &     0.5 &          0 &  $1.9^{+0.25}_{-0.11}$ &  $2.0^{+0.05}_{-0.06}$ \\
+  HIP 18724 & AB &     1 &  $6831 \pm 154$ &      20 &     0.0 &          0 &  $1.7^{+0.13}_{-0.23}$ &  $1.4^{+0.04}_{-0.04}$ \\
+  HIP 19949 & AB$^{\dagger}$ &     1 &  $6492 \pm 155$ &      20 &    -0.5 &          0 &  $1.3^{+0.06}_{-0.05}$ &  $1.3^{+0.06}_{-0.06}$ \\
+  HIP 20380 & AB$^{\dagger}$ &     2 &  $6492 \pm 109$ &      20 &    -0.5 &          0 &  $1.3^{+0.04}_{-0.04}$ &  $1.3^{+0.03}_{-0.05}$ \\
+  HIP 21589 & Aa,Ab? &     1? &  $4562 \pm 154$ &       5 &     0.0 &          0 &  $0.7^{+0.04}_{-0.03}$ &  $0.8^{+0.02}_{-0.03}$ \\
+  HIP 22833 & AB &     2 &  $4745 \pm 107$ &      10 &     0.0 &          0 &  $0.8^{+0.02}_{-0.02}$ &  $0.8^{+0.02}_{-0.01}$ \\
+  HIP 22958 & Aa,Ab &     2 &  $6126 \pm 112$ &      30 &    -0.5 &          0 &  $1.4^{+0.22}_{-0.21}$ &  $1.2^{+0.04}_{-0.04}$ \\
+  HIP 23362 & AB$^{\dagger}$ &     1 &  $6283 \pm 158$ &       5 &    -0.5 &          0 &  $1.2^{+0.06}_{-0.05}$ &  $1.2^{+0.07}_{-0.05}$ \\
+  HIP 23916 & Aa,Ab$^{\dagger}$ &     1 &  $5450 \pm 158$ &       5 &    -0.5 &          0 &  $1.1^{+0.20}_{-0.20}$ &  $0.9^{+0.04}_{-0.03}$ \\
+  HIP 24902 & AB &     1 &  $5679 \pm 154$ &      30 &     0.0 &          0 &  $1.0^{+0.05}_{-0.04}$ &  $1.0^{+0.04}_{-0.03}$ \\
+  HIP 25143 & AB$^{\dagger}$ &     2 &  $5883 \pm 109$ &      30 &     0.0 &          0 &  $1.1^{+0.04}_{-0.03}$ &  $1.1^{+0.05}_{-0.07}$ \\
+  HIP 26126 & AB? &     3 &   $5841 \pm 91$ &       5 &    -0.5 &          0 &  $1.0^{+0.03}_{-0.03}$ &  $1.0^{+0.05}_{-0.04}$ \\
+  HIP 32607 & AB$^{\dagger}$ &     3 &   $5068 \pm 91$ &       5 &    -0.5 &          0 &  $0.8^{+0.02}_{-0.02}$ &  $0.9^{+0.01}_{-0.01}$ \\
+  HIP 37450 & AB$^{\dagger}$ &     1 &   $nan \pm nan$ & \nodata & \nodata &          0 &    $nan^{+nan}_{-nan}$ &    $nan^{+nan}_{-nan}$ \\
+  HIP 38593 & AB$^{\dagger}$ &     2 &  $5398 \pm 112$ &       5 &    -0.5 &          0 &  $1.3^{+0.08}_{-0.13}$ &  $0.9^{+0.03}_{-0.03}$ \\
+  HIP 38846 & AB$^{\dagger}$ &     1 &  $6595 \pm 158$ &      10 &     0.0 &          0 &  $1.7^{+0.12}_{-0.21}$ &  $1.3^{+0.09}_{-0.05}$ \\
+  HIP 39847 & Aa,Ab$^{\dagger}$ &     2 &  $5750 \pm 107$ &      10 &    -0.5 &          0 &  $1.0^{+0.04}_{-0.03}$ &  $1.0^{+0.05}_{-0.03}$ \\
+  HIP 40881 & AB$^{\dagger}$ &     1 &  $4562 \pm 154$ &      10 &    -0.5 &          0 &  $0.8^{+0.18}_{-0.05}$ &  $0.8^{+0.02}_{-0.03}$ \\
+  HIP 42129 & AB &     1 &  $5241 \pm 158$ &      10 &    -0.5 &          0 &  $1.2^{+0.12}_{-0.18}$ &  $0.9^{+0.04}_{-0.02}$ \\
+  HIP 46283 & AB? &     3 &   $9268 \pm 85$ &      10 &     0.5 &          0 &    $nan^{+nan}_{-nan}$ &  $2.2^{+0.02}_{-0.02}$ \\
+  HIP 55266 & AB &     1 &  $8483 \pm 139$ &      30 &    -0.5 &          0 &  $1.8^{+0.06}_{-0.04}$ &  $2.0^{+0.06}_{-0.05}$ \\
+  HIP 63945 & Aa,Ab or AC? &     1 &  $7038 \pm 162$ &      10 &    -0.5 &          0 &  $1.6^{+0.26}_{-0.16}$ &  $1.5^{+0.08}_{-0.06}$ \\
+  HIP 72154 & AB$^{\dagger}$ &     1 &  $4918 \pm 162$ &      30 &    -0.5 &          0 &  $0.9^{+0.22}_{-0.09}$ &  $0.8^{+0.03}_{-0.03}$ \\
+  HIP 76267 & AB &     1 &  $5449 \pm 158$ &       5 &    -0.5 &          0 &  $0.9^{+0.04}_{-0.04}$ &  $0.9^{+0.04}_{-0.03}$ \\
+  HIP 77336 & AB$^{\dagger}$ &     2 &  $6407 \pm 112$ &      20 &     0.0 &          0 &  $1.2^{+0.04}_{-0.04}$ &  $1.3^{+0.04}_{-0.05}$ \\
+  HIP 77516 & AB &     1 &  $6825 \pm 141$ &       5 &     0.5 &          0 &  $1.4^{+0.21}_{-0.06}$ &  $1.4^{+0.03}_{-0.04}$ \\
+  HIP 78820 & AB &     1 &  $5658 \pm 158$ &       5 &    -0.5 &          0 &  $1.3^{+0.11}_{-0.13}$ &  $1.0^{+0.04}_{-0.04}$ \\
+  HIP 79199 & AB &     1 &  $4616 \pm 158$ &       5 &    -0.5 &          0 &  $0.9^{+0.14}_{-0.14}$ &  $0.8^{+0.02}_{-0.03}$ \\
+  HIP 79404 & AB$^{\dagger}$ &     2 &  $4773 \pm 112$ &      10 &    -0.5 &          0 &  $1.1^{+0.07}_{-0.08}$ &  $0.8^{+0.02}_{-0.01}$ \\
+  HIP 80460 & AB &     1 &  $6391 \pm 155$ &      10 &     0.0 &          0 &  $1.2^{+0.06}_{-0.05}$ &  $1.3^{+0.06}_{-0.06}$ \\
+  HIP 82673 & AB$^{\dagger}$ &     2 &  $4668 \pm 112$ &       5 &     0.5 &          0 &  $0.8^{+0.03}_{-0.03}$ &  $0.8^{+0.01}_{-0.02}$ \\
+  HIP 84606 & AB &     1 &  $5476 \pm 154$ &      10 &    -0.5 &          0 &  $0.9^{+0.05}_{-0.04}$ &  $0.9^{+0.04}_{-0.03}$ \\
+  HIP 88116 & AB$^{\dagger}$ &     2 &  $5293 \pm 112$ &       5 &     0.0 &          0 &  $0.9^{+0.03}_{-0.03}$ &  $0.9^{+0.02}_{-0.03}$ \\
+  HIP 88818 & Aa,Ab &     3 &   $5296 \pm 91$ &      20 &    -0.5 &          0 &  $0.9^{+0.02}_{-0.02}$ &  $0.9^{+0.02}_{-0.03}$ \\
+  HIP 88817 & Aa,Ab &     1 &  $3647 \pm 154$ &      20 &     0.0 &          0 &  $0.5^{+0.07}_{-0.10}$ &  $0.5^{+0.03}_{-0.05}$ \\
+  HIP 91118 & AB &     1 &  $6492 \pm 155$ &      10 &    -0.5 &          0 &  $1.3^{+0.26}_{-0.07}$ &  $1.3^{+0.06}_{-0.06}$ \\
+  HIP 93805 & Aa,Ab$^{\dagger}$ &     2 &  $4054 \pm 109$ &       5 &    -0.5 &          0 &  $0.6^{+0.03}_{-0.03}$ &  $0.6^{+0.04}_{-0.02}$ \\
+  HIP 96840 & AB &     1 &  $9942 \pm 152$ &      10 &     0.0 &          0 &    $nan^{+nan}_{-nan}$ &  $2.3^{+0.03}_{-0.01}$ \\
+ HIP 100221 & AB &     1 &  $5273 \pm 154$ &      20 &    -0.5 &          0 &  $0.9^{+0.29}_{-0.07}$ &  $0.9^{+0.04}_{-0.03}$ \\
+ HIP 100907 & AB$^{\dagger}$ &     2 &  $5222 \pm 109$ &      10 &     0.0 &          0 &  $0.9^{+0.03}_{-0.03}$ &  $0.9^{+0.04}_{-0.02}$ \\
+ HIP 103298 & Aa,Ab &     3 &   $4615 \pm 90$ &       5 &    -0.5 &          0 &  $0.7^{+0.02}_{-0.02}$ &  $0.8^{+0.01}_{-0.02}$ \\
+ HIP 109139 & AB &     2 &  $5710 \pm 112$ &      20 &    -0.5 &          0 &  $1.0^{+0.04}_{-0.03}$ &  $1.0^{+0.03}_{-0.03}$ \\
+ HIP 109521 & Aa,Ab$^{\dagger}$ &     3 &   $4412 \pm 87$ &      10 &     0.0 &          0 &  $0.7^{+0.02}_{-0.02}$ &  $0.7^{+0.01}_{-0.01}$ \\
+ HIP 115115 & AB &     3 &   $4943 \pm 91$ &       5 &    -0.5 &          0 &  $0.8^{+0.02}_{-0.02}$ &  $0.8^{+0.02}_{-0.02}$
+
+ \enddata
+
+ \tablecomments{$\dagger$: Newly discovered companions.}
  \label{tab:companions}
-\end{longtable*}
+\end{deluxetable*}
+
+\clearpage
+\newpage
 

### 2016-01-26 paper/ms.tex
Added first part of completeness section.

@@
 Imperfect stellar models cause a bias between the true companion temperature and the temperature of the Phoenix model which produces the largest CCF peak.
-This bias is most pronounced at low temperatures, where molecular absorption becomes important.
-We correct for it by applying the calibrations developed in \citet{Gullikson2016}.
+This bias is most pronounced at low temperatures, where the difficult-to-model molecular absorption becomes important.
+We correct for the bias by applying the calibrations developed in \citet{Gullikson2016}.
 These calibrations are only valid for companions with $3000 < T_\mathrm{eff} < 7000 K$; for detections at hotter temperatures we assume that the temperature which produces the maximum CCF peak is an \emph{unbiased} estimator of the true companion temperature.
@@
 The $v\sin{i}$ and metallicity values do not have uncertainties and should only be taken as a rough estimate of the true value.
-TODO: Add columns to Table \ref{tab:companions} for the WDS designation if known, and mark the ones that are new.
-Also include imaging data (delta-magnitude) when I have it.
-Finally, include a column for the number of detections that went into the average.
 
@@
 In most cases, there is a clear shift in the radial velocity of the companion, indicating that it is orbiting the target star and is not a foreground or background companion.
-In addition we obtained Gemini/NIRI adaptive optics imaging data for some of the northern companions.
+In addition we obtained Gemini/NIRI adaptive optics imaging data for some of the northern companions, and were able to resolve 7 of the companions.
 
@@
 \label{sec:completeness}
+
+The detectability of a companion mostly depends on its temperature: cooler companions emit much less light and so are increasingly lost in the Poisson noise from the primary star spectrum.
+A companion with a high rotation rate is also more difficult to detect because the cross-correlation function gets most of its power from narrow spectral lines.
+To quantify the detection rate as a function of companion temperature and $v\sin{i}$, we performed a series of injection/recovery experiments.
+
+We started by creating synthetic binary star observations from each of our spectra.
+We made two distinct grids of companion stars: a low temperature grid spanning $3000\ K < T_\mathrm{eff} < 6500\ K$ and $0\ \mathrm{km\ s}^{-1} < v\sin{i} < 50\ \mathrm{km\ s}^{-1}$, and a high temperature grid spanning $7000\ K < T_\mathrm{eff} < 12000\ K$ and $100\ \mathrm{km\ s}^{-1} < v\sin{i} < 250\ \mathrm{km\ s}^{-1}$.
+The low temperature grid has a temperature spacing of $100$ K and a $v\sin{i}$ spacing of $10 \mathrm{km\ s}^{-1}$; the high temperature grid has a temperature spacing of $1000$ K and a $v\sin{i}$ spacing of $50 \mathrm{km\ s}^{-1}$.
+For each grid point, we added a solar metallicity Phoenix model spectrum to the observed data after scaling to replicate the expected flux between a main sequence companion of the model temperature and the known target star spectral type.
+If the target star had known companions within $3''$, we included the expected flux from the companion when computing the flux ratio.
+We repeated each grid point at different radial velocities spanning $-400\ \mathrm{km\ s}^{-1} < v < 400\ \mathrm{km\ s}^{-1}$ in $50\ \mathrm{km\ s}^{-1}$ steps to estimate a probability of detection at each point.
+
+Next, we cross correlated all of the synthetic observations against the Phoenix model template that was used to construct them.
+We counted the companion as detected if the highest point in the resulting CCF was found at the correct radial velocity.
+We then combined all of the radial velocity points for each grid point to estimate a probability of detection at that grid point:
+
+\begin{equation}
+P(\mathrm{detection}) = \frac{N_\mathrm{detected}}{N_\mathrm{rv}}
+\end{equation}
+where $N_\mathrm{rv} = 17$ is the number of radial velocity trial points.
+
+Finally, we interpolated between the grid points using a linear radial basis function interpolator.
+In order to extrapolate from our grids to estimate the detection rate at high temperature and low $v\sin{i}$ and at low temperature and high $v\sin{i}$, we made the following assumptions about the shape of the two-dimensional detection rate surface: First, we assumed that if all companions are detected at temperature $T=6500$ K and rotation speed $v\sin{i}$, then all companions with the same $v\sin{i}$ and larger temperature will also be detected.
+Likewise, we assume that if no companions are detected at temperature $T$ and rotation speed $v\sin{i} = 50\ \mathrm{km\ s}^{-1}$, we assume that no companions will be detected at the same temperature and faster rotation speeds.
+We show a typical detection rate surface in Figure \ref{fig:detrate_2d} to illustrate both the shape of the surface and the grid we interpolate from.
+The figure shows a clear diagonal dividing line between hot, slow rotators that are always detected and cool, fast rotators that never are.
+Additionally the figure shows that very fast rotators are never detected, regardless of their temperature, because the signal is completely removed when we high-pass filter the data (see Section \ref{sec:companions}).
+
+\begin{figure}
+\includegraphics[width=\columnwidth]{HIP_24244_20130919.pdf}
+\caption{Detection rate as a function of companion temperature and $v\sin{i}$ for HIP 24244.
+All companions that are shaded yellow are detectable, while companions in the purple region are never detectable.
+The grids of squares in the lower left and upper right show the low temperature and high temperature grid points we used in the sensitivity analysis.
+The remaining squares come from assumptions about the shape of the detection rate surface and allow us to fully interpolate (see text for details).}
+\label{fig:detrate_2d}
+\end{figure}
 
@@
 
-\begin{deluxetable}{|l|lll|}
+\begin{deluxetable}{|l|llllll|}
 \tabletypesize{\small}
@@
 \tablehead{
-       \colhead{star} &  \colhead{Kmag} &        \colhead{date} & \colhead{Exposure}
+       \colhead{star} &  \colhead{Kmag} &   \colhead{date} & \colhead{Exposure} & \colhead{$\rho$} & \colhead{$\theta$} & \colhead{$\Delta \mathrm{K_c}$}
        }
@@
 \startdata
-  HIP 22833 &  4.83 &  2015-03-29 &   50x0.3 \\
-  HIP 22958 &  5.79 &  2015-10-19 &   52x0.4 \\
-  HIP 23916 &  5.98 &  2015-04-05 &   18x1.1 \\
-  HIP 26093 &  5.96 &  2015-03-23 &   33x0.6 \\
-  HIP 26126 &  5.07 &  2015-03-29 &   40x0.4 \\
-  HIP 29735 &  5.10 &  2015-03-22 &   83x0.2 \\
-  HIP 31278 &  5.46 &  2015-03-28 &   29x0.6 \\
-  HIP 38538 &  4.66 &  2015-10-19 &   75x0.2 \\
-  HIP 39847 &  4.66 &  2015-03-27 &   50x0.3 \\
-  HIP 75178 &  5.49 &  2015-03-24 &   29x0.6 \\
-  HIP 88116 &  4.47 &  2015-03-22 &   50x0.3 \\
-  HIP 91118 &  5.67 &  2015-10-16 &   43x0.4 \\
- HIP 100221 &  5.70 &  2015-10-18 &   26x0.7 \\
- HIP 100907 &  5.41 &  2015-10-16 &   43x0.4 \\
- HIP 101909 &  $6.47^{\dagger}$ &  2015-10-16 &   39x0.5 \\
- HIP 109139 &  4.40 &  2015-04-26 &   50x0.3 \\
- HIP 109521 &  4.96 &  2015-04-25 &   40x0.4 \\
- HIP 115115 &  4.96 &  2015-10-18 &   40x0.4 \\
- HIP 118243 &  $5.87^{\dagger}$ &  2015-07-23 &   58x0.3 \\
+  HIP 22833 &  4.83 &  2015-03-29 &   50x0.3 & $0.352 +/- 0.003$ & $14.1 \pm 0.7$ & $3.04 \pm 0.06$ \\
+  HIP 22958 &  5.79 &  2015-10-19 &   52x0.4 & $0.445 +/- 0.003$ & $65.0 \pm 0.3$ & $2.57 \pm 0.05$ \\
+  HIP 23916 &  5.98 &  2015-04-05 &   18x1.1 & \nodata & \nodata & \nodata \\
+  HIP 26093 &  5.96 &  2015-03-23 &   33x0.6 & \nodata & \nodata & \nodata \\
+  HIP 26126 &  5.07 &  2015-03-29 &   40x0.4 & \nodata & \nodata & \nodata \\
+  HIP 29735 &  5.10 &  2015-03-22 &   83x0.2 & \nodata & \nodata & \nodata \\
+  HIP 31278 &  5.46 &  2015-03-28 &   29x0.6 & \nodata & \nodata & \nodata \\
+  HIP 38538 &  4.66 &  2015-10-19 &   75x0.2 & \nodata & \nodata & \nodata \\
+  HIP 39847 &  4.66 &  2015-03-27 &   50x0.3 & \nodata & \nodata & \nodata \\
+  HIP 75178 &  5.49 &  2015-03-24 &   29x0.6 & \nodata & \nodata & \nodata \\
+  HIP 88116 &  4.47 &  2015-03-22 &   50x0.3 & $3.260 +/- 0.001$ & $210.71 \pm 0.02$ & $3.9 \pm 0.4$ \\
+  HIP 91118 &  5.67 &  2015-10-16 &   43x0.4 & $0.1667 +/- 0.0007$ & $41.7 \pm 0.2$ & $1.77 \pm 0.01$ \\
+ HIP 100221 &  5.70 &  2015-10-18 &   26x0.7 & $0.250 +/- 0.002$ & $346.8 \pm 0.92$ & $2.28 \pm 0.04$ \\
+ HIP 100907 &  5.41 &  2015-10-16 &   43x0.4 & $0.463 +/- 0.002$ & $335.4 \pm 0.30$ & $2.91 \pm 0.04$ \\
+ HIP 101909 &  $6.47^{\dagger}$ &  2015-10-16 &   39x0.5 & \nodata & \nodata & \nodata \\
+ HIP 109139 &  4.40 &  2015-04-26 &   50x0.3 & \nodata & \nodata & \nodata \\
+ HIP 109521 &  4.96 &  2015-04-25 &   40x0.4 & \nodata & \nodata & \nodata \\
+ HIP 115115 &  4.96 &  2015-10-18 &   40x0.4 & $1.497 +/- 0.002$ & $313.14 \pm 0.08$ & $2.54 \pm 0.04$ \\
+ HIP 118243 &  $5.87^{\dagger}$ &  2015-07-23 &   58x0.3 & $4.082 +/- 0.002$ & $310.23 \pm 0.03$ & $2.20 \pm 0.03$
 \enddata
-\tablecomments{$\dagger$: There is no K-magnitude tabulated in the Simbad Database. The value quoted here is estimated from the spectral type of the star and its V-band magnitude.}
+\tablecomments{$\dagger$: There is no K-magnitude tabulated in the Simbad Database.
+The value quoted here is estimated from the spectral type of the star and its V-band magnitude.
+TODO: I think my detection in HIP 88116 is too close to be any of the 4 companions in the image (it has a large $\Delta \mathrm{RV}$, and the expected $\Delta \mathrm{K_c}$ is about 2.7, smaller than any of the images).
+What should I report here?}
 \label{tab:imaging_obs}

### 2016-01-26 paper/ms.tex
Wrote initial draft of primary star parameters section.

@@
 \usepackage{subfigure}
+\usepackage{amsmath}
 \usepackage{url}
@@
 In most cases, there is a clear shift in the radial velocity of the companion, indicating that it is orbiting the target star and is not a foreground or background companion.
-In addition we obtained Gemini/NIRI adaptive optics imaging data for some of the northern companions, and were able to resolve 7 of the companions.
+In addition we obtained Gemini/NIRI adaptive optics imaging data for 19 of the northern companions, and were able to resolve 7 of the companions.
+
+\section{Stellar Parameters}
+\label{sec:sp}
+
+In order to convert from companion temperature to mass ratio, we first need an estimate of the primary mass.
+In addition, since the primary stars in our systems are A- or B-type stars with main-sequence lifetimes from $\sim 10 - 1000$ Myr, very late-type companions may still be contracting onto the main sequence and so an age estimate for the system is necessary.
+
+About half of our detections have robust mass and age estimates for the primary stars from Str\"omgren uvby$\beta$ photometry \citep{David2015}.
+For those that do not, we estimate the mass and age of the system as follows.
+We first cross-correlate the data against a grid of Kurucz model spectra [CITE] spanning $7000\ K < T_\mathrm{eff} < 30000\ K$, $3.0 < \log{g} < 4.5$, and $75 < v\sin{i} < 300$.
+For the optical data, we use the blue echelle orders ($\lambda < 5550 \AA$).
+We ignore the strong hydrogren lines in the spectrum, because they span several echelle orders and make continuum normalization very difficult.
+There are sufficient metal lines in the optical spectra that the resulting CCF always has a very strong peak at the radial velocity of the primary star.
+The near-infrared IGRINS spectra do not have enough strong metal lines in their spectrum to justify ignoring the hydrogen lines; we use the subset from $1.51 - 1.73 \micron$ for these spectra.
+We then estimate the temperature and surface gravity of the primary stars from the CCF with the largest peak.
+We assume the following errors on the temperature and surface gravity:
+
+\begin{align}
+ \sigma_T &= \begin{cases}
+      \hfill 300\ K \hfill & T < 10000\ K \\
+      \hfill 1000\ K \hfill & T >= 10000\ K \\
+     \end{cases} \\
+ \sigma_{\log{g}} &= 0.25
+\end{align}
+
+Next, we use Padova stellar evolutionary tracks [CITE] and the isochrones code [CITE] to estimate the mass and age of the system from the measured temperature and $\log{g}$.
+As a consistency check, we also interpolate a table of spectral type relations [CITE mamajek table] to estimate the primary mass from the published spectral types.
+We show the comparison in Figure \ref{fig:prim_mass}.
+We estimate uncertainties in the spectral type mass by assuming a spectral type uncertainty of $\pm 0.5$ spectral types.
+There is excellent agreement between the masses we measure and the spectral type masses.
+
+\begin{figure}
+\includegraphics[width=\columnwidth]{PrimaryMassEstimates.pdf}
+\caption{Comparison of primary star masses derived from our cross-correlation analysis and Padova isochrones [CITE] with those expected from the published spectral type.
+There is excellent agreement between the two measures across the entire range of masses.}
+\label{fig:prim_mass}.
+\end{figure}
 
@@
 
+TODO: Discuss marginalization of vsini.
+
 \begin{figure}
@@
 \end{figure}
-
-\section{Stellar Parameters}
-\label{sec:sp}
 

### 2016-01-26 Priors.py

@@ -10,14 +10,14 @@ import numpy as np
 import os
 import h5py
 from scipy.interpolate import InterpolatedUnivariateSpline as spline
-import SpectralTypeRelations
+from kglib.spectral_type import SpectralTypeRelations
 import pandas as pd
 import Mamajek_Table
-import Feiden
-from Feiden import Feiden_Isochrone
+from kglib.isochrone_helpers import Feiden
+from kglib.isochrone_helpers.Feiden import Feiden_Isochrone
 import scipy.interpolate
 import logging
-import StarData
+from kglib.utils import StarData
 
 
 

### 2016-01-27 paper/ms.tex
Discussed marginalization over vsini

@@
 \begin{figure}
-\includegraphics[width=\columnwidth]{PrimaryMassEstimates.pdf}
+\includegraphics[width=\columnwidth]{PrimaryMassEstimates_log.pdf}
 \caption{Comparison of primary star masses derived from our cross-correlation analysis and Padova isochrones [CITE] with those expected from the published spectral type.
@@
 Additionally the figure shows that very fast rotators are never detected, regardless of their temperature, because the signal is completely removed when we high-pass filter the data (see Section \ref{sec:companions}).
-
-TODO: Discuss marginalization of vsini.
 
@@
 \end{figure}
+
+To estimate the survey completeness as a function of mass ratio, we first need to remove the dependence on $v\sin{i}$.
+We do this by sampling a suitable distribution of $v\sin{i}$ values for a star of each temperature and marginalizing over the completeness:
+
+\begin{equation}
+Q(T_\mathrm{eff}) = \sum_k Q(T, v_k) v_k 
+\end{equation} 
+where $Q(T, v\sin{i})$ is the surface plotted in Figure \ref{fig:detrate_2d} and $v_k$ are the samples from the distribution of $v\sin{i}$.
+For $T < 6000$ K, we sample $v\sin{i}$ using the gyrochronology relation given in \citet{Barnes2010b}:
+
+\begin{equation}
+\frac{k_Ct}{\tau} = \ln\left ( \frac{P}{P_0} \right ) \frac{k_Ik_C}{2\tau^2} (P^2 - P_0^2)
+\label{eqn:gyro}
+\end{equation}
+In Equation \ref{eqn:gyro}, $k_C$ and $k_I$ are constants fit to data with known ages and rotation periods, $P$ and $P_0$ are respectively the current and zero-age main sequence (ZAMS) rotation periods, $\tau$ is the convective turnover time scale and $t$ is the current age of the star.
+We use the same values that \cite{Barnes2010b} use for the constants:
+
+\begin{itemize}
+\item $k_C = 0.646$ day/Myr
+\item $k_I = 452$ Myr/day
+\end{itemize}
+We estimate the convective timescale ($\tau$) by interpolating Table 1 of \citet{Barnes2010}.
+We then sample the system age $t$ (see Section \ref{sec:sp} and Table \ref{tab:primary}), and sample the initial rotation period $P_0$ as log-uniform from 0.2 to 10 days.
+Equation \ref{eqn:gyro} then gives a current rotation period for each sample, which we convert to an equatorial velocity with the stellar radius $R$.
+We estimate the stellar radius by interpolating Dartmouth pre main sequence isochrones [CITE] using the temperature temperature and age.
+TODO: Probably need to rewrite at least parts of this...
+
+The gyrochronology relations do not work for stars with $T \gtrsim 6250\ K$, the canonical limit at which the convective zone is too small to efficiently remove angular momentum to the stellar wind and spin down the star \citep{Pinsonneault2001}.
+\citet{Zorec2012} fit maxwellian distributions to the equatorial velocity of A- and B-type stars in several mass bins.
+For $T > 7000\ K$, we interpolate the fit parameters, and sample the maxwellian probability density function.
+
+Typical velocities from the gyrochronology relationships are $10-20 \mathrm{km s}^{-1}$, while the maxwellian velocity distributions have typical velocities $\sim 100 \mathrm{km s}^{-1}$.
+We transition between the two regimes for temperatures in the range $6000\ K < T < 7000\ K$ by first estimating the equatorial velocities from the gyrochronology relationship (Equation \ref{eqn:gyro}).
+We then fit the velocities to a maxwellian distribution, and interpolate the fitted parameters for temperatures in the transition range.
+We show the marginalized detection rate and mean value of $v\sin{i}$ as a function of temperature in Figure \ref{fig:marginalized}.
+Both the detection rate and the average $v\sin{i}$ are smoothly varying, and show the correct behaviour with temperature.
+The detection rate actually falls with hotter temperatures because the companions are expected to be fast rotators, which are more difficult to detect.
+
+\begin{figure}
+\includegraphics[width=\columnwidth]{HIP_24244_20130919_marginalized.pdf}
+\caption{Marginalized detection rate for the same star as shown in Figure \ref{fig:detrate_2d}. The fall in detection rate towards hotter stars is caused by the increase in typical rotational speeds.}
+\label{fig:marginalized}
+\end{figure}
+
+TODO: Discuss conversion from temperature to mass, and introduce the overall completeness curve.
 

### 2016-01-27 paper/ms.tex
Finished initial draft of completeness and mass ratio distribution sections.

@@
 \usepackage{url}
+\usepackage{bm}
 \bibliographystyle{astroads}
 \providecommand{\e}[1]{\ensuremath{\times 10^{#1}}}
+\renewcommand{\vec}[1]{\bm{#1}}
+\DeclareMathOperator\erf{erf}
 \begin{document}
@@
 A companion with a high rotation rate is also more difficult to detect because the cross-correlation function gets most of its power from narrow spectral lines.
+
+\subsection{Sensitivity Analysis}
+
 To quantify the detection rate as a function of companion temperature and $v\sin{i}$, we performed a series of injection/recovery experiments.
-
 We started by creating synthetic binary star observations from each of our spectra.
@@
 
+\subsection{Marginalization}
 To estimate the survey completeness as a function of mass ratio, we first need to remove the dependence on $v\sin{i}$.
@@
 
-TODO: Discuss conversion from temperature to mass, and introduce the overall completeness curve.
+\subsection{Conversion to Mass Ratio}
+
+The result of the previous analysis is a series of estimates for the detection rate as a function of companion temperature for each star.
+We convert each companion temperature to a mass by interpolating the spectral type relations table given in [CITE Mamajek table].
+Next, we estimate the primary mass for each star as the median of the mass samples developed in Section \ref{sec:sp}.
+We then convert each detection rate curve to be a function of mass ratio ($Q_j(q)$, where $j$ denotes the $j$th star in the sample), and linearly interpolate onto a grid in mass ratio from $0 < q_i < 1$.
+Finally, we combine the detection rate curves for each star into an estimate of the survey-wide completeness by taking the average of the detection rate for all stars:
+
+\begin{equation}
+Q(q_i) = \frac{1}{N_i} \sum_j Q_j(q_i)
+\label{eqn:completeness}
+\end{equation}
+In the equation above, $N_i$ is the number of sample stars that contain an estimate for $Q(q_i)$.
+For $q_i \sim 0.2$, $N_i$ is near the total sample size.
+However, $N_i$ falls for both low and high q, since a $3000\ K$/$12000\ K$ companion converts into $q = 0.08/2.0$ for an A9V primary, but converts into $q = 0.007/0.19$ for a B0V primary.
+Our sensitivity analysis therefore does not sample large mass ratios around the very early-type primary stars in the sample, and does not sample very low mass ratios around late-type primary stars.
+
+\begin{figure}
+\includegraphics[width=\columnwidth]{SurveyCompleteness.pdf}
+\caption{Survey completeness as a function of mass ratio ($q$).}
+\label{fig:completeness}
+\end{figure}
+
+We show the total survey completeness in Figure \ref{fig:completeness}.
+The completeness falls very rapidly towards low mass ratios, although we are still $\sim 70\%$ complete at $q = 0.1$.
+The slow fall-off towards large mass ratios is caused by the same effect as in Figure \ref{fig:marginalized}: large mass ratio companions tend to be rapid rotators that are more difficult to detect.
 
@@
 \label{sec:mrd}
+
+We are now finally in a position to estimate the mass-ratio distribution for our sample.
+We estimate the mass for each detected companion star by sampling the temperatures given in Table \ref{tab:companions} as a gaussian, and converting each temperature sample into a mass sample.
+We do the conversion to mass both by interpolating the spectral type relations from [CITE mamajek table], and by interpolating from temperature and system age (see Section \ref{sec:sp}) to mass with Dartmouth isochrones [CITE].
+Both methods give similar results in most cases, although the isochrone masses are significantly higher for very young systems.
+We sample the mass ratio of the system by dividing the companion mass samples by samples of the primary mass (Section \ref{sec:sp}).
+We denote the $n$th mass ratio sample for the $k$th star as $q_k^{(n)}$, and denote the number of these samples as $N_k$.
+
+We use the methodology developed in \citet{Foreman2014} to perform bayesian inference on the shape and form of the mass ratio distribution. The log-likelihood function in this formalism is:
+
+\begin{multline}
+\ln{\mathcal{L}(\{\vec{x_k}\}| \vec{\theta})} = -K \int_0^1 Q(q)P(q|\vec{\theta})dq + \\ \sum_{k=1}^K \ln{\frac{K}{N_k} \sum_{n=1}^{N_k} Q(q_k^{(n)}) P(q_k^{(n)}|\vec{\theta})}
+\end{multline}
+
+In the above equation, $\{\vec{x_k}\}$ denote all of the data for each star, and $\vec{\theta}$ denotes the parameters for the model we are fitting.
+$K=380$ [TODO: make sure this count is correct!] is the total sample size for our survey, $Q(q)$ is the completeness function shown in Figure \ref{fig:completeness}, and $P(q|\vec{\theta})$ is the likelihood function for the mass ratio given the model parameters.
+We fit the data to two distinct distributions: a histogram ($P_1$) and a log-normal distribution ($P_2$):
+
+\begin{align}
+ P_1(q|\vec{\theta}) &= \begin{cases}
+      \hfill \theta_1 \hfill & q \in \Delta_1 \\
+      \hfill \theta_2 \hfill & q \in \Delta_2 \\
+      \hfill \ldots \\
+      \hfill \theta_7 \hfill & q \in \Delta_7
+     \end{cases} \\
+ P_2(q|\vec{\theta}) &= \frac{A}{q \sqrt{2\pi\sigma^2}} e^{-\frac{(\ln{q} - \mu)^2}{2\sigma^2}}
+\end{align}
+The constant $A$ in the log-normal distribution is a renormalization factor such that the distribution is only defined from $0 < q < 1$:
+
+\begin{equation}
+A = \frac{2}{1 - \erf(\mu / (\sigma \sqrt{2}))}
+\end{equation}
+
+We fit both distributions via Nested Sampling with the MultiNest code [CITE]. Following \citet{Foreman2014}, we apply a smoothing prior on the parameters $\vec{\theta}$:
+
+\begin{align}
+P(\vec{\theta}| \alpha, m, \tau, \epsilon) &= \mathcal{N}(\vec{\theta} | m, K(\{\Delta_j\}, \alpha, \tau, \epsilon)) \\
+K_{ij} &= \sqrt{\left[\alpha \exp{\left(-\frac{(\Delta_i - \Delta_j)^2}{2\tau^2}\right)}\right]^2 + \epsilon^2 \delta_{ij}}
+\end{align}
+The smoothing prior is an 7-dimensional gaussian with mean $m$ and covariance matrix $K_{ij}$, and encodes our belief that the mass ratio distribution is a smoothly varying function while leaving enough flexibility to let the data drive the shape of the function.
+Since we have introduced three new hyperparameters ($a, m, \tau, \epsilon$), we must apply a prior to them and marginalize over them when estimating the true bin heights.
+We choose log-uniform priors for $a, \tau$, and $\epsilon$, and a uniform prior for the mean $m$.
+The full posterior probability distribution for the histogram model is:
+
+\begin{equation}
+P_1(\vec{\theta} | \{\vec{x_k}\}) \propto P_1(q|\vec{\theta}) P(\vec{\theta}| \alpha, m, \tau, \epsilon) P(\alpha, m, \tau, \epsilon)
+\end{equation}
+
+The log-normal fit only has two parameters ($\mu, \sigma$), and was chosen because it has a similar shape to the histogram resulting from the first model.
+We use uniform priors on both $\mu$ and $\sigma$, resulting in the posterior probability
+
+\begin{equation}
+P_2(\mu, \sigma | \{\vec{x_k}\}) \propto P_2(q|\mu, \sigma) 
+\end{equation}
+
+We show the resulting distribution in Figure \ref{fig:mrd}.
+The $1\sigma$ uncertainties in the bin heights from the histogram model are shown as error bars, and we overplot 500 samples of the log-normal fit to show the spread allowed by the data.
+
+\begin{figure}
+\includegraphics[width=\columnwidth]{MRD_lognormal.pdf}
+\caption{Mass ratio distribution for our sample.
+The data was fit to both a histogram and a log-normal distribution.
+The histogram is shown in the solid blue blocks, with $1 \sigma$ uncertainties marked with error bars.
+The variance of the log-normal fit is shown with 500 samples from the posterior probability distribution for the parameters.}
+\label{fig:mrd}
+\end{figure}
 
@@
 IDs: 13A-0139, 13B-0112, 2014A-0260, 14A-0260, 15A-0245; PI: Kevin Gullikson), which is operated by the Association of Universities for Research in Astronomy (AURA) under a cooperative agreement with the National Science Foundation.
-
-We would like to thank Bill Cochran and Mike Endl for observing some of the spectra used in this project.
-.
-Finally, we would like to thank the anonymous referee for numerous comments that improved the paper.
 

### 2016-01-27 paper/ms.tex
Started discussion section.

@@
 \label{sec:discussion}
+
+Previous measurements of the mass-ratio distribution find that the data is well fit by a power law with index $0.39 \pm 0.23$ \citep[M dwarf stars][]{Delfosse2004}, $0.27 \pm 0.05$ \citep[Solar type stars][]{Duchene2013}, and $-0.45 \pm 0.15$ \citep[intermediate-mass stars][]{Kouwenhoven2007}.
+The more recent VAST survey found a much steeper power law index of $-2.3^{+1.0}_{-0.9}$ for wide companions, and an inner mass-ratio distribution that is consistent with flat.
+
+The most striking feature of the mass ratio distribution shown in Figure \ref{fig:mrd} is the turnover at intermediate q, which the log-normal fit finds occurs at $q = 0.30 \pm 0.03$ and which excludes a power law fit (including a flat distribution).
+
+TODO: Compare to chabrier IMF, power law, and flat distribution quantitatively. Bayesian evidence ratios?
+
+TODO: Speculate on the discrepancy between my results and VAST. Perhaps the change occurs closer than their cut of 125 AU? Perhaps it is inside $\sim 30$ AU, where they have very low completeness?
+
+TODO: Discuss ways forward.
+Compile table giving the estimated maximum separation from the RVs.
+Promote an imaging survey to follow these up.
+Promote RV monitoring of the detections to get dynamical mass ratios and, more importantly, separations.
+
+TODO: Discuss physical mechanism to generate a preferrence for $q = 0.3$.
+Saying something about when disk fragments (how much time is left for the companion to accrete)?
+Saying something about migration in the early disk?
+Perhaps the extreme mass-ratio systems migrate inwards as they accrete material.
+If they continue migrating long enough to get much over $q \sim 0.3$, they end up falling into the star?
+
+%Estimates of the mass-ratio distribution for spectroscopic binaries with slowly rotating chemically peculiar Am/Ap stars also appears to be roughly Gaussian with mean $\sim 0.4$ \citep{Carrier2002, Vuissoz2004}, in apparent conflict from the close companions identified with adaptive optics imaging in the VAST survey \citep{DeRosa2014} that show a ~flat mass-ratio distribution.
 

### 2016-01-27 paper/ms.tex
Used new aasjournal references style.

@@
 \usepackage{bm}
-\bibliographystyle{astroads}
+\bibliographystyle{aasjournal}
 \providecommand{\e}[1]{\ensuremath{\times 10^{#1}}}
@@
 However close fragments ($a \sim 100$ AU) will interact with each other; the protostellar disk may be truncated, destabilized, or even merge into a circumbinary disk if the separation is small enough.
-In addition, unstable disk can fragment to form low-mass companions \citep{Kratter2006, Stammatellos2011}.
+In addition, unstable disk can fragment to form low-mass companions \citep{Kratter2006, Stamatellos2011}.
 The mass ratios of close companions formed via either mechanism should be effected by preferential accretion.
@@
 \end{itemize}
-We estimate the convective timescale ($\tau$) by interpolating Table 1 of \citet{Barnes2010}.
+We estimate the convective timescale ($\tau$) by interpolating Table 1 of \citet{Barnes2010a}.
 We then sample the system age $t$ (see Section \ref{sec:sp} and Table \ref{tab:primary}), and sample the initial rotation period $P_0$ as log-uniform from 0.2 to 10 days.

### 2016-01-28 Completeness.py
Use kglib.

@@ -10,16 +10,16 @@ from scipy.optimize import minimize_scalar
 from scipy.interpolate import InterpolatedUnivariateSpline as spline
 from scipy.stats import gaussian_kde
 import pandas as pd 
-import Mamajek_Table
+from kglib.spectral_type import Mamajek_Table
 from astropy import units as u, constants
 import os
 import h5py
-import StarData
+from kglib.utils import StarData
 import Priors
 import logging
 import pickle
 from scipy.interpolate import LinearNDInterpolator
-from HelperFunctions import IsListlike
+from kglib.utils.HelperFunctions import IsListlike
 
 PRIOR_HDF5 = 'data/OrbitPrior.h5'
 

### 2016-01-28 paper/ms.tex
Added malmquist bias discussion to paper.

@@
 Both methods give similar results in most cases, although the isochrone masses are significantly higher for very young systems.
+We therefore only show the results obtained with the isochrone masses.
 We sample the mass ratio of the system by dividing the companion mass samples by samples of the primary mass (Section \ref{sec:sp}).
@@
 
-We use the methodology developed in \citet{Foreman2014} to perform bayesian inference on the shape and form of the mass ratio distribution. The log-likelihood function in this formalism is:
+\subsection{Fitting  Methodology}
+
+We use the methodology developed in \citet{Foreman2014} to perform bayesian inference on the shape and form of the mass ratio distribution.
+The log-likelihood function in this formalism is derived from modeling the survey as a draw from the inhomogeneous Poisson process with rate density $\Gamma \equiv KQ(q)P(q)$:
 
@@
 \ln{\mathcal{L}(\{\vec{x_k}\}| \vec{\theta})} = -K \int_0^1 Q(q)P(q|\vec{\theta})dq + \\ \sum_{k=1}^K \ln{\frac{K}{N_k} \sum_{n=1}^{N_k} Q(q_k^{(n)}) P(q_k^{(n)}|\vec{\theta})}
+\label{eqn:money}
 \end{multline}
@@
       \hfill \theta_7 \hfill & q \in \Delta_7
-     \end{cases} \\
- P_2(q|\vec{\theta}) &= \frac{A}{q \sqrt{2\pi\sigma^2}} e^{-\frac{(\ln{q} - \mu)^2}{2\sigma^2}}
+     \end{cases} \label{eqn:P1} \\
+ P_2(q|\vec{\theta}) &= \frac{A}{q \sqrt{2\pi\sigma^2}} e^{-\frac{(\ln{q} - \mu)^2}{2\sigma^2}} \label{eqn:P2}
 \end{align}
@@
 \begin{equation}
-P_1(\vec{\theta} | \{\vec{x_k}\}) \propto P_1(q|\vec{\theta}) P(\vec{\theta}| \alpha, m, \tau, \epsilon) P(\alpha, m, \tau, \epsilon)
+P_1(\vec{\theta} | \{\vec{x_k}\}) \propto \mathcal{L}_1(\{\vec{x_k}\}| \vec{\theta}) P(\vec{\theta}| \alpha, m, \tau, \epsilon) P(\alpha, m, \tau, \epsilon)
 \end{equation}
@@
 
-We show the resulting distribution in Figure \ref{fig:mrd}.
+\subsection{Malmquist Bias Correction}
+
+We are trying to recover the intrinsic distribution from an observed sample; thus we should fit the data to the probability distribution function (PDF) for mass ratio, \emph{given that we observed the star}: $P(q|\vec{\theta}, \mathrm{obs})$.
+In a volume-limited sample, this is equal to $P(q|\vec{\theta})$; however, our sample is volume-limited and therefore suffers from Malmquist bias.
+There is a higher probability of equal-mass binary systems in our data because they contribute twice the flux and are therefore more likely to fall under the magnitude limit.
+We can calculate the PDF for mass ratio given that we observed the system from Bayes' theorem:
+
+\begin{equation}
+P(q|\vec{\theta}, \mathrm{obs}) = \frac{P(\mathrm{obs}|q, \vec{\theta}) P(q|\vec{\theta})}{\int_0^1 P(\mathrm{obs}|q, \vec{\theta}) P(q|\vec{\theta}) dq}
+\end{equation}
+
+We already know $P(q|\vec{\theta})$ (Equations \ref{eqn:P1} and \ref{eqn:P2}). We estimate $P(\mathrm{obs}|q)$ by simulating a very large sample of binary stars:
+
+\begin{enumerate}
+\item Sample primary star masses from the Kroupa IMF [CITE]
+\item Sample a distance for each star from a disk with infinite extent and scale height of $300$ pc. 
+\item For each $q$ from 0 to 1, in steps of 0.01:
+\begin{enumerate}
+  \item Add a companion star to each primary with the appropriate mass to make a binary system with mass ratio $q$.
+  \item Calculate the combined absolute V-magnitude by interpolating the spectral type relations in [CITE mamajek]
+  \item Calculate apparent magnitude $V$
+  \item Find fraction of stars ($f(q)$) with apparent $V < 6$
+\end{enumerate}
+\item Fit the sampled fractions $f(q)$ to a 5th-order polynomial.
+\end{enumerate}
+
+With the fitted malmquist-correction polynomial, we then substitute $P(q|\vec{\theta}, \mathrm{obs})$ everywhere $P(q|\vec{\theta})$ appears in Equation \ref{eqn:money}.
+
+We show the resulting fits in Figure \ref{fig:mrd}.
 The $1\sigma$ uncertainties in the bin heights from the histogram model are shown as error bars, and we overplot 500 samples of the log-normal fit to show the spread allowed by the data.

### 2016-01-28 Simulation.py
Removed unused functions.

@@ -1,391 +1,8 @@
 """ Utility functions for simulating my proposed analysis method.
 """
-import logging
-
-import h5py
-from scipy.stats import ks_2samp
-import pandas as pd
 import numpy as np
-import matplotlib.pyplot as plt
-from scipy.stats import truncnorm
 
-import ForwardModeling
-import Distributions
-from Distributions import mass2teff, OrbitPrior, CensoredCompleteness
-import Orbit
 
-
-def make_comparison_plot(true_vals, fitted_vals, low=0, high=1, axes=None):
-    if axes is None:
-        fig, axes = plt.subplots(nrows=1, ncols=2, figsize=(15, 7))
-    axes[0].scatter(true_vals, fitted_vals, alpha=0.5)
-    axes[0].plot([low, high], [low, high], 'r-', lw=2)
-    axes[0].set_xlabel('True value')
-    axes[0].set_ylabel('Fitted value')
-
-    bins = np.linspace(low, high, 10)
-    _, bins, _ = axes[1].hist(true_vals, bins=bins, cumulative=True, histtype='step', normed=True, lw=2)
-    axes[1].hist(fitted_vals, bins=bins, cumulative=True, histtype='step', normed=True, lw=2)
-
-    ks_stat, p_value = ks_2samp(true_vals, fitted_vals)
-    print('KS-test p-value = {:.3g}'.format(p_value))
-
-    return axes
-
-
-def comparison_plots(mcmc_samples, true_q, true_a, true_e):
-    """
-    Make comparison plots for all of the variables we care about
-    """
-
-    q = np.nanmean(mcmc_samples[:, :, 0], axis=1)
-    loga = np.nanmean(np.log10(mcmc_samples[:, :, 1]), axis=1)
-    loge = np.nanmean(np.log10(mcmc_samples[:, :, 2]), axis=1)
-
-    fig, axes = plt.subplots(nrows=3, ncols=2, figsize=(15, 21))
-
-    # Mass-ratio
-    print('\nMass-ratio comparison: ')
-    axes[0] = make_comparison_plot(true_q, q, axes=axes[0])
-    axes[0][0].set_xlabel('True Mass-Ratio')
-    axes[0][0].set_ylabel('Fitted Mass-Ratio')
-    axes[0][1].set_xlabel('Mass-Ratio')
-    axes[0][1].set_ylabel('Cumulative Frequency')
-
-    # Mass-ratio
[…]

### 2016-01-28 ForwardModeling.py
Removed unused modules.

@@ -1,285 +1,0 @@
-import numpy as np
-import scipy.stats
-from astropy import units as u, constants
-from scipy.optimize import newton
-import pandas as pd
-
-import HelperFunctions
-import IMF_utils
-from Mamajek_Table import MamajekTable
-import Orbit
-import Simulation
-
-
-def truncated_expon(scale=0.0, Nsamp=100):
-    """ Get random samples from an exponential distribution confined to [0,1]
-    """
-    u = np.random.uniform(size=Nsamp)
-    x = u**(1./(1-scale))
-    return x
-
-
-def get_eccentric_anomaly(M, e):
-    """
-    Get the eccentric anomaly (E) from the mean anomaly (M) and orbital eccentricity (e)
-    Uses the equation M = E - esinE
-    """
-    if HelperFunctions.IsListlike(M):
-        return np.array([get_eccentric_anomaly(Mi, e) for Mi in M])
-
-    func = lambda E: E - e*np.sin(E) - M
-    dfunc = lambda E: 1.0 - e*np.cos(E)
-    d2func = lambda E: e*np.sin(E)
-    
-    output = newton(func, np.pi, fprime=dfunc, fprime2=d2func)
-
-    #output = minimize_scalar(chisquare, bounds=[0, 2*np.pi], method='brent')
-    return output
-
-
-def get_true_anomaly(E, e):
-    """
-    Get the true anomaly from the eccentric anomaly (E) and the eccentricity
-    """
-    A = (np.cos(E) - e)/(1-e*np.cos(E))
-    B = (np.sqrt(1.-e**2) * np.sin(E)) / (1.-e*np.cos(E))
-    return np.arctan2(B, A)
-
-
-def get_rv(phase, e, K1, w):
-    """
-    Get the radial velocity at the given phase, given the parameters:
-    e = eccentricity
-    K1 = semiamplitude
-    w = longitude of pericenter (radians)
-    """
-    M = 2.0*np.pi*phase
-    Erad = get_eccentric_anomaly(M, e)
-    nu = get_true_anomaly(Erad, e)
-
-    return K1 * (np.cos(nu+w) + e*np.cos(w))
-
-
-
-class ForwardModeler(object):
-    """
-    A class to do forward modeling to measure population parameters amongst observational biases
-    """
-    
-    def __init__(self, *args, **kwargs):
-        """ Eventually, this should take all the data I have in some reasonable way
-        """
-        MT = MamajekTable()
[…]

### 2016-01-28 Completeness.py
optimized imports.

@@ -4,22 +4,24 @@ Functions for estimating the completeness functions
 
 from __future__ import print_function, division, absolute_import
 
-import numpy as np
 import multiprocessing
+from astropy import units as u, constants
+import os
+import logging
+import pickle
+
+import numpy as np
 from scipy.optimize import minimize_scalar
 from scipy.interpolate import InterpolatedUnivariateSpline as spline
 from scipy.stats import gaussian_kde
-import pandas as pd 
-from kglib.spectral_type import Mamajek_Table
-from astropy import units as u, constants
-import os
+import pandas as pd
 import h5py
+from scipy.interpolate import LinearNDInterpolator
+
+from kglib.spectral_type import Mamajek_Table
 from kglib.utils import StarData
 import Priors
-import logging
-import pickle
-from scipy.interpolate import LinearNDInterpolator
-from kglib.utils.HelperFunctions import IsListlike
+
 
 PRIOR_HDF5 = 'data/OrbitPrior.h5'
 
@@ -181,9 +183,8 @@ def get_age(star):
     """
     with h5py.File(PRIOR_HDF5, 'r') as infile:
         if star in infile.keys():
-            return infile[star]['system_age'].value 
+            return infile[star]['system_age'].value
 
-    from Priors import get_age
     spt = StarData.GetData(star).spectype
     return get_ages(star, spt)
 

### 2016-01-28 fit_parameters.py

@@ -1,11 +1,11 @@
-import pymultinest
+import sys
+import os
+
 from isochrones import StarModel
 from isochrones.padova import Padova_Isochrone
-import sys
 import pandas as pd
-import os
 import numpy as np
-import h5py
+
 
 HDF5_OUTPUT = 'Primary_Parameters.h5'
 

### 2016-01-28 open_slideshow.sh
Removed TexMex script.

@@ -1,3 +1,0 @@
-#/bin/bash
-#ipython nbconvert TexMex.ipynb --to slides --post serve --reveal-prefix "http://cdn.jsdelivr.net/reveal.js/2.6.2"
-ipython nbconvert TexMex.ipynb --to slides --post serve

### 2016-01-29 paper/ms.tex
Added a bunch of references.

@@
 For those that do not, we estimate the mass and age of the system as follows.
-We first cross-correlate the data against a grid of Kurucz model spectra [CITE] spanning $7000\ K < T_\mathrm{eff} < 30000\ K$, $3.0 < \log{g} < 4.5$, and $75 < v\sin{i} < 300$.
+We first cross-correlate the data against a grid of Kurucz model spectra \citep{Castelli2003} spanning $7000\ K < T_\mathrm{eff} < 30000\ K$, $3.0 < \log{g} < 4.5$, and $75 < v\sin{i} < 300$.
 For the optical data, we use the blue echelle orders ($\lambda < 5550 \AA$).
@@
 
-Next, we use Padova stellar evolutionary tracks [CITE] and the isochrones code [CITE] to estimate the mass and age of the system from the measured temperature and $\log{g}$.
-As a consistency check, we also interpolate a table of spectral type relations [CITE mamajek table] to estimate the primary mass from the published spectral types.
+Next, we use Padova stellar evolutionary tracks \citep{Bressan2012} and the isochrones code \citep{isochrones_code} to estimate the mass and age of the system from the measured temperature and $\log{g}$.
+As a consistency check, we also interpolate from a table of stellar properties as a function of spectral type \citep{Pecaut2013} to estimate the primary mass from the published spectral types.
 We show the comparison in Figure \ref{fig:prim_mass}.
@@
 \includegraphics[width=\columnwidth]{PrimaryMassEstimates_log.pdf}
-\caption{Comparison of primary star masses derived from our cross-correlation analysis and Padova isochrones [CITE] with those expected from the published spectral type.
+\caption{Comparison of primary star masses derived from our cross-correlation analysis and Padova isochrones \citep{Bressan2012} with those expected from the published spectral type.
 There is excellent agreement between the two measures across the entire range of masses.}
@@
 The result of the previous analysis is a series of estimates for the detection rate as a function of companion temperature for each star.
-We convert each companion temperature to a mass by interpolating the spectral type relations table given in [CITE Mamajek table].
+We convert each companion temperature to a mass by interpolating Table 5 of \citet{Pecaut2013}.
 Next, we estimate the primary mass for each star as the median of the mass samples developed in Section \ref{sec:sp}.
@@
 We estimate the mass for each detected companion star by sampling the temperatures given in Table \ref{tab:companions} as a gaussian, and converting each temperature sample into a mass sample.
-We do the conversion to mass both by interpolating the spectral type relations from [CITE mamajek table], and by interpolating from temperature and system age (see Section \ref{sec:sp}) to mass with Dartmouth isochrones [CITE].
+We do the conversion to mass both by interpolating Table 5 from \citet{Pecaut2013}, and by interpolating from temperature and system age (see Section \ref{sec:sp}) to mass with Dartmouth isochrones [CITE].
 Both methods give similar results in most cases, although the isochrone masses are significantly higher for very young systems.
@@
 
-We fit both distributions via Nested Sampling with the MultiNest code [CITE]. Following \citet{Foreman2014}, we apply a smoothing prior on the parameters $\vec{\theta}$:
+We fit both distributions via Importance Nested Sampling with the MultiNest code \citep{multinest}. Following \citet{Foreman2014}, we apply a smoothing prior on the parameters $\vec{\theta}$:
 
@@
 \begin{enumerate}
-\item Sample primary star masses from the Kroupa IMF [CITE]
+\item Sample primary star masses from the Kroupa IMF \citep{Kroupa2002}
 \item Sample a distance for each star from a disk with infinite extent and scale height of $300$ pc. 
@@
   \item Add a companion star to each primary with the appropriate mass to make a binary system with mass ratio $q$.
-  \item Calculate the combined absolute V-magnitude by interpolating the spectral type relations in [CITE mamajek]
+  \item Calculate the combined absolute V-magnitude by interpolating Table 5 of \citet{Pecaut2013}.
   \item Calculate apparent magnitude $V$

### 2016-01-29 paper/ms.tex
Proofreading round 1 complete. Changed MRD figure to a gaussian fit instead of lognormal.

@@
 Stellar multiplicity is an inevitable and common outcome of star formation, with roughly half of all solar-type field stars in binary or multiple systems \citep{Raghavan2010} and an even higher fraction as the stellar mass increases.
-Young stellar associations and clusters tend to have even higher multiplicity \citep{Duchene2013}, indicating that stars often form in multiple systems that are destroyed by dynamical interactions as the cluster dissociates.
-
-Beyond the overall multiplicity rate, the mass ratio, period, and eccentricity distributions of a binary star population place important constraints on the mode of binary star formation.
+Young stellar associations and clusters tend to have even higher multiplicity \citep{Duchene2013}, indicating that stars often form in multiple systems that are subsequently destroyed by dynamical interactions as the cluster dissociates.
+
+The overall multiplicity rate and the distributions of mass ratio, period, and eccentricity of a binary star population place important constraints on the mode of binary star formation.
 Most binary stars are thought to form via core fragmentation \citep{Boss1979, Boss1986, Bate1995}, in which a collapsing core fragments into two or more individual protostars.
@@
 All of the distributions are much less certain for more massive stars.
-The reason for this is two-fold: first, more massive stars tend to more rare and farther away, meaning many of the companions are angularly close to the very bright primaries.
+The reason for this is two-fold: first, more massive stars tend to more rare and farther away, meaning many of the companions are angularly close to the very bright primaries and difficult to detect with imaging techniques.
 Second, the primary stars tend to be rapid rotators, which limits radial velocity precision to $\sim 1 \mathrm{km\ s}^{-1}$.
@@
 We describe the stellar sample and data used for the survey in Section \ref{sec:obs}, as well as the data reduction steps in the same section.
-Next, we describe the direct spectroscopic detection and tabulate the companion detections in Section \ref{sec:companions}, and discuss the survey completeness in Section \ref{sec:completeness}.
-We then describe our estimation of the stellar parameters for the primary stars in our sample in Section \ref{sec:sp}.
+Next, we describe the direct spectroscopic detection and tabulate the companion detections in Section \ref{sec:companions}.
+We estimate the mass and age of the primary stars in Section \ref{sec:sp}, and discuss the survey completeness in Section \ref{sec:completeness}.
 Finally, we end with a derivation of the mass ratio distribution from our sample in Section \ref{sec:mrd} and discuss its implications for binary formation in Section \ref{sec:discussion}.
@@
 It does introduce a Malmquist bias in the derived mass ratio, which we discuss and correct for in Section \ref{sec:mrd}.
-Likewise, the $v\sin{i}$ limit makes accounting for the primary star spectrum in the companion search trivial; since most A- or B-type stars are rapid rotators, it does not actually remove very many stars from the sample.
+Likewise, the $v\sin{i}$ limit makes accounting for the primary star spectrum in the companion search trivial; since most A- or B-type stars are rapid rotators, the cutoff does not remove very many stars from the sample.
 Finally we only include normal, main sequence stars in the sample because the binary flux ratio would be even less favorable to companion detection in an evolved star.
+Most of the spectral peculiarities denote narrow lines, which are already cut from the sample by the $v\sin{i}$ cut.
 The target list and observing details are given in Table \ref{tab:observations}.
@@
 For the HRS, we use the $R = 60000$ setting with a $2''$ fiber, and with wavelength coverage from 410-780 nm.
-We bias-correct, flat-field, and extract the spectra using an IRAF pipeline.
+We bias-correct, flat-field, and extract the spectra using an IRAF pipeline very similar to the one we use for the CHIRON data.
 The HRS spectra are wavelength-calibrated using a Th-Ar lamp observed immediately before or after the science observations.
@@
 For the TS23, we use a $1.2''$ slit in combination with the E2 \'echelle grating (53 grooves/mm, blaze angle $65^{\circ}$), yielding a resolving power of $R=60000$ and a wavelength coverage from 375-1020 nm.
-We reduce the data using an IRAF pipeline very similar to the one we use for the HRS, and wavelength calibrate using a Th-Ar lamp observed immediately before the science observations.
+We reduce the data using an IRAF pipeline very similar to the ones we use for CHIRON and HRS, and wavelength calibrate using a Th-Ar lamp observed immediately before the science observations.
 
@@
 The telluric correction is critical for IGRINS spectra, where every order is dominated by telluric absorption lines.
-For the optical spectra, it is less critical but allows us to use some of the redder orders than we otherwise would be able to.
+For the optical spectra, it is less critical but allows us to use some of the redder orders than we otherwise would not be able to.
 For unsaturated lines, the best-fit telluric model reproduces the data to within $\sim 1-5\%$ of the continuum level.
@@
 Because the targets are all extremely bright, we used the high read noise and high flux detector settings to allow for very short co-add exposure times.
-We reduced the data using the Gemini set of IRAF[TODO: Add iraf footnote] tasks, which include steps for nonlinearity correction, flat-fielding, sky subtraction, and co-addition of the dither frames.
+We reduced the data using the Gemini set of IRAF tasks, which include steps for nonlinearity correction, flat-fielding, sky subtraction, and co-addition of the dither frames.
 
@@
 In most cases, there is a clear shift in the radial velocity of the companion, indicating that it is orbiting the target star and is not a foreground or background companion.
-In addition we obtained Gemini/NIRI adaptive optics imaging data for 19 of the northern companions, and were able to resolve 7 of the companions.
+In addition we obtained Gemini/NIRI adaptive optics imaging data for 19 of the northern companions, and were able to resolve 7 of them.
 
@@
 For those that do not, we estimate the mass and age of the system as follows.
-We first cross-correlate the data against a grid of Kurucz model spectra \citep{Castelli2003} spanning $7000\ K < T_\mathrm{eff} < 30000\ K$, $3.0 < \log{g} < 4.5$, and $75 < v\sin{i} < 300$.
+We first cross-correlate the data against a grid of Kurucz model spectra \citep{Castelli2003} spanning
+
+\begin{itemize}
+\item $7000\ K < T_\mathrm{eff} < 30000\ K$ in steps of $1000\ K$
+\item $3.0 < \log{g} < 4.5$ in steps of $0.25$ dex
+\item $75 < v\sin{i} < 300\ \mathrm{km s}^{-1}$ in steps of $25\ \mathrm{km s}^{-1}$
+\end{itemize}
 For the optical data, we use the blue echelle orders ($\lambda < 5550 \AA$).
-We ignore the strong hydrogren lines in the spectrum, because they span several echelle orders and make continuum normalization very difficult.
+We ignore the strong hydrogren Balmer lines in the spectrum because they span several echelle orders and make continuum normalization very difficult, potentially biasing the result.
 There are sufficient metal lines in the optical spectra that the resulting CCF always has a very strong peak at the radial velocity of the primary star.
-The near-infrared IGRINS spectra do not have enough strong metal lines in their spectrum to justify ignoring the hydrogen lines; we use the subset from $1.51 - 1.73 \micron$ for these spectra.
+The near-infrared IGRINS spectra are dominated by hydrogren Brackett lines and have very few strong metal lines; we use the subset from $1.51 - 1.73 \micron$ for these spectra.
 We then estimate the temperature and surface gravity of the primary stars from the CCF with the largest peak.
-We assume the following errors on the temperature and surface gravity:
+We adopt the following errors on the temperature and surface gravity:
 
@@
 We started by creating synthetic binary star observations from each of our spectra.
-We made two distinct grids of companion stars: a low temperature grid spanning $3000\ K < T_\mathrm{eff} < 6500\ K$ and $0\ \mathrm{km\ s}^{-1} < v\sin{i} < 50\ \mathrm{km\ s}^{-1}$, and a high temperature grid spanning $7000\ K < T_\mathrm{eff} < 12000\ K$ and $100\ \mathrm{km\ s}^{-1} < v\sin{i} < 250\ \mathrm{km\ s}^{-1}$.
-The low temperature grid has a temperature spacing of $100$ K and a $v\sin{i}$ spacing of $10 \mathrm{km\ s}^{-1}$; the high temperature grid has a temperature spacing of $1000$ K and a $v\sin{i}$ spacing of $50 \mathrm{km\ s}^{-1}$.
+We made two distinct grids of companion stars: a low temperature grid spanning
+
+\begin{itemize}
+\item $3000\ K < T_\mathrm{eff} < 6500\ K$ in steps of $100\ K$
+\item $0\ \mathrm{km\ s}^{-1} < v\sin{i} < 50\ \mathrm{km\ s}^{-1}$ in steps of $10\ \mathrm{km\ s}^{-1}$
+\end{itemize}
+and a high temperature grid spanning
+
+\begin{itemize}
+\item $7000\ K < T_\mathrm{eff} < 1200\ K$ in steps of $1000\ K$
+\item $100\ \mathrm{km\ s}^{-1} < v\sin{i} < 250\ \mathrm{km\ s}^{-1}$ in steps of $50\ \mathrm{km\ s}^{-1}$
+\end{itemize}
 For each grid point, we added a solar metallicity Phoenix model spectrum to the observed data after scaling to replicate the expected flux between a main sequence companion of the model temperature and the known target star spectral type.
 If the target star had known companions within $3''$, we included the expected flux from the companion when computing the flux ratio.
-We repeated each grid point at different radial velocities spanning $-400\ \mathrm{km\ s}^{-1} < v < 400\ \mathrm{km\ s}^{-1}$ in $50\ \mathrm{km\ s}^{-1}$ steps to estimate a probability of detection at each point.
+We repeated each grid point at different radial velocities spanning $-400\ \mathrm{km\ s}^{-1} < v < 400\ \mathrm{km\ s}^{-1}$ in $50\ \mathrm{km\ s}^{-1}$ steps to sample the noise properties of the spectra and estimate a probability of detection at each point.
 
@@
 Equation \ref{eqn:gyro} then gives a current rotation period for each sample, which we convert to an equatorial velocity with the stellar radius $R$.
-We estimate the stellar radius by interpolating Dartmouth pre main sequence isochrones [CITE] using the temperature temperature and age.
-TODO: Probably need to rewrite at least parts of this...
+We estimate the stellar radius by interpolating Dartmouth pre main sequence isochrones [CITE] using the companion temperature and system age.
+TODO:
 
@@
 Typical velocities from the gyrochronology relationships are $10-20 \mathrm{km s}^{-1}$, while the maxwellian velocity distributions have typical velocities $\sim 100 \mathrm{km s}^{-1}$.
-We transition between the two regimes for temperatures in the range $6000\ K < T < 7000\ K$ by first estimating the equatorial velocities from the gyrochronology relationship (Equation \ref{eqn:gyro}).
-We then fit the velocities to a maxwellian distribution, and interpolate the fitted parameters for temperatures in the transition range.
+We transition between the two regimes for temperatures in the range $6000\ K < T < 7000\ K$ by first estimating the equatorial velocities from the gyrochronology relationship (Equation \ref{eqn:gyro}) at $T=6000\ K$.
+We then fit the velocities to a maxwellian distribution, and add the result to the tabulated parameters from \citep{Zorec2012}.
+With the extended table, we treat stars in the transition range the same way we treat hot stars.
+
 We show the marginalized detection rate and mean value of $v\sin{i}$ as a function of temperature in Figure \ref{fig:marginalized}.
 Both the detection rate and the average $v\sin{i}$ are smoothly varying, and show the correct behaviour with temperature.
-The detection rate actually falls with hotter temperatures because the companions are expected to be fast rotators, which are more difficult to detect.
+The detection rate falls with hotter temperatures because the companions are expected to be fast rotators, which are more difficult to detect.
 
@@
 For $q_i \sim 0.2$, $N_i$ is near the total sample size.
-However, $N_i$ falls for both low and high q, since a $3000\ K$/$12000\ K$ companion converts into $q = 0.08/2.0$ for an A9V primary, but converts into $q = 0.007/0.19$ for a B0V primary.
+However, $N_i$ falls for both low and high q, since a $3000\ K$/$12000\ K$ companion has a mass ratio $q = 0.08/2.0$ for an A9V primary, but $q = 0.007/0.19$ for a B0V primary.
 Our sensitivity analysis therefore does not sample large mass ratios around the very early-type primary stars in the sample, and does not sample very low mass ratios around late-type primary stars.
@@
 In the above equation, $\{\vec{x_k}\}$ denote all of the data for each star, and $\vec{\theta}$ denotes the parameters for the model we are fitting.
-$K=380$ [TODO: make sure this count is correct!] is the total sample size for our survey, $Q(q)$ is the completeness function shown in Figure \ref{fig:completeness}, and $P(q|\vec{\theta})$ is the likelihood function for the mass ratio given the model parameters.
-We fit the data to two distinct distributions: a histogram ($P_1$) and a log-normal distribution ($P_2$):
+$K=360$ is the total sample size for our survey, $Q(q)$ is the completeness function shown in Figure \ref{fig:completeness}, and $P(q|\vec{\theta})$ is the likelihood function for the mass ratio given the model parameters.
+We fit the data to two distinct distributions: a histogram ($P_1$) and a gaussian distribution ($P_2$):
 
@@
      \end{cases} \label{eqn:P1} \\
- P_2(q|\vec{\theta}) &= \frac{A}{q \sqrt{2\pi\sigma^2}} e^{-\frac{(\ln{q} - \mu)^2}{2\sigma^2}} \label{eqn:P2}
+ P_2(q|\vec{\theta}) &= \frac{A}{\sqrt{2\pi\sigma^2}} e^{-\frac{(q - \mu)^2}{2\sigma^2}} \label{eqn:P2}
 \end{align}
-The constant $A$ in the log-normal distribution is a renormalization factor such that the distribution is only defined from $0 < q < 1$:
+The constant $A$ in the gaussian distribution is a renormalization factor such that the distribution is only defined from $0 < q < 1$:
 
 \begin{equation}
-A = \frac{2}{1 - \erf(\mu / (\sigma \sqrt{2}))}
+A = \frac{2}{\erf\left(\frac{\mu}{\sigma \sqrt{2}}\right) - \erf\left(\frac{\mu - 1}{\sigma \sqrt{2}}\right)}
 \end{equation}
 
-We fit both distributions via Importance Nested Sampling with the MultiNest code \citep{multinest}. Following \citet{Foreman2014}, we apply a smoothing prior on the parameters $\vec{\theta}$:
+We fit both distributions via Importance Nested Sampling with the MultiNest code \citep{multinest}.
+Following \citet{Foreman2014}, we apply a smoothing prior on the parameters $\vec{\theta}$ for the histogram model:
 
@@
 
-The log-normal fit only has two parameters ($\mu, \sigma$), and was chosen because it has a similar shape to the histogram resulting from the first model.
+The gaussian fit only has two parameters ($\mu, \sigma$), and was chosen because it has a similar shape to the histogram resulting from the first model.
 We use uniform priors on both $\mu$ and $\sigma$, resulting in the posterior probability
@@
 We are trying to recover the intrinsic distribution from an observed sample; thus we should fit the data to the probability distribution function (PDF) for mass ratio, \emph{given that we observed the star}: $P(q|\vec{\theta}, \mathrm{obs})$.
-In a volume-limited sample, this is equal to $P(q|\vec{\theta})$; however, our sample is volume-limited and therefore suffers from Malmquist bias.
+In a volume-limited sample, this is equal to $P(q|\vec{\theta})$; however, our sample is magnitude-limited and therefore suffers from Malmquist bias.
 There is a higher probability of equal-mass binary systems in our data because they contribute twice the flux and are therefore more likely to fall under the magnitude limit.
@@
 \begin{equation}
-P(q|\vec{\theta}, \mathrm{obs}) = \frac{P(\mathrm{obs}|q, \vec{\theta}) P(q|\vec{\theta})}{\int_0^1 P(\mathrm{obs}|q, \vec{\theta}) P(q|\vec{\theta}) dq}
+P(q|\vec{\theta}, \mathrm{obs}) = \frac{P(\mathrm{obs}|q) P(q|\vec{\theta})}{\int_0^1 P(\mathrm{obs}|q) P(q|\vec{\theta}) dq}
 \end{equation}
@@
   \item Calculate the combined absolute V-magnitude by interpolating Table 5 of \citet{Pecaut2013}.
-  \item Calculate apparent magnitude $V$
+  \item Calculate apparent magnitude $V$ from the absolute magnitude and distance.
   \item Find fraction of stars ($f(q)$) with apparent $V < 6$
@@
 We show the resulting fits in Figure \ref{fig:mrd}.
-The $1\sigma$ uncertainties in the bin heights from the histogram model are shown as error bars, and we overplot 500 samples of the log-normal fit to show the spread allowed by the data.
+The $1\sigma$ uncertainties in the bin heights from the histogram model are shown as error bars, and we overplot 500 samples of the gaussian fit to show the spread allowed by the data.
 
 \begin{figure}
-\includegraphics[width=\columnwidth]{MRD_lognormal.pdf}
+\includegraphics[width=\columnwidth]{MRD_normal.pdf}
 \caption{Mass ratio distribution for our sample.
@@
 
-The most striking feature of the mass ratio distribution shown in Figure \ref{fig:mrd} is the turnover at intermediate q, which the log-normal fit finds occurs at $q = 0.30 \pm 0.03$ and which excludes a power law fit (including a flat distribution).
+The most striking feature of the mass ratio distribution shown in Figure \ref{fig:mrd} is the turnover at intermediate q, which the gaussian fit finds occurs at $q = 0.36 \pm 0.04$ and which excludes a power law fit (including a flat distribution).
 
@@
 
-\begin{longtable*}{|l|lllrlrr|}
-\hline
-              &                &                &                &          MJD &            &  exptime &     snr \\
-         star &            SpT &             ra &            dec & (JD-2450000) & instrument &  (sec)   &         \\ \hline
-\endhead
-\hline
-\multicolumn{3}{r}{{Continued on next page}} \\
-\endfoot
-
-\hline
-\endlastfoot
+%              &                &                &                &          MJD &            &  exptime &     snr \\
+%         star &            SpT &             ra &            dec & (JD-2450000) & instrument &  (sec)   &
+
+\LongTables
+\begin{deluxetable*}{|l|lllrlrr|}
+\tabletypesize{\small}
+\tablewidth{0pt}
+\tablecaption{Target Lists and Observation Log}
+\tablehead{
+      \colhead{} & \colhead{} & \colhead{} & \colhead{} &  \colhead{MJD} & \colhead{}  & \colhead{exptime} & \colhead{} \\
+       \colhead{star} & \colhead{SpT} & \colhead{RA} & \colhead{DEC} &  \colhead{(JD-2450000)} &   \colhead{instrument} & \colhead{(sec)} & \colhead{snr}
+       }
+
+\startdata
      HIP 813 &           B9Vn &     00:10:2.20 &   +11:08:44.93 &  6618.58 &       TS23 &      557 &    1810 \\
@@
   HIP 118243 &            B1V &     23:59:0.54 &   +55:45:17.74 &  6583.74 &       TS23 &      351 &    1760
+\enddata
+
 \label{tab:observations}
-\end{longtable*}
+\end{deluxetable*}
 

### 2016-01-29 paper/ms.tex
Added abstract.

@@
 \begin{abstract}
-Abstract here
+Binary stars and higher-order multiple systems are a ubiquitous outcome of star formation, especially as the system mass increases.
+The mass-ratio distribution is a unique probe into the physics of the collapsing molecular core as well as the circumstellar disk of the binary fragments.
+The mass-ratio distribution should change as the companion gets with $a \sim 1000$ AU, at which point the disks from the two forming stars can interact, and companions can form directly from the disk of the primary star.
+Unfortunately, close companions to A- and B-type stars are very difficult to detect and characterize because they are so much dimmer than the primary star.
+We present the results of a survey searching for companions to A- and B-type stars using the direct spectroscopic detection technique, which is sensitive to late-type companions within $\sim 1''$ of the primary.
+We estimate the temperatures and masses of the 58 companion detections, 25 of which are new detections.
+We present the mass-ratio distribution for our sample, and find that it is well described by a gaussian with mean of $q = 0.35 \pm 0.04$.
+TODO: discuss implications.
 \end{abstract}
+\keywords{binaries: spectroscopic, stars:early-type, stars:formation, stars:statistics}
 
@@
 We denote the $n$th mass ratio sample for the $k$th star as $q_k^{(n)}$, and denote the number of these samples as $N_k$.
+
+TODO: Discuss the stars I actually use in the fit, and the ones I don't!
 
@@
 It was supported by a start-up grant to Adam Kraus as well as a University of Texas Continuing Fellowship to Kevin Gullikson.
-J.-E.
-Lee was supported by the Basic Science Research Program through the National Research Foundation of Korea (NRF) (grant No.
-NRF-2015R1A2A2A01004769) and the Korea
-Astronomy and Space Science Institute under the R\&D program (Project No. 2015-1-320-18) supervised by the Ministry of Science, ICT and Future Planning.
 

### 2016-01-31 fit_parameters.py
Added HIP 37322 to sample.

@@ -28,11 +28,12 @@ if __name__ == '__main__':
     pad = Padova_Isochrone()
 
     i = int(sys.argv[1])
-    pars = pd.read_csv('Primary_Parameters.csv').loc[i]
+    pars = pd.read_csv('data/Primary_Parameters.csv').loc[i]
     model = MyModel(pad, Teff=(pars.teff, pars.teff_err),
                       logg=(pars.logg, pars.logg_err),
                       feh=(pars.feh, pars.feh_err))
     starname = pars.star.replace(' ', '_')
+    print(starname)
     model.fit(basename=os.path.join('ParFitter', starname),
               overwrite=False)
     print(model.samples.describe())

### 2016-02-01 paper/ms.tex
Minor formatting stuff.
Added short discussion of the sample subset that I use in the analysis.

@@
 We estimate the stellar radius by interpolating Dartmouth pre main sequence isochrones [CITE] using the companion temperature and system age.
-TODO:
 
@@
 
-TODO: Discuss the stars I actually use in the fit, and the ones I don't!
+We do not use systems with more than one companion, unless known the wider companion separated by $ > 10''$ from the primary star (TODO: Check that this limit is true...).
+We mark the 47 companions we use in the mass ratio analysis with the fourth column of Table \ref{tab:companions}.
+Many of the companions we use in the analysis only have one detection in our data; 12/22 of these are previously known companions.
+The remaining 10 are new and unconfirmed detections; these all have very strong CCF signals and are likely to be confirmed with follow-up spectroscopy or imaging.
+We do not expect their inclusion to significantly alter the results.
+TODO: test this statement...
 
@@
 
-\begin{deluxetable}{|l|llllll|}
+\begin{deluxetable*}{|l|llllll|}
 \tabletypesize{\small}
@@
 \label{tab:imaging_obs}
-\end{deluxetable}
+\end{deluxetable*}
 
@@
 \LongTables
-\begin{deluxetable*}{|l|rrlrrrll|}
+\begin{deluxetable*}{|l|rrlrrrrll|}
 \tabletypesize{\small}
@@
 \tablehead{
-       \colhead{star} & \colhead{component} & \colhead{$N_\mathrm{obs}$}   &   \colhead{$T_\mathrm{eff}$} &   \colhead{$v\sin{i}$} &  \colhead{[Fe/H]} & \colhead{$\Delta K$} &   \colhead{Isochrone Mass} &   \colhead{Spectral Type Mass}
+     \colhead{} & \colhead{} & \colhead{} & \colhead{Used in} & \colhead{$T_\mathrm{eff}$} & \colhead{$v\sin{i}$} & \colhead{[Fe/H]} & \colhead{} & \multicolumn{2}{c}{Mass ($M_{\odot}$)} \\ 
+       \colhead{star} & \colhead{component} & \colhead{$N_\mathrm{obs}$} & \colhead{Analysis}  &   \colhead{(K)} &   \colhead{($\mathrm{km\ s}^{-1}$)} &  \colhead{(dex)} & \colhead{$\Delta K$} &   \colhead{Isochrone} &   \colhead{Spectral Type}
        }
@@
 \startdata
-   HIP 2548 & Aa,Ab &     2 &  $5732 \pm 112$ &      30 &    -0.5 &          0 &  $1.0^{+0.06}_{-0.04}$ &  $1.0^{+0.04}_{-0.03}$ \\
-   HIP 5310 & AB &     1 &  $3343 \pm 154$ &      30 &     0.0 &          0 &  $0.3^{+0.13}_{-0.08}$ &  $0.4^{+0.12}_{-0.12}$ \\
-     HR 545 & Aa,Ab$^{\dagger}$ &     3 &   $4312 \pm 87$ &       5 &    -0.5 &          0 &  $0.8^{+0.11}_{-0.10}$ &  $0.7^{+0.01}_{-0.02}$ \\
-     HR 604 & AB &     1 &  $4736 \pm 150$ &       5 &     0.5 &          0 &    $nan^{+nan}_{-nan}$ &  $0.8^{+0.02}_{-0.02}$ \\
-  HIP 10732 & AB$^{\dagger}$ &     2 &  $5578 \pm 109$ &       5 &     0.0 &          0 &  $1.0^{+0.29}_{-0.04}$ &  $1.0^{+0.02}_{-0.04}$ \\
-  HIP 12332 & AB$^{\dagger}$ &     2 &  $5551 \pm 107$ &      10 &     0.0 &          0 &    $nan^{+nan}_{-nan}$ &  $1.0^{+0.01}_{-0.04}$ \\
-  HIP 12706 & AB &     2 &  $6051 \pm 107$ &      10 &     0.0 &          0 &  $1.1^{+0.03}_{-0.03}$ &  $1.1^{+0.04}_{-0.05}$ \\
-  HIP 13165 & AB? &     1 &  $5773 \pm 163$ &       5 &    -0.5 &          0 &  $1.1^{+0.31}_{-0.08}$ &  $1.0^{+0.10}_{-0.03}$ \\
-  HIP 13327 & AB$^{\dagger}$ &     1 &  $5524 \pm 150$ &       5 &    -0.5 &          0 &  $1.2^{+0.20}_{-0.21}$ &  $1.0^{+0.03}_{-0.04}$ \\
-  HIP 14576 & Aa,Ab &     2 &  $6980 \pm 103$ &      10 &     0.0 &          0 &  $1.4^{+0.03}_{-0.03}$ &  $1.5^{+0.05}_{-0.03}$ \\
-  HIP 14764 & AB$^{\dagger}$ &     2 &  $5601 \pm 108$ &      30 &     0.5 &          0 &    $nan^{+nan}_{-nan}$ &  $1.0^{+0.03}_{-0.03}$ \\
-  HIP 16244 & AB &     2 &  $5592 \pm 107$ &       5 &    -0.5 &          0 &  $1.2^{+0.20}_{-0.22}$ &  $1.0^{+0.03}_{-0.03}$ \\
-  HIP 16340 & AB$^{\dagger}$ &     1 &  $6214 \pm 150$ &       5 &    -0.5 &          0 &  $1.2^{+0.29}_{-0.07}$ &  $1.2^{+0.06}_{-0.05}$ \\
-  HIP 16611 & AB &     1 &  $5476 \pm 154$ &       1 &     0.5 &          0 &  $0.9^{+0.04}_{-0.04}$ &  $0.9^{+0.04}_{-0.03}$ \\
-  HIP 17563 & AB &     1 &  $8574 \pm 147$ &       5 &     0.5 &          0 &  $1.9^{+0.25}_{-0.11}$ &  $2.0^{+0.05}_{-0.06}$ \\
-  HIP 18724 & AB &     1 &  $6831 \pm 154$ &      20 &     0.0 &          0 &  $1.7^{+0.13}_{-0.23}$ &  $1.4^{+0.04}_{-0.04}$ \\
-  HIP 19949 & AB$^{\dagger}$ &     1 &  $6492 \pm 155$ &      20 &    -0.5 &          0 &  $1.3^{+0.06}_{-0.05}$ &  $1.3^{+0.06}_{-0.06}$ \\
-  HIP 20380 & AB$^{\dagger}$ &     2 &  $6492 \pm 109$ &      20 &    -0.5 &          0 &  $1.3^{+0.04}_{-0.04}$ &  $1.3^{+0.03}_{-0.05}$ \\
-  HIP 21589 & Aa,Ab? &     1? &  $4562 \pm 154$ &       5 &     0.0 &          0 &  $0.7^{+0.04}_{-0.03}$ &  $0.8^{+0.02}_{-0.03}$ \\
-  HIP 22833 & AB &     2 &  $4745 \pm 107$ &      10 &     0.0 &          0 &  $0.8^{+0.02}_{-0.02}$ &  $0.8^{+0.02}_{-0.01}$ \\
-  HIP 22958 & Aa,Ab &     2 &  $6126 \pm 112$ &      30 &    -0.5 &          0 &  $1.4^{+0.22}_{-0.21}$ &  $1.2^{+0.04}_{-0.04}$ \\
-  HIP 23362 & AB$^{\dagger}$ &     1 &  $6283 \pm 158$ &       5 &    -0.5 &          0 &  $1.2^{+0.06}_{-0.05}$ &  $1.2^{+0.07}_{-0.05}$ \\
-  HIP 23916 & Aa,Ab$^{\dagger}$ &     1 &  $5450 \pm 158$ &       5 &    -0.5 &          0 &  $1.1^{+0.20}_{-0.20}$ &  $0.9^{+0.04}_{-0.03}$ \\
-  HIP 24902 & AB &     1 &  $5679 \pm 154$ &      30 &     0.0 &          0 &  $1.0^{+0.05}_{-0.04}$ &  $1.0^{+0.04}_{-0.03}$ \\
-  HIP 25143 & AB$^{\dagger}$ &     2 &  $5883 \pm 109$ &      30 &     0.0 &          0 &  $1.1^{+0.04}_{-0.03}$ &  $1.1^{+0.05}_{-0.07}$ \\
-  HIP 26126 & AB? &     3 &   $5841 \pm 91$ &       5 &    -0.5 &          0 &  $1.0^{+0.03}_{-0.03}$ &  $1.0^{+0.05}_{-0.04}$ \\
-  HIP 32607 & AB$^{\dagger}$ &     3 &   $5068 \pm 91$ &       5 &    -0.5 &          0 &  $0.8^{+0.02}_{-0.02}$ &  $0.9^{+0.01}_{-0.01}$ \\
-  HIP 37450 & AB$^{\dagger}$ &     1 &   $nan \pm nan$ & \nodata & \nodata &          0 &    $nan^{+nan}_{-nan}$ &    $nan^{+nan}_{-nan}$ \\
-  HIP 38593 & AB$^{\dagger}$ &     2 &  $5398 \pm 112$ &       5 &    -0.5 &          0 &  $1.3^{+0.08}_{-0.13}$ &  $0.9^{+0.03}_{-0.03}$ \\
-  HIP 38846 & AB$^{\dagger}$ &     1 &  $6595 \pm 158$ &      10 &     0.0 &          0 &  $1.7^{+0.12}_{-0.21}$ &  $1.3^{+0.09}_{-0.05}$ \\
-  HIP 39847 & Aa,Ab$^{\dagger}$ &     2 &  $5750 \pm 107$ &      10 &    -0.5 &          0 &  $1.0^{+0.04}_{-0.03}$ &  $1.0^{+0.05}_{-0.03}$ \\
-  HIP 40881 & AB$^{\dagger}$ &     1 &  $4562 \pm 154$ &      10 &    -0.5 &          0 &  $0.8^{+0.18}_{-0.05}$ &  $0.8^{+0.02}_{-0.03}$ \\
-  HIP 42129 & AB &     1 &  $5241 \pm 158$ &      10 &    -0.5 &          0 &  $1.2^{+0.12}_{-0.18}$ &  $0.9^{+0.04}_{-0.02}$ \\
-  HIP 46283 & AB? &     3 &   $9268 \pm 85$ &      10 &     0.5 &          0 &    $nan^{+nan}_{-nan}$ &  $2.2^{+0.02}_{-0.02}$ \\
-  HIP 55266 & AB &     1 &  $8483 \pm 139$ &      30 &    -0.5 &          0 &  $1.8^{+0.06}_{-0.04}$ &  $2.0^{+0.06}_{-0.05}$ \\
-  HIP 63945 & Aa,Ab or AC? &     1 &  $7038 \pm 162$ &      10 &    -0.5 &          0 &  $1.6^{+0.26}_{-0.16}$ &  $1.5^{+0.08}_{-0.06}$ \\
-  HIP 72154 & AB$^{\dagger}$ &     1 &  $4918 \pm 162$ &      30 &    -0.5 &          0 &  $0.9^{+0.22}_{-0.09}$ &  $0.8^{+0.03}_{-0.03}$ \\
-  HIP 76267 & AB &     1 &  $5449 \pm 158$ &       5 &    -0.5 &          0 &  $0.9^{+0.04}_{-0.04}$ &  $0.9^{+0.04}_{-0.03}$ \\
-  HIP 77336 & AB$^{\dagger}$ &     2 &  $6407 \pm 112$ &      20 &     0.0 &          0 &  $1.2^{+0.04}_{-0.04}$ &  $1.3^{+0.04}_{-0.05}$ \\
-  HIP 77516 & AB &     1 &  $6825 \pm 141$ &       5 &     0.5 &          0 &  $1.4^{+0.21}_{-0.06}$ &  $1.4^{+0.03}_{-0.04}$ \\
-  HIP 78820 & AB &     1 &  $5658 \pm 158$ &       5 &    -0.5 &          0 &  $1.3^{+0.11}_{-0.13}$ &  $1.0^{+0.04}_{-0.04}$ \\
-  HIP 79199 & AB &     1 &  $4616 \pm 158$ &       5 &    -0.5 &          0 &  $0.9^{+0.14}_{-0.14}$ &  $0.8^{+0.02}_{-0.03}$ \\
-  HIP 79404 & AB$^{\dagger}$ &     2 &  $4773 \pm 112$ &      10 &    -0.5 &          0 &  $1.1^{+0.07}_{-0.08}$ &  $0.8^{+0.02}_{-0.01}$ \\
-  HIP 80460 & AB &     1 &  $6391 \pm 155$ &      10 &     0.0 &          0 &  $1.2^{+0.06}_{-0.05}$ &  $1.3^{+0.06}_{-0.06}$ \\
-  HIP 82673 & AB$^{\dagger}$ &     2 &  $4668 \pm 112$ &       5 &     0.5 &          0 &  $0.8^{+0.03}_{-0.03}$ &  $0.8^{+0.01}_{-0.02}$ \\
-  HIP 84606 & AB &     1 &  $5476 \pm 154$ &      10 &    -0.5 &          0 &  $0.9^{+0.05}_{-0.04}$ &  $0.9^{+0.04}_{-0.03}$ \\
-  HIP 88116 & AB$^{\dagger}$ &     2 &  $5293 \pm 112$ &       5 &     0.0 &          0 &  $0.9^{+0.03}_{-0.03}$ &  $0.9^{+0.02}_{-0.03}$ \\
-  HIP 88818 & Aa,Ab &     3 &   $5296 \pm 91$ &      20 &    -0.5 &          0 &  $0.9^{+0.02}_{-0.02}$ &  $0.9^{+0.02}_{-0.03}$ \\
-  HIP 88817 & Aa,Ab &     1 &  $3647 \pm 154$ &      20 &     0.0 &          0 &  $0.5^{+0.07}_{-0.10}$ &  $0.5^{+0.03}_{-0.05}$ \\
-  HIP 91118 & AB &     1 &  $6492 \pm 155$ &      10 &    -0.5 &          0 &  $1.3^{+0.26}_{-0.07}$ &  $1.3^{+0.06}_{-0.06}$ \\
-  HIP 93805 & Aa,Ab$^{\dagger}$ &     2 &  $4054 \pm 109$ &       5 &    -0.5 &          0 &  $0.6^{+0.03}_{-0.03}$ &  $0.6^{+0.04}_{-0.02}$ \\
-  HIP 96840 & AB &     1 &  $9942 \pm 152$ &      10 &     0.0 &          0 &    $nan^{+nan}_{-nan}$ &  $2.3^{+0.03}_{-0.01}$ \\
- HIP 100221 & AB &     1 &  $5273 \pm 154$ &      20 &    -0.5 &          0 &  $0.9^{+0.29}_{-0.07}$ &  $0.9^{+0.04}_{-0.03}$ \\
- HIP 100907 & AB$^{\dagger}$ &     2 &  $5222 \pm 109$ &      10 &     0.0 &          0 &  $0.9^{+0.03}_{-0.03}$ &  $0.9^{+0.04}_{-0.02}$ \\
- HIP 103298 & Aa,Ab &     3 &   $4615 \pm 90$ &       5 &    -0.5 &          0 &  $0.7^{+0.02}_{-0.02}$ &  $0.8^{+0.01}_{-0.02}$ \\
- HIP 109139 & AB &     2 &  $5710 \pm 112$ &      20 &    -0.5 &          0 &  $1.0^{+0.04}_{-0.03}$ &  $1.0^{+0.03}_{-0.03}$ \\
- HIP 109521 & Aa,Ab$^{\dagger}$ &     3 &   $4412 \pm 87$ &      10 &     0.0 &          0 &  $0.7^{+0.02}_{-0.02}$ &  $0.7^{+0.01}_{-0.01}$ \\
- HIP 115115 & AB &     3 &   $4943 \pm 91$ &       5 &    -0.5 &          0 &  $0.8^{+0.02}_{-0.02}$ &  $0.8^{+0.02}_{-0.02}$
+   HIP 2548 & Aa,Ab &     2 & yes &  $5732 \pm 112$ &      30 &    -0.5 &          0 &  $1.0^{+0.06}_{-0.04}$ &  $1.0^{+0.04}_{-0.03}$ \\
+   HIP 5310 & AB &     1 & yes &  $3343 \pm 154$ &      30 &     0.0 &          0 &  $0.3^{+0.13}_{-0.08}$ &  $0.4^{+0.12}_{-0.12}$ \\
+     HR 545 & Aa,Ab$^{\dagger}$ &     3 & yes &   $4312 \pm 87$ &       5 &    -0.5 &          0 &  $0.8^{+0.11}_{-0.10}$ &  $0.7^{+0.01}_{-0.02}$ \\
+     HR 604 & AB &     1 & no &  $4736 \pm 150$ &       5 &     0.5 &          0 &    $nan^{+nan}_{-nan}$ &  $0.8^{+0.02}_{-0.02}$ \\
+  HIP 10732 & AB$^{\dagger}$ &     2 & yes &  $5578 \pm 109$ &       5 &     0.0 &          0 &  $1.0^{+0.29}_{-0.04}$ &  $1.0^{+0.02}_{-0.04}$ \\
+  HIP 12332 & AB$^{\dagger}$ &     2 & yes &  $5551 \pm 107$ &      10 &     0.0 &          0 &    $nan^{+nan}_{-nan}$ &  $1.0^{+0.01}_{-0.04}$ \\
+  HIP 12706 & AB &     2 & yes &  $6051 \pm 107$ &      10 &     0.0 &          0 &  $1.1^{+0.03}_{-0.03}$ &  $1.1^{+0.04}_{-0.05}$ \\
+  HIP 13165 & AB? &     1 & no &  $5773 \pm 163$ &       5 &    -0.5 &          0 &  $1.1^{+0.31}_{-0.08}$ &  $1.0^{+0.10}_{-0.03}$ \\
+  HIP 13327 & AB$^{\dagger}$ &     1 & yes &  $5524 \pm 150$ &       5 &    -0.5 &          0 &  $1.2^{+0.20}_{-0.21}$ &  $1.0^{+0.03}_{-0.04}$ \\
+  HIP 14576 & Aa,Ab &     2 & no &  $6980 \pm 103$ &      10 &     0.0 &          0 &  $1.4^{+0.03}_{-0.03}$ &  $1.5^{+0.05}_{-0.03}$ \\
+  HIP 14764 & AB$^{\dagger}$ &     2 & yes &  $5601 \pm 108$ &      30 &     0.5 &          0 &    $nan^{+nan}_{-nan}$ &  $1.0^{+0.03}_{-0.03}$ \\
+  HIP 16244 & AB &     2 & yes &  $5592 \pm 107$ &       5 &    -0.5 &          0 &  $1.2^{+0.20}_{-0.22}$ &  $1.0^{+0.03}_{-0.03}$ \\
+  HIP 16340 & AB$^{\dagger}$ &     1 & yes &  $6214 \pm 150$ &       5 &    -0.5 &          0 &  $1.2^{+0.29}_{-0.07}$ &  $1.2^{+0.06}_{-0.05}$ \\
+  HIP 16611 & AB &     1 & no &  $5476 \pm 154$ &       1 &     0.5 &          0 &  $0.9^{+0.04}_{-0.04}$ &  $0.9^{+0.04}_{-0.03}$ \\
+  HIP 17563 & AB &     1 & yes &  $8574 \pm 147$ &       5 &     0.5 &          0 &  $1.9^{+0.25}_{-0.11}$ &  $2.0^{+0.05}_{-0.06}$ \\
+  HIP 18724 & AB &     1 & no &  $6831 \pm 154$ &      20 &     0.0 &          0 &  $1.7^{+0.13}_{-0.23}$ &  $1.4^{+0.04}_{-0.04}$ \\
+  HIP 19949 & AB$^{\dagger}$ &     1 & yes &  $6492 \pm 155$ &      20 &    -0.5 &          0 &  $1.3^{+0.06}_{-0.05}$ &  $1.3^{+0.06}_{-0.06}$ \\
+  HIP 20380 & AB$^{\dagger}$ &     2 & yes &  $6492 \pm 109$ &      20 &    -0.5 &          0 &  $1.3^{+0.04}_{-0.04}$ &  $1.3^{+0.03}_{-0.05}$ \\
+  HIP 21589 & Aa,Ab &     1 & yes &  $4562 \pm 154$ &       5 &     0.0 &          0 &  $0.7^{+0.04}_{-0.03}$ &  $0.8^{+0.02}_{-0.03}$ \\
+  HIP 22833 & AB &     2 & yes &  $4745 \pm 107$ &      10 &     0.0 &          0 &  $0.8^{+0.02}_{-0.02}$ &  $0.8^{+0.02}_{-0.01}$ \\
+  HIP 22958 & Aa,Ab &     2 & yes &  $6126 \pm 112$ &      30 &    -0.5 &          0 &  $1.4^{+0.22}_{-0.21}$ &  $1.2^{+0.04}_{-0.04}$ \\
+  HIP 23362 & AB$^{\dagger}$ &     1 & yes &  $6283 \pm 158$ &       5 &    -0.5 &          0 &  $1.2^{+0.06}_{-0.05}$ &  $1.2^{+0.07}_{-0.05}$ \\
+  HIP 23916 & Aa,Ab$^{\dagger}$ &     1 & yes &  $5450 \pm 158$ &       5 &    -0.5 &          0 &  $1.1^{+0.20}_{-0.20}$ &  $0.9^{+0.04}_{-0.03}$ \\
+  HIP 24902 & AB &     1 & yes &  $5679 \pm 154$ &      30 &     0.0 &          0 &  $1.0^{+0.05}_{-0.04}$ &  $1.0^{+0.04}_{-0.03}$ \\
+  HIP 25143 & AB$^{\dagger}$ &     2 & yes &  $5883 \pm 109$ &      30 &     0.0 &          0 &  $1.1^{+0.04}_{-0.03}$ &  $1.1^{+0.05}_{-0.07}$ \\
+  HIP 26126 & AB? &     3 & yes &   $5841 \pm 91$ &       5 &    -0.5 &          0 &  $1.0^{+0.03}_{-0.03}$ &  $1.0^{+0.05}_{-0.04}$ \\
+  HIP 32607 & AB$^{\dagger}$ &     3 & yes &   $5068 \pm 91$ &       5 &    -0.5 &          0 &  $0.8^{+0.02}_{-0.02}$ &  $0.9^{+0.01}_{-0.01}$ \\
+  HIP 37450 & AB$^{\dagger}$ &     1 & yes &   $nan \pm nan$ & \nodata & \nodata &          0 &    $nan^{+nan}_{-nan}$ &    $nan^{+nan}_{-nan}$ \\
+  HIP 38593 & AB$^{\dagger}$ &     2 & yes &  $5398 \pm 112$ &       5 &    -0.5 &          0 &  $1.3^{+0.08}_{-0.13}$ &  $0.9^{+0.03}_{-0.03}$ \\
+  HIP 38846 & AB$^{\dagger}$ &     1 & yes &  $6595 \pm 158$ &      10 &     0.0 &          0 &  $1.7^{+0.12}_{-0.21}$ &  $1.3^{+0.09}_{-0.05}$ \\
+  HIP 39847 & Aa,Ab$^{\dagger}$ &     2 & no &  $5750 \pm 107$ &      10 &    -0.5 &          0 &  $1.0^{+0.04}_{-0.03}$ &  $1.0^{+0.05}_{-0.03}$ \\
+  HIP 40881 & AB$^{\dagger}$ &     1 & yes &  $4562 \pm 154$ &      10 &    -0.5 &          0 &  $0.8^{+0.18}_{-0.05}$ &  $0.8^{+0.02}_{-0.03}$ \\
+  HIP 42129 & AB &     1 & yes &  $5241 \pm 158$ &      10 &    -0.5 &          0 &  $1.2^{+0.12}_{-0.18}$ &  $0.9^{+0.04}_{-0.02}$ \\
+  HIP 46283 & AB? &     3 & yes &   $9268 \pm 85$ &      10 &     0.5 &          0 &    $nan^{+nan}_{-nan}$ &  $2.2^{+0.02}_{-0.02}$ \\
+  HIP 55266 & AB &     1 & no &  $8483 \pm 139$ &      30 &    -0.5 &          0 &  $1.8^{+0.06}_{-0.04}$ &  $2.0^{+0.06}_{-0.05}$ \\
+  HIP 63945 & Aa,Ab or AC? &     1 & no &  $7038 \pm 162$ &      10 &    -0.5 &          0 &  $1.6^{+0.26}_{-0.16}$ &  $1.5^{+0.08}_{-0.06}$ \\
+  HIP 72154 & AB$^{\dagger}$ &     1 & yes &  $4918 \pm 162$ &      30 &    -0.5 &          0 &  $0.9^{+0.22}_{-0.09}$ &  $0.8^{+0.03}_{-0.03}$ \\
+  HIP 76267 & AB &     1 & yes &  $5449 \pm 158$ &       5 &    -0.5 &          0 &  $0.9^{+0.04}_{-0.04}$ &  $0.9^{+0.04}_{-0.03}$ \\
+  HIP 77336 & AB$^{\dagger}$ &     2 & yes &  $6407 \pm 112$ &      20 &     0.0 &          0 &  $1.2^{+0.04}_{-0.04}$ &  $1.3^{+0.04}_{-0.05}$ \\
+  HIP 77516 & AB &     1 & yes &  $6825 \pm 141$ &       5 &     0.5 &          0 &  $1.4^{+0.21}_{-0.06}$ &  $1.4^{+0.03}_{-0.04}$ \\
+  HIP 78820 & AB &     1 & no &  $5658 \pm 158$ &       5 &    -0.5 &          0 &  $1.3^{+0.11}_{-0.13}$ &  $1.0^{+0.04}_{-0.04}$ \\
+  HIP 79199 & AB &     1 & no &  $4616 \pm 158$ &       5 &    -0.5 &          0 &  $0.9^{+0.14}_{-0.14}$ &  $0.8^{+0.02}_{-0.03}$ \\
+  HIP 79404 & AB$^{\dagger}$ &     2 & yes &  $4773 \pm 112$ &      10 &    -0.5 &          0 &  $1.1^{+0.07}_{-0.08}$ &  $0.8^{+0.02}_{-0.01}$ \\
+  HIP 80460 & AB &     1 & yes &  $6391 \pm 155$ &      10 &     0.0 &          0 &  $1.2^{+0.06}_{-0.05}$ &  $1.3^{+0.06}_{-0.06}$ \\
+  HIP 82673 & AB$^{\dagger}$ &     2 & yes &  $4668 \pm 112$ &       5 &     0.5 &          0 &  $0.8^{+0.03}_{-0.03}$ &  $0.8^{+0.01}_{-0.02}$ \\
+  HIP 84606 & AB &     1 & yes &  $5476 \pm 154$ &      10 &    -0.5 &          0 &  $0.9^{+0.05}_{-0.04}$ &  $0.9^{+0.04}_{-0.03}$ \\
+  HIP 88116 & AB$^{\dagger}$ &     2 & yes &  $5293 \pm 112$ &       5 &     0.0 &          0 &  $0.9^{+0.03}_{-0.03}$ &  $0.9^{+0.02}_{-0.03}$ \\
+  HIP 88817 & Ba,Bb$^{\dagger}$ &     1 & yes &  $3647 \pm 154$ &      20 &     0.0 &          0 &  $0.5^{+0.07}_{-0.10}$ &  $0.5^{+0.03}_{-0.05}$ \\
+  HIP 88818 & Aa,Ab &     3 & yes &   $5296 \pm 91$ &      20 &    -0.5 &          0 &  $0.9^{+0.02}_{-0.02}$ &  $0.9^{+0.02}_{-0.03}$ \\
+  HIP 91118 & AB &     1 & yes &  $6492 \pm 155$ &      10 &    -0.5 &          0 &  $1.3^{+0.26}_{-0.07}$ &  $1.3^{+0.06}_{-0.06}$ \\
+  HIP 93805 & Aa,Ab$^{\dagger}$ &     2 & yes &  $4054 \pm 109$ &       5 &    -0.5 &          0 &  $0.6^{+0.03}_{-0.03}$ &  $0.6^{+0.04}_{-0.02}$ \\
+  HIP 96840 & AB &     1 & yes &  $9942 \pm 152$ &      10 &     0.0 &          0 &    $nan^{+nan}_{-nan}$ &  $2.3^{+0.03}_{-0.01}$ \\
+ HIP 100221 & AB &     1 & yes &  $5273 \pm 154$ &      20 &    -0.5 &          0 &  $0.9^{+0.29}_{-0.07}$ &  $0.9^{+0.04}_{-0.03}$ \\
+ HIP 100907 & AB$^{\dagger}$ &     2 & yes &  $5222 \pm 109$ &      10 &     0.0 &          0 &  $0.9^{+0.03}_{-0.03}$ &  $0.9^{+0.04}_{-0.02}$ \\
+ HIP 103298 & Aa,Ab &     3 & yes &   $4615 \pm 90$ &       5 &    -0.5 &          0 &  $0.7^{+0.02}_{-0.02}$ &  $0.8^{+0.01}_{-0.02}$ \\
+ HIP 109139 & AB &     2 & yes &  $5710 \pm 112$ &      20 &    -0.5 &          0 &  $1.0^{+0.04}_{-0.03}$ &  $1.0^{+0.03}_{-0.03}$ \\
+ HIP 109521 & Aa,Ab$^{\dagger}$ &     3 & no &   $4412 \pm 87$ &      10 &     0.0 &          0 &  $0.7^{+0.02}_{-0.02}$ &  $0.7^{+0.01}_{-0.01}$ \\
+ HIP 115115 & AB &     3 & yes &   $4943 \pm 91$ &       5 &    -0.5 &          0 &  $0.8^{+0.02}_{-0.02}$ &  $0.8^{+0.02}_{-0.02}$
 

### 2016-02-02 paper/ms.tex
Fixed spectral types in Table 1
Fixed isochrone masses in Table 3
Fixed IGRINS snr calculations.
Added HIP 96840 to Table 4.
Added three stars to companion table, and removed delta-K column.

@@
     HIP 2505 &           B8Vn &    00:31:46.36 &   +54:31:20.23 &  6962.71 &       TS23 &      804 &  1960 \\
-    HIP 2505 &           B8Vn &    00:31:46.36 &   +54:31:20.23 &  6945.71 &     IGRINS &      224 &     450 \\
-    HIP 2548 &          B9.5V &    00:32:23.78 &   +06:57:19.66 &  7240.93 &     IGRINS &      360 &     490 \\
+    HIP 2505 &           B8Vn &    00:31:46.36 &   +54:31:20.23 &  6945.71 &     IGRINS &      224 &   210 \\
+    HIP 2548 &          B9.5V &    00:32:23.78 &   +06:57:19.66 &  7240.93 &     IGRINS &      360 &   100 \\
     HIP 2548 &          B9.5V &    00:32:23.78 &   +06:57:19.66 &  6516.84 &        HRS &      412 &  1070 \\
-    HIP 2912 &            B5V &    00:36:52.85 &    +33:43:9.64 &  7238.96 &     IGRINS &      367 &     790 \\
+    HIP 2912 &            B5V &    00:36:52.85 &    +33:43:9.64 &  7238.96 &     IGRINS &      367 &   130 \\
     HIP 2912 &            B5V &    00:36:52.85 &    +33:43:9.64 &  6583.78 &       TS23 &      199 &  2460 \\
@@
     HIP 3478 &            B5V &    00:44:26.19 &   +47:51:50.34 &  6963.63 &       TS23 &     1200 &  1020 \\
-    HIP 3478 &            B5V &    00:44:26.19 &   +47:51:50.34 &  7288.82 &     IGRINS &      540 &     800 \\
+    HIP 3478 &            B5V &    00:44:26.19 &   +47:51:50.34 &  7288.82 &     IGRINS &      540 &    30 \\
     HIP 3478 &            B5V &    00:44:26.19 &   +47:51:50.34 &  6669.53 &       TS23 &      743 &  1870 \\
-    HIP 3478 &            B5V &    00:44:26.19 &   +47:51:50.34 &  6945.72 &     IGRINS &      224 &     260 \\
+    HIP 3478 &            B5V &    00:44:26.19 &   +47:51:50.34 &  6945.72 &     IGRINS &      224 &   150 \\
     HIP 3741 &            B9V &     00:48:1.06 &   -21:43:20.99 &  7174.89 &     CHIRON &     3981 &   430 \\
     HIP 3741 &            B9V &     00:48:1.06 &   -21:43:20.99 &  7175.90 &     CHIRON &     3561 &   420 \\
-    HIP 3881 &     F8IV-V+M4V &    00:49:48.85 &   +41:04:44.08 &  6585.70 &       TS23 &      222 &    1690 \\
-    HIP 3881 &     F8IV-V+M4V &    00:49:48.85 &   +41:04:44.08 &  6964.60 &       TS23 &     1200 &     710 \\
-    HIP 3881 &     F8IV-V+M4V &    00:49:48.85 &   +41:04:44.08 &  6945.74 &     IGRINS &      224 &     510 \\
+    HIP 3881 &            B5V &    00:49:48.85 &   +41:04:44.08 &  6585.70 &       TS23 &      222 &  1690 \\
+    HIP 3881 &            B5V &    00:49:48.85 &   +41:04:44.08 &  6964.60 &       TS23 &     1200 &   710 \\
+    HIP 3881 &            B5V &    00:49:48.85 &   +41:04:44.08 &  6945.74 &     IGRINS &      224 &   200 \\
     HIP 4436 &            A5V &    00:56:45.21 &   +38:29:57.64 &  6585.76 &       TS23 &      129 &  1940 \\
     HIP 5131 &           A1Vn &    01:05:40.96 &   +21:28:23.45 &  6587.70 &       TS23 &      655 &  1780 \\
-    HIP 5131 &           A1Vn &    01:05:40.96 &   +21:28:23.45 &  7083.57 &     IGRINS &      930 &     130 \\
-    HIP 5131 &           A1Vn &    01:05:40.96 &   +21:28:23.45 &  6847.89 &     IGRINS &     1600 &     490 \\
+    HIP 5131 &           A1Vn &    01:05:40.96 &   +21:28:23.45 &  7083.57 &     IGRINS &      930 &    70 \\
+    HIP 5131 &           A1Vn &    01:05:40.96 &   +21:28:23.45 &  6847.89 &     IGRINS &     1600 &   110 \\
     HIP 5132 &           A0Vn &    01:05:41.71 &   +21:27:55.60 &  6587.77 &       TS23 &      535 &  1550 \\
-    HIP 5132 &           A0Vn &    01:05:41.71 &   +21:27:55.60 &  6847.89 &     IGRINS &      480 &     490 \\
-    HIP 5310 &            A3V &    01:07:57.16 &   +20:44:20.83 &  6945.75 &     IGRINS &      224 &     390 \\
+    HIP 5132 &           A0Vn &    01:05:41.71 &   +21:27:55.60 &  6847.89 &     IGRINS &      480 &   110 \\
+    HIP 5310 &            A3V &    01:07:57.16 &   +20:44:20.83 &  6945.75 &     IGRINS &      224 &   200 \\
     HIP 5348 &        B6V+B9V &    01:08:23.08 &   -55:14:44.73 &  6325.56 &     CHIRON &      186 &   390 \\
     HIP 5361 &            B8V &    01:08:33.47 &   +58:15:48.41 &  6523.84 &        HRS &     1000 &   810 \\
-    HIP 5518 &          A0Vnn &    01:10:39.32 &   +68:46:43.04 &  7238.94 &     IGRINS &      540 &     750 \\
-    HIP 5518 &          A0Vnn &    01:10:39.32 &   +68:46:43.04 &  6945.77 &     IGRINS &      224 &     370 \\
-    HIP 5626 &            A3V &    01:12:16.82 &   +79:40:26.27 &  6945.88 &     IGRINS &      224 &     270 \\
+    HIP 5518 &          A0Vnn &    01:10:39.32 &   +68:46:43.04 &  7238.94 &     IGRINS &      540 &    80 \\
+    HIP 5518 &          A0Vnn &    01:10:39.32 &   +68:46:43.04 &  6945.77 &     IGRINS &      224 &   160 \\
+    HIP 5626 &            A3V &    01:12:16.82 &   +79:40:26.27 &  6945.88 &     IGRINS &      224 &   160 \\
     HIP 7345 &            A1V &    01:34:37.78 &   -15:40:34.90 &  6888.76 &     CHIRON &     1080 &   480 \\
@@
     HIP 8704 &          B1.5V &    01:51:59.32 &   +55:08:50.58 &  6506.90 &        HRS &      365 &   420 \\
-    HIP 8704 &          B1.5V &    01:51:59.32 &   +55:08:50.58 &  7084.57 &     IGRINS &      960 &     140 \\
-    HIP 8704 &          B1.5V &    01:51:59.32 &   +55:08:50.58 &  7237.93 &     IGRINS &      720 &     630 \\
-      HR 545 &         B9.5IV &    01:53:31.77 &   +19:17:46.27 &  6668.56 &       TS23 &      597 &    1920 \\
-      HR 545 &         B9.5IV &    01:53:31.77 &   +19:17:46.27 &  6586.75 &       TS23 &      265 &    1710 \\
-      HR 545 &         B9.5IV &    01:53:31.77 &   +19:17:46.27 &  6945.81 &     IGRINS &      224 &     540 \\
+    HIP 8704 &          B1.5V &    01:51:59.32 &   +55:08:50.58 &  7084.57 &     IGRINS &      960 &    30 \\
+    HIP 8704 &          B1.5V &    01:51:59.32 &   +55:08:50.58 &  7237.93 &     IGRINS &      720 &    90 \\
+      HR 545 &            B9V &    01:53:31.77 &   +19:17:46.27 &  6668.56 &       TS23 &      597 &  1920 \\
+      HR 545 &            B9V &    01:53:31.77 &   +19:17:46.27 &  6586.75 &       TS23 &      265 &  1710 \\
+      HR 545 &            B9V &    01:53:31.77 &   +19:17:46.27 &  6945.81 &     IGRINS &      224 &   230 \\
     HIP 9312 &           A0Vn &    01:59:38.04 &   +64:37:17.76 &  6586.78 &       TS23 &      419 &  1750 \\
-    HIP 9564 &           A1Vn &    02:02:52.48 &    +64:54:5.27 &  6945.78 &     IGRINS &      224 &     180 \\
+    HIP 9564 &           A1Vn &    02:02:52.48 &    +64:54:5.27 &  6945.78 &     IGRINS &      224 &   140 \\
       HR 604 &        B8V+A0V &    02:03:54.72 &   +42:19:51.41 &  6585.86 &       TS23 &      349 &  1650 \\
@@
    HIP 10670 &          A1Vnn &    02:17:18.87 &   +33:50:49.90 &  6618.68 &       TS23 &      141 &  1810 \\
-   HIP 10732 &           A1Vn &     02:18:7.54 &    +19:54:4.19 &  6945.82 &     IGRINS &      224 &     290 \\
-   HIP 10732 &           A1Vn &     02:18:7.54 &    +19:54:4.19 &  7083.56 &     IGRINS &      240 &     160 \\
+   HIP 10732 &           A1Vn &     02:18:7.54 &    +19:54:4.19 &  6945.82 &     IGRINS &      224 &   180 \\
+   HIP 10732 &           A1Vn &     02:18:7.54 &    +19:54:4.19 &  7083.56 &     IGRINS &      240 &   110 \\
    HIP 11345 &            A0V &    02:25:57.01 &   -12:17:25.71 &  6894.90 &     CHIRON &      540 &   520 \\
    HIP 12332 &            A7V &    02:38:48.99 &   +21:57:41.06 &  6677.54 &       TS23 &     1107 &  1530 \\
-   HIP 12332 &            A7V &    02:38:48.99 &   +21:57:41.06 &  6947.79 &     IGRINS &      224 &     430 \\
+   HIP 12332 &            A7V &    02:38:48.99 &   +21:57:41.06 &  6947.79 &     IGRINS &      224 &   170 \\
    HIP 12706 &       A2Vn+F4V &    02:43:18.04 &    +03:14:8.94 &  6584.86 &       TS23 &      362 &   990 \\
-   HIP 12706 &       A2Vn+F4V &    02:43:18.04 &    +03:14:8.94 &  6946.84 &     IGRINS &      224 &    2280 \\
+   HIP 12706 &       A2Vn+F4V &    02:43:18.04 &    +03:14:8.94 &  6946.84 &     IGRINS &      224 &   150 \\
    HIP 12719 &            B3V &    02:43:27.11 &   +27:42:25.72 &  6583.87 &       TS23 &      264 &  1720 \\
    HIP 12803 &           B9Vn &    02:44:32.97 &   +15:18:42.71 &  6676.53 &       TS23 &      452 &  1410 \\
-   HIP 12803 &           B9Vn &    02:44:32.97 &   +15:18:42.71 &  6947.80 &     IGRINS &      224 &     450 \\
-   HIP 12803 &           B9Vn &    02:44:32.97 &   +15:18:42.71 &  7240.95 &     IGRINS &      780 &    1120 \\
+   HIP 12803 &           B9Vn &    02:44:32.97 &   +15:18:42.71 &  6947.80 &     IGRINS &      224 &   140 \\
+   HIP 12803 &           B9Vn &    02:44:32.97 &   +15:18:42.71 &  7240.95 &     IGRINS &      780 &   120 \\
    HIP 13165 &            B6V &    02:49:17.56 &   +17:27:51.52 &  6518.91 &        HRS &      275 &   850 \\
@@
    HIP 13717 &            A3V &    02:56:37.42 &   -03:42:44.35 &  6970.75 &     CHIRON &      703 &   550 \\
-   HIP 13879 &           A2Vn &    02:58:45.67 &   +39:39:45.81 &  6945.79 &     IGRINS &      224 &     620 \\
+   HIP 13879 &           A2Vn &    02:58:45.67 &   +39:39:45.81 &  6945.79 &     IGRINS &      224 &   260 \\
    HIP 13879 &           A2Vn &    02:58:45.67 &   +39:39:45.81 &  6681.68 &       TS23 &      930 &   230 \\
@@
    HIP 14764 &            B8V &    03:10:38.79 &   +11:52:21.44 &  6679.53 &       TS23 &      532 &  1370 \\
-   HIP 14764 &            B8V &    03:10:38.79 &   +11:52:21.44 &  6946.80 &     IGRINS &      360 &     410 \\
-   HIP 14862 &          A2Vnn &    03:11:56.27 &   +74:23:37.17 &  6945.86 &     IGRINS &      224 &     500 \\
-   HIP 14862 &          A2Vnn &    03:11:56.27 &   +74:23:37.17 &  7084.60 &     IGRINS &     1200 &     370 \\
-   HIP 15110 &            A1V &    03:14:54.10 &   +21:02:40.01 &  6946.83 &     IGRINS &      224 &     630 \\
+   HIP 14764 &            B8V &    03:10:38.79 &   +11:52:21.44 &  6946.80 &     IGRINS &      360 &   150 \\
+   HIP 14862 &          A2Vnn &    03:11:56.27 &   +74:23:37.17 &  6945.86 &     IGRINS &      224 &   180 \\
+   HIP 14862 &          A2Vnn &    03:11:56.27 &   +74:23:37.17 &  7084.60 &     IGRINS &     1200 &   120 \\
+   HIP 15110 &            A1V &    03:14:54.10 &   +21:02:40.01 &  6946.83 &     IGRINS &      224 &   120 \\
    HIP 15338 &            B8V &    03:17:47.35 &   +44:01:30.08 &  6523.90 &        HRS &      570 &   690 \\
@@
    HIP 16210 &           B6Vn &    03:28:52.33 &   +49:50:54.17 &  6676.58 &       TS23 &      406 &  1440 \\
-   HIP 16210 &           B6Vn &    03:28:52.33 &   +49:50:54.17 &  6945.84 &     IGRINS &      224 &     430 \\
+   HIP 16210 &           B6Vn &    03:28:52.33 &   +49:50:54.17 &  6945.84 &     IGRINS &      224 &   160 \\
    HIP 16244 &            B3V &    03:29:22.05 &   +49:30:32.21 &  6583.84 &       TS23 &      311 &  1750 \\
-   HIP 16244 &            B3V &    03:29:22.05 &   +49:30:32.21 &  6945.83 &     IGRINS &      224 &     430 \\
+   HIP 16244 &            B3V &    03:29:22.05 &   +49:30:32.21 &  6945.83 &     IGRINS &      224 &   230 \\
    HIP 16285 &            A5V &    03:29:55.15 &    -42:38:3.32 &  6933.84 &     CHIRON &      767 &   570 \\
    HIP 16322 &           A0Vn &    03:30:24.47 &   +11:20:11.19 &  6944.72 &     CHIRON &      680 &   410 \\
-   HIP 16322 &           A0Vn &    03:30:24.47 &   +11:20:11.19 &  6946.82 &     IGRINS &      224 &     590 \\
+   HIP 16322 &           A0Vn &    03:30:24.47 &   +11:20:11.19 &  6946.82 &     IGRINS &      224 &   170 \\
    HIP 16340 &            B8V &    03:30:36.95 &   +48:06:12.95 &  6678.54 &       TS23 &      570 &  1410 \\
-   HIP 16599 &            A3V &    03:33:39.06 &   +54:58:29.49 &  6945.85 &     IGRINS &      224 &     280 \\
-   HIP 16611 &            B9V &    03:33:47.28 &   -21:37:58.38 &  6946.85 &     IGRINS &      224 &     420 \\
+   HIP 16599 &            A3V &    03:33:39.06 &   +54:58:29.49 &  6945.85 &     IGRINS &      224 &   170 \\
+   HIP 16611 &            B9V &    03:33:47.28 &   -21:37:58.38 &  6946.85 &     IGRINS &      224 &   210 \\
    HIP 16611 &            B9V &    03:33:47.28 &   -21:37:58.38 &  6522.88 &     CHIRON &      255 &   580 \\
@@
    HIP 17563 &            B3V &    03:45:40.44 &   +06:02:59.97 &  6538.82 &     CHIRON &     1088 &   400 \\
-   HIP 17527 &            B8V &     03:45:9.74 &   +24:50:21.34 &  6947.82 &     IGRINS &      224 &     230 \\
+   HIP 17527 &            B8V &     03:45:9.74 &   +24:50:21.34 &  6947.82 &     IGRINS &      224 &   120 \\
    HIP 17527 &            B8V &     03:45:9.74 &   +24:50:21.34 &  6517.93 &        HRS &      429 &   670 \\
@@
    HIP 18396 &            B6V &    03:55:58.17 &   +47:52:17.12 &  6516.94 &        HRS &      259 &   510 \\
-   HIP 18724 &        B3V+... &    04:00:40.82 &   +12:29:25.22 &  6299.62 &       TS23 &      226 &    1220 \\
+   HIP 18724 &            B3V &    04:00:40.82 &   +12:29:25.22 &  6299.62 &       TS23 &      226 &  1220 \\
    HIP 18788 &            B5V &    04:01:32.05 &   -01:32:58.78 &  6535.81 &     CHIRON &     1039 &   180 \\
@@
    HIP 19799 &           B9Vn &    04:14:36.23 &   +10:00:41.05 &  6668.63 &       TS23 &     1200 &  1900 \\
-   HIP 19949 &           A2Vn &    04:16:43.09 &   +53:36:42.47 &  6945.90 &     IGRINS &      224 &     440 \\
-   HIP 19949 &           A2Vn &    04:16:43.09 &   +53:36:42.47 &  7084.62 &     IGRINS &      960 &      80 \\
+   HIP 19949 &           A2Vn &    04:16:43.09 &   +53:36:42.47 &  6945.90 &     IGRINS &      224 &   220 \\
+   HIP 19949 &           A2Vn &    04:16:43.09 &   +53:36:42.47 &  7084.62 &     IGRINS &      960 &    30 \\
    HIP 19968 &            B7V &    04:16:53.56 &   +61:50:59.97 &  6676.62 &       TS23 &      524 &  1390 \\
    HIP 20264 &            A0V &    04:20:39.01 &   -20:38:22.64 &  6718.53 &     CHIRON &      860 &   410 \\
-   HIP 20380 &            A3V &    04:21:51.81 &   +56:30:22.74 &  6945.89 &     IGRINS &      224 &     280 \\
-   HIP 20380 &            A3V &    04:21:51.81 &   +56:30:22.74 &  7084.67 &     IGRINS &     1200 &     180 \\
+   HIP 20380 &            A3V &    04:21:51.81 &   +56:30:22.74 &  6945.89 &     IGRINS &      224 &   180 \\
+   HIP 20380 &            A3V &    04:21:51.81 &   +56:30:22.74 &  7084.67 &     IGRINS &     1200 &    30 \\
    HIP 20430 &          B9Vnn &    04:22:34.94 &   +25:37:45.54 &  6520.95 &        HRS &      360 &   710 \\
@@
    HIP 20579 &            B8V &    04:24:29.16 &   +34:07:50.73 &  6517.96 &        HRS &      490 &   830 \\
-   HIP 20789 &            B7V &    04:27:17.45 &   +22:59:46.80 &  6946.86 &     IGRINS &      224 &     250 \\
+   HIP 20789 &            B7V &    04:27:17.45 &   +22:59:46.80 &  6946.86 &     IGRINS &      224 &   150 \\
    HIP 20789 &            B7V &    04:27:17.45 &   +22:59:46.80 &  6586.83 &       TS23 &      524 &  1610 \\
@@
    HIP 21589 &            A6V &     04:38:9.46 &   +12:30:39.01 &  7065.63 &     CHIRON &      754 &   290 \\
-   HIP 21589 &            A6V &     04:38:9.46 &   +12:30:39.01 &  6948.96 &     IGRINS &      112 &     670 \\
-   HIP 21683 &           A5Vn &    04:39:16.50 &    +15:55:4.70 &  6948.98 &     IGRINS &      230 &     220 \\
+   HIP 21589 &            A6V &     04:38:9.46 &   +12:30:39.01 &  6948.96 &     IGRINS &      112 &   140 \\
+   HIP 21683 &           A5Vn &    04:39:16.50 &    +15:55:4.70 &  6948.98 &     IGRINS &      230 &   110 \\
    HIP 21683 &           A5Vn &    04:39:16.50 &    +15:55:4.70 &  6962.97 &       TS23 &      335 &  1040 \\
@@
    HIP 21928 &           A1Vn &    04:42:54.33 &   +43:21:54.53 &  6677.63 &       TS23 &     1124 &  1470 \\
-   HIP 22028 &            A1V &     04:44:7.98 &   -18:39:59.71 &  6947.90 &     IGRINS &      240 &     260 \\
+   HIP 22028 &            A1V &     04:44:7.98 &   -18:39:59.71 &  6947.90 &     IGRINS &      240 &   140 \\
    HIP 22509 &           A1Vn &    04:50:36.72 &    +08:54:0.65 &  6667.62 &       TS23 &     1200 &  1100 \\
@@
    HIP 22833 &            A3V &    04:54:46.90 &   +11:25:33.63 &  6679.60 &       TS23 &      521 &  1520 \\
-   HIP 22833 &            A3V &    04:54:46.90 &   +11:25:33.63 &  6946.87 &     IGRINS &      224 &     420 \\
+   HIP 22833 &            A3V &    04:54:46.90 &   +11:25:33.63 &  6946.87 &     IGRINS &      224 &   140 \\
    HIP 22840 &            B5V &    04:54:50.71 &    +00:28:1.81 &  6678.64 &       TS23 &      528 &  1380 \\
@@
    HIP 23362 &            B9V &    05:01:25.58 &    -20:03:6.91 &  6548.87 &     CHIRON &      725 &   520 \\
-   HIP 23362 &            B9V &    05:01:25.58 &    -20:03:6.91 &  6946.93 &     IGRINS &      240 &     290 \\
-   HIP 23916 &          B8III &    05:08:20.19 &   -08:39:55.17 &  6555.82 &     CHIRON &     1200 &      40 \\
-   HIP 23916 &          B8III &    05:08:20.19 &   -08:39:55.17 &  6946.95 &     IGRINS &      280 &     260 \\
+   HIP 23362 &            B9V &    05:01:25.58 &    -20:03:6.91 &  6946.93 &     IGRINS &      240 &   180 \\
+   HIP 23916 &            B8V &    05:08:20.19 &   -08:39:55.17 &  6555.82 &     CHIRON &     1200 &    40 \\
+   HIP 23916 &            B8V &    05:08:20.19 &   -08:39:55.17 &  6946.95 &     IGRINS &      280 &   140 \\
    HIP 24244 &         B7.5Vn &    05:12:17.90 &    -11:52:9.19 &  6949.84 &     CHIRON &      370 &   560 \\
@@
    HIP 24505 &            B9V &    05:15:24.37 &   -26:56:36.63 &  7036.69 &     CHIRON &     2045 &   480 \\
-   HIP 24902 &            A3V &    05:20:14.67 &   +41:05:10.35 &  6946.88 &     IGRINS &      224 &     300 \\
+   HIP 24902 &            A3V &    05:20:14.67 &   +41:05:10.35 &  6946.88 &     IGRINS &      224 &   180 \\
    HIP 25048 &            B3V &    05:21:48.42 &   +41:48:16.46 &  6299.69 &       TS23 &      900 &   420 \\
- ADS 3962 AB &           B1Vn &    05:22:50.30 &   +03:32:52.00 &  6946.92 &     IGRINS &      280 &     330 \\
-   HIP 25143 &            A3V &    05:22:50.31 &   +41:01:45.33 &  7084.65 &     IGRINS &      960 &     170 \\
-   HIP 25143 &            A3V &    05:22:50.31 &   +41:01:45.33 &  6946.89 &     IGRINS &      224 &     290 \\
+ ADS 3962 AB &           B1Vn &    05:22:50.30 &   +03:32:52.00 &  6946.92 &     IGRINS &      280 &   170 \\
+   HIP 25143 &            A3V &    05:22:50.31 &   +41:01:45.33 &  7084.65 &     IGRINS &      960 &    80 \\
+   HIP 25143 &            A3V &    05:22:50.31 &   +41:01:45.33 &  6946.89 &     IGRINS &      224 &   180 \\
    HIP 25280 &            A0V &    05:24:28.49 &   -16:58:32.81 &  6950.75 &     CHIRON &      597 &   540 \\
-   HIP 25280 &            A0V &    05:24:28.49 &   -16:58:32.81 &  6947.91 &     IGRINS &      240 &     250 \\
+   HIP 25280 &            A0V &    05:24:28.49 &   -16:58:32.81 &  6947.91 &     IGRINS &      240 &   130 \\
    HIP 25281 &        B1V+B2: &    05:24:28.62 &   -02:23:49.73 &  6299.71 &       TS23 &      583 &  1120 \\
@@
    HIP 25695 &           B9Vn &    05:29:16.50 &    +25:09:0.78 &  6669.65 &       TS23 &     1200 &  1860 \\
-   HIP 25790 &           A3Vn &    05:30:26.16 &   +15:21:37.61 &  6946.90 &     IGRINS &      224 &     260 \\
-   HIP 25813 &            B5V &    05:30:47.05 &   +05:56:53.29 &  7083.58 &     IGRINS &     1020 &     630 \\
+   HIP 25790 &           A3Vn &    05:30:26.16 &   +15:21:37.61 &  6946.90 &     IGRINS &      224 &   160 \\
+   HIP 25813 &            B5V &    05:30:47.05 &   +05:56:53.29 &  7083.58 &     IGRINS &     1020 &   200 \\
    HIP 25813 &            B5V &    05:30:47.05 &   +05:56:53.29 &  6544.88 &     CHIRON &      384 &   260 \\
    HIP 26063 &            B1V &    05:33:31.45 &   -01:09:21.87 &  6582.80 &     CHIRON &     1139 &   250 \\
-   HIP 26093 &            B3V &    05:33:54.28 &   +14:18:20.08 &  6946.91 &     IGRINS &      280 &     260 \\
+   HIP 26093 &            B3V &    05:33:54.28 &   +14:18:20.08 &  6946.91 &     IGRINS &      280 &   150 \\
    HIP 26093 &            B3V &    05:33:54.28 &   +14:18:20.08 &  6676.66 &       TS23 &      525 &  1380 \\
-   HIP 26093 &            B3V &    05:33:54.28 &   +14:18:20.08 &  7084.72 &     IGRINS &     1800 &     370 \\
-   HIP 26126 &            A2V &    05:34:16.77 &    +03:46:0.82 &  6946.96 &     IGRINS &      240 &     470 \\
+   HIP 26093 &            B3V &    05:33:54.28 &   +14:18:20.08 &  7084.72 &     IGRINS &     1800 &    90 \\
+   HIP 26126 &            A2V &    05:34:16.77 &    +03:46:0.82 &  6946.96 &     IGRINS &      240 &   170 \\
    HIP 26126 &            A2V &    05:34:16.77 &    +03:46:0.82 &  6721.50 &     CHIRON &      507 &   450 \\
@@
    HIP 27321 &            A6V &    05:47:17.09 &   -51:03:59.44 &  6696.62 &     CHIRON &      178 &   640 \\
-   HIP 27713 &           A2Vn &     05:52:7.73 &   -09:02:30.84 &  6946.97 &     IGRINS &      240 &     270 \\
+   HIP 27713 &           A2Vn &     05:52:7.73 &   -09:02:30.84 &  6946.97 &     IGRINS &      240 &   150 \\
    HIP 28691 &            B8V &    06:03:27.37 &   +19:41:26.02 &  6298.78 &       TS23 &      646 &  1300 \\
@@
    HIP 29150 &            A0V &    06:08:57.87 &   -22:25:38.68 &  6697.63 &     CHIRON &      950 &   380 \\
-   HIP 29151 &           A3Vn &    06:08:57.90 &   +02:29:58.89 &  6946.99 &     IGRINS &      264 &     340 \\
+   HIP 29151 &           A3Vn &    06:08:57.90 &   +02:29:58.89 &  6946.99 &     IGRINS &      264 &   170 \\
    HIP 29151 &           A3Vn &    06:08:57.90 &   +02:29:58.89 &  6953.82 &     CHIRON &      617 &   540 \\
    HIP 29735 &            B9V &    06:15:44.89 &    -13:43:6.29 &  6559.80 &     CHIRON &      803 &   380 \\
-   HIP 29735 &            B9V &    06:15:44.89 &    -13:43:6.29 &  6946.98 &     IGRINS &      240 &     250 \\
+   HIP 29735 &            B9V &    06:15:44.89 &    -13:43:6.29 &  6946.98 &     IGRINS &      240 &   170 \\
    HIP 29997 &           A0Vn &    06:18:50.78 &   +69:19:11.23 &  6679.70 &       TS23 &      415 &  1460 \\
@@
    HIP 30073 &          B2.5V &  06:19:42.7989 &  -07:49:22.473 &  6581.82 &     CHIRON &     1011 &   280 \\
-   HIP 30666 &           A3Vn &    06:26:39.59 &   -01:30:26.41 &  6947.00 &     IGRINS &      280 &     310 \\
+   HIP 30666 &           A3Vn &    06:26:39.59 &   -01:30:26.41 &  6947.00 &     IGRINS &      280 &   160 \\
    HIP 30788 &            B4V &    06:28:10.21 &   -32:34:48.25 &  6574.75 &     CHIRON &      488 &   340 \\
-   HIP 31278 &           B5Vn &    06:33:37.92 &   -01:13:12.55 &  7084.69 &     IGRINS &      960 &     350 \\
+   HIP 31278 &           B5Vn &    06:33:37.92 &   -01:13:12.55 &  7084.69 &     IGRINS &      960 &    90 \\
    HIP 31278 &           B5Vn &    06:33:37.92 &   -01:13:12.55 &  6668.71 &       TS23 &      797 &  1920 \\
-   HIP 31278 &           B5Vn &    06:33:37.92 &   -01:13:12.55 &  6947.01 &     IGRINS &      280 &     390 \\
+   HIP 31278 &           B5Vn &    06:33:37.92 &   -01:13:12.55 &  6947.01 &     IGRINS &      280 &   170 \\
    HIP 31362 &            B8V &    06:34:35.33 &   -32:42:58.51 &  6598.72 &     CHIRON &     1200 &   250 \\
@@
    HIP 32474 &          B9.5V &    06:46:39.02 &   -10:06:26.50 &  6592.74 &     CHIRON &     1200 &   340 \\
-   HIP 32607 &        A8VnkA6 &    06:48:11.46 &   -61:56:29.00 &  7037.75 &     CHIRON &       56 &     210 \\
-   HIP 32607 &        A8VnkA6 &    06:48:11.46 &   -61:56:29.00 &  7039.62 &     CHIRON &       49 &     210 \\
-   HIP 32607 &        A8VnkA6 &    06:48:11.46 &   -61:56:29.00 &  6724.56 &     CHIRON &       67 &     560 \\
-   HIP 33372 &           B8Vn &    06:56:25.83 &   +09:57:23.67 &  6948.00 &     IGRINS &      320 &     330 \\
+   HIP 32607 &            A7V &    06:48:11.46 &   -61:56:29.00 &  7037.75 &     CHIRON &       56 &   210 \\
+   HIP 32607 &            A7V &    06:48:11.46 &   -61:56:29.00 &  7039.62 &     CHIRON &       49 &   210 \\
+   HIP 32607 &            A7V &    06:48:11.46 &   -61:56:29.00 &  6724.56 &     CHIRON &       67 &   560 \\
+   HIP 33372 &           B8Vn &    06:56:25.83 &   +09:57:23.67 &  6948.00 &     IGRINS &      320 &   110 \\
    HIP 33372 &           B8Vn &    06:56:25.83 &   +09:57:23.67 &  6678.72 &       TS23 &      720 &  1380 \\
@@
    HIP 36393 &            A4V &    07:29:20.44 &    +28:07:5.79 &  6670.76 &       TS23 &      494 &  1400 \\
-   HIP 36760 &           A1Vn &    07:33:36.48 &   +15:49:35.98 &  7084.74 &     IGRINS &      720 &     760 \\
+   HIP 36760 &           A1Vn &    07:33:36.48 &   +15:49:35.98 &  7084.74 &     IGRINS &      720 &   150 \\
    HIP 36760 &           A1Vn &    07:33:36.48 &   +15:49:35.98 &  7037.76 &     CHIRON &     4284 &   370 \\
@@
    HIP 36760 &           A1Vn &    07:33:36.48 &   +15:49:35.98 &  6668.79 &       TS23 &      836 &   700 \\
-   HIP 36812 &          A0Vnn &    07:34:15.89 &   +03:22:18.19 &  6947.99 &     IGRINS &      280 &     320 \\
+   HIP 36812 &          A0Vnn &    07:34:15.89 &   +03:22:18.19 &  6947.99 &     IGRINS &      280 &   110 \\
    HIP 36917 &            B7V &    07:35:22.89 &    -28:22:9.57 &  6583.81 &     CHIRON &      571 &   420 \\
@@
    HIP 39567 &            A1V &     08:05:4.49 &    +13:07:5.58 &  6668.80 &       TS23 &      613 &  1940 \\
-   HIP 39847 &            A2V &    08:08:27.45 &   +51:30:24.01 &  7084.68 &     IGRINS &      480 &     570 \\
+   HIP 39847 &            A2V &    08:08:27.45 &   +51:30:24.01 &  7084.68 &     IGRINS &      480 &   160 \\
    HIP 39847 &            A2V &    08:08:27.45 &   +51:30:24.01 &  6676.80 &       TS23 &      402 &  1500 \\
@@
    HIP 40706 &            A8V &    08:18:33.31 &   -36:39:33.44 &  6327.64 &     CHIRON &      277 &   630 \\
-   HIP 40881 &          B9.5V &    08:20:32.14 &   +24:01:20.32 &  6947.97 &     IGRINS &      240 &     310 \\
+   HIP 40881 &          B9.5V &    08:20:32.14 &   +24:01:20.32 &  6947.97 &     IGRINS &      240 &   100 \\
    HIP 41039 &            B1V &    08:22:31.69 &   -48:29:25.36 &  7039.73 &     CHIRON &     1728 &   530 \\
@@
    HIP 41307 &           A0Va &    08:25:39.63 &   -03:54:23.12 &  6667.82 &       TS23 &      700 &  1220 \\
-   HIP 42090 &          A2Vnn &    08:34:43.88 &   +36:25:10.63 &  7124.62 &     IGRINS &      630 &     280 \\
-   HIP 42129 &        B3V+... &    08:35:15.56 &   -58:13:29.05 &  6603.80 &     CHIRON &     1001 &     370 \\
+   HIP 42090 &          A2Vnn &    08:34:43.88 &   +36:25:10.63 &  7124.62 &     IGRINS &      630 &   120 \\
+   HIP 42129 &            B3V &    08:35:15.56 &   -58:13:29.05 &  6603.80 &     CHIRON &     1001 &   370 \\
    HIP 42313 &          A0Vnn &    08:37:39.37 &   +05:42:13.61 &  6681.81 &       TS23 &      489 &  1020 \\
@@
    HIP 44127 &     A7V(n)+M1V &    08:59:12.45 &   +48:02:30.57 &  6677.88 &       TS23 &      239 &  1600 \\
-   HIP 44307 &            A2V &    09:01:24.13 &    +32:15:8.26 &  6947.98 &     IGRINS &      280 &     500 \\
+   HIP 44307 &            A2V &    09:01:24.13 &    +32:15:8.26 &  6947.98 &     IGRINS &      280 &    80 \\
    HIP 45336 &    B9.5V+DA1.6 &    09:14:21.86 &   +02:18:51.34 &  6328.70 &     CHIRON &      171 &   290 \\
-   HIP 45336 &    B9.5V+DA1.6 &    09:14:21.86 &   +02:18:51.34 &  7122.66 &     IGRINS &      270 &     230 \\
-   HIP 45336 &    B9.5V+DA1.6 &    09:14:21.86 &   +02:18:51.34 &  7084.75 &     IGRINS &      240 &     330 \\
+   HIP 45336 &    B9.5V+DA1.6 &    09:14:21.86 &   +02:18:51.34 &  7122.66 &     IGRINS &      270 &   130 \\
+   HIP 45336 &    B9.5V+DA1.6 &    09:14:21.86 &   +02:18:51.34 &  7084.75 &     IGRINS &      240 &   140 \\
    HIP 45344 &            B4V &    09:14:24.48 &   -43:13:38.97 &  6612.79 &     CHIRON &     1001 &   320 \\
@@
    HIP 46283 &            B6V &    09:26:17.96 &   -53:22:44.07 &  6712.70 &     CHIRON &      352 &   450 \\
-   HIP 46897 &          B9.5V &    09:33:26.05 &   -22:51:49.99 &  7084.78 &     IGRINS &     1200 &     230 \\
-   HIP 46897 &          B9.5V &    09:33:26.05 &   -22:51:49.99 &  7139.59 &     IGRINS &      720 &     400 \\
+   HIP 46897 &          B9.5V &    09:33:26.05 &   -22:51:49.99 &  7084.78 &     IGRINS &     1200 &    20 \\
+   HIP 46897 &          B9.5V &    09:33:26.05 &   -22:51:49.99 &  7139.59 &     IGRINS &      720 &   120 \\
    HIP 47006 &           A0Vn &    09:34:49.43 &    +52:03:5.32 &  6677.03 &       TS23 &      373 &  1590 \\
@@
    HIP 51362 &          B9.5V &    10:29:28.70 &   -02:44:20.69 &  6673.75 &     CHIRON &      606 &   510 \\
-   HIP 51362 &          B9.5V &    10:29:28.70 &   -02:44:20.69 &  7084.76 &     IGRINS &      720 &     240 \\
+   HIP 51362 &          B9.5V &    10:29:28.70 &   -02:44:20.69 &  7084.76 &     IGRINS &      720 &   100 \\
    HIP 51685 &           A2Vn &    10:33:30.91 &   +34:59:19.30 &  6677.90 &       TS23 &     1046 &  1460 \\
@@
    HIP 60009 &          B2.5V &    12:18:26.25 &   -64:00:11.05 &  7009.78 &     CHIRON &      206 &   510 \\
-   HIP 60030 &           A5Vn &    12:18:40.32 &   -00:47:13.87 &  7084.81 &     IGRINS &     2400 &     230 \\
+   HIP 60030 &           A5Vn &    12:18:40.32 &   -00:47:13.87 &  7084.81 &     IGRINS &     2400 &    80 \\
    HIP 60595 &            A1V &    12:25:11.76 &   -11:36:38.12 &  6676.94 &       TS23 &      746 &  1540 \\
@@
    HIP 60957 &            A3V &    12:29:43.24 &   +20:53:45.99 &  6678.92 &       TS23 &      904 &  1500 \\
-   HIP 61558 &            A3V &    12:36:47.35 &   -05:49:54.84 &  7139.67 &     IGRINS &     1440 &     390 \\
-   HIP 61558 &            A3V &    12:36:47.35 &   -05:49:54.84 &  7084.84 &     IGRINS &     1200 &     130 \\
-   HIP 61622 &         A1IVnn &    12:37:42.16 &   -48:32:28.69 &  6378.69 &     CHIRON &      167 &     620 \\
-   HIP 62541 &            A1V &    12:48:54.21 &   +14:07:21.31 &  7124.80 &     IGRINS &      480 &     270 \\
-   HIP 62541 &            A1V &    12:48:54.21 &   +14:07:21.31 &  7084.86 &     IGRINS &     1500 &     110 \\
-   HIP 62576 &            A2V &    12:49:17.45 &    +27:33:8.57 &  7122.83 &     IGRINS &      546 &     290 \\
+   HIP 61558 &            A3V &    12:36:47.35 &   -05:49:54.84 &  7139.67 &     IGRINS &     1440 &   180 \\
+   HIP 61558 &            A3V &    12:36:47.35 &   -05:49:54.84 &  7084.84 &     IGRINS &     1200 &    70 \\
+   HIP 61622 &            A2V &    12:37:42.16 &   -48:32:28.69 &  6378.69 &     CHIRON &      167 &   620 \\
+   HIP 62541 &            A1V &    12:48:54.21 &   +14:07:21.31 &  7124.80 &     IGRINS &      480 &   120 \\
+   HIP 62541 &            A1V &    12:48:54.21 &   +14:07:21.31 &  7084.86 &     IGRINS &     1500 &    80 \\
+   HIP 62576 &            A2V &    12:49:17.45 &    +27:33:8.57 &  7122.83 &     IGRINS &      546 &   130 \\
    HIP 63724 &            A0V &    13:03:33.31 &   -49:31:38.15 &  6338.76 &     CHIRON &      412 &   560 \\
@@
    HIP 66821 &  B8.5Vn+A2.5Va &    13:41:44.77 &   -54:33:33.93 &  6718.75 &     CHIRON &      610 &   540 \\
-   HIP 67143 &            A0V &    13:45:36.89 &   -26:06:57.63 &  7139.77 &     IGRINS &      480 &     270 \\
+   HIP 67143 &            A0V &    13:45:36.89 &   -26:06:57.63 &  7139.77 &     IGRINS &      480 &   120 \\
    HIP 67194 &            A5V &    13:46:13.55 &   +41:05:19.48 &  6389.70 &        HRS &      368 &   740 \\
    HIP 67782 &           A8IV &    13:53:10.28 &   +28:38:53.28 &  6394.92 &        HRS &      359 &   680 \\
-   HIP 68092 &            A8V &    13:56:27.88 &    +01:03:2.09 &  7139.80 &     IGRINS &      840 &     640 \\
+   HIP 68092 &            A8V &    13:56:27.88 &    +01:03:2.09 &  7139.80 &     IGRINS &      840 &   200 \\
    HIP 68520 &            A3V &    14:01:38.79 &   +01:32:40.31 &  6403.59 &     CHIRON &      239 &   470 \\
-   HIP 70327 &            A0V &    14:23:22.70 &   +08:26:47.84 &  7123.90 &     IGRINS &      420 &     300 \\
+   HIP 70327 &            A0V &    14:23:22.70 &   +08:26:47.84 &  7123.90 &     IGRINS &      420 &    90 \\
    HIP 70327 &            A0V &    14:23:22.70 &   +08:26:47.84 &  6681.98 &       TS23 &     1152 &   230 \\
@@
    HIP 71974 &          B9.5V &    14:43:13.55 &   -24:59:51.91 &  7078.80 &     CHIRON &     3786 &   470 \\
-   HIP 72104 &         A0IVnn &    14:44:59.20 &   -35:11:30.57 &  6720.86 &     CHIRON &      492 &     490 \\
+   HIP 72104 &          A0Vnn &    14:44:59.20 &   -35:11:30.57 &  6720.86 &     CHIRON &      492 &   490 \\
    HIP 72154 &          B9.5V &    14:45:30.20 &    +00:43:2.19 &  6403.75 &        HRS &      300 &   470 \\
    HIP 72250 &            A1V &    14:46:28.99 &   -47:26:28.02 &  7070.72 &     CHIRON &     4025 &   490 \\
-   HIP 72378 &            B9V &    14:47:57.56 &   -26:38:46.16 &  7139.82 &     IGRINS &      720 &     450 \\
-   HIP 72552 &            A4V &    14:49:58.40 &   +28:36:57.00 &  7124.81 &     IGRINS &      600 &     200 \\
+   HIP 72378 &            B9V &    14:47:57.56 &   -26:38:46.16 &  7139.82 &     IGRINS &      720 &   140 \\
+   HIP 72552 &            A4V &    14:49:58.40 &   +28:36:57.00 &  7124.81 &     IGRINS &      600 &   110 \\
    HIP 73049 &            A0V &    14:55:44.71 &   -33:51:20.82 &  6715.73 &     CHIRON &      749 &   530 \\
@@
    HIP 75304 &            B4V &     15:23:9.35 &   -36:51:30.55 &  6427.78 &     CHIRON &      309 &   340 \\
-   HIP 76267 &           A1IV &    15:34:41.27 &   +26:42:52.89 &  6380.88 &     CHIRON &       36 &     290 \\
+   HIP 76267 &            A0V &    15:34:41.27 &   +26:42:52.89 &  6380.88 &     CHIRON &       36 &   290 \\
    HIP 76600 &          B2.5V &    15:38:39.37 &   -29:46:39.89 &  6380.91 &     CHIRON &      137 &   500 \\
@@
    HIP 77336 &            A3V &    15:47:17.32 &   +14:06:55.26 &  6396.79 &        HRS &      264 &   610 \\
-   HIP 77336 &            A3V &    15:47:17.32 &   +14:06:55.26 &  7122.91 &     IGRINS &      480 &     230 \\
+   HIP 77336 &            A3V &    15:47:17.32 &   +14:06:55.26 &  7122.91 &     IGRINS &      480 &   120 \\
    HIP 77516 &            A0V &    15:49:37.21 &   -03:25:48.73 &  6380.89 &     CHIRON &      126 &   450 \\
@@
    HIP 78106 &            B9V &    15:56:54.12 &   -33:57:51.34 &  6736.70 &     CHIRON &      584 &   500 \\
-   HIP 78265 &      B1V+B2:V: &  15:58:51.1132 &  -26:06:50.788 &  6766.77 &     CHIRON &       22 &     250 \\
    HIP 78554 &            A3V &    16:02:17.69 &   +22:48:16.03 &  6427.74 &     CHIRON &      408 &   270 \\
    HIP 78820 &            B1V &    16:05:26.23 &   -19:48:19.63 &  6380.93 &     CHIRON &       53 &   490 \\
-   HIP 78820 &            B1V &    16:05:26.23 &   -19:48:19.63 &  7139.83 &     IGRINS &      120 &     840 \\
+   HIP 78820 &            B1V &    16:05:26.23 &   -19:48:19.63 &  7139.83 &     IGRINS &      120 &   190 \\
    HIP 78820 &            B1V &    16:05:26.23 &   -19:48:19.63 &  7060.85 &     CHIRON &      263 &   360 \\
    HIP 78820 &            B1V &    16:05:26.23 &   -19:48:19.63 &  7156.63 &     CHIRON &      164 &   390 \\
-   HIP 78821 &            B2V &    16:05:26.57 &    -19:48:6.85 &  7139.84 &     IGRINS &      210 &     100 \\
-     HR 6025 &           A0Vn &  16:06:19.6762 &  +67:48:36.480 &  6847.83 &     IGRINS &      600 &     610 \\
+   HIP 78821 &            B2V &    16:05:26.57 &    -19:48:6.85 &  7139.84 &     IGRINS &      210 &    50 \\
+     HR 6025 &           A0Vn &  16:06:19.6762 &  +67:48:36.480 &  6847.83 &     IGRINS &      600 &   100 \\
    HIP 78918 &         B2.5Vn &    16:06:35.55 &    -36:48:8.26 &  6718.86 &     CHIRON &      300 &   610 \\
@@
    HIP 79653 &            B8V &    16:15:15.32 &   -47:22:19.27 &  6740.79 &     CHIRON &      469 &   490 \\
-   HIP 80460 &            A5V &    16:25:24.17 &   +37:23:38.68 &  7122.93 &     IGRINS &      720 &     400 \\
+   HIP 80460 &            A5V &    16:25:24.17 &   +37:23:38.68 &  7122.93 &     IGRINS &      720 &   110 \\
    HIP 80815 &            B3V &    16:30:12.48 &   -25:06:54.80 &  6378.86 &     CHIRON &      393 &   530 \\
-   HIP 80883 &           A1IV &    16:30:54.82 &    +01:59:2.12 &  6378.84 &     CHIRON &      174 &     550 \\
+   HIP 80883 &            A0V &    16:30:54.82 &    +01:59:2.12 &  6378.84 &     CHIRON &      174 &   550 \\
    HIP 80991 &            A2V &    16:32:25.68 &   +60:49:23.96 &  6389.86 &        HRS &      404 &   720 \\
-   HIP 81126 &            B9V &     16:34:6.18 &   +42:26:13.34 &  7122.95 &     IGRINS &      720 &     620 \\
+   HIP 81126 &            B9V &     16:34:6.18 &   +42:26:13.34 &  7122.95 &     IGRINS &      720 &   150 \\
    HIP 81641 &            A1V &    16:40:38.69 &   +04:13:11.23 &  6404.83 &        HRS &      320 &   540 \\
    HIP 82350 &            A1V &    16:49:34.66 &   +13:15:40.10 &  6391.84 &        HRS &      404 &   660 \\
-   HIP 82514 &     B1.5Vp+... &  16:51:52.2311 &  -38:02:50.569 &  6726.81 &     CHIRON &       34 &     250 \\
    HIP 82673 &            B8V &     16:54:0.47 &   +10:09:55.30 &  6871.58 &     CHIRON &      250 &   310 \\
@@
    HIP 83635 &            B1V &    17:05:32.26 &   -00:53:31.45 &  6407.86 &        HRS &      316 &   480 \\
-   HIP 84606 &            A2V &    17:17:40.25 &   +37:17:29.40 &  6945.54 &     IGRINS &      224 &     460 \\
-   HIP 85290 &           A1Vn &    17:25:41.35 &   +60:02:54.23 &  6946.56 &     IGRINS &      224 &     240 \\
+   HIP 84606 &            A2V &    17:17:40.25 &   +37:17:29.40 &  6945.54 &     IGRINS &      224 &   150 \\
+   HIP 85290 &           A1Vn &    17:25:41.35 &   +60:02:54.23 &  6946.56 &     IGRINS &      224 &   120 \\
    HIP 85379 &            A4V &    17:26:44.24 &   +48:15:36.23 &  6398.85 &        HRS &      330 &   740 \\
-   HIP 85385 &            B5V &    17:26:49.13 &   +20:04:51.52 &  6848.83 &     IGRINS &      480 &   40390 \\
+   HIP 85385 &            B5V &    17:26:49.13 &   +20:04:51.52 &  6848.83 &     IGRINS &      480 &    80 \\
    HIP 85537 &           A8Vp &    17:28:49.65 &   +00:19:50.25 &  7096.88 &     CHIRON &     4227 &   570 \\
    HIP 85537 &           A8Vp &    17:28:49.65 &   +00:19:50.25 &  6792.73 &     CHIRON &      900 &   600 \\
-   HIP 85537 &           A8Vp &    17:28:49.65 &   +00:19:50.25 &  6848.73 &     IGRINS &      240 &   68720 \\
+   HIP 85537 &           A8Vp &    17:28:49.65 &   +00:19:50.25 &  6848.73 &     IGRINS &      240 &    60 \\
    HIP 85727 &           B8Vn &     17:31:5.91 &    -60:41:1.85 &  6771.85 &     CHIRON &      175 &   570 \\
-   HIP 85922 &     A4III-IVnn &    17:33:29.85 &   -05:44:41.29 &  6847.82 &     IGRINS &      480 &     760 \\
-   HIP 85922 &     A4III-IVnn &    17:33:29.85 &   -05:44:41.29 &  7139.95 &     IGRINS &      240 &     290 \\
-   HIP 85922 &     A4III-IVnn &    17:33:29.85 &   -05:44:41.29 &  6886.56 &     CHIRON &      791 &     590 \\
-   HIP 85922 &     A4III-IVnn &    17:33:29.85 &   -05:44:41.29 &  7103.85 &     CHIRON &     2543 &     370 \\
-   HIP 85922 &     A4III-IVnn &    17:33:29.85 &   -05:44:41.29 &  7104.82 &     CHIRON &     7386 &     360 \\
-   HIP 85998 &            A2V &    17:34:36.69 &   +09:35:12.12 &  7122.96 &     IGRINS &      480 &     120 \\
-   HIP 85998 &            A2V &    17:34:36.69 &   +09:35:12.12 &  7230.64 &     IGRINS &      720 &     700 \\
+   HIP 85922 &            A5V &    17:33:29.85 &   -05:44:41.29 &  6847.82 &     IGRINS &      480 &   120 \\
+   HIP 85922 &            A5V &    17:33:29.85 &   -05:44:41.29 &  7139.95 &     IGRINS &      240 &   170 \\
+   HIP 85922 &            A5V &    17:33:29.85 &   -05:44:41.29 &  6886.56 &     CHIRON &      791 &   590 \\
+   HIP 85922 &            A5V &    17:33:29.85 &   -05:44:41.29 &  7103.85 &     CHIRON &     2543 &   370 \\
+   HIP 85922 &            A5V &    17:33:29.85 &   -05:44:41.29 &  7104.82 &     CHIRON &     7386 &   360 \\
+   HIP 85998 &            A2V &    17:34:36.69 &   +09:35:12.12 &  7122.96 &     IGRINS &      480 &    50 \\
+   HIP 85998 &            A2V &    17:34:36.69 &   +09:35:12.12 &  7230.64 &     IGRINS &      720 &   170 \\
    HIP 85998 &            A2V &    17:34:36.69 &   +09:35:12.12 &  6407.84 &        HRS &      324 &   490 \\
@@
    HIP 86782 &            A2V &    17:43:59.18 &    +53:48:6.17 &  6404.85 &        HRS &      310 &   500 \\
-   HIP 87108 &     A1VnkA0mA0 &    17:47:53.56 &   +02:42:26.20 &  6847.87 &     IGRINS &      120 &     630 \\
-   HIP 87108 &     A1VnkA0mA0 &    17:47:53.56 &   +02:42:26.20 &  6445.79 &     CHIRON &      152 &     300 \\
+   HIP 87108 &           A0Vn &    17:47:53.56 &   +02:42:26.20 &  6847.87 &     IGRINS &      120 &   120 \\
+   HIP 87108 &           A0Vn &    17:47:53.56 &   +02:42:26.20 &  6445.79 &     CHIRON &      152 &   300 \\
    HIP 88116 &             A0 &    17:59:47.56 &   -23:48:58.09 &  6488.71 &     CHIRON &      373 &   590 \\
@@
    HIP 88290 &           A2Vn &    18:01:45.20 &   +01:18:18.28 &  6873.59 &     CHIRON &      365 &   540 \\
-   HIP 88818 &            A3V &    18:07:49.45 &    +26:06:4.13 &  7122.98 &     IGRINS &      960 &     530 \\
-   HIP 88818 &            A3V &    18:07:49.45 &    +26:06:4.13 &  7230.66 &     IGRINS &      600 &     830 \\
+   HIP 88818 &            A3V &    18:07:49.45 &    +26:06:4.13 &  7122.98 &     IGRINS &      960 &    90 \\
+   HIP 88818 &            A3V &    18:07:49.45 &    +26:06:4.13 &  7230.66 &     IGRINS &      600 &   110 \\
    HIP 88818 &            A3V &    18:07:49.45 &    +26:06:4.13 &  6397.85 &        HRS &      355 &   510 \\
-   HIP 88817 &            A3V &    18:07:49.50 &   +26:05:50.40 &  7123.00 &     IGRINS &      960 &     430 \\
+   HIP 88817 &            A3V &    18:07:49.50 &   +26:05:50.40 &  7123.00 &     IGRINS &      960 &   100 \\
    HIP 88817 &            A3V &    18:07:49.50 &   +26:05:50.40 &  6405.84 &        HRS &      400 &   720 \\
    HIP 89156 &            A3V &    18:11:45.12 &   +33:26:49.41 &  6405.82 &        HRS &      470 &   610 \\
-   HIP 89935 &            A7V &     18:21:1.02 &   +28:52:11.83 &  6848.85 &     IGRINS &      240 &   77520 \\
-   HIP 89935 &            A7V &     18:21:1.02 &   +28:52:11.83 &  6945.56 &     IGRINS &      224 &     620 \\
+   HIP 89935 &            A7V &     18:21:1.02 &   +28:52:11.83 &  6848.85 &     IGRINS &      240 &   100 \\
+   HIP 89935 &            A7V &     18:21:1.02 &   +28:52:11.83 &  6945.56 &     IGRINS &      224 &   250 \\
    HIP 90052 &            A2V &    18:22:35.32 &   +12:01:46.85 &  6405.88 &        HRS &      500 &   760 \\
-   HIP 90762 &            A2V &     18:31:4.45 &   +16:55:42.80 &  6848.85 &     IGRINS &      480 &   47190 \\
-   HIP 90762 &            A2V &     18:31:4.45 &   +16:55:42.80 &  6945.57 &     IGRINS &      480 &     570 \\
+   HIP 90762 &            A2V &     18:31:4.45 &   +16:55:42.80 &  6848.85 &     IGRINS &      480 &    80 \\
+   HIP 90762 &            A2V &     18:31:4.45 &   +16:55:42.80 &  6945.57 &     IGRINS &      480 &   200 \\
    HIP 90887 &           A3Vn &    18:32:21.33 &   -39:42:14.40 &  6748.80 &     CHIRON &      710 &   560 \\
-   HIP 91118 &           A0Vn &    18:35:12.60 &   +18:12:12.28 &  6945.58 &     IGRINS &      360 &     390 \\
+   HIP 91118 &           A0Vn &    18:35:12.60 &   +18:12:12.28 &  6945.58 &     IGRINS &      360 &   190 \\
    HIP 91875 &           A2Vn &    18:43:46.94 &   -38:19:24.39 &  6745.81 &     CHIRON &      680 &   580 \\
-   HIP 92027 &        A1V+... &    18:45:28.36 &    +05:30:0.44 &  6405.91 &        HRS &      360 &     570 \\
+   HIP 92027 &            A1V &    18:45:28.36 &    +05:30:0.44 &  6405.91 &        HRS &      360 &   570 \\
    HIP 92312 &            A1V &    18:48:53.39 &   +19:19:43.40 &  6408.88 &        HRS &      390 &   650 \\
@@
    HIP 92946 &            A5V &    18:56:13.18 &   +04:12:12.91 &  6475.79 &     CHIRON &      339 &   500 \\
-   HIP 93225 &            B4V &    18:59:23.80 &   -12:50:25.86 &  6946.54 &     IGRINS &      224 &     640 \\
+   HIP 93225 &            B4V &    18:59:23.80 &   -12:50:25.86 &  6946.54 &     IGRINS &      224 &    80 \\
    HIP 93225 &            B4V &    18:59:23.80 &   -12:50:25.86 &  6516.69 &     CHIRON &     1200 &   540 \\
@@
    HIP 93580 &            A4V &    19:03:32.25 &    +01:49:7.57 &  7116.84 &     CHIRON &     5594 &   520 \\
-   HIP 93580 &            A4V &    19:03:32.25 &    +01:49:7.57 &  6848.84 &     IGRINS &      480 &   55820 \\
-   HIP 93713 &           A0Vn &    19:04:55.17 &   +53:23:47.96 &  6848.87 &     IGRINS &      600 &   42950 \\
+   HIP 93580 &            A4V &    19:03:32.25 &    +01:49:7.57 &  6848.84 &     IGRINS &      480 &   100 \\
+   HIP 93713 &           A0Vn &    19:04:55.17 &   +53:23:47.96 &  6848.87 &     IGRINS &      600 &    90 \\
    HIP 93747 &       A0IV-Vnn &    19:05:24.61 &   +13:51:48.52 &  6587.54 &       TS23 &       85 &  1880 \\
-   HIP 93805 &           B9Vn &    19:06:14.94 &   -04:52:57.20 &  6852.82 &     IGRINS &     2640 &  188380 \\
-   HIP 93805 &           B9Vn &    19:06:14.94 &   -04:52:57.20 &  7139.96 &     IGRINS &      120 &     280 \\
+   HIP 93805 &           B9Vn &    19:06:14.94 &   -04:52:57.20 &  6852.82 &     IGRINS &     2640 &    60 \\
+   HIP 93805 &           B9Vn &    19:06:14.94 &   -04:52:57.20 &  7139.96 &     IGRINS &      120 &   210 \\
    HIP 93805 &           B9Vn &    19:06:14.94 &   -04:52:57.20 &  6775.78 &     CHIRON &      150 &   520 \\
-   HIP 94620 &            A4V &    19:15:17.36 &   +21:13:55.62 &  6848.88 &     IGRINS &      480 &   69950 \\
+   HIP 94620 &            A4V &    19:15:17.36 &   +21:13:55.62 &  6848.88 &     IGRINS &      480 &   100 \\
    HIP 94720 &          B9.5V &    19:16:26.79 &   +14:32:40.62 &  6517.78 &        HRS &      400 &   880 \\
@@
    HIP 95241 &            B9V &    19:22:38.30 &   -44:27:32.25 &  6459.89 &     CHIRON &      183 &   360 \\
-   HIP 95560 &            A0V &    19:26:13.25 &   +20:05:51.84 &  6848.89 &     IGRINS &      480 &   57010 \\
-   HIP 95619 &          B8.5V &    19:26:56.48 &   -29:44:35.62 &  7139.97 &     IGRINS &      480 &     310 \\
+   HIP 95560 &            A0V &    19:26:13.25 &   +20:05:51.84 &  6848.89 &     IGRINS &      480 &   110 \\
+   HIP 95619 &          B8.5V &    19:26:56.48 &   -29:44:35.62 &  7139.97 &     IGRINS &      480 &   120 \\
    HIP 95619 &          B8.5V &    19:26:56.48 &   -29:44:35.62 &  7118.79 &     CHIRON &     3451 &   320 \\
@@
    HIP 96840 &            B5V &     19:41:5.53 &   +13:48:56.45 &  6408.92 &        HRS &      552 &   940 \\
-   HIP 97376 &           B8Vn &    19:47:27.78 &   +38:24:27.41 &  6848.90 &     IGRINS &     1680 &   35630 \\
+   HIP 97376 &           B8Vn &    19:47:27.78 &   +38:24:27.41 &  6848.90 &     IGRINS &     1680 &    70 \\
    HIP 97496 &            A3V &    19:48:58.66 &   +19:08:31.35 &  6584.54 &       TS23 &      342 &  1820 \\
@@
    HIP 99080 &            B3V &    20:06:53.41 &   +23:36:51.93 &  6583.63 &       TS23 &      358 &  1740 \\
-   HIP 99742 &           A1Va &    20:14:16.62 &   +15:11:51.39 &  6945.59 &     IGRINS &      224 &     540 \\
-  HIP 100069 &  O9IV(n)+B1.5V &     20:18:6.99 &   +40:43:55.50 &  6409.91 &        HRS &      451 &     560 \\
-  HIP 100221 &            B9V &    20:19:36.72 &   +62:15:26.90 &  7230.72 &     IGRINS &     1100 &     930 \\
+   HIP 99742 &           A1Va &    20:14:16.62 &   +15:11:51.39 &  6945.59 &     IGRINS &      224 &   210 \\
+  HIP 100069 &          B1.5V &     20:18:6.99 &   +40:43:55.50 &  6409.91 &        HRS &      451 &   560 \\
+  HIP 100221 &            B9V &    20:19:36.72 &   +62:15:26.90 &  7230.72 &     IGRINS &     1100 &    80 \\
   HIP 100221 &            B9V &    20:19:36.72 &   +62:15:26.90 &  6523.79 &        HRS &      874 &   830 \\
   HIP 100881 &            B4V &    20:27:19.21 &   -18:12:42.20 &  6511.69 &     CHIRON &     1011 &   570 \\
-  HIP 100907 &            A3V &    20:27:34.26 &   +38:26:25.19 &  6946.57 &     IGRINS &      224 &     730 \\
-  HIP 100907 &            A3V &    20:27:34.26 &   +38:26:25.19 &  7230.67 &     IGRINS &      600 &    1030 \\
-  HIP 101123 &            A1V &    20:29:53.91 &   -18:34:59.48 &  6945.70 &     IGRINS &      224 &     810 \\
+  HIP 100907 &            A3V &    20:27:34.26 &   +38:26:25.19 &  6946.57 &     IGRINS &      224 &   120 \\
+  HIP 100907 &            A3V &    20:27:34.26 &   +38:26:25.19 &  7230.67 &     IGRINS &      600 &   120 \\
+  HIP 101123 &            A1V &    20:29:53.91 &   -18:34:59.48 &  6945.70 &     IGRINS &      224 &   160 \\
   HIP 101589 &            A3V &    20:35:18.54 &   +14:40:27.17 &  6448.83 &     CHIRON &      352 &   420 \\
@@
   HIP 101867 &            A0V &    20:38:31.34 &    +21:12:4.25 &  6489.78 &     CHIRON &      408 &   440 \\
-  HIP 101909 &            B3V &     20:39:4.97 &   +15:50:17.52 &  6945.60 &     IGRINS &      360 &     280 \\
-  HIP 101909 &            B3V &     20:39:4.97 &   +15:50:17.52 &  7230.69 &     IGRINS &      720 &     430 \\
-  HIP 102487 &            A1V &     20:46:9.99 &   -21:30:50.52 &  6847.80 &     IGRINS &      480 &     530 \\
-  HIP 103298 &            A5V &    20:55:38.57 &    +12:34:6.81 &  6946.58 &     IGRINS &      224 &     630 \\
-  HIP 103298 &            A5V &    20:55:38.57 &    +12:34:6.81 &  7230.70 &     IGRINS &      600 &     870 \\
+  HIP 101909 &            B3V &     20:39:4.97 &   +15:50:17.52 &  6945.60 &     IGRINS &      360 &   140 \\
+  HIP 101909 &            B3V &     20:39:4.97 &   +15:50:17.52 &  7230.69 &     IGRINS &      720 &    90 \\
+  HIP 102487 &            A1V &     20:46:9.99 &   -21:30:50.52 &  6847.80 &     IGRINS &      480 &    80 \\
+  HIP 103298 &            A5V &    20:55:38.57 &    +12:34:6.81 &  6946.58 &     IGRINS &      224 &   100 \\
+  HIP 103298 &            A5V &    20:55:38.57 &    +12:34:6.81 &  7230.70 &     IGRINS &      600 &    80 \\
   HIP 103298 &            A5V &    20:55:38.57 &    +12:34:6.81 &  7155.93 &     CHIRON &     1141 &   290 \\
   HIP 104019 &            A5V &    21:04:24.30 &   -19:51:17.97 &  6474.90 &     CHIRON &      423 &   550 \\
-  HIP 104105 &           B8Vn &    21:05:29.27 &   +78:07:35.02 &  6945.69 &     IGRINS &      280 &     310 \\
+  HIP 104105 &           B8Vn &    21:05:29.27 &   +78:07:35.02 &  6945.69 &     IGRINS &      280 &   140 \\
   HIP 104139 &            A1V &    21:05:56.83 &   -17:13:58.30 &  6448.90 &     CHIRON &      204 &   490 \\
-  HIP 104365 &            A0V &    21:08:33.63 &   -21:11:37.22 &  6847.81 &     IGRINS &      480 &     710 \\
-  HIP 104365 &            A0V &    21:08:33.63 &   -21:11:37.22 &  7237.82 &     IGRINS &      720 &    2150 \\
+  HIP 104365 &            A0V &    21:08:33.63 &   -21:11:37.22 &  6847.81 &     IGRINS &      480 &   100 \\
+  HIP 104365 &            A0V &    21:08:33.63 &   -21:11:37.22 &  7237.82 &     IGRINS &      720 &    50 \\
   HIP 105140 &            A1V &    21:17:56.28 &   -32:10:21.15 &  6485.90 &     CHIRON &      372 &   420 \\
   HIP 105282 &            B6V &    21:19:28.75 &   +49:30:37.06 &  6522.65 &        HRS &     1006 &   850 \\
-  HIP 105891 &          B7III &    21:26:44.97 &   +52:53:54.73 &  6946.59 &     IGRINS &      224 &     210 \\
+  HIP 105891 &            B6V &    21:26:44.97 &   +52:53:54.73 &  6946.59 &     IGRINS &      224 &    90 \\
   HIP 105942 &            B3V &    21:27:21.37 &    +37:07:0.47 &  6523.87 &        HRS &      480 &   760 \\
-  HIP 105966 &         A1VmA3 &    21:27:40.06 &   +27:36:30.94 &  6585.64 &       TS23 &      530 &    1800 \\
+  HIP 105966 &            A1V &    21:27:40.06 &   +27:36:30.94 &  6585.64 &       TS23 &      530 &  1800 \\
   HIP 105972 &            B7V &    21:27:46.14 &   +66:48:32.74 &  6507.82 &        HRS &      267 &   690 \\
@@
   HIP 106711 &           A3Vn &    21:36:56.98 &   +40:24:48.67 &  6618.53 &       TS23 &      557 &  2010 \\
-  HIP 106786 &            A7V &    21:37:45.11 &   -07:51:15.13 &  6945.64 &     IGRINS &      224 &     830 \\
+  HIP 106786 &            A7V &    21:37:45.11 &   -07:51:15.13 &  6945.64 &     IGRINS &      224 &   230 \\
   HIP 106786 &            A7V &    21:37:45.11 &   -07:51:15.13 &  6962.59 &       TS23 &      284 &  1620 \\
@@
   HIP 108294 &           A2Vn &    21:56:22.77 &   -37:15:13.16 &  6790.81 &     CHIRON &      470 &   510 \\
-  HIP 108339 &          A2Vnn &    21:56:56.37 &   +12:04:35.37 &  6945.65 &     IGRINS &      224 &     320 \\
-  HIP 109056 &           B9Vn &    22:05:34.67 &   +28:57:50.32 &  6945.66 &     IGRINS &      240 &     280 \\
-  HIP 109056 &           B9Vn &    22:05:34.67 &   +28:57:50.32 &  6948.56 &     IGRINS &     1156 &    1510 \\
-  HIP 109056 &           B9Vn &    22:05:34.67 &   +28:57:50.32 &  6946.65 &     IGRINS &      784 &    1070 \\
-  HIP 109056 &           B9Vn &    22:05:34.67 &   +28:57:50.32 &  6947.57 &     IGRINS &     1746 &     850 \\
+  HIP 108339 &          A2Vnn &    21:56:56.37 &   +12:04:35.37 &  6945.65 &     IGRINS &      224 &   160 \\
+  HIP 109056 &           B9Vn &    22:05:34.67 &   +28:57:50.32 &  6945.66 &     IGRINS &      240 &   150 \\
+  HIP 109056 &           B9Vn &    22:05:34.67 &   +28:57:50.32 &  6948.56 &     IGRINS &     1156 &   160 \\
+  HIP 109056 &           B9Vn &    22:05:34.67 &   +28:57:50.32 &  6946.65 &     IGRINS &      784 &   230 \\
+  HIP 109056 &           B9Vn &    22:05:34.67 &   +28:57:50.32 &  6947.57 &     IGRINS &     1746 &   170 \\
   HIP 109139 &            B8V &    22:06:26.23 &   -13:52:10.86 &  6524.67 &     CHIRON &      207 &   590 \\
@@
   HIP 109521 &            A5V &     22:11:9.89 &   +50:49:24.26 &  6962.60 &       TS23 &      587 &  1500 \\
-  HIP 109521 &            A5V &     22:11:9.89 &   +50:49:24.26 &  6945.68 &     IGRINS &      224 &     590 \\
-  HIP 109831 &          A2Vnn &    22:14:44.37 &   +42:57:14.07 &  6945.67 &     IGRINS &      224 &     380 \\
-  HIP 109831 &          A2Vnn &    22:14:44.37 &   +42:57:14.07 &  7237.77 &     IGRINS &     1440 &     860 \\
-  HIP 109831 &          A2Vnn &    22:14:44.37 &   +42:57:14.07 &  7288.73 &     IGRINS &      900 &    2560 \\
-  HIP 110838 &       B9Vn+G0V &    22:27:19.97 &   -64:57:58.88 &  6543.82 &     CHIRON &      506 &     550 \\
-  HIP 110838 &       B9Vn+G0V &    22:27:19.97 &   -64:57:58.88 &  6880.76 &     CHIRON &      354 &     780 \\
+  HIP 109521 &            A5V &     22:11:9.89 &   +50:49:24.26 &  6945.68 &     IGRINS &      224 &   200 \\
+  HIP 109831 &          A2Vnn &    22:14:44.37 &   +42:57:14.07 &  6945.67 &     IGRINS &      224 &   160 \\
+  HIP 109831 &          A2Vnn &    22:14:44.37 &   +42:57:14.07 &  7237.77 &     IGRINS &     1440 &   100 \\
+  HIP 109831 &          A2Vnn &    22:14:44.37 &   +42:57:14.07 &  7288.73 &     IGRINS &      900 &    30 \\
+  HIP 110838 &           B9Vn &    22:27:19.97 &   -64:57:58.88 &  6543.82 &     CHIRON &      506 &   550 \\
+  HIP 110838 &           B9Vn &    22:27:19.97 &   -64:57:58.88 &  6880.76 &     CHIRON &      354 &   780 \\
   HIP 110935 &            A4V &    22:28:37.67 &   -67:29:20.62 &  6896.67 &     CHIRON &      696 &   630 \\
-  HIP 111056 &            A3V &    22:29:52.98 &   +78:49:27.43 &  7288.80 &     IGRINS &      180 &    1010 \\
-  HIP 111056 &            A3V &    22:29:52.98 &   +78:49:27.43 &  6945.76 &     IGRINS &      224 &     380 \\
+  HIP 111056 &            A3V &    22:29:52.98 &   +78:49:27.43 &  7288.80 &     IGRINS &      180 &    30 \\
+  HIP 111056 &            A3V &    22:29:52.98 &   +78:49:27.43 &  6945.76 &     IGRINS &      224 &   120 \\
   HIP 111068 &          B9.5V &     22:30:1.81 &   +32:34:21.50 &  6512.74 &        HRS &      362 &   500 \\
@@
   HIP 115115 &            A0V &    23:18:57.68 &   -09:36:38.70 &  7163.90 &     CHIRON &      600 &   190 \\
-  HIP 115115 &            A0V &    23:18:57.68 &   -09:36:38.70 &  7230.95 &     IGRINS &      500 &    1040 \\
+  HIP 115115 &            A0V &    23:18:57.68 &   -09:36:38.70 &  7230.95 &     IGRINS &      500 &    40 \\
   HIP 115115 &            A0V &    23:18:57.68 &   -09:36:38.70 &  6797.87 &     CHIRON &      610 &   330 \\
   HIP 116247 &            A0V &    23:33:16.62 &   -20:54:52.21 &  6463.89 &     CHIRON &      368 &   560 \\
-  HIP 116247 &            A0V &    23:33:16.62 &   -20:54:52.21 &  7237.94 &     IGRINS &      240 &     980 \\
+  HIP 116247 &            A0V &    23:33:16.62 &   -20:54:52.21 &  7237.94 &     IGRINS &      240 &   100 \\
   HIP 116582 &            B8V &    23:37:32.04 &   +44:25:44.37 &  6510.77 &        HRS &      534 &   670 \\
-  HIP 116611 &           A0Vn &    23:37:56.80 &    +18:24:2.40 &  6946.61 &     IGRINS &      224 &     400 \\
+  HIP 116611 &           A0Vn &    23:37:56.80 &    +18:24:2.40 &  6946.61 &     IGRINS &      224 &   140 \\
   HIP 116631 &            B8V &     23:38:8.20 &    +43:16:5.06 &  6962.63 &       TS23 &      249 &  1980 \\
-  HIP 116631 &            B8V &     23:38:8.20 &    +43:16:5.06 &  6946.78 &     IGRINS &      224 &     680 \\
+  HIP 116631 &            B8V &     23:38:8.20 &    +43:16:5.06 &  6946.78 &     IGRINS &      224 &   160 \\
   HIP 116631 &            B8V &     23:38:8.20 &    +43:16:5.06 &  6583.71 &       TS23 &      162 &  1740 \\
-  HIP 116631 &            B8V &     23:38:8.20 &    +43:16:5.06 &  7288.80 &     IGRINS &      180 &    2150 \\
+  HIP 116631 &            B8V &     23:38:8.20 &    +43:16:5.06 &  7288.80 &     IGRINS &      180 &    30 \\
   HIP 116805 &            A0V &    23:40:24.51 &    +44:20:2.16 &  6528.84 &       TS23 &      158 &  1680 \\
@@
   HIP 116971 &            B9V &    23:42:43.34 &   -14:32:41.65 &  6936.73 &     CHIRON &      344 &   600 \\
-  HIP 117089 &            B9V &    23:44:12.08 &   -18:16:36.97 &  7288.81 &     IGRINS &      180 &    1130 \\
-  HIP 117089 &            B9V &    23:44:12.08 &   -18:16:36.97 &  7237.95 &     IGRINS &      720 &    1610 \\
+  HIP 117089 &            B9V &    23:44:12.08 &   -18:16:36.97 &  7288.81 &     IGRINS &      180 &    20 \\
+  HIP 117089 &            B9V &    23:44:12.08 &   -18:16:36.97 &  7237.95 &     IGRINS &      720 &    60 \\
   HIP 117089 &            B9V &    23:44:12.08 &   -18:16:36.97 &  6513.86 &     CHIRON &      853 &   600 \\
@@
   HIP 118121 &            A1V &    23:57:35.08 &   -64:17:53.63 &  6795.86 &     CHIRON &      233 &   500 \\
-  HIP 118243 &            B1V &     23:59:0.54 &   +55:45:17.74 &  6945.73 &     IGRINS &      224 &     370 \\
+  HIP 118243 &            B1V &     23:59:0.54 &   +55:45:17.74 &  6945.73 &     IGRINS &      224 &   170 \\
   HIP 118243 &            B1V &     23:59:0.54 &   +55:45:17.74 &  6583.74 &       TS23 &      351 &  1760
@@
 \LongTables
-\begin{deluxetable*}{|l|rrlrrrrll|}
+\begin{deluxetable*}{|l|rrlrrrll|}
 \tabletypesize{\small}
@@
 \tablehead{
-     \colhead{} & \colhead{} & \colhead{} & \colhead{Used in} & \colhead{$T_\mathrm{eff}$} & \colhead{$v\sin{i}$} & \colhead{[Fe/H]} & \colhead{} & \multicolumn{2}{c}{Mass ($M_{\odot}$)} \\ 
-       \colhead{star} & \colhead{component} & \colhead{$N_\mathrm{obs}$} & \colhead{Analysis}  &   \colhead{(K)} &   \colhead{($\mathrm{km\ s}^{-1}$)} &  \colhead{(dex)} & \colhead{$\Delta K$} &   \colhead{Isochrone} &   \colhead{Spectral Type}
+     \colhead{} & \colhead{} & \colhead{} & \colhead{Used in} & \colhead{$T_\mathrm{eff}$} & \colhead{$v\sin{i}$} & \colhead{[Fe/H]} & \multicolumn{2}{c}{Mass ($M_{\odot}$)} \\ 
+       \colhead{star} & \colhead{component} & \colhead{$N_\mathrm{obs}$} & \colhead{Analysis}  &   \colhead{(K)} &   \colhead{($\mathrm{km\ s}^{-1}$)} &  \colhead{(dex)} &   \colhead{Isochrone} &   \colhead{Spectral Type}
        }
@@
 \startdata
-   HIP 2548 & Aa,Ab &     2 & yes &  $5732 \pm 112$ &      30 &    -0.5 &          0 &  $1.0^{+0.06}_{-0.04}$ &  $1.0^{+0.04}_{-0.03}$ \\
-   HIP 5310 & AB &     1 & yes &  $3343 \pm 154$ &      30 &     0.0 &          0 &  $0.3^{+0.13}_{-0.08}$ &  $0.4^{+0.12}_{-0.12}$ \\
-     HR 545 & Aa,Ab$^{\dagger}$ &     3 & yes &   $4312 \pm 87$ &       5 &    -0.5 &          0 &  $0.8^{+0.11}_{-0.10}$ &  $0.7^{+0.01}_{-0.02}$ \\
-     HR 604 & AB &     1 & no &  $4736 \pm 150$ &       5 &     0.5 &          0 &    $nan^{+nan}_{-nan}$ &  $0.8^{+0.02}_{-0.02}$ \\
-  HIP 10732 & AB$^{\dagger}$ &     2 & yes &  $5578 \pm 109$ &       5 &     0.0 &          0 &  $1.0^{+0.29}_{-0.04}$ &  $1.0^{+0.02}_{-0.04}$ \\
-  HIP 12332 & AB$^{\dagger}$ &     2 & yes &  $5551 \pm 107$ &      10 &     0.0 &          0 &    $nan^{+nan}_{-nan}$ &  $1.0^{+0.01}_{-0.04}$ \\
-  HIP 12706 & AB &     2 & yes &  $6051 \pm 107$ &      10 &     0.0 &          0 &  $1.1^{+0.03}_{-0.03}$ &  $1.1^{+0.04}_{-0.05}$ \\
-  HIP 13165 & AB? &     1 & no &  $5773 \pm 163$ &       5 &    -0.5 &          0 &  $1.1^{+0.31}_{-0.08}$ &  $1.0^{+0.10}_{-0.03}$ \\
-  HIP 13327 & AB$^{\dagger}$ &     1 & yes &  $5524 \pm 150$ &       5 &    -0.5 &          0 &  $1.2^{+0.20}_{-0.21}$ &  $1.0^{+0.03}_{-0.04}$ \\
-  HIP 14576 & Aa,Ab &     2 & no &  $6980 \pm 103$ &      10 &     0.0 &          0 &  $1.4^{+0.03}_{-0.03}$ &  $1.5^{+0.05}_{-0.03}$ \\
-  HIP 14764 & AB$^{\dagger}$ &     2 & yes &  $5601 \pm 108$ &      30 &     0.5 &          0 &    $nan^{+nan}_{-nan}$ &  $1.0^{+0.03}_{-0.03}$ \\
-  HIP 16244 & AB &     2 & yes &  $5592 \pm 107$ &       5 &    -0.5 &          0 &  $1.2^{+0.20}_{-0.22}$ &  $1.0^{+0.03}_{-0.03}$ \\
-  HIP 16340 & AB$^{\dagger}$ &     1 & yes &  $6214 \pm 150$ &       5 &    -0.5 &          0 &  $1.2^{+0.29}_{-0.07}$ &  $1.2^{+0.06}_{-0.05}$ \\
-  HIP 16611 & AB &     1 & no &  $5476 \pm 154$ &       1 &     0.5 &          0 &  $0.9^{+0.04}_{-0.04}$ &  $0.9^{+0.04}_{-0.03}$ \\
-  HIP 17563 & AB &     1 & yes &  $8574 \pm 147$ &       5 &     0.5 &          0 &  $1.9^{+0.25}_{-0.11}$ &  $2.0^{+0.05}_{-0.06}$ \\
-  HIP 18724 & AB &     1 & no &  $6831 \pm 154$ &      20 &     0.0 &          0 &  $1.7^{+0.13}_{-0.23}$ &  $1.4^{+0.04}_{-0.04}$ \\
-  HIP 19949 & AB$^{\dagger}$ &     1 & yes &  $6492 \pm 155$ &      20 &    -0.5 &          0 &  $1.3^{+0.06}_{-0.05}$ &  $1.3^{+0.06}_{-0.06}$ \\
-  HIP 20380 & AB$^{\dagger}$ &     2 & yes &  $6492 \pm 109$ &      20 &    -0.5 &          0 &  $1.3^{+0.04}_{-0.04}$ &  $1.3^{+0.03}_{-0.05}$ \\
-  HIP 21589 & Aa,Ab &     1 & yes &  $4562 \pm 154$ &       5 &     0.0 &          0 &  $0.7^{+0.04}_{-0.03}$ &  $0.8^{+0.02}_{-0.03}$ \\
-  HIP 22833 & AB &     2 & yes &  $4745 \pm 107$ &      10 &     0.0 &          0 &  $0.8^{+0.02}_{-0.02}$ &  $0.8^{+0.02}_{-0.01}$ \\
-  HIP 22958 & Aa,Ab &     2 & yes &  $6126 \pm 112$ &      30 &    -0.5 &          0 &  $1.4^{+0.22}_{-0.21}$ &  $1.2^{+0.04}_{-0.04}$ \\
-  HIP 23362 & AB$^{\dagger}$ &     1 & yes &  $6283 \pm 158$ &       5 &    -0.5 &          0 &  $1.2^{+0.06}_{-0.05}$ &  $1.2^{+0.07}_{-0.05}$ \\
-  HIP 23916 & Aa,Ab$^{\dagger}$ &     1 & yes &  $5450 \pm 158$ &       5 &    -0.5 &          0 &  $1.1^{+0.20}_{-0.20}$ &  $0.9^{+0.04}_{-0.03}$ \\
-  HIP 24902 & AB &     1 & yes &  $5679 \pm 154$ &      30 &     0.0 &          0 &  $1.0^{+0.05}_{-0.04}$ &  $1.0^{+0.04}_{-0.03}$ \\
-  HIP 25143 & AB$^{\dagger}$ &     2 & yes &  $5883 \pm 109$ &      30 &     0.0 &          0 &  $1.1^{+0.04}_{-0.03}$ &  $1.1^{+0.05}_{-0.07}$ \\
-  HIP 26126 & AB? &     3 & yes &   $5841 \pm 91$ &       5 &    -0.5 &          0 &  $1.0^{+0.03}_{-0.03}$ &  $1.0^{+0.05}_{-0.04}$ \\
-  HIP 32607 & AB$^{\dagger}$ &     3 & yes &   $5068 \pm 91$ &       5 &    -0.5 &          0 &  $0.8^{+0.02}_{-0.02}$ &  $0.9^{+0.01}_{-0.01}$ \\
-  HIP 37450 & AB$^{\dagger}$ &     1 & yes &   $nan \pm nan$ & \nodata & \nodata &          0 &    $nan^{+nan}_{-nan}$ &    $nan^{+nan}_{-nan}$ \\
-  HIP 38593 & AB$^{\dagger}$ &     2 & yes &  $5398 \pm 112$ &       5 &    -0.5 &          0 &  $1.3^{+0.08}_{-0.13}$ &  $0.9^{+0.03}_{-0.03}$ \\
-  HIP 38846 & AB$^{\dagger}$ &     1 & yes &  $6595 \pm 158$ &      10 &     0.0 &          0 &  $1.7^{+0.12}_{-0.21}$ &  $1.3^{+0.09}_{-0.05}$ \\
-  HIP 39847 & Aa,Ab$^{\dagger}$ &     2 & no &  $5750 \pm 107$ &      10 &    -0.5 &          0 &  $1.0^{+0.04}_{-0.03}$ &  $1.0^{+0.05}_{-0.03}$ \\
-  HIP 40881 & AB$^{\dagger}$ &     1 & yes &  $4562 \pm 154$ &      10 &    -0.5 &          0 &  $0.8^{+0.18}_{-0.05}$ &  $0.8^{+0.02}_{-0.03}$ \\
-  HIP 42129 & AB &     1 & yes &  $5241 \pm 158$ &      10 &    -0.5 &          0 &  $1.2^{+0.12}_{-0.18}$ &  $0.9^{+0.04}_{-0.02}$ \\
-  HIP 46283 & AB? &     3 & yes &   $9268 \pm 85$ &      10 &     0.5 &          0 &    $nan^{+nan}_{-nan}$ &  $2.2^{+0.02}_{-0.02}$ \\
-  HIP 55266 & AB &     1 & no &  $8483 \pm 139$ &      30 &    -0.5 &          0 &  $1.8^{+0.06}_{-0.04}$ &  $2.0^{+0.06}_{-0.05}$ \\
-  HIP 63945 & Aa,Ab or AC? &     1 & no &  $7038 \pm 162$ &      10 &    -0.5 &          0 &  $1.6^{+0.26}_{-0.16}$ &  $1.5^{+0.08}_{-0.06}$ \\
-  HIP 72154 & AB$^{\dagger}$ &     1 & yes &  $4918 \pm 162$ &      30 &    -0.5 &          0 &  $0.9^{+0.22}_{-0.09}$ &  $0.8^{+0.03}_{-0.03}$ \\
-  HIP 76267 & AB &     1 & yes &  $5449 \pm 158$ &       5 &    -0.5 &          0 &  $0.9^{+0.04}_{-0.04}$ &  $0.9^{+0.04}_{-0.03}$ \\
-  HIP 77336 & AB$^{\dagger}$ &     2 & yes &  $6407 \pm 112$ &      20 &     0.0 &          0 &  $1.2^{+0.04}_{-0.04}$ &  $1.3^{+0.04}_{-0.05}$ \\
-  HIP 77516 & AB &     1 & yes &  $6825 \pm 141$ &       5 &     0.5 &          0 &  $1.4^{+0.21}_{-0.06}$ &  $1.4^{+0.03}_{-0.04}$ \\
-  HIP 78820 & AB &     1 & no &  $5658 \pm 158$ &       5 &    -0.5 &          0 &  $1.3^{+0.11}_{-0.13}$ &  $1.0^{+0.04}_{-0.04}$ \\
-  HIP 79199 & AB &     1 & no &  $4616 \pm 158$ &       5 &    -0.5 &          0 &  $0.9^{+0.14}_{-0.14}$ &  $0.8^{+0.02}_{-0.03}$ \\
-  HIP 79404 & AB$^{\dagger}$ &     2 & yes &  $4773 \pm 112$ &      10 &    -0.5 &          0 &  $1.1^{+0.07}_{-0.08}$ &  $0.8^{+0.02}_{-0.01}$ \\
-  HIP 80460 & AB &     1 & yes &  $6391 \pm 155$ &      10 &     0.0 &          0 &  $1.2^{+0.06}_{-0.05}$ &  $1.3^{+0.06}_{-0.06}$ \\
-  HIP 82673 & AB$^{\dagger}$ &     2 & yes &  $4668 \pm 112$ &       5 &     0.5 &          0 &  $0.8^{+0.03}_{-0.03}$ &  $0.8^{+0.01}_{-0.02}$ \\
-  HIP 84606 & AB &     1 & yes &  $5476 \pm 154$ &      10 &    -0.5 &          0 &  $0.9^{+0.05}_{-0.04}$ &  $0.9^{+0.04}_{-0.03}$ \\
-  HIP 88116 & AB$^{\dagger}$ &     2 & yes &  $5293 \pm 112$ &       5 &     0.0 &          0 &  $0.9^{+0.03}_{-0.03}$ &  $0.9^{+0.02}_{-0.03}$ \\
-  HIP 88817 & Ba,Bb$^{\dagger}$ &     1 & yes &  $3647 \pm 154$ &      20 &     0.0 &          0 &  $0.5^{+0.07}_{-0.10}$ &  $0.5^{+0.03}_{-0.05}$ \\
-  HIP 88818 & Aa,Ab &     3 & yes &   $5296 \pm 91$ &      20 &    -0.5 &          0 &  $0.9^{+0.02}_{-0.02}$ &  $0.9^{+0.02}_{-0.03}$ \\
-  HIP 91118 & AB &     1 & yes &  $6492 \pm 155$ &      10 &    -0.5 &          0 &  $1.3^{+0.26}_{-0.07}$ &  $1.3^{+0.06}_{-0.06}$ \\
-  HIP 93805 & Aa,Ab$^{\dagger}$ &     2 & yes &  $4054 \pm 109$ &       5 &    -0.5 &          0 &  $0.6^{+0.03}_{-0.03}$ &  $0.6^{+0.04}_{-0.02}$ \\
-  HIP 96840 & AB &     1 & yes &  $9942 \pm 152$ &      10 &     0.0 &          0 &    $nan^{+nan}_{-nan}$ &  $2.3^{+0.03}_{-0.01}$ \\
- HIP 100221 & AB &     1 & yes &  $5273 \pm 154$ &      20 &    -0.5 &          0 &  $0.9^{+0.29}_{-0.07}$ &  $0.9^{+0.04}_{-0.03}$ \\
- HIP 100907 & AB$^{\dagger}$ &     2 & yes &  $5222 \pm 109$ &      10 &     0.0 &          0 &  $0.9^{+0.03}_{-0.03}$ &  $0.9^{+0.04}_{-0.02}$ \\
- HIP 103298 & Aa,Ab &     3 & yes &   $4615 \pm 90$ &       5 &    -0.5 &          0 &  $0.7^{+0.02}_{-0.02}$ &  $0.8^{+0.01}_{-0.02}$ \\
- HIP 109139 & AB &     2 & yes &  $5710 \pm 112$ &      20 &    -0.5 &          0 &  $1.0^{+0.04}_{-0.03}$ &  $1.0^{+0.03}_{-0.03}$ \\
- HIP 109521 & Aa,Ab$^{\dagger}$ &     3 & no &   $4412 \pm 87$ &      10 &     0.0 &          0 &  $0.7^{+0.02}_{-0.02}$ &  $0.7^{+0.01}_{-0.01}$ \\
- HIP 115115 & AB &     3 & yes &   $4943 \pm 91$ &       5 &    -0.5 &          0 &  $0.8^{+0.02}_{-0.02}$ &  $0.8^{+0.02}_{-0.02}$
+   HIP 2548 & Aa,Ab &     2 & yes &  $5732 \pm 112$ &      30 &    -0.5  &  $1.0^{+0.06}_{-0.04}$ &  $1.0^{+0.04}_{-0.03}$ \\
+   HIP 5310 & AB &     1 & yes &  $3343 \pm 154$ &      30 &     0.0  &  $0.3^{+0.13}_{-0.08}$ &  $0.4^{+0.12}_{-0.12}$ \\
+     HR 545 & Aa,Ab$^{\dagger}$ &     3 & yes &   $4312 \pm 87$ &       5 &    -0.5  &  $0.8^{+0.11}_{-0.10}$ &  $0.7^{+0.01}_{-0.02}$ \\
+     HR 604 & AB &     1 & no &  $4736 \pm 150$ &       5 &     0.5  &    $0.9^{+0.17}_{-0.12}$ &  $0.8^{+0.02}_{-0.02}$ \\
+  HIP 10732 & AB$^{\dagger}$ &     2 & yes &  $5578 \pm 109$ &       5 &     0.0  &  $1.0^{+0.29}_{-0.04}$ &  $1.0^{+0.02}_{-0.04}$ \\
+  HIP 12332 & AB$^{\dagger}$ &     2 & yes &  $5551 \pm 107$ &      10 &     0.0  &    $1.0^{+0.03}_{--0.03}$ &  $1.0^{+0.01}_{-0.04}$ \\
+  HIP 12706 & AB &     2 & yes &  $6051 \pm 107$ &      10 &     0.0  &  $1.1^{+0.03}_{-0.03}$ &  $1.1^{+0.04}_{-0.05}$ \\
+  HIP 13165 & AB? &     1 & no &  $5773 \pm 163$ &       5 &    -0.5  &  $1.1^{+0.31}_{-0.08}$ &  $1.0^{+0.10}_{-0.03}$ \\
+  HIP 13327 & AB$^{\dagger}$ &     1 & yes &  $5524 \pm 150$ &       5 &    -0.5  &  $1.2^{+0.20}_{-0.21}$ &  $1.0^{+0.03}_{-0.04}$ \\
+  HIP 14576 & Aa,Ab &     2 & no &  $6980 \pm 103$ &      10 &     0.0  &  $1.4^{+0.03}_{-0.03}$ &  $1.5^{+0.05}_{-0.03}$ \\
+  HIP 14764 & AB$^{\dagger}$ &     2 & yes &  $5601 \pm 108$ &      30 &     0.5 0 &    $1.0^{+0.34}_{-0.05}$ &  $1.0^{+0.03}_{-0.03}$ \\
+  HIP 16244 & AB &     2 & yes &  $5592 \pm 107$ &       5 &    -0.5  &  $1.2^{+0.20}_{-0.22}$ &  $1.0^{+0.03}_{-0.03}$ \\
+  HIP 16340 & AB$^{\dagger}$ &     1 & yes &  $6214 \pm 150$ &       5 &    -0.5  &  $1.2^{+0.29}_{-0.07}$ &  $1.2^{+0.06}_{-0.05}$ \\
+  HIP 16611 & AB &     1 & no &  $5476 \pm 154$ &       1 &     0.5  &  $0.9^{+0.04}_{-0.04}$ &  $0.9^{+0.04}_{-0.03}$ \\
+  HIP 17563 & AB &     1 & yes &  $8574 \pm 147$ &       5 &     0.5  &  $1.9^{+0.25}_{-0.11}$ &  $2.0^{+0.05}_{-0.06}$ \\
+  HIP 18724 & AB &     1 & no &  $6831 \pm 154$ &      20 &     0.0  &  $1.7^{+0.13}_{-0.23}$ &  $1.4^{+0.04}_{-0.04}$ \\
+  HIP 19949 & AB$^{\dagger}$ &     1 & yes &  $6492 \pm 155$ &      20 &    -0.5  &  $1.3^{+0.06}_{-0.05}$ &  $1.3^{+0.06}_{-0.06}$ \\
+  HIP 20380 & AB$^{\dagger}$ &     2 & yes &  $6492 \pm 109$ &      20 &    -0.5  &  $1.3^{+0.04}_{-0.04}$ &  $1.3^{+0.03}_{-0.05}$ \\
+  HIP 21589 & Aa,Ab &     1 & yes &  $4562 \pm 154$ &       5 &     0.0  &  $0.7^{+0.04}_{-0.03}$ &  $0.8^{+0.02}_{-0.03}$ \\
+  HIP 22833 & AB &     2 & yes &  $4745 \pm 107$ &      10 &     0.0  &  $0.8^{+0.02}_{-0.02}$ &  $0.8^{+0.02}_{-0.01}$ \\
+  HIP 22958 & Aa,Ab &     2 & yes &  $6126 \pm 112$ &      30 &    -0.5  &  $1.4^{+0.22}_{-0.21}$ &  $1.2^{+0.04}_{-0.04}$ \\
+  HIP 23362 & AB$^{\dagger}$ &     1 & yes &  $6283 \pm 158$ &       5 &    -0.5  &  $1.2^{+0.06}_{-0.05}$ &  $1.2^{+0.07}_{-0.05}$ \\
+  HIP 23916 & Aa,Ab$^{\dagger}$ &     1 & yes &  $5450 \pm 158$ &       5 &    -0.5  &  $1.1^{+0.20}_{-0.20}$ &  $0.9^{+0.04}_{-0.03}$ \\
+  HIP 24902 & AB &     1 & yes &  $5679 \pm 154$ &      30 &     0.0  &  $1.0^{+0.05}_{-0.04}$ &  $1.0^{+0.04}_{-0.03}$ \\
+  HIP 25143 & AB$^{\dagger}$ &     2 & yes &  $5883 \pm 109$ &      30 &     0.0  &  $1.1^{+0.04}_{-0.03}$ &  $1.1^{+0.05}_{-0.07}$ \\
+  HIP 26126 & AB? &     3 & yes &   $5841 \pm 91$ &       5 &    -0.5  &  $1.0^{+0.03}_{-0.03}$ &  $1.0^{+0.05}_{-0.04}$ \\
+  HIP 32607 & AB$^{\dagger}$ &     3 & yes &   $5068 \pm 91$ &       5 &    -0.5  &  $0.8^{+0.02}_{-0.02}$ &  $0.9^{+0.01}_{-0.01}$ \\
+  HIP 38538 & AB      &     1 & no &   $6576 \pm 150$ &      30 &    -0.5  &  $1.3^{+0.05}_{-0.05}$ &  $1.3^{+0.09}_{-0.05}$ \\
+  HIP 38593 & AB$^{\dagger}$ &     2 & yes &  $5398 \pm 112$ &       5 &    -0.5  &  $1.3^{+0.08}_{-0.13}$ &  $0.9^{+0.03}_{-0.03}$ \\
+  HIP 38846 & AB$^{\dagger}$ &     1 & yes &  $6595 \pm 158$ &      10 &     0.0  &  $1.7^{+0.12}_{-0.21}$ &  $1.3^{+0.09}_{-0.05}$ \\
+  HIP 39847 & Aa,Ab$^{\dagger}$ &     2 & no &  $5750 \pm 107$ &      10 &    -0.5  &  $1.0^{+0.04}_{-0.03}$ &  $1.0^{+0.05}_{-0.03}$ \\
+  HIP 40881 & AB$^{\dagger}$ &     1 & yes &  $4562 \pm 154$ &      10 &    -0.5  &  $0.8^{+0.18}_{-0.05}$ &  $0.8^{+0.02}_{-0.03}$ \\
+  HIP 42129 & AB &     1 & yes &  $5241 \pm 158$ &      10 &    -0.5  &  $1.2^{+0.12}_{-0.18}$ &  $0.9^{+0.04}_{-0.02}$ \\
+  HIP 46283 & AB? &     3 & yes &   $9268 \pm 85$ &      10 &     0.5  &    $2.0^{+0.04}_{-0.02}$ &  $2.2^{+0.02}_{-0.02}$ \\
+  HIP 52678 & AB$^{\dagger}$ &     2 & yes &  $5033 \pm 112$ &      10 &    -0.5  &  $1.0^{+0.15}_{-0.19}$ &  $0.8^{+0.01}_{-0.02}$ \\  
+  HIP 55266 & AB &     1 & no &  $8483 \pm 139$ &      30 &    -0.5 &  $1.8^{+0.06}_{-0.04}$ &  $2.0^{+0.06}_{-0.05}$ \\
+  HIP 63945 & Aa,Ab or AC? &     1 & no &  $7038 \pm 162$ &      10 &    -0.5 &  $1.6^{+0.26}_{-0.16}$ &  $1.5^{+0.08}_{-0.06}$ \\
+  HIP 72154 & AB$^{\dagger}$ &     1 & yes &  $4918 \pm 162$ &      30 &    -0.5  &  $0.9^{+0.22}_{-0.09}$ &  $0.8^{+0.03}_{-0.03}$ \\
+  HIP 76267 & AB &     1 & yes &  $5449 \pm 158$ &       5 &    -0.5  &  $0.9^{+0.04}_{-0.04}$ &  $0.9^{+0.04}_{-0.03}$ \\
+  HIP 77336 & AB$^{\dagger}$ &     2 & yes &  $6407 \pm 112$ &      20 &     0.0  &  $1.2^{+0.04}_{-0.04}$ &  $1.3^{+0.04}_{-0.05}$ \\
+  HIP 77516 & AB &     1 & yes &  $6825 \pm 141$ &       5 &     0.5  &  $1.4^{+0.21}_{-0.06}$ &  $1.4^{+0.03}_{-0.04}$ \\
+  HIP 78820 & AB &     1 & no &  $5658 \pm 158$ &       5 &    -0.5 0 &  $1.3^{+0.11}_{-0.13}$ &  $1.0^{+0.04}_{-0.04}$ \\
+  HIP 79199 & AB &     1 & no &  $4616 \pm 158$ &       5 &    -0.5  &  $0.9^{+0.14}_{-0.14}$ &  $0.8^{+0.02}_{-0.03}$ \\
+  HIP 79404 & AB$^{\dagger}$ &     2 & yes &  $4773 \pm 112$ &      10 &    -0.5  &  $1.1^{+0.07}_{-0.08}$ &  $0.8^{+0.02}_{-0.01}$ \\
+  HIP 80460 & AB &     1 & yes &  $6391 \pm 155$ &      10 &     0.0  &  $1.2^{+0.06}_{-0.05}$ &  $1.3^{+0.06}_{-0.06}$ \\
+  HIP 82673 & AB$^{\dagger}$ &     2 & yes &  $4668 \pm 112$ &       5 &     0.5  &  $0.8^{+0.03}_{-0.03}$ &  $0.8^{+0.01}_{-0.02}$ \\
+  HIP 84606 & AB &     1 & yes &  $5476 \pm 154$ &      10 &    -0.5 &  $0.9^{+0.05}_{-0.04}$ &  $0.9^{+0.04}_{-0.03}$ \\
+  HIP 85998 & Aa,Ab &     3 & yes &  $5460 \pm 91$ &      1 &    -0.5  &  $1.0^{+0.28}_{-0.03}$ &  $0.9^{+0.04}_{-0.01}$ \\
+  HIP 88116 & AB$^{\dagger}$ &     2 & yes &  $5293 \pm 112$ &       5 &     0.0  &  $0.9^{+0.03}_{-0.03}$ &  $0.9^{+0.02}_{-0.03}$ \\
+  HIP 88817 & Ba,Bb$^{\dagger}$ &     1 & yes &  $3647 \pm 154$ &      20 &     0.0  &  $0.5^{+0.07}_{-0.10}$ &  $0.5^{+0.03}_{-0.05}$ \\
+  HIP 88818 & Aa,Ab &     3 & yes &   $5296 \pm 91$ &      20 &    -0.5 &  $0.9^{+0.02}_{-0.02}$ &  $0.9^{+0.02}_{-0.03}$ \\
+  HIP 91118 & AB &     1 & yes &  $6492 \pm 155$ &      10 &    -0.5  &  $1.3^{+0.26}_{-0.07}$ &  $1.3^{+0.06}_{-0.06}$ \\
+  HIP 93805 & Aa,Ab$^{\dagger}$ &     2 & yes &  $4054 \pm 109$ &       5 &    -0.5  &  $0.6^{+0.03}_{-0.03}$ &  $0.6^{+0.04}_{-0.02}$ \\
+  HIP 96840 & AB &     1 & yes &  $9942 \pm 152$ &      10 &     0.0  &    $2.2^{+0.06}_{-0.05}$ &  $2.3^{+0.03}_{-0.01}$ \\
+ HIP 100221 & AB &     1 & yes &  $5273 \pm 154$ &      20 &    -0.5  &  $0.9^{+0.29}_{-0.07}$ &  $0.9^{+0.04}_{-0.03}$ \\
+ HIP 100907 & AB$^{\dagger}$ &     2 & yes &  $5222 \pm 109$ &      10 &     0.0  &  $0.9^{+0.03}_{-0.03}$ &  $0.9^{+0.04}_{-0.02}$ \\
+ HIP 103298 & Aa,Ab &     3 & yes &   $4615 \pm 90$ &       5 &    -0.5  &  $0.7^{+0.02}_{-0.02}$ &  $0.8^{+0.01}_{-0.02}$ \\
+ HIP 109139 & AB &     2 & yes &  $5710 \pm 112$ &      20 &    -0.5  &  $1.0^{+0.04}_{-0.03}$ &  $1.0^{+0.03}_{-0.03}$ \\
+ HIP 109521 & Aa,Ab$^{\dagger}$ &     3 & no &   $4412 \pm 87$ &      10 &     0.0  &  $0.7^{+0.02}_{-0.02}$ &  $0.7^{+0.01}_{-0.01}$ \\
+ HIP 115115 & AB &     3 & yes &   $4943 \pm 91$ &       5 &    -0.5  &  $0.8^{+0.02}_{-0.02}$ &  $0.8^{+0.02}_{-0.02}$
 
@@
 
-\begin{longtable*}{|l|lllll|}
-\hline
-            &        $T_\mathrm{eff}$ &      $\log{g}$ &             Mass &            Age & \\
-       star &        (K)              &      (cgs)     &      ($M_{\odot}$) &          (Myr) & source \\
-\hline
-\endhead
-\hline
-\multicolumn{3}{r}{{Continued on next page}} \\
-\endfoot
-
-\hline
-\endlastfoot
+\LongTables
+\begin{deluxetable*}{|l|lllll|}
+\tabletypesize{\small}
+\tablewidth{0pt}
+\tablecaption{Primary Star Fundamental Parameters}
+\tablehead{
+      \colhead{}  &  \colhead{$T_\mathrm{eff}$} &  \colhead{$\log{g}$} &  \colhead{Mass}          & \colhead{Age} & \colhead{} \\
+   \colhead{star} &  \colhead{(K)}              &  \colhead{(cgs)}     &  \colhead{($M_{\odot}$)} &  \colhead{(Myr)} & \colhead{source}
+       }
+
+\startdata
    HIP 2548 &   $11864 \pm 403$ &  $4.4 \pm 0.14$ &  $2.8^{+0.16}_{-0.15}$ &     $79^{+68}_{-53}$ &      DH2015 \\
-   HIP 3478 &  $14250 \pm 1000$ &  $4.2 \pm 0.25$ &  $3.8^{+0.50}_{-0.45}$ &     $22^{+40}_{-15}$ &  This Study \\
    HIP 5310 &    $8611 \pm 293$ &  $4.4 \pm 0.14$ &  $1.8^{+0.10}_{-0.08}$ &  $306^{+236}_{-196}$ &      DH2015 \\
@@
   HIP 17563 &  $19000 \pm 1000$ &  $4.5 \pm 0.25$ &  $6.0^{+0.66}_{-0.59}$ &      $10^{+11}_{-4}$ &  This Study \\
-  HIP 18396 &  $15000 \pm 1000$ &  $4.5 \pm 0.25$ &  $4.0^{+0.52}_{-0.47}$ &      $15^{+27}_{-9}$ &  This Study \\
   HIP 18724 &  $21000 \pm 1000$ &  $4.5 \pm 0.25$ &  $7.1^{+0.68}_{-0.64}$ &        $8^{+7}_{-3}$ &  This Study \\
@@
   HIP 23916 &  $16500 \pm 1000$ &  $4.2 \pm 0.25$ &  $4.8^{+0.56}_{-0.52}$ &     $16^{+26}_{-10}$ &  This Study \\
-  HIP 24244 &   $13781 \pm 469$ &  $4.2 \pm 0.14$ &  $3.9^{+0.29}_{-0.23}$ &    $114^{+11}_{-23}$ &      DH2015 \\
   HIP 24902 &    $8275 \pm 281$ &  $4.0 \pm 0.14$ &  $1.7^{+0.10}_{-0.08}$ &  $466^{+252}_{-286}$ &      DH2015 \\
@@
   HIP 42129 &  $18000 \pm 1000$ &  $4.5 \pm 0.25$ &  $5.4^{+0.63}_{-0.54}$ &      $11^{+14}_{-5}$ &  This Study \\
-  HIP 51362 &   $10899 \pm 371$ &  $4.0 \pm 0.14$ &  $2.6^{+0.14}_{-0.12}$ &   $182^{+79}_{-102}$ &      DH2015 \\
   HIP 52678 &  $15000 \pm 1000$ &  $4.5 \pm 0.25$ &  $4.0^{+0.49}_{-0.50}$ &     $16^{+26}_{-10}$ &  This Study \\
@@
   HIP 78820 &  $24062 \pm 1000$ &  $3.9 \pm 0.25$ &  $9.2^{+0.51}_{-0.64}$ &        $9^{+6}_{-4}$ &  This Study \\
-  HIP 78821 &    $7250 \pm 300$ &  $4.0 \pm 0.25$ &  $9.1^{+0.65}_{-0.96}$ &        $8^{+6}_{-3}$ &  This Study \\
   HIP 79199 &  $12500 \pm 1000$ &  $4.5 \pm 0.25$ &  $3.0^{+0.42}_{-0.39}$ &     $23^{+55}_{-16}$ &  This Study \\
@@
   HIP 84606 &    $9702 \pm 330$ &  $4.0 \pm 0.14$ &  $2.1^{+0.10}_{-0.09}$ &   $154^{+137}_{-99}$ &      DH2015 \\
-  HIP 85379 &    $8250 \pm 300$ &  $3.5 \pm 0.25$ &  $2.1^{+0.37}_{-0.34}$ &  $550^{+154}_{-260}$ &  This Study \\
+%  HIP 85379 &    $8250 \pm 300$ &  $3.5 \pm 0.25$ &  $2.1^{+0.37}_{-0.34}$ &  $550^{+154}_{-260}$ &  This Study \\
   HIP 85998 &    $8812 \pm 300$ &  $4.0 \pm 0.25$ &  $1.9^{+0.16}_{-0.13}$ &    $95^{+332}_{-84}$ &  This Study \\
   HIP 88116 &    $9750 \pm 300$ &  $3.5 \pm 0.25$ &  $2.7^{+0.43}_{-0.39}$ &   $305^{+68}_{-150}$ &  This Study \\
+  HIP 88817 &    $9162 \pm 312$ &  $4.3 \pm 0.14$ &  $2.1^{+0.16}_{-0.12}$ &   $480^{+84}_{-168}$ &      DH2015 \\
   HIP 88818 &    $9162 \pm 312$ &  $4.3 \pm 0.14$ &  $2.7^{+0.24}_{-0.23}$ &    $441^{+86}_{-72}$ &      DH2015 \\
-  HIP 88817 &    $9162 \pm 312$ &  $4.3 \pm 0.14$ &  $2.1^{+0.16}_{-0.12}$ &   $480^{+84}_{-168}$ &      DH2015 \\
   HIP 91118 &    $9500 \pm 300$ &  $4.0 \pm 0.25$ &  $2.1^{+0.19}_{-0.15}$ &    $70^{+244}_{-60}$ &  This Study \\
   HIP 93805 &   $11962 \pm 407$ &  $4.2 \pm 0.14$ &  $3.5^{+0.32}_{-0.26}$ &    $194^{+19}_{-21}$ &      DH2015 \\
+  HIP 96840 &  $17000 \pm 1000$ &  $4.5 \pm 0.25$ &  $4.9^{+0.57}_{-0.53}$ &    $12^{+17}_{-6}$ &  This Study \\
  HIP 100221 &    $9750 \pm 300$ &  $4.5 \pm 0.25$ &  $2.2^{+0.15}_{-0.15}$ &    $34^{+110}_{-26}$ &  This Study \\
@@
  HIP 109521 &    $8420 \pm 286$ &  $4.2 \pm 0.14$ &  $2.0^{+0.19}_{-0.16}$ &  $728^{+109}_{-104}$ &      DH2015 \\
- HIP 115115 &   $10671 \pm 363$ &  $4.2 \pm 0.14$ &  $2.6^{+0.19}_{-0.16}$ &    $284^{+38}_{-81}$ &      DH2015 \\
+ HIP 115115 &   $10671 \pm 363$ &  $4.2 \pm 0.14$ &  $2.6^{+0.19}_{-0.16}$ &    $284^{+38}_{-81}$ &      DH2015
 \label{tab:primary}
-\end{longtable*}
+\end{deluxetable*}
 

### 2016-02-02 paper/ms.tex
Updated abstract.

@@
 Binary stars and higher-order multiple systems are a ubiquitous outcome of star formation, especially as the system mass increases.
-The mass-ratio distribution is a unique probe into the physics of the collapsing molecular core as well as the circumstellar disk of the binary fragments.
-The mass-ratio distribution should change as the companion gets with $a \sim 1000$ AU, at which point the disks from the two forming stars can interact, and companions can form directly from the disk of the primary star.
+The distribution of mass ratios is a unique probe into the conditions of the collapsing molecular core as well as the circumstellar disks of the binary fragments.
+Inside $a \sim 1000$ AU the disks from the two forming stars can interact, and additionally companions can form directly from the primary star disk.
+We should therefore expect the mass-ratio distribution of close companions to differ from that of wide companions.
 Unfortunately, close companions to A- and B-type stars are very difficult to detect and characterize because they are so much dimmer than the primary star.
@@
 \label{sec:intro}
-%There has recently been a revival of interest in the multiplicity properties of intermediate-mass stars,  spurred largely by the detection of planets orbiting nearby \mbox{$\sim2 M_{\odot}$} stars on both wide \citep[e.g.][]{Lagrange2010, Marois2008} and close \citep{Johnson2011} orbits.
-In this context, binary companions are contaminants; companions complicate radial velocity planet searches because they necessitate simultaneous modeling of both stellar motions \citep[e.g.][]{Bergmann2015}.
-Likewise, companions complicate direct imaging planet searches by requiring either extremely high-contrast instrumentation \citep{Thalmann2014} or specialized coronagraphs \citep{Crepp2010}.
-
-%However, known binary stars are typically avoided in planet search programs for a more fundamental reason: the binary companion depletes or destroys the planet-forming disk.
-By combining a binary census of the $\sim 2$ Myr Taurus-Auriga star-forming region with a disk census of the same, \cite{Kraus2012} showed that close ($\lesssim 40$ AU) binaries are about 2-3 times less likely to host a protoplanetary disk, and so hasten disk dispersal.
-Even if a disk survives, it tends to be depleted in mass by a factor of $\sim 25$ for binary separations $\lesssim 30$ AU \citep{Harris2012}.
-%[CITE KRAUS PAPER] performed a search for binary companions among Kepler planet host stars, and found that the presence of a companion within 5-50AU suppresses planet formation by a factor of $\sim 4$.
 

### 2016-02-02 paper/ms.tex
Updated into section.

@@
 Unfortunately, close companions to A- and B-type stars are very difficult to detect and characterize because they are so much dimmer than the primary star.
-We present the results of a survey searching for companions to A- and B-type stars using the direct spectroscopic detection technique, which is sensitive to late-type companions within $\sim 1''$ of the primary.
+We present the results of a survey searching for companions to A- and B-type stars using the direct spectral detection technique, which is sensitive to late-type companions within $\sim 1''$ of the primary.
 We estimate the temperatures and masses of the 58 companion detections, 25 of which are new detections.
@@
 
-Stellar multiplicity is an inevitable and common outcome of star formation, with roughly half of all solar-type field stars in binary or multiple systems \citep{Raghavan2010} and an even higher fraction as the stellar mass increases.
+Stellar multiplicity is an inevitable and common outcome of star formation, with roughly half of all solar-type field stars in binary or multiple systems \citep{Raghavan2010} and an even higher fraction as the stellar mass increases \citep{Zinnecker2007}.
 Young stellar associations and clusters tend to have even higher multiplicity \citep{Duchene2013}, indicating that stars often form in multiple systems that are subsequently destroyed by dynamical interactions as the cluster dissociates.
@@
 The overall multiplicity rate and the distributions of mass ratio, period, and eccentricity of a binary star population place important constraints on the mode of binary star formation.
+While the period and eccentricity are altered by dynamical processing in the birth cluster, the present-day mass ratio of a binary system is a tracer of its formation \citep{Parker2013}.
 Most binary stars are thought to form via core fragmentation \citep{Boss1979, Boss1986, Bate1995}, in which a collapsing core fragments into two or more individual protostars.
 The number and initial masses of the fragments are set by the total core mass, as well as its rotation, turbulence, and its temperature and density structure.
-If the fragments are separated by $\gtrsim 1000$ AU, they will evolve relatively independently of each other, accreting mass from the core material onto their own protostellar disks and then onto the protostars themselves.
-However close fragments ($a \sim 100$ AU) will interact with each other; the protostellar disk may be truncated, destabilized, or even merge into a circumbinary disk if the separation is small enough.
+If the fragments are well separated ($a \gtrsim 1000$ AU), they will evolve relatively independently of each other, accreting mass from the core material onto their own protostellar disks and then onto the protostars themselves.
+However close fragments ($a \sim 100$ AU) will interact with each other; the protostellar disk may be truncated, destabilized, or form into a circumbinary disk if the separation is small enough \citep{Bate1997}.
 In addition, unstable disk can fragment to form low-mass companions \citep{Kratter2006, Stamatellos2011}.
@@
 Most work has suggested that the disk material will preferentially accrete onto the lower mass companion \citep{Bate1997, BBB2002}; however, recent work has indicated that magnetic disk braking may result in preferential accretion onto the more massive component \citep{Zhao2013} instead.
-In either case, we would expect to find a different mass ratio distribution for companions inside a few $100$ AU and companions on wider orbits.
+In either case, we would expect to find a mass ratio distribution for companions inside a few $100$ AU that differs from that of companions on wider orbits.
 
@@
 Worse, radial velocity monitoring can only measure a mass ratio if spectral lines from both components are visible; this typically suffers from the same flux ratio difficulty as imaging techniques.
+
 Nonetheless, \citet{DeRosa2014} performed an adaptive optics imaging survey of nearby A-type stars and found initial evidence that the mass ratio distribution for companions inside $125$ AU is much flatter than that of wide companions.
 Unfortunately they had only very few detections at these near separations, and the result is complicated by the inherent difficulty of detecting close companions with low mass ratios in an imaging survey.
-
-In this paper, we describe a spectroscopic survey of nearby intermediate-mass stars.
+Additionally, spectroscopic companions to chemically peculiar Am stars appear to have a mass ratio distribution which peaks near $q \sim 0.5$ \citep{Vuissoz2004}.
+Am stars are typically associated with binary companions, and are slow rotators due to tidal braking; they thus form a highly biased sample of intermediate-mass stars.
+
+In this paper, we describe a spectroscopic survey of nearby normal, main sequence intermediate-mass stars.
 We search for companions using the direct spectral detection technique \citep{Gullikson2016}, which has a separation-invariant detection rate for all separations inside $\sim 1 ''$.
 We describe the stellar sample and data used for the survey in Section \ref{sec:obs}, as well as the data reduction steps in the same section.
-Next, we describe the direct spectroscopic detection and tabulate the companion detections in Section \ref{sec:companions}.
+Next, we describe the direct spectral detection method and tabulate the companion detections in Section \ref{sec:companions}.
 We estimate the mass and age of the primary stars in Section \ref{sec:sp}, and discuss the survey completeness in Section \ref{sec:completeness}.
 Finally, we end with a derivation of the mass ratio distribution from our sample in Section \ref{sec:mrd} and discuss its implications for binary formation in Section \ref{sec:discussion}.
-
-TODO: mass-ratio is the most dynamically stable orbital feature. Where did I see this?
-
-TODO: \citep{Carrier2002} and \citep{Vuissoz2004} look at Am/Ap stars and find a mass-ratio distribution with a broad peak near $q \sim 0.5$.
-This is coming mostly from SB1s, and assuming uniform inclinations to go from the mass function to the companion mass, and make simple assumptions about the primary mass.
-Still, it is interesting that my result is pretty similar for normal A-stars.
 
@@
 
-We search for stellar companions to our sample stars using the direct spectroscopic detection technique, described in detail in \citet{Gullikson2016}.
+We search for stellar companions to our sample stars using the direct spectral detection technique, described in detail in \citet{Gullikson2016}.
 In short, we high-pass filter each of our spectra to remove the broad lines from the primary star, and cross-correlate each \'echelle order or each filtered spectrum against a large grid of Phoenix model spectra \citep{Husser2013_b} with the following parameters:

### 2016-02-02 paper/ms.tex
Updated observation section.

@@
 
-The first two criteria are to ensure that the direct spectral detection technique (Section \ref{sec:companions}) both works and is well-calibrated.
 The magnitude limit ensures that a sufficiently high signal-to-noise ratio can be achieved in a short period of time.
@@
 
-For the TS23, we use a $1.2''$ slit in combination with the E2 \'echelle grating (53 grooves/mm, blaze angle $65^{\circ}$), yielding a resolving power of $R=60000$ and a wavelength coverage from 375-1020 nm.
+For the TS23 spectrograph, we use a $1.2''$ slit in combination with the E2 \'echelle grating (53 grooves/mm, blaze angle $65^{\circ}$), yielding a resolving power of $R=60000$ and a wavelength coverage from 375-1020 nm.
 We reduce the data using an IRAF pipeline very similar to the ones we use for CHIRON and HRS, and wavelength calibrate using a Th-Ar lamp observed immediately before the science observations.
@@
 IGRINS only has one setting with $R = 40000$.
-It has complete wavelength coverage from 1475-2480 nm, except for where telluric absorption is almost $100\%$ from 1810 - 1930 nm.
+It has complete wavelength coverage from $1475-2480$ nm, except in the telluric water band from $1810 - 1930$ nm.
 Each star is observed in an ABBA nodding mode, and reduced using the standard IGRINS pipeline \citep{IGRINS_plp_v2}.
-The standard pipeline uses atmospheric OH emission lines as well as a Th-Ar calibration frame to calibrate the wavelengths; we further refine the wavelength solution using telluric absorption lines.
+The standard pipeline uses atmospheric OH emission lines as well as a Th-Ar calibration frame to calibrate the wavelengths; we further refine the wavelength solution using telluric absorption lines in the science spectrum.
 
@@
 The telluric correction is critical for IGRINS spectra, where every order is dominated by telluric absorption lines.
-For the optical spectra, it is less critical but allows us to use some of the redder orders than we otherwise would not be able to.
+For the optical spectra, it is less critical but allows us to use some of the redder orders than we otherwise would be able to.
 For unsaturated lines, the best-fit telluric model reproduces the data to within $\sim 1-5\%$ of the continuum level.

### 2016-02-02 paper/ms.tex
Updated compaion search section.

@@
 We search for stellar companions to our sample stars using the direct spectral detection technique, described in detail in \citet{Gullikson2016}.
-In short, we high-pass filter each of our spectra to remove the broad lines from the primary star, and cross-correlate each \'echelle order or each filtered spectrum against a large grid of Phoenix model spectra \citep{Husser2013_b} with the following parameters:
+In short, we high-pass filter each of our spectra to remove the broad lines from the primary star, and cross-correlate each \'echelle order of each filtered spectrum against a large grid of Phoenix model spectra \citep{Husser2013_b} with the following parameters:
 
@@
 While the maximum-likelihood scheme produces detections with much higher significance, it also magnifies spurious peaks and so has a larger false-positive rate.
-For this reason, we use the simple average CCFs in all further analysis unless otherwise specified.
+For this reason, we use the simple average CCFs in all further analysis.
 

### 2016-02-02 paper/ms.tex
Updated primary parameters section.

@@
 In order to convert from companion temperature to mass ratio, we first need an estimate of the primary mass.
-In addition, since the primary stars in our systems are A- or B-type stars with main-sequence lifetimes from $\sim 10 - 1000$ Myr, very late-type companions may still be contracting onto the main sequence and so an age estimate for the system is necessary.
+In addition, since the primary stars in our survey have short main-sequence lifetimes, some companions may still be contracting onto the main sequence and so an age estimate for the system is necessary to convert from companion temperature to mass.
 
 About half of our detections have robust mass and age estimates for the primary stars from Str\"omgren uvby$\beta$ photometry \citep{David2015}.
-For those that do not, we estimate the mass and age of the system as follows.
+For those that do not, we estimate the mass and age of the system from our spectra.
 We first cross-correlate the data against a grid of Kurucz model spectra \citep{Castelli2003} spanning
@@
 \item $7000\ K < T_\mathrm{eff} < 30000\ K$ in steps of $1000\ K$
-\item $3.0 < \log{g} < 4.5$ in steps of $0.25$ dex
+\item $3.0 < \log{g} < 4.5$ in steps of $0.5$ dex
 \item $75 < v\sin{i} < 300\ \mathrm{km s}^{-1}$ in steps of $25\ \mathrm{km s}^{-1}$
@@
 We show the comparison in Figure \ref{fig:prim_mass}.
-We estimate uncertainties in the spectral type mass by assuming a spectral type uncertainty of $\pm 0.5$ spectral types.
+We estimate uncertainties in the spectral type mass by assuming a spectral type uncertainty of $\pm 0.5$ spectral types and propagating to mass.
 There is excellent agreement between the masses we measure and the spectral type masses.

### 2016-02-02 paper/ms.tex
Updated survey completeness section.

@@
 To quantify the detection rate as a function of companion temperature and $v\sin{i}$, we performed a series of injection/recovery experiments.
-We started by creating synthetic binary star observations from each of our spectra.
+We started by creating synthetic binary star observations from each of our observed spectra.
 We made two distinct grids of companion stars: a low temperature grid spanning
@@
 We counted the companion as detected if the highest point in the resulting CCF was found at the correct radial velocity.
-We then combined all of the radial velocity points for each grid point to estimate a probability of detection at that grid point:
+We then combined all of the radial velocity trials for each grid point to estimate a probability of detection at that grid point:
 
@@
 
-Finally, we interpolated between the grid points using a linear radial basis function interpolator.
-In order to extrapolate from our grids to estimate the detection rate at high temperature and low $v\sin{i}$ and at low temperature and high $v\sin{i}$, we made the following assumptions about the shape of the two-dimensional detection rate surface: First, we assumed that if all companions are detected at temperature $T=6500$ K and rotation speed $v\sin{i}$, then all companions with the same $v\sin{i}$ and larger temperature will also be detected.
-Likewise, we assume that if no companions are detected at temperature $T$ and rotation speed $v\sin{i} = 50\ \mathrm{km\ s}^{-1}$, we assume that no companions will be detected at the same temperature and faster rotation speeds.
-We show a typical detection rate surface in Figure \ref{fig:detrate_2d} to illustrate both the shape of the surface and the grid we interpolate from.
-The figure shows a clear diagonal dividing line between hot, slow rotators that are always detected and cool, fast rotators that never are.
+Finally, we interpolated between the grid points using a linear radial basis function interpolator (Figure \ref{fig:detrate_2d}).
+In order to extrapolate from our grids to estimate the detection rate at high temperature and low $v\sin{i}$ and at low temperature and high $v\sin{i}$, we made the following assumptions about the shape of the two-dimensional detection rate surface: First, we assumed that if all companions are detected at temperature $T=6500$ K and rotation speed $v\sin{i}$, then all companions with the same $v\sin{i}$ and larger temperature will also be detected (lower right points in Figure \ref{fig:detrate_2d}).
+Likewise, we assume that if no companions are detected at temperature $T$ and rotation speed $v\sin{i} = 50\ \mathrm{km\ s}^{-1}$, then no companions will be detected at the same temperature and faster rotation speeds (upper left points in Figure \ref{fig:detrate_2d}).
+Figure \ref{fig:detrate_2d} shows a clear diagonal dividing line between hot, slow rotators that are always detected and cool, fast rotators that never are.
 Additionally the figure shows that very fast rotators are never detected, regardless of their temperature, because the signal is completely removed when we high-pass filter the data (see Section \ref{sec:companions}).
@@
 \subsection{Marginalization}
-To estimate the survey completeness as a function of mass ratio, we first need to remove the dependence on $v\sin{i}$.
-We do this by sampling a suitable distribution of $v\sin{i}$ values for a star of each temperature and marginalizing over the completeness:
+By sampling a suitable distribution of $v\sin{i}$ values for a star of each temperature, we marginalize over the rotation speed:
 
@@
 \citet{Zorec2012} fit maxwellian distributions to the equatorial velocity of A- and B-type stars in several mass bins.
-For $T > 7000\ K$, we interpolate the fit parameters, and sample the maxwellian probability density function.
-
-Typical velocities from the gyrochronology relationships are $10-20 \mathrm{km s}^{-1}$, while the maxwellian velocity distributions have typical velocities $\sim 100 \mathrm{km s}^{-1}$.
+For $T > 7000\ K$, we linearly interpolate the fit parameters as a function of mass and sample the resulting maxwellian probability density function.
+
+Typical velocities from the gyrochronology relationships are $10-20 \mathrm{km\ s}^{-1}$, while the maxwellian velocity distributions have typical velocities $\sim 100 \mathrm{km\ s}^{-1}$.
 We transition between the two regimes for temperatures in the range $6000\ K < T < 7000\ K$ by first estimating the equatorial velocities from the gyrochronology relationship (Equation \ref{eqn:gyro}) at $T=6000\ K$.
@@
 We show the marginalized detection rate and mean value of $v\sin{i}$ as a function of temperature in Figure \ref{fig:marginalized}.
-Both the detection rate and the average $v\sin{i}$ are smoothly varying, and show the correct behaviour with temperature.
+Both the detection rate and the average $v\sin{i}$ are smoothly varying, and show the expected behaviour with temperature.
 The detection rate falls with hotter temperatures because the companions are expected to be fast rotators, which are more difficult to detect.
+ADAM AND SALLY: IS THIS FIGURE NECESSARY OR IS THE TEXT ENOUGH?
 
@@
 
-The result of the previous analysis is a series of estimates for the detection rate as a function of companion temperature for each star.
-We convert each companion temperature to a mass by interpolating Table 5 of \citet{Pecaut2013}.
+The result of the previous analysis is a series of estimates for the detection rate as a function of companion temperature for each observation of each star.
+We convert companion temperature to mass by interpolating Table 5 of \citet{Pecaut2013}.
 Next, we estimate the primary mass for each star as the median of the mass samples developed in Section \ref{sec:sp}.
 We then convert each detection rate curve to be a function of mass ratio ($Q_j(q)$, where $j$ denotes the $j$th star in the sample), and linearly interpolate onto a grid in mass ratio from $0 < q_i < 1$.
-Finally, we combine the detection rate curves for each star into an estimate of the survey-wide completeness by taking the average of the detection rate for all stars:
+Finally, we combine the detection rate curves for each star \emph{with no companion detection in our data} into an estimate of the survey-wide completeness by taking the average of the detection rate for all stars:
 
@@
 \end{equation}
-In the equation above, $N_i$ is the number of sample stars that contain an estimate for $Q(q_i)$.
+In the equation above, $N_i$ is the number of sample stars that contain an estimate for $Q(q_i)$ without extrapolating.
 For $q_i \sim 0.2$, $N_i$ is near the total sample size.
@@
 Both methods give similar results in most cases, although the isochrone masses are significantly higher for very young systems.
-We therefore only show the results obtained with the isochrone masses.
+We only use the results obtained with the isochrone masses in the analysis.
 We sample the mass ratio of the system by dividing the companion mass samples by samples of the primary mass (Section \ref{sec:sp}).

### 2016-02-02 paper/ms.tex
Finished making text edits.

@@
 
-We do not use systems with more than one companion, unless known the wider companion separated by $ > 10''$ from the primary star (TODO: Check that this limit is true...).
-We mark the 47 companions we use in the mass ratio analysis with the fourth column of Table \ref{tab:companions}.
-Many of the companions we use in the analysis only have one detection in our data; 12/22 of these are previously known companions.
+We do not use systems with more than one companion, unless the wider companion is separated by $ > 10''$ from the primary star.
+We mark the 48 companions we use in the mass ratio analysis with the fourth column of Table \ref{tab:companions}.
+Many of the companions we use in the analysis only have one detection in our data; 12/22 of these are previously known companions and so don't need follow-up to confirm.
 The remaining 10 are new and unconfirmed detections; these all have very strong CCF signals and are likely to be confirmed with follow-up spectroscopy or imaging.
@@
 
-In the above equation, $\{\vec{x_k}\}$ denote all of the data for each star, and $\vec{\theta}$ denotes the parameters for the model we are fitting.
+In the above equation, $\{\vec{x_k}\}$ denotes the full spectrum of star $k$, and $\vec{\theta}$ denotes the parameters for the model we are fitting.
 $K=360$ is the total sample size for our survey, $Q(q)$ is the completeness function shown in Figure \ref{fig:completeness}, and $P(q|\vec{\theta})$ is the likelihood function for the mass ratio given the model parameters.
@@
 The smoothing prior is an 7-dimensional gaussian with mean $m$ and covariance matrix $K_{ij}$, and encodes our belief that the mass ratio distribution is a smoothly varying function while leaving enough flexibility to let the data drive the shape of the function.
-Since we have introduced three new hyperparameters ($a, m, \tau, \epsilon$), we must apply a prior to them and marginalize over them when estimating the true bin heights.
+Since we have introduced three new hyperparameters ($a, m, \tau, \epsilon$), we must apply a prior to them and marginalize over them when estimating the bin heights.
 We choose log-uniform priors for $a, \tau$, and $\epsilon$, and a uniform prior for the mean $m$.
@@
  HIP 109139 & AB &     2 & yes &  $5710 \pm 112$ &      20 &    -0.5  &  $1.0^{+0.04}_{-0.03}$ &  $1.0^{+0.03}_{-0.03}$ \\
- HIP 109521 & Aa,Ab$^{\dagger}$ &     3 & no &   $4412 \pm 87$ &      10 &     0.0  &  $0.7^{+0.02}_{-0.02}$ &  $0.7^{+0.01}_{-0.01}$ \\
+ HIP 109521 & Aa,Ab$^{\dagger}$ &     3 & yes &   $4412 \pm 87$ &      10 &     0.0  &  $0.7^{+0.02}_{-0.02}$ &  $0.7^{+0.01}_{-0.01}$ \\
  HIP 115115 & AB &     3 & yes &   $4943 \pm 91$ &       5 &    -0.5  &  $0.8^{+0.02}_{-0.02}$ &  $0.8^{+0.02}_{-0.02}$

### 2016-02-02 paper/ms.tex
Fixed MRD figure caption.

@@
 \caption{Mass ratio distribution for our sample.
-The data was fit to both a histogram and a log-normal distribution.
+The data was fit to both a histogram and a gaussian distribution.
 The histogram is shown in the solid blue blocks, with $1 \sigma$ uncertainties marked with error bars.
-The variance of the log-normal fit is shown with 500 samples from the posterior probability distribution for the parameters.}
+The variance of the gaussian fit is shown with 500 samples from the posterior probability distribution for the parameters.}
 \label{fig:mrd}

### 2016-02-05 paper/ms.tex
Removed some stars with detections I do not believe.
Added CCF figure for demonstration purposes.

@@
 The $v\sin{i}$ and metallicity values do not have uncertainties and should only be taken as a rough estimate of the true value.
-
-TODO: Make plots for all of the CCFs.
+We show the detection CCFs and a plot of peak CCF height as a function of model temperature in Figure \ref{fig:ccf}.
+Similar figures for all companions are available in the supplementary files.
+
+\begin{figure}
+\includegraphics[width=\pagewidth]{HIP_109139.pdf}
+\caption{\emph{Left}: Cross-correlation function between the observed spectra of HIP 109139 and a $5700\ K$ Phoenix model spectra.
+The detection at two dates shows significant velocity variation, indicating orbital motion with a short period.
+\emph{Right}: Peak CCF height as a function of Phoenix model spectra template temperature.
+The maxima of the curves indicate the temperature of the companion.}
+\label{fig:ccf}
+\end{figure}
 
 Most of the detected companions have follow-up spectra to confirm the existence of the companion.
-[MENTION THAT YOU CAN SEE THEM ALL IN THE FIGURES].
 In most cases, there is a clear shift in the radial velocity of the companion, indicating that it is orbiting the target star and is not a foreground or background companion.
 In addition we obtained Gemini/NIRI adaptive optics imaging data for 19 of the northern companions, and were able to resolve 7 of them.
+We show the separation, position angle, and magnitude difference in Table \ref{tab:imaging_obs}.
 
@@
 Many of the companions we use in the analysis only have one detection in our data; 12/22 of these are previously known companions and so don't need follow-up to confirm.
-The remaining 10 are new and unconfirmed detections; these all have very strong CCF signals and are likely to be confirmed with follow-up spectroscopy or imaging.
+An The remaining 10 are new and unconfirmed detections; these all have very strong CCF signals and are likely to be confirmed with follow-up spectroscopy or imaging.
 We do not expect their inclusion to significantly alter the results.
 TODO: test this statement...
+
+Where did HIP 118243 go? It has an imaging detection (though at very wide separation), but nothing in the Companion table.
 
@@
     HIP 5310 &            A3V &    01:07:57.16 &   +20:44:20.83 &  6945.75 &     IGRINS &      224 &   200 \\
-    HIP 5348 &        B6V+B9V &    01:08:23.08 &   -55:14:44.73 &  6325.56 &     CHIRON &      186 &   390 \\
     HIP 5361 &            B8V &    01:08:33.47 &   +58:15:48.41 &  6523.84 &        HRS &     1000 &   810 \\
@@
   HIP 10732 & AB$^{\dagger}$ &     2 & yes &  $5578 \pm 109$ &       5 &     0.0  &  $1.0^{+0.29}_{-0.04}$ &  $1.0^{+0.02}_{-0.04}$ \\
-  HIP 12332 & AB$^{\dagger}$ &     2 & yes &  $5551 \pm 107$ &      10 &     0.0  &    $1.0^{+0.03}_{--0.03}$ &  $1.0^{+0.01}_{-0.04}$ \\
+  HIP 12332 & AB$^{\dagger}$ &     2 & yes &  $5551 \pm 107$ &      10 &     0.0  &    $1.0^{+0.03}_{-0.03}$ &  $1.0^{+0.01}_{-0.04}$ \\
   HIP 12706 & AB &     2 & yes &  $6051 \pm 107$ &      10 &     0.0  &  $1.1^{+0.03}_{-0.03}$ &  $1.1^{+0.04}_{-0.05}$ \\
@@
   HIP 14576 & Aa,Ab &     2 & no &  $6980 \pm 103$ &      10 &     0.0  &  $1.4^{+0.03}_{-0.03}$ &  $1.5^{+0.05}_{-0.03}$ \\
-  HIP 14764 & AB$^{\dagger}$ &     2 & yes &  $5601 \pm 108$ &      30 &     0.5 0 &    $1.0^{+0.34}_{-0.05}$ &  $1.0^{+0.03}_{-0.03}$ \\
+  HIP 14764 & AB$^{\dagger}$ &     2 & yes &  $5623 \pm 150$ &      5 &     -0.5 &    $1.0^{+0.32}_{-0.07}$ &  $1.0^{+0.03}_{-0.04}$ \\
   HIP 16244 & AB &     2 & yes &  $5592 \pm 107$ &       5 &    -0.5  &  $1.2^{+0.20}_{-0.22}$ &  $1.0^{+0.03}_{-0.03}$ \\
   HIP 16340 & AB$^{\dagger}$ &     1 & yes &  $6214 \pm 150$ &       5 &    -0.5  &  $1.2^{+0.29}_{-0.07}$ &  $1.2^{+0.06}_{-0.05}$ \\
-  HIP 16611 & AB &     1 & no &  $5476 \pm 154$ &       1 &     0.5  &  $0.9^{+0.04}_{-0.04}$ &  $0.9^{+0.04}_{-0.03}$ \\
-  HIP 17563 & AB &     1 & yes &  $8574 \pm 147$ &       5 &     0.5  &  $1.9^{+0.25}_{-0.11}$ &  $2.0^{+0.05}_{-0.06}$ \\
   HIP 18724 & AB &     1 & no &  $6831 \pm 154$ &      20 &     0.0  &  $1.7^{+0.13}_{-0.23}$ &  $1.4^{+0.04}_{-0.04}$ \\
@@
   HIP 22833 & AB &     2 & yes &  $4745 \pm 107$ &      10 &     0.0  &  $0.8^{+0.02}_{-0.02}$ &  $0.8^{+0.02}_{-0.01}$ \\
-  HIP 22958 & Aa,Ab &     2 & yes &  $6126 \pm 112$ &      30 &    -0.5  &  $1.4^{+0.22}_{-0.21}$ &  $1.2^{+0.04}_{-0.04}$ \\
+  HIP 22958 & Aa,Ab &     2 & yes &  $5762 \pm 158$ &      30 &    -0.5  &  $1.3^{+0.19}_{-0.23}$ &  $1.0^{+0.09}_{-0.03}$ \\
   HIP 23362 & AB$^{\dagger}$ &     1 & yes &  $6283 \pm 158$ &       5 &    -0.5  &  $1.2^{+0.06}_{-0.05}$ &  $1.2^{+0.07}_{-0.05}$ \\
@@
   HIP 24902 & AB &     1 & yes &  $5679 \pm 154$ &      30 &     0.0  &  $1.0^{+0.05}_{-0.04}$ &  $1.0^{+0.04}_{-0.03}$ \\
-  HIP 25143 & AB$^{\dagger}$ &     2 & yes &  $5883 \pm 109$ &      30 &     0.0  &  $1.1^{+0.04}_{-0.03}$ &  $1.1^{+0.05}_{-0.07}$ \\
   HIP 26126 & AB? &     3 & yes &   $5841 \pm 91$ &       5 &    -0.5  &  $1.0^{+0.03}_{-0.03}$ &  $1.0^{+0.05}_{-0.04}$ \\
@@
   HIP 16340 &  $12500 \pm 1000$ &  $4.0 \pm 0.25$ &  $3.1^{+0.51}_{-0.42}$ &     $49^{+92}_{-39}$ &  This Study \\
-  HIP 16611 &   $12514 \pm 425$ &  $4.0 \pm 0.14$ &  $3.3^{+0.25}_{-0.20}$ &    $157^{+23}_{-46}$ &      DH2015 \\
-  HIP 17563 &  $19000 \pm 1000$ &  $4.5 \pm 0.25$ &  $6.0^{+0.66}_{-0.59}$ &      $10^{+11}_{-4}$ &  This Study \\
   HIP 18724 &  $21000 \pm 1000$ &  $4.5 \pm 0.25$ &  $7.1^{+0.68}_{-0.64}$ &        $8^{+7}_{-3}$ &  This Study \\
@@
   HIP 24902 &    $8275 \pm 281$ &  $4.0 \pm 0.14$ &  $1.7^{+0.10}_{-0.08}$ &  $466^{+252}_{-286}$ &      DH2015 \\
-  HIP 25143 &    $8101 \pm 275$ &  $3.8 \pm 0.14$ &  $1.7^{+0.06}_{-0.06}$ &  $236^{+247}_{-160}$ &      DH2015 \\
   HIP 26126 &    $9542 \pm 324$ &  $3.9 \pm 0.14$ &  $2.1^{+0.09}_{-0.08}$ &  $175^{+148}_{-112}$ &      DH2015 \\

### 2016-02-10 paper/ms.tex
Fixed typo in new figure.
Moved figure around a bit.
Tweaked ccf figure and added imaging data figure.

@@
 
+\begin{figure*}
+\includegraphics[width=\textwidth]{HIP_109139.pdf}
+\caption{\emph{Left}: Cross-correlation function between the observed spectra of HIP 109139 and a $5700\ K$ Phoenix model spectra.
+The detection at two dates shows significant velocity variation, indicating orbital motion with a short period.
+\emph{Right}: Peak CCF height as a function of Phoenix model spectra template temperature.
+The maxima of the curves indicate the temperature of the companion.}
+\label{fig:ccf}
+\end{figure*}
+
 We search for stellar companions to our sample stars using the direct spectral detection technique, described in detail in \citet{Gullikson2016}.
@@
 The $v\sin{i}$ and metallicity values do not have uncertainties and should only be taken as a rough estimate of the true value.
-We show the detection CCFs and a plot of peak CCF height as a function of model temperature in Figure \ref{fig:ccf}.
+We show the detection CCFs and a plot of peak CCF height as a function of model temperature for HIP 109139 in Figure \ref{fig:ccf}.
 Similar figures for all companions are available in the supplementary files.
 
+Most of the detected companions have follow-up spectra to confirm the existence of the companion.
+In most cases, there is a clear shift in the radial velocity of the companion, indicating that it is orbiting the target star and is not a foreground or background companion (See Figure \ref{fig:ccf}).
+In addition we obtained Gemini/NIRI adaptive optics imaging data for 19 of the northern companions, and were able to resolve 7 of them.
+We show the separation, position angle, and magnitude difference in Table \ref{tab:imaging_obs}, and display the images in Figure \ref{fig:images}.
+
 \begin{figure}
-\includegraphics[width=\pagewidth]{HIP_109139.pdf}
-\caption{\emph{Left}: Cross-correlation function between the observed spectra of HIP 109139 and a $5700\ K$ Phoenix model spectra.
-The detection at two dates shows significant velocity variation, indicating orbital motion with a short period.
-\emph{Right}: Peak CCF height as a function of Phoenix model spectra template temperature.
-The maxima of the curves indicate the temperature of the companion.}
-\label{fig:ccf}
+\includegraphics[width=\columnwidth]{Imaging_Data.pdf}
+\caption{Detection images for all stars in which we detect a companion in the follow-up NIRI data.}
+\label{fig:images}
 \end{figure}
-
-Most of the detected companions have follow-up spectra to confirm the existence of the companion.
-In most cases, there is a clear shift in the radial velocity of the companion, indicating that it is orbiting the target star and is not a foreground or background companion.
-In addition we obtained Gemini/NIRI adaptive optics imaging data for 19 of the northern companions, and were able to resolve 7 of them.
-We show the separation, position angle, and magnitude difference in Table \ref{tab:imaging_obs}.
 

### 2016-02-11 paper/ms.tex
Updated to address (most of) the concerns Sally had.

@@
 In addition, unstable disk can fragment to form low-mass companions \citep{Kratter2006, Stamatellos2011}.
-The mass ratios of close companions formed via either mechanism should be effected by preferential accretion.
+The mass ratios of close companions formed via either mechanism should be affected by preferential accretion.
 Most work has suggested that the disk material will preferentially accrete onto the lower mass companion \citep{Bate1997, BBB2002}; however, recent work has indicated that magnetic disk braking may result in preferential accretion onto the more massive component \citep{Zhao2013} instead.
@@
 
-Nonetheless, \citet{DeRosa2014} performed an adaptive optics imaging survey of nearby A-type stars and found initial evidence that the mass ratio distribution for companions inside $125$ AU is much flatter than that of wide companions.
+Nonetheless, \citet{DeRosa2014} performed an adaptive optics imaging survey of nearby A-type stars; they found initial evidence that the mass ratio distribution for companions inside $125$ AU has a much shallower power law slope than that of wide companions.
 Unfortunately they had only very few detections at these near separations, and the result is complicated by the inherent difficulty of detecting close companions with low mass ratios in an imaging survey.
@@
 Likewise, the $v\sin{i}$ limit makes accounting for the primary star spectrum in the companion search trivial; since most A- or B-type stars are rapid rotators, the cutoff does not remove very many stars from the sample.
-Finally we only include normal, main sequence stars in the sample because the binary flux ratio would be even less favorable to companion detection in an evolved star.
+We exclude pre-main sequence stars because both the primary and the companion mass would depend very strongly on young and uncertain ($\lesssim 1$ Myr) evolutionary models.
+Finally, we exclude post-main sequence stars from our sample because the binary flux ratio would be even less favorable to companion detection in an evolved star.
 Most of the spectral peculiarities denote narrow lines, which are already cut from the sample by the $v\sin{i}$ cut.
@@
 As part of the follow-up effort, we used the NIRI instrument behind the Altair adaptive optics system at the Gemini North Telescope.
-We obtained 25 images in 5 dithering positions in the K-continuum band centered on $2.2718\ \mu m$, with a variety of exposure times and dates listed in Table \ref{tab:imaging_obs}.
+For each star listed in Table \ref{tab:imaging_obs}, we obtained 25 images in 5 dithering positions.
+We used the K-continuum band centered on $2.2718\ \mu m$ and a variety of exposure times and dates (listed in Table \ref{tab:imaging_obs}).
 Because the targets are all extremely bright, we used the high read noise and high flux detector settings to allow for very short co-add exposure times.
@@
 We search for stellar companions to our sample stars using the direct spectral detection technique, described in detail in \citet{Gullikson2016}.
-In short, we high-pass filter each of our spectra to remove the broad lines from the primary star, and cross-correlate each \'echelle order of each filtered spectrum against a large grid of Phoenix model spectra \citep{Husser2013_b} with the following parameters:
+In short, we unsharp-mask each spectrum using a gaussian filter with width proportional to to primary star $v\sin{i}$ to remove the broad lines from the primary star.
+We then cross-correlate each \'echelle order of each filtered spectrum against a large grid of Phoenix model spectra \citep{Husser2013_b} with the following parameters:
 
@@
 
-\section{Stellar Parameters}
+\section{Primary Star Parameters}
 \label{sec:sp}
@@
 For those that do not, we estimate the mass and age of the system from our spectra.
-We first cross-correlate the data against a grid of Kurucz model spectra \citep{Castelli2003} spanning
+We first cross-correlate the data against a grid of model spectra spanning
 
@@
 \end{itemize}
+Since the Phoenix model library does not extend to temperatures $T > 12000\ K$, we used Kurucz model spectra \citep{Castelli2003} for this grid.
+
 For the optical data, we use the blue echelle orders ($\lambda < 5550 \AA$).
@@
 \begin{itemize}
-\item $7000\ K < T_\mathrm{eff} < 1200\ K$ in steps of $1000\ K$
+\item $7000\ K < T_\mathrm{eff} < 12000\ K$ in steps of $1000\ K$
 \item $100\ \mathrm{km\ s}^{-1} < v\sin{i} < 250\ \mathrm{km\ s}^{-1}$ in steps of $50\ \mathrm{km\ s}^{-1}$
@@
 We estimate the convective timescale ($\tau$) by interpolating Table 1 of \citet{Barnes2010a}.
-We then sample the system age $t$ (see Section \ref{sec:sp} and Table \ref{tab:primary}), and sample the initial rotation period $P_0$ as log-uniform from 0.2 to 10 days.
+We then randomly sample the system age $t$ from its probability distribution function (see Section \ref{sec:sp} and Table \ref{tab:primary}), and randomly sample the initial rotation period $P_0$ as log-uniform from 0.2 to 10 days [TODO: Find rotation periods for Ae/Be stars.
+Is this reasonable?].
 Equation \ref{eqn:gyro} then gives a current rotation period for each sample, which we convert to an equatorial velocity with the stellar radius $R$.
 We estimate the stellar radius by interpolating Dartmouth pre main sequence isochrones [CITE] using the companion temperature and system age.
+We finally convert to projected velocity $v\sin{i}$ by randomly sampling a uniform distribution for the inclination $\sin{i}$.
 

### 2016-02-11 paper/ms.tex
Justified P0 range.

@@
 We estimate the convective timescale ($\tau$) by interpolating Table 1 of \citet{Barnes2010a}.
-We then randomly sample the system age $t$ from its probability distribution function (see Section \ref{sec:sp} and Table \ref{tab:primary}), and randomly sample the initial rotation period $P_0$ as log-uniform from 0.2 to 10 days [TODO: Find rotation periods for Ae/Be stars.
-Is this reasonable?].
+We then randomly sample the system age $t$ from its probability distribution function (see Section \ref{sec:sp} and Table \ref{tab:primary}).
+Young stars have rotation periods in the range of 0.2 to 10 days \citep{Bouvier2014}, so we randomly choose an initial rotation period $P_0$ from a log-uniform distribution in this range for each age sample.
 Equation \ref{eqn:gyro} then gives a current rotation period for each sample, which we convert to an equatorial velocity with the stellar radius $R$.

### 2016-02-11 paper/ms.tex
Fixed MRD figure.
Added some model comparison to discussion section.

@@
      \end{cases} \label{eqn:P1} \\
- P_2(q|\vec{\theta}) &= \frac{A}{\sqrt{2\pi\sigma^2}} e^{-\frac{(q - \mu)^2}{2\sigma^2}} \label{eqn:P2}
+ P_2(q|\vec{\theta}) &= \frac{A}{\sqrt{2\pi\sigma^2}} e^{-\frac{(q - \mu)^2}{2\sigma^2}} \label{eqn:P2} \\
+ P_3(q|\vec{\theta}) &= (1-\gamma)q^{-\gamma} \label{eqn:P3}
 \end{align}
@@
 
-We fit both distributions via Importance Nested Sampling with the MultiNest code \citep{multinest}.
+We fit all distributions via Importance Nested Sampling with the MultiNest code \citep{multinest}.
 Following \citet{Foreman2014}, we apply a smoothing prior on the parameters $\vec{\theta}$ for the histogram model:
@@
 
+The power law fit has only one parameter ($\gamma$); we use a uniform prior in the fit.
+
 \subsection{Malmquist Bias Correction}
@@
 
-We already know $P(q|\vec{\theta})$ (Equations \ref{eqn:P1} and \ref{eqn:P2}). We estimate $P(\mathrm{obs}|q)$ by simulating a very large sample of binary stars:
+We already know $P(q|\vec{\theta})$ (Equations \ref{eqn:P1} - \ref{eqn:P3}). We estimate $P(\mathrm{obs}|q)$ by simulating a very large sample of binary stars:
 
@@
 The $1\sigma$ uncertainties in the bin heights from the histogram model are shown as error bars, and we overplot 500 samples of the gaussian fit to show the spread allowed by the data.
+The best-fit power law is plotted with a green dot-dashed line, as well as the mass ratio distribution expected from random pairing from the Kroupa IMF in yellow.
+
+TODO: Put the MCMC samples up on zenodo or something.
 
 \begin{figure}
-\includegraphics[width=\columnwidth]{MRD_normal.pdf}
+\includegraphics[width=\columnwidth]{MRD_total.pdf}
 \caption{Mass ratio distribution for our sample.
-The data was fit to both a histogram and a gaussian distribution.
+The data was fit to a histogram, a gaussian distribution, and a power law.
 The histogram is shown in the solid blue blocks, with $1 \sigma$ uncertainties marked with error bars.
-The variance of the gaussian fit is shown with 500 samples from the posterior probability distribution for the parameters.}
+The variance of the gaussian fit is shown with 500 samples from the posterior probability distribution for the parameters.
+We also show the best-fit power law and the mass ratio distribution from random pairing of the Kroupa initial mass function (IMF).}
 \label{fig:mrd}
@@
 
-The most striking feature of the mass ratio distribution shown in Figure \ref{fig:mrd} is the turnover at intermediate q, which the gaussian fit finds occurs at $q = 0.36 \pm 0.04$ and which excludes a power law fit (including a flat distribution).
-
-TODO: Compare to chabrier IMF, power law, and flat distribution quantitatively. Bayesian evidence ratios?
+The most striking feature of the mass ratio distribution shown in Figure \ref{fig:mrd} is the turnover at intermediate q, which the gaussian fit finds occurs at $q = 0.36 \pm 0.04$.
+Although the power law fit and the Kroupa IMF are visually very poor fits to the data, we formally compare the models to ensure that the different form is not an artifact of binning or simple noise.
+We make the comparison using the posterior odds:
+
+\begin{equation}
+\mathrm{Odds} = \frac{\int_{\vec{\theta_1}} P_1(q|\vec{\theta_1}) P(\vec{\theta_1})}{\int_{\vec{\theta_2}} P_2(q|\vec{\theta_2}  P(\vec{\theta_2})} \equiv \frac{Z_1}{Z_2}
+\end{equation}
+
+The integrals are estimated as part of the nested sampling algorithm in the MultiNest code.
+The odds ratio comparing the gaussian to power law fit is $Z_\mathrm{gauss} / Z_\mathrm{power} = 69 \pm 1.1 \e{7}$ indicating a very strong preference for the gaussian model.
+We also compare to the mass ratio distribution expected for random pairing from the Kroupa IMF.
+In this case, there are no free parameters so the evidence integral just becomes the likelihood function (Equation \ref{eqn:money}).
+The corresponding odds ratio is  $Z_\mathrm{gauss} / Z_\mathrm{kroupa} = 333 \pm 4 \e{17}$, again indicating a very strong preference for the gaussian fit.
 
@@
 IDs: 13A-0139, 13B-0112, 2014A-0260, 14A-0260, 15A-0245; PI: Kevin Gullikson), which is operated by the Association of Universities for Research in Astronomy (AURA) under a cooperative agreement with the National Science Foundation.
-
-%              &                &                &                &          MJD &            &  exptime &     snr \\
-%         star &            SpT &             ra &            dec & (JD-2450000) & instrument &  (sec)   &
 

### 2016-02-12 paper/ms.tex
Switched from gaussian to beta distribution fit, among other small things.

@@
 \includegraphics[width=\columnwidth]{Imaging_Data.pdf}
-\caption{Detection images for all stars in which we detect a companion in the follow-up NIRI data.}
+\caption{Detection images for all stars in which we detect a companion in the follow-up NIRI data. 
+TODO: Update imaging table. What to do with HIP 88116???}
 \label{fig:images}
@@
 \begin{equation}
-Q(T_\mathrm{eff}) = \sum_k Q(T, v_k) v_k 
+Q(T) = \sum_k Q(T, v_k) v_k 
 \end{equation} 
@@
 The detection rate falls with hotter temperatures because the companions are expected to be fast rotators, which are more difficult to detect.
-ADAM AND SALLY: IS THIS FIGURE NECESSARY OR IS THE TEXT ENOUGH?
 
@@
 
-Where did HIP 118243 go? It has an imaging detection (though at very wide separation), but nothing in the Companion table.
-
 \subsection{Fitting  Methodology}
@@
 $K=360$ is the total sample size for our survey, $Q(q)$ is the completeness function shown in Figure \ref{fig:completeness}, and $P(q|\vec{\theta})$ is the likelihood function for the mass ratio given the model parameters.
-We fit the data to two distinct distributions: a histogram ($P_1$) and a gaussian distribution ($P_2$):
+We fit the data to three distinct distributions: a histogram ($P_1$) and a beta distribution ($P_2$), and a power law ($P_3$):
 
@@
      \end{cases} \label{eqn:P1} \\
- P_2(q|\vec{\theta}) &= \frac{A}{\sqrt{2\pi\sigma^2}} e^{-\frac{(q - \mu)^2}{2\sigma^2}} \label{eqn:P2} \\
+ %P_2(q|\vec{\theta}) &= \frac{A}{\sqrt{2\pi\sigma^2}} e^{-\frac{(q - \mu)^2}{2\sigma^2}} \label{eqn:P2} \\
+ P_2(q|\vec{\theta}) &= \frac{\Gamma(a+b)}{\Gamma(a)\Gamma(b)} q^{a-1}(1-q)^{b-1} \\
  P_3(q|\vec{\theta}) &= (1-\gamma)q^{-\gamma} \label{eqn:P3}
 \end{align}
-The constant $A$ in the gaussian distribution is a renormalization factor such that the distribution is only defined from $0 < q < 1$:
-
-\begin{equation}
-A = \frac{2}{\erf\left(\frac{\mu}{\sigma \sqrt{2}}\right) - \erf\left(\frac{\mu - 1}{\sigma \sqrt{2}}\right)}
-\end{equation}
+%The constant $A$ in the gaussian distribution is a renormalization factor such that the distribution is only defined from $0 < q < 1$:
+
+%\begin{equation}
+%A = \frac{2}{\erf\left(\frac{\mu}{\sigma \sqrt{2}}\right) - \erf\left(\frac{\mu - 1}{\sigma \sqrt{2}}\right)}
+%\end{equation}
 
@@
 
-The gaussian fit only has two parameters ($\mu, \sigma$), and was chosen because it has a similar shape to the histogram resulting from the first model.
-We use uniform priors on both $\mu$ and $\sigma$, resulting in the posterior probability
+The beta function fit only has two parameters ($a, b$), and was chosen because it has a similar shape to the histogram resulting from the first model and is only defined for $0 < q < 1$.
+We use uniform priors on both $a$ and $b$, resulting in the posterior probability
 
 \begin{equation}
-P_2(\mu, \sigma | \{\vec{x_k}\}) \propto P_2(q|\mu, \sigma) 
+P_2(a, b | \{\vec{x_k}\}) \propto P_2(q|a, b) 
 \end{equation}
@@
 The $1\sigma$ uncertainties in the bin heights from the histogram model are shown as error bars, and we overplot 500 samples of the gaussian fit to show the spread allowed by the data.
-The best-fit power law is plotted with a green dot-dashed line, as well as the mass ratio distribution expected from random pairing from the Kroupa IMF in yellow.
+The best-fit power law is plotted with a green dot-dashed line, as well as the mass ratio distribution expected from random pairing from the Kroupa initial mass function (IMF) in yellow.
 
@@
 \caption{Mass ratio distribution for our sample.
-The data was fit to a histogram, a gaussian distribution, and a power law.
+The data was fit to a histogram, a beta distribution, and a power law.
 The histogram is shown in the solid blue blocks, with $1 \sigma$ uncertainties marked with error bars.
-The variance of the gaussian fit is shown with 500 samples from the posterior probability distribution for the parameters.
-We also show the best-fit power law and the mass ratio distribution from random pairing of the Kroupa initial mass function (IMF).}
+The variance of the beta function fit is shown with 500 samples from the posterior probability distribution for the parameters.
+We also show the best-fit power law and the mass ratio distribution resulting from random pairing of the Kroupa initial mass function.}
 \label{fig:mrd}
@@
 
-The most striking feature of the mass ratio distribution shown in Figure \ref{fig:mrd} is the turnover at intermediate q, which the gaussian fit finds occurs at $q = 0.36 \pm 0.04$.
+The most striking feature of the mass ratio distribution shown in Figure \ref{fig:mrd} is the turnover at intermediate q, which the beta distribution fit finds occurs at $q = 0.30^{+0.03}_{-0.04}$.
 Although the power law fit and the Kroupa IMF are visually very poor fits to the data, we formally compare the models to ensure that the different form is not an artifact of binning or simple noise.
@@
 The integrals are estimated as part of the nested sampling algorithm in the MultiNest code.
-The odds ratio comparing the gaussian to power law fit is $Z_\mathrm{gauss} / Z_\mathrm{power} = 69 \pm 1.1 \e{7}$ indicating a very strong preference for the gaussian model.
+The odds ratio comparing the beta distribution to power law fit is $Z_\mathrm{beta} / Z_\mathrm{power} = 81 \pm 1.3 \e{8}$ indicating a very strong preference for the beta distribution model.
 We also compare to the mass ratio distribution expected for random pairing from the Kroupa IMF.
 In this case, there are no free parameters so the evidence integral just becomes the likelihood function (Equation \ref{eqn:money}).
-The corresponding odds ratio is  $Z_\mathrm{gauss} / Z_\mathrm{kroupa} = 333 \pm 4 \e{17}$, again indicating a very strong preference for the gaussian fit.
-
-TODO: Speculate on the discrepancy between my results and VAST. Perhaps the change occurs closer than their cut of 125 AU? Perhaps it is inside $\sim 30$ AU, where they have very low completeness?
+The corresponding odds ratio is  $Z_\mathrm{beta} / Z_\mathrm{kroupa} = 325 \pm 3.6 \e{18}$, again indicating a very strong preference for the beta distribution fit.
+
+\subsection{Comparison to Previous Results}
+
+Our mass ratio distribution appears to be in tension with the results of the VAST survey \citep{DeRosa2014}, which finds a nearly flat distribution for close companions.
+However, their subsample of close companions only includes 18 binaries, so it is possible that the different forms are just a result of small number statistics.
+To assess the degree of tension, we use the Anderson-Darling [CITE] test to find the probability that both their close companion subsample and our companions are drawn from the same parent distribution.
+We only use companions from this work with mean $\overline{q} > 0.15$, since the survey completeness is roughly constant in that range.
+To account for measurement uncertainties in the mass ratios, we choose from the mass ratio samples (see Section \ref{sec:mrd}) many times and compute the Anderson-Darling test statistic each time.
+Since \citet{DeRosa2014} do not quote uncertainties, we assume uncertainties of $\sigma_q = 0.05$ for all of their measurements.
+The result is $p = 0.02^{+0.02}_{-0.01}$, indicating that it is unlikely that both samples come from the same parent distribution.
+
+The differing results indicate that the mass ratio distribution changes inside $\sim 30-50$ AU, where \citet{DeRosa2014} has low completeness.
+This intrepretation implies that the mass ratio distribution is a very steep power law at wide ($a \gtrsim 150$ AU) separations, flattens out at intermediate separations ($50\ \mathrm{AU} \lesssim a \lesssim 150\ \mathrm{AU}$), and begins to show a preference for $q \sim 0.3$ at close separations ($a \lesssim 50$ AU).
+
+\subsection{Theoretical Implications}
 

### 2016-02-15 paper/ms.tex
Figured out HIP 88116

@@
 
+\subsection{Spectroscopic Data}
 We use several high spectral resolution, cross-dispersed \'echelle spectrographs for this survey.
@@
 
+\subsection{Imaging Data}
 As part of the follow-up effort, we used the NIRI instrument behind the Altair adaptive optics system at the Gemini North Telescope.
@@
 We reduced the data using the Gemini set of IRAF tasks, which include steps for nonlinearity correction, flat-fielding, sky subtraction, and co-addition of the dither frames.
+
+We measure the flux and position of both stars by fitting a 2D Moffat function [CITE] to both stars simultaneously, constraining the shape parameters for both functions to be the same.
+The ratio of the amplitudes gives the magnitude difference, and the pixel locations along with the detector pixel scale gives the separation and position angle between the stars.
+We note that the goal of these images was confirmation and no reference tip-tilt targets were observed; the position angle uncertainty is therefore likely underestimated.
 
@@
 We show the separation, position angle, and magnitude difference in Table \ref{tab:imaging_obs}, and display the images in Figure \ref{fig:images}.
+One star, HIP 88116, has several nearby sources in the image.
+We quote the magnitude difference and separation of the brightest source in Table \ref{tab:imaging_obs}, but stress that \emph{none} of the visible sources is likely to be the companion we see in the spectroscopic data.
+The two epochs of spectroscopic data show a radial velocity shift of $\Delta v = 30.7 \mathrm{km\ s}^{-1}$ over the course of roughly one year; this orbital motion is much too large to allow for any of the companions visible in the image (all with separations $ > 1''$).
 
@@
 \caption{Detection images for all stars in which we detect a companion in the follow-up NIRI data. 
-TODO: Update imaging table. What to do with HIP 88116???}
+There are several nearby sources for HIP 88116, none of which are the source we detect in the 
+spectroscopic data (see Section \ref{sec:companions}).}
 \label{fig:images}
@@
 Many of the companions we use in the analysis only have one detection in our data; 12/22 of these are previously known companions and so don't need follow-up to confirm.
-An The remaining 10 are new and unconfirmed detections; these all have very strong CCF signals and are likely to be confirmed with follow-up spectroscopy or imaging.
-We do not expect their inclusion to significantly alter the results.
-TODO: test this statement...
+The remaining 10 are new and unconfirmed detections; these all have very strong CCF signals and are likely to be confirmed with follow-up spectroscopy or imaging.
+Their inclusion does not significantly change the results.
 
@@
 We only use companions from this work with mean $\overline{q} > 0.15$, since the survey completeness is roughly constant in that range.
-To account for measurement uncertainties in the mass ratios, we choose from the mass ratio samples (see Section \ref{sec:mrd}) many times and compute the Anderson-Darling test statistic each time.
+To account for measurement uncertainties in the mass ratios, we choose from the mass ratio samples ($q_k^{(n)}$, see Section \ref{sec:mrd}) many times and compute the Anderson-Darling test statistic each time.
 Since \citet{DeRosa2014} do not quote uncertainties, we assume uncertainties of $\sigma_q = 0.05$ for all of their measurements.
@@
 \enddata
-\tablecomments{$\dagger$: There is no K-magnitude tabulated in the Simbad Database.
-The value quoted here is estimated from the spectral type of the star and its V-band magnitude.
-TODO: I think my detection in HIP 88116 is too close to be any of the 4 companions in the image (it has a large $\Delta \mathrm{RV}$, and the expected $\Delta \mathrm{K_c}$ is about 2.7, smaller than any of the images).
-What should I report here?}
+\tablecomments{$\dagger$: There is no K-magnitude tabulated in the Simbad Database. The value quoted here is estimated from the spectral type of the star and its V-band magnitude.}
 \label{tab:imaging_obs}

### 2016-02-16 paper/ms.tex
Removed title from spectroscopic figure

@@
 The distribution of mass ratios is a unique probe into the conditions of the collapsing molecular core as well as the circumstellar disks of the binary fragments.
-Inside $a \sim 1000$ AU the disks from the two forming stars can interact, and additionally companions can form directly from the primary star disk.
+Inside $a \sim 1000$ AU the disks from the two forming stars can interact, and additionally companions can form directly through disk fragmentation.
 We should therefore expect the mass-ratio distribution of close companions to differ from that of wide companions.
@@
 We estimate the temperatures and masses of the 58 companion detections, 25 of which are new detections.
-We present the mass-ratio distribution for our sample, and find that it is well described by a gaussian with mean of $q = 0.35 \pm 0.04$.
+We present the mass-ratio distribution for our sample, and find that it is has a robust maximum near mass ratios $q \sim 0.3$.
 TODO: discuss implications.
@@
 However close fragments ($a \sim 100$ AU) will interact with each other; the protostellar disk may be truncated, destabilized, or form into a circumbinary disk if the separation is small enough \citep{Bate1997}.
-In addition, unstable disk can fragment to form low-mass companions \citep{Kratter2006, Stamatellos2011}.
+In addition, an unstable disk can fragment to form low-mass companions \citep{Kratter2006, Stamatellos2011}.
 The mass ratios of close companions formed via either mechanism should be affected by preferential accretion.
@@
 It does introduce a Malmquist bias in the derived mass ratio, which we discuss and correct for in Section \ref{sec:mrd}.
-Likewise, the $v\sin{i}$ limit makes accounting for the primary star spectrum in the companion search trivial; since most A- or B-type stars are rapid rotators, the cutoff does not remove very many stars from the sample.
+Likewise, the $v\sin{i}$ limit makes accounting for the primary star spectrum in the companion search trivial; since most A- or B-type stars are rapid rotators, the cutoff does not remove very many stars from the potential sample.
 We exclude pre-main sequence stars because both the primary and the companion mass would depend very strongly on young and uncertain ($\lesssim 1$ Myr) evolutionary models.
 Finally, we exclude post-main sequence stars from our sample because the binary flux ratio would be even less favorable to companion detection in an evolved star.
-Most of the spectral peculiarities denote narrow lines, which are already cut from the sample by the $v\sin{i}$ cut.
+Most of the spectral peculiarities denote narrow lines, which are already removed from the sample by the $v\sin{i}$ cut.
 The target list and observing details are given in Table \ref{tab:observations}.
@@
 For unsaturated lines, the best-fit telluric model reproduces the data to within $\sim 1-5\%$ of the continuum level.
-
-\subsection{Imaging Data}
-As part of the follow-up effort, we used the NIRI instrument behind the Altair adaptive optics system at the Gemini North Telescope.
-For each star listed in Table \ref{tab:imaging_obs}, we obtained 25 images in 5 dithering positions.
-We used the K-continuum band centered on $2.2718\ \mu m$ and a variety of exposure times and dates (listed in Table \ref{tab:imaging_obs}).
-Because the targets are all extremely bright, we used the high read noise and high flux detector settings to allow for very short co-add exposure times.
-We reduced the data using the Gemini set of IRAF tasks, which include steps for nonlinearity correction, flat-fielding, sky subtraction, and co-addition of the dither frames.
-
-We measure the flux and position of both stars by fitting a 2D Moffat function [CITE] to both stars simultaneously, constraining the shape parameters for both functions to be the same.
-The ratio of the amplitudes gives the magnitude difference, and the pixel locations along with the detector pixel scale gives the separation and position angle between the stars.
-We note that the goal of these images was confirmation and no reference tip-tilt targets were observed; the position angle uncertainty is therefore likely underestimated.
-
-TODO: MAKE THE SPECTRA AVAILABLE SOMEHOW...
-
-\section{Companion Search}
-\label{sec:companions}
 
@@
 
+\subsection{Imaging Data}
+As part of the follow-up effort, we used the NIRI instrument behind the Altair adaptive optics system at the Gemini North Telescope.
+For each star listed in Table \ref{tab:imaging_obs}, we obtained 25 images in 5 dithering positions.
+We used the K-continuum band centered on $2.2718\ \mu m$ and a variety of exposure times and dates (listed in Table \ref{tab:imaging_obs}).
+Because the targets are all extremely bright, we used the high read noise and high flux detector settings to allow for very short co-add exposure times.
+We reduced the data using the Gemini set of IRAF tasks, which include steps for nonlinearity correction, flat-fielding, sky subtraction, and co-addition of the dither frames.
+
+We measure the flux and position of both stars by fitting a 2D Moffat function [CITE] to both stars simultaneously, constraining the shape parameters for both functions to be the same.
+The ratio of the amplitudes gives the magnitude difference, and the pixel locations along with the detector pixel scale gives the separation and position angle between the stars.
+We note that the goal of these images was confirmation and we did not observe any reference targets to make a distortion map and correct the image rotation.
+The uncertainty in position angle and to a lesser degree separation quoted in Table \ref{tab:imaging_obs} is likely underestimated.
+
+TODO: MAKE THE SPECTRA AVAILABLE SOMEHOW...
+
+\section{Companion Search}
+\label{sec:companions}
+
 We search for stellar companions to our sample stars using the direct spectral detection technique, described in detail in \citet{Gullikson2016}.
-In short, we unsharp-mask each spectrum using a gaussian filter with width proportional to to primary star $v\sin{i}$ to remove the broad lines from the primary star.
+In short, we unsharp-mask each spectrum using a gaussian filter with width proportional to the primary star $v\sin{i}$ to remove the broad lines from the primary star.
 We then cross-correlate each \'echelle order of each filtered spectrum against a large grid of Phoenix model spectra \citep{Husser2013_b} with the following parameters:
@@
 
-We then combine the cross-correlation functions for all orders using both a simple average and the maximum-likelihood weighting scheme \citep{Zucker2003}.
+We combine the cross-correlation functions for all orders using both a simple average and the maximum-likelihood weighting scheme \citep{Zucker2003}.
 A companion detection is denoted by a strong peak in the combined cross-correlation function (CCF).
@@
 Most of the detected companions have follow-up spectra to confirm the existence of the companion.
-In most cases, there is a clear shift in the radial velocity of the companion, indicating that it is orbiting the target star and is not a foreground or background companion (See Figure \ref{fig:ccf}).
+In most cases, there is a clear shift in the radial velocity of the companion, indicating that it is orbiting the target star and is not a foreground or background contaminant (See Figure \ref{fig:ccf}).
 In addition we obtained Gemini/NIRI adaptive optics imaging data for 19 of the northern companions, and were able to resolve 7 of them.
@@
 We quote the magnitude difference and separation of the brightest source in Table \ref{tab:imaging_obs}, but stress that \emph{none} of the visible sources is likely to be the companion we see in the spectroscopic data.
-The two epochs of spectroscopic data show a radial velocity shift of $\Delta v = 30.7 \mathrm{km\ s}^{-1}$ over the course of roughly one year; this orbital motion is much too large to allow for any of the companions visible in the image (all with separations $ > 1''$).
+The two epochs of spectroscopic data show a radial velocity shift of $\Delta v = 30.7\ \mathrm{km\ s}^{-1}$ over the course of roughly one year; this orbital motion is much too large to allow for any of the companions visible in the image (all with separations $ > 1''$).
 
@@
 There are sufficient metal lines in the optical spectra that the resulting CCF always has a very strong peak at the radial velocity of the primary star.
-The near-infrared IGRINS spectra are dominated by hydrogren Brackett lines and have very few strong metal lines; we use the subset from $1.51 - 1.73 \micron$ for these spectra.
+The near-infrared IGRINS spectra have very few strong metal lines; we use the subset from $1.51 - 1.73 \micron$ that is dominated by hydrogren Brackett lines for these spectra.
 We then estimate the temperature and surface gravity of the primary stars from the CCF with the largest peak.
@@
 
-The gyrochronology relations do not work for stars with $T \gtrsim 6250\ K$, the canonical limit at which the convective zone is too small to efficiently remove angular momentum to the stellar wind and spin down the star \citep{Pinsonneault2001}.
+The gyrochronology relations are invalid for stars with $T \gtrsim 6250\ K$, the canonical limit at which the convective zone is too small to efficiently remove angular momentum to the stellar wind and spin down the star \citep{Pinsonneault2001}.
 \citet{Zorec2012} fit maxwellian distributions to the equatorial velocity of A- and B-type stars in several mass bins.
@@
 $K=360$ is the total sample size for our survey, $Q(q)$ is the completeness function shown in Figure \ref{fig:completeness}, and $P(q|\vec{\theta})$ is the likelihood function for the mass ratio given the model parameters.
-We fit the data to three distinct distributions: a histogram ($P_1$) and a beta distribution ($P_2$), and a power law ($P_3$):
+We fit the data to three distinct distributions: a histogram ($P_1$), a beta distribution ($P_2$), and a power law ($P_3$):
 
@@
 We show the resulting fits in Figure \ref{fig:mrd}.
-The $1\sigma$ uncertainties in the bin heights from the histogram model are shown as error bars, and we overplot 500 samples of the gaussian fit to show the spread allowed by the data.
+The $1\sigma$ uncertainties in the bin heights from the histogram model are shown as error bars, and we overplot 500 samples of the beta distribution fit to show the spread allowed by the data.
 The best-fit power law is plotted with a green dot-dashed line, as well as the mass ratio distribution expected from random pairing from the Kroupa initial mass function (IMF) in yellow.
@@
 The corresponding odds ratio is  $Z_\mathrm{beta} / Z_\mathrm{kroupa} = 325 \pm 3.6 \e{18}$, again indicating a very strong preference for the beta distribution fit.
+The extreme unlikeliness of the Kroupa IMF model also indicates that our sample is not significantly biased by foreground or background contaminants.
 
@@
 To assess the degree of tension, we use the Anderson-Darling [CITE] test to find the probability that both their close companion subsample and our companions are drawn from the same parent distribution.
-We only use companions from this work with mean $\overline{q} > 0.15$, since the survey completeness is roughly constant in that range.
+We only use companions from this work with mean $\overline{q} > 0.15$, since the survey completeness is roughly constant in that range and because the VAST survey subsample makes the same cut.
 To account for measurement uncertainties in the mass ratios, we choose from the mass ratio samples ($q_k^{(n)}$, see Section \ref{sec:mrd}) many times and compute the Anderson-Darling test statistic each time.
@@
   HIP 75178 &  5.49 &  2015-03-24 &   29x0.6 & \nodata & \nodata & \nodata \\
-  HIP 88116 &  4.47 &  2015-03-22 &   50x0.3 & $3.260 +/- 0.001$ & $210.71 \pm 0.02$ & $3.9 \pm 0.4$ \\
+  HIP 88116 &  4.47 &  2015-03-22 &   50x0.3 & $3.260 +/- 0.001$ & $59.29 \pm 0.02$ & $3.9 \pm 0.4$ \\
   HIP 91118 &  5.67 &  2015-10-16 &   43x0.4 & $0.1667 +/- 0.0007$ & $41.7 \pm 0.2$ & $1.77 \pm 0.01$ \\

### 2016-02-19 paper/ms.tex
Split sample properties from observation log

@@
 Most of the spectral peculiarities denote narrow lines, which are already removed from the sample by the $v\sin{i}$ cut.
-The target list and observing details are given in Table \ref{tab:observations}.
+The sample is given in Table \ref{tab:sample}.
 
@@
 For unsaturated lines, the best-fit telluric model reproduces the data to within $\sim 1-5\%$ of the continuum level.
+
+We give the spectroscopic observation log in Table \ref{tab:observations}.
+We calculate the signal-to-noise ratio (the "snr" column) for the optical instruments (CHIRON, TS23, and HRS) as the median of the extracted flux divided by it's uncertainty for each pixel from the \'echelle order nearest $675$ nm.
+For the IGRINS instrument, we calculate the signal-to-noise ratio from the order nearest $2200$ nm.
+
+TODO: MAKE THE SPECTRA AVAILABLE SOMEHOW...
 
@@
 The uncertainty in position angle and to a lesser degree separation quoted in Table \ref{tab:imaging_obs} is likely underestimated.
-
-TODO: MAKE THE SPECTRA AVAILABLE SOMEHOW...
 
@@
 \LongTables
-\begin{deluxetable*}{|l|lllrlrr|}
+\begin{deluxetable*}{|l|lrrrrllllll|}
+\tabletypesize{\scriptsize}
+\tablewidth{0pt}
+\tablecaption{Sample Properties}
+\tablehead{
+      \colhead{} & \colhead{} & \colhead{} & \colhead{} &  \colhead{}  & \colhead{parallax} & \colhead{$T_\mathrm{eff}$} & \colhead{$\log{g}$} & \colhead{Mass} & \colhead{Age} & \colhead{} \\
+       \colhead{star} & \colhead{SpT} & \colhead{RA} & \colhead{DEC} &  \colhead{V} &   \colhead{
+       (mas)} & \colhead{(K)} & \colhead{(cgs)} & \colhead{($M_{\odot}$)} & \colhead{(Myr)} & \colhead{Ref}
+       }
+
+\startdata
+
+     HIP 813 &           B9Vn &    00:10:02.20 &   +11:08:44.93 &   5.537 &     10.68 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+    HIP 1191 &          B8.5V &    00:14:54.52 &   -09:34:10.45 &   5.757 &      9.63 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+    HIP 1366 &            A2V &    00:17:05.50 &   +38:40:53.89 &   4.610 &     10.56 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+    HIP 1647 &            B9V &    00:20:39.04 &   -69:37:29.68 &   5.498 &     10.25 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+    HIP 2381 &            A3V &    00:30:22.65 &   -23:47:15.65 &   5.190 &     18.83 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+    HIP 2505 &           B8Vn &    00:31:46.36 &   +54:31:20.23 &   4.732 &      8.64 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+    HIP 2548 &          B9.5V &    00:32:23.78 &   +06:57:19.66 &   5.698 &     12.35 &   $11864 \pm 403$ &  $4.4 \pm 0.14$ &  $2.8^{+0.16}_{-0.15}$ &     $78^{+70}_{-52}$ &      1 \\
+    HIP 2912 &            B5V &    00:36:52.85 &   +33:43:09.64 &   4.360 &      5.45 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+    HIP 3300 &            B2V &    00:42:03.90 &   +50:30:45.09 &   4.810 &      2.28 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+    HIP 3478 &            B5V &    00:44:26.19 &   +47:51:50.34 &   5.646 &      5.23 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+    HIP 3741 &            B9V &    00:48:01.06 &   -21:43:20.99 &   5.570 &      9.51 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+    HIP 3881 &            B5V &    00:49:48.85 &   +41:04:44.08 &   4.530 &      5.28 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+    HIP 4436 &            A5V &    00:56:45.21 &   +38:29:57.64 &   3.870 &     25.14 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+    HIP 5131 &           A1Vn &    01:05:40.96 &   +21:28:23.45 &   5.317 &     11.86 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+    HIP 5132 &           A0Vn &    01:05:41.71 &   +21:27:55.60 &   5.532 &     11.64 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+    HIP 5310 &            A3V &    01:07:57.16 &   +20:44:20.83 &   5.569 &     21.14 &    $8611 \pm 293$ &  $4.4 \pm 0.14$ &  $1.8^{+0.10}_{-0.08}$ &  $307^{+234}_{-196}$ &      1 \\
+    HIP 5348 &            B6V &    01:08:23.08 &   -55:14:44.73 &   3.967 &     10.92 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+    HIP 5361 &            B8V &    01:08:33.47 &   +58:15:48.41 &   5.773 &      5.41 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+    HIP 5518 &          A0Vnn &    01:10:39.32 &   +68:46:43.04 &   5.318 &     11.78 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+    HIP 5626 &            A3V &    01:12:16.82 &   +79:40:26.27 &   5.600 &     12.07 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+    HIP 7345 &            A1V &    01:34:37.78 &   -15:40:34.90 &   5.619 &     16.84 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+    HIP 8016 &            B9V &    01:42:55.86 &   +70:37:21.09 &   5.177 &     11.75 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+    HIP 8704 &          B1.5V &    01:51:59.32 &   +55:08:50.58 &   5.520 &      2.52 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+      HR 545 &          B9.5V &    01:53:31.77 &   +19:17:46.27 &   4.700 &   \nodata &  $11000 \pm 1000$ &  $4.3 \pm 0.25$ &  $2.5^{+0.39}_{-0.35}$ &    $37^{+105}_{-28}$ &  2 \\
+    HIP 9312 &           A0Vn &    01:59:38.04 &   +64:37:17.76 &   5.283 &     13.28 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+    HIP 9564 &           A1Vn &    02:02:52.48 &   +64:54:05.27 &   5.999 &     11.92 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+      HR 604 &            B8V &    02:03:54.72 &   +42:19:51.41 &   5.820 &   \nodata &  $11000 \pm 1000$ &  $4.5 \pm 0.25$ &  $2.4^{+0.37}_{-0.34}$ &     $28^{+87}_{-20}$ &  2 \\
+   HIP 10320 &            B9V &    02:12:54.47 &   -30:43:25.77 &   5.261 &     10.18 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 10670 &          A1Vnn &    02:17:18.87 &   +33:50:49.90 &   4.000 &     29.04 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 10732 &           A1Vn &    02:18:07.54 &   +19:54:04.19 &   5.575 &      7.29 &    $9500 \pm 300$ &  $4.0 \pm 0.25$ &  $2.1^{+0.18}_{-0.16}$ &    $80^{+237}_{-70}$ &  2 \\
+   HIP 11345 &            A0V &    02:25:57.01 &   -12:17:25.71 &   4.869 &      7.15 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 12332 &            A7V &    02:38:48.99 &   +21:57:41.06 &   5.454 &      9.68 &    $7750 \pm 300$ &  $3.5 \pm 0.25$ &  $1.9^{+0.37}_{-0.30}$ &  $687^{+218}_{-425}$ &  2 \\
+   HIP 12706 &           A2Vn &    02:43:18.04 &   +03:14:08.94 &   3.470 &     40.97 &    $8551 \pm 291$ &  $4.3 \pm 0.14$ &  $1.9^{+0.15}_{-0.12}$ &  $650^{+105}_{-188}$ &      1 \\
+   HIP 12719 &            B3V &    02:43:27.11 &   +27:42:25.72 &   4.670 &      9.51 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 12803 &           B9Vn &    02:44:32.97 &   +15:18:42.71 &   5.776 &      5.49 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 13165 &            B6V &    02:49:17.56 &   +17:27:51.52 &   5.314 &      4.18 &  $15000 \pm 1000$ &  $4.0 \pm 0.25$ &  $4.2^{+0.58}_{-0.50}$ &     $31^{+42}_{-22}$ &  2 \\
+   HIP 13202 &            A0V &    02:49:54.18 &   -27:56:31.14 &   5.389 &      7.11 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 13209 &           B8Vn &    02:49:59.03 &   +27:15:37.83 &   3.606 &     19.69 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 13327 &            B7V &    02:51:29.59 &   +15:04:55.45 &   5.514 &      6.60 &  $15000 \pm 1000$ &  $4.5 \pm 0.25$ &  $4.0^{+0.50}_{-0.45}$ &      $15^{+26}_{-9}$ &  2 \\
+   HIP 13717 &            A3V &    02:56:37.42 &   -03:42:44.35 &   5.160 &     17.49 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 13879 &           A2Vn &    02:58:45.67 &   +39:39:45.81 &   4.700 &     10.53 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 14043 &            B7V &    03:00:52.21 &   +52:21:06.22 &   5.253 &      7.11 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 14143 &            B7V &    03:02:22.52 &   +04:21:10.39 &   5.607 &      5.93 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 14293 &            A5V &    03:04:16.52 &   -07:36:03.08 &   5.300 &     24.06 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 14576 &            B8V &    03:08:10.13 &   +40:57:20.33 &   2.120 &     36.27 &   $13070 \pm 444$ &  $4.0 \pm 0.14$ &  $3.6^{+0.28}_{-0.23}$ &    $139^{+16}_{-25}$ &      1 \\
+   HIP 14764 &            B8V &    03:10:38.79 &   +11:52:21.44 &   5.965 &      7.33 &  $11750 \pm 1000$ &  $4.2 \pm 0.25$ &  $2.8^{+0.42}_{-0.39}$ &     $35^{+91}_{-27}$ &  2 \\
+   HIP 14862 &          A2Vnn &    03:11:56.27 &   +74:23:37.17 &   4.840 &     19.72 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 15110 &            A1V &    03:14:54.10 &   +21:02:40.01 &   4.880 &     12.44 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 15338 &            B8V &    03:17:47.35 &   +44:01:30.08 &   5.478 &      4.46 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 15404 &            B3V &    03:18:37.74 &   +50:13:19.83 &   5.158 &      5.12 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 15444 &            B5V &    03:19:07.64 &   +50:05:41.88 &   5.036 &      5.82 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 16147 &            B5V &    03:28:03.07 &   +49:03:46.32 &   4.970 &      6.22 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 16210 &           B6Vn &    03:28:52.33 &   +49:50:54.17 &   5.578 &      6.22 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 16244 &            B3V &    03:29:22.05 &   +49:30:32.21 &   4.678 &      6.05 &  $16333 \pm 1000$ &  $4.3 \pm 0.25$ &  $4.7^{+0.57}_{-0.50}$ &      $15^{+22}_{-9}$ &  2 \\
+   HIP 16285 &            A5V &    03:29:55.15 &   -42:38:03.32 &   5.768 &     15.28 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 16322 &           A0Vn &    03:30:24.47 &   +11:20:11.19 &   5.125 &      9.03 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 16340 &            B8V &    03:30:36.95 &   +48:06:12.95 &   5.820 &      3.65 &  $12500 \pm 1000$ &  $4.0 \pm 0.25$ &  $3.1^{+0.51}_{-0.42}$ &     $49^{+92}_{-39}$ &  2 \\
+   HIP 16599 &            A3V &    03:33:39.06 &   +54:58:29.49 &   5.981 &     13.44 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 16611 &            B9V &    03:33:47.28 &   -21:37:58.38 &   4.300 &     11.12 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 17457 &            B7V &    03:44:30.51 &   -01:09:47.14 &   5.250 &      4.98 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 17527 &            B8V &    03:45:09.74 &   +24:50:21.34 &   5.640 &      7.97 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 17563 &            B3V &    03:45:40.44 &   +06:02:59.97 &   5.332 &      6.11 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 18141 &            B8V &    03:52:41.66 &   -05:21:40.54 &   5.476 &      5.57 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 18396 &            B6V &    03:55:58.17 &   +47:52:17.12 &   5.379 &      4.47 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 18724 &            B3V &    04:00:40.82 &   +12:29:25.22 &   3.410 &      6.74 &  $21000 \pm 1000$ &  $4.5 \pm 0.25$ &  $7.1^{+0.68}_{-0.64}$ &        $8^{+7}_{-3}$ &  2 \\
+   HIP 18788 &            B5V &    04:01:32.05 &   -01:32:58.78 &   5.280 &      7.88 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 18805 &            B5V &    04:01:46.14 &   +09:59:52.84 &   5.676 &      5.71 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 19799 &           B9Vn &    04:14:36.23 &   +10:00:41.05 &   5.208 &      8.34 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 19949 &           A2Vn &    04:16:43.09 &   +53:36:42.47 &   5.200 &      9.98 &    $9825 \pm 334$ &  $3.8 \pm 0.14$ &  $2.2^{+0.11}_{-0.09}$ &  $199^{+135}_{-124}$ &      1 \\
+   HIP 19968 &            B7V &    04:16:53.56 &   +61:50:59.97 &   5.700 &      7.31 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 20264 &            A0V &    04:20:39.01 &   -20:38:22.64 &   5.380 &      6.86 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 20380 &            A3V &    04:21:51.81 &   +56:30:22.74 &   5.920 &     10.31 &    $8738 \pm 297$ &  $3.9 \pm 0.14$ &  $1.9^{+0.10}_{-0.08}$ &  $331^{+213}_{-202}$ &      1 \\
+   HIP 20430 &          B9Vnn &    04:22:34.94 &   +25:37:45.54 &   5.376 &     11.20 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 20507 &            A2V &    04:23:40.85 &   -03:44:43.68 &   5.171 &     15.60 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 20579 &            B8V &    04:24:29.16 &   +34:07:50.73 &   5.722 &      7.28 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 20789 &            B7V &    04:27:17.45 &   +22:59:46.80 &   5.515 &      8.63 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 21589 &            A6V &    04:38:09.46 &   +12:30:39.01 &   4.270 &     21.24 &    $8591 \pm 292$ &  $3.9 \pm 0.14$ &  $1.8^{+0.09}_{-0.07}$ &  $303^{+231}_{-193}$ &      1 \\
+   HIP 21683 &           A5Vn &    04:39:16.50 &   +15:55:04.70 &   4.675 &     20.97 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 21819 &            A2V &    04:41:19.76 &   +28:36:53.98 &   5.726 &      8.55 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 21928 &           A1Vn &    04:42:54.33 &   +43:21:54.53 &   5.301 &     13.52 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 22028 &            A1V &    04:44:07.98 &   -18:39:59.71 &   5.527 &     10.66 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 22509 &           A1Vn &    04:50:36.72 &   +08:54:00.65 &   4.350 &     14.53 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 22833 &            A3V &    04:54:46.90 &   +11:25:33.63 &   5.186 &     14.29 &    $8278 \pm 281$ &  $3.9 \pm 0.14$ &  $1.8^{+0.13}_{-0.09}$ &  $653^{+159}_{-300}$ &      1 \\
+   HIP 22840 &            B5V &    04:54:50.71 &   +00:28:01.81 &   5.975 &      4.50 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 22913 &            B9V &    04:55:50.15 &   +15:02:25.00 &   5.785 &      8.97 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 22958 &            B6V &    04:56:24.19 &   -05:10:16.87 &   5.490 &      4.40 &  $16000 \pm 1000$ &  $4.5 \pm 0.25$ &  $4.5^{+0.53}_{-0.50}$ &      $14^{+21}_{-8}$ &  2 \\
+   HIP 23362 &            B9V &    05:01:25.58 &   -20:03:06.91 &   4.894 &     16.48 &   $12450 \pm 423$ &  $4.3 \pm 0.14$ &  $3.2^{+0.21}_{-0.16}$ &    $147^{+28}_{-59}$ &      1 \\
+   HIP 23916 &            B8V &    05:08:20.19 &   -08:39:55.17 &   5.780 &      4.79 &  $16500 \pm 1000$ &  $4.2 \pm 0.25$ &  $4.8^{+0.56}_{-0.52}$ &     $16^{+26}_{-10}$ &  2 \\
+   HIP 24244 &         B7.5Vn &    05:12:17.90 &   -11:52:09.19 &   4.450 &     14.07 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 24327 &            B7V &    05:13:13.88 &   -12:56:28.65 &   4.421 &      4.48 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 24505 &            B9V &    05:15:24.37 &   -26:56:36.63 &   5.040 &     11.73 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 24902 &            A3V &    05:20:14.67 &   +41:05:10.35 &   5.468 &     11.77 &    $8275 \pm 281$ &  $4.0 \pm 0.14$ &  $1.7^{+0.10}_{-0.08}$ &  $463^{+256}_{-284}$ &      1 \\
+   HIP 25048 &            B3V &    05:21:48.42 &   +41:48:16.46 &   5.200 &      6.16 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+ ADS 3962 AB &           B1Vn &    05:22:50.30 &   +03:32:52.00 &   4.990 &   \nodata &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 25143 &            A3V &    05:22:50.31 &   +41:01:45.33 &   5.545 &     11.15 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 25280 &            A0V &    05:24:28.49 &   -16:58:32.81 &   5.644 &     14.65 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 25281 &           B1V: &    05:24:28.62 &   -02:23:49.73 &   3.350 &      3.34 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 25555 &         B9.5Vn &    05:27:45.61 &   +15:52:26.58 &   5.512 &      7.69 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 25608 &            A1V &    05:28:15.34 &   -37:13:50.75 &   5.562 &     11.39 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 25695 &           B9Vn &    05:29:16.50 &   +25:09:00.78 &   5.480 &      7.67 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 25790 &           A3Vn &    05:30:26.16 &   +15:21:37.61 &   5.940 &     12.89 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 25813 &            B5V &    05:30:47.05 &   +05:56:53.29 &   4.200 &     10.77 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 26063 &            B1V &    05:33:31.45 &   -01:09:21.87 &   5.340 &      2.22 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 26093 &            B3V &    05:33:54.28 &   +14:18:20.08 &   5.588 &      7.31 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 26126 &            A2V &    05:34:16.77 &   +03:46:00.82 &   5.332 &     11.82 &    $9542 \pm 324$ &  $3.9 \pm 0.14$ &  $2.1^{+0.09}_{-0.08}$ &  $176^{+147}_{-116}$ &      1 \\
+     HR 1880 &          B0.5V &    05:35:08.48 &   +09:56:06.10 &   6.322 &   \nodata &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 26563 &           A4Vn &    05:38:53.08 &   -07:12:46.18 &   4.800 &     22.42 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 27100 &            A7V &    05:44:46.38 &   -65:44:07.90 &   4.360 &     21.80 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 27321 &            A6V &    05:47:17.09 &   -51:03:59.44 &   3.860 &     51.44 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 27713 &           A2Vn &    05:52:07.73 &   -09:02:30.84 &   5.964 &     10.11 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 28691 &            B8V &    06:03:27.37 &   +19:41:26.02 &   5.135 &      4.54 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 28756 &          B2.5V &    06:04:20.27 &   -32:10:20.74 &   5.631 &      3.24 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 28910 &            A0V &    06:06:09.32 &   -14:56:06.92 &   4.669 &     18.88 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 29150 &            A0V &    06:08:57.87 &   -22:25:38.68 &   5.482 &     13.24 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 29151 &           A3Vn &    06:08:57.90 &   +02:29:58.89 &   5.730 &      4.98 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 29735 &            B9V &    06:15:44.89 &   -13:43:06.29 &   4.998 &      8.00 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 29997 &           A0Vn &    06:18:50.78 &   +69:19:11.23 &   4.762 &     18.64 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 30069 &            B9V &    06:19:40.96 &   -34:23:47.73 &   5.750 &      8.00 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 30073 &            B2V &  06:19:42.7989 &  -07:49:22.473 &   5.246 &      3.74 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 30666 &           A3Vn &    06:26:39.59 &   -01:30:26.41 &   5.874 &     13.80 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 30788 &            B4V &    06:28:10.21 &   -32:34:48.25 &   4.480 &      7.70 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 31278 &           B5Vn &    06:33:37.92 &   -01:13:12.55 &   5.083 &      5.89 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 31362 &            B8V &    06:34:35.33 &   -32:42:58.51 &   5.610 &      6.20 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 31434 &          A0Vnn &    06:35:12.06 &   +28:01:20.32 &   5.266 &      8.82 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 32474 &          B9.5V &    06:46:39.02 &   -10:06:26.50 &   5.653 &      6.04 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 32607 &            A8V &    06:48:11.46 &   -61:56:29.00 &   3.300 &     33.78 &    $7770 \pm 264$ &  $3.8 \pm 0.14$ &  $1.6^{+0.07}_{-0.06}$ &  $517^{+344}_{-341}$ &      1 \\
+   HIP 33372 &           B8Vn &    06:56:25.83 &   +09:57:23.67 &   5.905 &      7.18 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 33575 &            B2V &    06:58:35.90 &   -25:24:50.97 &   5.577 &      3.78 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 34769 &            A2V &    07:11:51.86 &   -00:29:33.96 &   4.150 &      8.49 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 35180 &            A1V &    07:16:14.55 &   -15:35:08.49 &   5.454 &     12.12 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 35341 &           A5Vn &    07:18:02.22 &   +40:53:00.22 &   5.870 &     11.73 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 36393 &            A4V &    07:29:20.44 &   +28:07:05.79 &   5.072 &     18.51 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 36760 &           A1Vn &    07:33:36.48 &   +15:49:35.98 &   5.269 &      7.70 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 36812 &          A0Vnn &    07:34:15.89 &   +03:22:18.19 &   5.830 &      5.67 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 36917 &            B7V &    07:35:22.89 &   -28:22:09.57 &   4.630 &     14.72 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+     HR 2948 &            B6V &    07:38:49.38 &   -26:48:06.49 &   4.500 &   \nodata &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 37297 &          B2.5V &    07:39:27.34 &   -38:18:28.88 &   4.840 &      5.87 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 37322 &            B5V &    07:39:43.81 &   -38:08:21.44 &   5.664 &      5.70 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 37450 &            B5V &    07:41:15.81 &   -38:32:00.72 &   5.410 &      5.50 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 38538 &            A5V &    07:53:29.81 &   +26:45:56.82 &   4.977 &     14.66 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 38593 &            B2V &    07:54:11.01 &   -35:52:38.23 &   5.462 &      4.81 &  $21667 \pm 1000$ &  $4.5 \pm 0.25$ &  $7.6^{+0.74}_{-0.68}$ &        $8^{+6}_{-3}$ &  2 \\
+   HIP 38846 &          B2.5V &    07:56:57.80 &   -43:30:01.48 &   5.340 &      2.08 &  $22000 \pm 1000$ &  $4.5 \pm 0.25$ &  $7.8^{+0.74}_{-0.71}$ &        $8^{+6}_{-3}$ &  2 \\
+   HIP 39095 &            A1V &    07:59:52.05 &   -18:23:57.23 &   4.610 &     13.52 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 39236 &         B9.5Vn &    08:01:30.29 &   +16:27:19.12 &   5.990 &      6.04 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 39567 &            A1V &    08:05:04.49 &   +13:07:05.58 &   5.146 &     15.20 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 39847 &            A2V &    08:08:27.45 &   +51:30:24.01 &   4.802 &     13.04 &   $10014 \pm 340$ &  $4.0 \pm 0.14$ &  $2.2^{+0.13}_{-0.12}$ &  $193^{+132}_{-119}$ &      1 \\
+   HIP 39906 &            B5V &    08:09:01.64 &   -19:14:42.05 &   4.390 &      7.01 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 40429 &            A2V &    08:15:15.92 &   -62:54:56.32 &   5.160 &     12.90 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 40706 &            A8V &    08:18:33.31 &   -36:39:33.44 &   4.400 &     34.93 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 40881 &          B9.5V &    08:20:32.14 &   +24:01:20.32 &   5.930 &      7.13 &    $9500 \pm 300$ &  $4.0 \pm 0.25$ &  $2.1^{+0.17}_{-0.16}$ &    $71^{+239}_{-60}$ &  2 \\
+   HIP 41039 &            B1V &    08:22:31.69 &   -48:29:25.36 &   4.820 &      1.90 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 41307 &           A0Va &    08:25:39.63 &   -03:54:23.12 &   3.900 &     26.66 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 42090 &          A2Vnn &    08:34:43.88 &   +36:25:10.63 &   5.755 &      9.19 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 42129 &            B3V &    08:35:15.56 &   -58:13:29.05 &   5.241 &      3.64 &  $18000 \pm 1000$ &  $4.5 \pm 0.25$ &  $5.4^{+0.63}_{-0.54}$ &      $11^{+14}_{-5}$ &  2 \\
+   HIP 42313 &          A0Vnn &    08:37:39.37 &   +05:42:13.61 &   4.137 &     20.34 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 42334 &            A0V &    08:37:52.15 &   -26:15:18.01 &   5.270 &     14.07 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 43142 &            A3V &    08:47:14.99 &   -01:53:49.31 &   5.279 &      8.12 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 44127 &            A7V &    08:59:12.45 &   +48:02:30.57 &   3.140 &     68.92 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 44307 &            A2V &    09:01:24.13 &   +32:15:08.26 &   5.870 &      6.99 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 45336 &          B9.5V &    09:14:21.86 &   +02:18:51.34 &   3.880 &     28.74 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 45344 &            B4V &    09:14:24.48 &   -43:13:38.97 &   5.250 &      5.33 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 45688 &            A1V &    09:18:50.64 &   +36:48:09.33 &   3.820 &     26.13 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 46225 &            A4V &    09:25:27.23 &   -61:57:01.72 &   5.781 &     12.92 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 46283 &            B6V &    09:26:17.96 &   -53:22:44.07 &   5.088 &      7.60 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 46897 &          B9.5V &    09:33:26.05 &   -22:51:49.99 &   5.911 &     12.46 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 47006 &           A0Vn &    09:34:49.43 &   +52:03:05.32 &   4.479 &     12.44 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 47175 &            A7V &    09:36:49.54 &   -49:21:18.09 &   4.350 &     30.94 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 50303 &           A0Vn &    10:16:14.43 &   +29:18:37.81 &   5.490 &     12.51 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 50860 &          A5IVn &    10:23:06.33 &   +33:54:29.31 &   5.900 &     13.46 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 51362 &          B9.5V &    10:29:28.70 &   -02:44:20.69 &   5.180 &     10.13 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 51685 &           A2Vn &    10:33:30.91 &   +34:59:19.30 &   5.580 &      4.77 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 52422 &           A4Vn &    10:43:01.88 &   +26:19:32.09 &   5.517 &     20.67 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 52457 &           A3Vn &    10:43:24.96 &   +23:11:18.25 &   5.075 &     14.23 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 52638 &           A1Vn &    10:45:51.89 &   +30:40:56.33 &   5.349 &      8.53 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 52678 &          B6Vnn &    10:46:16.56 &   -64:30:52.41 &   5.340 &      6.85 &  $15000 \pm 1000$ &  $4.5 \pm 0.25$ &  $4.0^{+0.49}_{-0.50}$ &     $16^{+26}_{-10}$ &  2 \\
+   HIP 52736 &         B2.5Vn &    10:46:51.22 &   -64:23:00.50 &   4.850 &      6.79 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 52911 &            A2V &    10:49:15.43 &   +10:32:42.73 &   5.314 &      8.57 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+     HR 4259 &            A1V &    10:55:36.80 &   +24:44:59.00 &   4.500 &   \nodata &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 54849 &            A0V &    11:13:45.55 &   -00:04:10.20 &   5.399 &      6.18 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 55266 &            A2V &    11:19:07.90 &   +38:11:08.03 &   4.800 &     17.00 &    $8720 \pm 296$ &  $4.5 \pm 0.14$ &  $1.9^{+0.09}_{-0.07}$ &  $345^{+211}_{-213}$ &      1 \\
+   HIP 55434 &         B9.5Vs &  11:21:08.1934 &  +06:01:45.571 &   4.044 &     14.82 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 56034 &            A2V &    11:29:04.12 &   +39:20:13.11 &   5.354 &     15.33 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 56633 &          B9.5V &    11:36:40.91 &   -09:48:08.09 &   4.682 &     11.63 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 57328 &            A4V &    11:45:17.04 &   +08:15:29.21 &   4.845 &     26.73 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 58590 &            A5V &    12:00:52.39 &   +06:36:51.56 &   4.659 &      8.49 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 59394 &            A1V &    12:11:03.84 &   -23:36:08.72 &   5.470 &     17.00 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 59449 &            B3V &    12:11:39.12 &   -52:22:06.44 &   3.960 &      8.61 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 59819 &            A3V &    12:16:00.19 &   +14:53:56.65 &   5.090 &     16.42 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 60009 &          B2.5V &    12:18:26.25 &   -64:00:11.05 &   4.050 &      9.12 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 60030 &           A5Vn &    12:18:40.32 &   -00:47:13.87 &   5.908 &      8.73 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 60595 &            A1V &    12:25:11.76 &   -11:36:38.12 &   5.949 &     14.18 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 60710 &           B3Vn &    12:26:31.76 &   -51:27:02.29 &   4.805 &      7.28 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 60957 &            A3V &    12:29:43.24 &   +20:53:45.99 &   5.680 &     11.90 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 61558 &            A3V &    12:36:47.35 &   -05:49:54.84 &   5.880 &     14.49 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 61622 &          A1Vnn &    12:37:42.16 &   -48:32:28.69 &   3.860 &     24.85 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 62541 &            A1V &    12:48:54.21 &   +14:07:21.31 &   5.702 &      8.17 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 62576 &            A2V &    12:49:17.45 &   +27:33:08.57 &   5.780 &     10.76 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 63724 &            A0V &    13:03:33.31 &   -49:31:38.15 &   4.830 &     14.79 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 63945 &            B5V &    13:06:16.70 &   -48:27:47.85 &   4.694 &      8.36 &  $18000 \pm 1000$ &  $4.5 \pm 0.25$ &  $5.4^{+0.60}_{-0.56}$ &      $11^{+14}_{-5}$ &  2 \\
+   HIP 65198 &            A2V &    13:21:41.64 &   +02:05:14.07 &   5.693 &     14.77 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 65477 &            A5V &    13:25:13.54 &   +54:59:16.65 &   4.010 &     39.91 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 65728 &           A1Vn &    13:28:27.09 &   +59:56:44.83 &   5.400 &     14.01 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 66249 &          A2Van &    13:34:41.74 &   -00:35:45.38 &   3.380 &     44.03 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 66798 &            A2V &    13:41:29.89 &   +64:49:20.68 &   5.850 &     14.66 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 66821 &          B8.5V &    13:41:44.77 &   -54:33:33.93 &   5.010 &     12.02 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 67143 &            A0V &    13:45:36.89 &   -26:06:57.63 &   5.805 &     11.49 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 67194 &            A5V &    13:46:13.55 &   +41:05:19.48 &   5.891 &     19.03 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 67782 &           A8IV &    13:53:10.28 &   +28:38:53.28 &   5.911 &     15.21 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 68092 &            A8V &    13:56:27.88 &   +01:03:02.09 &   5.906 &     11.08 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 68520 &            A3V &    14:01:38.79 &   +01:32:40.31 &   4.244 &     14.50 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 70327 &            A0V &    14:23:22.70 &   +08:26:47.84 &   5.120 &     15.17 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 70384 &            A3V &    14:24:00.88 &   +08:14:38.30 &   5.935 &      7.38 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 70400 &            A3V &    14:24:11.34 &   +05:49:12.47 &   5.103 &     20.51 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 70915 &           B8Vn &    14:30:08.63 &   -45:19:16.88 &   5.500 &      6.84 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+     HR 5476 &            A6V &    14:40:43.94 &   +16:25:03.90 &   5.820 &   \nodata &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 71865 &            B3V &    14:41:57.59 &   -37:47:36.59 &   4.000 &      9.62 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 71974 &          B9.5V &    14:43:13.55 &   -24:59:51.91 &   5.730 &      6.56 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 72104 &          A0Vnn &    14:44:59.20 &   -35:11:30.57 &   4.923 &     15.22 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 72154 &          B9.5V &    14:45:30.20 &   +00:43:02.19 &   5.673 &      6.61 &  $10500 \pm 1000$ &  $4.5 \pm 0.25$ &  $2.3^{+0.36}_{-0.33}$ &    $32^{+101}_{-24}$ &  2 \\
+   HIP 72250 &            A1V &    14:46:28.99 &   -47:26:28.02 &   5.740 &     10.67 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 72378 &            B9V &    14:47:57.56 &   -26:38:46.16 &   5.768 &      7.29 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 72552 &            A4V &    14:49:58.40 &   +28:36:57.00 &   5.800 &     10.16 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 73049 &            A0V &    14:55:44.71 &   -33:51:20.82 &   5.318 &     12.85 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+     HR 5605 &            B5V &    15:05:07.18 &   -47:03:04.00 &   4.720 &   \nodata &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 74117 &            B3V &    15:08:50.62 &   -45:16:47.49 &   4.070 &      4.20 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 74689 &            A4V &    15:15:49.08 &   +00:22:19.70 &   5.629 &     21.67 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 75178 &           B9Vn &    15:21:48.58 &   +32:56:01.30 &   5.375 &     12.45 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 75304 &            B4V &    15:23:09.35 &   -36:51:30.55 &   4.540 &      6.28 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 76267 &            A1V &    15:34:41.27 &   +26:42:52.89 &   2.240 &     43.46 &   $10342 \pm 352$ &  $4.0 \pm 0.14$ &  $2.5^{+0.19}_{-0.16}$ &    $314^{+53}_{-94}$ &      1 \\
+   HIP 76600 &          B2.5V &    15:38:39.37 &   -29:46:39.89 &   3.644 &      8.89 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 76852 &            A1V &    15:41:33.05 &   +19:40:13.44 &   4.509 &     17.16 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 77233 &            A3V &    15:46:11.25 &   +15:25:18.59 &   3.670 &     21.03 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 77336 &            A3V &    15:47:17.32 &   +14:06:55.26 &   5.712 &     13.04 &    $8917 \pm 303$ &  $4.0 \pm 0.14$ &  $2.9^{+0.24}_{-0.21}$ &    $404^{+71}_{-71}$ &      1 \\
+   HIP 77516 &            A0V &    15:49:37.21 &   -03:25:48.73 &   3.530 &     19.23 &    $9250 \pm 300$ &  $4.0 \pm 0.25$ &  $2.1^{+0.17}_{-0.16}$ &    $74^{+275}_{-64}$ &  2 \\
+   HIP 77635 &         B1.5Vn &    15:50:58.74 &   -25:45:04.66 &   4.638 &      6.59 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 77858 &            B5V &    15:53:53.92 &   -24:31:59.37 &   5.376 &      7.76 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 78105 &            A3V &    15:56:53.50 &   -33:57:58.01 &   5.080 &     23.60 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 78106 &            B9V &    15:56:54.12 &   -33:57:51.34 &   5.550 &     21.71 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 78265 &            B1V &  15:58:51.1132 &  -26:06:50.788 &   2.910 &      5.57 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 78554 &            A3V &    16:02:17.69 &   +22:48:16.03 &   4.817 &     18.22 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 78820 &            B1V &    16:05:26.23 &   -19:48:19.63 &   2.620 &      8.07 &  $24062 \pm 1000$ &  $3.9 \pm 0.25$ &  $9.2^{+0.51}_{-0.64}$ &        $9^{+6}_{-4}$ &  2 \\
+   HIP 78821 &            B2V &    16:05:26.57 &   -19:48:06.85 &   4.890 &      8.19 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+     HR 6025 &           A0Vn &  16:06:19.6762 &  +67:48:36.480 &   5.439 &     12.85 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 78918 &         B2.5Vn &    16:06:35.55 &   -36:48:08.26 &   4.205 &      7.87 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 78933 &            B1V &  16:06:48.4269 &  -20:40:09.090 &   3.970 &      6.92 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 79005 &            B9V &    16:07:36.42 &   -12:44:43.46 &   5.757 &      8.90 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 79007 &            A7V &    16:07:37.54 &   +09:53:30.27 &   5.639 &     10.10 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 79199 &            B8V &    16:09:52.59 &   -33:32:44.90 &   5.496 &      8.00 &  $12500 \pm 1000$ &  $4.5 \pm 0.25$ &  $3.0^{+0.42}_{-0.39}$ &     $23^{+55}_{-16}$ &  2 \\
+   HIP 79387 &            A4V &    16:12:07.32 &   -08:32:51.28 &   5.435 &     12.92 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 79404 &            B2V &    16:12:18.20 &   -27:55:34.95 &   4.567 &      6.81 &  $21667 \pm 1000$ &  $4.5 \pm 0.25$ &  $7.6^{+0.75}_{-0.69}$ &        $8^{+6}_{-3}$ &  2 \\
+   HIP 79653 &            B8V &    16:15:15.32 &   -47:22:19.27 &   5.124 &      8.46 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 80460 &            A5V &    16:25:24.17 &   +37:23:38.68 &   5.540 &     13.43 &    $7810 \pm 266$ &  $3.7 \pm 0.14$ &  $1.7^{+0.11}_{-0.08}$ &  $779^{+234}_{-402}$ &      1 \\
+   HIP 80815 &            B3V &    16:30:12.48 &   -25:06:54.80 &   4.790 &      7.89 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 80883 &           A1IV &    16:30:54.82 &   +01:59:02.12 &   3.900 &     18.84 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 80991 &            A2V &    16:32:25.68 &   +60:49:23.96 &   5.910 &      8.79 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 81126 &            B9V &    16:34:06.18 &   +42:26:13.34 &   4.196 &     10.36 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 81641 &            A1V &    16:40:38.69 &   +04:13:11.23 &   5.772 &     11.11 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 82350 &            A1V &    16:49:34.66 &   +13:15:40.10 &   5.910 &      9.99 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 82514 &          B1.5V &  16:51:52.2311 &  -38:02:50.569 &   2.980 &      6.51 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 82673 &            B8V &    16:54:00.47 &   +10:09:55.30 &   4.380 &     13.30 &  $11750 \pm 1000$ &  $3.5 \pm 0.25$ &  $3.4^{+0.65}_{-0.57}$ &    $171^{+73}_{-64}$ &  2 \\
+   HIP 83635 &            B1V &    17:05:32.26 &   -00:53:31.45 &   5.610 &      2.92 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 84606 &            A2V &    17:17:40.25 &   +37:17:29.40 &   4.650 &     18.59 &    $9702 \pm 330$ &  $4.0 \pm 0.14$ &  $2.1^{+0.10}_{-0.08}$ &   $155^{+142}_{-99}$ &      1 \\
+   HIP 85290 &           A1Vn &    17:25:41.35 &   +60:02:54.23 &   5.645 &     10.32 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 85379 &            A4V &    17:26:44.24 &   +48:15:36.23 &   5.830 &      8.68 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 85385 &            B5V &    17:26:49.13 &   +20:04:51.52 &   5.510 &      5.59 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 85537 &           A8Vp &    17:28:49.65 &   +00:19:50.25 &   5.424 &     16.77 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 85727 &           B8Vn &    17:31:05.91 &   -60:41:01.85 &   3.620 &     16.48 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 85922 &            A5V &    17:33:29.85 &   -05:44:41.29 &   5.619 &     20.79 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 85998 &            A2V &    17:34:36.69 &   +09:35:12.12 &   5.810 &      9.66 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 86019 &           B8Vn &    17:34:46.35 &   -11:14:31.19 &   5.537 &      8.11 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 86782 &            A2V &    17:43:59.18 &   +53:48:06.17 &   5.760 &      6.12 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 87108 &            A1V &    17:47:53.56 &   +02:42:26.20 &   3.750 &     31.73 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 88116 &             A0 &    17:59:47.56 &   -23:48:58.09 &   4.731 &      7.85 &    $9750 \pm 300$ &  $3.5 \pm 0.25$ &  $2.7^{+0.43}_{-0.39}$ &   $305^{+68}_{-150}$ &  2 \\
+   HIP 88290 &           A2Vn &    18:01:45.20 &   +01:18:18.28 &   4.439 &     11.15 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 88818 &            A3V &    18:07:49.45 &   +26:06:04.13 &   5.870 &     20.16 &    $9162 \pm 312$ &  $4.3 \pm 0.14$ &  $2.7^{+0.25}_{-0.23}$ &    $441^{+85}_{-70}$ &      1 \\
+   HIP 88817 &            A3V &    18:07:49.50 &   +26:05:50.40 &   5.900 &     25.92 &    $9162 \pm 312$ &  $4.3 \pm 0.14$ &  $2.1^{+0.15}_{-0.12}$ &   $478^{+84}_{-175}$ &      1 \\
+   HIP 89156 &            A3V &    18:11:45.12 &   +33:26:49.41 &   5.970 &      4.21 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 89935 &            A7V &    18:21:01.02 &   +28:52:11.83 &   5.129 &     12.40 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 90052 &            A2V &    18:22:35.32 &   +12:01:46.85 &   5.980 &      7.42 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 90762 &            A2V &    18:31:04.45 &   +16:55:42.80 &   5.760 &      7.49 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 90887 &           A3Vn &    18:32:21.33 &   -39:42:14.40 &   5.162 &     14.23 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 91118 &           A0Vn &    18:35:12.60 &   +18:12:12.28 &   5.790 &      5.04 &    $9500 \pm 300$ &  $4.0 \pm 0.25$ &  $2.1^{+0.19}_{-0.15}$ &    $70^{+244}_{-60}$ &  2 \\
+   HIP 91875 &           A2Vn &    18:43:46.94 &   -38:19:24.39 &   5.120 &     15.89 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 92027 &            A1V &    18:45:28.36 &   +05:30:00.44 &   5.830 &      5.30 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 92312 &            A1V &    18:48:53.39 &   +19:19:43.40 &   5.894 &     11.41 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 92728 &          B2.5V &    18:53:43.56 &   +36:58:18.19 &   5.569 &      3.29 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 92855 &            B2V &    18:55:15.93 &   -26:17:48.21 &   2.058 &     14.32 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 92946 &            A5V &    18:56:13.18 &   +04:12:12.91 &   4.620 &     21.09 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 93225 &            B4V &    18:59:23.80 &   -12:50:25.86 &   5.516 &      6.84 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 93393 &            B5V &    19:01:17.36 &   +26:17:29.08 &   5.683 &      5.02 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 93580 &            A4V &    19:03:32.25 &   +01:49:07.57 &   5.826 &     18.22 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 93713 &           A0Vn &    19:04:55.17 &   +53:23:47.96 &   5.380 &      9.00 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 93747 &          A0Vnn &    19:05:24.61 &   +13:51:48.52 &   2.990 &     39.28 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 93805 &           B9Vn &    19:06:14.94 &   -04:52:57.20 &   3.430 &     26.37 &   $11962 \pm 407$ &  $4.2 \pm 0.14$ &  $3.5^{+0.33}_{-0.26}$ &    $195^{+19}_{-21}$ &      1 \\
+   HIP 94620 &            A4V &    19:15:17.36 &   +21:13:55.62 &   5.654 &     10.89 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 94720 &          B9.5V &    19:16:26.79 &   +14:32:40.62 &   5.630 &      7.96 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 95241 &            B9V &    19:22:38.30 &   -44:27:32.25 &   4.010 &     10.40 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 95560 &            A0V &    19:26:13.25 &   +20:05:51.84 &   5.594 &     13.72 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 95619 &          B8.5V &    19:26:56.48 &   -29:44:35.62 &   5.650 &     14.30 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 95853 &            A5V &    19:29:42.36 &   +51:43:47.21 &   3.769 &     26.88 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 96288 &            A2V &    19:34:41.26 &   +42:24:45.04 &   5.348 &      5.66 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 96840 &            B5V &    19:41:05.53 &   +13:48:56.45 &   5.988 &      0.49 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 97376 &           B8Vn &    19:47:27.78 &   +38:24:27.41 &   5.826 &      6.90 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 97496 &            A3V &    19:48:58.66 &   +19:08:31.35 &   5.000 &     12.79 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 97870 &            B5V &    19:53:17.38 &   +57:31:24.53 &   5.132 &      5.15 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 97966 &           B7Vn &    19:54:37.65 &   -08:13:38.24 &   5.710 &      6.76 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 98055 &           A4Vn &    19:55:37.79 &   +52:26:20.21 &   4.920 &     11.59 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 98194 &            B5V &    19:57:13.87 &   +40:22:04.17 &   5.453 &      2.94 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 98325 &           B9Vn &    19:58:37.98 &   +30:59:01.19 &   5.506 &      7.01 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 99080 &            B3V &    20:06:53.41 &   +23:36:51.93 &   5.064 &      6.47 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 99742 &           A1Va &    20:14:16.62 &   +15:11:51.39 &   4.947 &     21.75 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+  HIP 100069 &          B1.5V &    20:18:06.99 &   +40:43:55.50 &   5.840 &      1.68 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+  HIP 100221 &            B9V &    20:19:36.72 &   +62:15:26.90 &   5.712 &      8.63 &    $9750 \pm 300$ &  $4.5 \pm 0.25$ &  $2.2^{+0.15}_{-0.15}$ &    $34^{+110}_{-26}$ &  2 \\
+  HIP 100881 &            B4V &    20:27:19.21 &   -18:12:42.20 &   5.250 &      5.98 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+  HIP 100907 &            A3V &    20:27:34.26 &   +38:26:25.19 &   5.620 &     12.28 &    $9042 \pm 307$ &  $4.0 \pm 0.14$ &  $2.1^{+0.17}_{-0.13}$ &   $512^{+98}_{-169}$ &      1 \\
+  HIP 101123 &            A1V &    20:29:53.91 &   -18:34:59.48 &   5.906 &     15.07 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+  HIP 101589 &            A3V &    20:35:18.54 &   +14:40:27.17 &   4.664 &     14.82 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+  HIP 101716 &            B8V &    20:37:04.67 &   +26:27:43.01 &   5.589 &     10.27 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+  HIP 101867 &            A0V &    20:38:31.34 &   +21:12:04.25 &   4.820 &     14.01 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+  HIP 101909 &            B3V &    20:39:04.97 &   +15:50:17.52 &   5.980 &      2.42 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+  HIP 102487 &            A1V &    20:46:09.99 &   -21:30:50.52 &   5.913 &     12.37 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+  HIP 103298 &            A5V &    20:55:38.57 &   +12:34:06.81 &   5.540 &     16.53 &    $9093 \pm 309$ &  $4.1 \pm 0.14$ &  $2.0^{+0.13}_{-0.11}$ &  $393^{+151}_{-208}$ &      1 \\
+  HIP 104019 &            A5V &    21:04:24.30 &   -19:51:17.97 &   4.840 &     20.20 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+  HIP 104105 &           B8Vn &    21:05:29.27 &   +78:07:35.02 &   5.915 &      8.10 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+  HIP 104139 &            A1V &    21:05:56.83 &   -17:13:58.30 &   4.070 &     20.11 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+  HIP 104365 &            A0V &    21:08:33.63 &   -21:11:37.22 &   5.280 &     18.14 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+  HIP 105140 &            A1V &    21:17:56.28 &   -32:10:21.15 &   4.721 &     17.90 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+  HIP 105282 &            B6V &    21:19:28.75 &   +49:30:37.06 &   5.740 &      5.98 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+  HIP 105891 &            B6V &    21:26:44.97 &   +52:53:54.73 &   5.989 &      7.28 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+  HIP 105942 &            B3V &    21:27:21.37 &   +37:07:00.47 &   5.289 &      2.50 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+  HIP 105966 &            A1V &    21:27:40.06 &   +27:36:30.94 &   5.389 &     17.14 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+  HIP 105972 &            B7V &    21:27:46.14 &   +66:48:32.74 &   5.407 &      4.05 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+  HIP 106711 &           A3Vn &    21:36:56.98 &   +40:24:48.67 &   5.052 &     15.19 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+  HIP 106786 &            A7V &    21:37:45.11 &   -07:51:15.13 &   4.690 &     18.26 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+  HIP 107517 &            A1V &    21:46:32.10 &   -11:21:57.44 &   5.570 &     11.58 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+  HIP 107608 &            A2V &    21:47:44.15 &   -30:53:53.90 &   5.016 &     10.16 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+  HIP 108294 &           A2Vn &    21:56:22.77 &   -37:15:13.16 &   5.457 &      9.71 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+  HIP 108339 &          A2Vnn &    21:56:56.37 &   +12:04:35.37 &   5.544 &      8.14 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+  HIP 109056 &           B9Vn &    22:05:34.67 &   +28:57:50.32 &   5.700 &      9.40 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+  HIP 109139 &            B8V &    22:06:26.23 &   -13:52:10.86 &   4.270 &     18.62 &   $12641 \pm 430$ &  $4.3 \pm 0.14$ &  $3.2^{+0.19}_{-0.17}$ &    $122^{+38}_{-60}$ &      1 \\
+  HIP 109521 &            A5V &    22:11:09.89 &   +50:49:24.26 &   5.386 &     17.81 &    $8420 \pm 286$ &  $4.2 \pm 0.14$ &  $2.0^{+0.19}_{-0.16}$ &  $728^{+107}_{-105}$ &      1 \\
+  HIP 109831 &          A2Vnn &    22:14:44.37 &   +42:57:14.07 &   5.720 &     12.14 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+  HIP 110838 &           B9Vn &    22:27:19.97 &   -64:57:58.88 &   4.495 &     13.00 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+  HIP 110935 &            A4V &    22:28:37.67 &   -67:29:20.62 &   5.570 &     23.19 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+  HIP 111056 &            A3V &    22:29:52.98 &   +78:49:27.43 &   5.460 &     13.31 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+  HIP 111068 &          B9.5V &    22:30:01.81 &   +32:34:21.50 &   5.650 &      9.05 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+  HIP 111169 &            A1V &    22:31:17.50 &   +50:16:56.97 &   3.770 &     31.79 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+  HIP 111841 &            O9V &    22:39:15.68 &   +39:03:00.97 &   4.880 &      1.89 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+  HIP 112029 &            B8V &    22:41:27.73 &   +10:49:52.64 &   3.410 &   \nodata &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+  HIP 113788 &            A1V &    23:02:36.38 &   +42:45:28.06 & \nodata &      7.74 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+  HIP 114520 &           A5Vn &    23:11:44.19 &   +08:43:12.40 &   5.157 &     13.46 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+  HIP 114822 &            A2V &    23:15:34.26 &   -03:29:46.96 &   5.550 &     14.04 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+  HIP 115115 &            A0V &    23:18:57.68 &   -09:36:38.70 &   5.001 &     12.47 &   $10671 \pm 363$ &  $4.2 \pm 0.14$ &  $2.6^{+0.19}_{-0.16}$ &    $285^{+39}_{-80}$ &      1 \\
+  HIP 116247 &            A0V &    23:33:16.62 &   -20:54:52.21 &   4.709 &     11.11 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+  HIP 116582 &            B8V &    23:37:32.04 &   +44:25:44.37 &   5.817 &      4.04 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+  HIP 116611 &           A0Vn &    23:37:56.80 &   +18:24:02.40 &   5.482 &     14.01 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+  HIP 116631 &            B8V &    23:38:08.20 &   +43:16:05.06 &   4.290 &      6.53 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+  HIP 116805 &            A0V &    23:40:24.51 &   +44:20:02.16 &   4.140 &     19.37 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+  HIP 116971 &            B9V &    23:42:43.34 &   -14:32:41.65 &   4.483 &     21.96 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+  HIP 117089 &            B9V &    23:44:12.08 &   -18:16:36.97 &   5.235 &      8.61 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+  HIP 117371 &           A1Vn &    23:47:54.77 &   +67:48:24.51 &   5.048 &     10.76 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+  HIP 117452 &          A0Vnp &    23:48:55.55 &   -28:07:48.97 &   4.570 &     23.73 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+  HIP 118121 &            A1V &    23:57:35.08 &   -64:17:53.63 &   5.002 &     21.08 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+  HIP 118243 &            B1V &    23:59:00.54 &   +55:45:17.74 &   4.997 &      0.72 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata
+
+\enddata
+\tablecomments{The spectral types, coordinates, V-band magnitudes, and parallax measurements are taken from the Simbad database; the spectral type given is that of the brightest star if part of a known multiple system.
+The "Ref" column denotes the reference for the stellar effective temperature, surface gravity, mass, and age.
+The references are: [1]: \citep{David2015}; [2]: This study.}
+\label{tab:sample}
+\end{deluxetable*}
+
+\clearpage
+%\newpage
+
+%\LongTables
+\begin{deluxetable}{|l|rlrr|}
 \tabletypesize{\small}
 \tablewidth{0pt}
-\tablecaption{Target Lists and Observation Log}
+\tablecaption{Spectroscopic Observation Log}
 \tablehead{
-      \colhead{} & \colhead{} & \colhead{} & \colhead{} &  \colhead{MJD} & \colhead{}  & \colhead{exptime} & \colhead{} \\
-       \colhead{star} & \colhead{SpT} & \colhead{RA} & \colhead{DEC} &  \colhead{(JD-2450000)} &   \colhead{instrument} & \colhead{(sec)} & \colhead{snr}
+      \colhead{} &  \colhead{MJD} & \colhead{}  & \colhead{exptime} & \colhead{} \\
+       \colhead{star} &  \colhead{(JD-2450000)} &   \colhead{instrument} & \colhead{(sec)} & \colhead{snr}
        }
@@
 \startdata
-     HIP 813 &           B9Vn &     00:10:2.20 &   +11:08:44.93 &  6618.58 &       TS23 &      557 &  1810 \\
-    HIP 1191 &          B8.5V &    00:14:54.52 &   -09:34:10.45 &  6552.60 &     CHIRON &     1200 &   320 \\
-    HIP 1366 &            A2V &     00:17:5.50 &   +38:40:53.89 &  6585.73 &       TS23 &      274 &  1790 \\
-    HIP 1647 &            B9V &    00:20:39.04 &   -69:37:29.68 &  6510.74 &     CHIRON &     1105 &   630 \\
-    HIP 2381 &            A3V &    00:30:22.65 &   -23:47:15.65 &  6874.71 &     CHIRON &      505 &   580 \\
-    HIP 2505 &           B8Vn &    00:31:46.36 &   +54:31:20.23 &  6586.71 &       TS23 &      235 &  1700 \\
-    HIP 2505 &           B8Vn &    00:31:46.36 &   +54:31:20.23 &  6962.71 &       TS23 &      804 &  1960 \\
-    HIP 2505 &           B8Vn &    00:31:46.36 &   +54:31:20.23 &  6945.71 &     IGRINS &      224 &   210 \\
-    HIP 2548 &          B9.5V &    00:32:23.78 &   +06:57:19.66 &  7240.93 &     IGRINS &      360 &   100 \\
-    HIP 2548 &          B9.5V &    00:32:23.78 &   +06:57:19.66 &  6516.84 &        HRS &      412 &  1070 \\
-    HIP 2912 &            B5V &    00:36:52.85 &    +33:43:9.64 &  7238.96 &     IGRINS &      367 &   130 \\
-    HIP 2912 &            B5V &    00:36:52.85 &    +33:43:9.64 &  6583.78 &       TS23 &      199 &  2460 \\
-    HIP 3300 &            B2V &     00:42:3.90 &   +50:30:45.09 &  6299.55 &       TS23 &      689 &  1010 \\
-    HIP 3478 &            B5V &    00:44:26.19 &   +47:51:50.34 &  6963.63 &       TS23 &     1200 &  1020 \\
-    HIP 3478 &            B5V &    00:44:26.19 &   +47:51:50.34 &  7288.82 &     IGRINS &      540 &    30 \\
-    HIP 3478 &            B5V &    00:44:26.19 &   +47:51:50.34 &  6669.53 &       TS23 &      743 &  1870 \\
-    HIP 3478 &            B5V &    00:44:26.19 &   +47:51:50.34 &  6945.72 &     IGRINS &      224 &   150 \\
-    HIP 3741 &            B9V &     00:48:1.06 &   -21:43:20.99 &  7174.89 &     CHIRON &     3981 &   430 \\
-    HIP 3741 &            B9V &     00:48:1.06 &   -21:43:20.99 &  7175.90 &     CHIRON &     3561 &   420 \\
-    HIP 3881 &            B5V &    00:49:48.85 &   +41:04:44.08 &  6585.70 &       TS23 &      222 &  1690 \\
-    HIP 3881 &            B5V &    00:49:48.85 &   +41:04:44.08 &  6964.60 &       TS23 &     1200 &   710 \\
-    HIP 3881 &            B5V &    00:49:48.85 &   +41:04:44.08 &  6945.74 &     IGRINS &      224 &   200 \\
-    HIP 4436 &            A5V &    00:56:45.21 &   +38:29:57.64 &  6585.76 &       TS23 &      129 &  1940 \\
-    HIP 5131 &           A1Vn &    01:05:40.96 &   +21:28:23.45 &  6587.70 &       TS23 &      655 &  1780 \\
-    HIP 5131 &           A1Vn &    01:05:40.96 &   +21:28:23.45 &  7083.57 &     IGRINS &      930 &    70 \\
-    HIP 5131 &           A1Vn &    01:05:40.96 &   +21:28:23.45 &  6847.89 &     IGRINS &     1600 &   110 \\
-    HIP 5132 &           A0Vn &    01:05:41.71 &   +21:27:55.60 &  6587.77 &       TS23 &      535 &  1550 \\
-    HIP 5132 &           A0Vn &    01:05:41.71 &   +21:27:55.60 &  6847.89 &     IGRINS &      480 &   110 \\
-    HIP 5310 &            A3V &    01:07:57.16 &   +20:44:20.83 &  6945.75 &     IGRINS &      224 &   200 \\
-    HIP 5361 &            B8V &    01:08:33.47 &   +58:15:48.41 &  6523.84 &        HRS &     1000 &   810 \\
-    HIP 5518 &          A0Vnn &    01:10:39.32 &   +68:46:43.04 &  7238.94 &     IGRINS &      540 &    80 \\
-    HIP 5518 &          A0Vnn &    01:10:39.32 &   +68:46:43.04 &  6945.77 &     IGRINS &      224 &   160 \\
-    HIP 5626 &            A3V &    01:12:16.82 &   +79:40:26.27 &  6945.88 &     IGRINS &      224 &   160 \\
-    HIP 7345 &            A1V &    01:34:37.78 &   -15:40:34.90 &  6888.76 &     CHIRON &     1080 &   480 \\
-    HIP 7345 &            A1V &    01:34:37.78 &   -15:40:34.90 &  6887.76 &     CHIRON &      706 &   540 \\
-    HIP 8016 &            B9V &    01:42:55.86 &   +70:37:21.09 &  6522.96 &        HRS &      328 &   580 \\
-    HIP 8704 &          B1.5V &    01:51:59.32 &   +55:08:50.58 &  6506.90 &        HRS &      365 &   420 \\
-    HIP 8704 &          B1.5V &    01:51:59.32 &   +55:08:50.58 &  7084.57 &     IGRINS &      960 &    30 \\
-    HIP 8704 &          B1.5V &    01:51:59.32 &   +55:08:50.58 &  7237.93 &     IGRINS &      720 &    90 \\
-      HR 545 &            B9V &    01:53:31.77 &   +19:17:46.27 &  6668.56 &       TS23 &      597 &  1920 \\
-      HR 545 &            B9V &    01:53:31.77 &   +19:17:46.27 &  6586.75 &       TS23 &      265 &  1710 \\
-      HR 545 &            B9V &    01:53:31.77 &   +19:17:46.27 &  6945.81 &     IGRINS &      224 &   230 \\
-    HIP 9312 &           A0Vn &    01:59:38.04 &   +64:37:17.76 &  6586.78 &       TS23 &      419 &  1750 \\
-    HIP 9564 &           A1Vn &    02:02:52.48 &    +64:54:5.27 &  6945.78 &     IGRINS &      224 &   140 \\
-      HR 604 &        B8V+A0V &    02:03:54.72 &   +42:19:51.41 &  6585.86 &       TS23 &      349 &  1650 \\
-   HIP 10320 &            B9V &    02:12:54.47 &   -30:43:25.77 &  6532.80 &     CHIRON &     1020 &   550 \\
-   HIP 10670 &          A1Vnn &    02:17:18.87 &   +33:50:49.90 &  6618.68 &       TS23 &      141 &  1810 \\
-   HIP 10732 &           A1Vn &     02:18:7.54 &    +19:54:4.19 &  6945.82 &     IGRINS &      224 &   180 \\
-   HIP 10732 &           A1Vn &     02:18:7.54 &    +19:54:4.19 &  7083.56 &     IGRINS &      240 &   110 \\
-   HIP 11345 &            A0V &    02:25:57.01 &   -12:17:25.71 &  6894.90 &     CHIRON &      540 &   520 \\
-   HIP 12332 &            A7V &    02:38:48.99 &   +21:57:41.06 &  6677.54 &       TS23 &     1107 &  1530 \\
-   HIP 12332 &            A7V &    02:38:48.99 &   +21:57:41.06 &  6947.79 &     IGRINS &      224 &   170 \\
-   HIP 12706 &       A2Vn+F4V &    02:43:18.04 &    +03:14:8.94 &  6584.86 &       TS23 &      362 &   990 \\
-   HIP 12706 &       A2Vn+F4V &    02:43:18.04 &    +03:14:8.94 &  6946.84 &     IGRINS &      224 &   150 \\
-   HIP 12719 &            B3V &    02:43:27.11 &   +27:42:25.72 &  6583.87 &       TS23 &      264 &  1720 \\
-   HIP 12803 &           B9Vn &    02:44:32.97 &   +15:18:42.71 &  6676.53 &       TS23 &      452 &  1410 \\
-   HIP 12803 &           B9Vn &    02:44:32.97 &   +15:18:42.71 &  6947.80 &     IGRINS &      224 &   140 \\
-   HIP 12803 &           B9Vn &    02:44:32.97 &   +15:18:42.71 &  7240.95 &     IGRINS &      780 &   120 \\
-   HIP 13165 &            B6V &    02:49:17.56 &   +17:27:51.52 &  6518.91 &        HRS &      275 &   850 \\
-   HIP 13202 &            A0V &    02:49:54.18 &   -27:56:31.14 &  6910.83 &     CHIRON &      580 &   570 \\
-   HIP 13209 &           B8Vn &    02:49:59.03 &   +27:15:37.83 &  6618.66 &       TS23 &      143 &  1880 \\
-   HIP 13327 &            B7V &    02:51:29.59 &   +15:04:55.45 &  6670.54 &       TS23 &     1200 &  1800 \\
-   HIP 13717 &            A3V &    02:56:37.42 &   -03:42:44.35 &  6917.83 &     CHIRON &      644 &   550 \\
-   HIP 13717 &            A3V &    02:56:37.42 &   -03:42:44.35 &  6970.75 &     CHIRON &      703 &   550 \\
-   HIP 13879 &           A2Vn &    02:58:45.67 &   +39:39:45.81 &  6945.79 &     IGRINS &      224 &   260 \\
-   HIP 13879 &           A2Vn &    02:58:45.67 &   +39:39:45.81 &  6681.68 &       TS23 &      930 &   230 \\
-   HIP 13879 &           A2Vn &    02:58:45.67 &   +39:39:45.81 &  6618.70 &       TS23 &      265 &  1490 \\
-   HIP 14043 &            B7V &    03:00:52.21 &    +52:21:6.22 &  6523.92 &        HRS &      400 &   620 \\
-   HIP 14143 &            B7V &    03:02:22.52 &   +04:21:10.39 &  6518.94 &        HRS &      462 &   900 \\
-   HIP 14293 &            A5V &    03:04:16.52 &    -07:36:3.08 &  6919.89 &     CHIRON &      800 &   240 \\
-   HIP 14576 &            B8V &    03:08:10.13 &   +40:57:20.33 &  6583.83 &       TS23 &       40 &  1030 \\
-   HIP 14576 &            B8V &    03:08:10.13 &   +40:57:20.33 &  6582.92 &       TS23 &       36 &  2050 \\
-   HIP 14764 &            B8V &    03:10:38.79 &   +11:52:21.44 &  6679.53 &       TS23 &      532 &  1370 \\
-   HIP 14764 &            B8V &    03:10:38.79 &   +11:52:21.44 &  6946.80 &     IGRINS &      360 &   150 \\
-   HIP 14862 &          A2Vnn &    03:11:56.27 &   +74:23:37.17 &  6945.86 &     IGRINS &      224 &   180 \\
-   HIP 14862 &          A2Vnn &    03:11:56.27 &   +74:23:37.17 &  7084.60 &     IGRINS &     1200 &   120 \\
-   HIP 15110 &            A1V &    03:14:54.10 &   +21:02:40.01 &  6946.83 &     IGRINS &      224 &   120 \\
-   HIP 15338 &            B8V &    03:17:47.35 &   +44:01:30.08 &  6523.90 &        HRS &      570 &   690 \\
-   HIP 15404 &            B3V &    03:18:37.74 &   +50:13:19.83 &  6517.92 &        HRS &      205 &   620 \\
-   HIP 15444 &            B5V &     03:19:7.64 &   +50:05:41.88 &  6582.94 &       TS23 &      340 &  1790 \\
-   HIP 16147 &            B5V &     03:28:3.07 &   +49:03:46.32 &  6299.59 &       TS23 &      735 &  1300 \\
-   HIP 16210 &           B6Vn &    03:28:52.33 &   +49:50:54.17 &  6676.58 &       TS23 &      406 &  1440 \\
-   HIP 16210 &           B6Vn &    03:28:52.33 &   +49:50:54.17 &  6945.84 &     IGRINS &      224 &   160 \\
-   HIP 16244 &            B3V &    03:29:22.05 &   +49:30:32.21 &  6583.84 &       TS23 &      311 &  1750 \\
-   HIP 16244 &            B3V &    03:29:22.05 &   +49:30:32.21 &  6945.83 &     IGRINS &      224 &   230 \\
-   HIP 16285 &            A5V &    03:29:55.15 &    -42:38:3.32 &  6933.84 &     CHIRON &      767 &   570 \\
-   HIP 16322 &           A0Vn &    03:30:24.47 &   +11:20:11.19 &  6944.72 &     CHIRON &      680 &   410 \\
-   HIP 16322 &           A0Vn &    03:30:24.47 &   +11:20:11.19 &  6946.82 &     IGRINS &      224 &   170 \\
-   HIP 16340 &            B8V &    03:30:36.95 &   +48:06:12.95 &  6678.54 &       TS23 &      570 &  1410 \\
-   HIP 16599 &            A3V &    03:33:39.06 &   +54:58:29.49 &  6945.85 &     IGRINS &      224 &   170 \\
-   HIP 16611 &            B9V &    03:33:47.28 &   -21:37:58.38 &  6946.85 &     IGRINS &      224 &   210 \\
-   HIP 16611 &            B9V &    03:33:47.28 &   -21:37:58.38 &  6522.88 &     CHIRON &      255 &   580 \\
-   HIP 17457 &           B7IV &    03:44:30.51 &   -01:09:47.14 &  6531.82 &     CHIRON &     1005 &   520 \\
-   HIP 17563 &            B3V &    03:45:40.44 &   +06:02:59.97 &  6538.82 &     CHIRON &     1088 &   400 \\
-   HIP 17527 &            B8V &     03:45:9.74 &   +24:50:21.34 &  6947.82 &     IGRINS &      224 &   120 \\
-   HIP 17527 &            B8V &     03:45:9.74 &   +24:50:21.34 &  6517.93 &        HRS &      429 &   670 \\
-   HIP 17527 &            B8V &     03:45:9.74 &   +24:50:21.34 &  6963.91 &       TS23 &      818 &   470 \\
-   HIP 18141 &            B8V &    03:52:41.66 &   -05:21:40.54 &  6678.59 &       TS23 &      605 &  1430 \\
-   HIP 18396 &            B6V &    03:55:58.17 &   +47:52:17.12 &  6516.94 &        HRS &      259 &   510 \\
-   HIP 18724 &            B3V &    04:00:40.82 &   +12:29:25.22 &  6299.62 &       TS23 &      226 &  1220 \\
-   HIP 18788 &            B5V &    04:01:32.05 &   -01:32:58.78 &  6535.81 &     CHIRON &     1039 &   180 \\
-   HIP 18805 &            B5V &    04:01:46.14 &   +09:59:52.84 &  6585.78 &       TS23 &      631 &  1760 \\
-   HIP 19799 &           B9Vn &    04:14:36.23 &   +10:00:41.05 &  6668.63 &       TS23 &     1200 &  1900 \\
-   HIP 19949 &           A2Vn &    04:16:43.09 &   +53:36:42.47 &  6945.90 &     IGRINS &      224 &   220 \\
-   HIP 19949 &           A2Vn &    04:16:43.09 &   +53:36:42.47 &  7084.62 &     IGRINS &      960 &    30 \\
-   HIP 19968 &            B7V &    04:16:53.56 &   +61:50:59.97 &  6676.62 &       TS23 &      524 &  1390 \\
-   HIP 20264 &            A0V &    04:20:39.01 &   -20:38:22.64 &  6718.53 &     CHIRON &      860 &   410 \\
-   HIP 20380 &            A3V &    04:21:51.81 &   +56:30:22.74 &  6945.89 &     IGRINS &      224 &   180 \\
-   HIP 20380 &            A3V &    04:21:51.81 &   +56:30:22.74 &  7084.67 &     IGRINS &     1200 &    30 \\
-   HIP 20430 &          B9Vnn &    04:22:34.94 &   +25:37:45.54 &  6520.95 &        HRS &      360 &   710 \\
-   HIP 20507 &            A2V &    04:23:40.85 &   -03:44:43.68 &  6719.50 &     CHIRON &      715 &   470 \\
-   HIP 20579 &            B8V &    04:24:29.16 &   +34:07:50.73 &  6517.96 &        HRS &      490 &   830 \\
-   HIP 20789 &            B7V &    04:27:17.45 &   +22:59:46.80 &  6946.86 &     IGRINS &      224 &   150 \\
-   HIP 20789 &            B7V &    04:27:17.45 &   +22:59:46.80 &  6586.83 &       TS23 &      524 &  1610 \\
-   HIP 21589 &            A6V &     04:38:9.46 &   +12:30:39.01 &  6962.94 &       TS23 &      220 &  1020 \\
-   HIP 21589 &            A6V &     04:38:9.46 &   +12:30:39.01 &  7065.63 &     CHIRON &      754 &   290 \\
-   HIP 21589 &            A6V &     04:38:9.46 &   +12:30:39.01 &  6948.96 &     IGRINS &      112 &   140 \\
-   HIP 21683 &           A5Vn &    04:39:16.50 &    +15:55:4.70 &  6948.98 &     IGRINS &      230 &   110 \\
-   HIP 21683 &           A5Vn &    04:39:16.50 &    +15:55:4.70 &  6962.97 &       TS23 &      335 &  1040 \\
-   HIP 21819 &            A2V &    04:41:19.76 &   +28:36:53.98 &  6679.64 &       TS23 &      466 &  1480 \\
-   HIP 21928 &           A1Vn &    04:42:54.33 &   +43:21:54.53 &  6677.63 &       TS23 &     1124 &  1470 \\
-   HIP 22028 &            A1V &     04:44:7.98 &   -18:39:59.71 &  6947.90 &     IGRINS &      240 &   140 \\
-   HIP 22509 &           A1Vn &    04:50:36.72 &    +08:54:0.65 &  6667.62 &       TS23 &     1200 &  1100 \\
-   HIP 22509 &           A1Vn &    04:50:36.72 &    +08:54:0.65 &  7126.51 &     CHIRON &     2612 &   440 \\
-   HIP 22833 &            A3V &    04:54:46.90 &   +11:25:33.63 &  6679.60 &       TS23 &      521 &  1520 \\
-   HIP 22833 &            A3V &    04:54:46.90 &   +11:25:33.63 &  6946.87 &     IGRINS &      224 &   140 \\
-   HIP 22840 &            B5V &    04:54:50.71 &    +00:28:1.81 &  6678.64 &       TS23 &      528 &  1380 \\
-   HIP 22913 &            B9V &    04:55:50.15 &   +15:02:25.00 &  6585.74 &     CHIRON &     1200 &   230 \\
-   HIP 22958 &            B6V &    04:56:24.19 &   -05:10:16.87 &  6551.79 &     CHIRON &     1200 &   340 \\
-   HIP 22958 &            B6V &    04:56:24.19 &   -05:10:16.87 &  6943.77 &     CHIRON &      650 &   320 \\
-   HIP 23362 &            B9V &    05:01:25.58 &    -20:03:6.91 &  6548.87 &     CHIRON &      725 &   520 \\
-   HIP 23362 &            B9V &    05:01:25.58 &    -20:03:6.91 &  6946.93 &     IGRINS &      240 &   180 \\
-   HIP 23916 &            B8V &    05:08:20.19 &   -08:39:55.17 &  6555.82 &     CHIRON &     1200 &    40 \\
-   HIP 23916 &            B8V &    05:08:20.19 &   -08:39:55.17 &  6946.95 &     IGRINS &      280 &   140 \\
-   HIP 24244 &         B7.5Vn &    05:12:17.90 &    -11:52:9.19 &  6949.84 &     CHIRON &      370 &   560 \\
-   HIP 24244 &         B7.5Vn &    05:12:17.90 &    -11:52:9.19 &  6554.91 &     CHIRON &      488 &   330 \\
-   HIP 24327 &            B7V &    05:13:13.88 &   -12:56:28.65 &  6529.88 &     CHIRON &      277 &   560 \\
-   HIP 24505 &            B9V &    05:15:24.37 &   -26:56:36.63 &  7036.69 &     CHIRON &     2045 &   480 \\
-   HIP 24902 &            A3V &    05:20:14.67 &   +41:05:10.35 &  6946.88 &     IGRINS &      224 &   180 \\
-   HIP 25048 &            B3V &    05:21:48.42 &   +41:48:16.46 &  6299.69 &       TS23 &      900 &   420 \\
- ADS 3962 AB &           B1Vn &    05:22:50.30 &   +03:32:52.00 &  6946.92 &     IGRINS &      280 &   170 \\
-   HIP 25143 &            A3V &    05:22:50.31 &   +41:01:45.33 &  7084.65 &     IGRINS &      960 &    80 \\
-   HIP 25143 &            A3V &    05:22:50.31 &   +41:01:45.33 &  6946.89 &     IGRINS &      224 &   180 \\
-   HIP 25280 &            A0V &    05:24:28.49 &   -16:58:32.81 &  6950.75 &     CHIRON &      597 &   540 \\
-   HIP 25280 &            A0V &    05:24:28.49 &   -16:58:32.81 &  6947.91 &     IGRINS &      240 &   130 \\
-   HIP 25281 &        B1V+B2: &    05:24:28.62 &   -02:23:49.73 &  6299.71 &       TS23 &      583 &  1120 \\
-   HIP 25555 &         B9.5Vn &    05:27:45.61 &   +15:52:26.58 &  6670.63 &       TS23 &      600 &  1950 \\
-   HIP 25608 &            A1V &    05:28:15.34 &   -37:13:50.75 &  6718.62 &     CHIRON &     1030 &   360 \\
-   HIP 25695 &           B9Vn &    05:29:16.50 &    +25:09:0.78 &  6669.65 &       TS23 &     1200 &  1860 \\
-   HIP 25790 &           A3Vn &    05:30:26.16 &   +15:21:37.61 &  6946.90 &     IGRINS &      224 &   160 \\
-   HIP 25813 &            B5V &    05:30:47.05 &   +05:56:53.29 &  7083.58 &     IGRINS &     1020 &   200 \\
-   HIP 25813 &            B5V &    05:30:47.05 &   +05:56:53.29 &  6544.88 &     CHIRON &      384 &   260 \\
-   HIP 26063 &            B1V &    05:33:31.45 &   -01:09:21.87 &  6582.80 &     CHIRON &     1139 &   250 \\
-   HIP 26093 &            B3V &    05:33:54.28 &   +14:18:20.08 &  6946.91 &     IGRINS &      280 &   150 \\
-   HIP 26093 &            B3V &    05:33:54.28 &   +14:18:20.08 &  6676.66 &       TS23 &      525 &  1380 \\
-   HIP 26093 &            B3V &    05:33:54.28 &   +14:18:20.08 &  7084.72 &     IGRINS &     1800 &    90 \\
-   HIP 26126 &            A2V &    05:34:16.77 &    +03:46:0.82 &  6946.96 &     IGRINS &      240 &   170 \\
-   HIP 26126 &            A2V &    05:34:16.77 &    +03:46:0.82 &  6721.50 &     CHIRON &      507 &   450 \\
-   HIP 26126 &            A2V &    05:34:16.77 &    +03:46:0.82 &  6948.81 &     CHIRON &      550 &   360 \\
-     HR 1880 &          B0.5V &     05:35:8.48 &    +09:56:6.10 &  6594.74 &     CHIRON &      472 &   540 \\
-   HIP 26563 &           A4Vn &    05:38:53.08 &   -07:12:46.18 &  6677.68 &       TS23 &      502 &  1550 \\
-   HIP 27100 &            A7V &    05:44:46.38 &    -65:44:7.90 &  6692.59 &     CHIRON &      294 &   680 \\
-   HIP 27100 &            A7V &    05:44:46.38 &    -65:44:7.90 &  6727.54 &     CHIRON &      177 &   560 \\
-   HIP 27321 &            A6V &    05:47:17.09 &   -51:03:59.44 &  6696.62 &     CHIRON &      178 &   640 \\
-   HIP 27713 &           A2Vn &     05:52:7.73 &   -09:02:30.84 &  6946.97 &     IGRINS &      240 &   150 \\
-   HIP 28691 &            B8V &    06:03:27.37 &   +19:41:26.02 &  6298.78 &       TS23 &      646 &  1300 \\
-   HIP 28756 &          B2.5V &    06:04:20.27 &   -32:10:20.74 &  6571.74 &     CHIRON &     1200 &   320 \\
-   HIP 28910 &            A0V &     06:06:9.32 &    -14:56:6.92 &  6693.61 &     CHIRON &      343 &   560 \\
-   HIP 29150 &            A0V &    06:08:57.87 &   -22:25:38.68 &  6697.63 &     CHIRON &      950 &   380 \\
-   HIP 29151 &           A3Vn &    06:08:57.90 &   +02:29:58.89 &  6946.99 &     IGRINS &      264 &   170 \\
-   HIP 29151 &           A3Vn &    06:08:57.90 &   +02:29:58.89 &  6953.82 &     CHIRON &      617 &   540 \\
-   HIP 29735 &            B9V &    06:15:44.89 &    -13:43:6.29 &  6559.80 &     CHIRON &      803 &   380 \\
-   HIP 29735 &            B9V &    06:15:44.89 &    -13:43:6.29 &  6946.98 &     IGRINS &      240 &   170 \\
-   HIP 29997 &           A0Vn &    06:18:50.78 &   +69:19:11.23 &  6679.70 &       TS23 &      415 &  1460 \\
-   HIP 30069 &            B9V &    06:19:40.96 &   -34:23:47.73 &  6573.75 &     CHIRON &     1200 &   250 \\
-   HIP 30073 &          B2.5V &  06:19:42.7989 &  -07:49:22.473 &  6581.82 &     CHIRON &     1011 &   280 \\
-   HIP 30666 &           A3Vn &    06:26:39.59 &   -01:30:26.41 &  6947.00 &     IGRINS &      280 &   160 \\
-   HIP 30788 &            B4V &    06:28:10.21 &   -32:34:48.25 &  6574.75 &     CHIRON &      488 &   340 \\
-   HIP 31278 &           B5Vn &    06:33:37.92 &   -01:13:12.55 &  7084.69 &     IGRINS &      960 &    90 \\
-   HIP 31278 &           B5Vn &    06:33:37.92 &   -01:13:12.55 &  6668.71 &       TS23 &      797 &  1920 \\
-   HIP 31278 &           B5Vn &    06:33:37.92 &   -01:13:12.55 &  6947.01 &     IGRINS &      280 &   170 \\
-   HIP 31362 &            B8V &    06:34:35.33 &   -32:42:58.51 &  6598.72 &     CHIRON &     1200 &   250 \\
-   HIP 31434 &          A0Vnn &    06:35:12.06 &   +28:01:20.32 &  6676.71 &       TS23 &      611 &  1480 \\
-   HIP 32474 &          B9.5V &    06:46:39.02 &   -10:06:26.50 &  6592.74 &     CHIRON &     1200 &   340 \\
-   HIP 32607 &            A7V &    06:48:11.46 &   -61:56:29.00 &  7037.75 &     CHIRON &       56 &   210 \\
-   HIP 32607 &            A7V &    06:48:11.46 &   -61:56:29.00 &  7039.62 &     CHIRON &       49 &   210 \\
-   HIP 32607 &            A7V &    06:48:11.46 &   -61:56:29.00 &  6724.56 &     CHIRON &       67 &   560 \\
-   HIP 33372 &           B8Vn &    06:56:25.83 &   +09:57:23.67 &  6948.00 &     IGRINS &      320 &   110 \\
-   HIP 33372 &           B8Vn &    06:56:25.83 &   +09:57:23.67 &  6678.72 &       TS23 &      720 &  1380 \\
-   HIP 33575 &            B2V &    06:58:35.90 &   -25:24:50.97 &  6599.72 &     CHIRON &     1200 &   390 \\
-   HIP 34769 &            A2V &    07:11:51.86 &   -00:29:33.96 &  6677.75 &       TS23 &      279 &  1520 \\
-   HIP 35180 &            A1V &    07:16:14.55 &    -15:35:8.49 &  6696.76 &     CHIRON &      925 &   290 \\
-   HIP 35341 &           A5Vn &     07:18:2.22 &    +40:53:0.22 &  6680.75 &       TS23 &      833 &  1070 \\
-   HIP 36393 &            A4V &    07:29:20.44 &    +28:07:5.79 &  6676.76 &       TS23 &      616 &  1550 \\
-   HIP 36393 &            A4V &    07:29:20.44 &    +28:07:5.79 &  6670.76 &       TS23 &      494 &  1400 \\
-   HIP 36760 &           A1Vn &    07:33:36.48 &   +15:49:35.98 &  7084.74 &     IGRINS &      720 &   150 \\
-   HIP 36760 &           A1Vn &    07:33:36.48 &   +15:49:35.98 &  7037.76 &     CHIRON &     4284 &   370 \\
-   HIP 36760 &           A1Vn &    07:33:36.48 &   +15:49:35.98 &  7039.68 &     CHIRON &     3127 &   480 \\
-   HIP 36760 &           A1Vn &    07:33:36.48 &   +15:49:35.98 &  6668.79 &       TS23 &      836 &   700 \\
-   HIP 36812 &          A0Vnn &    07:34:15.89 &   +03:22:18.19 &  6947.99 &     IGRINS &      280 &   110 \\
-   HIP 36917 &            B7V &    07:35:22.89 &    -28:22:9.57 &  6583.81 &     CHIRON &      571 &   420 \\
-   HIP 36917 &            B7V &    07:35:22.89 &    -28:22:9.57 &  6971.83 &     CHIRON &      435 &   690 \\
-     HR 2948 &            B6V &    07:38:49.38 &    -26:48:6.49 &  6584.81 &     CHIRON &      576 &   370 \\
-   HIP 37297 &          B2.5V &    07:39:27.34 &   -38:18:28.88 &  6698.74 &     CHIRON &      370 &   480 \\
-   HIP 37297 &          B2.5V &    07:39:27.34 &   -38:18:28.88 &  6574.82 &     CHIRON &      686 &   340 \\
-   HIP 37297 &          B2.5V &    07:39:27.34 &   -38:18:28.88 &  6729.53 &     CHIRON &      231 &   460 \\
-   HIP 37322 &            B5V &    07:39:43.81 &   -38:08:21.44 &  6975.79 &     CHIRON &      817 &   540 \\
-   HIP 37450 &            B5V &    07:41:15.81 &    -38:32:0.72 &  6600.74 &     CHIRON &     1171 &   450 \\
-   HIP 38538 &           A5IV &    07:53:29.81 &   +26:45:56.82 &  6669.78 &       TS23 &      474 &  1990 \\
-   HIP 38593 &            B2V &    07:54:11.01 &   -35:52:38.23 &  7039.70 &     CHIRON &      331 &   170 \\
-   HIP 38593 &            B2V &    07:54:11.01 &   -35:52:38.23 &  6599.82 &     CHIRON &     1200 &   410 \\
-   HIP 38593 &            B2V &    07:54:11.01 &   -35:52:38.23 &  6592.87 &     CHIRON &     1200 &   300 \\
-   HIP 38846 &          B2.5V &    07:56:57.80 &    -43:30:1.48 &  6601.76 &     CHIRON &     1098 &   400 \\
-   HIP 39095 &            A1V &    07:59:52.05 &   -18:23:57.23 &  6765.53 &     CHIRON &      430 &   450 \\
-   HIP 39095 &            A1V &    07:59:52.05 &   -18:23:57.23 &  6757.56 &     CHIRON &      238 &   490 \\
-   HIP 39095 &            A1V &    07:59:52.05 &   -18:23:57.23 &  6711.62 &     CHIRON &      288 &   500 \\
-   HIP 39236 &         B9.5Vn &    08:01:30.29 &   +16:27:19.12 &  6679.73 &       TS23 &      730 &  1420 \\
-   HIP 39567 &            A1V &     08:05:4.49 &    +13:07:5.58 &  6668.80 &       TS23 &      613 &  1940 \\
-   HIP 39847 &            A2V &    08:08:27.45 &   +51:30:24.01 &  7084.68 &     IGRINS &      480 &   160 \\
-   HIP 39847 &            A2V &    08:08:27.45 &   +51:30:24.01 &  6676.80 &       TS23 &      402 &  1500 \\
-   HIP 39906 &            B5V &     08:09:1.64 &   -19:14:42.05 &  6580.86 &     CHIRON &      457 &   270 \\
-   HIP 40429 &            A2V &    08:15:15.92 &   -62:54:56.32 &  6691.72 &     CHIRON &      710 &   560 \\
-   HIP 40706 &            A8V &    08:18:33.31 &   -36:39:33.44 &  6327.64 &     CHIRON &      277 &   630 \\
-   HIP 40881 &          B9.5V &    08:20:32.14 &   +24:01:20.32 &  6947.97 &     IGRINS &      240 &   100 \\
-   HIP 41039 &            B1V &    08:22:31.69 &   -48:29:25.36 &  7039.73 &     CHIRON &     1728 &   530 \\
-   HIP 41039 &            B1V &    08:22:31.69 &   -48:29:25.36 &  6330.77 &     CHIRON &      404 &   400 \\
-   HIP 41307 &           A0Va &    08:25:39.63 &   -03:54:23.12 &  6667.82 &       TS23 &      700 &  1220 \\
-   HIP 42090 &          A2Vnn &    08:34:43.88 &   +36:25:10.63 &  7124.62 &     IGRINS &      630 &   120 \\
-   HIP 42129 &            B3V &    08:35:15.56 &   -58:13:29.05 &  6603.80 &     CHIRON &     1001 &   370 \\
-   HIP 42313 &          A0Vnn &    08:37:39.37 &   +05:42:13.61 &  6681.81 &       TS23 &      489 &  1020 \\
-   HIP 42334 &            A0V &    08:37:52.15 &   -26:15:18.01 &  6712.64 &     CHIRON &      381 &   480 \\
-   HIP 43142 &            A3V &    08:47:14.99 &   -01:53:49.31 &  6670.79 &       TS23 &      647 &  1980 \\
-   HIP 44127 &     A7V(n)+M1V &    08:59:12.45 &   +48:02:30.57 &  6677.88 &       TS23 &      239 &  1600 \\
-   HIP 44307 &            A2V &    09:01:24.13 &    +32:15:8.26 &  6947.98 &     IGRINS &      280 &    80 \\
-   HIP 45336 &    B9.5V+DA1.6 &    09:14:21.86 &   +02:18:51.34 &  6328.70 &     CHIRON &      171 &   290 \\
-   HIP 45336 &    B9.5V+DA1.6 &    09:14:21.86 &   +02:18:51.34 &  7122.66 &     IGRINS &      270 &   130 \\
-   HIP 45336 &    B9.5V+DA1.6 &    09:14:21.86 &   +02:18:51.34 &  7084.75 &     IGRINS &      240 &   140 \\
-   HIP 45344 &            B4V &    09:14:24.48 &   -43:13:38.97 &  6612.79 &     CHIRON &     1001 &   320 \\
-   HIP 45688 &            A1V &    09:18:50.64 &    +36:48:9.33 &  6299.93 &       TS23 &      600 &   880 \\
-   HIP 46225 &            A4V &    09:25:27.23 &    -61:57:1.72 &  6679.84 &       TS23 &      933 &  1300 \\
-   HIP 46283 &            B6V &    09:26:17.96 &   -53:22:44.07 &  6732.56 &     CHIRON &      357 &   490 \\
-   HIP 46283 &            B6V &    09:26:17.96 &   -53:22:44.07 &  6619.80 &     CHIRON &      872 &   430 \\
-   HIP 46283 &            B6V &    09:26:17.96 &   -53:22:44.07 &  6712.70 &     CHIRON &      352 &   450 \\
-   HIP 46897 &          B9.5V &    09:33:26.05 &   -22:51:49.99 &  7084.78 &     IGRINS &     1200 &    20 \\
-   HIP 46897 &          B9.5V &    09:33:26.05 &   -22:51:49.99 &  7139.59 &     IGRINS &      720 &   120 \\
-   HIP 47006 &           A0Vn &    09:34:49.43 &    +52:03:5.32 &  6677.03 &       TS23 &      373 &  1590 \\
-   HIP 47175 &            A7V &    09:36:49.54 &   -49:21:18.09 &  6424.56 &     CHIRON &      264 &   660 \\
-   HIP 50303 &           A0Vn &    10:16:14.43 &   +29:18:37.81 &  6677.78 &       TS23 &     1200 &  1350 \\
-   HIP 50860 &          A5IVn &     10:23:6.33 &   +33:54:29.31 &  6678.81 &       TS23 &     1151 &  1470 \\
-   HIP 51362 &          B9.5V &    10:29:28.70 &   -02:44:20.69 &  7043.79 &     CHIRON &     1298 &   340 \\
-   HIP 51362 &          B9.5V &    10:29:28.70 &   -02:44:20.69 &  6625.81 &     CHIRON &      947 &   200 \\
-   HIP 51362 &          B9.5V &    10:29:28.70 &   -02:44:20.69 &  6673.75 &     CHIRON &      606 &   510 \\
-   HIP 51362 &          B9.5V &    10:29:28.70 &   -02:44:20.69 &  7084.76 &     IGRINS &      720 &   100 \\
-   HIP 51685 &           A2Vn &    10:33:30.91 &   +34:59:19.30 &  6677.90 &       TS23 &     1046 &  1460 \\
-   HIP 52422 &           A4Vn &     10:43:1.88 &   +26:19:32.09 &  6676.87 &       TS23 &      522 &  1540 \\
-   HIP 52457 &           A3Vn &    10:43:24.96 &   +23:11:18.25 &  6676.83 &       TS23 &      647 &  1500 \\
-   HIP 52638 &           A1Vn &    10:45:51.89 &   +30:40:56.33 &  6669.83 &       TS23 &      711 &  1900 \\
-   HIP 52678 &          B6Vnn &    10:46:16.56 &   -64:30:52.41 &  6748.56 &     CHIRON &      375 &   500 \\
-   HIP 52678 &          B6Vnn &    10:46:16.56 &   -64:30:52.41 &  6690.70 &     CHIRON &      618 &   610 \\
-   HIP 52736 &         B2.5Vn &    10:46:51.22 &    -64:23:0.50 &  6748.52 &     CHIRON &      530 &   540 \\
-   HIP 52736 &         B2.5Vn &    10:46:51.22 &    -64:23:0.50 &  6713.70 &     CHIRON &      263 &   490 \\
-   HIP 52911 &            A2V &    10:49:15.43 &   +10:32:42.73 &  6670.86 &       TS23 &      758 &  1950 \\
-     HR 4259 &            A1V &    10:55:36.80 &   +24:44:59.00 &  6335.70 &     CHIRON &      304 &   330 \\
-   HIP 54849 &            A0V &    11:13:45.55 &   -00:04:10.20 &  6670.94 &       TS23 &      797 &  2080 \\
-   HIP 55266 &            A2V &     11:19:7.90 &    +38:11:8.03 &  6300.00 &       TS23 &      900 &   200 \\
-   HIP 55434 &         B9.5Vs &  11:21:08.1934 &  +06:01:45.571 &  6332.77 &     CHIRON &      199 &   410 \\
-   HIP 56034 &            A2V &     11:29:4.12 &   +39:20:13.11 &  6676.91 &       TS23 &      502 &  1460 \\
-   HIP 56633 &          B9.5V &    11:36:40.91 &    -09:48:8.09 &  6669.91 &       TS23 &      447 &  1990 \\
-   HIP 56633 &          B9.5V &    11:36:40.91 &    -09:48:8.09 &  6335.75 &     CHIRON &      358 &   470 \\
-   HIP 57328 &            A4V &    11:45:17.04 &   +08:15:29.21 &  6338.68 &     CHIRON &      419 &   490 \\
-   HIP 57328 &            A4V &    11:45:17.04 &   +08:15:29.21 &  6370.62 &     CHIRON &      419 &   450 \\
-   HIP 58590 &            A5V &    12:00:52.39 &   +06:36:51.56 &  6338.72 &     CHIRON &      352 &   520 \\
-   HIP 59394 &            A1V &     12:11:3.84 &    -23:36:8.72 &  6754.57 &     CHIRON &      815 &   500 \\
-   HIP 59394 &            A1V &     12:11:3.84 &    -23:36:8.72 &  6690.78 &     CHIRON &      940 &   370 \\
-   HIP 59449 &            B3V &    12:11:39.12 &    -52:22:6.44 &  6711.88 &     CHIRON &      186 &   440 \\
-   HIP 59449 &            B3V &    12:11:39.12 &    -52:22:6.44 &  6641.76 &     CHIRON &      305 &   150 \\
-   HIP 59819 &            A3V &     12:16:0.19 &   +14:53:56.65 &  6669.96 &       TS23 &      465 &  1940 \\
-   HIP 60009 &          B2.5V &    12:18:26.25 &   -64:00:11.05 &  6370.66 &     CHIRON &      200 &   520 \\
-   HIP 60009 &          B2.5V &    12:18:26.25 &   -64:00:11.05 &  7009.78 &     CHIRON &      206 &   510 \\
-   HIP 60030 &           A5Vn &    12:18:40.32 &   -00:47:13.87 &  7084.81 &     IGRINS &     2400 &    80 \\
-   HIP 60595 &            A1V &    12:25:11.76 &   -11:36:38.12 &  6676.94 &       TS23 &      746 &  1540 \\
-   HIP 60710 &           B3Vn &    12:26:31.76 &    -51:27:2.29 &  7062.77 &     CHIRON &     1515 &   470 \\
-   HIP 60957 &            A3V &    12:29:43.24 &   +20:53:45.99 &  6678.92 &       TS23 &      904 &  1500 \\
-   HIP 61558 &            A3V &    12:36:47.35 &   -05:49:54.84 &  7139.67 &     IGRINS &     1440 &   180 \\
-   HIP 61558 &            A3V &    12:36:47.35 &   -05:49:54.84 &  7084.84 &     IGRINS &     1200 &    70 \\
-   HIP 61622 &            A2V &    12:37:42.16 &   -48:32:28.69 &  6378.69 &     CHIRON &      167 &   620 \\
-   HIP 62541 &            A1V &    12:48:54.21 &   +14:07:21.31 &  7124.80 &     IGRINS &      480 &   120 \\
-   HIP 62541 &            A1V &    12:48:54.21 &   +14:07:21.31 &  7084.86 &     IGRINS &     1500 &    80 \\
-   HIP 62576 &            A2V &    12:49:17.45 &    +27:33:8.57 &  7122.83 &     IGRINS &      546 &   130 \\
-   HIP 63724 &            A0V &    13:03:33.31 &   -49:31:38.15 &  6338.76 &     CHIRON &      412 &   560 \\
-   HIP 63724 &            A0V &    13:03:33.31 &   -49:31:38.15 &  6371.72 &     CHIRON &      412 &   630 \\
-   HIP 63945 &            B5V &    13:06:16.70 &   -48:27:47.85 &  6371.68 &     CHIRON &      362 &   560 \\
-   HIP 65198 &            A2V &    13:21:41.64 &   +02:05:14.07 &  7044.85 &     CHIRON &     3352 &   430 \\
-   HIP 65477 &      A5V+M3-4V &    13:25:13.54 &   +54:59:16.65 &  6670.01 &       TS23 &      207 &  2520 \\
-   HIP 65728 &           A1Vn &    13:28:27.09 &   +59:56:44.83 &  6677.98 &       TS23 &     1200 &  1710 \\
-   HIP 66249 &          A2Van &    13:34:41.74 &   -00:35:45.38 &  6378.71 &     CHIRON &      110 &   520 \\
-   HIP 66798 &            A2V &    13:41:29.89 &   +64:49:20.68 &  6377.82 &        HRS &      362 &   610 \\
-   HIP 66821 &  B8.5Vn+A2.5Va &    13:41:44.77 &   -54:33:33.93 &  6718.75 &     CHIRON &      610 &   540 \\
-   HIP 67143 &            A0V &    13:45:36.89 &   -26:06:57.63 &  7139.77 &     IGRINS &      480 &   120 \\
-   HIP 67194 &            A5V &    13:46:13.55 &   +41:05:19.48 &  6389.70 &        HRS &      368 &   740 \\
-   HIP 67782 &           A8IV &    13:53:10.28 &   +28:38:53.28 &  6394.92 &        HRS &      359 &   680 \\
-   HIP 68092 &            A8V &    13:56:27.88 &    +01:03:2.09 &  7139.80 &     IGRINS &      840 &   200 \\
-   HIP 68520 &            A3V &    14:01:38.79 &   +01:32:40.31 &  6403.59 &     CHIRON &      239 &   470 \\
-   HIP 70327 &            A0V &    14:23:22.70 &   +08:26:47.84 &  7123.90 &     IGRINS &      420 &    90 \\
-   HIP 70327 &            A0V &    14:23:22.70 &   +08:26:47.84 &  6681.98 &       TS23 &     1152 &   230 \\
-   HIP 70327 &            A0V &    14:23:22.70 &   +08:26:47.84 &  6719.80 &     CHIRON &      368 &   460 \\
-   HIP 70384 &            A3V &     14:24:0.88 &   +08:14:38.30 &  6403.73 &        HRS &      420 &   560 \\
-   HIP 70400 &            A3V &    14:24:11.34 &   +05:49:12.47 &  6669.00 &       TS23 &      602 &  2000 \\
-   HIP 70915 &           B8Vn &     14:30:8.63 &   -45:19:16.88 &  7136.63 &     CHIRON &     3281 &   480 \\
-   HIP 70915 &           B8Vn &     14:30:8.63 &   -45:19:16.88 &  7090.71 &     CHIRON &     2985 &   460 \\
-     HR 5476 &            A6V &    14:40:43.94 &    +16:25:3.90 &  6408.71 &        HRS &      305 &   660 \\
-   HIP 71865 &            B3V &    14:41:57.59 &   -37:47:36.59 &  6383.71 &     CHIRON &      190 &   460 \\
-   HIP 71865 &            B3V &    14:41:57.59 &   -37:47:36.59 &  7060.80 &     CHIRON &     1205 &   500 \\
-   HIP 71974 &          B9.5V &    14:43:13.55 &   -24:59:51.91 &  7078.80 &     CHIRON &     3786 &   470 \\
-   HIP 72104 &          A0Vnn &    14:44:59.20 &   -35:11:30.57 &  6720.86 &     CHIRON &      492 &   490 \\
-   HIP 72154 &          B9.5V &    14:45:30.20 &    +00:43:2.19 &  6403.75 &        HRS &      300 &   470 \\
-   HIP 72250 &            A1V &    14:46:28.99 &   -47:26:28.02 &  7070.72 &     CHIRON &     4025 &   490 \\
-   HIP 72378 &            B9V &    14:47:57.56 &   -26:38:46.16 &  7139.82 &     IGRINS &      720 &   140 \\
-   HIP 72552 &            A4V &    14:49:58.40 &   +28:36:57.00 &  7124.81 &     IGRINS &      600 &   110 \\
-   HIP 73049 &            A0V &    14:55:44.71 &   -33:51:20.82 &  6715.73 &     CHIRON &      749 &   530 \\
-     HR 5605 &            B5V &     15:05:7.18 &    -47:03:4.00 &  6383.74 &     CHIRON &      330 &   530 \\
-   HIP 74117 &            B3V &    15:08:50.62 &   -45:16:47.49 &  6383.77 &     CHIRON &      204 &   370 \\
-   HIP 74689 &            A4V &    15:15:49.08 &   +00:22:19.70 &  6872.52 &     CHIRON &      693 &   550 \\
-   HIP 75178 &           B9Vn &    15:21:48.58 &    +32:56:1.30 &  6678.99 &       TS23 &      815 &  1620 \\
-   HIP 75304 &            B4V &     15:23:9.35 &   -36:51:30.55 &  6427.78 &     CHIRON &      309 &   340 \\
-   HIP 76267 &            A0V &    15:34:41.27 &   +26:42:52.89 &  6380.88 &     CHIRON &       36 &   290 \\
-   HIP 76600 &          B2.5V &    15:38:39.37 &   -29:46:39.89 &  6380.91 &     CHIRON &      137 &   500 \\
-   HIP 76852 &            A1V &    15:41:33.05 &   +19:40:13.44 &  6426.65 &     CHIRON &      306 &   370 \\
-   HIP 77233 &            A3V &    15:46:11.25 &   +15:25:18.59 &  6426.69 &     CHIRON &      140 &   320 \\
-   HIP 77336 &            A3V &    15:47:17.32 &   +14:06:55.26 &  6396.79 &        HRS &      264 &   610 \\
-   HIP 77336 &            A3V &    15:47:17.32 &   +14:06:55.26 &  7122.91 &     IGRINS &      480 &   120 \\
-   HIP 77516 &            A0V &    15:49:37.21 &   -03:25:48.73 &  6380.89 &     CHIRON &      126 &   450 \\
-   HIP 77635 &         B1.5Vn &    15:50:58.74 &    -25:45:4.66 &  6725.72 &     CHIRON &      288 &   420 \\
-   HIP 77858 &            B5V &    15:53:53.92 &   -24:31:59.37 &  6733.75 &     CHIRON &      628 &   490 \\
-   HIP 78105 &            A3V &    15:56:53.50 &   -33:57:58.01 &  6870.54 &     CHIRON &      655 &   590 \\
-   HIP 78106 &            B9V &    15:56:54.12 &   -33:57:51.34 &  6736.70 &     CHIRON &      584 &   500 \\
-   HIP 78554 &            A3V &    16:02:17.69 &   +22:48:16.03 &  6427.74 &     CHIRON &      408 &   270 \\
-   HIP 78820 &            B1V &    16:05:26.23 &   -19:48:19.63 &  6380.93 &     CHIRON &       53 &   490 \\
-   HIP 78820 &            B1V &    16:05:26.23 &   -19:48:19.63 &  7139.83 &     IGRINS &      120 &   190 \\
-   HIP 78820 &            B1V &    16:05:26.23 &   -19:48:19.63 &  7060.85 &     CHIRON &      263 &   360 \\
-   HIP 78820 &            B1V &    16:05:26.23 &   -19:48:19.63 &  7156.63 &     CHIRON &      164 &   390 \\
-   HIP 78821 &            B2V &    16:05:26.57 &    -19:48:6.85 &  7139.84 &     IGRINS &      210 &    50 \\
-     HR 6025 &           A0Vn &  16:06:19.6762 &  +67:48:36.480 &  6847.83 &     IGRINS &      600 &   100 \\
-   HIP 78918 &         B2.5Vn &    16:06:35.55 &    -36:48:8.26 &  6718.86 &     CHIRON &      300 &   610 \\
-   HIP 78933 &            B1V &  16:06:48.4269 &  -20:40:09.090 &  6737.76 &     CHIRON &       77 &   250 \\
-   HIP 79005 &            B9V &    16:07:36.42 &   -12:44:43.46 &  7090.77 &     CHIRON &     4646 &   430 \\
-   HIP 79007 &            A7V &    16:07:37.54 &   +09:53:30.27 &  6874.48 &     CHIRON &      659 &   550 \\
-   HIP 79199 &            B8V &    16:09:52.59 &   -33:32:44.90 &  6734.71 &     CHIRON &      451 &   470 \\
-   HIP 79404 &            B2V &    16:12:18.20 &   -27:55:34.95 &  6415.77 &     CHIRON &      324 &   470 \\
-   HIP 79404 &            B2V &    16:12:18.20 &   -27:55:34.95 &  7076.81 &     CHIRON &     1307 &   430 \\
-   HIP 79404 &            B2V &    16:12:18.20 &   -27:55:34.95 &  7090.88 &     CHIRON &     1135 &   450 \\
-   HIP 79387 &            A4V &     16:12:7.32 &   -08:32:51.28 &  6746.75 &     CHIRON &      573 &   500 \\
-   HIP 79653 &            B8V &    16:15:15.32 &   -47:22:19.27 &  6740.79 &     CHIRON &      469 &   490 \\
-   HIP 80460 &            A5V &    16:25:24.17 &   +37:23:38.68 &  7122.93 &     IGRINS &      720 &   110 \\
-   HIP 80815 &            B3V &    16:30:12.48 &   -25:06:54.80 &  6378.86 &     CHIRON &      393 &   530 \\
-   HIP 80883 &            A0V &    16:30:54.82 &    +01:59:2.12 &  6378.84 &     CHIRON &      174 &   550 \\
-   HIP 80991 &            A2V &    16:32:25.68 &   +60:49:23.96 &  6389.86 &        HRS &      404 &   720 \\
-   HIP 81126 &            B9V &     16:34:6.18 &   +42:26:13.34 &  7122.95 &     IGRINS &      720 &   150 \\
-   HIP 81641 &            A1V &    16:40:38.69 &   +04:13:11.23 &  6404.83 &        HRS &      320 &   540 \\
-   HIP 82350 &            A1V &    16:49:34.66 &   +13:15:40.10 &  6391.84 &        HRS &      404 &   660 \\
-   HIP 82673 &            B8V &     16:54:0.47 &   +10:09:55.30 &  6871.58 &     CHIRON &      250 &   310 \\
-   HIP 82673 &            B8V &     16:54:0.47 &   +10:09:55.30 &  6410.86 &     CHIRON &      272 &   180 \\
-   HIP 83635 &            B1V &    17:05:32.26 &   -00:53:31.45 &  6407.86 &        HRS &      316 &   480 \\
-   HIP 84606 &            A2V &    17:17:40.25 &   +37:17:29.40 &  6945.54 &     IGRINS &      224 &   150 \\
-   HIP 85290 &           A1Vn &    17:25:41.35 &   +60:02:54.23 &  6946.56 &     IGRINS &      224 &   120 \\
-   HIP 85379 &            A4V &    17:26:44.24 &   +48:15:36.23 &  6398.85 &        HRS &      330 &   740 \\
-   HIP 85385 &            B5V &    17:26:49.13 &   +20:04:51.52 &  6848.83 &     IGRINS &      480 &    80 \\
-   HIP 85537 &           A8Vp &    17:28:49.65 &   +00:19:50.25 &  7096.88 &     CHIRON &     4227 &   570 \\
-   HIP 85537 &           A8Vp &    17:28:49.65 &   +00:19:50.25 &  6792.73 &     CHIRON &      900 &   600 \\
-   HIP 85537 &           A8Vp &    17:28:49.65 &   +00:19:50.25 &  6848.73 &     IGRINS &      240 &    60 \\
-   HIP 85727 &           B8Vn &     17:31:5.91 &    -60:41:1.85 &  6771.85 &     CHIRON &      175 &   570 \\
-   HIP 85922 &            A5V &    17:33:29.85 &   -05:44:41.29 &  6847.82 &     IGRINS &      480 &   120 \\
-   HIP 85922 &            A5V &    17:33:29.85 &   -05:44:41.29 &  7139.95 &     IGRINS &      240 &   170 \\
-   HIP 85922 &            A5V &    17:33:29.85 &   -05:44:41.29 &  6886.56 &     CHIRON &      791 &   590 \\
-   HIP 85922 &            A5V &    17:33:29.85 &   -05:44:41.29 &  7103.85 &     CHIRON &     2543 &   370 \\
-   HIP 85922 &            A5V &    17:33:29.85 &   -05:44:41.29 &  7104.82 &     CHIRON &     7386 &   360 \\
-   HIP 85998 &            A2V &    17:34:36.69 &   +09:35:12.12 &  7122.96 &     IGRINS &      480 &    50 \\
-   HIP 85998 &            A2V &    17:34:36.69 &   +09:35:12.12 &  7230.64 &     IGRINS &      720 &   170 \\
-   HIP 85998 &            A2V &    17:34:36.69 &   +09:35:12.12 &  6407.84 &        HRS &      324 &   490 \\
-   HIP 85998 &            A2V &    17:34:36.69 &   +09:35:12.12 &  7079.89 &     CHIRON &     1600 &   220 \\
-   HIP 86019 &           B8Vn &    17:34:46.35 &   -11:14:31.19 &  6747.85 &     CHIRON &      228 &   510 \\
-   HIP 86782 &            A2V &    17:43:59.18 &    +53:48:6.17 &  6404.85 &        HRS &      310 &   500 \\
-   HIP 87108 &           A0Vn &    17:47:53.56 &   +02:42:26.20 &  6847.87 &     IGRINS &      120 &   120 \\
-   HIP 87108 &           A0Vn &    17:47:53.56 &   +02:42:26.20 &  6445.79 &     CHIRON &      152 &   300 \\
-   HIP 88116 &             A0 &    17:59:47.56 &   -23:48:58.09 &  6488.71 &     CHIRON &      373 &   590 \\
-   HIP 88116 &             A0 &    17:59:47.56 &   -23:48:58.09 &  6876.54 &     CHIRON &      320 &   380 \\
-   HIP 88290 &           A2Vn &    18:01:45.20 &   +01:18:18.28 &  6873.59 &     CHIRON &      365 &   540 \\
-   HIP 88818 &            A3V &    18:07:49.45 &    +26:06:4.13 &  7122.98 &     IGRINS &      960 &    90 \\
-   HIP 88818 &            A3V &    18:07:49.45 &    +26:06:4.13 &  7230.66 &     IGRINS &      600 &   110 \\
-   HIP 88818 &            A3V &    18:07:49.45 &    +26:06:4.13 &  6397.85 &        HRS &      355 &   510 \\
-   HIP 88817 &            A3V &    18:07:49.50 &   +26:05:50.40 &  7123.00 &     IGRINS &      960 &   100 \\
-   HIP 88817 &            A3V &    18:07:49.50 &   +26:05:50.40 &  6405.84 &        HRS &      400 &   720 \\
-   HIP 89156 &            A3V &    18:11:45.12 &   +33:26:49.41 &  6405.82 &        HRS &      470 &   610 \\
-   HIP 89935 &            A7V &     18:21:1.02 &   +28:52:11.83 &  6848.85 &     IGRINS &      240 &   100 \\
-   HIP 89935 &            A7V &     18:21:1.02 &   +28:52:11.83 &  6945.56 &     IGRINS &      224 &   250 \\
-   HIP 90052 &            A2V &    18:22:35.32 &   +12:01:46.85 &  6405.88 &        HRS &      500 &   760 \\
-   HIP 90762 &            A2V &     18:31:4.45 &   +16:55:42.80 &  6848.85 &     IGRINS &      480 &    80 \\
-   HIP 90762 &            A2V &     18:31:4.45 &   +16:55:42.80 &  6945.57 &     IGRINS &      480 &   200 \\
-   HIP 90887 &           A3Vn &    18:32:21.33 &   -39:42:14.40 &  6748.80 &     CHIRON &      710 &   560 \\
-   HIP 91118 &           A0Vn &    18:35:12.60 &   +18:12:12.28 &  6945.58 &     IGRINS &      360 &   190 \\
-   HIP 91875 &           A2Vn &    18:43:46.94 &   -38:19:24.39 &  6745.81 &     CHIRON &      680 &   580 \\
-   HIP 92027 &            A1V &    18:45:28.36 &    +05:30:0.44 &  6405.91 &        HRS &      360 &   570 \\
-   HIP 92312 &            A1V &    18:48:53.39 &   +19:19:43.40 &  6408.88 &        HRS &      390 &   650 \\
-   HIP 92728 &          B2.5V &    18:53:43.56 &   +36:58:18.19 &  6405.86 &        HRS &      280 &   560 \\
-   HIP 92855 &            B2V &    18:55:15.93 &   -26:17:48.21 &  6880.57 &     CHIRON &       30 &   550 \\
-   HIP 92855 &            B2V &    18:55:15.93 &   -26:17:48.21 &  6415.80 &     CHIRON &       32 &   400 \\
-   HIP 92946 &            A5V &    18:56:13.18 &   +04:12:12.91 &  6475.79 &     CHIRON &      339 &   500 \\
-   HIP 93225 &            B4V &    18:59:23.80 &   -12:50:25.86 &  6946.54 &     IGRINS &      224 &    80 \\
-   HIP 93225 &            B4V &    18:59:23.80 &   -12:50:25.86 &  6516.69 &     CHIRON &     1200 &   540 \\
-   HIP 93225 &            B4V &    18:59:23.80 &   -12:50:25.86 &  6962.56 &       TS23 &      562 &  1430 \\
-   HIP 93393 &            B5V &    19:01:17.36 &   +26:17:29.08 &  6404.88 &        HRS &      320 &   540 \\
-   HIP 93580 &            A4V &    19:03:32.25 &    +01:49:7.57 &  7116.84 &     CHIRON &     5594 &   520 \\
-   HIP 93580 &            A4V &    19:03:32.25 &    +01:49:7.57 &  6848.84 &     IGRINS &      480 &   100 \\
-   HIP 93713 &           A0Vn &    19:04:55.17 &   +53:23:47.96 &  6848.87 &     IGRINS &      600 &    90 \\
-   HIP 93747 &       A0IV-Vnn &    19:05:24.61 &   +13:51:48.52 &  6587.54 &       TS23 &       85 &  1880 \\
-   HIP 93805 &           B9Vn &    19:06:14.94 &   -04:52:57.20 &  6852.82 &     IGRINS &     2640 &    60 \\
-   HIP 93805 &           B9Vn &    19:06:14.94 &   -04:52:57.20 &  7139.96 &     IGRINS &      120 &   210 \\
-   HIP 93805 &           B9Vn &    19:06:14.94 &   -04:52:57.20 &  6775.78 &     CHIRON &      150 &   520 \\
-   HIP 94620 &            A4V &    19:15:17.36 &   +21:13:55.62 &  6848.88 &     IGRINS &      480 &   100 \\
-   HIP 94720 &          B9.5V &    19:16:26.79 &   +14:32:40.62 &  6517.78 &        HRS &      400 &   880 \\
-   HIP 95241 &            B9V &    19:22:38.30 &   -44:27:32.25 &  6869.63 &     CHIRON &      325 &   120 \\
-   HIP 95241 &            B9V &    19:22:38.30 &   -44:27:32.25 &  6508.80 &     CHIRON &      294 &   600 \\
-   HIP 95241 &            B9V &    19:22:38.30 &   -44:27:32.25 &  6459.89 &     CHIRON &      183 &   360 \\
-   HIP 95560 &            A0V &    19:26:13.25 &   +20:05:51.84 &  6848.89 &     IGRINS &      480 &   110 \\
-   HIP 95619 &          B8.5V &    19:26:56.48 &   -29:44:35.62 &  7139.97 &     IGRINS &      480 &   120 \\
-   HIP 95619 &          B8.5V &    19:26:56.48 &   -29:44:35.62 &  7118.79 &     CHIRON &     3451 &   320 \\
-   HIP 95619 &          B8.5V &    19:26:56.48 &   -29:44:35.62 &  6523.61 &     CHIRON &      768 &   670 \\
-   HIP 95853 &            A5V &    19:29:42.36 &   +51:43:47.21 &  6585.54 &       TS23 &      129 &  2010 \\
-   HIP 96288 &            A2V &    19:34:41.26 &   +42:24:45.04 &  6585.56 &       TS23 &      489 &  1860 \\
-   HIP 96840 &            B5V &     19:41:5.53 &   +13:48:56.45 &  6408.92 &        HRS &      552 &   940 \\
-   HIP 97376 &           B8Vn &    19:47:27.78 &   +38:24:27.41 &  6848.90 &     IGRINS &     1680 &    70 \\
-   HIP 97496 &            A3V &    19:48:58.66 &   +19:08:31.35 &  6584.54 &       TS23 &      342 &  1820 \\
-   HIP 97870 &            B5V &    19:53:17.38 &   +57:31:24.53 &  6517.81 &        HRS &      185 &   830 \\
-   HIP 97966 &           B7Vn &    19:54:37.65 &   -08:13:38.24 &  6925.51 &     CHIRON &      655 &   380 \\
-   HIP 97966 &           B7Vn &    19:54:37.65 &   -08:13:38.24 &  6881.70 &     CHIRON &     1158 &   660 \\
-   HIP 98055 &           A4Vn &    19:55:37.79 &   +52:26:20.21 &  6586.54 &       TS23 &      320 &  1820 \\
-   HIP 98194 &            B5V &    19:57:13.87 &    +40:22:4.17 &  6583.54 &       TS23 &      495 &  1750 \\
-   HIP 98325 &           B9Vn &    19:58:37.98 &    +30:59:1.19 &  6587.56 &       TS23 &      543 &  1750 \\
-   HIP 99080 &            B3V &    20:06:53.41 &   +23:36:51.93 &  6583.63 &       TS23 &      358 &  1740 \\
-   HIP 99742 &           A1Va &    20:14:16.62 &   +15:11:51.39 &  6945.59 &     IGRINS &      224 &   210 \\
-  HIP 100069 &          B1.5V &     20:18:6.99 &   +40:43:55.50 &  6409.91 &        HRS &      451 &   560 \\
-  HIP 100221 &            B9V &    20:19:36.72 &   +62:15:26.90 &  7230.72 &     IGRINS &     1100 &    80 \\
-  HIP 100221 &            B9V &    20:19:36.72 &   +62:15:26.90 &  6523.79 &        HRS &      874 &   830 \\
-  HIP 100881 &            B4V &    20:27:19.21 &   -18:12:42.20 &  6511.69 &     CHIRON &     1011 &   570 \\
-  HIP 100907 &            A3V &    20:27:34.26 &   +38:26:25.19 &  6946.57 &     IGRINS &      224 &   120 \\
-  HIP 100907 &            A3V &    20:27:34.26 &   +38:26:25.19 &  7230.67 &     IGRINS &      600 &   120 \\
-  HIP 101123 &            A1V &    20:29:53.91 &   -18:34:59.48 &  6945.70 &     IGRINS &      224 &   160 \\
-  HIP 101589 &            A3V &    20:35:18.54 &   +14:40:27.17 &  6448.83 &     CHIRON &      352 &   420 \\
-  HIP 101716 &            B8V &     20:37:4.67 &   +26:27:43.01 &  6582.60 &       TS23 &      549 &  1260 \\
-  HIP 101867 &            A0V &    20:38:31.34 &    +21:12:4.25 &  6489.78 &     CHIRON &      408 &   440 \\
-  HIP 101909 &            B3V &     20:39:4.97 &   +15:50:17.52 &  6945.60 &     IGRINS &      360 &   140 \\
-  HIP 101909 &            B3V &     20:39:4.97 &   +15:50:17.52 &  7230.69 &     IGRINS &      720 &    90 \\
-  HIP 102487 &            A1V &     20:46:9.99 &   -21:30:50.52 &  6847.80 &     IGRINS &      480 &    80 \\
-  HIP 103298 &            A5V &    20:55:38.57 &    +12:34:6.81 &  6946.58 &     IGRINS &      224 &   100 \\
-  HIP 103298 &            A5V &    20:55:38.57 &    +12:34:6.81 &  7230.70 &     IGRINS &      600 &    80 \\
-  HIP 103298 &            A5V &    20:55:38.57 &    +12:34:6.81 &  7155.93 &     CHIRON &     1141 &   290 \\
-  HIP 104019 &            A5V &    21:04:24.30 &   -19:51:17.97 &  6474.90 &     CHIRON &      423 &   550 \\
-  HIP 104105 &           B8Vn &    21:05:29.27 &   +78:07:35.02 &  6945.69 &     IGRINS &      280 &   140 \\
-  HIP 104139 &            A1V &    21:05:56.83 &   -17:13:58.30 &  6448.90 &     CHIRON &      204 &   490 \\
-  HIP 104365 &            A0V &    21:08:33.63 &   -21:11:37.22 &  6847.81 &     IGRINS &      480 &   100 \\
-  HIP 104365 &            A0V &    21:08:33.63 &   -21:11:37.22 &  7237.82 &     IGRINS &      720 &    50 \\
-  HIP 105140 &            A1V &    21:17:56.28 &   -32:10:21.15 &  6485.90 &     CHIRON &      372 &   420 \\
-  HIP 105282 &            B6V &    21:19:28.75 &   +49:30:37.06 &  6522.65 &        HRS &     1006 &   850 \\
-  HIP 105891 &            B6V &    21:26:44.97 &   +52:53:54.73 &  6946.59 &     IGRINS &      224 &    90 \\
-  HIP 105942 &            B3V &    21:27:21.37 &    +37:07:0.47 &  6523.87 &        HRS &      480 &   760 \\
-  HIP 105966 &            A1V &    21:27:40.06 &   +27:36:30.94 &  6585.64 &       TS23 &      530 &  1800 \\
-  HIP 105972 &            B7V &    21:27:46.14 &   +66:48:32.74 &  6507.82 &        HRS &      267 &   690 \\
-  HIP 106711 &           A3Vn &    21:36:56.98 &   +40:24:48.67 &  6584.60 &       TS23 &      689 &   700 \\
-  HIP 106711 &           A3Vn &    21:36:56.98 &   +40:24:48.67 &  6618.53 &       TS23 &      557 &  2010 \\
-  HIP 106786 &            A7V &    21:37:45.11 &   -07:51:15.13 &  6945.64 &     IGRINS &      224 &   230 \\
-  HIP 106786 &            A7V &    21:37:45.11 &   -07:51:15.13 &  6962.59 &       TS23 &      284 &  1620 \\
-  HIP 106786 &            A7V &    21:37:45.11 &   -07:51:15.13 &  6794.81 &     CHIRON &      232 &   470 \\
-  HIP 107517 &            A1V &    21:46:32.10 &   -11:21:57.44 &  6873.74 &     CHIRON &     1025 &   490 \\
-  HIP 107608 &            A2V &    21:47:44.15 &   -30:53:53.90 &  6788.84 &     CHIRON &      620 &   470 \\
-  HIP 108294 &           A2Vn &    21:56:22.77 &   -37:15:13.16 &  6790.81 &     CHIRON &      470 &   510 \\
-  HIP 108339 &          A2Vnn &    21:56:56.37 &   +12:04:35.37 &  6945.65 &     IGRINS &      224 &   160 \\
-  HIP 109056 &           B9Vn &    22:05:34.67 &   +28:57:50.32 &  6945.66 &     IGRINS &      240 &   150 \\
-  HIP 109056 &           B9Vn &    22:05:34.67 &   +28:57:50.32 &  6948.56 &     IGRINS &     1156 &   160 \\
-  HIP 109056 &           B9Vn &    22:05:34.67 &   +28:57:50.32 &  6946.65 &     IGRINS &      784 &   230 \\
-  HIP 109056 &           B9Vn &    22:05:34.67 &   +28:57:50.32 &  6947.57 &     IGRINS &     1746 &   170 \\
-  HIP 109139 &            B8V &    22:06:26.23 &   -13:52:10.86 &  6524.67 &     CHIRON &      207 &   590 \\
-  HIP 109139 &            B8V &    22:06:26.23 &   -13:52:10.86 &  6447.91 &     CHIRON &      248 &   470 \\
-  HIP 109521 &            A5V &     22:11:9.89 &   +50:49:24.26 &  6586.58 &       TS23 &      511 &  1860 \\
-  HIP 109521 &            A5V &     22:11:9.89 &   +50:49:24.26 &  6962.60 &       TS23 &      587 &  1500 \\
-  HIP 109521 &            A5V &     22:11:9.89 &   +50:49:24.26 &  6945.68 &     IGRINS &      224 &   200 \\
-  HIP 109831 &          A2Vnn &    22:14:44.37 &   +42:57:14.07 &  6945.67 &     IGRINS &      224 &   160 \\
-  HIP 109831 &          A2Vnn &    22:14:44.37 &   +42:57:14.07 &  7237.77 &     IGRINS &     1440 &   100 \\
-  HIP 109831 &          A2Vnn &    22:14:44.37 &   +42:57:14.07 &  7288.73 &     IGRINS &      900 &    30 \\
-  HIP 110838 &           B9Vn &    22:27:19.97 &   -64:57:58.88 &  6543.82 &     CHIRON &      506 &   550 \\
-  HIP 110838 &           B9Vn &    22:27:19.97 &   -64:57:58.88 &  6880.76 &     CHIRON &      354 &   780 \\
-  HIP 110935 &            A4V &    22:28:37.67 &   -67:29:20.62 &  6896.67 &     CHIRON &      696 &   630 \\
-  HIP 111056 &            A3V &    22:29:52.98 &   +78:49:27.43 &  7288.80 &     IGRINS &      180 &    30 \\
-  HIP 111056 &            A3V &    22:29:52.98 &   +78:49:27.43 &  6945.76 &     IGRINS &      224 &   120 \\
-  HIP 111068 &          B9.5V &     22:30:1.81 &   +32:34:21.50 &  6512.74 &        HRS &      362 &   500 \\
-  HIP 111169 &            A1V &    22:31:17.50 &   +50:16:56.97 &  6585.62 &       TS23 &      121 &  1900 \\
-  HIP 111841 &            O9V &    22:39:15.68 &    +39:03:0.97 &  6583.68 &       TS23 &      267 &  1670 \\
-  HIP 112029 &            B8V &    22:41:27.73 &   +10:49:52.64 &  6487.85 &     CHIRON &      109 &   460 \\
-  HIP 112029 &            B8V &    22:41:27.73 &   +10:49:52.64 &  6892.74 &     CHIRON &       95 &   250 \\
-  HIP 113788 &            A1V &    23:02:36.38 &   +42:45:28.06 &  6586.63 &       TS23 &      367 &  1830 \\
-  HIP 114520 &           A5Vn &    23:11:44.19 &   +08:43:12.40 &  6587.64 &       TS23 &      541 &  1880 \\
-  HIP 114822 &            A2V &    23:15:34.26 &   -03:29:46.96 &  6886.68 &     CHIRON &      715 &   550 \\
-  HIP 114822 &            A2V &    23:15:34.26 &   -03:29:46.96 &  6884.68 &     CHIRON &      530 &   530 \\
-  HIP 115115 &            A0V &    23:18:57.68 &   -09:36:38.70 &  7163.90 &     CHIRON &      600 &   190 \\
-  HIP 115115 &            A0V &    23:18:57.68 &   -09:36:38.70 &  7230.95 &     IGRINS &      500 &    40 \\
-  HIP 115115 &            A0V &    23:18:57.68 &   -09:36:38.70 &  6797.87 &     CHIRON &      610 &   330 \\
-  HIP 116247 &            A0V &    23:33:16.62 &   -20:54:52.21 &  6463.89 &     CHIRON &      368 &   560 \\
-  HIP 116247 &            A0V &    23:33:16.62 &   -20:54:52.21 &  7237.94 &     IGRINS &      240 &   100 \\
-  HIP 116582 &            B8V &    23:37:32.04 &   +44:25:44.37 &  6510.77 &        HRS &      534 &   670 \\
-  HIP 116611 &           A0Vn &    23:37:56.80 &    +18:24:2.40 &  6946.61 &     IGRINS &      224 &   140 \\
-  HIP 116631 &            B8V &     23:38:8.20 &    +43:16:5.06 &  6962.63 &       TS23 &      249 &  1980 \\
-  HIP 116631 &            B8V &     23:38:8.20 &    +43:16:5.06 &  6946.78 &     IGRINS &      224 &   160 \\
-  HIP 116631 &            B8V &     23:38:8.20 &    +43:16:5.06 &  6583.71 &       TS23 &      162 &  1740 \\
-  HIP 116631 &            B8V &     23:38:8.20 &    +43:16:5.06 &  7288.80 &     IGRINS &      180 &    30 \\
-  HIP 116805 &            A0V &    23:40:24.51 &    +44:20:2.16 &  6528.84 &       TS23 &      158 &  1680 \\
-  HIP 116971 &            B9V &    23:42:43.34 &   -14:32:41.65 &  6527.85 &       TS23 &      407 &  1650 \\
-  HIP 116971 &            B9V &    23:42:43.34 &   -14:32:41.65 &  6487.88 &     CHIRON &      298 &   540 \\
-  HIP 116971 &            B9V &    23:42:43.34 &   -14:32:41.65 &  6555.56 &     CHIRON &      497 &   430 \\
-  HIP 116971 &            B9V &    23:42:43.34 &   -14:32:41.65 &  6869.76 &     CHIRON &      380 &   110 \\
-  HIP 116971 &            B9V &    23:42:43.34 &   -14:32:41.65 &  6936.73 &     CHIRON &      344 &   600 \\
-  HIP 117089 &            B9V &    23:44:12.08 &   -18:16:36.97 &  7288.81 &     IGRINS &      180 &    20 \\
-  HIP 117089 &            B9V &    23:44:12.08 &   -18:16:36.97 &  7237.95 &     IGRINS &      720 &    60 \\
-  HIP 117089 &            B9V &    23:44:12.08 &   -18:16:36.97 &  6513.86 &     CHIRON &      853 &   600 \\
-  HIP 117371 &           A1Vn &    23:47:54.77 &   +67:48:24.51 &  6586.67 &       TS23 &      349 &  1760 \\
-  HIP 117452 &          A0Vnp &    23:48:55.55 &   -28:07:48.97 &  6469.90 &     CHIRON &      327 &   540 \\
-  HIP 118121 &            A1V &    23:57:35.08 &   -64:17:53.63 &  6795.86 &     CHIRON &      233 &   500 \\
-  HIP 118243 &            B1V &     23:59:0.54 &   +55:45:17.74 &  6945.73 &     IGRINS &      224 &   170 \\
-  HIP 118243 &            B1V &     23:59:0.54 &   +55:45:17.74 &  6583.74 &       TS23 &      351 &  1760
+     HIP 813 &  6618.58 &       TS23 &      557 &  1810 \\
+    HIP 1191 &  6552.60 &     CHIRON &     1200 &   320 \\
+    HIP 1366 &  6585.73 &       TS23 &      274 &  1790 \\
+    HIP 1647 &  6510.74 &     CHIRON &     1105 &   630 \\
+    HIP 2381 &  6874.71 &     CHIRON &      505 &   580 \\
+    HIP 2505 &  6586.71 &       TS23 &      235 &  1700 \\
+    HIP 2505 &  6962.71 &       TS23 &      804 &  1960 \\
+    HIP 2505 &  6945.71 &     IGRINS &      224 &   210 \\
+    HIP 2548 &  7240.93 &     IGRINS &      360 &   100 \\
+    HIP 2548 &  6516.84 &        HRS &      412 &  1070 \\
+    HIP 2912 &  7238.96 &     IGRINS &      367 &   130 \\
+    HIP 2912 &  6583.78 &       TS23 &      199 &  2460 \\
+    HIP 3300 &  6299.55 &       TS23 &      689 &  1010 \\
+    HIP 3478 &  6963.63 &       TS23 &     1200 &  1020 \\
+    HIP 3478 &  7288.82 &     IGRINS &      540 &    30 \\
+    HIP 3478 &  6669.53 &       TS23 &      743 &  1870 \\
+    HIP 3478 &  6945.72 &     IGRINS &      224 &   150 \\
+    HIP 3741 &  7174.89 &     CHIRON &     3981 &   430 \\
+    HIP 3741 &  7175.90 &     CHIRON &     3561 &   420 \\
+    HIP 3881 &  6585.70 &       TS23 &      222 &  1690 \\
+    HIP 3881 &  6964.60 &       TS23 &     1200 &   710 \\
+    HIP 3881 &  6945.74 &     IGRINS &      224 &   200 \\
+    HIP 4436 &  6585.76 &       TS23 &      129 &  1940 \\
+    HIP 5131 &  6587.70 &       TS23 &      655 &  1780 \\
+    HIP 5131 &  7083.57 &     IGRINS &      930 &    70 \\
+    HIP 5131 &  6847.89 &     IGRINS &     1600 &   110 \\
+    HIP 5132 &  6587.77 &       TS23 &      535 &  1550 \\
+    HIP 5132 &  6847.89 &     IGRINS &      480 &   110 \\
+    HIP 5310 &  6945.75 &     IGRINS &      224 &   200 \\
+    HIP 5348 &  6325.56 &     CHIRON &      186 &   390 \\
+    HIP 5361 &  6523.84 &        HRS &     1000 &   810 \\
+    HIP 5518 &  7238.94 &     IGRINS &      540 &    80 \\
+    HIP 5518 &  6945.77 &     IGRINS &      224 &   160 \\
+    HIP 5626 &  6945.88 &     IGRINS &      224 &   160 \\
+    HIP 7345 &  6888.76 &     CHIRON &     1080 &   480 \\
+    HIP 7345 &  6887.76 &     CHIRON &      706 &   540 \\
+    HIP 8016 &  6522.96 &        HRS &      328 &   580 \\
+    HIP 8704 &  6506.90 &        HRS &      365 &   420 \\
+    HIP 8704 &  7084.57 &     IGRINS &      960 &    30 \\
+    HIP 8704 &  7237.93 &     IGRINS &      720 &    90 \\
+      HR 545 &  6668.56 &       TS23 &      597 &  1920 \\
+      HR 545 &  6586.75 &       TS23 &      265 &  1710 \\
+      HR 545 &  6945.81 &     IGRINS &      224 &   230 \\
+    HIP 9312 &  6586.78 &       TS23 &      419 &  1750 \\
+    HIP 9564 &  6945.78 &     IGRINS &      224 &   140 \\
+      HR 604 &  6585.86 &       TS23 &      349 &  1650 \\
+   HIP 10320 &  6532.80 &     CHIRON &     1020 &   550 \\
+   HIP 10670 &  6618.68 &       TS23 &      141 &  1810 \\
+   HIP 10732 &  6945.82 &     IGRINS &      224 &   180 \\
+   HIP 10732 &  7083.56 &     IGRINS &      240 &   110 \\
+   HIP 11345 &  6894.90 &     CHIRON &      540 &   520 \\
+   HIP 12332 &  6677.54 &       TS23 &     1107 &  1530 \\
+   HIP 12332 &  6947.79 &     IGRINS &      224 &   170 \\
+   HIP 12706 &  6584.86 &       TS23 &      362 &   990 \\
+   HIP 12706 &  6946.84 &     IGRINS &      224 &   150 \\
+   HIP 12719 &  6583.87 &       TS23 &      264 &  1720 \\
+   HIP 12803 &  6676.53 &       TS23 &      452 &  1410 \\
+   HIP 12803 &  6947.80 &     IGRINS &      224 &   140 \\
+   HIP 12803 &  7240.95 &     IGRINS &      780 &   120 \\
+   HIP 13165 &  6518.91 &        HRS &      275 &   850 \\
+   HIP 13202 &  6910.83 &     CHIRON &      580 &   570 \\
+   HIP 13209 &  6618.66 &       TS23 &      143 &  1880 \\
+   HIP 13327 &  6670.54 &       TS23 &     1200 &  1800 \\
+   HIP 13717 &  6917.83 &     CHIRON &      644 &   550 \\
+   HIP 13717 &  6970.75 &     CHIRON &      703 &   550 \\
+   HIP 13879 &  6945.79 &     IGRINS &      224 &   260 \\
+   HIP 13879 &  6681.68 &       TS23 &      930 &   230 \\
+   HIP 13879 &  6618.70 &       TS23 &      265 &  1490 \\
+   HIP 14043 &  6523.92 &        HRS &      400 &   620 \\
+   HIP 14143 &  6518.94 &        HRS &      462 &   900 \\
+   HIP 14293 &  6919.89 &     CHIRON &      800 &   240 \\
+   HIP 14576 &  6583.83 &       TS23 &       40 &  1030 \\
+   HIP 14576 &  6582.92 &       TS23 &       36 &  2050 \\
+   HIP 14764 &  6679.53 &       TS23 &      532 &  1370 \\
+   HIP 14764 &  6946.80 &     IGRINS &      360 &   150 \\
+   HIP 14862 &  6945.86 &     IGRINS &      224 &   180 \\
+   HIP 14862 &  7084.60 &     IGRINS &     1200 &   120 \\
+   HIP 15110 &  6946.83 &     IGRINS &      224 &   120 \\
+   HIP 15338 &  6523.90 &        HRS &      570 &   690 \\
+   HIP 15404 &  6517.92 &        HRS &      205 &   620 \\
+   HIP 15444 &  6582.94 &       TS23 &      340 &  1790 \\
+   HIP 16147 &  6299.59 &       TS23 &      735 &  1300 \\
+   HIP 16210 &  6676.58 &       TS23 &      406 &  1440 \\
+   HIP 16210 &  6945.84 &     IGRINS &      224 &   160 \\
+   HIP 16244 &  6583.84 &       TS23 &      311 &  1750 \\
+   HIP 16244 &  6945.83 &     IGRINS &      224 &   230 \\
+   HIP 16285 &  6933.84 &     CHIRON &      767 &   570 \\
+   HIP 16322 &  6944.72 &     CHIRON &      680 &   410 \\
+   HIP 16322 &  6946.82 &     IGRINS &      224 &   170 \\
+   HIP 16340 &  6678.54 &       TS23 &      570 &  1410 \\
+   HIP 16599 &  6945.85 &     IGRINS &      224 &   170 \\
+   HIP 16611 &  6946.85 &     IGRINS &      224 &   210 \\
+   HIP 16611 &  6522.88 &     CHIRON &      255 &   580 \\
+   HIP 17457 &  6531.82 &     CHIRON &     1005 &   520 \\
+   HIP 17527 &  6947.82 &     IGRINS &      224 &   120 \\
+   HIP 17527 &  6517.93 &        HRS &      429 &   670 \\
+   HIP 17527 &  6963.91 &       TS23 &      818 &   470 \\
+   HIP 17563 &  6538.82 &     CHIRON &     1088 &   400 \\
+   HIP 18141 &  6678.59 &       TS23 &      605 &  1430 \\
+   HIP 18396 &  6516.94 &        HRS &      259 &   510 \\
+   HIP 18724 &  6299.62 &       TS23 &      226 &  1220 \\
+   HIP 18788 &  6535.81 &     CHIRON &     1039 &   180 \\
+   HIP 18805 &  6585.78 &       TS23 &      631 &  1760 \\
+   HIP 19799 &  6668.63 &       TS23 &     1200 &  1900 \\
+   HIP 19949 &  6945.90 &     IGRINS &      224 &   220 \\
+   HIP 19949 &  7084.62 &     IGRINS &      960 &    30 \\
+   HIP 19968 &  6676.62 &       TS23 &      524 &  1390 \\
+   HIP 20264 &  6718.53 &     CHIRON &      860 &   410 \\
+   HIP 20380 &  6945.89 &     IGRINS &      224 &   180 \\
+   HIP 20380 &  7084.67 &     IGRINS &     1200 &    30 \\
+   HIP 20430 &  6520.95 &        HRS &      360 &   710 \\
+   HIP 20507 &  6719.50 &     CHIRON &      715 &   470 \\
+   HIP 20579 &  6517.96 &        HRS &      490 &   830 \\
+   HIP 20789 &  6946.86 &     IGRINS &      224 &   150 \\
+   HIP 20789 &  6586.83 &       TS23 &      524 &  1610 \\
+   HIP 21589 &  6962.94 &       TS23 &      220 &  1020 \\
+   HIP 21589 &  7065.63 &     CHIRON &      754 &   290 \\
+   HIP 21589 &  6948.96 &     IGRINS &      112 &   140 \\
+   HIP 21683 &  6948.98 &     IGRINS &      230 &   110 \\
+   HIP 21683 &  6962.97 &       TS23 &      335 &  1040 \\
+   HIP 21819 &  6679.64 &       TS23 &      466 &  1480 \\
+   HIP 21928 &  6677.63 &       TS23 &     1124 &  1470 \\
+   HIP 22028 &  6947.90 &     IGRINS &      240 &   140 \\
+   HIP 22509 &  6667.62 &       TS23 &     1200 &  1100 \\
+   HIP 22509 &  7126.51 &     CHIRON &     2612 &   440 \\
+   HIP 22833 &  6679.60 &       TS23 &      521 &  1520 \\
+   HIP 22833 &  6946.87 &     IGRINS &      224 &   140 \\
+   HIP 22840 &  6678.64 &       TS23 &      528 &  1380 \\
+   HIP 22913 &  6585.74 &     CHIRON &     1200 &   230 \\
+   HIP 22958 &  6551.79 &     CHIRON &     1200 &   340 \\
+   HIP 22958 &  6943.77 &     CHIRON &      650 &   320 \\
+   HIP 23362 &  6548.87 &     CHIRON &      725 &   520 \\
+   HIP 23362 &  6946.93 &     IGRINS &      240 &   180 \\
+   HIP 23916 &  6555.82 &     CHIRON &     1200 &    40 \\
+   HIP 23916 &  6946.95 &     IGRINS &      280 &   140 \\
+   HIP 24244 &  6949.84 &     CHIRON &      370 &   560 \\
+   HIP 24244 &  6554.91 &     CHIRON &      488 &   330 \\
+   HIP 24327 &  6529.88 &     CHIRON &      277 &   560 \\
+   HIP 24505 &  7036.69 &     CHIRON &     2045 &   480 \\
+   HIP 24902 &  6946.88 &     IGRINS &      224 &   180 \\
+   HIP 25048 &  6299.69 &       TS23 &      900 &   420 \\
+ ADS 3962 AB &  6946.92 &     IGRINS &      280 &   170 \\
+   HIP 25143 &  7084.65 &     IGRINS &      960 &    80 \\
+   HIP 25143 &  6946.89 &     IGRINS &      224 &   180 \\
+   HIP 25280 &  6950.75 &     CHIRON &      597 &   540 \\
+   HIP 25280 &  6947.91 &     IGRINS &      240 &   130 \\
+   HIP 25281 &  6299.71 &       TS23 &      583 &  1120 \\
+   HIP 25555 &  6670.63 &       TS23 &      600 &  1950 \\
+   HIP 25608 &  6718.62 &     CHIRON &     1030 &   360 \\
+   HIP 25695 &  6669.65 &       TS23 &     1200 &  1860 \\
+   HIP 25790 &  6946.90 &     IGRINS &      224 &   160 \\
+   HIP 25813 &  7083.58 &     IGRINS &     1020 &   200 \\
+   HIP 25813 &  6544.88 &     CHIRON &      384 &   260 \\
+   HIP 26063 &  6582.80 &     CHIRON &     1139 &   250 \\
+   HIP 26093 &  6946.91 &     IGRINS &      280 &   150 \\
+   HIP 26093 &  6676.66 &       TS23 &      525 &  1380 \\
+   HIP 26093 &  7084.72 &     IGRINS &     1800 &    90 \\
+   HIP 26126 &  6946.96 &     IGRINS &      240 &   170 \\
+   HIP 26126 &  6721.50 &     CHIRON &      507 &   450 \\
+   HIP 26126 &  6948.81 &     CHIRON &      550 &   360 \\
+     HR 1880 &  6594.74 &     CHIRON &      472 &   540 \\
+   HIP 26563 &  6677.68 &       TS23 &      502 &  1550 \\
+   HIP 27100 &  6692.59 &     CHIRON &      294 &   680 \\
+   HIP 27100 &  6727.54 &     CHIRON &      177 &   560 \\
+   HIP 27321 &  6696.62 &     CHIRON &      178 &   640 \\
+   HIP 27713 &  6946.97 &     IGRINS &      240 &   150 \\
+   HIP 28691 &  6298.78 &       TS23 &      646 &  1300 \\
+   HIP 28756 &  6571.74 &     CHIRON &     1200 &   320 \\
+   HIP 28910 &  6693.61 &     CHIRON &      343 &   560 \\
+   HIP 29150 &  6697.63 &     CHIRON &      950 &   380 \\
+   HIP 29151 &  6946.99 &     IGRINS &      264 &   170 \\
+   HIP 29151 &  6953.82 &     CHIRON &      617 &   540 \\
+   HIP 29735 &  6559.80 &     CHIRON &      803 &   380 \\
+   HIP 29735 &  6946.98 &     IGRINS &      240 &   170 \\
+   HIP 29997 &  6679.70 &       TS23 &      415 &  1460 \\
+   HIP 30069 &  6573.75 &     CHIRON &     1200 &   250 \\
+   HIP 30073 &  6581.82 &     CHIRON &     1011 &   280 \\
+   HIP 30666 &  6947.00 &     IGRINS &      280 &   160 \\
+   HIP 30788 &  6574.75 &     CHIRON &      488 &   340 \\
+   HIP 31278 &  7084.69 &     IGRINS &      960 &    90 \\
+   HIP 31278 &  6668.71 &       TS23 &      797 &  1920 \\
+   HIP 31278 &  6947.01 &     IGRINS &      280 &   170 \\
+   HIP 31362 &  6598.72 &     CHIRON &     1200 &   250 \\
+   HIP 31434 &  6676.71 &       TS23 &      611 &  1480 \\
+   HIP 32474 &  6592.74 &     CHIRON &     1200 &   340 \\
+   HIP 32607 &  7037.75 &     CHIRON &       56 &   210 \\
+   HIP 32607 &  7039.62 &     CHIRON &       49 &   210 \\
+   HIP 32607 &  6724.56 &     CHIRON &       67 &   560 \\
+   HIP 33372 &  6948.00 &     IGRINS &      320 &   110 \\
+   HIP 33372 &  6678.72 &       TS23 &      720 &  1380 \\
+   HIP 33575 &  6599.72 &     CHIRON &     1200 &   390 \\
+   HIP 34769 &  6677.75 &       TS23 &      279 &  1520 \\
+   HIP 35180 &  6696.76 &     CHIRON &      925 &   290 \\
+   HIP 35341 &  6680.75 &       TS23 &      833 &  1070 \\
+   HIP 36393 &  6676.76 &       TS23 &      616 &  1550 \\
+   HIP 36393 &  6670.76 &       TS23 &      494 &  1400 \\
+   HIP 36760 &  7084.74 &     IGRINS &      720 &   150 \\
+   HIP 36760 &  7037.76 &     CHIRON &     4284 &   370 \\
+   HIP 36760 &  7039.68 &     CHIRON &     3127 &   480 \\
+   HIP 36760 &  6668.79 &       TS23 &      836 &   700 \\
+   HIP 36812 &  6947.99 &     IGRINS &      280 &   110 \\
+   HIP 36917 &  6583.81 &     CHIRON &      571 &   420 \\
+   HIP 36917 &  6971.83 &     CHIRON &      435 &   690 \\
+     HR 2948 &  6584.81 &     CHIRON &      576 &   370 \\
+   HIP 37297 &  6698.74 &     CHIRON &      370 &   480 \\
+   HIP 37297 &  6574.82 &     CHIRON &      686 &   340 \\
+   HIP 37297 &  6729.53 &     CHIRON &      231 &   460 \\
+   HIP 37322 &  6975.79 &     CHIRON &      817 &   540 \\
+   HIP 37450 &  6600.74 &     CHIRON &     1171 &   450 \\
+   HIP 38538 &  6669.78 &       TS23 &      474 &  1990 \\
+   HIP 38593 &  7039.70 &     CHIRON &      331 &   170 \\
+   HIP 38593 &  6599.82 &     CHIRON &     1200 &   410 \\
+   HIP 38593 &  6592.87 &     CHIRON &     1200 &   300 \\
+   HIP 38846 &  6601.76 &     CHIRON &     1098 &   400 \\
+   HIP 39095 &  6765.53 &     CHIRON &      430 &   450 \\
+   HIP 39095 &  6757.56 &     CHIRON &      238 &   490 \\
+   HIP 39095 &  6711.62 &     CHIRON &      288 &   500 \\
+   HIP 39236 &  6679.73 &       TS23 &      730 &  1420 \\
+   HIP 39567 &  6668.80 &       TS23 &      613 &  1940 \\
+   HIP 39847 &  7084.68 &     IGRINS &      480 &   160 \\
+   HIP 39847 &  6676.80 &       TS23 &      402 &  1500 \\
+   HIP 39906 &  6580.86 &     CHIRON &      457 &   270 \\
+   HIP 40429 &  6691.72 &     CHIRON &      710 &   560 \\
+   HIP 40706 &  6327.64 &     CHIRON &      277 &   630 \\
+   HIP 40881 &  6947.97 &     IGRINS &      240 &   100 \\
+   HIP 41039 &  7039.73 &     CHIRON &     1728 &   530 \\
+   HIP 41039 &  6330.77 &     CHIRON &      404 &   400 \\
+   HIP 41307 &  6667.82 &       TS23 &      700 &  1220 \\
+   HIP 42090 &  7124.62 &     IGRINS &      630 &   120 \\
+   HIP 42129 &  6603.80 &     CHIRON &     1001 &   370 \\
+   HIP 42313 &  6681.81 &       TS23 &      489 &  1020 \\
+   HIP 42334 &  6712.64 &     CHIRON &      381 &   480 \\
+   HIP 43142 &  6670.79 &       TS23 &      647 &  1980 \\
+   HIP 44127 &  6677.88 &       TS23 &      239 &  1600 \\
+   HIP 44307 &  6947.98 &     IGRINS &      280 &    80 \\
+   HIP 45336 &  6328.70 &     CHIRON &      171 &   290 \\
+   HIP 45336 &  7122.66 &     IGRINS &      270 &   130 \\
+   HIP 45336 &  7084.75 &     IGRINS &      240 &   140 \\
+   HIP 45344 &  6612.79 &     CHIRON &     1001 &   320 \\
+   HIP 45688 &  6299.93 &       TS23 &      600 &   880 \\
+   HIP 46225 &  6679.84 &       TS23 &      933 &  1300 \\
+   HIP 46283 &  6732.56 &     CHIRON &      357 &   490 \\
+   HIP 46283 &  6619.80 &     CHIRON &      872 &   430 \\
+   HIP 46283 &  6712.70 &     CHIRON &      352 &   450 \\
+   HIP 46897 &  7084.78 &     IGRINS &     1200 &    20 \\
+   HIP 46897 &  7139.59 &     IGRINS &      720 &   120 \\
+   HIP 47006 &  6677.03 &       TS23 &      373 &  1590 \\
+   HIP 47175 &  6424.56 &     CHIRON &      264 &   660 \\
+   HIP 50303 &  6677.78 &       TS23 &     1200 &  1350 \\
+   HIP 50860 &  6678.81 &       TS23 &     1151 &  1470 \\
+   HIP 51362 &  7043.79 &     CHIRON &     1298 &   340 \\
+   HIP 51362 &  6625.81 &     CHIRON &      947 &   200 \\
+   HIP 51362 &  6673.75 &     CHIRON &      606 &   510 \\
+   HIP 51362 &  7084.76 &     IGRINS &      720 &   100 \\
+   HIP 51685 &  6677.90 &       TS23 &     1046 &  1460 \\
+   HIP 52422 &  6676.87 &       TS23 &      522 &  1540 \\
+   HIP 52457 &  6676.83 &       TS23 &      647 &  1500 \\
+   HIP 52638 &  6669.83 &       TS23 &      711 &  1900 \\
+   HIP 52678 &  6748.56 &     CHIRON &      375 &   500 \\
+   HIP 52678 &  6690.70 &     CHIRON &      618 &   610 \\
+   HIP 52736 &  6748.52 &     CHIRON &      530 &   540 \\
+   HIP 52736 &  6713.70 &     CHIRON &      263 &   490 \\
+   HIP 52911 &  6670.86 &       TS23 &      758 &  1950 \\
+     HR 4259 &  6335.70 &     CHIRON &      304 &   330 \\
+   HIP 54849 &  6670.94 &       TS23 &      797 &  2080 \\
+   HIP 55266 &  6300.00 &       TS23 &      900 &   200 \\
+   HIP 55434 &  6332.77 &     CHIRON &      199 &   410 \\
+   HIP 56034 &  6676.91 &       TS23 &      502 &  1460 \\
+   HIP 56633 &  6669.91 &       TS23 &      447 &  1990 \\
+   HIP 56633 &  6335.75 &     CHIRON &      358 &   470 \\
+   HIP 57328 &  6338.68 &     CHIRON &      419 &   490 \\
+   HIP 57328 &  6370.62 &     CHIRON &      419 &   450 \\
+   HIP 58590 &  6338.72 &     CHIRON &      352 &   520 \\
+   HIP 59394 &  6754.57 &     CHIRON &      815 &   500 \\
+   HIP 59394 &  6690.78 &     CHIRON &      940 &   370 \\
+   HIP 59449 &  6711.88 &     CHIRON &      186 &   440 \\
+   HIP 59449 &  6641.76 &     CHIRON &      305 &   150 \\
+   HIP 59819 &  6669.96 &       TS23 &      465 &  1940 \\
+   HIP 60009 &  6370.66 &     CHIRON &      200 &   520 \\
+   HIP 60009 &  7009.78 &     CHIRON &      206 &   510 \\
+   HIP 60030 &  7084.81 &     IGRINS &     2400 &    80 \\
+   HIP 60595 &  6676.94 &       TS23 &      746 &  1540 \\
+   HIP 60710 &  7062.77 &     CHIRON &     1515 &   470 \\
+   HIP 60957 &  6678.92 &       TS23 &      904 &  1500 \\
+   HIP 61558 &  7139.67 &     IGRINS &     1440 &   180 \\
+   HIP 61558 &  7084.84 &     IGRINS &     1200 &    70 \\
+   HIP 61622 &  6378.69 &     CHIRON &      167 &   620 \\
+   HIP 62541 &  7124.80 &     IGRINS &      480 &   120 \\
+   HIP 62541 &  7084.86 &     IGRINS &     1500 &    80 \\
+   HIP 62576 &  7122.83 &     IGRINS &      546 &   130 \\
+   HIP 63724 &  6338.76 &     CHIRON &      412 &   560 \\
+   HIP 63724 &  6371.72 &     CHIRON &      412 &   630 \\
+   HIP 63945 &  6371.68 &     CHIRON &      362 &   560 \\
+   HIP 65198 &  7044.85 &     CHIRON &     3352 &   430 \\
+   HIP 65477 &  6670.01 &       TS23 &      207 &  2520 \\
+   HIP 65728 &  6677.98 &       TS23 &     1200 &  1710 \\
+   HIP 66249 &  6378.71 &     CHIRON &      110 &   520 \\
+   HIP 66798 &  6377.82 &        HRS &      362 &   610 \\
+   HIP 66821 &  6718.75 &     CHIRON &      610 &   540 \\
+   HIP 67143 &  7139.77 &     IGRINS &      480 &   120 \\
+   HIP 67194 &  6389.70 &        HRS &      368 &   740 \\
+   HIP 67782 &  6394.92 &        HRS &      359 &   680 \\
+   HIP 68092 &  7139.80 &     IGRINS &      840 &   200 \\
+   HIP 68520 &  6403.59 &     CHIRON &      239 &   470 \\
+   HIP 70327 &  7123.90 &     IGRINS &      420 &    90 \\
+   HIP 70327 &  6681.98 &       TS23 &     1152 &   230 \\
+   HIP 70327 &  6719.80 &     CHIRON &      368 &   460 \\
+   HIP 70384 &  6403.73 &        HRS &      420 &   560 \\
+   HIP 70400 &  6669.00 &       TS23 &      602 &  2000 \\
+   HIP 70915 &  7136.63 &     CHIRON &     3281 &   480 \\
+   HIP 70915 &  7090.71 &     CHIRON &     2985 &   460 \\
+     HR 5476 &  6408.71 &        HRS &      305 &   660 \\
+   HIP 71865 &  6383.71 &     CHIRON &      190 &   460 \\
+   HIP 71865 &  7060.80 &     CHIRON &     1205 &   500 \\
+   HIP 71974 &  7078.80 &     CHIRON &     3786 &   470 \\
+   HIP 72104 &  6720.86 &     CHIRON &      492 &   490 \\
+   HIP 72154 &  6403.75 &        HRS &      300 &   470 \\
+   HIP 72250 &  7070.72 &     CHIRON &     4025 &   490 \\
+   HIP 72378 &  7139.82 &     IGRINS &      720 &   140 \\
+   HIP 72552 &  7124.81 &     IGRINS &      600 &   110 \\
+   HIP 73049 &  6715.73 &     CHIRON &      749 &   530 \\
+     HR 5605 &  6383.74 &     CHIRON &      330 &   530 \\
+   HIP 74117 &  6383.77 &     CHIRON &      204 &   370 \\
+   HIP 74689 &  6872.52 &     CHIRON &      693 &   550 \\
+   HIP 75178 &  6678.99 &       TS23 &      815 &  1620 \\
+   HIP 75304 &  6427.78 &     CHIRON &      309 &   340 \\
+   HIP 76267 &  6380.88 &     CHIRON &       36 &   290 \\
+   HIP 76600 &  6380.91 &     CHIRON &      137 &   500 \\
+   HIP 76852 &  6426.65 &     CHIRON &      306 &   370 \\
+   HIP 77233 &  6426.69 &     CHIRON &      140 &   320 \\
+   HIP 77336 &  6396.79 &        HRS &      264 &   610 \\
+   HIP 77336 &  7122.91 &     IGRINS &      480 &   120 \\
+   HIP 77516 &  6380.89 &     CHIRON &      126 &   450 \\
+   HIP 77635 &  6725.72 &     CHIRON &      288 &   420 \\
+   HIP 77858 &  6733.75 &     CHIRON &      628 &   490 \\
+   HIP 78105 &  6870.54 &     CHIRON &      655 &   590 \\
+   HIP 78106 &  6736.70 &     CHIRON &      584 &   500 \\
+   HIP 78265 &  6766.77 &     CHIRON &       22 &   250 \\
+   HIP 78554 &  6427.74 &     CHIRON &      408 &   270 \\
+   HIP 78820 &  6380.93 &     CHIRON &       53 &   490 \\
+   HIP 78820 &  7139.83 &     IGRINS &      120 &   190 \\
+   HIP 78820 &  7060.85 &     CHIRON &      263 &   360 \\
+   HIP 78820 &  7156.63 &     CHIRON &      164 &   390 \\
+   HIP 78821 &  7139.84 &     IGRINS &      210 &    50 \\
+     HR 6025 &  6847.83 &     IGRINS &      600 &   100 \\
+   HIP 78918 &  6718.86 &     CHIRON &      300 &   610 \\
+   HIP 78933 &  6737.76 &     CHIRON &       77 &   250 \\
+   HIP 79005 &  7090.77 &     CHIRON &     4646 &   430 \\
+   HIP 79007 &  6874.48 &     CHIRON &      659 &   550 \\
+   HIP 79199 &  6734.71 &     CHIRON &      451 &   470 \\
+   HIP 79387 &  6746.75 &     CHIRON &      573 &   500 \\
+   HIP 79404 &  6415.77 &     CHIRON &      324 &   470 \\
+   HIP 79404 &  7076.81 &     CHIRON &     1307 &   430 \\
+   HIP 79404 &  7090.88 &     CHIRON &     1135 &   450 \\
+   HIP 79653 &  6740.79 &     CHIRON &      469 &   490 \\
+   HIP 80460 &  7122.93 &     IGRINS &      720 &   110 \\
+   HIP 80815 &  6378.86 &     CHIRON &      393 &   530 \\
+   HIP 80883 &  6378.84 &     CHIRON &      174 &   550 \\
+   HIP 80991 &  6389.86 &        HRS &      404 &   720 \\
+   HIP 81126 &  7122.95 &     IGRINS &      720 &   150 \\
+   HIP 81641 &  6404.83 &        HRS &      320 &   540 \\
+   HIP 82350 &  6391.84 &        HRS &      404 &   660 \\
+   HIP 82514 &  6726.81 &     CHIRON &       34 &   250 \\
+   HIP 82673 &  6871.58 &     CHIRON &      250 &   310 \\
+   HIP 82673 &  6410.86 &     CHIRON &      272 &   180 \\
+   HIP 83635 &  6407.86 &        HRS &      316 &   480 \\
+   HIP 84606 &  6945.54 &     IGRINS &      224 &   150 \\
+   HIP 85290 &  6946.56 &     IGRINS &      224 &   120 \\
+   HIP 85379 &  6398.85 &        HRS &      330 &   740 \\
+   HIP 85385 &  6848.83 &     IGRINS &      480 &    80 \\
+   HIP 85537 &  7096.88 &     CHIRON &     4227 &   570 \\
+   HIP 85537 &  6792.73 &     CHIRON &      900 &   600 \\
+   HIP 85537 &  6848.73 &     IGRINS &      240 &    60 \\
+   HIP 85727 &  6771.85 &     CHIRON &      175 &   570 \\
+   HIP 85922 &  6847.82 &     IGRINS &      480 &   120 \\
+   HIP 85922 &  7139.95 &     IGRINS &      240 &   170 \\
+   HIP 85922 &  6886.56 &     CHIRON &      791 &   590 \\
+   HIP 85922 &  7103.85 &     CHIRON &     2543 &   370 \\
+   HIP 85922 &  7104.82 &     CHIRON &     7386 &   360 \\
+   HIP 85998 &  7122.96 &     IGRINS &      480 &    50 \\
+   HIP 85998 &  7230.64 &     IGRINS &      720 &   170 \\
+   HIP 85998 &  6407.84 &        HRS &      324 &   490 \\
+   HIP 85998 &  7079.89 &     CHIRON &     1600 &   220 \\
+   HIP 86019 &  6747.85 &     CHIRON &      228 &   510 \\
+   HIP 86782 &  6404.85 &        HRS &      310 &   500 \\
+   HIP 87108 &  6847.87 &     IGRINS &      120 &   120 \\
+   HIP 87108 &  6445.79 &     CHIRON &      152 &   300 \\
+   HIP 88116 &  6488.71 &     CHIRON &      373 &   590 \\
+   HIP 88116 &  6876.54 &     CHIRON &      320 &   380 \\
+   HIP 88290 &  6873.59 &     CHIRON &      365 &   540 \\
+   HIP 88818 &  7122.98 &     IGRINS &      960 &    90 \\
+   HIP 88818 &  7230.66 &     IGRINS &      600 &   110 \\
+   HIP 88818 &  6397.85 &        HRS &      355 &   510 \\
+   HIP 88817 &  7123.00 &     IGRINS &      960 &   100 \\
+   HIP 88817 &  6405.84 &        HRS &      400 &   720 \\
+   HIP 89156 &  6405.82 &        HRS &      470 &   610 \\
+   HIP 89935 &  6848.85 &     IGRINS &      240 &   100 \\
+   HIP 89935 &  6945.56 &     IGRINS &      224 &   250 \\
+   HIP 90052 &  6405.88 &        HRS &      500 &   760 \\
+   HIP 90762 &  6848.85 &     IGRINS &      480 &    80 \\
+   HIP 90762 &  6945.57 &     IGRINS &      480 &   200 \\
+   HIP 90887 &  6748.80 &     CHIRON &      710 &   560 \\
+   HIP 91118 &  6945.58 &     IGRINS &      360 &   190 \\
+   HIP 91875 &  6745.81 &     CHIRON &      680 &   580 \\
+   HIP 92027 &  6405.91 &        HRS &      360 &   570 \\
+   HIP 92312 &  6408.88 &        HRS &      390 &   650 \\
+   HIP 92728 &  6405.86 &        HRS &      280 &   560 \\
+   HIP 92855 &  6880.57 &     CHIRON &       30 &   550 \\
+   HIP 92855 &  6415.80 &     CHIRON &       32 &   400 \\
+   HIP 92946 &  6475.79 &     CHIRON &      339 &   500 \\
+   HIP 93225 &  6946.54 &     IGRINS &      224 &    80 \\
+   HIP 93225 &  6516.69 &     CHIRON &     1200 &   540 \\
+   HIP 93225 &  6962.56 &       TS23 &      562 &  1430 \\
+   HIP 93393 &  6404.88 &        HRS &      320 &   540 \\
+   HIP 93580 &  7116.84 &     CHIRON &     5594 &   520 \\
+   HIP 93580 &  6848.84 &     IGRINS &      480 &   100 \\
+   HIP 93713 &  6848.87 &     IGRINS &      600 &    90 \\
+   HIP 93747 &  6587.54 &       TS23 &       85 &  1880 \\
+   HIP 93805 &  6852.82 &     IGRINS &     2640 &    60 \\
+   HIP 93805 &  7139.96 &     IGRINS &      120 &   210 \\
+   HIP 93805 &  6775.78 &     CHIRON &      150 &   520 \\
+   HIP 94620 &  6848.88 &     IGRINS &      480 &   100 \\
+   HIP 94720 &  6517.78 &        HRS &      400 &   880 \\
+   HIP 95241 &  6869.63 &     CHIRON &      325 &   120 \\
+   HIP 95241 &  6508.80 &     CHIRON &      294 &   600 \\
+   HIP 95241 &  6459.89 &     CHIRON &      183 &   360 \\
+   HIP 95560 &  6848.89 &     IGRINS &      480 &   110 \\
+   HIP 95619 &  7139.97 &     IGRINS &      480 &   120 \\
+   HIP 95619 &  7118.79 &     CHIRON &     3451 &   320 \\
+   HIP 95619 &  6523.61 &     CHIRON &      768 &   670 \\
+   HIP 95853 &  6585.54 &       TS23 &      129 &  2010 \\
+   HIP 96288 &  6585.56 &       TS23 &      489 &  1860 \\
+   HIP 96840 &  6408.92 &        HRS &      552 &   940 \\
+   HIP 97376 &  6848.90 &     IGRINS &     1680 &    70 \\
+   HIP 97496 &  6584.54 &       TS23 &      342 &  1820 \\
+   HIP 97870 &  6517.81 &        HRS &      185 &   830 \\
+   HIP 97966 &  6925.51 &     CHIRON &      655 &   380 \\
+   HIP 97966 &  6881.70 &     CHIRON &     1158 &   660 \\
+   HIP 98055 &  6586.54 &       TS23 &      320 &  1820 \\
+   HIP 98194 &  6583.54 &       TS23 &      495 &  1750 \\
+   HIP 98325 &  6587.56 &       TS23 &      543 &  1750 \\
+   HIP 99080 &  6583.63 &       TS23 &      358 &  1740 \\
+   HIP 99742 &  6945.59 &     IGRINS &      224 &   210 \\
+  HIP 100069 &  6409.91 &        HRS &      451 &   560 \\
+  HIP 100221 &  7230.72 &     IGRINS &     1100 &    80 \\
+  HIP 100221 &  6523.79 &        HRS &      874 &   830 \\
+  HIP 100881 &  6511.69 &     CHIRON &     1011 &   570 \\
+  HIP 100907 &  6946.57 &     IGRINS &      224 &   120 \\
+  HIP 100907 &  7230.67 &     IGRINS &      600 &   120 \\
+  HIP 101123 &  6945.70 &     IGRINS &      224 &   160 \\
+  HIP 101589 &  6448.83 &     CHIRON &      352 &   420 \\
+  HIP 101716 &  6582.60 &       TS23 &      549 &  1260 \\
+  HIP 101867 &  6489.78 &     CHIRON &      408 &   440 \\
+  HIP 101909 &  6945.60 &     IGRINS &      360 &   140 \\
+  HIP 101909 &  7230.69 &     IGRINS &      720 &    90 \\
+  HIP 102487 &  6847.80 &     IGRINS &      480 &    80 \\
+  HIP 103298 &  6946.58 &     IGRINS &      224 &   100 \\
+  HIP 103298 &  7230.70 &     IGRINS &      600 &    80 \\
+  HIP 103298 &  7155.93 &     CHIRON &     1141 &   290 \\
+  HIP 104019 &  6474.90 &     CHIRON &      423 &   550 \\
+  HIP 104105 &  6945.69 &     IGRINS &      280 &   140 \\
+  HIP 104139 &  6448.90 &     CHIRON &      204 &   490 \\
+  HIP 104365 &  6847.81 &     IGRINS &      480 &   100 \\
+  HIP 104365 &  7237.82 &     IGRINS &      720 &    50 \\
+  HIP 105140 &  6485.90 &     CHIRON &      372 &   420 \\
+  HIP 105282 &  6522.65 &        HRS &     1006 &   850 \\
+  HIP 105891 &  6946.59 &     IGRINS &      224 &    90 \\
+  HIP 105942 &  6523.87 &        HRS &      480 &   760 \\
+  HIP 105966 &  6585.64 &       TS23 &      530 &  1800 \\
+  HIP 105972 &  6507.82 &        HRS &      267 &   690 \\
+  HIP 106711 &  6584.60 &       TS23 &      689 &   700 \\
+  HIP 106711 &  6618.53 &       TS23 &      557 &  2010 \\
+  HIP 106786 &  6945.64 &     IGRINS &      224 &   230 \\
+  HIP 106786 &  6962.59 &       TS23 &      284 &  1620 \\
+  HIP 106786 &  6794.81 &     CHIRON &      232 &   470 \\
+  HIP 107517 &  6873.74 &     CHIRON &     1025 &   490 \\
+  HIP 107608 &  6788.84 &     CHIRON &      620 &   470 \\
+  HIP 108294 &  6790.81 &     CHIRON &      470 &   510 \\
+  HIP 108339 &  6945.65 &     IGRINS &      224 &   160 \\
+  HIP 109056 &  6945.66 &     IGRINS &      240 &   150 \\
+  HIP 109056 &  6948.56 &     IGRINS &     1156 &   160 \\
+  HIP 109056 &  6946.65 &     IGRINS &      784 &   230 \\
+  HIP 109056 &  6947.57 &     IGRINS &     1746 &   170 \\
+  HIP 109139 &  6524.67 &     CHIRON &      207 &   590 \\
+  HIP 109139 &  6447.91 &     CHIRON &      248 &   470 \\
+  HIP 109521 &  6586.58 &       TS23 &      511 &  1860 \\
+  HIP 109521 &  6962.60 &       TS23 &      587 &  1500 \\
+  HIP 109521 &  6945.68 &     IGRINS &      224 &   200 \\
+  HIP 109831 &  6945.67 &     IGRINS &      224 &   160 \\
+  HIP 109831 &  7237.77 &     IGRINS &     1440 &   100 \\
+  HIP 109831 &  7288.73 &     IGRINS &      900 &    30 \\
+  HIP 110838 &  6543.82 &     CHIRON &      506 &   550 \\
+  HIP 110838 &  6880.76 &     CHIRON &      354 &   780 \\
+  HIP 110935 &  6896.67 &     CHIRON &      696 &   630 \\
+  HIP 111056 &  7288.80 &     IGRINS &      180 &    30 \\
+  HIP 111056 &  6945.76 &     IGRINS &      224 &   120 \\
+  HIP 111068 &  6512.74 &        HRS &      362 &   500 \\
+  HIP 111169 &  6585.62 &       TS23 &      121 &  1900 \\
+  HIP 111841 &  6583.68 &       TS23 &      267 &  1670 \\
+  HIP 112029 &  6487.85 &     CHIRON &      109 &   460 \\
+  HIP 112029 &  6892.74 &     CHIRON &       95 &   250 \\
+  HIP 113788 &  6586.63 &       TS23 &      367 &  1830 \\
+  HIP 114520 &  6587.64 &       TS23 &      541 &  1880 \\
+  HIP 114822 &  6886.68 &     CHIRON &      715 &   550 \\
+  HIP 114822 &  6884.68 &     CHIRON &      530 &   530 \\
+  HIP 115115 &  7163.90 &     CHIRON &      600 &   190 \\
+  HIP 115115 &  7230.95 &     IGRINS &      500 &    40 \\
+  HIP 115115 &  6797.87 &     CHIRON &      610 &   330 \\
+  HIP 116247 &  6463.89 &     CHIRON &      368 &   560 \\
+  HIP 116247 &  7237.94 &     IGRINS &      240 &   100 \\
+  HIP 116582 &  6510.77 &        HRS &      534 &   670 \\
+  HIP 116611 &  6946.61 &     IGRINS &      224 &   140 \\
+  HIP 116631 &  6962.63 &       TS23 &      249 &  1980 \\
+  HIP 116631 &  6946.78 &     IGRINS &      224 &   160 \\
+  HIP 116631 &  6583.71 &       TS23 &      162 &  1740 \\
+  HIP 116631 &  7288.80 &     IGRINS &      180 &    30 \\
+  HIP 116805 &  6528.84 &       TS23 &      158 &  1680 \\
+  HIP 116971 &  6527.85 &       TS23 &      407 &  1650 \\
+  HIP 116971 &  6487.88 &     CHIRON &      298 &   540 \\
+  HIP 116971 &  6555.56 &     CHIRON &      497 &   430 \\
+  HIP 116971 &  6869.76 &     CHIRON &      380 &   110 \\
+  HIP 116971 &  6936.73 &     CHIRON &      344 &   600 \\
+  HIP 117089 &  7288.81 &     IGRINS &      180 &    20 \\
+  HIP 117089 &  7237.95 &     IGRINS &      720 &    60 \\
+  HIP 117089 &  6513.86 &     CHIRON &      853 &   600 \\
+  HIP 117371 &  6586.67 &       TS23 &      349 &  1760 \\
+  HIP 117452 &  6469.90 &     CHIRON &      327 &   540 \\
+  HIP 118121 &  6795.86 &     CHIRON &      233 &   500 \\
+  HIP 118243 &  6945.73 &     IGRINS &      224 &   170 \\
+  HIP 118243 &  6583.74 &       TS23 &      351 &  1760
 \enddata
-
 \label{tab:observations}
-\end{deluxetable*}
+\end{deluxetable}
+
+\clearpage
 
@@
 \tablehead{
-       \colhead{star} &  \colhead{Kmag} &   \colhead{date} & \colhead{Exposure} & \colhead{$\rho$} & \colhead{$\theta$} & \colhead{$\Delta \mathrm{K_c}$}
+       \colhead{star} &  \colhead{K} &   \colhead{date} & \colhead{Exposure} & \colhead{$\rho$} & \colhead{$\theta$} & \colhead{$\Delta \mathrm{K_c}$}
        }
@@
 
-\LongTables
-\begin{deluxetable*}{|l|lllll|}
-\tabletypesize{\small}
-\tablewidth{0pt}
-\tablecaption{Primary Star Fundamental Parameters}
-\tablehead{
-      \colhead{}  &  \colhead{$T_\mathrm{eff}$} &  \colhead{$\log{g}$} &  \colhead{Mass}          & \colhead{Age} & \colhead{} \\
-   \colhead{star} &  \colhead{(K)}              &  \colhead{(cgs)}     &  \colhead{($M_{\odot}$)} &  \colhead{(Myr)} & \colhead{source}
-       }
-
-\startdata
-   HIP 2548 &   $11864 \pm 403$ &  $4.4 \pm 0.14$ &  $2.8^{+0.16}_{-0.15}$ &     $79^{+68}_{-53}$ &      DH2015 \\
-   HIP 5310 &    $8611 \pm 293$ &  $4.4 \pm 0.14$ &  $1.8^{+0.10}_{-0.08}$ &  $306^{+236}_{-196}$ &      DH2015 \\
-     HR 545 &  $11000 \pm 1000$ &  $4.3 \pm 0.25$ &  $2.5^{+0.39}_{-0.35}$ &    $37^{+105}_{-28}$ &  This Study \\
-     HR 604 &  $11000 \pm 1000$ &  $4.5 \pm 0.25$ &  $2.4^{+0.37}_{-0.34}$ &     $28^{+87}_{-20}$ &  This Study \\
-  HIP 10732 &    $9500 \pm 300$ &  $4.0 \pm 0.25$ &  $2.1^{+0.18}_{-0.16}$ &    $80^{+237}_{-70}$ &  This Study \\
-  HIP 12332 &    $7750 \pm 300$ &  $3.5 \pm 0.25$ &  $1.9^{+0.37}_{-0.30}$ &  $687^{+218}_{-425}$ &  This Study \\
-  HIP 12706 &    $8551 \pm 291$ &  $4.3 \pm 0.14$ &  $1.9^{+0.15}_{-0.12}$ &  $650^{+104}_{-180}$ &      DH2015 \\
-  HIP 13165 &  $15000 \pm 1000$ &  $4.0 \pm 0.25$ &  $4.2^{+0.58}_{-0.50}$ &     $31^{+42}_{-22}$ &  This Study \\
-  HIP 13327 &  $15000 \pm 1000$ &  $4.5 \pm 0.25$ &  $4.0^{+0.50}_{-0.45}$ &      $15^{+26}_{-9}$ &  This Study \\
-  HIP 14576 &   $13070 \pm 444$ &  $4.0 \pm 0.14$ &  $3.6^{+0.29}_{-0.23}$ &    $139^{+17}_{-25}$ &      DH2015 \\
-  HIP 14764 &  $11750 \pm 1000$ &  $4.2 \pm 0.25$ &  $2.8^{+0.42}_{-0.39}$ &     $35^{+91}_{-27}$ &  This Study \\
-  HIP 16244 &  $16333 \pm 1000$ &  $4.3 \pm 0.25$ &  $4.7^{+0.57}_{-0.50}$ &      $15^{+22}_{-9}$ &  This Study \\
-  HIP 16340 &  $12500 \pm 1000$ &  $4.0 \pm 0.25$ &  $3.1^{+0.51}_{-0.42}$ &     $49^{+92}_{-39}$ &  This Study \\
-  HIP 18724 &  $21000 \pm 1000$ &  $4.5 \pm 0.25$ &  $7.1^{+0.68}_{-0.64}$ &        $8^{+7}_{-3}$ &  This Study \\
-  HIP 19949 &    $9825 \pm 334$ &  $3.8 \pm 0.14$ &  $2.2^{+0.11}_{-0.10}$ &  $198^{+136}_{-125}$ &      DH2015 \\
-  HIP 20380 &    $8738 \pm 297$ &  $3.9 \pm 0.14$ &  $1.9^{+0.09}_{-0.08}$ &  $339^{+210}_{-207}$ &      DH2015 \\
-  HIP 21589 &    $8591 \pm 292$ &  $3.9 \pm 0.14$ &  $1.8^{+0.09}_{-0.07}$ &  $302^{+225}_{-196}$ &      DH2015 \\
-  HIP 22833 &    $8278 \pm 281$ &  $3.9 \pm 0.14$ &  $1.8^{+0.12}_{-0.09}$ &  $649^{+163}_{-295}$ &      DH2015 \\
-  HIP 22958 &  $16000 \pm 1000$ &  $4.5 \pm 0.25$ &  $4.5^{+0.53}_{-0.50}$ &      $14^{+21}_{-8}$ &  This Study \\
-  HIP 23362 &   $12450 \pm 423$ &  $4.3 \pm 0.14$ &  $3.2^{+0.20}_{-0.16}$ &    $147^{+29}_{-58}$ &      DH2015 \\
-  HIP 23916 &  $16500 \pm 1000$ &  $4.2 \pm 0.25$ &  $4.8^{+0.56}_{-0.52}$ &     $16^{+26}_{-10}$ &  This Study \\
-  HIP 24902 &    $8275 \pm 281$ &  $4.0 \pm 0.14$ &  $1.7^{+0.10}_{-0.08}$ &  $466^{+252}_{-286}$ &      DH2015 \\
-  HIP 26126 &    $9542 \pm 324$ &  $3.9 \pm 0.14$ &  $2.1^{+0.09}_{-0.08}$ &  $175^{+148}_{-112}$ &      DH2015 \\
-  HIP 32607 &    $7770 \pm 264$ &  $3.8 \pm 0.14$ &  $1.6^{+0.07}_{-0.06}$ &  $519^{+342}_{-335}$ &      DH2015 \\
-  HIP 38538 &    $8551 \pm 291$ &  $4.0 \pm 0.14$ &  $1.9^{+0.14}_{-0.12}$ &  $637^{+109}_{-211}$ &      DH2015 \\
-  HIP 38593 &  $21667 \pm 1000$ &  $4.5 \pm 0.25$ &  $7.6^{+0.74}_{-0.68}$ &        $8^{+6}_{-3}$ &  This Study \\
-  HIP 38846 &  $22000 \pm 1000$ &  $4.5 \pm 0.25$ &  $7.8^{+0.74}_{-0.71}$ &        $8^{+6}_{-3}$ &  This Study \\
-  HIP 39847 &   $10014 \pm 340$ &  $4.0 \pm 0.14$ &  $2.2^{+0.13}_{-0.12}$ &  $195^{+131}_{-121}$ &      DH2015 \\
-  HIP 40881 &    $9500 \pm 300$ &  $4.0 \pm 0.25$ &  $2.1^{+0.17}_{-0.16}$ &    $71^{+239}_{-60}$ &  This Study \\
-  HIP 42129 &  $18000 \pm 1000$ &  $4.5 \pm 0.25$ &  $5.4^{+0.63}_{-0.54}$ &      $11^{+14}_{-5}$ &  This Study \\
-  HIP 52678 &  $15000 \pm 1000$ &  $4.5 \pm 0.25$ &  $4.0^{+0.49}_{-0.50}$ &     $16^{+26}_{-10}$ &  This Study \\
-  HIP 55266 &    $8720 \pm 296$ &  $4.5 \pm 0.14$ &  $1.9^{+0.09}_{-0.07}$ &  $346^{+209}_{-215}$ &      DH2015 \\
-  HIP 63945 &  $18000 \pm 1000$ &  $4.5 \pm 0.25$ &  $5.4^{+0.60}_{-0.56}$ &      $11^{+14}_{-5}$ &  This Study \\
-  HIP 72154 &  $10500 \pm 1000$ &  $4.5 \pm 0.25$ &  $2.3^{+0.36}_{-0.33}$ &    $32^{+101}_{-24}$ &  This Study \\
-  HIP 76267 &   $10342 \pm 352$ &  $4.0 \pm 0.14$ &  $2.5^{+0.19}_{-0.16}$ &    $314^{+53}_{-99}$ &      DH2015 \\
-  HIP 77336 &    $8917 \pm 303$ &  $4.0 \pm 0.14$ &  $2.9^{+0.23}_{-0.20}$ &    $404^{+73}_{-70}$ &      DH2015 \\
-  HIP 77516 &    $9250 \pm 300$ &  $4.0 \pm 0.25$ &  $2.1^{+0.17}_{-0.16}$ &    $74^{+275}_{-64}$ &  This Study \\
-  HIP 78820 &  $24062 \pm 1000$ &  $3.9 \pm 0.25$ &  $9.2^{+0.51}_{-0.64}$ &        $9^{+6}_{-4}$ &  This Study \\
-  HIP 79199 &  $12500 \pm 1000$ &  $4.5 \pm 0.25$ &  $3.0^{+0.42}_{-0.39}$ &     $23^{+55}_{-16}$ &  This Study \\
-  HIP 79404 &  $21667 \pm 1000$ &  $4.5 \pm 0.25$ &  $7.6^{+0.75}_{-0.69}$ &        $8^{+6}_{-3}$ &  This Study \\
-  HIP 80460 &    $7810 \pm 266$ &  $3.7 \pm 0.14$ &  $1.7^{+0.11}_{-0.08}$ &  $783^{+232}_{-394}$ &      DH2015 \\
-  HIP 82673 &  $11750 \pm 1000$ &  $3.5 \pm 0.25$ &  $3.4^{+0.65}_{-0.57}$ &    $171^{+73}_{-64}$ &  This Study \\
-  HIP 84606 &    $9702 \pm 330$ &  $4.0 \pm 0.14$ &  $2.1^{+0.10}_{-0.09}$ &   $154^{+137}_{-99}$ &      DH2015 \\
-%  HIP 85379 &    $8250 \pm 300$ &  $3.5 \pm 0.25$ &  $2.1^{+0.37}_{-0.34}$ &  $550^{+154}_{-260}$ &  This Study \\
-  HIP 85998 &    $8812 \pm 300$ &  $4.0 \pm 0.25$ &  $1.9^{+0.16}_{-0.13}$ &    $95^{+332}_{-84}$ &  This Study \\
-  HIP 88116 &    $9750 \pm 300$ &  $3.5 \pm 0.25$ &  $2.7^{+0.43}_{-0.39}$ &   $305^{+68}_{-150}$ &  This Study \\
-  HIP 88817 &    $9162 \pm 312$ &  $4.3 \pm 0.14$ &  $2.1^{+0.16}_{-0.12}$ &   $480^{+84}_{-168}$ &      DH2015 \\
-  HIP 88818 &    $9162 \pm 312$ &  $4.3 \pm 0.14$ &  $2.7^{+0.24}_{-0.23}$ &    $441^{+86}_{-72}$ &      DH2015 \\
-  HIP 91118 &    $9500 \pm 300$ &  $4.0 \pm 0.25$ &  $2.1^{+0.19}_{-0.15}$ &    $70^{+244}_{-60}$ &  This Study \\
-  HIP 93805 &   $11962 \pm 407$ &  $4.2 \pm 0.14$ &  $3.5^{+0.32}_{-0.26}$ &    $194^{+19}_{-21}$ &      DH2015 \\
-  HIP 96840 &  $17000 \pm 1000$ &  $4.5 \pm 0.25$ &  $4.9^{+0.57}_{-0.53}$ &    $12^{+17}_{-6}$ &  This Study \\
- HIP 100221 &    $9750 \pm 300$ &  $4.5 \pm 0.25$ &  $2.2^{+0.15}_{-0.15}$ &    $34^{+110}_{-26}$ &  This Study \\
- HIP 100907 &    $9042 \pm 307$ &  $4.0 \pm 0.14$ &  $2.1^{+0.16}_{-0.13}$ &  $512^{+100}_{-168}$ &      DH2015 \\
- HIP 103298 &    $9093 \pm 309$ &  $4.1 \pm 0.14$ &  $2.0^{+0.13}_{-0.11}$ &  $399^{+146}_{-209}$ &      DH2015 \\
- HIP 109139 &   $12641 \pm 430$ &  $4.3 \pm 0.14$ &  $3.2^{+0.20}_{-0.16}$ &    $122^{+38}_{-61}$ &      DH2015 \\
- HIP 109521 &    $8420 \pm 286$ &  $4.2 \pm 0.14$ &  $2.0^{+0.19}_{-0.16}$ &  $728^{+109}_{-104}$ &      DH2015 \\
- HIP 115115 &   $10671 \pm 363$ &  $4.2 \pm 0.14$ &  $2.6^{+0.19}_{-0.16}$ &    $284^{+38}_{-81}$ &      DH2015
-\label{tab:primary}
-\end{deluxetable*}
-
 \newpage

### 2016-02-19 paper/ms.tex
Included short discussion of companion feh values.
Fixed references to tab:primary

@@
 The $v\sin{i}$ and metallicity values do not have uncertainties and should only be taken as a rough estimate of the true value.
+The mean and standard deviation of the companion metallicities is $-0.29 \pm 0.30$; the marginal bias towards low metallicities is most likely a measurement bias and does not reflect the true companion population \citep{Gullikson2016}.
 We show the detection CCFs and a plot of peak CCF height as a function of model temperature for HIP 109139 in Figure \ref{fig:ccf}.
@@
 \end{figure}
+
+We show the temperature, surface gravity, mass, and age estimates for all primary stars in Table \ref{tab:sample}.
+The MCMC samples generated by the isochrones code are available at [GIVE ZENODO LINK OR SOMETHING].
 
@@
 We estimate the convective timescale ($\tau$) by interpolating Table 1 of \citet{Barnes2010a}.
-We then randomly sample the system age $t$ from its probability distribution function (see Section \ref{sec:sp} and Table \ref{tab:primary}).
+We then randomly sample the system age $t$ from its probability distribution function (see Section \ref{sec:sp} and Table \ref{tab:sample}).
 Young stars have rotation periods in the range of 0.2 to 10 days \citep{Bouvier2014}, so we randomly choose an initial rotation period $P_0$ from a log-uniform distribution in this range for each age sample.
@@
 The "Ref" column denotes the reference for the stellar effective temperature, surface gravity, mass, and age.
-The references are: [1]: \citep{David2015}; [2]: This study.}
+The references are: [1]: \citep{David2015}; [2]: This study.
+We only estimate stellar parameters for the stars in which we detect a companion.}
 \label{tab:sample}
@@
   HIP 77516 & AB &     1 & yes &  $6825 \pm 141$ &       5 &     0.5  &  $1.4^{+0.21}_{-0.06}$ &  $1.4^{+0.03}_{-0.04}$ \\
-  HIP 78820 & AB &     1 & no &  $5658 \pm 158$ &       5 &    -0.5 0 &  $1.3^{+0.11}_{-0.13}$ &  $1.0^{+0.04}_{-0.04}$ \\
+  HIP 78820 & AB &     1 & no &  $5658 \pm 158$ &       5 &    0 &  $1.3^{+0.11}_{-0.13}$ &  $1.0^{+0.04}_{-0.04}$ \\
   HIP 79199 & AB &     1 & no &  $4616 \pm 158$ &       5 &    -0.5  &  $0.9^{+0.14}_{-0.14}$ &  $0.8^{+0.02}_{-0.03}$ \\

### 2016-02-19 paper/ms.tex

@@
 
-Nonetheless, \citet{DeRosa2014} performed an adaptive optics imaging survey of nearby A-type stars; they found initial evidence that the mass ratio distribution for companions inside $125$ AU has a much shallower power law slope than that of wide companions.
-Unfortunately they had only very few detections at these near separations, and the result is complicated by the inherent difficulty of detecting close companions with low mass ratios in an imaging survey.
-Additionally, spectroscopic companions to chemically peculiar Am stars appear to have a mass ratio distribution which peaks near $q \sim 0.5$ \citep{Vuissoz2004}.
+Nonetheless, \citet{DeRosa2014} performed an adaptive optics imaging survey of nearby A-type stars, and found that the mass ratio distribution is well-described by a power law with large slope, indicating a very strong preference for low-mass companions.
+They also found initial evidence that the mass ratio distribution for companions inside $125$ AU has a much shallower power law slope than that of wide companions, and is consistent with flat.
+Unfortunately the close companion subsample contained only 18 binary systems, and the result is complicated by the inherent difficulty of detecting close companions with low mass ratios in an imaging survey.
+
+Spectroscopic companions to chemically peculiar Am stars appear to have a mass ratio distribution which peaks near $q \sim 0.5$ \citep{Vuissoz2004}.
 Am stars are typically associated with binary companions, and are slow rotators due to tidal braking; they thus form a highly biased sample of intermediate-mass stars.
-
-In this paper, we describe a spectroscopic survey of nearby normal, main sequence intermediate-mass stars.
+It is however interesting that the inner mass ratio distribution around these chemically peculiar stars has an entirely different form than the distribution around chemically normal stars at wide separations probed by imaging.
+
+In this paper, we describe a spectroscopic survey of nearby chemically normal, main sequence intermediate-mass stars ($M \approx 1.5 - 15 M_{\odot}$).
 We search for companions using the direct spectral detection technique \citep{Gullikson2016}, which has a separation-invariant detection rate for all separations inside $\sim 1 ''$.
@@
 The sample is given in Table \ref{tab:sample}.
+The spectral type, coordinates, V magnitude, and parallax are all pulled from the Simbad Database \citep{Simbad}.
 
 \subsection{Spectroscopic Data}
+\label{subsec:specdata}
 We use several high spectral resolution, cross-dispersed \'echelle spectrographs for this survey.
@@
 We reduce the data using an IRAF pipeline very similar to the ones we use for CHIRON and HRS, and wavelength calibrate using a Th-Ar lamp observed immediately before the science observations.
-
-IGRINS only has one setting with $R = 40000$.
-It has complete wavelength coverage from $1475-2480$ nm, except in the telluric water band from $1810 - 1930$ nm.
-Each star is observed in an ABBA nodding mode, and reduced using the standard IGRINS pipeline \citep{IGRINS_plp_v2}.
-The standard pipeline uses atmospheric OH emission lines as well as a Th-Ar calibration frame to calibrate the wavelengths; we further refine the wavelength solution using telluric absorption lines in the science spectrum.
-
-After reducing the data, we fit and remove the telluric spectrum using the TelFit code \citep{Gullikson2014}.
-We fit each \'echelle order affected by telluric absorption independently from each other to get the best removal.
-The telluric correction is critical for IGRINS spectra, where every order is dominated by telluric absorption lines.
-For the optical spectra, it is less critical but allows us to use some of the redder orders than we otherwise would be able to.
-For unsaturated lines, the best-fit telluric model reproduces the data to within $\sim 1-5\%$ of the continuum level.
-
-We give the spectroscopic observation log in Table \ref{tab:observations}.
-We calculate the signal-to-noise ratio (the "snr" column) for the optical instruments (CHIRON, TS23, and HRS) as the median of the extracted flux divided by it's uncertainty for each pixel from the \'echelle order nearest $675$ nm.
-For the IGRINS instrument, we calculate the signal-to-noise ratio from the order nearest $2200$ nm.
-
-TODO: MAKE THE SPECTRA AVAILABLE SOMEHOW...
 
@@
 \end{figure*}
+
+IGRINS only has one setting with $R = 40000$.
+It has complete wavelength coverage from $1475-2480$ nm, except in the telluric water band from $1810 - 1930$ nm.
+Each star is observed in an ABBA nodding mode, and reduced using the standard IGRINS pipeline \citep{IGRINS_plp_v2}.
+The standard pipeline uses atmospheric OH emission lines as well as a Th-Ar calibration frame to calibrate the wavelengths; we further refine the wavelength solution using telluric absorption lines in the science spectrum.
+
+After reducing the data, we fit and remove the telluric spectrum using the TelFit code \citep{Gullikson2014}.
+We fit each \'echelle order affected by telluric absorption independently from each other to get the best removal.
+The telluric correction is critical for IGRINS spectra, where every order is dominated by telluric absorption lines.
+For the optical spectra, it is less critical but allows us to use some of the redder orders than we otherwise would be able to.
+For unsaturated lines, the best-fit telluric model reproduces the data to within $\sim 1-5\%$ of the continuum level.
+
+We give the spectroscopic observation log in Table \ref{tab:observations}.
+We calculate the signal-to-noise ratio (the "snr" column) for the optical instruments (CHIRON, TS23, and HRS) as the median of the extracted flux divided by it's uncertainty for each pixel from the \'echelle order nearest $675$ nm.
+For the IGRINS instrument, we calculate the signal-to-noise ratio from the order nearest $2200$ nm.
+
+TODO: MAKE THE SPECTRA AVAILABLE SOMEHOW...
 
@@
 
-\subsection{Theoretical Implications}
-
-TODO: Discuss ways forward.
+%\subsection{Theoretical Implications}
+
+%TODO: Discuss ways forward.
 Compile table giving the estimated maximum separation from the RVs.
@@
 
-TODO: Discuss physical mechanism to generate a preferrence for $q = 0.3$.
+%TODO: Discuss physical mechanism to generate a preferrence for $q = 0.3$.
 Saying something about when disk fragments (how much time is left for the companion to accrete)?
@@
 If they continue migrating long enough to get much over $q \sim 0.3$, they end up falling into the star?
-
-%Estimates of the mass-ratio distribution for spectroscopic binaries with slowly rotating chemically peculiar Am/Ap stars also appears to be roughly Gaussian with mean $\sim 0.4$ \citep{Carrier2002, Vuissoz2004}, in apparent conflict from the close companions identified with adaptive optics imaging in the VAST survey \citep{DeRosa2014} that show a ~flat mass-ratio distribution.
 
@@
 \enddata
+\tablecomments{See Section \ref{subsec:specdata} for details of the signal-to-noise ratio calculation (the snr column)}
 \label{tab:observations}

### 2016-02-19 paper/ms.tex

@@
 We present the results of a survey searching for companions to A- and B-type stars using the direct spectral detection technique, which is sensitive to late-type companions within $\sim 1''$ of the primary.
-We estimate the temperatures and masses of the 58 companion detections, 25 of which are new detections.
+We estimate the temperatures and masses of the 57 companion detections, 25 of which are new detections.
 We present the mass-ratio distribution for our sample, and find that it is has a robust maximum near mass ratios $q \sim 0.3$.
-TODO: discuss implications.
+This is a very different form for the mass ratio distribution, which is usually well-described by a power law, and indicates that close companions to intermediate-mass stars experience significantly different accretion histories or formation mechanisms than wide companions.
 \end{abstract}
@@
 
-We measure the flux and position of both stars by fitting a 2D Moffat function [CITE] to both stars simultaneously, constraining the shape parameters for both functions to be the same.
+We measure the flux and position of both stars by fitting a 2D Moffat function \citep{Moffat1969} to both stars simultaneously, constraining the shape parameters for both functions to be the same.
 The ratio of the amplitudes gives the magnitude difference, and the pixel locations along with the detector pixel scale gives the separation and position angle between the stars.
@@
 
+\subsection{Model Comparison}
+
 The most striking feature of the mass ratio distribution shown in Figure \ref{fig:mrd} is the turnover at intermediate q, which the beta distribution fit finds occurs at $q = 0.30^{+0.03}_{-0.04}$.
@@
 However, their subsample of close companions only includes 18 binaries, so it is possible that the different forms are just a result of small number statistics.
-To assess the degree of tension, we use the Anderson-Darling [CITE] test to find the probability that both their close companion subsample and our companions are drawn from the same parent distribution.
+To assess the degree of tension, we use the Anderson-Darling  test \citep{Anderson1954} to find the probability that both their close companion subsample and our companions are drawn from the same parent distribution.
 We only use companions from this work with mean $\overline{q} > 0.15$, since the survey completeness is roughly constant in that range and because the VAST survey subsample makes the same cut.
@@
   HIP 12706 & AB &     2 & yes &  $6051 \pm 107$ &      10 &     0.0  &  $1.1^{+0.03}_{-0.03}$ &  $1.1^{+0.04}_{-0.05}$ \\
-  HIP 13165 & AB? &     1 & no &  $5773 \pm 163$ &       5 &    -0.5  &  $1.1^{+0.31}_{-0.08}$ &  $1.0^{+0.10}_{-0.03}$ \\
+  HIP 13165 & Aa,Ab &     1 & no &  $5773 \pm 163$ &       5 &    -0.5  &  $1.1^{+0.31}_{-0.08}$ &  $1.0^{+0.10}_{-0.03}$ \\
   HIP 13327 & AB$^{\dagger}$ &     1 & yes &  $5524 \pm 150$ &       5 &    -0.5  &  $1.2^{+0.20}_{-0.21}$ &  $1.0^{+0.03}_{-0.04}$ \\
@@
   HIP 55266 & AB &     1 & no &  $8483 \pm 139$ &      30 &    -0.5 &  $1.8^{+0.06}_{-0.04}$ &  $2.0^{+0.06}_{-0.05}$ \\
-  HIP 63945 & Aa,Ab or AC? &     1 & no &  $7038 \pm 162$ &      10 &    -0.5 &  $1.6^{+0.26}_{-0.16}$ &  $1.5^{+0.08}_{-0.06}$ \\
+  HIP 63945 & AC &     1 & no &  $7038 \pm 162$ &      10 &    -0.5 &  $1.6^{+0.26}_{-0.16}$ &  $1.5^{+0.08}_{-0.06}$ \\
   HIP 72154 & AB$^{\dagger}$ &     1 & yes &  $4918 \pm 162$ &      30 &    -0.5  &  $0.9^{+0.22}_{-0.09}$ &  $0.8^{+0.03}_{-0.03}$ \\

### 2016-02-23 paper/ms.tex

@@
 
-TODO: Put the MCMC samples up on zenodo or something.
-
 \begin{figure}
@@
 If they continue migrating long enough to get much over $q \sim 0.3$, they end up falling into the star?
+
+\subsection{Supplemental Data}
+
+In the effort of open and reproducible research, we have made several data products freely available to the community.
+The samples of primary and companion mass and system age are available at \url{https://zenodo.org/record/46340}.
+The files generated by MultiNest, which include samples from the posterior distributions described in Section \ref{sec:mrd}, are available at the same url.
+We additionally provide a series of python libraries and jupyter notebooks with the computer code we used for the analysis on github: \url{https://github.com/kgullikson88/BinaryInference}.
 

### 2016-02-25 paper/ms.tex
Updated abstract and intro as per Adams suggestions.

@@
 Binary stars and higher-order multiple systems are a ubiquitous outcome of star formation, especially as the system mass increases.
-The distribution of mass ratios is a unique probe into the conditions of the collapsing molecular core as well as the circumstellar disks of the binary fragments.
+The distribution of mass ratios is a unique probe into the conditions of the collapsing cloud core and circumstellar disk(s) of the binary fragments.
 Inside $a \sim 1000$ AU the disks from the two forming stars can interact, and additionally companions can form directly through disk fragmentation.
 We should therefore expect the mass-ratio distribution of close companions to differ from that of wide companions.
-Unfortunately, close companions to A- and B-type stars are very difficult to detect and characterize because they are so much dimmer than the primary star.
-We present the results of a survey searching for companions to A- and B-type stars using the direct spectral detection technique, which is sensitive to late-type companions within $\sim 1''$ of the primary.
-We estimate the temperatures and masses of the 57 companion detections, 25 of which are new detections.
-We present the mass-ratio distribution for our sample, and find that it is has a robust maximum near mass ratios $q \sim 0.3$.
-This is a very different form for the mass ratio distribution, which is usually well-described by a power law, and indicates that close companions to intermediate-mass stars experience significantly different accretion histories or formation mechanisms than wide companions.
+This prediction is difficult to test with intermediate-mass to massive primary stars because close companions are so much dimmer.
+We present the results of a survey searching for companions to A- and B-type stars using the direct spectral detection technique, which is sensitive to late-type companions within $\sim 1''$ of the primary and which has no inner working angle.
+We estimate the temperatures and masses of the 57 companions , 25 of which are new detections.
+We find that the mass-ratio distribution for our sample has a robust maximum near $q \sim 0.3$.
+Our mass-ratio distribution has a very different form than in previous work, where it is usually well-described by a power law, and indicates that close companions to intermediate-mass stars experience significantly different accretion histories or formation mechanisms than wide companions.
 \end{abstract}
@@
 The overall multiplicity rate and the distributions of mass ratio, period, and eccentricity of a binary star population place important constraints on the mode of binary star formation.
-While the period and eccentricity are altered by dynamical processing in the birth cluster, the present-day mass ratio of a binary system is a tracer of its formation \citep{Parker2013}.
+While the period and eccentricity are altered by dynamical processing in the birth cluster, the present-day mass ratio of a binary system is a direct result of its formation \citep{Parker2013}.
 Most binary stars are thought to form via core fragmentation \citep{Boss1979, Boss1986, Bate1995}, in which a collapsing core fragments into two or more individual protostars.
 The number and initial masses of the fragments are set by the total core mass, as well as its rotation, turbulence, and its temperature and density structure.
-If the fragments are well separated ($a \gtrsim 1000$ AU), they will evolve relatively independently of each other, accreting mass from the core material onto their own protostellar disks and then onto the protostars themselves.
+If the fragments are well separated ($a \gtrsim 1000$ AU), they will evolve independently of each other, accreting mass from the core material onto their own protostellar disks and then onto the protostars themselves.
 However close fragments ($a \sim 100$ AU) will interact with each other; the protostellar disk may be truncated, destabilized, or form into a circumbinary disk if the separation is small enough \citep{Bate1997}.
@@
 Second, the primary stars tend to be rapid rotators, which limits radial velocity precision to $\sim 1 \mathrm{km\ s}^{-1}$.
-Worse, radial velocity monitoring can only measure a mass ratio if spectral lines from both components are visible; this typically suffers from the same flux ratio difficulty as imaging techniques.
+Additionally, radial velocity monitoring can only measure a mass ratio if spectral lines from both components are visible; this typically suffers from the same flux ratio difficulty as imaging techniques.
 
@@
 They also found initial evidence that the mass ratio distribution for companions inside $125$ AU has a much shallower power law slope than that of wide companions, and is consistent with flat.
-Unfortunately the close companion subsample contained only 18 binary systems, and the result is complicated by the inherent difficulty of detecting close companions with low mass ratios in an imaging survey.
-
-Spectroscopic companions to chemically peculiar Am stars appear to have a mass ratio distribution which peaks near $q \sim 0.5$ \citep{Vuissoz2004}.
-Am stars are typically associated with binary companions, and are slow rotators due to tidal braking; they thus form a highly biased sample of intermediate-mass stars.
-It is however interesting that the inner mass ratio distribution around these chemically peculiar stars has an entirely different form than the distribution around chemically normal stars at wide separations probed by imaging.
+Their close companion subsample contained only 18 binary systems, and the result is complicated by the inherent difficulty of detecting close companions with low mass ratios in an imaging survey.
+
+Radial velocity monitoring surveys can detect much closer companions than imaging surveys, but are typically only complete to low-mass companions if the primary is a slow rotator.
+Chemically peculiar Am stars are typically associated with binary companions, and are slow rotators due to tidal braking; they thus form a highly biased sample of intermediate-mass stars.
+Nonetheless, it is interesting to note that they have a mass-ratio distribution which peaks near $q \sim 0.5$ \citep{Vuissoz2004}, an entirely different form than the distribution found around chemically normal stars at wide separations.
 

### 2016-02-25 paper/ms.tex
Updated section 2 as per Adams comments.

@@
 \begin{itemize}
-\item $V < 6$
+\item $V < 6$ mag
 \item $v\sin{i} > 80 \mathrm{km\ s}^{-1}$
@@
 It does introduce a Malmquist bias in the derived mass ratio, which we discuss and correct for in Section \ref{sec:mrd}.
-Likewise, the $v\sin{i}$ limit makes accounting for the primary star spectrum in the companion search trivial; since most A- or B-type stars are rapid rotators, the cutoff does not remove very many stars from the potential sample.
+Likewise, the $v\sin{i}$ limit makes accounting for the primary star spectrum in the companion search trivial; since most A- or B-type stars are rapid rotators, the cutoff removes less than half of the stars from the potential sample.
 We exclude pre-main sequence stars because both the primary and the companion mass would depend very strongly on young and uncertain ($\lesssim 1$ Myr) evolutionary models.
@@
 The sample is given in Table \ref{tab:sample}.
-The spectral type, coordinates, V magnitude, and parallax are all pulled from the Simbad Database \citep{Simbad}.
+The spectral type, coordinates, V magnitude, and parallax are all adopted from the Simbad Database \citep{Simbad}.
 

### 2016-02-25 Priors.py

@@ -12,8 +12,8 @@ from scipy.interpolate import InterpolatedUnivariateSpline as spline
 import pandas as pd
 import scipy.interpolate
 
-from kglib.spectral_type import SpectralTypeRelations
-import Mamajek_Table
+from kglib.spectral_type import SpectralTypeRelations, Mamajek_Table
+
 from kglib.isochrone_helpers import Feiden
 from kglib.utils import StarData
 
@@ -23,7 +23,8 @@ MT = Mamajek_Table.MamajekTable()
 sptnum2mass = MT.get_interpolator('SpTNum', 'Msun')
 
 # Read in the David & Hillenbrand summary
-dh2015 = pd.read_csv('/home/kgullikson/Dropbox/School/Research/AstarStuff/TargetLists/David_and_Hillenbrand2015/dh2015-table5.csv')
+home = os.environ['HOME']
+dh2015 = pd.read_csv('{}/Dropbox/School/Research/AstarStuff/TargetLists/David_and_Hillenbrand2015/dh2015-table5.csv'.format(home))
 
 def read_dh2015_posterior(hipnum,
                           basedir='/home/kgullikson/Dropbox/School/Research/AstarStuff/TargetLists/David_and_Hillenbrand2015',

### 2016-02-26 paper/ms.tex
Expanded on spectroscopic follow-up section.

@@
 We give the spectroscopic observation log in Table \ref{tab:observations}.
-We calculate the signal-to-noise ratio (the "snr" column) for the optical instruments (CHIRON, TS23, and HRS) as the median of the extracted flux divided by it's uncertainty for each pixel from the \'echelle order nearest $675$ nm.
+We calculate the signal-to-noise ratio (the ``snr'' column) for the optical instruments (CHIRON, TS23, and HRS) as the median of the extracted flux divided by it's uncertainty for each pixel from the \'echelle order nearest $675$ nm.
 For the IGRINS instrument, we calculate the signal-to-noise ratio from the order nearest $2200$ nm.
@@
 
-Most of the detected companions have follow-up spectra to confirm the existence of the companion.
+We have follow-up spectroscopy for 17/27 of the new companions to confirm their existence.
 In most cases, there is a clear shift in the radial velocity of the companion, indicating that it is orbiting the target star and is not a foreground or background contaminant (See Figure \ref{fig:ccf}).
-In addition we obtained Gemini/NIRI adaptive optics imaging data for 19 of the northern companions, and were able to resolve 7 of them.
+Two of the new detections (companions to HIPs 38593 and 79404) were detected twice but not in a third attempt, most likely because the third spectrum had low signal-to-noise.
+The companion to HIP 93805, at $\sim 4000$ K, was detected twice with near-infrared IGRINS but not the optical CHIRON instrument that is less sensitive to cool companions than IGRINS.
+Two of the companions with only one detection were observed at least twice (HIPs 19949 and HIP 23362); both of the non-detections are from the IGRINS instrument, which is less sensitive to hot companions with rapid rotation speeds because there are far fewer spectral lines of the companion in the near-infrared than there are in the optical.
+
+In addition we obtained Gemini/NIRI adaptive optics imaging data for 18 of the northern companions, and were able to resolve 7 of them.
 We show the separation, position angle, and magnitude difference in Table \ref{tab:imaging_obs}, and display the images in Figure \ref{fig:images}.
@@
   HIP 22958 &  5.79 &  2015-10-19 &   52x0.4 & $0.445 +/- 0.003$ & $65.0 \pm 0.3$ & $2.57 \pm 0.05$ \\
-  HIP 23916 &  5.98 &  2015-04-05 &   18x1.1 & \nodata & \nodata & \nodata \\
   HIP 26093 &  5.96 &  2015-03-23 &   33x0.6 & \nodata & \nodata & \nodata \\
@@
   HIP 23362 & AB$^{\dagger}$ &     1 & yes &  $6283 \pm 158$ &       5 &    -0.5  &  $1.2^{+0.06}_{-0.05}$ &  $1.2^{+0.07}_{-0.05}$ \\
-  HIP 23916 & Aa,Ab$^{\dagger}$ &     1 & yes &  $5450 \pm 158$ &       5 &    -0.5  &  $1.1^{+0.20}_{-0.20}$ &  $0.9^{+0.04}_{-0.03}$ \\
   HIP 24902 & AB &     1 & yes &  $5679 \pm 154$ &      30 &     0.0  &  $1.0^{+0.05}_{-0.04}$ &  $1.0^{+0.04}_{-0.03}$ \\

### 2016-02-29 fit_parameters.py
Updated fit parameters for primary star

@@ -7,7 +7,7 @@ import pandas as pd
 import numpy as np
 
 
-HDF5_OUTPUT = 'Primary_Parameters.h5'
+HDF5_OUTPUT = 'Primary_Parameters_full.h5'
 
 class MyModel(StarModel):
     def _make_samples(self):
@@ -28,7 +28,7 @@ if __name__ == '__main__':
     pad = Padova_Isochrone()
 
     i = int(sys.argv[1])
-    pars = pd.read_csv('data/Primary_Parameters.csv').loc[i]
+    pars = pd.read_csv('data/Primary_Parameters_full.csv').loc[i]
     model = MyModel(pad, Teff=(pars.teff, pars.teff_err),
                       logg=(pars.logg, pars.logg_err),
                       feh=(pars.feh, pars.feh_err))

### 2016-03-02 paper/ms.tex
Several minor changes as per Adam.

@@
 In addition we obtained Gemini/NIRI adaptive optics imaging data for 18 of the northern companions, and were able to resolve 7 of them.
-We show the separation, position angle, and magnitude difference in Table \ref{tab:imaging_obs}, and display the images in Figure \ref{fig:images}.
-One star, HIP 88116, has several nearby sources in the image.
+We show the separation, position angle, and magnitude difference measurements in Table \ref{tab:imaging_obs}, and display the images in Figure \ref{fig:images}.
+We also derive the projected separation in AU and the companion mass from the images.
+We calculate the separation from the measured angular separation and the Hipparchos parallax \citep{Hipparchos}.
+We calculate the companion mass and uncertainties from 1000 samples of the magnitude difference measurement and the primary star mass, temperature, age, and radius (see Section \ref{sec:sp}).
+For each sample, we use a grid of Kurucz stellar model spectra [CITE] and the pysynphot code [CITE] to determine the companion temperature needed to replicate the observed magnitude difference.
+We estimate the companion radius by interpolating solar metallicity Dartmouth isochrones [CITE] from the companion temperature and system age sample.
+We convert the best temperature to a companion mass using the same isochrone grid.
+The masses derived from the imaging data have very large uncertainties because the primary star property estimates that they depend on are very uncertain.
+
+One star in the imaging sample, HIP 88116, has several nearby sources in the image.
 We quote the magnitude difference and separation of the brightest source in Table \ref{tab:imaging_obs}, but stress that \emph{none} of the visible sources is likely to be the companion we see in the spectroscopic data.
-The two epochs of spectroscopic data show a radial velocity shift of $\Delta v = 30.7\ \mathrm{km\ s}^{-1}$ over the course of roughly one year; this orbital motion is much too large to allow for any of the companions visible in the image (all with separations $ > 1''$).
+The two epochs of spectroscopic data show a radial velocity shift of $\Delta v = 30.7\ \mathrm{km\ s}^{-1}$ over the course of roughly one year; this orbital motion is much too large to allow for any of the companions visible in the image (all with separations $ > 1''$ and projected separations $ > 300$ AU).
 
@@
 We do the conversion to mass both by interpolating Table 5 from \citet{Pecaut2013}, and by interpolating from temperature and system age (see Section \ref{sec:sp}) to mass with Dartmouth isochrones [CITE].
-Both methods give similar results in most cases, although the isochrone masses are significantly higher for very young systems.
-We only use the results obtained with the isochrone masses in the analysis.
+Both methods give similar results in most cases, although the isochrone masses are significantly higher for very young systems, so we adopt the isochronal values in the analysis.
 We sample the mass ratio of the system by dividing the companion mass samples by samples of the primary mass (Section \ref{sec:sp}).
@@
 
-We are trying to recover the intrinsic distribution from an observed sample; thus we should fit the data to the probability distribution function (PDF) for mass ratio, \emph{given that we observed the star}: $P(q|\vec{\theta}, \mathrm{obs})$.
-In a volume-limited sample, this is equal to $P(q|\vec{\theta})$; however, our sample is magnitude-limited and therefore suffers from Malmquist bias.
-There is a higher probability of equal-mass binary systems in our data because they contribute twice the flux and are therefore more likely to fall under the magnitude limit.
-We can calculate the PDF for mass ratio given that we observed the system from Bayes' theorem:
+We are trying to recover the intrinsic distribution from an observed sample, so we must fit the data to the probability distribution function (PDF) for mass ratio, \emph{given that we observed the star}: $P(q|\vec{\theta}, \mathrm{obs})$.
+In a volume-limited sample, this is equal to $P(q|\vec{\theta})$.
+However, our sample is magnitude-limited and therefore suffers from Malmquist bias.
+There is a higher probability of equal-mass binary systems to occur in our survey because they contribute twice the flux and are therefore more likely to fall under the magnitude limit.
+We can calculate the PDF for mass ratio, given that we observed the system, from Bayes' theorem:
 
@@
 
-We already know $P(q|\vec{\theta})$ (Equations \ref{eqn:P1} - \ref{eqn:P3}). We estimate $P(\mathrm{obs}|q)$ by simulating a very large sample of binary stars:
+We already know $P(q|\vec{\theta})$ (Equations \ref{eqn:P1} - \ref{eqn:P3}). We estimate $P(\mathrm{obs}|q)$ by simulating a very large sample of binary stars via these steps:
 
 \begin{enumerate}
-\item Sample primary star masses from the Kroupa IMF \citep{Kroupa2002}
-\item Sample a distance for each star from a disk with infinite extent and scale height of $300$ pc. 
+\item Draw random primary star masses from the Kroupa IMF \citep{Kroupa2002}
+\item Draw a random distance for each star from a disk with infinite extent and scale height of $150$ pc \citep[the approximate scale height of the Milky Way disk for A-type stars,][]{BM1998}. 
 \item For each $q$ from 0 to 1, in steps of 0.01:
@@
 
-Previous measurements of the mass-ratio distribution find that the data is well fit by a power law with index $0.39 \pm 0.23$ \citep[M dwarf stars][]{Delfosse2004}, $0.27 \pm 0.05$ \citep[Solar type stars][]{Duchene2013}, and $-0.45 \pm 0.15$ \citep[intermediate-mass stars][]{Kouwenhoven2007}.
-The more recent VAST survey found a much steeper power law index of $-2.3^{+1.0}_{-0.9}$ for wide companions, and an inner mass-ratio distribution that is consistent with flat.
+Previous measurements of the mass-ratio distribution find that the data is well fit by a power law.
+\citet{Kouwenhoven2007} compiled spectroscopic, imaging, and astrometric observations of binary stars with intermediate-mass primaries in the Scorpius OB association, and derived a power law index of  $-0.45 \pm 0.15$.
+More recently \citet{DeRosa2014} performed an adaptive optics and common proper motion search for companions to field A-type stars.
+They found that the distribution for companions on wide ($a > 125\ AU$) orbits has a very steep power law index of $-2.3^{+1.0}_{-0.9}$, while the distribution for close ($30\ AU < a < 125\ AU$) companions is consistent with flat.
 
@@
 
-\begin{deluxetable*}{|l|llllll|}
+\begin{deluxetable*}{|l|llllllll|}
 \tabletypesize{\small}
@@
 \tablehead{
-       \colhead{star} &  \colhead{K} &   \colhead{date} & \colhead{Exposure} & \colhead{$\rho$} & \colhead{$\theta$} & \colhead{$\Delta \mathrm{K_c}$}
+       \colhead{star} &  \colhead{K} &   \colhead{date} & \colhead{Exposure} & \colhead{$\rho$} & \colhead{$\theta$} & \colhead{$\Delta \mathrm{K_c}$} & \colhead{$M_2 (M_{\odot})$} & \colhead{$a$ (AU)}
        }
@@
 \startdata
-  HIP 22833 &  4.83 &  2015-03-29 &   50x0.3 & $0.352 +/- 0.003$ & $14.1 \pm 0.7$ & $3.04 \pm 0.06$ \\
-  HIP 22958 &  5.79 &  2015-10-19 &   52x0.4 & $0.445 +/- 0.003$ & $65.0 \pm 0.3$ & $2.57 \pm 0.05$ \\
-  HIP 26093 &  5.96 &  2015-03-23 &   33x0.6 & \nodata & \nodata & \nodata \\
-  HIP 26126 &  5.07 &  2015-03-29 &   40x0.4 & \nodata & \nodata & \nodata \\
-  HIP 29735 &  5.10 &  2015-03-22 &   83x0.2 & \nodata & \nodata & \nodata \\
-  HIP 31278 &  5.46 &  2015-03-28 &   29x0.6 & \nodata & \nodata & \nodata \\
-  HIP 38538 &  4.66 &  2015-10-19 &   75x0.2 & \nodata & \nodata & \nodata \\
-  HIP 39847 &  4.66 &  2015-03-27 &   50x0.3 & \nodata & \nodata & \nodata \\
-  HIP 75178 &  5.49 &  2015-03-24 &   29x0.6 & \nodata & \nodata & \nodata \\
-  HIP 88116 &  4.47 &  2015-03-22 &   50x0.3 & $3.260 +/- 0.001$ & $59.29 \pm 0.02$ & $3.9 \pm 0.4$ \\
-  HIP 91118 &  5.67 &  2015-10-16 &   43x0.4 & $0.1667 +/- 0.0007$ & $41.7 \pm 0.2$ & $1.77 \pm 0.01$ \\
- HIP 100221 &  5.70 &  2015-10-18 &   26x0.7 & $0.250 +/- 0.002$ & $346.8 \pm 0.92$ & $2.28 \pm 0.04$ \\
- HIP 100907 &  5.41 &  2015-10-16 &   43x0.4 & $0.463 +/- 0.002$ & $335.4 \pm 0.30$ & $2.91 \pm 0.04$ \\
- HIP 101909 &  $6.47^{\dagger}$ &  2015-10-16 &   39x0.5 & \nodata & \nodata & \nodata \\
- HIP 109139 &  4.40 &  2015-04-26 &   50x0.3 & \nodata & \nodata & \nodata \\
- HIP 109521 &  4.96 &  2015-04-25 &   40x0.4 & \nodata & \nodata & \nodata \\
- HIP 115115 &  4.96 &  2015-10-18 &   40x0.4 & $1.497 +/- 0.002$ & $313.14 \pm 0.08$ & $2.54 \pm 0.04$ \\
- HIP 118243 &  $5.87^{\dagger}$ &  2015-07-23 &   58x0.3 & $4.082 +/- 0.002$ & $310.23 \pm 0.03$ & $2.20 \pm 0.03$
+  HIP 22833 &  4.83 &  2015-03-29 &   50x0.3 & $0.352 +/- 0.003$ & $14.1 \pm 0.7$ & $3.04 \pm 0.06$ & $0.9^{+0.16}_{-0.17}$ & $25.1 \pm 0.24$ \\
+  HIP 22958 &  5.79 &  2015-10-19 &   52x0.4 & $0.445 +/- 0.003$ & $65.0 \pm 0.3$ & $2.57 \pm 0.05$ & $1.5^{+0.35}_{-0.28}$ & $124.1 \pm 0.81$ \\
+  HIP 26093 &  5.96 &  2015-03-23 &   33x0.6 & \nodata & \nodata & \nodata & \nodata & \nodata \\
+  HIP 26126 &  5.07 &  2015-03-29 &   40x0.4 & \nodata & \nodata & \nodata & \nodata & \nodata \\
+  HIP 29735 &  5.10 &  2015-03-22 &   83x0.2 & \nodata & \nodata & \nodata & \nodata & \nodata \\
+  HIP 31278 &  5.46 &  2015-03-28 &   29x0.6 & \nodata & \nodata & \nodata & \nodata & \nodata \\
+  HIP 38538 &  4.66 &  2015-10-19 &   75x0.2 & \nodata & \nodata & \nodata & \nodata & \nodata \\
+  HIP 39847 &  4.66 &  2015-03-27 &   50x0.3 & \nodata & \nodata & \nodata & \nodata & \nodata \\
+  HIP 75178 &  5.49 &  2015-03-24 &   29x0.6 & \nodata & \nodata & \nodata & \nodata & \nodata \\
+  HIP 88116 &  4.47 &  2015-03-22 &   50x0.3 & $3.671 +/- 0.001$ & $242.99 \pm 0.02$ & $3.9 \pm 0.4$ & $1.2^{+0.28}_{-0.24}$ & $467.7 \pm 0.18$ \\
+  HIP 91118 &  5.67 &  2015-10-16 &   43x0.4 & $0.1667 +/- 0.0007$ & $41.7 \pm 0.2$ & $1.77 \pm 0.01$ & $1.5^{+0.39}_{-0.25}$ & $36.4 \pm 0.16$ \\
+ HIP 100221 &  5.70 &  2015-10-18 &   26x0.7 & $0.250 +/- 0.002$ & $346.8 \pm 0.92$ & $2.28 \pm 0.04$ & $0.9^{+0.2}_{-0.23}$ & $28.5 \pm 0.24$ \\
+ HIP 100907 &  5.41 &  2015-10-16 &   43x0.4 & $0.463 +/- 0.002$ & $335.4 \pm 0.30$ & $2.91 \pm 0.04$ & $0.7^{+0.14}_{-0.10}$ & $37.7 \pm 0.16$ \\
+ HIP 101909 &  $6.47^{\dagger}$ &  2015-10-16 &   39x0.5 & \nodata & \nodata & \nodata & \nodata & \nodata \\
+ HIP 109139 &  4.40 &  2015-04-26 &   50x0.3 & \nodata & \nodata & \nodata & \nodata & \nodata \\
+ HIP 109521 &  4.96 &  2015-04-25 &   40x0.4 & \nodata & \nodata & \nodata & \nodata & \nodata \\
+ HIP 115115 &  4.96 &  2015-10-18 &   40x0.4 & $1.497 +/- 0.002$ & $313.14 \pm 0.08$ & $2.54 \pm 0.04$ & $1.3^{+0.28}_{-0.19}$ & $120.0 \pm 0.17$
 \enddata

### 2016-03-04 Priors.py
Update default hdf5_filename in get_padova_posterior.

@@ -41,7 +41,7 @@ def get_cdf(x, P, accuracy=10):
     return np.round(cdf/cdf[-1], decimals=accuracy)
 
 
-def get_padova_posterior(star, hdf5_filename='Primary_Parameters.h5', var='mass'):
+def get_padova_posterior(star, hdf5_filename='data/Primary_Parameters.h5', var='mass'):
     """ Search the given HDF5 file for an entry for star. If it exists, return the mass samples.
     """
     try:

### 2016-03-07 paper/ms.tex
Updated Table 1 with lots more measurements
Added new detections to table.
Removed low vsini primaries from sample and detections tables.
Updated search methodology for hot grid.

@@
 
-TODO: MAKE THE SPECTRA AVAILABLE SOMEHOW...
+All of the reduced and telluric-corrected spectra used in this study will be released with this work, and will be available at the following url: \url{https://zenodo.org/record/46482}.
 
@@
 \item $v\sin{i} = 1, 5, 10, 20, 30 \ \mathrm{km\ s}^{-1}$
+\end{itemize}
+
+In order to be sensitive to hot companions, we additionally cross-correlate the spectra against a second grid of Kurucz model spectra \citep{Castelli2003}.
+The change in model is necessary because the Phoenix model library does not extend beyond $12000\ K$.
+The Kurucz grid is defined as follows:
+
+\begin{itemize}
+\item $T_\mathrm{eff} = 9000-30000$ K, in steps of 1000 K
+\item {[}Fe/H{]} = -0.5, 0.0, +0.5
+\item $v\sin{i} = 1, 5, 10, 20, 30, 40, 50 \ \mathrm{km\ s}^{-1}$
 \end{itemize}
@@
 We calculate the companion mass and uncertainties from 1000 samples of the magnitude difference measurement and the primary star mass, temperature, age, and radius (see Section \ref{sec:sp}).
-For each sample, we use a grid of Kurucz stellar model spectra [CITE] and the pysynphot code [CITE] to determine the companion temperature needed to replicate the observed magnitude difference.
+For each sample, we use a grid of Kurucz stellar model spectra \citep{Castelli2003}and the pysynphot code\footnote{pysynphot is a python code package to perform synthetic photometry, and is available at this url: \url{https://pypi.python.org/pypi/pysynphot}} to determine the companion temperature needed to replicate the observed magnitude difference.
 We estimate the companion radius by interpolating solar metallicity Dartmouth isochrones [CITE] from the companion temperature and system age sample.
@@
 
-For the optical data, we use the blue echelle orders ($\lambda < 5550 \AA$).
-We ignore the strong hydrogren Balmer lines in the spectrum because they span several echelle orders and make continuum normalization very difficult, potentially biasing the result.
+For the optical data, we use the blue \'echelle orders ($\lambda < 5550 \AA$).
+We ignore the strong hydrogren Balmer lines in the spectrum because they span several \'echelle orders and make continuum normalization very difficult, potentially biasing the result.
 There are sufficient metal lines in the optical spectra that the resulting CCF always has a very strong peak at the radial velocity of the primary star.
@@
  \sigma_T &= \begin{cases}
-      \hfill 300\ K \hfill & T < 10000\ K \\
+      \hfill 500\ K \hfill & T < 10000\ K \\
       \hfill 1000\ K \hfill & T >= 10000\ K \\
@@
 \end{align}
-
-Next, we use Padova stellar evolutionary tracks \citep{Bressan2012} and the isochrones code \citep{isochrones_code} to estimate the mass and age of the system from the measured temperature and $\log{g}$.
+The IGRINS parameters are less reliable because they rely almost solely on the hydrogren Brackett lines that span an entire \'echelle order, so we double the uncertainty on the IGRINS-derived temperature, surface gravity, and metallicity.
+Additionally, we throw out the IGRINS parameters if the star was also observed by one of the optical instruments in our survey.
+For stars observed multiple times, we use the average parameters and reduce the uncertainties accordingly.
+
+Next, we use Padova stellar evolutionary tracks \citep{Bressan2012} and the isochrones code \citep{isochrones_code} to estimate the mass and age of the system from the measured temperature and surface gravity.
 As a consistency check, we also interpolate from a table of stellar properties as a function of spectral type \citep{Pecaut2013} to estimate the primary mass from the published spectral types.
@@
 
-We show the temperature, surface gravity, mass, and age estimates for all primary stars in Table \ref{tab:sample}.
-The MCMC samples generated by the isochrones code are available at [GIVE ZENODO LINK OR SOMETHING].
+We show the temperature, surface gravity, mass, and age estimates for most of our sample stars Table \ref{tab:sample}.
+We do not give parameters for the few stars that show strong discrepancies with the spectral-type estimate, most of which are early B-stars that have temperatures higher than the maximum grid temperature of $30000\ K$.
+The MCMC samples generated by the isochrones code are available at the following url: \url{https://zenodo.org/record/46482}.
 
@@
 
-To quantify the detection rate as a function of companion temperature and $v\sin{i}$, we performed a series of injection/recovery experiments.
+To quantify the detection rate as a function of companion temperature and $v\sin{i}$, we performed a series of injection and recovery experiments.
 We started by creating synthetic binary star observations from each of our observed spectra.
@@
 Next, we cross correlated all of the synthetic observations against the Phoenix model template that was used to construct them.
-We counted the companion as detected if the highest point in the resulting CCF was found at the correct radial velocity.
+We counted the companion as detected if the highest point in the resulting CCF was found at the correct radial velocity, and if the peak had a significance of $>5\sigma$, where $\sigma$ is the standard deviation of the CCF for points more than $100\ \mathrm{km\ s}^{-1}$ away from the peak.
 We then combined all of the radial velocity trials for each grid point to estimate a probability of detection at that grid point:
@@
 The slow fall-off towards large mass ratios is caused by the same effect as in Figure \ref{fig:marginalized}: large mass ratio companions tend to be rapid rotators that are more difficult to detect.
+
+TODO: Discuss fudge factor if Adam agrees...
 
@@
 
-     HIP 813 &           B9Vn &    00:10:02.20 &   +11:08:44.93 &   5.537 &     10.68 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-    HIP 1191 &          B8.5V &    00:14:54.52 &   -09:34:10.45 &   5.757 &      9.63 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-    HIP 1366 &            A2V &    00:17:05.50 &   +38:40:53.89 &   4.610 &     10.56 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-    HIP 1647 &            B9V &    00:20:39.04 &   -69:37:29.68 &   5.498 &     10.25 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-    HIP 2381 &            A3V &    00:30:22.65 &   -23:47:15.65 &   5.190 &     18.83 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-    HIP 2505 &           B8Vn &    00:31:46.36 &   +54:31:20.23 &   4.732 &      8.64 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-    HIP 2548 &          B9.5V &    00:32:23.78 &   +06:57:19.66 &   5.698 &     12.35 &   $11864 \pm 403$ &  $4.4 \pm 0.14$ &  $2.8^{+0.16}_{-0.15}$ &     $78^{+70}_{-52}$ &      1 \\
-    HIP 2912 &            B5V &    00:36:52.85 &   +33:43:09.64 &   4.360 &      5.45 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-    HIP 3300 &            B2V &    00:42:03.90 &   +50:30:45.09 &   4.810 &      2.28 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-    HIP 3478 &            B5V &    00:44:26.19 &   +47:51:50.34 &   5.646 &      5.23 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-    HIP 3741 &            B9V &    00:48:01.06 &   -21:43:20.99 &   5.570 &      9.51 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-    HIP 3881 &            B5V &    00:49:48.85 &   +41:04:44.08 &   4.530 &      5.28 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-    HIP 4436 &            A5V &    00:56:45.21 &   +38:29:57.64 &   3.870 &     25.14 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-    HIP 5131 &           A1Vn &    01:05:40.96 &   +21:28:23.45 &   5.317 &     11.86 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-    HIP 5132 &           A0Vn &    01:05:41.71 &   +21:27:55.60 &   5.532 &     11.64 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-    HIP 5310 &            A3V &    01:07:57.16 &   +20:44:20.83 &   5.569 &     21.14 &    $8611 \pm 293$ &  $4.4 \pm 0.14$ &  $1.8^{+0.10}_{-0.08}$ &  $307^{+234}_{-196}$ &      1 \\
-    HIP 5348 &            B6V &    01:08:23.08 &   -55:14:44.73 &   3.967 &     10.92 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-    HIP 5361 &            B8V &    01:08:33.47 &   +58:15:48.41 &   5.773 &      5.41 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-    HIP 5518 &          A0Vnn &    01:10:39.32 &   +68:46:43.04 &   5.318 &     11.78 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-    HIP 5626 &            A3V &    01:12:16.82 &   +79:40:26.27 &   5.600 &     12.07 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-    HIP 7345 &            A1V &    01:34:37.78 &   -15:40:34.90 &   5.619 &     16.84 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-    HIP 8016 &            B9V &    01:42:55.86 &   +70:37:21.09 &   5.177 &     11.75 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-    HIP 8704 &          B1.5V &    01:51:59.32 &   +55:08:50.58 &   5.520 &      2.52 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-      HR 545 &          B9.5V &    01:53:31.77 &   +19:17:46.27 &   4.700 &   \nodata &  $11000 \pm 1000$ &  $4.3 \pm 0.25$ &  $2.5^{+0.39}_{-0.35}$ &    $37^{+105}_{-28}$ &  2 \\
-    HIP 9312 &           A0Vn &    01:59:38.04 &   +64:37:17.76 &   5.283 &     13.28 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-    HIP 9564 &           A1Vn &    02:02:52.48 &   +64:54:05.27 &   5.999 &     11.92 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-      HR 604 &            B8V &    02:03:54.72 &   +42:19:51.41 &   5.820 &   \nodata &  $11000 \pm 1000$ &  $4.5 \pm 0.25$ &  $2.4^{+0.37}_{-0.34}$ &     $28^{+87}_{-20}$ &  2 \\
-   HIP 10320 &            B9V &    02:12:54.47 &   -30:43:25.77 &   5.261 &     10.18 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 10670 &          A1Vnn &    02:17:18.87 &   +33:50:49.90 &   4.000 &     29.04 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 10732 &           A1Vn &    02:18:07.54 &   +19:54:04.19 &   5.575 &      7.29 &    $9500 \pm 300$ &  $4.0 \pm 0.25$ &  $2.1^{+0.18}_{-0.16}$ &    $80^{+237}_{-70}$ &  2 \\
-   HIP 11345 &            A0V &    02:25:57.01 &   -12:17:25.71 &   4.869 &      7.15 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 12332 &            A7V &    02:38:48.99 &   +21:57:41.06 &   5.454 &      9.68 &    $7750 \pm 300$ &  $3.5 \pm 0.25$ &  $1.9^{+0.37}_{-0.30}$ &  $687^{+218}_{-425}$ &  2 \\
-   HIP 12706 &           A2Vn &    02:43:18.04 &   +03:14:08.94 &   3.470 &     40.97 &    $8551 \pm 291$ &  $4.3 \pm 0.14$ &  $1.9^{+0.15}_{-0.12}$ &  $650^{+105}_{-188}$ &      1 \\
-   HIP 12719 &            B3V &    02:43:27.11 &   +27:42:25.72 &   4.670 &      9.51 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 12803 &           B9Vn &    02:44:32.97 &   +15:18:42.71 &   5.776 &      5.49 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 13165 &            B6V &    02:49:17.56 &   +17:27:51.52 &   5.314 &      4.18 &  $15000 \pm 1000$ &  $4.0 \pm 0.25$ &  $4.2^{+0.58}_{-0.50}$ &     $31^{+42}_{-22}$ &  2 \\
-   HIP 13202 &            A0V &    02:49:54.18 &   -27:56:31.14 &   5.389 &      7.11 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 13209 &           B8Vn &    02:49:59.03 &   +27:15:37.83 &   3.606 &     19.69 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 13327 &            B7V &    02:51:29.59 &   +15:04:55.45 &   5.514 &      6.60 &  $15000 \pm 1000$ &  $4.5 \pm 0.25$ &  $4.0^{+0.50}_{-0.45}$ &      $15^{+26}_{-9}$ &  2 \\
-   HIP 13717 &            A3V &    02:56:37.42 &   -03:42:44.35 &   5.160 &     17.49 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 13879 &           A2Vn &    02:58:45.67 &   +39:39:45.81 &   4.700 &     10.53 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 14043 &            B7V &    03:00:52.21 &   +52:21:06.22 &   5.253 &      7.11 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 14143 &            B7V &    03:02:22.52 &   +04:21:10.39 &   5.607 &      5.93 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 14293 &            A5V &    03:04:16.52 &   -07:36:03.08 &   5.300 &     24.06 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 14576 &            B8V &    03:08:10.13 &   +40:57:20.33 &   2.120 &     36.27 &   $13070 \pm 444$ &  $4.0 \pm 0.14$ &  $3.6^{+0.28}_{-0.23}$ &    $139^{+16}_{-25}$ &      1 \\
-   HIP 14764 &            B8V &    03:10:38.79 &   +11:52:21.44 &   5.965 &      7.33 &  $11750 \pm 1000$ &  $4.2 \pm 0.25$ &  $2.8^{+0.42}_{-0.39}$ &     $35^{+91}_{-27}$ &  2 \\
-   HIP 14862 &          A2Vnn &    03:11:56.27 &   +74:23:37.17 &   4.840 &     19.72 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 15110 &            A1V &    03:14:54.10 &   +21:02:40.01 &   4.880 &     12.44 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 15338 &            B8V &    03:17:47.35 &   +44:01:30.08 &   5.478 &      4.46 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 15404 &            B3V &    03:18:37.74 &   +50:13:19.83 &   5.158 &      5.12 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 15444 &            B5V &    03:19:07.64 &   +50:05:41.88 &   5.036 &      5.82 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 16147 &            B5V &    03:28:03.07 &   +49:03:46.32 &   4.970 &      6.22 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+     HIP 813 &     B9Vn &    00:10:02.20 &   +11:08:44.93 &   5.537 &     10.68 &   $12516 \pm 426$ &  $4.3 \pm 0.14$ &  $3.1^{+0.18}_{-0.17}$ &      $85^{+56}_{-52}$ &       1 \\
+    HIP 1191 &    B8.5V &    00:14:54.52 &   -09:34:10.45 &   5.757 &      9.63 &  $12000 \pm 1000$ &  $4.5 \pm 0.25$ &  $2.8^{+0.41}_{-0.37}$ &      $23^{+63}_{-16}$ &       2 \\
+    HIP 1366 &      A2V &    00:17:05.50 &   +38:40:53.89 &   4.610 &     10.56 &    $9371 \pm 319$ &  $4.0 \pm 0.14$ &  $2.2^{+0.18}_{-0.16}$ &    $464^{+83}_{-119}$ &       1 \\
+    HIP 1647 &      B9V &    00:20:39.04 &   -69:37:29.68 &   5.498 &     10.25 &   $11393 \pm 387$ &  $4.0 \pm 0.14$ &  $2.8^{+0.21}_{-0.18}$ &     $206^{+48}_{-79}$ &       1 \\
+    HIP 2381 &      A3V &    00:30:22.65 &   -23:47:15.65 &   5.190 &     18.83 &    $8364 \pm 284$ &  $4.0 \pm 0.14$ &  $1.9^{+0.16}_{-0.13}$ &   $715^{+135}_{-183}$ &       1 \\
+    HIP 2505 &     B8Vn &    00:31:46.36 &   +54:31:20.23 &   4.732 &      8.64 &  $12000 \pm 1000$ &  $4.0 \pm 0.25$ &  $2.9^{+0.45}_{-0.40}$ &     $58^{+104}_{-48}$ &       2 \\
+    HIP 2548 &    B9.5V &    00:32:23.78 &   +06:57:19.66 &   5.698 &     12.35 &   $11864 \pm 403$ &  $4.4 \pm 0.14$ &  $2.8^{+0.16}_{-0.15}$ &      $77^{+69}_{-51}$ &       1 \\
+    HIP 2912 &      B5V &    00:36:52.85 &   +33:43:09.64 &   4.360 &      5.45 &  $16000 \pm 1000$ &  $4.0 \pm 0.25$ &  $4.7^{+0.61}_{-0.54}$ &      $26^{+32}_{-18}$ &       2 \\
+    HIP 3300 &      B2V &    00:42:03.90 &   +50:30:45.09 &   4.810 &      2.28 &  $18000 \pm 1000$ &  $4.0 \pm 0.25$ &  $5.7^{+0.67}_{-0.63}$ &      $19^{+19}_{-13}$ &       2 \\
+    HIP 3478 &      B5V &    00:44:26.19 &   +47:51:50.34 &   5.646 &      5.23 &  $18000 \pm 1000$ &  $4.5 \pm 0.25$ &  $5.4^{+0.60}_{-0.57}$ &       $11^{+14}_{-5}$ &       2 \\
+    HIP 3741 &      B9V &    00:48:01.06 &   -21:43:20.99 &   5.570 &      9.51 &   $10000 \pm 500$ &  $3.5 \pm 0.25$ &  $2.8^{+0.47}_{-0.42}$ &    $282^{+82}_{-115}$ &       2 \\
+    HIP 3881 &      B5V &    00:49:48.85 &   +41:04:44.08 &   4.530 &      5.28 &  $16000 \pm 1000$ &  $4.2 \pm 0.25$ &  $4.5^{+0.58}_{-0.52}$ &      $17^{+28}_{-11}$ &       2 \\
+    HIP 4436 &      A5V &    00:56:45.21 &   +38:29:57.64 &   3.870 &     25.14 &    $8351 \pm 284$ &  $4.0 \pm 0.14$ &  $1.9^{+0.17}_{-0.14}$ &   $733^{+129}_{-158}$ &       1 \\
+    HIP 5131 &     A1Vn &    01:05:40.96 &   +21:28:23.45 &   5.317 &     11.86 &   $11956 \pm 406$ &  $4.4 \pm 0.14$ &  $2.8^{+0.16}_{-0.14}$ &      $69^{+65}_{-45}$ &       1 \\
+    HIP 5132 &     A0Vn &    01:05:41.71 &   +21:27:55.60 &   5.532 &     11.64 &   $12053 \pm 410$ &  $4.4 \pm 0.14$ &  $2.9^{+0.16}_{-0.14}$ &      $64^{+61}_{-42}$ &       1 \\
+    HIP 5310 &      A3V &    01:07:57.16 &   +20:44:20.83 &   5.569 &     21.14 &    $8611 \pm 293$ &  $4.4 \pm 0.14$ &  $1.8^{+0.10}_{-0.08}$ &   $307^{+228}_{-196}$ &       1 \\
+    HIP 5348 &  B6V+B9V &    01:08:23.08 &   -55:14:44.73 &   3.967 &     10.92 &   $13776 \pm 468$ &  $4.2 \pm 0.14$ &  $3.6^{+0.23}_{-0.21}$ &      $67^{+38}_{-39}$ &       1 \\
+    HIP 5361 &      B8V &    01:08:33.47 &   +58:15:48.41 &   5.773 &      5.41 &  $14000 \pm 1000$ &  $4.5 \pm 0.25$ &  $3.6^{+0.49}_{-0.43}$ &      $18^{+36}_{-11}$ &       2 \\
+    HIP 5518 &    A0Vnn &    01:10:39.32 &   +68:46:43.04 &   5.318 &     11.78 &   $11894 \pm 404$ &  $4.1 \pm 0.14$ &  $3.0^{+0.21}_{-0.19}$ &     $172^{+40}_{-72}$ &       1 \\
+    HIP 5626 &      A3V &    01:12:16.82 &   +79:40:26.27 &   5.600 &     12.07 &   $10342 \pm 352$ &  $4.2 \pm 0.14$ &  $2.4^{+0.15}_{-0.14}$ &   $218^{+102}_{-127}$ &       1 \\
+    HIP 7345 &      A1V &    01:34:37.78 &   -15:40:34.90 &   5.619 &     16.84 &   $10007 \pm 340$ &  $4.4 \pm 0.14$ &  $2.2^{+0.12}_{-0.11}$ &   $156^{+130}_{-100}$ &       1 \\
+    HIP 8016 &      B9V &    01:42:55.86 &   +70:37:21.09 &   5.177 &     11.75 &   $10000 \pm 500$ &  $4.0 \pm 0.25$ &  $2.3^{+0.25}_{-0.21}$ &     $67^{+188}_{-57}$ &       2 \\
+    HIP 8704 &    B1.5V &    01:51:59.32 &   +55:08:50.58 &   5.520 &      2.52 &  $22000 \pm 1000$ &  $4.5 \pm 0.25$ &  $7.8^{+0.74}_{-0.70}$ &         $8^{+6}_{-3}$ &       2 \\
+      HR 545 &      B9V &    01:53:31.77 &   +19:17:46.27 &   4.700 &   \nodata &   $10000 \pm 500$ &  $4.5 \pm 0.25$ &  $2.2^{+0.21}_{-0.20}$ &     $34^{+106}_{-27}$ &       2 \\
+    HIP 9312 &     A0Vn &    01:59:38.04 &   +64:37:17.76 &   5.283 &     13.28 &   $11913 \pm 405$ &  $4.1 \pm 0.14$ &  $2.8^{+0.13}_{-0.11}$ &      $77^{+65}_{-50}$ &       1 \\
+    HIP 9564 &     A1Vn &    02:02:52.48 &   +64:54:05.27 &   5.999 &     11.92 &   $11266 \pm 383$ &  $4.3 \pm 0.14$ &  $2.7^{+0.15}_{-0.12}$ &     $149^{+74}_{-88}$ &       1 \\
+      HR 604 &      B8V &    02:03:54.72 &   +42:19:51.41 &   5.820 &   \nodata &   $10000 \pm 500$ &  $3.5 \pm 0.25$ &  $2.8^{+0.46}_{-0.42}$ &    $281^{+82}_{-117}$ &       2 \\
+   HIP 10320 &      B9V &    02:12:54.47 &   -30:43:25.77 &   5.261 &     10.18 &   $11745 \pm 399$ &  $3.7 \pm 0.14$ &  $3.1^{+0.23}_{-0.19}$ &     $205^{+22}_{-43}$ &       1 \\
+   HIP 10670 &    A1Vnn &    02:17:18.87 &   +33:50:49.90 &   4.000 &     29.04 &   $10772 \pm 366$ &  $4.2 \pm 0.14$ &  $2.6^{+0.16}_{-0.13}$ &    $230^{+63}_{-109}$ &       1 \\
+   HIP 10732 &     A1Vn &    02:18:07.54 &   +19:54:04.19 &   5.575 &      7.29 &   $9500 \pm 1000$ &  $4.0 \pm 0.25$ &  $2.1^{+0.37}_{-0.31}$ &    $107^{+286}_{-93}$ &       2 \\
+   HIP 11345 &      A0V &    02:25:57.01 &   -12:17:25.71 &   4.869 &      7.15 &   $10000 \pm 500$ &  $4.0 \pm 0.25$ &  $2.3^{+0.25}_{-0.22}$ &     $72^{+206}_{-60}$ &       2 \\
+   HIP 12332 &      A7V &    02:38:48.99 &   +21:57:41.06 &   5.454 &      9.68 &    $8000 \pm 500$ &  $3.5 \pm 0.25$ &  $2.0^{+0.40}_{-0.33}$ &   $621^{+269}_{-268}$ &       2 \\
+   HIP 12706 &     A2Vn &    02:43:18.04 &   +03:14:08.94 &   3.470 &     40.97 &    $8551 \pm 291$ &  $4.3 \pm 0.14$ &  $1.9^{+0.15}_{-0.13}$ &   $647^{+104}_{-184}$ &       1 \\
+   HIP 12719 &      B3V &    02:43:27.11 &   +27:42:25.72 &   4.670 &      9.51 &  $18000 \pm 1000$ &  $4.5 \pm 0.25$ &  $5.4^{+0.62}_{-0.57}$ &       $11^{+14}_{-5}$ &       2 \\
+   HIP 12803 &     B9Vn &    02:44:32.97 &   +15:18:42.71 &   5.776 &      5.49 &  $12000 \pm 1000$ &  $4.5 \pm 0.25$ &  $2.8^{+0.39}_{-0.36}$ &      $25^{+63}_{-17}$ &       2 \\
+   HIP 13165 &      B6V &    02:49:17.56 &   +17:27:51.52 &   5.314 &      4.18 &  $16000 \pm 1000$ &  $4.5 \pm 0.25$ &  $4.4^{+0.55}_{-0.51}$ &       $13^{+22}_{-7}$ &       2 \\
+   HIP 13202 &      A0V &    02:49:54.18 &   -27:56:31.14 &   5.389 &      7.11 &    $9000 \pm 500$ &  $3.5 \pm 0.25$ &  $2.4^{+0.44}_{-0.38}$ &   $401^{+138}_{-170}$ &       2 \\
+   HIP 13209 &     B8Vn &    02:49:59.03 &   +27:15:37.83 &   3.606 &     19.69 &   $13316 \pm 453$ &  $4.1 \pm 0.14$ &  $3.3^{+0.15}_{-0.13}$ &      $45^{+43}_{-30}$ &       1 \\
+   HIP 13327 &      B7V &    02:51:29.59 &   +15:04:55.45 &   5.514 &      6.60 &  $14000 \pm 1000$ &  $4.0 \pm 0.25$ &  $3.8^{+0.55}_{-0.46}$ &      $36^{+57}_{-27}$ &       2 \\
+   HIP 13717 &      A3V &    02:56:37.42 &   -03:42:44.35 &   5.160 &     17.49 &    $8612 \pm 293$ &  $4.0 \pm 0.14$ &  $1.9^{+0.13}_{-0.11}$ &   $571^{+138}_{-255}$ &       1 \\
+   HIP 13879 &     A2Vn &    02:58:45.67 &   +39:39:45.81 &   4.700 &     10.53 &    $9298 \pm 316$ &  $3.5 \pm 0.14$ &  $2.1^{+0.12}_{-0.09}$ &   $340^{+141}_{-193}$ &       1 \\
+   HIP 14043 &      B7V &    03:00:52.21 &   +52:21:06.22 &   5.253 &      7.11 &  $14000 \pm 1000$ &  $4.5 \pm 0.25$ &  $3.6^{+0.48}_{-0.45}$ &      $17^{+33}_{-10}$ &       2 \\
+   HIP 14143 &      B7V &    03:02:22.52 &   +04:21:10.39 &   5.607 &      5.93 &  $14000 \pm 1000$ &  $4.5 \pm 0.25$ &  $3.6^{+0.50}_{-0.45}$ &      $17^{+36}_{-11}$ &       2 \\
+   HIP 14293 &      A5V &    03:04:16.52 &   -07:36:03.08 &   5.300 &     24.06 &    $8039 \pm 273$ &  $4.2 \pm 0.14$ &  $1.8^{+0.14}_{-0.10}$ &   $782^{+166}_{-291}$ &       1 \\
+   HIP 14576 &      B8V &    03:08:10.13 &   +40:57:20.33 &   2.120 &     36.27 &   $13070 \pm 444$ &  $4.0 \pm 0.14$ &  $3.6^{+0.29}_{-0.24}$ &     $139^{+16}_{-25}$ &       1 \\
+   HIP 14764 &      B8V &    03:10:38.79 &   +11:52:21.44 &   5.965 &      7.33 &  $12000 \pm 1000$ &  $4.0 \pm 0.25$ &  $2.9^{+0.47}_{-0.40}$ &     $54^{+103}_{-44}$ &       2 \\
+   HIP 14862 &    A2Vnn &    03:11:56.27 &   +74:23:37.17 &   4.840 &     19.72 &   $8875 \pm 1000$ &  $4.2 \pm 0.25$ &  $1.8^{+0.32}_{-0.29}$ &     $71^{+317}_{-60}$ &       2 \\
+   HIP 15110 &      A1V &    03:14:54.10 &   +21:02:40.01 &   4.880 &     12.44 &    $9902 \pm 337$ &  $4.0 \pm 0.14$ &  $2.4^{+0.18}_{-0.15}$ &    $375^{+52}_{-104}$ &       1 \\
+   HIP 15338 &      B8V &    03:17:47.35 &   +44:01:30.08 &   5.478 &      4.46 &  $12000 \pm 1000$ &  $3.5 \pm 0.25$ &  $3.5^{+0.65}_{-0.59}$ &     $155^{+68}_{-59}$ &       2 \\
+   HIP 15404 &      B3V &    03:18:37.74 &   +50:13:19.83 &   5.158 &      5.12 &  $20000 \pm 1000$ &  $4.5 \pm 0.25$ &  $6.5^{+0.68}_{-0.64}$ &         $9^{+9}_{-4}$ &       2 \\
+   HIP 15444 &      B5V &    03:19:07.64 &   +50:05:41.88 &   5.036 &      5.82 &  $18000 \pm 1000$ &  $4.5 \pm 0.25$ &  $5.5^{+0.60}_{-0.60}$ &       $11^{+14}_{-6}$ &       2 \\
+   HIP 16147 &      B5V &    03:28:03.07 &   +49:03:46.32 &   4.970 &      6.22 &  $18000 \pm 1000$ &  $4.5 \pm 0.25$ &  $5.4^{+0.59}_{-0.58}$ &       $11^{+14}_{-5}$ &       2 \\
    HIP 16210 &     B6Vn &    03:28:52.33 &   +49:50:54.17 &   5.578 &      6.22 &           \nodata &         \nodata &                \nodata &               \nodata & \nodata \\
-   HIP 16244 &            B3V &    03:29:22.05 &   +49:30:32.21 &   4.678 &      6.05 &  $16333 \pm 1000$ &  $4.3 \pm 0.25$ &  $4.7^{+0.57}_{-0.50}$ &      $15^{+22}_{-9}$ &  2 \\
-   HIP 16285 &            A5V &    03:29:55.15 &   -42:38:03.32 &   5.768 &     15.28 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 16322 &           A0Vn &    03:30:24.47 &   +11:20:11.19 &   5.125 &      9.03 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 16340 &            B8V &    03:30:36.95 &   +48:06:12.95 &   5.820 &      3.65 &  $12500 \pm 1000$ &  $4.0 \pm 0.25$ &  $3.1^{+0.51}_{-0.42}$ &     $49^{+92}_{-39}$ &  2 \\
-   HIP 16599 &            A3V &    03:33:39.06 &   +54:58:29.49 &   5.981 &     13.44 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 16611 &            B9V &    03:33:47.28 &   -21:37:58.38 &   4.300 &     11.12 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 17457 &            B7V &    03:44:30.51 &   -01:09:47.14 &   5.250 &      4.98 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 17527 &            B8V &    03:45:09.74 &   +24:50:21.34 &   5.640 &      7.97 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 17563 &            B3V &    03:45:40.44 &   +06:02:59.97 &   5.332 &      6.11 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 18141 &            B8V &    03:52:41.66 &   -05:21:40.54 &   5.476 &      5.57 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 18396 &            B6V &    03:55:58.17 &   +47:52:17.12 &   5.379 &      4.47 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 18724 &            B3V &    04:00:40.82 &   +12:29:25.22 &   3.410 &      6.74 &  $21000 \pm 1000$ &  $4.5 \pm 0.25$ &  $7.1^{+0.68}_{-0.64}$ &        $8^{+7}_{-3}$ &  2 \\
-   HIP 18788 &            B5V &    04:01:32.05 &   -01:32:58.78 &   5.280 &      7.88 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 18805 &            B5V &    04:01:46.14 &   +09:59:52.84 &   5.676 &      5.71 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 19799 &           B9Vn &    04:14:36.23 &   +10:00:41.05 &   5.208 &      8.34 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 19949 &           A2Vn &    04:16:43.09 &   +53:36:42.47 &   5.200 &      9.98 &    $9825 \pm 334$ &  $3.8 \pm 0.14$ &  $2.2^{+0.11}_{-0.09}$ &  $199^{+135}_{-124}$ &      1 \\
-   HIP 19968 &            B7V &    04:16:53.56 &   +61:50:59.97 &   5.700 &      7.31 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 20264 &            A0V &    04:20:39.01 &   -20:38:22.64 &   5.380 &      6.86 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 20380 &            A3V &    04:21:51.81 &   +56:30:22.74 &   5.920 &     10.31 &    $8738 \pm 297$ &  $3.9 \pm 0.14$ &  $1.9^{+0.10}_{-0.08}$ &  $331^{+213}_{-202}$ &      1 \\
-   HIP 20430 &          B9Vnn &    04:22:34.94 &   +25:37:45.54 &   5.376 &     11.20 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 20507 &            A2V &    04:23:40.85 &   -03:44:43.68 &   5.171 &     15.60 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 20579 &            B8V &    04:24:29.16 &   +34:07:50.73 &   5.722 &      7.28 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 20789 &            B7V &    04:27:17.45 &   +22:59:46.80 &   5.515 &      8.63 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 21589 &            A6V &    04:38:09.46 &   +12:30:39.01 &   4.270 &     21.24 &    $8591 \pm 292$ &  $3.9 \pm 0.14$ &  $1.8^{+0.09}_{-0.07}$ &  $303^{+231}_{-193}$ &      1 \\
-   HIP 21683 &           A5Vn &    04:39:16.50 &   +15:55:04.70 &   4.675 &     20.97 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 21819 &            A2V &    04:41:19.76 &   +28:36:53.98 &   5.726 &      8.55 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 21928 &           A1Vn &    04:42:54.33 &   +43:21:54.53 &   5.301 &     13.52 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 22028 &            A1V &    04:44:07.98 &   -18:39:59.71 &   5.527 &     10.66 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 22509 &           A1Vn &    04:50:36.72 &   +08:54:00.65 &   4.350 &     14.53 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 22833 &            A3V &    04:54:46.90 &   +11:25:33.63 &   5.186 &     14.29 &    $8278 \pm 281$ &  $3.9 \pm 0.14$ &  $1.8^{+0.13}_{-0.09}$ &  $653^{+159}_{-300}$ &      1 \\
-   HIP 22840 &            B5V &    04:54:50.71 &   +00:28:01.81 &   5.975 &      4.50 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 22913 &            B9V &    04:55:50.15 &   +15:02:25.00 &   5.785 &      8.97 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 22958 &            B6V &    04:56:24.19 &   -05:10:16.87 &   5.490 &      4.40 &  $16000 \pm 1000$ &  $4.5 \pm 0.25$ &  $4.5^{+0.53}_{-0.50}$ &      $14^{+21}_{-8}$ &  2 \\
+   HIP 16244 &      B3V &    03:29:22.05 &   +49:30:32.21 &   4.678 &      6.05 &  $18000 \pm 1000$ &  $4.5 \pm 0.25$ &  $5.4^{+0.61}_{-0.57}$ &       $11^{+14}_{-5}$ &       2 \\
+   HIP 16285 &      A5V &    03:29:55.15 &   -42:38:03.32 &   5.768 &     15.28 &    $7884 \pm 268$ &  $3.9 \pm 0.14$ &  $1.7^{+0.13}_{-0.09}$ &   $841^{+183}_{-335}$ &       1 \\
+   HIP 16322 &     A0Vn &    03:30:24.47 &   +11:20:11.19 &   5.125 &      9.03 &   $10000 \pm 500$ &  $4.0 \pm 0.25$ &  $2.3^{+0.26}_{-0.22}$ &     $80^{+200}_{-69}$ &       2 \\
+   HIP 16340 &      B8V &    03:30:36.95 &   +48:06:12.95 &   5.820 &      3.65 &  $12000 \pm 1000$ &  $4.0 \pm 0.25$ &  $2.9^{+0.48}_{-0.40}$ &     $54^{+107}_{-44}$ &       2 \\
+   HIP 16599 &      A3V &    03:33:39.06 &   +54:58:29.49 &   5.981 &     13.44 &    $8383 \pm 285$ &  $4.0 \pm 0.14$ &  $2.0^{+0.19}_{-0.15}$ &   $737^{+102}_{-102}$ &       1 \\
+   HIP 16611 &      B9V &    03:33:47.28 &   -21:37:58.38 &   4.300 &     11.12 &   $12514 \pm 425$ &  $4.0 \pm 0.14$ &  $3.3^{+0.24}_{-0.20}$ &     $157^{+23}_{-45}$ &       1 \\
+   HIP 17457 &     B7IV &    03:44:30.51 &   -01:09:47.14 &   5.250 &      4.98 &  $14000 \pm 1000$ &  $4.5 \pm 0.25$ &  $3.6^{+0.47}_{-0.44}$ &      $17^{+36}_{-10}$ &       2 \\
+   HIP 17527 &      B8V &    03:45:09.74 &   +24:50:21.34 &   5.640 &      7.97 &  $14000 \pm 1000$ &  $4.5 \pm 0.25$ &  $3.6^{+0.47}_{-0.44}$ &      $18^{+34}_{-11}$ &       2 \\
+   HIP 17563 &      B3V &    03:45:40.44 &   +06:02:59.97 &   5.332 &      6.11 &  $18000 \pm 1000$ &  $4.5 \pm 0.25$ &  $5.4^{+0.64}_{-0.57}$ &       $11^{+14}_{-5}$ &       2 \\
+   HIP 18141 &      B8V &    03:52:41.66 &   -05:21:40.54 &   5.476 &      5.57 &  $14000 \pm 1000$ &  $4.5 \pm 0.25$ &  $3.6^{+0.47}_{-0.43}$ &      $18^{+35}_{-12}$ &       2 \\
+   HIP 18396 &      B6V &    03:55:58.17 &   +47:52:17.12 &   5.379 &      4.47 &  $16000 \pm 1000$ &  $4.5 \pm 0.25$ &  $4.5^{+0.54}_{-0.50}$ &       $14^{+21}_{-8}$ &       2 \\
+   HIP 18724 &      B3V &    04:00:40.82 &   +12:29:25.22 &   3.410 &      6.74 &           \nodata &         \nodata &                \nodata &               \nodata & \nodata \\
+   HIP 18788 &      B5V &    04:01:32.05 &   -01:32:58.78 &   5.280 &      7.88 &  $16000 \pm 1000$ &  $4.5 \pm 0.25$ &  $4.5^{+0.51}_{-0.49}$ &       $13^{+22}_{-7}$ &       2 \\
+   HIP 18805 &      B5V &    04:01:46.14 &   +09:59:52.84 &   5.676 &      5.71 &  $18000 \pm 1000$ &  $4.5 \pm 0.25$ &  $5.4^{+0.60}_{-0.57}$ &       $10^{+14}_{-5}$ &       2 \\
+   HIP 19799 &     B9Vn &    04:14:36.23 &   +10:00:41.05 &   5.208 &      8.34 &   $10000 \pm 500$ &  $4.5 \pm 0.25$ &  $2.2^{+0.21}_{-0.19}$ &     $34^{+116}_{-26}$ &       2 \\
+   HIP 19949 &     A2Vn &    04:16:43.09 &   +53:36:42.47 &   5.200 &      9.98 &    $9825 \pm 334$ &  $3.8 \pm 0.14$ &  $2.2^{+0.11}_{-0.10}$ &   $197^{+140}_{-122}$ &       1 \\
+   HIP 19968 &      B7V &    04:16:53.56 &   +61:50:59.97 &   5.700 &      7.31 &  $16000 \pm 1000$ &  $4.5 \pm 0.25$ &  $4.5^{+0.53}_{-0.51}$ &       $13^{+21}_{-8}$ &       2 \\
+   HIP 20264 &      A0V &    04:20:39.01 &   -20:38:22.64 &   5.380 &      6.86 &   $10000 \pm 500$ &  $4.0 \pm 0.25$ &  $2.3^{+0.25}_{-0.21}$ &     $77^{+207}_{-65}$ &       2 \\
+   HIP 20380 &      A3V &    04:21:51.81 &   +56:30:22.74 &   5.920 &     10.31 &    $8738 \pm 297$ &  $3.9 \pm 0.14$ &  $1.9^{+0.10}_{-0.08}$ &   $338^{+206}_{-209}$ &       1 \\
+   HIP 20430 &    B9Vnn &    04:22:34.94 &   +25:37:45.54 &   5.376 &     11.20 &   $11981 \pm 407$ &  $4.2 \pm 0.14$ &  $3.2^{+0.28}_{-0.23}$ &     $195^{+23}_{-27}$ &       1 \\
+   HIP 20507 &      A2V &    04:23:40.85 &   -03:44:43.68 &   5.171 &     15.60 &    $8793 \pm 299$ &  $4.0 \pm 0.14$ &  $1.9^{+0.10}_{-0.08}$ &   $340^{+200}_{-210}$ &       1 \\
+   HIP 20579 &      B8V &    04:24:29.16 &   +34:07:50.73 &   5.722 &      7.28 &  $14000 \pm 1000$ &  $4.5 \pm 0.25$ &  $3.6^{+0.46}_{-0.46}$ &      $17^{+32}_{-10}$ &       2 \\
+   HIP 20789 &      B7V &    04:27:17.45 &   +22:59:46.80 &   5.515 &      8.63 &  $14000 \pm 1000$ &  $4.0 \pm 0.25$ &  $3.7^{+0.53}_{-0.47}$ &      $38^{+55}_{-28}$ &       2 \\
+   HIP 21589 &      A6V &    04:38:09.46 &   +12:30:39.01 &   4.270 &     21.24 &    $8591 \pm 292$ &  $3.9 \pm 0.14$ &  $1.8^{+0.09}_{-0.07}$ &   $300^{+231}_{-193}$ &       1 \\
+   HIP 21683 &     A5Vn &    04:39:16.50 &   +15:55:04.70 &   4.675 &     20.97 &    $8165 \pm 278$ &  $4.0 \pm 0.14$ &  $1.7^{+0.07}_{-0.06}$ &   $318^{+266}_{-211}$ &       1 \\
+   HIP 21819 &      A2V &    04:41:19.76 &   +28:36:53.98 &   5.726 &      8.55 &    $9000 \pm 500$ &  $3.5 \pm 0.25$ &  $2.4^{+0.41}_{-0.37}$ &   $411^{+135}_{-158}$ &       2 \\
+   HIP 21928 &     A1Vn &    04:42:54.33 &   +43:21:54.53 &   5.301 &     13.52 &   $10734 \pm 365$ &  $4.0 \pm 0.14$ &  $2.6^{+0.16}_{-0.13}$ &    $242^{+59}_{-108}$ &       1 \\
+   HIP 22028 &      A1V &    04:44:07.98 &   -18:39:59.71 &   5.527 &     10.66 &   $10118 \pm 344$ &  $4.0 \pm 0.14$ &  $2.3^{+0.14}_{-0.11}$ &   $246^{+105}_{-135}$ &       1 \\
+   HIP 22509 &     A1Vn &    04:50:36.72 &   +08:54:00.65 &   4.350 &     14.53 &    $9784 \pm 333$ &  $2.7 \pm 0.14$ &  $2.2^{+0.11}_{-0.10}$ &   $205^{+141}_{-129}$ &       1 \\
+   HIP 22833 &      A3V &    04:54:46.90 &   +11:25:33.63 &   5.186 &     14.29 &    $8278 \pm 281$ &  $3.9 \pm 0.14$ &  $1.8^{+0.12}_{-0.09}$ &   $645^{+165}_{-304}$ &       1 \\
+   HIP 22840 &      B5V &    04:54:50.71 &   +00:28:01.81 &   5.975 &      4.50 &  $16000 \pm 1000$ &  $4.0 \pm 0.25$ &  $4.7^{+0.61}_{-0.55}$ &      $27^{+32}_{-18}$ &       2 \\
+   HIP 22913 &      B9V &    04:55:50.15 &   +15:02:25.00 &   5.785 &      8.97 &  $12000 \pm 1000$ &  $3.5 \pm 0.25$ &  $3.5^{+0.67}_{-0.57}$ &     $155^{+68}_{-64}$ &       2 \\
+   HIP 22958 &      B6V &    04:56:24.19 &   -05:10:16.87 &   5.490 &      4.40 &  $16000 \pm 1000$ &  $4.5 \pm 0.25$ &  $4.5^{+0.52}_{-0.53}$ &       $13^{+20}_{-7}$ &       2 \\
    HIP 23362 &      B9V &    05:01:25.58 &   -20:03:06.91 &   4.894 &     16.48 &   $12450 \pm 423$ &  $4.3 \pm 0.14$ &  $3.2^{+0.21}_{-0.16}$ &     $147^{+28}_{-59}$ &       1 \\
-   HIP 23916 &            B8V &    05:08:20.19 &   -08:39:55.17 &   5.780 &      4.79 &  $16500 \pm 1000$ &  $4.2 \pm 0.25$ &  $4.8^{+0.56}_{-0.52}$ &     $16^{+26}_{-10}$ &  2 \\
-   HIP 24244 &         B7.5Vn &    05:12:17.90 &   -11:52:09.19 &   4.450 &     14.07 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 24327 &            B7V &    05:13:13.88 &   -12:56:28.65 &   4.421 &      4.48 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 24505 &            B9V &    05:15:24.37 &   -26:56:36.63 &   5.040 &     11.73 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 24902 &            A3V &    05:20:14.67 &   +41:05:10.35 &   5.468 &     11.77 &    $8275 \pm 281$ &  $4.0 \pm 0.14$ &  $1.7^{+0.10}_{-0.08}$ &  $463^{+256}_{-284}$ &      1 \\
-   HIP 25048 &            B3V &    05:21:48.42 &   +41:48:16.46 &   5.200 &      6.16 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 23916 &      B8V &    05:08:20.19 &   -08:39:55.17 &   5.780 &      4.79 &           \nodata &         \nodata &                \nodata &               \nodata & \nodata \\
+   HIP 24244 &   B7.5Vn &    05:12:17.90 &   -11:52:09.19 &   4.450 &     14.07 &   $13781 \pm 469$ &  $4.2 \pm 0.14$ &  $3.9^{+0.29}_{-0.23}$ &     $114^{+11}_{-23}$ &       1 \\
+   HIP 24327 &      B7V &    05:13:13.88 &   -12:56:28.65 &   4.421 &      4.48 &  $14000 \pm 1000$ &  $4.5 \pm 0.25$ &  $3.6^{+0.47}_{-0.44}$ &      $18^{+35}_{-11}$ &       2 \\
+   HIP 24505 &      B9V &    05:15:24.37 &   -26:56:36.63 &   5.040 &     11.73 &   $11748 \pm 399$ &  $4.2 \pm 0.14$ &  $2.9^{+0.16}_{-0.14}$ &     $152^{+53}_{-80}$ &       1 \\
+   HIP 24902 &      A3V &    05:20:14.67 &   +41:05:10.35 &   5.468 &     11.77 &    $8275 \pm 281$ &  $4.0 \pm 0.14$ &  $1.8^{+0.09}_{-0.08}$ &   $457^{+261}_{-281}$ &       1 \\
+   HIP 25048 &      B3V &    05:21:48.42 &   +41:48:16.46 &   5.200 &      6.16 &  $18000 \pm 1000$ &  $4.5 \pm 0.25$ &  $5.5^{+0.62}_{-0.61}$ &       $11^{+13}_{-5}$ &       2 \\
  ADS 3962 AB &     B1Vn &    05:22:50.30 &   +03:32:52.00 &   4.990 &   \nodata &           \nodata &         \nodata &                \nodata &               \nodata & \nodata \\
-   HIP 25143 &            A3V &    05:22:50.31 &   +41:01:45.33 &   5.545 &     11.15 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 25280 &            A0V &    05:24:28.49 &   -16:58:32.81 &   5.644 &     14.65 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 25281 &           B1V: &    05:24:28.62 &   -02:23:49.73 &   3.350 &      3.34 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 25555 &         B9.5Vn &    05:27:45.61 &   +15:52:26.58 &   5.512 &      7.69 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 25608 &            A1V &    05:28:15.34 &   -37:13:50.75 &   5.562 &     11.39 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 25695 &           B9Vn &    05:29:16.50 &   +25:09:00.78 &   5.480 &      7.67 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 25790 &           A3Vn &    05:30:26.16 &   +15:21:37.61 &   5.940 &     12.89 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 25813 &            B5V &    05:30:47.05 &   +05:56:53.29 &   4.200 &     10.77 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 25143 &      A3V &    05:22:50.31 &   +41:01:45.33 &   5.545 &     11.15 &    $8101 \pm 275$ &  $3.8 \pm 0.14$ &  $1.7^{+0.06}_{-0.06}$ &   $231^{+250}_{-156}$ &       1 \\
+   HIP 25280 &      A0V &    05:24:28.49 &   -16:58:32.81 &   5.644 &     14.65 &   $10398 \pm 354$ &  $4.4 \pm 0.14$ &  $2.4^{+0.13}_{-0.11}$ &   $199^{+101}_{-115}$ &       1 \\
+   HIP 25281 &      B1V &    05:24:28.62 &   -02:23:49.73 &   3.350 &      3.34 &           \nodata &         \nodata &                \nodata &               \nodata & \nodata \\
+   HIP 25555 &   B9.5Vn &    05:27:45.61 &   +15:52:26.58 &   5.512 &      7.69 &   $10000 \pm 500$ &  $3.5 \pm 0.25$ &  $2.8^{+0.45}_{-0.43}$ &    $283^{+79}_{-104}$ &       2 \\
+   HIP 25608 &      A1V &    05:28:15.34 &   -37:13:50.75 &   5.562 &     11.39 &    $9960 \pm 339$ &  $4.1 \pm 0.14$ &  $2.3^{+0.15}_{-0.12}$ &    $311^{+83}_{-149}$ &       1 \\
+   HIP 25695 &     B9Vn &    05:29:16.50 &   +25:09:00.78 &   5.480 &      7.67 &  $12000 \pm 1000$ &  $4.5 \pm 0.25$ &  $2.8^{+0.43}_{-0.37}$ &      $24^{+63}_{-17}$ &       2 \\
+   HIP 25790 &     A3Vn &    05:30:26.16 &   +15:21:37.61 &   5.940 &     12.89 &    $8397 \pm 286$ &  $3.9 \pm 0.14$ &  $1.8^{+0.08}_{-0.07}$ &   $329^{+250}_{-212}$ &       1 \\
+   HIP 25813 &      B5V &    05:30:47.05 &   +05:56:53.29 &   4.200 &     10.77 &   $15603 \pm 531$ &  $4.4 \pm 0.14$ &  $4.7^{+0.35}_{-0.28}$ &       $71^{+8}_{-16}$ &       1 \\
    HIP 26063 &      B1V &    05:33:31.45 &   -01:09:21.87 &   5.340 &      2.22 &           \nodata &         \nodata &                \nodata &               \nodata & \nodata \\
-   HIP 26093 &            B3V &    05:33:54.28 &   +14:18:20.08 &   5.588 &      7.31 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 26126 &            A2V &    05:34:16.77 &   +03:46:00.82 &   5.332 &     11.82 &    $9542 \pm 324$ &  $3.9 \pm 0.14$ &  $2.1^{+0.09}_{-0.08}$ &  $176^{+147}_{-116}$ &      1 \\
+   HIP 26093 &      B3V &    05:33:54.28 &   +14:18:20.08 &   5.588 &      7.31 &  $20000 \pm 1000$ &  $4.5 \pm 0.25$ &  $6.6^{+0.66}_{-0.64}$ &         $9^{+9}_{-4}$ &       2 \\
+   HIP 26126 &      A2V &    05:34:16.77 &   +03:46:00.82 &   5.332 &     11.82 &    $9542 \pm 324$ &  $3.9 \pm 0.14$ &  $2.1^{+0.09}_{-0.07}$ &   $177^{+150}_{-115}$ &       1 \\
      HR 1880 &    B0.5V &    05:35:08.48 &   +09:56:06.10 &   6.322 &   \nodata &  \nodata          &  \nodata        &  \nodata                &         \nodata          &       \nodata \\
-   HIP 26563 &           A4Vn &    05:38:53.08 &   -07:12:46.18 &   4.800 &     22.42 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 27100 &            A7V &    05:44:46.38 &   -65:44:07.90 &   4.360 &     21.80 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 27321 &            A6V &    05:47:17.09 &   -51:03:59.44 &   3.860 &     51.44 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 27713 &           A2Vn &    05:52:07.73 &   -09:02:30.84 &   5.964 &     10.11 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 28691 &            B8V &    06:03:27.37 &   +19:41:26.02 &   5.135 &      4.54 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 28756 &          B2.5V &    06:04:20.27 &   -32:10:20.74 &   5.631 &      3.24 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 28910 &            A0V &    06:06:09.32 &   -14:56:06.92 &   4.669 &     18.88 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 29150 &            A0V &    06:08:57.87 &   -22:25:38.68 &   5.482 &     13.24 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 29151 &           A3Vn &    06:08:57.90 &   +02:29:58.89 &   5.730 &      4.98 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 29735 &            B9V &    06:15:44.89 &   -13:43:06.29 &   4.998 &      8.00 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 29997 &           A0Vn &    06:18:50.78 &   +69:19:11.23 &   4.762 &     18.64 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 30069 &            B9V &    06:19:40.96 &   -34:23:47.73 &   5.750 &      8.00 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 30073 &            B2V &  06:19:42.7989 &  -07:49:22.473 &   5.246 &      3.74 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 30666 &           A3Vn &    06:26:39.59 &   -01:30:26.41 &   5.874 &     13.80 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 30788 &            B4V &    06:28:10.21 &   -32:34:48.25 &   4.480 &      7.70 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 31278 &           B5Vn &    06:33:37.92 &   -01:13:12.55 &   5.083 &      5.89 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 31362 &            B8V &    06:34:35.33 &   -32:42:58.51 &   5.610 &      6.20 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 31434 &          A0Vnn &    06:35:12.06 &   +28:01:20.32 &   5.266 &      8.82 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 32474 &          B9.5V &    06:46:39.02 &   -10:06:26.50 &   5.653 &      6.04 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 32607 &            A8V &    06:48:11.46 &   -61:56:29.00 &   3.300 &     33.78 &    $7770 \pm 264$ &  $3.8 \pm 0.14$ &  $1.6^{+0.07}_{-0.06}$ &  $517^{+344}_{-341}$ &      1 \\
-   HIP 33372 &           B8Vn &    06:56:25.83 &   +09:57:23.67 &   5.905 &      7.18 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 33575 &            B2V &    06:58:35.90 &   -25:24:50.97 &   5.577 &      3.78 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 34769 &            A2V &    07:11:51.86 &   -00:29:33.96 &   4.150 &      8.49 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 35180 &            A1V &    07:16:14.55 &   -15:35:08.49 &   5.454 &     12.12 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 35341 &           A5Vn &    07:18:02.22 &   +40:53:00.22 &   5.870 &     11.73 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 36393 &            A4V &    07:29:20.44 &   +28:07:05.79 &   5.072 &     18.51 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 36760 &           A1Vn &    07:33:36.48 &   +15:49:35.98 &   5.269 &      7.70 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 36812 &          A0Vnn &    07:34:15.89 &   +03:22:18.19 &   5.830 &      5.67 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 36917 &            B7V &    07:35:22.89 &   -28:22:09.57 &   4.630 &     14.72 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-     HR 2948 &            B6V &    07:38:49.38 &   -26:48:06.49 &   4.500 &   \nodata &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 37297 &          B2.5V &    07:39:27.34 &   -38:18:28.88 &   4.840 &      5.87 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 37322 &            B5V &    07:39:43.81 &   -38:08:21.44 &   5.664 &      5.70 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 37450 &            B5V &    07:41:15.81 &   -38:32:00.72 &   5.410 &      5.50 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 38538 &            A5V &    07:53:29.81 &   +26:45:56.82 &   4.977 &     14.66 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 38593 &            B2V &    07:54:11.01 &   -35:52:38.23 &   5.462 &      4.81 &  $21667 \pm 1000$ &  $4.5 \pm 0.25$ &  $7.6^{+0.74}_{-0.68}$ &        $8^{+6}_{-3}$ &  2 \\
-   HIP 38846 &          B2.5V &    07:56:57.80 &   -43:30:01.48 &   5.340 &      2.08 &  $22000 \pm 1000$ &  $4.5 \pm 0.25$ &  $7.8^{+0.74}_{-0.71}$ &        $8^{+6}_{-3}$ &  2 \\
-   HIP 39095 &            A1V &    07:59:52.05 &   -18:23:57.23 &   4.610 &     13.52 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 39236 &         B9.5Vn &    08:01:30.29 &   +16:27:19.12 &   5.990 &      6.04 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 39567 &            A1V &    08:05:04.49 &   +13:07:05.58 &   5.146 &     15.20 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 39847 &            A2V &    08:08:27.45 &   +51:30:24.01 &   4.802 &     13.04 &   $10014 \pm 340$ &  $4.0 \pm 0.14$ &  $2.2^{+0.13}_{-0.12}$ &  $193^{+132}_{-119}$ &      1 \\
-   HIP 39906 &            B5V &    08:09:01.64 &   -19:14:42.05 &   4.390 &      7.01 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 40429 &            A2V &    08:15:15.92 &   -62:54:56.32 &   5.160 &     12.90 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 40706 &            A8V &    08:18:33.31 &   -36:39:33.44 &   4.400 &     34.93 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 40881 &          B9.5V &    08:20:32.14 &   +24:01:20.32 &   5.930 &      7.13 &    $9500 \pm 300$ &  $4.0 \pm 0.25$ &  $2.1^{+0.17}_{-0.16}$ &    $71^{+239}_{-60}$ &  2 \\
+   HIP 26563 &     A4Vn &    05:38:53.08 &   -07:12:46.18 &   4.800 &     22.42 &    $8416 \pm 286$ &  $4.1 \pm 0.14$ &  $1.8^{+0.08}_{-0.07}$ &   $344^{+256}_{-218}$ &       1 \\
+   HIP 27100 &      A7V &    05:44:46.38 &   -65:44:07.90 &   4.360 &     21.80 &    $7828 \pm 266$ &  $3.9 \pm 0.14$ &  $1.8^{+0.18}_{-0.15}$ &   $965^{+153}_{-148}$ &       1 \\
+   HIP 27321 &      A6V &    05:47:17.09 &   -51:03:59.44 &   3.860 &     51.44 &    $8300 \pm 282$ &  $4.4 \pm 0.14$ &  $1.8^{+0.11}_{-0.09}$ &   $528^{+235}_{-300}$ &       1 \\
+   HIP 27713 &     A2Vn &    05:52:07.73 &   -09:02:30.84 &   5.964 &     10.11 &    $8474 \pm 288$ &  $3.9 \pm 0.14$ &  $1.8^{+0.09}_{-0.07}$ &   $383^{+238}_{-240}$ &       1 \\
+   HIP 28691 &      B5V &    06:03:27.37 &   +19:41:26.02 &   5.135 &      4.54 &  $14000 \pm 1000$ &  $4.0 \pm 0.25$ &  $3.8^{+0.54}_{-0.48}$ &      $36^{+55}_{-27}$ &       2 \\
+   HIP 28756 &    B2.5V &    06:04:20.27 &   -32:10:20.74 &   5.631 &      3.24 &  $20000 \pm 1000$ &  $4.0 \pm 0.25$ &  $6.9^{+0.75}_{-0.68}$ &       $14^{+13}_{-8}$ &       2 \\
+   HIP 28910 &      A0V &    06:06:09.32 &   -14:56:06.92 &   4.669 &     18.88 &   $10453 \pm 355$ &  $4.1 \pm 0.14$ &  $2.4^{+0.16}_{-0.14}$ &    $252^{+80}_{-122}$ &       1 \\
+   HIP 29150 &      A0V &    06:08:57.87 &   -22:25:38.68 &   5.482 &     13.24 &   $11283 \pm 384$ &  $4.2 \pm 0.14$ &  $2.6^{+0.12}_{-0.11}$ &     $112^{+82}_{-71}$ &       1 \\
+   HIP 29151 &     A3Vn &    06:08:57.90 &   +02:29:58.89 &   5.730 &      4.98 &    $9000 \pm 500$ &  $3.5 \pm 0.25$ &  $2.4^{+0.43}_{-0.37}$ &   $406^{+141}_{-177}$ &       2 \\
+   HIP 29735 &      B9V &    06:15:44.89 &   -13:43:06.29 &   4.998 &      8.00 &   $10000 \pm 500$ &  $3.5 \pm 0.25$ &  $2.8^{+0.48}_{-0.41}$ &    $281^{+84}_{-105}$ &       2 \\
+   HIP 29997 &     A0Vn &    06:18:50.78 &   +69:19:11.23 &   4.762 &     18.64 &   $10834 \pm 368$ &  $4.2 \pm 0.14$ &  $2.5^{+0.12}_{-0.10}$ &     $119^{+95}_{-77}$ &       1 \\
+   HIP 30069 &      B9V &    06:19:40.96 &   -34:23:47.73 &   5.750 &      8.00 &  $12000 \pm 1000$ &  $4.5 \pm 0.25$ &  $2.8^{+0.42}_{-0.38}$ &      $25^{+62}_{-18}$ &       2 \\
+   HIP 30073 &     B2V  &  06:19:42.7989 &  -07:49:22.473 &   5.246 &      3.74 &  $22000 \pm 1000$ &  $4.5 \pm 0.25$ &  $7.8^{+0.71}_{-0.71}$ &         $8^{+6}_{-3}$ &       2 \\
+   HIP 30666 &     A3Vn &    06:26:39.59 &   -01:30:26.41 &   5.874 &     13.80 &   $10520 \pm 358$ &  $4.2 \pm 0.14$ &  $2.6^{+0.20}_{-0.16}$ &     $304^{+37}_{-72}$ &       1 \\
+   HIP 30788 &      B4V &    06:28:10.21 &   -32:34:48.25 &   4.480 &      7.70 &  $18000 \pm 1000$ &  $4.5 \pm 0.25$ &  $5.4^{+0.59}_{-0.57}$ &       $11^{+13}_{-6}$ &       2 \\
+   HIP 31278 &     B5Vn &    06:33:37.92 &   -01:13:12.55 &   5.083 &      5.89 &  $16000 \pm 1000$ &  $4.0 \pm 0.25$ &  $4.7^{+0.61}_{-0.56}$ &      $26^{+31}_{-18}$ &       2 \\
+   HIP 31362 &      B8V &    06:34:35.33 &   -32:42:58.51 &   5.610 &      6.20 &  $12000 \pm 1000$ &  $4.5 \pm 0.25$ &  $2.8^{+0.41}_{-0.37}$ &      $24^{+62}_{-17}$ &       2 \\
+   HIP 31434 &    A0Vnn &    06:35:12.06 &   +28:01:20.32 &   5.266 &      8.82 &   $10000 \pm 500$ &  $3.5 \pm 0.25$ &  $2.7^{+0.46}_{-0.41}$ &    $281^{+83}_{-131}$ &       2 \\
+   HIP 32474 &    B9.5V &    06:46:39.02 &   -10:06:26.50 &   5.653 &      6.04 &   $10000 \pm 500$ &  $3.5 \pm 0.25$ &  $2.8^{+0.47}_{-0.43}$ &    $281^{+85}_{-117}$ &       2 \\
+   HIP 32607 &      A8V &    06:48:11.46 &   -61:56:29.00 &   3.300 &     33.78 &    $7770 \pm 264$ &  $3.8 \pm 0.14$ &  $1.6^{+0.07}_{-0.06}$ &   $519^{+344}_{-333}$ &       1 \\
+   HIP 33372 &     B8Vn &    06:56:25.83 &   +09:57:23.67 &   5.905 &      7.18 &  $14000 \pm 1000$ &  $4.5 \pm 0.25$ &  $3.6^{+0.47}_{-0.46}$ &      $18^{+37}_{-11}$ &       2 \\
+   HIP 33575 &      B2V &    06:58:35.90 &   -25:24:50.97 &   5.577 &      3.78 &  $22000 \pm 1000$ &  $4.5 \pm 0.25$ &  $7.8^{+0.69}_{-0.67}$ &         $8^{+6}_{-3}$ &       2 \\
+   HIP 34769 &      A2V &    07:11:51.86 &   -00:29:33.96 &   4.150 &      8.49 &    $9000 \pm 500$ &  $3.5 \pm 0.25$ &  $2.4^{+0.43}_{-0.38}$ &   $405^{+135}_{-207}$ &       2 \\
+   HIP 35180 &      A1V &    07:16:14.55 &   -15:35:08.49 &   5.454 &     12.12 &    $9562 \pm 325$ &  $4.1 \pm 0.14$ &  $2.1^{+0.12}_{-0.09}$ &   $267^{+139}_{-158}$ &       1 \\
+   HIP 35341 &     A5Vn &    07:18:02.22 &   +40:53:00.22 &   5.870 &     11.73 &    $8014 \pm 272$ &  $3.9 \pm 0.14$ &  $1.7^{+0.07}_{-0.06}$ &   $357^{+293}_{-237}$ &       1 \\
+   HIP 36393 &      A4V &    07:29:20.44 &   +28:07:05.79 &   5.072 &     18.51 &    $9184 \pm 312$ &  $4.1 \pm 0.14$ &  $2.1^{+0.15}_{-0.13}$ &   $431^{+128}_{-200}$ &       1 \\
+   HIP 36760 &     A1Vn &    07:33:36.48 &   +15:49:35.98 &   5.269 &      7.70 &    $9000 \pm 500$ &  $3.7 \pm 0.25$ &  $2.1^{+0.40}_{-0.26}$ &   $351^{+175}_{-318}$ &       2 \\
+   HIP 36812 &    A0Vnn &    07:34:15.89 &   +03:22:18.19 &   5.830 &      5.67 &   $9500 \pm 1000$ &  $4.0 \pm 0.25$ &  $2.1^{+0.40}_{-0.31}$ &    $108^{+273}_{-95}$ &       2 \\
+   HIP 36917 &      B7V &    07:35:22.89 &   -28:22:09.57 &   4.630 &     14.72 &   $13926 \pm 473$ &  $4.3 \pm 0.14$ &  $3.7^{+0.17}_{-0.15}$ &      $62^{+35}_{-37}$ &       1 \\
+     HR 2948 &      B6V &    07:38:49.38 &   -26:48:06.49 &   4.500 &   \nodata &  $14000 \pm 1000$ &  $4.5 \pm 0.25$ &  $3.6^{+0.48}_{-0.44}$ &      $17^{+36}_{-11}$ &       2 \\
+   HIP 37297 &    B2.5V &    07:39:27.34 &   -38:18:28.88 &   4.840 &      5.87 &  $20000 \pm 1000$ &  $4.5 \pm 0.25$ &  $6.6^{+0.67}_{-0.62}$ &         $9^{+9}_{-4}$ &       2 \\
+   HIP 37322 &      B5V &    07:39:43.81 &   -38:08:21.44 &   5.664 &      5.70 &  $16000 \pm 1000$ &  $4.5 \pm 0.25$ &  $4.5^{+0.50}_{-0.50}$ &       $13^{+22}_{-7}$ &       2 \\
+   HIP 37450 &      B5V &    07:41:15.81 &   -38:32:00.72 &   5.410 &      5.50 &  $16000 \pm 1000$ &  $4.5 \pm 0.25$ &  $4.4^{+0.53}_{-0.48}$ &       $13^{+22}_{-8}$ &       2 \\
+   HIP 38538 &      A3V &    07:53:29.81 &   +26:45:56.82 &   4.977 &     14.66 &    $8551 \pm 291$ &  $4.0 \pm 0.14$ &  $1.9^{+0.15}_{-0.12}$ &   $637^{+111}_{-199}$ &       1 \\
+   HIP 38593 &      B2V &    07:54:11.01 &   -35:52:38.23 &   5.462 &      4.81 &  $22000 \pm 1000$ &  $4.5 \pm 0.25$ &  $7.8^{+0.77}_{-0.68}$ &         $8^{+6}_{-3}$ &       2 \\
+   HIP 38846 &    B2.5V &    07:56:57.80 &   -43:30:01.48 &   5.340 &      2.08 &  $22000 \pm 1000$ &  $4.5 \pm 0.25$ &  $7.8^{+0.75}_{-0.72}$ &         $8^{+6}_{-3}$ &       2 \\
+   HIP 39095 &      A1V &    07:59:52.05 &   -18:23:57.23 &   4.610 &     13.52 &    $8872 \pm 302$ &  $3.4 \pm 0.14$ &  $2.1^{+0.18}_{-0.15}$ &     $593^{+74}_{-85}$ &       1 \\
+   HIP 39236 &   B9.5Vn &    08:01:30.29 &   +16:27:19.12 &   5.990 &      6.04 &   $10000 \pm 500$ &  $4.5 \pm 0.25$ &  $2.2^{+0.21}_{-0.19}$ &     $36^{+119}_{-27}$ &       2 \\
+   HIP 39567 &      A1V &    08:05:04.49 &   +13:07:05.58 &   5.146 &     15.20 &   $10352 \pm 352$ &  $4.3 \pm 0.14$ &  $2.4^{+0.12}_{-0.10}$ &   $178^{+110}_{-109}$ &       1 \\
+   HIP 39847 &      A2V &    08:08:27.45 &   +51:30:24.01 &   4.802 &     13.04 &   $10014 \pm 340$ &  $4.0 \pm 0.14$ &  $2.2^{+0.14}_{-0.12}$ &   $190^{+127}_{-116}$ &       1 \\
+   HIP 39906 &      B5V &    08:09:01.64 &   -19:14:42.05 &   4.390 &      7.01 &  $18000 \pm 1000$ &  $4.5 \pm 0.25$ &  $5.4^{+0.63}_{-0.54}$ &       $11^{+15}_{-5}$ &       2 \\
+   HIP 40429 &      A2V &    08:15:15.92 &   -62:54:56.32 &   5.160 &     12.90 &    $8725 \pm 297$ &  $3.9 \pm 0.14$ &  $2.1^{+0.20}_{-0.17}$ &     $635^{+88}_{-88}$ &       1 \\
+   HIP 40706 &      A8V &    08:18:33.31 &   -36:39:33.44 &   4.400 &     34.93 &    $7986 \pm 272$ &  $4.3 \pm 0.14$ &  $1.7^{+0.08}_{-0.06}$ &   $540^{+282}_{-330}$ &       1 \\
+   HIP 40881 &    B9.5V &    08:20:32.14 &   +24:01:20.32 &   5.930 &      7.13 &   $9500 \pm 1000$ &  $4.0 \pm 0.25$ &  $2.1^{+0.39}_{-0.32}$ &    $105^{+287}_{-93}$ &       2 \\
    HIP 41039 &      B1V &    08:22:31.69 &   -48:29:25.36 &   4.820 &      1.90 &           \nodata &         \nodata &                \nodata &               \nodata & \nodata \\
-   HIP 41307 &           A0Va &    08:25:39.63 &   -03:54:23.12 &   3.900 &     26.66 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 42090 &          A2Vnn &    08:34:43.88 &   +36:25:10.63 &   5.755 &      9.19 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 42129 &            B3V &    08:35:15.56 &   -58:13:29.05 &   5.241 &      3.64 &  $18000 \pm 1000$ &  $4.5 \pm 0.25$ &  $5.4^{+0.63}_{-0.54}$ &      $11^{+14}_{-5}$ &  2 \\
-   HIP 42313 &          A0Vnn &    08:37:39.37 &   +05:42:13.61 &   4.137 &     20.34 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 42334 &            A0V &    08:37:52.15 &   -26:15:18.01 &   5.270 &     14.07 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 43142 &            A3V &    08:47:14.99 &   -01:53:49.31 &   5.279 &      8.12 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 44127 &            A7V &    08:59:12.45 &   +48:02:30.57 &   3.140 &     68.92 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 44307 &            A2V &    09:01:24.13 &   +32:15:08.26 &   5.870 &      6.99 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 45336 &          B9.5V &    09:14:21.86 &   +02:18:51.34 &   3.880 &     28.74 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 45344 &            B4V &    09:14:24.48 &   -43:13:38.97 &   5.250 &      5.33 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 45688 &            A1V &    09:18:50.64 &   +36:48:09.33 &   3.820 &     26.13 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 46225 &            A4V &    09:25:27.23 &   -61:57:01.72 &   5.781 &     12.92 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 46283 &            B6V &    09:26:17.96 &   -53:22:44.07 &   5.088 &      7.60 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 46897 &          B9.5V &    09:33:26.05 &   -22:51:49.99 &   5.911 &     12.46 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 47006 &           A0Vn &    09:34:49.43 &   +52:03:05.32 &   4.479 &     12.44 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 47175 &            A7V &    09:36:49.54 &   -49:21:18.09 &   4.350 &     30.94 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 50303 &           A0Vn &    10:16:14.43 &   +29:18:37.81 &   5.490 &     12.51 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 50860 &          A5IVn &    10:23:06.33 &   +33:54:29.31 &   5.900 &     13.46 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 51362 &          B9.5V &    10:29:28.70 &   -02:44:20.69 &   5.180 &     10.13 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 51685 &           A2Vn &    10:33:30.91 &   +34:59:19.30 &   5.580 &      4.77 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 52422 &           A4Vn &    10:43:01.88 &   +26:19:32.09 &   5.517 &     20.67 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 52457 &           A3Vn &    10:43:24.96 &   +23:11:18.25 &   5.075 &     14.23 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 52638 &           A1Vn &    10:45:51.89 &   +30:40:56.33 &   5.349 &      8.53 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 52678 &          B6Vnn &    10:46:16.56 &   -64:30:52.41 &   5.340 &      6.85 &  $15000 \pm 1000$ &  $4.5 \pm 0.25$ &  $4.0^{+0.49}_{-0.50}$ &     $16^{+26}_{-10}$ &  2 \\
-   HIP 52736 &         B2.5Vn &    10:46:51.22 &   -64:23:00.50 &   4.850 &      6.79 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 52911 &            A2V &    10:49:15.43 &   +10:32:42.73 &   5.314 &      8.57 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-     HR 4259 &            A1V &    10:55:36.80 &   +24:44:59.00 &   4.500 &   \nodata &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 54849 &            A0V &    11:13:45.55 &   -00:04:10.20 &   5.399 &      6.18 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 55266 &            A2V &    11:19:07.90 &   +38:11:08.03 &   4.800 &     17.00 &    $8720 \pm 296$ &  $4.5 \pm 0.14$ &  $1.9^{+0.09}_{-0.07}$ &  $345^{+211}_{-213}$ &      1 \\
-   HIP 55434 &         B9.5Vs &  11:21:08.1934 &  +06:01:45.571 &   4.044 &     14.82 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 56034 &            A2V &    11:29:04.12 &   +39:20:13.11 &   5.354 &     15.33 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 56633 &          B9.5V &    11:36:40.91 &   -09:48:08.09 &   4.682 &     11.63 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 57328 &            A4V &    11:45:17.04 &   +08:15:29.21 &   4.845 &     26.73 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 58590 &            A5V &    12:00:52.39 &   +06:36:51.56 &   4.659 &      8.49 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 59394 &            A1V &    12:11:03.84 &   -23:36:08.72 &   5.470 &     17.00 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 59449 &            B3V &    12:11:39.12 &   -52:22:06.44 &   3.960 &      8.61 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 59819 &            A3V &    12:16:00.19 &   +14:53:56.65 &   5.090 &     16.42 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 60009 &          B2.5V &    12:18:26.25 &   -64:00:11.05 &   4.050 &      9.12 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 60030 &           A5Vn &    12:18:40.32 &   -00:47:13.87 &   5.908 &      8.73 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 60595 &            A1V &    12:25:11.76 &   -11:36:38.12 &   5.949 &     14.18 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 60710 &           B3Vn &    12:26:31.76 &   -51:27:02.29 &   4.805 &      7.28 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 60957 &            A3V &    12:29:43.24 &   +20:53:45.99 &   5.680 &     11.90 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 61558 &            A3V &    12:36:47.35 &   -05:49:54.84 &   5.880 &     14.49 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 61622 &          A1Vnn &    12:37:42.16 &   -48:32:28.69 &   3.860 &     24.85 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 62541 &            A1V &    12:48:54.21 &   +14:07:21.31 &   5.702 &      8.17 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 62576 &            A2V &    12:49:17.45 &   +27:33:08.57 &   5.780 &     10.76 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 63724 &            A0V &    13:03:33.31 &   -49:31:38.15 &   4.830 &     14.79 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 63945 &            B5V &    13:06:16.70 &   -48:27:47.85 &   4.694 &      8.36 &  $18000 \pm 1000$ &  $4.5 \pm 0.25$ &  $5.4^{+0.60}_{-0.56}$ &      $11^{+14}_{-5}$ &  2 \\
-   HIP 65198 &            A2V &    13:21:41.64 &   +02:05:14.07 &   5.693 &     14.77 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 65477 &            A5V &    13:25:13.54 &   +54:59:16.65 &   4.010 &     39.91 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 65728 &           A1Vn &    13:28:27.09 &   +59:56:44.83 &   5.400 &     14.01 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 66249 &          A2Van &    13:34:41.74 &   -00:35:45.38 &   3.380 &     44.03 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 66798 &            A2V &    13:41:29.89 &   +64:49:20.68 &   5.850 &     14.66 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 66821 &          B8.5V &    13:41:44.77 &   -54:33:33.93 &   5.010 &     12.02 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 67143 &            A0V &    13:45:36.89 &   -26:06:57.63 &   5.805 &     11.49 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 67194 &            A5V &    13:46:13.55 &   +41:05:19.48 &   5.891 &     19.03 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 67782 &           A8IV &    13:53:10.28 &   +28:38:53.28 &   5.911 &     15.21 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 68092 &            A8V &    13:56:27.88 &   +01:03:02.09 &   5.906 &     11.08 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 68520 &            A3V &    14:01:38.79 &   +01:32:40.31 &   4.244 &     14.50 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 70327 &            A0V &    14:23:22.70 &   +08:26:47.84 &   5.120 &     15.17 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 70384 &            A3V &    14:24:00.88 &   +08:14:38.30 &   5.935 &      7.38 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 70400 &            A3V &    14:24:11.34 &   +05:49:12.47 &   5.103 &     20.51 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 70915 &           B8Vn &    14:30:08.63 &   -45:19:16.88 &   5.500 &      6.84 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 41307 &     A0Va &    08:25:39.63 &   -03:54:23.12 &   3.900 &     26.66 &   $10281 \pm 350$ &  $4.2 \pm 0.14$ &  $2.3^{+0.12}_{-0.10}$ &   $201^{+109}_{-120}$ &       1 \\
+   HIP 42090 &    A2Vnn &    08:34:43.88 &   +36:25:10.63 &   5.755 &      9.19 &   $9000 \pm 1000$ &  $4.0 \pm 0.25$ &  $1.9^{+0.36}_{-0.31}$ &   $133^{+379}_{-119}$ &       2 \\
+   HIP 42129 &      B3V &    08:35:15.56 &   -58:13:29.05 &   5.241 &      3.64 &  $18000 \pm 1000$ &  $4.5 \pm 0.25$ &  $5.4^{+0.61}_{-0.56}$ &       $11^{+14}_{-5}$ &       2 \\
+   HIP 42313 &    A0Vnn &    08:37:39.37 &   +05:42:13.61 &   4.137 &     20.34 &   $11055 \pm 376$ &  $4.0 \pm 0.14$ &  $2.9^{+0.23}_{-0.19}$ &     $260^{+29}_{-44}$ &       1 \\
+   HIP 42334 &      A0V &    08:37:52.15 &   -26:15:18.01 &   5.270 &     14.07 &   $11614 \pm 395$ &  $4.3 \pm 0.14$ &  $2.7^{+0.12}_{-0.10}$ &      $79^{+71}_{-51}$ &       1 \\
+   HIP 43142 &      A3V &    08:47:14.99 &   -01:53:49.31 &   5.279 &      8.12 &    $9000 \pm 500$ &  $4.0 \pm 0.25$ &  $2.0^{+0.21}_{-0.18}$ &     $94^{+314}_{-83}$ &       2 \\
+   HIP 44127 &      A7V &    08:59:12.45 &   +48:02:30.57 &   3.140 &     68.92 &    $8233 \pm 280$ &  $4.4 \pm 0.14$ &  $1.7^{+0.09}_{-0.07}$ &   $474^{+257}_{-294}$ &       1 \\
+   HIP 44307 &      A2V &    09:01:24.13 &   +32:15:08.26 &   5.870 &      6.99 &   $8500 \pm 1000$ &  $4.0 \pm 0.25$ &  $1.7^{+0.33}_{-0.28}$ &   $162^{+537}_{-148}$ &       2 \\
+   HIP 45336 &    B9.5V &    09:14:21.86 &   +02:18:51.34 &   3.880 &     28.74 &   $10826 \pm 368$ &  $4.2 \pm 0.14$ &  $2.5^{+0.12}_{-0.10}$ &     $111^{+95}_{-71}$ &       1 \\
+   HIP 45344 &      B4V &    09:14:24.48 &   -43:13:38.97 &   5.250 &      5.33 &  $18000 \pm 1000$ &  $4.5 \pm 0.25$ &  $5.4^{+0.62}_{-0.57}$ &       $11^{+14}_{-5}$ &       2 \\
+   HIP 45688 &      A1V &    09:18:50.64 &   +36:48:09.33 &   3.820 &     26.13 &    $8862 \pm 301$ &  $3.9 \pm 0.14$ &  $1.9^{+0.08}_{-0.07}$ &   $255^{+202}_{-160}$ &       1 \\
+   HIP 46225 &      A4V &    09:25:27.23 &   -61:57:01.72 &   5.781 &     12.92 &    $8577 \pm 292$ &  $4.0 \pm 0.14$ &  $1.8^{+0.10}_{-0.07}$ &   $418^{+206}_{-252}$ &       1 \\
+   HIP 46283 &      B6V &    09:26:17.96 &   -53:22:44.07 &   5.088 &      7.60 &  $16000 \pm 1000$ &  $4.5 \pm 0.25$ &  $4.5^{+0.54}_{-0.50}$ &       $13^{+20}_{-8}$ &       2 \\
+   HIP 46897 &    B9.5V &    09:33:26.05 &   -22:51:49.99 &   5.911 &     12.46 &   $10075 \pm 343$ &  $4.2 \pm 0.14$ &  $2.3^{+0.16}_{-0.13}$ &    $286^{+93}_{-140}$ &       1 \\
+   HIP 47006 &     A0Vn &    09:34:49.43 &   +52:03:05.32 &   4.479 &     12.44 &    $9757 \pm 332$ &  $3.9 \pm 0.14$ &  $2.1^{+0.10}_{-0.08}$ &   $181^{+138}_{-114}$ &       1 \\
+   HIP 47175 &      A7V &    09:36:49.54 &   -49:21:18.09 &   4.350 &     30.94 &    $8331 \pm 283$ &  $4.3 \pm 0.14$ &  $1.8^{+0.11}_{-0.09}$ &   $453^{+256}_{-278}$ &       1 \\
+   HIP 50303 &     A0Vn &    10:16:14.43 &   +29:18:37.81 &   5.490 &     12.51 &   $10377 \pm 353$ &  $4.1 \pm 0.14$ &  $2.4^{+0.13}_{-0.11}$ &   $204^{+103}_{-116}$ &       1 \\
+   HIP 50860 &      A6V &    10:23:06.33 &   +33:54:29.31 &   5.900 &     13.46 &    $8327 \pm 283$ &  $4.1 \pm 0.14$ &  $1.8^{+0.11}_{-0.09}$ &   $591^{+183}_{-303}$ &       1 \\
+   HIP 51362 &    B9.5V &    10:29:28.70 &   -02:44:20.69 &   5.180 &     10.13 &   $10899 \pm 371$ &  $4.0 \pm 0.14$ &  $2.6^{+0.14}_{-0.12}$ &    $182^{+81}_{-101}$ &       1 \\
+   HIP 51685 &     A2Vn &    10:33:30.91 &   +34:59:19.30 &   5.580 &      4.77 &    $9000 \pm 500$ &  $3.5 \pm 0.25$ &  $2.4^{+0.42}_{-0.38}$ &   $406^{+134}_{-172}$ &       2 \\
+   HIP 52422 &     A4Vn &    10:43:01.88 &   +26:19:32.09 &   5.517 &     20.67 &    $8170 \pm 278$ &  $4.3 \pm 0.14$ &  $1.7^{+0.08}_{-0.06}$ &   $432^{+278}_{-278}$ &       1 \\
+   HIP 52457 &     A3Vn &    10:43:24.96 &   +23:11:18.25 &   5.075 &     14.23 &    $9902 \pm 337$ &  $4.0 \pm 0.14$ &  $2.2^{+0.12}_{-0.10}$ &   $228^{+126}_{-137}$ &       1 \\
+   HIP 52638 &     A1Vn &    10:45:51.89 &   +30:40:56.33 &   5.349 &      8.53 &   $10000 \pm 500$ &  $4.0 \pm 0.25$ &  $2.3^{+0.25}_{-0.21}$ &     $69^{+199}_{-59}$ &       2 \\
+   HIP 52678 &    B6Vnn &    10:46:16.56 &   -64:30:52.41 &   5.340 &      6.85 &  $16000 \pm 1000$ &  $4.5 \pm 0.25$ &  $4.4^{+0.55}_{-0.48}$ &       $13^{+20}_{-7}$ &       2 \\
+   HIP 52736 &   B2.5Vn &    10:46:51.22 &   -64:23:00.50 &   4.850 &      6.79 &  $20000 \pm 1000$ &  $4.5 \pm 0.25$ &  $6.5^{+0.66}_{-0.62}$ &         $9^{+9}_{-4}$ &       2 \\
+   HIP 52911 &      A2V &    10:49:15.43 &   +10:32:42.73 &   5.314 &      8.57 &    $9000 \pm 500$ &  $3.5 \pm 0.25$ &  $2.4^{+0.44}_{-0.37}$ &   $406^{+138}_{-172}$ &       2 \\
+     HR 4259 &      A1V &    10:55:36.80 &   +24:44:59.00 &   4.500 &   \nodata &    $9000 \pm 500$ &  $3.5 \pm 0.25$ &  $2.4^{+0.44}_{-0.36}$ &   $411^{+137}_{-168}$ &       2 \\
+   HIP 54849 &      A0V &    11:13:45.55 &   -00:04:10.20 &   5.399 &      6.18 &   $10000 \pm 500$ &  $4.0 \pm 0.25$ &  $2.3^{+0.24}_{-0.21}$ &     $72^{+197}_{-62}$ &       2 \\
+   HIP 55266 &      A2V &    11:19:07.90 &   +38:11:08.03 &   4.800 &     17.00 &    $8720 \pm 296$ &  $4.5 \pm 0.14$ &  $1.9^{+0.10}_{-0.08}$ &   $346^{+208}_{-217}$ &       1 \\
+   HIP 55434 &    B9.5V &  11:21:08.1934 &  +06:01:45.571 &   4.044 &     14.82 &   $10618 \pm 361$ &  $3.9 \pm 0.14$ &  $2.7^{+0.23}_{-0.19}$ &     $304^{+32}_{-38}$ &       1 \\
+   HIP 56034 &      A2V &    11:29:04.12 &   +39:20:13.11 &   5.354 &     15.33 &   $10000 \pm 500$ &  $4.5 \pm 0.25$ &  $2.2^{+0.21}_{-0.21}$ &     $37^{+118}_{-29}$ &       2 \\
+   HIP 56633 &    B9.5V &    11:36:40.91 &   -09:48:08.09 &   4.682 &     11.63 &   $11524 \pm 392$ &  $4.0 \pm 0.14$ &  $2.8^{+0.15}_{-0.12}$ &     $145^{+66}_{-82}$ &       1 \\
+   HIP 57328 &      A4V &    11:45:17.04 &   +08:15:29.21 &   4.845 &     26.73 &    $8298 \pm 282$ &  $4.3 \pm 0.14$ &  $1.9^{+0.17}_{-0.14}$ &   $757^{+105}_{-135}$ &       1 \\
+   HIP 58590 &      A5V &    12:00:52.39 &   +06:36:51.56 &   4.659 &      8.49 &    $8000 \pm 500$ &  $3.5 \pm 0.25$ &  $2.0^{+0.41}_{-0.35}$ &   $618^{+265}_{-300}$ &       2 \\
+   HIP 59394 &      A1V &    12:11:03.84 &   -23:36:08.72 &   5.470 &     17.00 &    $9671 \pm 329$ &  $4.3 \pm 0.14$ &  $2.1^{+0.10}_{-0.09}$ &   $203^{+144}_{-128}$ &       1 \\
+   HIP 59449 &      B3V &    12:11:39.12 &   -52:22:06.44 &   3.960 &      8.61 &  $18000 \pm 1000$ &  $4.5 \pm 0.25$ &  $5.4^{+0.61}_{-0.55}$ &       $11^{+14}_{-5}$ &       2 \\
+   HIP 59819 &      A3V &    12:16:00.19 &   +14:53:56.65 &   5.090 &     16.42 &    $9528 \pm 324$ &  $4.0 \pm 0.14$ &  $2.2^{+0.16}_{-0.14}$ &    $394^{+95}_{-165}$ &       1 \\
+   HIP 60009 &    B2.5V &    12:18:26.25 &   -64:00:11.05 &   4.050 &      9.12 &  $20000 \pm 1000$ &  $4.5 \pm 0.25$ &  $6.6^{+0.65}_{-0.66}$ &         $9^{+9}_{-4}$ &       2 \\
+   HIP 60030 &     A5Vn &    12:18:40.32 &   -00:47:13.87 &   5.908 &      8.73 &   $7750 \pm 1000$ &  $3.5 \pm 0.25$ &  $1.9^{+0.50}_{-0.39}$ &   $778^{+807}_{-403}$ &       2 \\
+   HIP 60595 &      A1V &    12:25:11.76 &   -11:36:38.12 &   5.949 &     14.18 &   $10396 \pm 353$ &  $4.4 \pm 0.14$ &  $2.4^{+0.12}_{-0.10}$ &   $161^{+111}_{-100}$ &       1 \\
+   HIP 60710 &     B3Vn &    12:26:31.76 &   -51:27:02.29 &   4.805 &      7.28 &  $20000 \pm 1000$ &  $4.5 \pm 0.25$ &  $6.5^{+0.67}_{-0.63}$ &         $9^{+9}_{-4}$ &       2 \\
+   HIP 60957 &      A3V &    12:29:43.24 &   +20:53:45.99 &   5.680 &     11.90 &    $9079 \pm 309$ &  $3.9 \pm 0.14$ &  $2.1^{+0.15}_{-0.12}$ &   $480^{+100}_{-192}$ &       1 \\
+   HIP 61558 &      A3V &    12:36:47.35 &   -05:49:54.84 &   5.880 &     14.49 &    $9600 \pm 326$ &  $4.2 \pm 0.14$ &  $2.3^{+0.19}_{-0.16}$ &     $436^{+57}_{-75}$ &       1 \\
+   HIP 61622 &      A2V &    12:37:42.16 &   -48:32:28.69 &   3.860 &     24.85 &   $10533 \pm 358$ &  $4.0 \pm 0.14$ &  $2.3^{+0.25}_{-0.23}$ &   $158^{+137}_{-102}$ &       1 \\
+   HIP 62541 &      A1V &    12:48:54.21 &   +14:07:21.31 &   5.702 &      8.17 &   $9250 \pm 1000$ &  $4.0 \pm 0.25$ &  $2.0^{+0.36}_{-0.31}$ &   $124^{+326}_{-110}$ &       2 \\
+   HIP 62576 &      A2V &    12:49:17.45 &   +27:33:08.57 &   5.780 &     10.76 &    $9955 \pm 338$ &  $4.1 \pm 0.14$ &  $2.2^{+0.12}_{-0.11}$ &   $188^{+132}_{-117}$ &       1 \\
+   HIP 63724 &      A0V &    13:03:33.31 &   -49:31:38.15 &   4.830 &     14.79 &   $10462 \pm 356$ &  $4.1 \pm 0.14$ &  $2.4^{+0.12}_{-0.10}$ &    $154^{+106}_{-96}$ &       1 \\
+   HIP 63945 &      B5V &    13:06:16.70 &   -48:27:47.85 &   4.694 &      8.36 &  $18000 \pm 1000$ &  $4.5 \pm 0.25$ &  $5.4^{+0.61}_{-0.56}$ &       $11^{+13}_{-6}$ &       2 \\
+   HIP 65198 &      A2V &    13:21:41.64 &   +02:05:14.07 &   5.693 &     14.77 &   $10291 \pm 350$ &  $4.2 \pm 0.14$ &  $2.3^{+0.11}_{-0.10}$ &   $174^{+111}_{-108}$ &       1 \\
+   HIP 65477 &      A5V &    13:25:13.54 &   +54:59:16.65 &   4.010 &     39.91 &    $8221 \pm 280$ &  $4.2 \pm 0.14$ &  $1.8^{+0.16}_{-0.13}$ &   $754^{+157}_{-222}$ &       1 \\
+   HIP 65728 &     A1Vn &    13:28:27.09 &   +59:56:44.83 &   5.400 &     14.01 &   $10388 \pm 353$ &  $4.2 \pm 0.14$ &  $2.7^{+0.24}_{-0.19}$ &     $331^{+39}_{-45}$ &       1 \\
+   HIP 66249 &    A2Van &    13:34:41.74 &   -00:35:45.38 &   3.380 &     44.03 &    $8542 \pm 290$ &  $4.1 \pm 0.14$ &  $1.9^{+0.15}_{-0.12}$ &   $631^{+113}_{-226}$ &       1 \\
+   HIP 66798 &      A2V &    13:41:29.89 &   +64:49:20.68 &   5.850 &     14.66 &    $9347 \pm 318$ &  $4.2 \pm 0.14$ &  $2.1^{+0.11}_{-0.09}$ &   $291^{+153}_{-170}$ &       1 \\
+   HIP 66821 &   B8.5Vn &    13:41:44.77 &   -54:33:33.93 &   5.010 &     12.02 &   $13141 \pm 447$ &  $4.4 \pm 0.14$ &  $3.7^{+0.29}_{-0.24}$ &     $138^{+12}_{-20}$ &       1 \\
+   HIP 67143 &      A0V &    13:45:36.89 &   -26:06:57.63 &   5.805 &     11.49 &   $10338 \pm 351$ &  $4.3 \pm 0.14$ &  $2.3^{+0.11}_{-0.09}$ &    $143^{+112}_{-93}$ &       1 \\
+   HIP 67194 &      A5V &    13:46:13.55 &   +41:05:19.48 &   5.891 &     19.03 &    $7953 \pm 270$ &  $4.3 \pm 0.14$ &  $1.7^{+0.10}_{-0.09}$ &   $504^{+325}_{-319}$ &       1 \\
+   HIP 67782 &     A8IV &    13:53:10.28 &   +28:38:53.28 &   5.911 &     15.21 &    $8051 \pm 274$ &  $4.1 \pm 0.14$ &  $1.8^{+0.16}_{-0.12}$ &   $846^{+121}_{-164}$ &       1 \\
+   HIP 68092 &      A8V &    13:56:27.88 &   +01:03:02.09 &   5.906 &     11.08 &    $7866 \pm 267$ &  $3.9 \pm 0.14$ &  $1.6^{+0.07}_{-0.07}$ &   $410^{+331}_{-274}$ &       1 \\
+   HIP 68520 &      A3V &    14:01:38.79 &   +01:32:40.31 &   4.244 &     14.50 &    $8413 \pm 286$ &  $3.4 \pm 0.14$ &  $2.0^{+0.18}_{-0.14}$ &   $722^{+118}_{-129}$ &       1 \\
+   HIP 70327 &      A0V &    14:23:22.70 &   +08:26:47.84 &   5.120 &     15.17 &    $9678 \pm 329$ &  $4.0 \pm 0.14$ &  $2.2^{+0.12}_{-0.09}$ &   $261^{+133}_{-154}$ &       1 \\
+   HIP 70384 &      A3V &    14:24:00.88 &   +08:14:38.30 &   5.935 &      7.38 &    $9000 \pm 500$ &  $4.0 \pm 0.25$ &  $2.0^{+0.22}_{-0.18}$ &     $99^{+316}_{-87}$ &       2 \\
+   HIP 70400 &      A3V &    14:24:11.34 &   +05:49:12.47 &   5.103 &     20.51 &    $8490 \pm 289$ &  $4.2 \pm 0.14$ &  $1.8^{+0.08}_{-0.07}$ &   $336^{+238}_{-215}$ &       1 \\
+   HIP 70915 &     B8Vn &    14:30:08.63 &   -45:19:16.88 &   5.500 &      6.84 &  $12000 \pm 1000$ &  $4.5 \pm 0.25$ &  $2.8^{+0.42}_{-0.37}$ &      $24^{+65}_{-17}$ &       2 \\
      HR 5476 &      A6V &    14:40:43.94 &   +16:25:03.90 &   5.820 &   \nodata &           \nodata &         \nodata &                \nodata &               \nodata & \nodata \\
-   HIP 71865 &            B3V &    14:41:57.59 &   -37:47:36.59 &   4.000 &      9.62 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 71974 &          B9.5V &    14:43:13.55 &   -24:59:51.91 &   5.730 &      6.56 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 72104 &          A0Vnn &    14:44:59.20 &   -35:11:30.57 &   4.923 &     15.22 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 72154 &          B9.5V &    14:45:30.20 &   +00:43:02.19 &   5.673 &      6.61 &  $10500 \pm 1000$ &  $4.5 \pm 0.25$ &  $2.3^{+0.36}_{-0.33}$ &    $32^{+101}_{-24}$ &  2 \\
-   HIP 72250 &            A1V &    14:46:28.99 &   -47:26:28.02 &   5.740 &     10.67 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 72378 &            B9V &    14:47:57.56 &   -26:38:46.16 &   5.768 &      7.29 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 72552 &            A4V &    14:49:58.40 &   +28:36:57.00 &   5.800 &     10.16 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 73049 &            A0V &    14:55:44.71 &   -33:51:20.82 &   5.318 &     12.85 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-     HR 5605 &            B5V &    15:05:07.18 &   -47:03:04.00 &   4.720 &   \nodata &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 74117 &            B3V &    15:08:50.62 &   -45:16:47.49 &   4.070 &      4.20 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 74689 &            A4V &    15:15:49.08 &   +00:22:19.70 &   5.629 &     21.67 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 75178 &           B9Vn &    15:21:48.58 &   +32:56:01.30 &   5.375 &     12.45 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 75304 &            B4V &    15:23:09.35 &   -36:51:30.55 &   4.540 &      6.28 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 76267 &            A1V &    15:34:41.27 &   +26:42:52.89 &   2.240 &     43.46 &   $10342 \pm 352$ &  $4.0 \pm 0.14$ &  $2.5^{+0.19}_{-0.16}$ &    $314^{+53}_{-94}$ &      1 \\
-   HIP 76600 &          B2.5V &    15:38:39.37 &   -29:46:39.89 &   3.644 &      8.89 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 76852 &            A1V &    15:41:33.05 &   +19:40:13.44 &   4.509 &     17.16 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 77233 &            A3V &    15:46:11.25 &   +15:25:18.59 &   3.670 &     21.03 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 77336 &            A3V &    15:47:17.32 &   +14:06:55.26 &   5.712 &     13.04 &    $8917 \pm 303$ &  $4.0 \pm 0.14$ &  $2.9^{+0.24}_{-0.21}$ &    $404^{+71}_{-71}$ &      1 \\
-   HIP 77516 &            A0V &    15:49:37.21 &   -03:25:48.73 &   3.530 &     19.23 &    $9250 \pm 300$ &  $4.0 \pm 0.25$ &  $2.1^{+0.17}_{-0.16}$ &    $74^{+275}_{-64}$ &  2 \\
-   HIP 77635 &         B1.5Vn &    15:50:58.74 &   -25:45:04.66 &   4.638 &      6.59 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 77858 &            B5V &    15:53:53.92 &   -24:31:59.37 &   5.376 &      7.76 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 78105 &            A3V &    15:56:53.50 &   -33:57:58.01 &   5.080 &     23.60 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 78106 &            B9V &    15:56:54.12 &   -33:57:51.34 &   5.550 &     21.71 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 71865 &      B3V &    14:41:57.59 &   -37:47:36.59 &   4.000 &      9.62 &  $20000 \pm 1000$ &  $4.5 \pm 0.25$ &  $6.6^{+0.66}_{-0.64}$ &         $9^{+9}_{-4}$ &       2 \\
+   HIP 71974 &    B9.5V &    14:43:13.55 &   -24:59:51.91 &   5.730 &      6.56 &   $10000 \pm 500$ &  $4.0 \pm 0.25$ &  $2.3^{+0.26}_{-0.22}$ &     $65^{+210}_{-55}$ &       2 \\
+   HIP 72104 &    A0Vnn &    14:44:59.20 &   -35:11:30.57 &   4.923 &     15.22 &    $9618 \pm 327$ &  $3.8 \pm 0.14$ &  $2.1^{+0.12}_{-0.09}$ &   $239^{+143}_{-144}$ &       1 \\
+   HIP 72154 &    B9.5V &    14:45:30.20 &   +00:43:02.19 &   5.673 &      6.61 &   $10000 \pm 500$ &  $4.0 \pm 0.25$ &  $2.3^{+0.24}_{-0.21}$ &     $75^{+199}_{-65}$ &       2 \\
+   HIP 72250 &      A1V &    14:46:28.99 &   -47:26:28.02 &   5.740 &     10.67 &    $9784 \pm 333$ &  $4.1 \pm 0.14$ &  $2.4^{+0.21}_{-0.18}$ &     $411^{+49}_{-59}$ &       1 \\
+   HIP 72378 &      B9V &    14:47:57.56 &   -26:38:46.16 &   5.768 &      7.29 &   $9500 \pm 1000$ &  $4.0 \pm 0.25$ &  $2.0^{+0.39}_{-0.31}$ &    $103^{+291}_{-91}$ &       2 \\
+   HIP 72552 &      A4V &    14:49:58.40 &   +28:36:57.00 &   5.800 &     10.16 &    $9591 \pm 326$ &  $3.9 \pm 0.14$ &  $2.2^{+0.14}_{-0.11}$ &    $359^{+95}_{-168}$ &       1 \\
+   HIP 73049 &      A0V &    14:55:44.71 &   -33:51:20.82 &   5.318 &     12.85 &   $10108 \pm 344$ &  $4.3 \pm 0.14$ &  $2.4^{+0.18}_{-0.14}$ &    $337^{+53}_{-113}$ &       1 \\
+     HR 5605 &      B5V &    15:05:07.18 &   -47:03:04.00 &   4.720 &   \nodata &  $16000 \pm 1000$ &  $4.5 \pm 0.25$ &  $4.5^{+0.53}_{-0.52}$ &       $14^{+21}_{-8}$ &       2 \\
+   HIP 74117 &      B3V &    15:08:50.62 &   -45:16:47.49 &   4.070 &      4.20 &  $20000 \pm 1000$ &  $4.5 \pm 0.25$ &  $6.6^{+0.67}_{-0.66}$ &         $9^{+9}_{-4}$ &       2 \\
+   HIP 74689 &      A4V &    15:15:49.08 &   +00:22:19.70 &   5.629 &     21.67 &    $8255 \pm 281$ &  $4.4 \pm 0.14$ &  $1.9^{+0.17}_{-0.14}$ &   $780^{+102}_{-113}$ &       1 \\
+   HIP 75178 &     B9Vn &    15:21:48.58 &   +32:56:01.30 &   5.375 &     12.45 &   $12140 \pm 413$ &  $4.3 \pm 0.14$ &  $3.3^{+0.26}_{-0.21}$ &     $184^{+19}_{-28}$ &       1 \\
+   HIP 75304 &      B4V &    15:23:09.35 &   -36:51:30.55 &   4.540 &      6.28 &  $18000 \pm 1000$ &  $4.5 \pm 0.25$ &  $5.4^{+0.58}_{-0.55}$ &       $11^{+13}_{-6}$ &       2 \\
+   HIP 76267 &      A0V &    15:34:41.27 &   +26:42:52.89 &   2.240 &     43.46 &   $10342 \pm 352$ &  $4.0 \pm 0.14$ &  $2.5^{+0.19}_{-0.16}$ &    $313^{+53}_{-100}$ &       1 \\
+   HIP 76600 &    B2.5V &    15:38:39.37 &   -29:46:39.89 &   3.644 &      8.89 &  $20000 \pm 1000$ &  $4.5 \pm 0.25$ &  $6.6^{+0.63}_{-0.65}$ &         $9^{+9}_{-4}$ &       2 \\
+   HIP 76852 &      A1V &    15:41:33.05 &   +19:40:13.44 &   4.509 &     17.16 &    $9366 \pm 318$ &  $4.1 \pm 0.14$ &  $2.0^{+0.09}_{-0.08}$ &   $190^{+162}_{-123}$ &       1 \\
+   HIP 77233 &      A3V &    15:46:11.25 &   +15:25:18.59 &   3.670 &     21.03 &    $8928 \pm 304$ &  $3.3 \pm 0.14$ &  $1.9^{+0.10}_{-0.08}$ &   $332^{+191}_{-201}$ &       1 \\
+   HIP 77336 &      A3V &    15:47:17.32 &   +14:06:55.26 &   5.712 &     13.04 &    $8917 \pm 303$ &  $4.0 \pm 0.14$ &  $2.9^{+0.23}_{-0.21}$ &     $403^{+70}_{-75}$ &       1 \\
+   HIP 77516 &      A0V &    15:49:37.21 &   -03:25:48.73 &   3.530 &     19.23 &   $10000 \pm 500$ &  $4.5 \pm 0.25$ &  $2.2^{+0.21}_{-0.19}$ &     $37^{+113}_{-28}$ &       2 \\
+   HIP 77635 &   B1.5Vn &    15:50:58.74 &   -25:45:04.66 &   4.638 &      6.59 &  $24000 \pm 1000$ &  $4.5 \pm 0.25$ &  $9.0^{+0.60}_{-0.67}$ &         $7^{+4}_{-2}$ &       2 \\
+   HIP 77858 &      B5V &    15:53:53.92 &   -24:31:59.37 &   5.376 &      7.76 &  $16000 \pm 1000$ &  $4.5 \pm 0.25$ &  $4.4^{+0.56}_{-0.49}$ &       $13^{+21}_{-8}$ &       2 \\
+   HIP 78105 &      A3V &    15:56:53.50 &   -33:57:58.01 &   5.080 &     23.60 &    $9206 \pm 313$ &  $4.1 \pm 0.14$ &  $2.0^{+0.12}_{-0.10}$ &   $291^{+173}_{-171}$ &       1 \\
+   HIP 78106 &      B9V &    15:56:54.12 &   -33:57:51.34 &   5.550 &     21.71 &    $9725 \pm 331$ &  $4.2 \pm 0.14$ &  $2.4^{+0.19}_{-0.15}$ &     $412^{+50}_{-83}$ &       1 \\
    HIP 78265 &      B1V &  15:58:51.1132 &  -26:06:50.788 &   2.910 &      5.57 &           \nodata &         \nodata &                \nodata &               \nodata & \nodata \\
-   HIP 78554 &            A3V &    16:02:17.69 &   +22:48:16.03 &   4.817 &     18.22 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 78820 &            B1V &    16:05:26.23 &   -19:48:19.63 &   2.620 &      8.07 &  $24062 \pm 1000$ &  $3.9 \pm 0.25$ &  $9.2^{+0.51}_{-0.64}$ &        $9^{+6}_{-4}$ &  2 \\
+   HIP 78554 &      A3V &    16:02:17.69 &   +22:48:16.03 &   4.817 &     18.22 &    $9226 \pm 314$ &  $4.1 \pm 0.14$ &  $2.1^{+0.15}_{-0.13}$ &    $464^{+88}_{-171}$ &       1 \\
+   HIP 78820 &      B1V &    16:05:26.23 &   -19:48:19.63 &   2.620 &      8.07 &           \nodata &         \nodata &                \nodata &               \nodata & \nodata \\
    HIP 78821 &      B2V &    16:05:26.57 &   -19:48:06.85 &   4.890 &      8.19 &           \nodata &         \nodata &                \nodata &               \nodata & \nodata \\
-     HR 6025 &           A0Vn &  16:06:19.6762 &  +67:48:36.480 &   5.439 &     12.85 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 78918 &         B2.5Vn &    16:06:35.55 &   -36:48:08.26 &   4.205 &      7.87 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+     HR 6025 &     A0Vn &  16:06:19.6762 &  +67:48:36.480 &   5.439 &     12.85 &   $9250 \pm 1000$ &  $4.5 \pm 0.25$ &  $1.9^{+0.32}_{-0.31}$ &     $48^{+210}_{-39}$ &       2 \\
+   HIP 78918 &   B2.5Vn &    16:06:35.55 &   -36:48:08.26 &   4.205 &      7.87 &  $20000 \pm 1000$ &  $4.5 \pm 0.25$ &  $6.6^{+0.68}_{-0.63}$ &         $9^{+9}_{-4}$ &       2 \\
    HIP 78933 &      B1V &  16:06:48.4269 &  -20:40:09.090 &   3.970 &      6.92 &           \nodata &         \nodata &                \nodata &               \nodata & \nodata \\
-   HIP 79005 &            B9V &    16:07:36.42 &   -12:44:43.46 &   5.757 &      8.90 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 79007 &            A7V &    16:07:37.54 &   +09:53:30.27 &   5.639 &     10.10 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 79199 &            B8V &    16:09:52.59 &   -33:32:44.90 &   5.496 &      8.00 &  $12500 \pm 1000$ &  $4.5 \pm 0.25$ &  $3.0^{+0.42}_{-0.39}$ &     $23^{+55}_{-16}$ &  2 \\
-   HIP 79387 &            A4V &    16:12:07.32 &   -08:32:51.28 &   5.435 &     12.92 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 79404 &            B2V &    16:12:18.20 &   -27:55:34.95 &   4.567 &      6.81 &  $21667 \pm 1000$ &  $4.5 \pm 0.25$ &  $7.6^{+0.75}_{-0.69}$ &        $8^{+6}_{-3}$ &  2 \\
-   HIP 79653 &            B8V &    16:15:15.32 &   -47:22:19.27 &   5.124 &      8.46 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 80460 &            A5V &    16:25:24.17 &   +37:23:38.68 &   5.540 &     13.43 &    $7810 \pm 266$ &  $3.7 \pm 0.14$ &  $1.7^{+0.11}_{-0.08}$ &  $779^{+234}_{-402}$ &      1 \\
-   HIP 80815 &            B3V &    16:30:12.48 &   -25:06:54.80 &   4.790 &      7.89 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 80883 &           A1IV &    16:30:54.82 &   +01:59:02.12 &   3.900 &     18.84 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 80991 &            A2V &    16:32:25.68 &   +60:49:23.96 &   5.910 &      8.79 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 79005 &      B9V &    16:07:36.42 &   -12:44:43.46 &   5.757 &      8.90 &   $10000 \pm 500$ &  $3.5 \pm 0.25$ &  $2.8^{+0.46}_{-0.42}$ &    $281^{+84}_{-111}$ &       2 \\
+   HIP 79007 &      A7V &    16:07:37.54 &   +09:53:30.27 &   5.639 &     10.10 &    $7893 \pm 268$ &  $3.9 \pm 0.14$ &  $1.6^{+0.08}_{-0.07}$ &   $463^{+324}_{-301}$ &       1 \\
+   HIP 79199 &      B8V &    16:09:52.59 &   -33:32:44.90 &   5.496 &      8.00 &  $12000 \pm 1000$ &  $4.5 \pm 0.25$ &  $2.8^{+0.40}_{-0.39}$ &      $25^{+65}_{-17}$ &       2 \\
+   HIP 79387 &      A4V &    16:12:07.32 &   -08:32:51.28 &   5.435 &     12.92 &    $8418 \pm 286$ &  $4.0 \pm 0.14$ &  $1.9^{+0.16}_{-0.12}$ &   $694^{+108}_{-181}$ &       1 \\
+   HIP 79404 &      B2V &    16:12:18.20 &   -27:55:34.95 &   4.567 &      6.81 &  $22000 \pm 1000$ &  $4.5 \pm 0.25$ &  $7.8^{+0.71}_{-0.68}$ &         $8^{+6}_{-3}$ &       2 \\
+   HIP 79653 &      B8V &    16:15:15.32 &   -47:22:19.27 &   5.124 &      8.46 &  $14000 \pm 1000$ &  $4.5 \pm 0.25$ &  $3.6^{+0.47}_{-0.44}$ &      $17^{+35}_{-11}$ &       2 \\
+   HIP 80460 &      A5V &    16:25:24.17 &   +37:23:38.68 &   5.540 &     13.43 &    $7810 \pm 266$ &  $3.7 \pm 0.14$ &  $1.7^{+0.11}_{-0.08}$ &   $783^{+229}_{-412}$ &       1 \\
+   HIP 80815 &      B3V &    16:30:12.48 &   -25:06:54.80 &   4.790 &      7.89 &  $22000 \pm 1000$ &  $4.5 \pm 0.25$ &  $7.8^{+0.76}_{-0.71}$ &         $8^{+6}_{-3}$ &       2 \\
+   HIP 80883 &      A0V &    16:30:54.82 &   +01:59:02.12 &   3.900 &     18.84 &    $9000 \pm 500$ &  $4.0 \pm 0.25$ &  $2.0^{+0.22}_{-0.18}$ &     $97^{+294}_{-86}$ &       2 \\
+   HIP 80991 &      A2V &    16:32:25.68 &   +60:49:23.96 &   5.910 &      8.79 &    $9000 \pm 500$ &  $3.5 \pm 0.25$ &  $2.4^{+0.42}_{-0.39}$ &   $405^{+134}_{-176}$ &       2 \\
    HIP 81126 &      B9V &    16:34:06.18 &   +42:26:13.34 &   4.196 &     10.36 &           \nodata &         \nodata &                \nodata &               \nodata & \nodata \\
-   HIP 81641 &            A1V &    16:40:38.69 &   +04:13:11.23 &   5.772 &     11.11 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 82350 &            A1V &    16:49:34.66 &   +13:15:40.10 &   5.910 &      9.99 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 82514 &          B1.5V &  16:51:52.2311 &  -38:02:50.569 &   2.980 &      6.51 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 82673 &            B8V &    16:54:00.47 &   +10:09:55.30 &   4.380 &     13.30 &  $11750 \pm 1000$ &  $3.5 \pm 0.25$ &  $3.4^{+0.65}_{-0.57}$ &    $171^{+73}_{-64}$ &  2 \\
+   HIP 81641 &      A1V &    16:40:38.69 &   +04:13:11.23 &   5.772 &     11.11 &   $10572 \pm 359$ &  $4.1 \pm 0.14$ &  $2.6^{+0.21}_{-0.17}$ &     $301^{+38}_{-66}$ &       1 \\
+   HIP 82350 &      A1V &    16:49:34.66 &   +13:15:40.10 &   5.910 &      9.99 &    $9630 \pm 327$ &  $4.1 \pm 0.14$ &  $2.1^{+0.10}_{-0.08}$ &   $207^{+145}_{-130}$ &       1 \\
+   HIP 82514 &    B1.5V &  16:51:52.2311 &  -38:02:50.569 &   2.980 &      6.51 &  $26000 \pm 1000$ &  $4.5 \pm 0.25$ &  $9.6^{+0.25}_{-0.43}$ &         $5^{+3}_{-1}$ &       2 \\
+   HIP 82673 &      B8V &    16:54:00.47 &   +10:09:55.30 &   4.380 &     13.30 &  $12000 \pm 1000$ &  $3.8 \pm 0.25$ &  $3.1^{+0.58}_{-0.45}$ &     $118^{+82}_{-98}$ &       2 \\
    HIP 83635 &      B1V &    17:05:32.26 &   -00:53:31.45 &   5.610 &      2.92 &           \nodata &         \nodata &                \nodata &               \nodata & \nodata \\
-   HIP 84606 &            A2V &    17:17:40.25 &   +37:17:29.40 &   4.650 &     18.59 &    $9702 \pm 330$ &  $4.0 \pm 0.14$ &  $2.1^{+0.10}_{-0.08}$ &   $155^{+142}_{-99}$ &      1 \\
-   HIP 85290 &           A1Vn &    17:25:41.35 &   +60:02:54.23 &   5.645 &     10.32 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 85379 &            A4V &    17:26:44.24 &   +48:15:36.23 &   5.830 &      8.68 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 84606 &      A2V &    17:17:40.25 &   +37:17:29.40 &   4.650 &     18.59 &    $9702 \pm 330$ &  $4.0 \pm 0.14$ &  $2.1^{+0.10}_{-0.09}$ &   $155^{+137}_{-100}$ &       1 \\
+   HIP 85290 &     A1Vn &    17:25:41.35 &   +60:02:54.23 &   5.645 &     10.32 &   $10989 \pm 374$ &  $4.0 \pm 0.14$ &  $2.5^{+0.12}_{-0.11}$ &     $110^{+88}_{-70}$ &       1 \\
+   HIP 85379 &      A4V &    17:26:44.24 &   +48:15:36.23 &   5.830 &      8.68 &    $8000 \pm 500$ &  $3.5 \pm 0.25$ &  $2.0^{+0.42}_{-0.32}$ &   $621^{+266}_{-320}$ &       2 \\
    HIP 85385 &      B5V &    17:26:49.13 &   +20:04:51.52 &   5.510 &      5.59 &           \nodata &         \nodata &                \nodata &               \nodata & \nodata \\
-   HIP 85537 &           A8Vp &    17:28:49.65 &   +00:19:50.25 &   5.424 &     16.77 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 85727 &           B8Vn &    17:31:05.91 &   -60:41:01.85 &   3.620 &     16.48 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 85922 &            A5V &    17:33:29.85 &   -05:44:41.29 &   5.619 &     20.79 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 85998 &            A2V &    17:34:36.69 &   +09:35:12.12 &   5.810 &      9.66 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 86019 &           B8Vn &    17:34:46.35 &   -11:14:31.19 &   5.537 &      8.11 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 86782 &            A2V &    17:43:59.18 &   +53:48:06.17 &   5.760 &      6.12 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 87108 &            A1V &    17:47:53.56 &   +02:42:26.20 &   3.750 &     31.73 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 88116 &             A0 &    17:59:47.56 &   -23:48:58.09 &   4.731 &      7.85 &    $9750 \pm 300$ &  $3.5 \pm 0.25$ &  $2.7^{+0.43}_{-0.39}$ &   $305^{+68}_{-150}$ &  2 \\
-   HIP 88290 &           A2Vn &    18:01:45.20 &   +01:18:18.28 &   4.439 &     11.15 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 88818 &            A3V &    18:07:49.45 &   +26:06:04.13 &   5.870 &     20.16 &    $9162 \pm 312$ &  $4.3 \pm 0.14$ &  $2.7^{+0.25}_{-0.23}$ &    $441^{+85}_{-70}$ &      1 \\
-   HIP 88817 &            A3V &    18:07:49.50 &   +26:05:50.40 &   5.900 &     25.92 &    $9162 \pm 312$ &  $4.3 \pm 0.14$ &  $2.1^{+0.15}_{-0.12}$ &   $478^{+84}_{-175}$ &      1 \\
-   HIP 89156 &            A3V &    18:11:45.12 &   +33:26:49.41 &   5.970 &      4.21 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 89935 &            A7V &    18:21:01.02 &   +28:52:11.83 &   5.129 &     12.40 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 90052 &            A2V &    18:22:35.32 &   +12:01:46.85 &   5.980 &      7.42 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 90762 &            A2V &    18:31:04.45 &   +16:55:42.80 &   5.760 &      7.49 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 90887 &           A3Vn &    18:32:21.33 &   -39:42:14.40 &   5.162 &     14.23 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 91118 &           A0Vn &    18:35:12.60 &   +18:12:12.28 &   5.790 &      5.04 &    $9500 \pm 300$ &  $4.0 \pm 0.25$ &  $2.1^{+0.19}_{-0.15}$ &    $70^{+244}_{-60}$ &  2 \\
-   HIP 91875 &           A2Vn &    18:43:46.94 &   -38:19:24.39 &   5.120 &     15.89 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 92027 &            A1V &    18:45:28.36 &   +05:30:00.44 &   5.830 &      5.30 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 92312 &            A1V &    18:48:53.39 &   +19:19:43.40 &   5.894 &     11.41 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 92728 &          B2.5V &    18:53:43.56 &   +36:58:18.19 &   5.569 &      3.29 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 92855 &            B2V &    18:55:15.93 &   -26:17:48.21 &   2.058 &     14.32 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 92946 &            A5V &    18:56:13.18 &   +04:12:12.91 &   4.620 &     21.09 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 93225 &            B4V &    18:59:23.80 &   -12:50:25.86 &   5.516 &      6.84 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 93393 &            B5V &    19:01:17.36 &   +26:17:29.08 &   5.683 &      5.02 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 93580 &            A4V &    19:03:32.25 &   +01:49:07.57 &   5.826 &     18.22 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 93713 &           A0Vn &    19:04:55.17 &   +53:23:47.96 &   5.380 &      9.00 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 93747 &          A0Vnn &    19:05:24.61 &   +13:51:48.52 &   2.990 &     39.28 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 93805 &           B9Vn &    19:06:14.94 &   -04:52:57.20 &   3.430 &     26.37 &   $11962 \pm 407$ &  $4.2 \pm 0.14$ &  $3.5^{+0.33}_{-0.26}$ &    $195^{+19}_{-21}$ &      1 \\
-   HIP 94620 &            A4V &    19:15:17.36 &   +21:13:55.62 &   5.654 &     10.89 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 94720 &          B9.5V &    19:16:26.79 &   +14:32:40.62 &   5.630 &      7.96 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 95241 &            B9V &    19:22:38.30 &   -44:27:32.25 &   4.010 &     10.40 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 95560 &            A0V &    19:26:13.25 &   +20:05:51.84 &   5.594 &     13.72 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 95619 &          B8.5V &    19:26:56.48 &   -29:44:35.62 &   5.650 &     14.30 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 95853 &            A5V &    19:29:42.36 &   +51:43:47.21 &   3.769 &     26.88 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 96288 &            A2V &    19:34:41.26 &   +42:24:45.04 &   5.348 &      5.66 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 96840 &            B5V &    19:41:05.53 &   +13:48:56.45 &   5.988 &      0.49 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 97376 &           B8Vn &    19:47:27.78 &   +38:24:27.41 &   5.826 &      6.90 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 97496 &            A3V &    19:48:58.66 &   +19:08:31.35 &   5.000 &     12.79 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 97870 &            B5V &    19:53:17.38 &   +57:31:24.53 &   5.132 &      5.15 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 97966 &           B7Vn &    19:54:37.65 &   -08:13:38.24 &   5.710 &      6.76 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 98055 &           A4Vn &    19:55:37.79 &   +52:26:20.21 &   4.920 &     11.59 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 98194 &            B5V &    19:57:13.87 &   +40:22:04.17 &   5.453 &      2.94 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 98325 &           B9Vn &    19:58:37.98 &   +30:59:01.19 &   5.506 &      7.01 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 99080 &            B3V &    20:06:53.41 &   +23:36:51.93 &   5.064 &      6.47 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-   HIP 99742 &           A1Va &    20:14:16.62 &   +15:11:51.39 &   4.947 &     21.75 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-  HIP 100069 &          B1.5V &    20:18:06.99 &   +40:43:55.50 &   5.840 &      1.68 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-  HIP 100221 &            B9V &    20:19:36.72 &   +62:15:26.90 &   5.712 &      8.63 &    $9750 \pm 300$ &  $4.5 \pm 0.25$ &  $2.2^{+0.15}_{-0.15}$ &    $34^{+110}_{-26}$ &  2 \\
-  HIP 100881 &            B4V &    20:27:19.21 &   -18:12:42.20 &   5.250 &      5.98 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-  HIP 100907 &            A3V &    20:27:34.26 &   +38:26:25.19 &   5.620 &     12.28 &    $9042 \pm 307$ &  $4.0 \pm 0.14$ &  $2.1^{+0.17}_{-0.13}$ &   $512^{+98}_{-169}$ &      1 \\
-  HIP 101123 &            A1V &    20:29:53.91 &   -18:34:59.48 &   5.906 &     15.07 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-  HIP 101589 &            A3V &    20:35:18.54 &   +14:40:27.17 &   4.664 &     14.82 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-  HIP 101716 &            B8V &    20:37:04.67 &   +26:27:43.01 &   5.589 &     10.27 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-  HIP 101867 &            A0V &    20:38:31.34 &   +21:12:04.25 &   4.820 &     14.01 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+   HIP 85537 &     A8Vp &    17:28:49.65 &   +00:19:50.25 &   5.424 &     16.77 &    $7624 \pm 259$ &  $3.8 \pm 0.14$ &  $1.8^{+0.16}_{-0.14}$ &  $1064^{+148}_{-159}$ &       1 \\
+   HIP 85727 &     B8Vn &    17:31:05.91 &   -60:41:01.85 &   3.620 &     16.48 &   $12740 \pm 433$ &  $4.0 \pm 0.14$ &  $3.2^{+0.15}_{-0.13}$ &      $92^{+48}_{-54}$ &       1 \\
+   HIP 85922 &      A5V &    17:33:29.85 &   -05:44:41.29 &   5.619 &     20.79 &    $8000 \pm 500$ &  $4.0 \pm 0.25$ &  $1.7^{+0.19}_{-0.16}$ &   $117^{+539}_{-105}$ &       2 \\
+   HIP 85998 &      A2V &    17:34:36.69 &   +09:35:12.12 &   5.810 &      9.66 &    $9000 \pm 500$ &  $3.5 \pm 0.25$ &  $2.4^{+0.44}_{-0.37}$ &   $399^{+137}_{-200}$ &       2 \\
+   HIP 86019 &     B8Vn &    17:34:46.35 &   -11:14:31.19 &   5.537 &      8.11 &  $12000 \pm 1000$ &  $4.5 \pm 0.25$ &  $2.8^{+0.42}_{-0.37}$ &      $25^{+62}_{-17}$ &       2 \\
+   HIP 86782 &      A2V &    17:43:59.18 &   +53:48:06.17 &   5.760 &      6.12 &   $10000 \pm 500$ &  $4.0 \pm 0.25$ &  $2.3^{+0.25}_{-0.22}$ &     $58^{+207}_{-49}$ &       2 \\
+   HIP 87108 &     A0Vn &    17:47:53.56 &   +02:42:26.20 &   3.750 &     31.73 &   $10075 \pm 343$ &  $4.2 \pm 0.14$ &  $2.3^{+0.15}_{-0.12}$ &   $258^{+101}_{-138}$ &       1 \\
+   HIP 88116 &       A0 &    17:59:47.56 &   -23:48:58.09 &   4.731 &      7.85 &   $10000 \pm 500$ &  $4.0 \pm 0.25$ &  $2.3^{+0.25}_{-0.20}$ &     $76^{+200}_{-66}$ &       2 \\
+   HIP 88290 &     A2Vn &    18:01:45.20 &   +01:18:18.28 &   4.439 &     11.15 &   $10010 \pm 340$ &  $3.8 \pm 0.14$ &  $2.3^{+0.12}_{-0.11}$ &   $243^{+112}_{-140}$ &       1 \\
+   HIP 88818 &      A3V &    18:07:49.45 &   +26:06:04.13 &   5.870 &     20.16 &    $9162 \pm 312$ &  $4.3 \pm 0.14$ &  $2.7^{+0.24}_{-0.23}$ &     $442^{+86}_{-70}$ &       1 \\
+   HIP 88817 &      A3V &    18:07:49.50 &   +26:05:50.40 &   5.900 &     25.92 &    $9162 \pm 312$ &  $4.3 \pm 0.14$ &  $2.1^{+0.15}_{-0.12}$ &    $481^{+83}_{-173}$ &       1 \\
+   HIP 89156 &      A3V &    18:11:45.12 &   +33:26:49.41 &   5.970 &      4.21 &    $9000 \pm 500$ &  $3.5 \pm 0.25$ &  $2.4^{+0.42}_{-0.39}$ &   $410^{+135}_{-157}$ &       2 \\
+   HIP 89935 &      A7V &    18:21:01.02 &   +28:52:11.83 &   5.129 &     12.40 &    $7594 \pm 258$ &  $3.4 \pm 0.14$ &  $2.3^{+0.10}_{-0.13}$ &    $727^{+108}_{-70}$ &       1 \\
+   HIP 90052 &      A2V &    18:22:35.32 &   +12:01:46.85 &   5.980 &      7.42 &    $9000 \pm 500$ &  $3.5 \pm 0.25$ &  $2.4^{+0.43}_{-0.40}$ &   $404^{+138}_{-175}$ &       2 \\
+   HIP 90762 &      A2V &    18:31:04.45 &   +16:55:42.80 &   5.760 &      7.49 &   $8750 \pm 1000$ &  $3.5 \pm 0.25$ &  $2.2^{+0.54}_{-0.46}$ &   $482^{+375}_{-247}$ &       2 \\
+   HIP 90887 &     A3Vn &    18:32:21.33 &   -39:42:14.40 &   5.162 &     14.23 &    $9403 \pm 320$ &  $4.1 \pm 0.14$ &  $2.1^{+0.14}_{-0.12}$ &   $335^{+143}_{-187}$ &       1 \\
+   HIP 91118 &     A0Vn &    18:35:12.60 &   +18:12:12.28 &   5.790 &      5.04 &   $9500 \pm 1000$ &  $4.0 \pm 0.25$ &  $2.1^{+0.39}_{-0.32}$ &    $111^{+276}_{-98}$ &       2 \\
+   HIP 91875 &     A2Vn &    18:43:46.94 &   -38:19:24.39 &   5.120 &     15.89 &    $9287 \pm 316$ &  $4.0 \pm 0.14$ &  $2.1^{+0.12}_{-0.10}$ &   $339^{+145}_{-189}$ &       1 \\
+   HIP 92027 &      A1V &    18:45:28.36 &   +05:30:00.44 &   5.830 &      5.30 &    $9000 \pm 500$ &  $3.5 \pm 0.25$ &  $2.4^{+0.43}_{-0.37}$ &   $406^{+140}_{-167}$ &       2 \\
+   HIP 92312 &      A1V &    18:48:53.39 &   +19:19:43.40 &   5.894 &     11.41 &    $9923 \pm 337$ &  $4.2 \pm 0.14$ &  $2.2^{+0.10}_{-0.09}$ &   $164^{+128}_{-105}$ &       1 \\
+   HIP 92728 &    B2.5V &    18:53:43.56 &   +36:58:18.19 &   5.569 &      3.29 &  $20000 \pm 1000$ &  $4.5 \pm 0.25$ &  $6.6^{+0.68}_{-0.61}$ &         $9^{+9}_{-4}$ &       2 \\
+   HIP 92855 &      B2V &    18:55:15.93 &   -26:17:48.21 &   2.058 &     14.32 &   $19192 \pm 653$ &  $4.3 \pm 0.14$ &  $6.3^{+0.38}_{-0.28}$ &       $29^{+6}_{-12}$ &       1 \\
+   HIP 92946 &      A5V &    18:56:13.18 &   +04:12:12.91 &   4.620 &     21.09 &    $7968 \pm 271$ &  $4.1 \pm 0.14$ &  $1.6^{+0.19}_{-0.23}$ &   $658^{+683}_{-409}$ &       1 \\
+   HIP 93225 &      B4V &    18:59:23.80 &   -12:50:25.86 &   5.516 &      6.84 &  $15000 \pm 1000$ &  $3.8 \pm 0.25$ &  $4.4^{+0.71}_{-0.55}$ &      $54^{+34}_{-42}$ &       2 \\
+   HIP 93393 &      B5V &    19:01:17.36 &   +26:17:29.08 &   5.683 &      5.02 &  $18000 \pm 1000$ &  $4.5 \pm 0.25$ &  $5.4^{+0.60}_{-0.55}$ &       $11^{+13}_{-5}$ &       2 \\
+   HIP 93580 &      A4V &    19:03:32.25 &   +01:49:07.57 &   5.826 &     18.22 &    $8224 \pm 280$ &  $4.3 \pm 0.14$ &  $1.8^{+0.12}_{-0.10}$ &   $590^{+236}_{-315}$ &       1 \\
+   HIP 93713 &     A0Vn &    19:04:55.17 &   +53:23:47.96 &   5.380 &      9.00 &   $9000 \pm 1000$ &  $4.0 \pm 0.25$ &  $1.9^{+0.36}_{-0.31}$ &   $129^{+363}_{-115}$ &       2 \\
+   HIP 93747 &     A0Vn &    19:05:24.61 &   +13:51:48.52 &   2.990 &     39.28 &   $11409 \pm 388$ &  $4.2 \pm 0.14$ &  $3.3^{+0.29}_{-0.25}$ &     $231^{+23}_{-26}$ &       1 \\
+   HIP 93805 &     B9Vn &    19:06:14.94 &   -04:52:57.20 &   3.430 &     26.37 &   $11962 \pm 407$ &  $4.2 \pm 0.14$ &  $3.5^{+0.33}_{-0.27}$ &     $194^{+20}_{-22}$ &       1 \\
+   HIP 94620 &      A4V &    19:15:17.36 &   +21:13:55.62 &   5.654 &     10.89 &    $9190 \pm 312$ &  $4.0 \pm 0.14$ &  $2.0^{+0.09}_{-0.07}$ &   $202^{+169}_{-130}$ &       1 \\
+   HIP 94720 &    B9.5V &    19:16:26.79 &   +14:32:40.62 &   5.630 &      7.96 &   $10000 \pm 500$ &  $4.0 \pm 0.25$ &  $2.3^{+0.25}_{-0.20}$ &     $69^{+194}_{-58}$ &       2 \\
+   HIP 95241 &      B9V &    19:22:38.30 &   -44:27:32.25 &   4.010 &     10.40 &  $12000 \pm 1000$ &  $4.0 \pm 0.25$ &  $2.9^{+0.50}_{-0.41}$ &     $53^{+108}_{-43}$ &       2 \\
+   HIP 95560 &      A0V &    19:26:13.25 &   +20:05:51.84 &   5.594 &     13.72 &   $9250 \pm 1000$ &  $4.5 \pm 0.25$ &  $1.9^{+0.32}_{-0.29}$ &     $45^{+197}_{-37}$ &       2 \\
+   HIP 95619 &    B8.5V &    19:26:56.48 &   -29:44:35.62 &   5.650 &     14.30 &   $11997 \pm 408$ &  $4.3 \pm 0.14$ &  $2.9^{+0.15}_{-0.12}$ &     $107^{+60}_{-63}$ &       1 \\
+   HIP 95853 &      A5V &    19:29:42.36 &   +51:43:47.21 &   3.769 &     26.88 &    $8216 \pm 279$ &  $3.9 \pm 0.14$ &  $1.8^{+0.14}_{-0.11}$ &   $693^{+186}_{-300}$ &       1 \\
+   HIP 96288 &      A2V &    19:34:41.26 &   +42:24:45.04 &   5.348 &      5.66 &    $9000 \pm 500$ &  $3.5 \pm 0.25$ &  $2.4^{+0.43}_{-0.39}$ &   $405^{+137}_{-166}$ &       2 \\
+   HIP 96840 &      B5V &    19:41:05.53 &   +13:48:56.45 &   5.988 &      0.49 &  $16000 \pm 1000$ &  $4.0 \pm 0.25$ &  $4.7^{+0.62}_{-0.56}$ &      $26^{+31}_{-18}$ &       2 \\
+   HIP 97376 &     B8Vn &    19:47:27.78 &   +38:24:27.41 &   5.826 &      6.90 &  $11500 \pm 2000$ &  $4.5 \pm 0.25$ &  $2.2^{+0.73}_{-0.70}$ &     $34^{+157}_{-26}$ &       2 \\
+   HIP 97496 &      A3V &    19:48:58.66 &   +19:08:31.35 &   5.000 &     12.79 &    $8422 \pm 286$ &  $3.9 \pm 0.14$ &  $1.8^{+0.09}_{-0.07}$ &   $435^{+227}_{-265}$ &       1 \\
+   HIP 97870 &      B5V &    19:53:17.38 &   +57:31:24.53 &   5.132 &      5.15 &  $16000 \pm 1000$ &  $4.0 \pm 0.25$ &  $4.7^{+0.64}_{-0.53}$ &      $26^{+32}_{-19}$ &       2 \\
+   HIP 97966 &     B7Vn &    19:54:37.65 &   -08:13:38.24 &   5.710 &      6.76 &  $14000 \pm 1000$ &  $4.2 \pm 0.25$ &  $3.6^{+0.47}_{-0.46}$ &      $24^{+45}_{-16}$ &       2 \\
+   HIP 98055 &     A4Vn &    19:55:37.79 &   +52:26:20.21 &   4.920 &     11.59 &    $9000 \pm 500$ &  $4.5 \pm 0.25$ &  $1.9^{+0.18}_{-0.17}$ &     $47^{+186}_{-38}$ &       2 \\
+   HIP 98194 &      B5V &    19:57:13.87 &   +40:22:04.17 &   5.453 &      2.94 &  $16000 \pm 1000$ &  $4.0 \pm 0.25$ &  $4.7^{+0.59}_{-0.54}$ &      $27^{+31}_{-19}$ &       2 \\
+   HIP 98325 &     B9Vn &    19:58:37.98 &   +30:59:01.19 &   5.506 &      7.01 &  $12000 \pm 1000$ &  $4.5 \pm 0.25$ &  $2.8^{+0.41}_{-0.37}$ &      $25^{+65}_{-17}$ &       2 \\
+   HIP 99080 &      B3V &    20:06:53.41 &   +23:36:51.93 &   5.064 &      6.47 &  $20000 \pm 1000$ &  $4.5 \pm 0.25$ &  $6.6^{+0.68}_{-0.64}$ &         $9^{+9}_{-4}$ &       2 \\
+   HIP 99742 &     A1Va &    20:14:16.62 &   +15:11:51.39 &   4.947 &     21.75 &    $9645 \pm 328$ &  $4.3 \pm 0.14$ &  $2.3^{+0.17}_{-0.14}$ &    $412^{+59}_{-116}$ &       1 \\
+  HIP 100069 &      B0V &    20:18:06.99 &   +40:43:55.50 &   5.840 &      1.68 &           \nodata &         \nodata &                \nodata &               \nodata & \nodata \\
+  HIP 100221 &      B9V &    20:19:36.72 &   +62:15:26.90 &   5.712 &      8.63 &   $10000 \pm 500$ &  $4.0 \pm 0.25$ &  $2.3^{+0.25}_{-0.21}$ &     $70^{+205}_{-60}$ &       2 \\
+  HIP 100881 &      B4V &    20:27:19.21 &   -18:12:42.20 &   5.250 &      5.98 &  $14000 \pm 1000$ &  $4.5 \pm 0.25$ &  $3.6^{+0.48}_{-0.45}$ &      $17^{+34}_{-10}$ &       2 \\
+  HIP 100907 &      A3V &    20:27:34.26 &   +38:26:25.19 &   5.620 &     12.28 &    $9042 \pm 307$ &  $4.0 \pm 0.14$ &  $2.1^{+0.16}_{-0.13}$ &    $514^{+99}_{-166}$ &       1 \\
+  HIP 101123 &      A1V &    20:29:53.91 &   -18:34:59.48 &   5.906 &     15.07 &   $10492 \pm 357$ &  $4.2 \pm 0.14$ &  $2.4^{+0.11}_{-0.09}$ &    $143^{+109}_{-91}$ &       1 \\
+  HIP 101589 &      A3V &    20:35:18.54 &   +14:40:27.17 &   4.664 &     14.82 &    $8639 \pm 294$ &  $3.8 \pm 0.14$ &  $2.0^{+0.15}_{-0.12}$ &    $624^{+98}_{-176}$ &       1 \\
+  HIP 101716 &      B8V &    20:37:04.67 &   +26:27:43.01 &   5.589 &     10.27 &   $12949 \pm 440$ &  $4.2 \pm 0.14$ &  $3.3^{+0.17}_{-0.14}$ &      $91^{+44}_{-53}$ &       1 \\
+  HIP 101867 &      A0V &    20:38:31.34 &   +21:12:04.25 &   4.820 &     14.01 &   $10507 \pm 357$ &  $4.2 \pm 0.14$ &  $3.4^{+0.24}_{-0.30}$ &     $252^{+45}_{-33}$ &       1 \\
   HIP 101909 &      B3V &    20:39:04.97 &   +15:50:17.52 &   5.980 &      2.42 &           \nodata &         \nodata &                \nodata &               \nodata & \nodata \\
-  HIP 102487 &            A1V &    20:46:09.99 &   -21:30:50.52 &   5.913 &     12.37 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-  HIP 103298 &            A5V &    20:55:38.57 &   +12:34:06.81 &   5.540 &     16.53 &    $9093 \pm 309$ &  $4.1 \pm 0.14$ &  $2.0^{+0.13}_{-0.11}$ &  $393^{+151}_{-208}$ &      1 \\
-  HIP 104019 &            A5V &    21:04:24.30 &   -19:51:17.97 &   4.840 &     20.20 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-  HIP 104105 &           B8Vn &    21:05:29.27 &   +78:07:35.02 &   5.915 &      8.10 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-  HIP 104139 &            A1V &    21:05:56.83 &   -17:13:58.30 &   4.070 &     20.11 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-  HIP 104365 &            A0V &    21:08:33.63 &   -21:11:37.22 &   5.280 &     18.14 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-  HIP 105140 &            A1V &    21:17:56.28 &   -32:10:21.15 &   4.721 &     17.90 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-  HIP 105282 &            B6V &    21:19:28.75 &   +49:30:37.06 &   5.740 &      5.98 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-  HIP 105891 &            B6V &    21:26:44.97 &   +52:53:54.73 &   5.989 &      7.28 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-  HIP 105942 &            B3V &    21:27:21.37 &   +37:07:00.47 &   5.289 &      2.50 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-  HIP 105966 &            A1V &    21:27:40.06 &   +27:36:30.94 &   5.389 &     17.14 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-  HIP 105972 &            B7V &    21:27:46.14 &   +66:48:32.74 &   5.407 &      4.05 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-  HIP 106711 &           A3Vn &    21:36:56.98 &   +40:24:48.67 &   5.052 &     15.19 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-  HIP 106786 &            A7V &    21:37:45.11 &   -07:51:15.13 &   4.690 &     18.26 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-  HIP 107517 &            A1V &    21:46:32.10 &   -11:21:57.44 &   5.570 &     11.58 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-  HIP 107608 &            A2V &    21:47:44.15 &   -30:53:53.90 &   5.016 &     10.16 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-  HIP 108294 &           A2Vn &    21:56:22.77 &   -37:15:13.16 &   5.457 &      9.71 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-  HIP 108339 &          A2Vnn &    21:56:56.37 &   +12:04:35.37 &   5.544 &      8.14 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-  HIP 109056 &           B9Vn &    22:05:34.67 &   +28:57:50.32 &   5.700 &      9.40 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-  HIP 109139 &            B8V &    22:06:26.23 &   -13:52:10.86 &   4.270 &     18.62 &   $12641 \pm 430$ &  $4.3 \pm 0.14$ &  $3.2^{+0.19}_{-0.17}$ &    $122^{+38}_{-60}$ &      1 \\
-  HIP 109521 &            A5V &    22:11:09.89 &   +50:49:24.26 &   5.386 &     17.81 &    $8420 \pm 286$ &  $4.2 \pm 0.14$ &  $2.0^{+0.19}_{-0.16}$ &  $728^{+107}_{-105}$ &      1 \\
-  HIP 109831 &          A2Vnn &    22:14:44.37 &   +42:57:14.07 &   5.720 &     12.14 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-  HIP 110838 &           B9Vn &    22:27:19.97 &   -64:57:58.88 &   4.495 &     13.00 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-  HIP 110935 &            A4V &    22:28:37.67 &   -67:29:20.62 &   5.570 &     23.19 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-  HIP 111056 &            A3V &    22:29:52.98 &   +78:49:27.43 &   5.460 &     13.31 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-  HIP 111068 &          B9.5V &    22:30:01.81 &   +32:34:21.50 &   5.650 &      9.05 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-  HIP 111169 &            A1V &    22:31:17.50 &   +50:16:56.97 &   3.770 &     31.79 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+  HIP 102487 &      A1V &    20:46:09.99 &   -21:30:50.52 &   5.913 &     12.37 &    $9702 \pm 330$ &  $4.1 \pm 0.14$ &  $2.1^{+0.11}_{-0.09}$ &   $180^{+143}_{-116}$ &       1 \\
+  HIP 103298 &      A5V &    20:55:38.57 &   +12:34:06.81 &   5.540 &     16.53 &    $9093 \pm 309$ &  $4.1 \pm 0.14$ &  $2.0^{+0.13}_{-0.11}$ &   $400^{+150}_{-215}$ &       1 \\
+  HIP 104019 &      A5V &    21:04:24.30 &   -19:51:17.97 &   4.840 &     20.20 &    $8319 \pm 283$ &  $4.2 \pm 0.14$ &  $1.8^{+0.09}_{-0.07}$ &   $452^{+245}_{-273}$ &       1 \\
+  HIP 104105 &     B8Vn &    21:05:29.27 &   +78:07:35.02 &   5.915 &      8.10 &   $9750 \pm 1000$ &  $4.0 \pm 0.25$ &  $2.1^{+0.39}_{-0.32}$ &     $92^{+255}_{-80}$ &       2 \\
+  HIP 104139 &      A1V &    21:05:56.83 &   -17:13:58.30 &   4.070 &     20.11 &   $10001 \pm 340$ &  $4.2 \pm 0.14$ &  $2.2^{+0.11}_{-0.09}$ &   $187^{+130}_{-116}$ &       1 \\
+  HIP 104365 &      A0V &    21:08:33.63 &   -21:11:37.22 &   5.280 &     18.14 &   $10878 \pm 370$ &  $4.3 \pm 0.14$ &  $2.8^{+0.21}_{-0.17}$ &     $272^{+33}_{-53}$ &       1 \\
+  HIP 105140 &      A1V &    21:17:56.28 &   -32:10:21.15 &   4.721 &     17.90 &    $9126 \pm 310$ &  $4.4 \pm 0.14$ &  $2.3^{+0.21}_{-0.18}$ &     $538^{+69}_{-70}$ &       1 \\
+  HIP 105282 &      B6V &    21:19:28.75 &   +49:30:37.06 &   5.740 &      5.98 &  $16000 \pm 1000$ &  $4.5 \pm 0.25$ &  $4.5^{+0.53}_{-0.51}$ &       $13^{+21}_{-7}$ &       2 \\
+  HIP 105891 &      B6V &    21:26:44.97 &   +52:53:54.73 &   5.989 &      7.28 &  $10500 \pm 2000$ &  $4.0 \pm 0.25$ &  $2.1^{+0.71}_{-0.58}$ &    $102^{+404}_{-89}$ &       2 \\
+  HIP 105942 &      B3V &    21:27:21.37 &   +37:07:00.47 &   5.289 &      2.50 &  $20000 \pm 1000$ &  $4.5 \pm 0.25$ &  $6.6^{+0.69}_{-0.64}$ &         $9^{+9}_{-4}$ &       2 \\
+  HIP 105966 &      A1V &    21:27:40.06 &   +27:36:30.94 &   5.389 &     17.14 &    $9622 \pm 327$ &  $4.3 \pm 0.14$ &  $2.1^{+0.12}_{-0.10}$ &   $263^{+138}_{-156}$ &       1 \\
+  HIP 105972 &      B7V &    21:27:46.14 &   +66:48:32.74 &   5.407 &      4.05 &  $14000 \pm 1000$ &  $4.0 \pm 0.25$ &  $3.8^{+0.53}_{-0.48}$ &      $38^{+54}_{-29}$ &       2 \\
+  HIP 106711 &     A3Vn &    21:36:56.98 &   +40:24:48.67 &   5.052 &     15.19 &    $7859 \pm 267$ &  $3.9 \pm 0.14$ &  $1.7^{+0.11}_{-0.08}$ &   $767^{+226}_{-387}$ &       1 \\
+  HIP 106786 &      A7V &    21:37:45.11 &   -07:51:15.13 &   4.690 &     18.26 &    $8140 \pm 277$ &  $4.0 \pm 0.14$ &  $1.7^{+0.10}_{-0.07}$ &   $567^{+239}_{-326}$ &       1 \\
+  HIP 107517 &      A1V &    21:46:32.10 &   -11:21:57.44 &   5.570 &     11.58 &   $10674 \pm 363$ &  $4.2 \pm 0.14$ &  $2.5^{+0.14}_{-0.11}$ &    $191^{+89}_{-108}$ &       1 \\
+  HIP 107608 &      A2V &    21:47:44.15 &   -30:53:53.90 &   5.016 &     10.16 &    $9716 \pm 330$ &  $4.0 \pm 0.14$ &  $2.2^{+0.15}_{-0.12}$ &    $342^{+93}_{-161}$ &       1 \\
+  HIP 108294 &     A2Vn &    21:56:22.77 &   -37:15:13.16 &   5.457 &      9.71 &    $9000 \pm 500$ &  $4.0 \pm 0.25$ &  $2.0^{+0.22}_{-0.18}$ &     $93^{+318}_{-81}$ &       2 \\
+  HIP 108339 &    A2Vnn &    21:56:56.37 &   +12:04:35.37 &   5.544 &      8.14 &   $9250 \pm 1000$ &  $4.0 \pm 0.25$ &  $2.0^{+0.35}_{-0.31}$ &   $121^{+316}_{-109}$ &       2 \\
+  HIP 109056 &     B9Vn &    22:05:34.67 &   +28:57:50.32 &   5.700 &      9.40 &   $9800 \pm 1200$ &  $4.4 \pm 0.25$ &  $2.0^{+0.41}_{-0.36}$ &     $51^{+200}_{-42}$ &       2 \\
+  HIP 109139 &      B8V &    22:06:26.23 &   -13:52:10.86 &   4.270 &     18.62 &   $12641 \pm 430$ &  $4.3 \pm 0.14$ &  $3.2^{+0.20}_{-0.16}$ &     $124^{+37}_{-62}$ &       1 \\
+  HIP 109521 &      A5V &    22:11:09.89 &   +50:49:24.26 &   5.386 &     17.81 &    $8420 \pm 286$ &  $4.2 \pm 0.14$ &  $2.0^{+0.19}_{-0.16}$ &   $728^{+107}_{-106}$ &       1 \\
+  HIP 109831 &    A2Vnn &    22:14:44.37 &   +42:57:14.07 &   5.720 &     12.14 &   $10932 \pm 372$ &  $4.2 \pm 0.14$ &  $2.5^{+0.13}_{-0.12}$ &     $123^{+92}_{-79}$ &       1 \\
+  HIP 110838 &     B9Vn &    22:27:19.97 &   -64:57:58.88 &   4.495 &     13.00 &   $11271 \pm 383$ &  $4.1 \pm 0.14$ &  $3.0^{+0.24}_{-0.20}$ &     $243^{+24}_{-33}$ &       1 \\
+  HIP 110935 &      A4V &    22:28:37.67 &   -67:29:20.62 &   5.570 &     23.19 &    $8026 \pm 273$ &  $4.3 \pm 0.14$ &  $1.7^{+0.08}_{-0.07}$ &   $447^{+301}_{-291}$ &       1 \\
+  HIP 111056 &      A3V &    22:29:52.98 &   +78:49:27.43 &   5.460 &     13.31 &   $8750 \pm 1000$ &  $4.2 \pm 0.25$ &  $1.8^{+0.33}_{-0.30}$ &     $85^{+347}_{-74}$ &       2 \\
+  HIP 111068 &    B9.5V &    22:30:01.81 &   +32:34:21.50 &   5.650 &      9.05 &   $10000 \pm 500$ &  $3.5 \pm 0.25$ &  $2.8^{+0.47}_{-0.42}$ &    $280^{+85}_{-112}$ &       2 \\
+  HIP 111169 &      A1V &    22:31:17.50 &   +50:16:56.97 &   3.770 &     31.79 &   $10071 \pm 342$ &  $4.3 \pm 0.14$ &  $2.3^{+0.12}_{-0.10}$ &   $202^{+123}_{-123}$ &       1 \\
   HIP 111841 &      O9V &    22:39:15.68 &   +39:03:00.97 &   4.880 &      1.89 &           \nodata &         \nodata &                \nodata &               \nodata & \nodata \\
-  HIP 112029 &            B8V &    22:41:27.73 &   +10:49:52.64 &   3.410 &   \nodata &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-  HIP 113788 &            A1V &    23:02:36.38 &   +42:45:28.06 & \nodata &      7.74 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-  HIP 114520 &           A5Vn &    23:11:44.19 &   +08:43:12.40 &   5.157 &     13.46 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-  HIP 114822 &            A2V &    23:15:34.26 &   -03:29:46.96 &   5.550 &     14.04 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-  HIP 115115 &            A0V &    23:18:57.68 &   -09:36:38.70 &   5.001 &     12.47 &   $10671 \pm 363$ &  $4.2 \pm 0.14$ &  $2.6^{+0.19}_{-0.16}$ &    $285^{+39}_{-80}$ &      1 \\
-  HIP 116247 &            A0V &    23:33:16.62 &   -20:54:52.21 &   4.709 &     11.11 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-  HIP 116582 &            B8V &    23:37:32.04 &   +44:25:44.37 &   5.817 &      4.04 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-  HIP 116611 &           A0Vn &    23:37:56.80 &   +18:24:02.40 &   5.482 &     14.01 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-  HIP 116631 &            B8V &    23:38:08.20 &   +43:16:05.06 &   4.290 &      6.53 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-  HIP 116805 &            A0V &    23:40:24.51 &   +44:20:02.16 &   4.140 &     19.37 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-  HIP 116971 &            B9V &    23:42:43.34 &   -14:32:41.65 &   4.483 &     21.96 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-  HIP 117089 &            B9V &    23:44:12.08 &   -18:16:36.97 &   5.235 &      8.61 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-  HIP 117371 &           A1Vn &    23:47:54.77 &   +67:48:24.51 &   5.048 &     10.76 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-  HIP 117452 &          A0Vnp &    23:48:55.55 &   -28:07:48.97 &   4.570 &     23.73 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
-  HIP 118121 &            A1V &    23:57:35.08 &   -64:17:53.63 &   5.002 &     21.08 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
+  HIP 112029 &      B8V &    22:41:27.73 &   +10:49:52.64 &   3.410 &   \nodata &   $11913 \pm 405$ &  $3.8 \pm 0.14$ &  $2.9^{+0.17}_{-0.14}$ &     $135^{+57}_{-76}$ &       1 \\
+  HIP 113788 &      A1V &    23:02:36.38 &   +42:45:28.06 & \nodata &      7.74 &    $9000 \pm 500$ &  $4.0 \pm 0.25$ &  $2.0^{+0.22}_{-0.18}$ &    $100^{+309}_{-88}$ &       2 \\
+  HIP 114520 &     A5Vn &    23:11:44.19 &   +08:43:12.40 &   5.157 &     13.46 &    $8220 \pm 279$ &  $3.8 \pm 0.14$ &  $1.7^{+0.10}_{-0.08}$ &   $437^{+277}_{-270}$ &       1 \\
+  HIP 114822 &      A2V &    23:15:34.26 &   -03:29:46.96 &   5.550 &     14.04 &    $9678 \pm 329$ &  $4.1 \pm 0.14$ &  $2.2^{+0.12}_{-0.10}$ &   $255^{+136}_{-153}$ &       1 \\
+  HIP 115115 &      A0V &    23:18:57.68 &   -09:36:38.70 &   5.001 &     12.47 &   $10671 \pm 363$ &  $4.2 \pm 0.14$ &  $2.6^{+0.20}_{-0.16}$ &     $284^{+38}_{-79}$ &       1 \\
+  HIP 116247 &      A0V &    23:33:16.62 &   -20:54:52.21 &   4.709 &     11.11 &   $10267 \pm 349$ &  $3.9 \pm 0.14$ &  $2.5^{+0.20}_{-0.16}$ &     $334^{+46}_{-78}$ &       1 \\
+  HIP 116582 &      B8V &    23:37:32.04 &   +44:25:44.37 &   5.817 &      4.04 &  $12000 \pm 1000$ &  $4.0 \pm 0.25$ &  $2.9^{+0.46}_{-0.43}$ &     $54^{+104}_{-44}$ &       2 \\
+  HIP 116611 &     A0Vn &    23:37:56.80 &   +18:24:02.40 &   5.482 &     14.01 &   $11060 \pm 376$ &  $4.1 \pm 0.14$ &  $2.7^{+0.19}_{-0.15}$ &     $228^{+46}_{-92}$ &       1 \\
+  HIP 116631 &      B8V &    23:38:08.20 &   +43:16:05.06 &   4.290 &      6.53 &  $12000 \pm 1000$ &  $3.8 \pm 0.25$ &  $3.1^{+0.55}_{-0.48}$ &     $116^{+82}_{-96}$ &       2 \\
+  HIP 116805 &      A0V &    23:40:24.51 &   +44:20:02.16 &   4.140 &     19.37 &   $11903 \pm 405$ &  $4.3 \pm 0.14$ &  $2.9^{+0.17}_{-0.14}$ &     $145^{+51}_{-74}$ &       1 \\
+  HIP 116971 &      B9V &    23:42:43.34 &   -14:32:41.65 &   4.483 &     21.96 &   $11108 \pm 378$ &  $4.3 \pm 0.14$ &  $2.6^{+0.15}_{-0.14}$ &     $109^{+90}_{-70}$ &       1 \\
+  HIP 117089 &      B9V &    23:44:12.08 &   -18:16:36.97 &   5.235 &      8.61 &  $12000 \pm 1000$ &  $4.5 \pm 0.25$ &  $2.8^{+0.40}_{-0.37}$ &      $24^{+63}_{-17}$ &       2 \\
+  HIP 117371 &     A1Vn &    23:47:54.77 &   +67:48:24.51 &   5.048 &     10.76 &   $10308 \pm 350$ &  $3.9 \pm 0.14$ &  $2.5^{+0.19}_{-0.17}$ &     $323^{+53}_{-92}$ &       1 \\
+  HIP 117452 &     A0Vn &    23:48:55.55 &   -28:07:48.97 &   4.570 &     23.73 &   $11417 \pm 388$ &  $4.3 \pm 0.14$ &  $3.0^{+0.26}_{-0.22}$ &     $233^{+32}_{-37}$ &       1 \\
+  HIP 118121 &      A1V &    23:57:35.08 &   -64:17:53.63 &   5.002 &     21.08 &    $9979 \pm 339$ &  $4.3 \pm 0.14$ &  $2.3^{+0.16}_{-0.13}$ &    $335^{+70}_{-134}$ &       1 \\
   HIP 118243 &      B1V &    23:59:00.54 &   +55:45:17.74 &   4.997 &      0.72 &           \nodata &         \nodata &                \nodata &               \nodata & \nodata
@@
    HIP 2548 & Aa,Ab &     2 & yes &  $5732 \pm 112$ &      30 &    -0.5  &  $1.0^{+0.06}_{-0.04}$ &  $1.0^{+0.04}_{-0.03}$ \\
-   HIP 5310 & AB &     1 & yes &  $3343 \pm 154$ &      30 &     0.0  &  $0.3^{+0.13}_{-0.08}$ &  $0.4^{+0.12}_{-0.12}$ \\
+   HIP 5348 & AB &     1 & no &  $12000 \pm 1000$ &     75 &     0.0 &  $2.9^{+0.40}_{-0.36}$ &  $3.3^{+0.23}_{-0.29}$ \\
      HR 545 & Aa,Ab$^{\dagger}$ &     3 & yes &   $4312 \pm 87$ &       5 &    -0.5  &  $0.8^{+0.11}_{-0.10}$ &  $0.7^{+0.01}_{-0.02}$ \\
@@
   HIP 13327 & AB$^{\dagger}$ &     1 & yes &  $5524 \pm 150$ &       5 &    -0.5  &  $1.2^{+0.20}_{-0.21}$ &  $1.0^{+0.03}_{-0.04}$ \\
+  HIP 14043 & Aa,Ab$^{\dagger}$ &     1 & yes &  $11500 \pm 500$ &       20 &    0.5  &  $2.6^{+0.36}_{-0.29}$ &  $3.3^{+0.15}_{-0.67}$ \\
   HIP 14576 & Aa,Ab &     2 & no &  $6980 \pm 103$ &      10 &     0.0  &  $1.4^{+0.03}_{-0.03}$ &  $1.5^{+0.05}_{-0.03}$ \\
   HIP 14764 & AB$^{\dagger}$ &     2 & yes &  $5623 \pm 150$ &      5 &     -0.5 &    $1.0^{+0.32}_{-0.07}$ &  $1.0^{+0.03}_{-0.04}$ \\
+  HIP 16147 & AB &     1 & yes &  $13000 \pm 1000$ &      1 &     0.0 &  $3.1^{+0.38}_{-0.36}$ &  $3.6^{+0.34}_{-0.23}$ \\
   HIP 16244 & AB &     2 & yes &  $5592 \pm 107$ &       5 &    -0.5  &  $1.2^{+0.20}_{-0.22}$ &  $1.0^{+0.03}_{-0.03}$ \\
   HIP 16340 & AB$^{\dagger}$ &     1 & yes &  $6214 \pm 150$ &       5 &    -0.5  &  $1.2^{+0.29}_{-0.07}$ &  $1.2^{+0.06}_{-0.05}$ \\
+  HIP 16611 & AB &     1 & yes &  $11500 \pm 1000$ &     75 &     0.0 &  $2.7^{+0.47}_{-0.37}$ &  $3.3^{+0.15}_{-0.66}$ \\
   HIP 18724 & AB &     1 & no &  $6831 \pm 154$ &      20 &     0.0  &  $1.7^{+0.13}_{-0.23}$ &  $1.4^{+0.04}_{-0.04}$ \\
@@
   HIP 26126 & AB? &     3 & yes &   $5841 \pm 91$ &       5 &    -0.5  &  $1.0^{+0.03}_{-0.03}$ &  $1.0^{+0.05}_{-0.04}$ \\
+  HIP 28691 & AB &     1 & no &  $15000 \pm 1000$ &      1 &     0.5 &  $4.0^{+0.45}_{-0.43}$ &  $4.2^{+0.43}_{-0.34}$ \\
+  HIP 28691 & AC &     1 & no &  $12000 \pm 1000$ &      1 &     0.5 &  $2.8^{+0.40}_{-0.34}$ &  $3.3^{+0.23}_{-0.30}$ \\
   HIP 32607 & AB$^{\dagger}$ &     3 & yes &   $5068 \pm 91$ &       5 &    -0.5  &  $0.8^{+0.02}_{-0.02}$ &  $0.9^{+0.01}_{-0.01}$ \\
+  HIP 37322 & AB &     1 & yes &    $8157 \pm 147$ &     30 &    -0.5 &  $1.8^{+0.30}_{-0.07}$ &  $1.9^{+0.01}_{-0.07}$ \\
+  HIP 37450 & AB$^{\dagger}$ &     1 & yes &  $16000 \pm 1000$ &     30 &     0.0 &  $4.3^{+0.36}_{-0.43}$ &  $4.7^{+0.71}_{-0.39}$ \\
   HIP 38538 & AB      &     1 & no &   $6576 \pm 150$ &      30 &    -0.5  &  $1.3^{+0.05}_{-0.05}$ &  $1.3^{+0.09}_{-0.05}$ \\
@@
   HIP 72154 & AB$^{\dagger}$ &     1 & yes &  $4918 \pm 162$ &      30 &    -0.5  &  $0.9^{+0.22}_{-0.09}$ &  $0.8^{+0.03}_{-0.03}$ \\
+    HR 5605 & AB &     1 & no &  $16000 \pm 1000$ &     10 &     0.0 &  $4.3^{+0.37}_{-0.42}$ &  $4.7^{+0.76}_{-0.40}$ \\
+    HR 5605 & AC &     1 & no &  $14000 \pm 1000$ &     10 &     0.0 &  $3.5^{+0.42}_{-0.38}$ &  $3.9^{+0.35}_{-0.34}$ \\
+  HIP 74117 & AB &     1 & no &  $14000 \pm 1000$ &     10 &     0.0 &  $3.5^{+0.42}_{-0.38}$ &  $3.9^{+0.34}_{-0.34}$ \\
   HIP 76267 & AB &     1 & yes &  $5449 \pm 158$ &       5 &    -0.5  &  $0.9^{+0.04}_{-0.04}$ &  $0.9^{+0.04}_{-0.03}$ \\
@@
   HIP 78820 & AB &     1 & no &  $5658 \pm 158$ &       5 &    0 &  $1.3^{+0.11}_{-0.13}$ &  $1.0^{+0.04}_{-0.04}$ \\
+  HIP 78918 & AB &     1 & yes &    $9000 \pm 500$ &    120 &    -0.5 &  $2.0^{+0.22}_{-0.17}$ &  $2.1^{+0.13}_{-0.17}$ \\
   HIP 79199 & AB &     1 & no &  $4616 \pm 158$ &       5 &    -0.5  &  $0.9^{+0.14}_{-0.14}$ &  $0.8^{+0.02}_{-0.03}$ \\
@@
   HIP 91118 & AB &     1 & yes &  $6492 \pm 155$ &      10 &    -0.5  &  $1.3^{+0.26}_{-0.07}$ &  $1.3^{+0.06}_{-0.06}$ \\
+  HIP 93225 & AB &     2 & yes &   $14000 \pm 700$ &     10 &     0.5 &  $3.6^{+0.34}_{-0.30}$ &  $3.9^{+0.18}_{-0.23}$ \\
   HIP 93805 & Aa,Ab$^{\dagger}$ &     2 & yes &  $4054 \pm 109$ &       5 &    -0.5  &  $0.6^{+0.03}_{-0.03}$ &  $0.6^{+0.04}_{-0.02}$ \\

### 2016-03-07 paper/ms.tex
Added discussion of fudge factor for completeness estimate

@@
 
+We test to determine if the completeness is reasonable at large mass ratios by comparing to known binary systems.
+We detect 15 of the 25 stars in our sample with a hot ($T > 7000\ K$) companion.
+The completeness function for hot, roughly equal-mass companions suggest the probability of detection if $\sim 80\%$, which is incompatible with our low detection rate (p=0.01).
+The discrepancy may be due to an underestimate of the typical rotation rates for hot stars, used when marginalizing out the dependence on $v\sin{i}$.
+Additionally, rapidly rotating companions, especially when they have a similar temperature to the primary, are more difficult to detect if they have a small radial velocity offset from the primary star.
+While the injection and recovery experiments do sample velocity space to account for this, they may be over-sampling companions with very large velocity offsets and producing anomalously high detection rates.
+We account for the discrepancy by introducing a scaling factor: we multiply the estimated detection rate for all companions with $T > 7000\ K$ by $f=0.8$.
+
 \begin{figure}
@@
 
-We show the total survey completeness in Figure \ref{fig:completeness}.
-The completeness falls very rapidly towards low mass ratios, although we are still $\sim 70\%$ complete at $q = 0.1$.
-The slow fall-off towards large mass ratios is caused by the same effect as in Figure \ref{fig:marginalized}: large mass ratio companions tend to be rapid rotators that are more difficult to detect.
-
-TODO: Discuss fudge factor if Adam agrees...
+We show the resulting total survey completeness in Figure \ref{fig:completeness}.
+The completeness falls very rapidly towards low mass ratios, although we are still $\sim 60\%$ complete at $q = 0.1$.
+The slow fall-off towards large mass ratios is caused by a combination of the scale factor described above and the inherent difficulty of detecting rapidly rotating companions (see Figure \ref{fig:marginalized}).
+The detection rate at large mass ratios is now $\sim 0.6-0.7$, which is consistent with our 15/25 empirical detection rate.
 
@@
     HIP 2548 &    B9.5V &    00:32:23.78 &   +06:57:19.66 &   5.698 &     12.35 &   $11864 \pm 403$ &  $4.4 \pm 0.14$ &  $2.8^{+0.16}_{-0.15}$ &      $77^{+69}_{-51}$ &       1 \\
-    HIP 2912 &      B5V &    00:36:52.85 &   +33:43:09.64 &   4.360 &      5.45 &  $16000 \pm 1000$ &  $4.0 \pm 0.25$ &  $4.7^{+0.61}_{-0.54}$ &      $26^{+32}_{-18}$ &       2 \\
     HIP 3300 &      B2V &    00:42:03.90 &   +50:30:45.09 &   4.810 &      2.28 &  $18000 \pm 1000$ &  $4.0 \pm 0.25$ &  $5.7^{+0.67}_{-0.63}$ &      $19^{+19}_{-13}$ &       2 \\
     HIP 3478 &      B5V &    00:44:26.19 &   +47:51:50.34 &   5.646 &      5.23 &  $18000 \pm 1000$ &  $4.5 \pm 0.25$ &  $5.4^{+0.60}_{-0.57}$ &       $11^{+14}_{-5}$ &       2 \\
-    HIP 3741 &      B9V &    00:48:01.06 &   -21:43:20.99 &   5.570 &      9.51 &   $10000 \pm 500$ &  $3.5 \pm 0.25$ &  $2.8^{+0.47}_{-0.42}$ &    $282^{+82}_{-115}$ &       2 \\
-    HIP 3881 &      B5V &    00:49:48.85 &   +41:04:44.08 &   4.530 &      5.28 &  $16000 \pm 1000$ &  $4.2 \pm 0.25$ &  $4.5^{+0.58}_{-0.52}$ &      $17^{+28}_{-11}$ &       2 \\
-    HIP 4436 &      A5V &    00:56:45.21 &   +38:29:57.64 &   3.870 &     25.14 &    $8351 \pm 284$ &  $4.0 \pm 0.14$ &  $1.9^{+0.17}_{-0.14}$ &   $733^{+129}_{-158}$ &       1 \\
     HIP 5131 &     A1Vn &    01:05:40.96 &   +21:28:23.45 &   5.317 &     11.86 &   $11956 \pm 406$ &  $4.4 \pm 0.14$ &  $2.8^{+0.16}_{-0.14}$ &      $69^{+65}_{-45}$ &       1 \\
@@
     HIP 5310 &      A3V &    01:07:57.16 &   +20:44:20.83 &   5.569 &     21.14 &    $8611 \pm 293$ &  $4.4 \pm 0.14$ &  $1.8^{+0.10}_{-0.08}$ &   $307^{+228}_{-196}$ &       1 \\
-    HIP 5348 &  B6V+B9V &    01:08:23.08 &   -55:14:44.73 &   3.967 &     10.92 &   $13776 \pm 468$ &  $4.2 \pm 0.14$ &  $3.6^{+0.23}_{-0.21}$ &      $67^{+38}_{-39}$ &       1 \\
     HIP 5361 &      B8V &    01:08:33.47 &   +58:15:48.41 &   5.773 &      5.41 &  $14000 \pm 1000$ &  $4.5 \pm 0.25$ &  $3.6^{+0.49}_{-0.43}$ &      $18^{+36}_{-11}$ &       2 \\
@@
    HIP 14043 &      B7V &    03:00:52.21 &   +52:21:06.22 &   5.253 &      7.11 &  $14000 \pm 1000$ &  $4.5 \pm 0.25$ &  $3.6^{+0.48}_{-0.45}$ &      $17^{+33}_{-10}$ &       2 \\
-   HIP 14143 &      B7V &    03:02:22.52 &   +04:21:10.39 &   5.607 &      5.93 &  $14000 \pm 1000$ &  $4.5 \pm 0.25$ &  $3.6^{+0.50}_{-0.45}$ &      $17^{+36}_{-11}$ &       2 \\
    HIP 14293 &      A5V &    03:04:16.52 &   -07:36:03.08 &   5.300 &     24.06 &    $8039 \pm 273$ &  $4.2 \pm 0.14$ &  $1.8^{+0.14}_{-0.10}$ &   $782^{+166}_{-291}$ &       1 \\
-   HIP 14576 &      B8V &    03:08:10.13 &   +40:57:20.33 &   2.120 &     36.27 &   $13070 \pm 444$ &  $4.0 \pm 0.14$ &  $3.6^{+0.29}_{-0.24}$ &     $139^{+16}_{-25}$ &       1 \\
    HIP 14764 &      B8V &    03:10:38.79 &   +11:52:21.44 &   5.965 &      7.33 &  $12000 \pm 1000$ &  $4.0 \pm 0.25$ &  $2.9^{+0.47}_{-0.40}$ &     $54^{+103}_{-44}$ &       2 \\
@@
    HIP 15444 &      B5V &    03:19:07.64 &   +50:05:41.88 &   5.036 &      5.82 &  $18000 \pm 1000$ &  $4.5 \pm 0.25$ &  $5.5^{+0.60}_{-0.60}$ &       $11^{+14}_{-6}$ &       2 \\
-   HIP 16147 &      B5V &    03:28:03.07 &   +49:03:46.32 &   4.970 &      6.22 &  $18000 \pm 1000$ &  $4.5 \pm 0.25$ &  $5.4^{+0.59}_{-0.58}$ &       $11^{+14}_{-5}$ &       2 \\
    HIP 16210 &     B6Vn &    03:28:52.33 &   +49:50:54.17 &   5.578 &      6.22 &           \nodata &         \nodata &                \nodata &               \nodata & \nodata \\
@@
    HIP 18396 &      B6V &    03:55:58.17 &   +47:52:17.12 &   5.379 &      4.47 &  $16000 \pm 1000$ &  $4.5 \pm 0.25$ &  $4.5^{+0.54}_{-0.50}$ &       $14^{+21}_{-8}$ &       2 \\
-   HIP 18724 &      B3V &    04:00:40.82 &   +12:29:25.22 &   3.410 &      6.74 &           \nodata &         \nodata &                \nodata &               \nodata & \nodata \\
    HIP 18788 &      B5V &    04:01:32.05 &   -01:32:58.78 &   5.280 &      7.88 &  $16000 \pm 1000$ &  $4.5 \pm 0.25$ &  $4.5^{+0.51}_{-0.49}$ &       $13^{+22}_{-7}$ &       2 \\
@@
    HIP 24902 &      A3V &    05:20:14.67 &   +41:05:10.35 &   5.468 &     11.77 &    $8275 \pm 281$ &  $4.0 \pm 0.14$ &  $1.8^{+0.09}_{-0.08}$ &   $457^{+261}_{-281}$ &       1 \\
-   HIP 25048 &      B3V &    05:21:48.42 &   +41:48:16.46 &   5.200 &      6.16 &  $18000 \pm 1000$ &  $4.5 \pm 0.25$ &  $5.5^{+0.62}_{-0.61}$ &       $11^{+13}_{-5}$ &       2 \\
  ADS 3962 AB &     B1Vn &    05:22:50.30 &   +03:32:52.00 &   4.990 &   \nodata &           \nodata &         \nodata &                \nodata &               \nodata & \nodata \\
@@
    HIP 25280 &      A0V &    05:24:28.49 &   -16:58:32.81 &   5.644 &     14.65 &   $10398 \pm 354$ &  $4.4 \pm 0.14$ &  $2.4^{+0.13}_{-0.11}$ &   $199^{+101}_{-115}$ &       1 \\
-   HIP 25281 &      B1V &    05:24:28.62 &   -02:23:49.73 &   3.350 &      3.34 &           \nodata &         \nodata &                \nodata &               \nodata & \nodata \\
    HIP 25555 &   B9.5Vn &    05:27:45.61 &   +15:52:26.58 &   5.512 &      7.69 &   $10000 \pm 500$ &  $3.5 \pm 0.25$ &  $2.8^{+0.45}_{-0.43}$ &    $283^{+79}_{-104}$ &       2 \\
@@
    HIP 26126 &      A2V &    05:34:16.77 &   +03:46:00.82 &   5.332 &     11.82 &    $9542 \pm 324$ &  $3.9 \pm 0.14$ &  $2.1^{+0.09}_{-0.07}$ &   $177^{+150}_{-115}$ &       1 \\
-     HR 1880 &    B0.5V &    05:35:08.48 &   +09:56:06.10 &   6.322 &   \nodata &  \nodata          &  \nodata        &  \nodata                &         \nodata          &       \nodata \\
    HIP 26563 &     A4Vn &    05:38:53.08 &   -07:12:46.18 &   4.800 &     22.42 &    $8416 \pm 286$ &  $4.1 \pm 0.14$ &  $1.8^{+0.08}_{-0.07}$ &   $344^{+256}_{-218}$ &       1 \\
@@
    HIP 33372 &     B8Vn &    06:56:25.83 &   +09:57:23.67 &   5.905 &      7.18 &  $14000 \pm 1000$ &  $4.5 \pm 0.25$ &  $3.6^{+0.47}_{-0.46}$ &      $18^{+37}_{-11}$ &       2 \\
-   HIP 33575 &      B2V &    06:58:35.90 &   -25:24:50.97 &   5.577 &      3.78 &  $22000 \pm 1000$ &  $4.5 \pm 0.25$ &  $7.8^{+0.69}_{-0.67}$ &         $8^{+6}_{-3}$ &       2 \\
    HIP 34769 &      A2V &    07:11:51.86 &   -00:29:33.96 &   4.150 &      8.49 &    $9000 \pm 500$ &  $3.5 \pm 0.25$ &  $2.4^{+0.43}_{-0.38}$ &   $405^{+135}_{-207}$ &       2 \\
@@
    HIP 36917 &      B7V &    07:35:22.89 &   -28:22:09.57 &   4.630 &     14.72 &   $13926 \pm 473$ &  $4.3 \pm 0.14$ &  $3.7^{+0.17}_{-0.15}$ &      $62^{+35}_{-37}$ &       1 \\
-     HR 2948 &      B6V &    07:38:49.38 &   -26:48:06.49 &   4.500 &   \nodata &  $14000 \pm 1000$ &  $4.5 \pm 0.25$ &  $3.6^{+0.48}_{-0.44}$ &      $17^{+36}_{-11}$ &       2 \\
    HIP 37297 &    B2.5V &    07:39:27.34 &   -38:18:28.88 &   4.840 &      5.87 &  $20000 \pm 1000$ &  $4.5 \pm 0.25$ &  $6.6^{+0.67}_{-0.62}$ &         $9^{+9}_{-4}$ &       2 \\
@@
    HIP 54849 &      A0V &    11:13:45.55 &   -00:04:10.20 &   5.399 &      6.18 &   $10000 \pm 500$ &  $4.0 \pm 0.25$ &  $2.3^{+0.24}_{-0.21}$ &     $72^{+197}_{-62}$ &       2 \\
-   HIP 55266 &      A2V &    11:19:07.90 &   +38:11:08.03 &   4.800 &     17.00 &    $8720 \pm 296$ &  $4.5 \pm 0.14$ &  $1.9^{+0.10}_{-0.08}$ &   $346^{+208}_{-217}$ &       1 \\
    HIP 55434 &    B9.5V &  11:21:08.1934 &  +06:01:45.571 &   4.044 &     14.82 &   $10618 \pm 361$ &  $3.9 \pm 0.14$ &  $2.7^{+0.23}_{-0.19}$ &     $304^{+32}_{-38}$ &       1 \\
@@
    HIP 70915 &     B8Vn &    14:30:08.63 &   -45:19:16.88 &   5.500 &      6.84 &  $12000 \pm 1000$ &  $4.5 \pm 0.25$ &  $2.8^{+0.42}_{-0.37}$ &      $24^{+65}_{-17}$ &       2 \\
-     HR 5476 &      A6V &    14:40:43.94 &   +16:25:03.90 &   5.820 &   \nodata &           \nodata &         \nodata &                \nodata &               \nodata & \nodata \\
    HIP 71865 &      B3V &    14:41:57.59 &   -37:47:36.59 &   4.000 &      9.62 &  $20000 \pm 1000$ &  $4.5 \pm 0.25$ &  $6.6^{+0.66}_{-0.64}$ &         $9^{+9}_{-4}$ &       2 \\
@@
    HIP 78820 &      B1V &    16:05:26.23 &   -19:48:19.63 &   2.620 &      8.07 &           \nodata &         \nodata &                \nodata &               \nodata & \nodata \\
-   HIP 78821 &      B2V &    16:05:26.57 &   -19:48:06.85 &   4.890 &      8.19 &           \nodata &         \nodata &                \nodata &               \nodata & \nodata \\
      HR 6025 &     A0Vn &  16:06:19.6762 &  +67:48:36.480 &   5.439 &     12.85 &   $9250 \pm 1000$ &  $4.5 \pm 0.25$ &  $1.9^{+0.32}_{-0.31}$ &     $48^{+210}_{-39}$ &       2 \\
@@
    HIP 85922 &      A5V &    17:33:29.85 &   -05:44:41.29 &   5.619 &     20.79 &    $8000 \pm 500$ &  $4.0 \pm 0.25$ &  $1.7^{+0.19}_{-0.16}$ &   $117^{+539}_{-105}$ &       2 \\
-   HIP 85998 &      A2V &    17:34:36.69 &   +09:35:12.12 &   5.810 &      9.66 &    $9000 \pm 500$ &  $3.5 \pm 0.25$ &  $2.4^{+0.44}_{-0.37}$ &   $399^{+137}_{-200}$ &       2 \\
    HIP 86019 &     B8Vn &    17:34:46.35 &   -11:14:31.19 &   5.537 &      8.11 &  $12000 \pm 1000$ &  $4.5 \pm 0.25$ &  $2.8^{+0.42}_{-0.37}$ &      $25^{+62}_{-17}$ &       2 \\
@@
    HIP 96288 &      A2V &    19:34:41.26 &   +42:24:45.04 &   5.348 &      5.66 &    $9000 \pm 500$ &  $3.5 \pm 0.25$ &  $2.4^{+0.43}_{-0.39}$ &   $405^{+137}_{-166}$ &       2 \\
-   HIP 96840 &      B5V &    19:41:05.53 &   +13:48:56.45 &   5.988 &      0.49 &  $16000 \pm 1000$ &  $4.0 \pm 0.25$ &  $4.7^{+0.62}_{-0.56}$ &      $26^{+31}_{-18}$ &       2 \\
    HIP 97376 &     B8Vn &    19:47:27.78 &   +38:24:27.41 &   5.826 &      6.90 &  $11500 \pm 2000$ &  $4.5 \pm 0.25$ &  $2.2^{+0.73}_{-0.70}$ &     $34^{+157}_{-26}$ &       2 \\
@@
    HIP 98055 &     A4Vn &    19:55:37.79 &   +52:26:20.21 &   4.920 &     11.59 &    $9000 \pm 500$ &  $4.5 \pm 0.25$ &  $1.9^{+0.18}_{-0.17}$ &     $47^{+186}_{-38}$ &       2 \\
-   HIP 98194 &      B5V &    19:57:13.87 &   +40:22:04.17 &   5.453 &      2.94 &  $16000 \pm 1000$ &  $4.0 \pm 0.25$ &  $4.7^{+0.59}_{-0.54}$ &      $27^{+31}_{-19}$ &       2 \\
    HIP 98325 &     B9Vn &    19:58:37.98 &   +30:59:01.19 &   5.506 &      7.01 &  $12000 \pm 1000$ &  $4.5 \pm 0.25$ &  $2.8^{+0.41}_{-0.37}$ &      $25^{+65}_{-17}$ &       2 \\
@@
   HIP 100221 &      B9V &    20:19:36.72 &   +62:15:26.90 &   5.712 &      8.63 &   $10000 \pm 500$ &  $4.0 \pm 0.25$ &  $2.3^{+0.25}_{-0.21}$ &     $70^{+205}_{-60}$ &       2 \\
-  HIP 100881 &      B4V &    20:27:19.21 &   -18:12:42.20 &   5.250 &      5.98 &  $14000 \pm 1000$ &  $4.5 \pm 0.25$ &  $3.6^{+0.48}_{-0.45}$ &      $17^{+34}_{-10}$ &       2 \\
   HIP 100907 &      A3V &    20:27:34.26 &   +38:26:25.19 &   5.620 &     12.28 &    $9042 \pm 307$ &  $4.0 \pm 0.14$ &  $2.1^{+0.16}_{-0.13}$ &    $514^{+99}_{-166}$ &       1 \\
@@
   HIP 101716 &      B8V &    20:37:04.67 &   +26:27:43.01 &   5.589 &     10.27 &   $12949 \pm 440$ &  $4.2 \pm 0.14$ &  $3.3^{+0.17}_{-0.14}$ &      $91^{+44}_{-53}$ &       1 \\
-  HIP 101867 &      A0V &    20:38:31.34 &   +21:12:04.25 &   4.820 &     14.01 &   $10507 \pm 357$ &  $4.2 \pm 0.14$ &  $3.4^{+0.24}_{-0.30}$ &     $252^{+45}_{-33}$ &       1 \\
   HIP 101909 &      B3V &    20:39:04.97 &   +15:50:17.52 &   5.980 &      2.42 &           \nodata &         \nodata &                \nodata &               \nodata & \nodata \\
@@
   HIP 103298 &      A5V &    20:55:38.57 &   +12:34:06.81 &   5.540 &     16.53 &    $9093 \pm 309$ &  $4.1 \pm 0.14$ &  $2.0^{+0.13}_{-0.11}$ &   $400^{+150}_{-215}$ &       1 \\
-  HIP 104019 &      A5V &    21:04:24.30 &   -19:51:17.97 &   4.840 &     20.20 &    $8319 \pm 283$ &  $4.2 \pm 0.14$ &  $1.8^{+0.09}_{-0.07}$ &   $452^{+245}_{-273}$ &       1 \\
   HIP 104105 &     B8Vn &    21:05:29.27 &   +78:07:35.02 &   5.915 &      8.10 &   $9750 \pm 1000$ &  $4.0 \pm 0.25$ &  $2.1^{+0.39}_{-0.32}$ &     $92^{+255}_{-80}$ &       2 \\
@@
   HIP 111169 &      A1V &    22:31:17.50 &   +50:16:56.97 &   3.770 &     31.79 &   $10071 \pm 342$ &  $4.3 \pm 0.14$ &  $2.3^{+0.12}_{-0.10}$ &   $202^{+123}_{-123}$ &       1 \\
-  HIP 111841 &      O9V &    22:39:15.68 &   +39:03:00.97 &   4.880 &      1.89 &           \nodata &         \nodata &                \nodata &               \nodata & \nodata \\
   HIP 112029 &      B8V &    22:41:27.73 &   +10:49:52.64 &   3.410 &   \nodata &   $11913 \pm 405$ &  $3.8 \pm 0.14$ &  $2.9^{+0.17}_{-0.14}$ &     $135^{+57}_{-76}$ &       1 \\
@@
     HIP 2548 &  6516.84 &        HRS &      412 &  1070 \\
-    HIP 2912 &  7238.96 &     IGRINS &      367 &   130 \\
-    HIP 2912 &  6583.78 &       TS23 &      199 &  2460 \\
     HIP 3300 &  6299.55 &       TS23 &      689 &  1010 \\
@@
     HIP 3478 &  6945.72 &     IGRINS &      224 &   150 \\
-    HIP 3741 &  7174.89 &     CHIRON &     3981 &   430 \\
-    HIP 3741 &  7175.90 &     CHIRON &     3561 &   420 \\
-    HIP 3881 &  6585.70 &       TS23 &      222 &  1690 \\
-    HIP 3881 &  6964.60 &       TS23 &     1200 &   710 \\
-    HIP 3881 &  6945.74 &     IGRINS &      224 &   200 \\
-    HIP 4436 &  6585.76 &       TS23 &      129 &  1940 \\
     HIP 5131 &  6587.70 &       TS23 &      655 &  1780 \\
@@
     HIP 5310 &  6945.75 &     IGRINS &      224 &   200 \\
-    HIP 5348 &  6325.56 &     CHIRON &      186 &   390 \\
     HIP 5361 &  6523.84 &        HRS &     1000 &   810 \\
@@
    HIP 14043 &  6523.92 &        HRS &      400 &   620 \\
-   HIP 14143 &  6518.94 &        HRS &      462 &   900 \\
    HIP 14293 &  6919.89 &     CHIRON &      800 &   240 \\
-   HIP 14576 &  6583.83 &       TS23 &       40 &  1030 \\
-   HIP 14576 &  6582.92 &       TS23 &       36 &  2050 \\
    HIP 14764 &  6679.53 &       TS23 &      532 &  1370 \\
@@
    HIP 15444 &  6582.94 &       TS23 &      340 &  1790 \\
-   HIP 16147 &  6299.59 &       TS23 &      735 &  1300 \\
    HIP 16210 &  6676.58 &       TS23 &      406 &  1440 \\
@@
    HIP 18396 &  6516.94 &        HRS &      259 &   510 \\
-   HIP 18724 &  6299.62 &       TS23 &      226 &  1220 \\
    HIP 18788 &  6535.81 &     CHIRON &     1039 &   180 \\
@@
    HIP 24902 &  6946.88 &     IGRINS &      224 &   180 \\
-   HIP 25048 &  6299.69 &       TS23 &      900 &   420 \\
  ADS 3962 AB &  6946.92 &     IGRINS &      280 &   170 \\
@@
    HIP 25280 &  6947.91 &     IGRINS &      240 &   130 \\
-   HIP 25281 &  6299.71 &       TS23 &      583 &  1120 \\
    HIP 25555 &  6670.63 &       TS23 &      600 &  1950 \\
@@
    HIP 26126 &  6948.81 &     CHIRON &      550 &   360 \\
-     HR 1880 &  6594.74 &     CHIRON &      472 &   540 \\
    HIP 26563 &  6677.68 &       TS23 &      502 &  1550 \\
@@
    HIP 33372 &  6678.72 &       TS23 &      720 &  1380 \\
-   HIP 33575 &  6599.72 &     CHIRON &     1200 &   390 \\
    HIP 34769 &  6677.75 &       TS23 &      279 &  1520 \\
@@
    HIP 36917 &  6971.83 &     CHIRON &      435 &   690 \\
-     HR 2948 &  6584.81 &     CHIRON &      576 &   370 \\
    HIP 37297 &  6698.74 &     CHIRON &      370 &   480 \\
@@
    HIP 54849 &  6670.94 &       TS23 &      797 &  2080 \\
-   HIP 55266 &  6300.00 &       TS23 &      900 &   200 \\
    HIP 55434 &  6332.77 &     CHIRON &      199 &   410 \\
@@
    HIP 70915 &  7090.71 &     CHIRON &     2985 &   460 \\
-     HR 5476 &  6408.71 &        HRS &      305 &   660 \\
    HIP 71865 &  6383.71 &     CHIRON &      190 &   460 \\
@@
    HIP 78820 &  7156.63 &     CHIRON &      164 &   390 \\
-   HIP 78821 &  7139.84 &     IGRINS &      210 &    50 \\
      HR 6025 &  6847.83 &     IGRINS &      600 &   100 \\
@@
    HIP 85922 &  7104.82 &     CHIRON &     7386 &   360 \\
-   HIP 85998 &  7122.96 &     IGRINS &      480 &    50 \\
-   HIP 85998 &  7230.64 &     IGRINS &      720 &   170 \\
-   HIP 85998 &  6407.84 &        HRS &      324 &   490 \\
-   HIP 85998 &  7079.89 &     CHIRON &     1600 &   220 \\
    HIP 86019 &  6747.85 &     CHIRON &      228 &   510 \\
@@
    HIP 98055 &  6586.54 &       TS23 &      320 &  1820 \\
-   HIP 98194 &  6583.54 &       TS23 &      495 &  1750 \\
    HIP 98325 &  6587.56 &       TS23 &      543 &  1750 \\
@@
   HIP 100221 &  6523.79 &        HRS &      874 &   830 \\
-  HIP 100881 &  6511.69 &     CHIRON &     1011 &   570 \\
   HIP 100907 &  6946.57 &     IGRINS &      224 &   120 \\
@@
   HIP 101716 &  6582.60 &       TS23 &      549 &  1260 \\
-  HIP 101867 &  6489.78 &     CHIRON &      408 &   440 \\
   HIP 101909 &  6945.60 &     IGRINS &      360 &   140 \\
@@
   HIP 103298 &  7155.93 &     CHIRON &     1141 &   290 \\
-  HIP 104019 &  6474.90 &     CHIRON &      423 &   550 \\
   HIP 104105 &  6945.69 &     IGRINS &      280 &   140 \\
@@
   HIP 111169 &  6585.62 &       TS23 &      121 &  1900 \\
-  HIP 111841 &  6583.68 &       TS23 &      267 &  1670 \\
   HIP 112029 &  6487.85 &     CHIRON &      109 &   460 \\
@@
   HIP 14043 & Aa,Ab$^{\dagger}$ &     1 & yes &  $11500 \pm 500$ &       20 &    0.5  &  $2.6^{+0.36}_{-0.29}$ &  $3.3^{+0.15}_{-0.67}$ \\
-  HIP 14576 & Aa,Ab &     2 & no &  $6980 \pm 103$ &      10 &     0.0  &  $1.4^{+0.03}_{-0.03}$ &  $1.5^{+0.05}_{-0.03}$ \\
   HIP 14764 & AB$^{\dagger}$ &     2 & yes &  $5623 \pm 150$ &      5 &     -0.5 &    $1.0^{+0.32}_{-0.07}$ &  $1.0^{+0.03}_{-0.04}$ \\
@@
   HIP 16611 & AB &     1 & yes &  $11500 \pm 1000$ &     75 &     0.0 &  $2.7^{+0.47}_{-0.37}$ &  $3.3^{+0.15}_{-0.66}$ \\
-  HIP 18724 & AB &     1 & no &  $6831 \pm 154$ &      20 &     0.0  &  $1.7^{+0.13}_{-0.23}$ &  $1.4^{+0.04}_{-0.04}$ \\
   HIP 19949 & AB$^{\dagger}$ &     1 & yes &  $6492 \pm 155$ &      20 &    -0.5  &  $1.3^{+0.06}_{-0.05}$ &  $1.3^{+0.06}_{-0.06}$ \\
@@
   HIP 52678 & AB$^{\dagger}$ &     2 & yes &  $5033 \pm 112$ &      10 &    -0.5  &  $1.0^{+0.15}_{-0.19}$ &  $0.8^{+0.01}_{-0.02}$ \\  
-  HIP 55266 & AB &     1 & no &  $8483 \pm 139$ &      30 &    -0.5 &  $1.8^{+0.06}_{-0.04}$ &  $2.0^{+0.06}_{-0.05}$ \\
   HIP 63945 & AC &     1 & no &  $7038 \pm 162$ &      10 &    -0.5 &  $1.6^{+0.26}_{-0.16}$ &  $1.5^{+0.08}_{-0.06}$ \\
@@
   HIP 84606 & AB &     1 & yes &  $5476 \pm 154$ &      10 &    -0.5 &  $0.9^{+0.05}_{-0.04}$ &  $0.9^{+0.04}_{-0.03}$ \\
-  HIP 85998 & Aa,Ab &     3 & yes &  $5460 \pm 91$ &      1 &    -0.5  &  $1.0^{+0.28}_{-0.03}$ &  $0.9^{+0.04}_{-0.01}$ \\
   HIP 88116 & AB$^{\dagger}$ &     2 & yes &  $5293 \pm 112$ &       5 &     0.0  &  $0.9^{+0.03}_{-0.03}$ &  $0.9^{+0.02}_{-0.03}$ \\

### 2016-03-07 paper/ms.tex
Initial draft of updated paper.

@@
 In the above equation, $\{\vec{x_k}\}$ denotes the full spectrum of star $k$, and $\vec{\theta}$ denotes the parameters for the model we are fitting.
-$K=360$ is the total sample size for our survey, $Q(q)$ is the completeness function shown in Figure \ref{fig:completeness}, and $P(q|\vec{\theta})$ is the likelihood function for the mass ratio given the model parameters.
-We fit the data to three distinct distributions: a histogram ($P_1$), a beta distribution ($P_2$), and a power law ($P_3$):
+$K=341$ is the total sample size for our survey, $Q(q)$ is the completeness function shown in Figure \ref{fig:completeness}, and $P(q|\vec{\theta})$ is the likelihood function for the mass ratio given the model parameters.
+We fit the data to three distinct distributions: a histogram ($P_1$), a lognormal distribution ($P_2$), and a power law ($P_3$):
 
@@
  %P_2(q|\vec{\theta}) &= \frac{A}{\sqrt{2\pi\sigma^2}} e^{-\frac{(q - \mu)^2}{2\sigma^2}} \label{eqn:P2} \\
- P_2(q|\vec{\theta}) &= \frac{\Gamma(a+b)}{\Gamma(a)\Gamma(b)} q^{a-1}(1-q)^{b-1} \\
+ %P_2(q|\vec{\theta}) &= \frac{\Gamma(a+b)}{\Gamma(a)\Gamma(b)} q^{a-1}(1-q)^{b-1} \\
+ P_2(q|\vec{\theta}) &= \frac{A}{q\sqrt{2\pi\sigma^2}} e^{-\frac{(\ln{q} - \mu)^2}{2\sigma^2}} \label{eqn:P2} \\
  P_3(q|\vec{\theta}) &= (1-\gamma)q^{-\gamma} \label{eqn:P3}
 \end{align}
-%The constant $A$ in the gaussian distribution is a renormalization factor such that the distribution is only defined from $0 < q < 1$:
-
-%\begin{equation}
+The constant $A$ in the lognormal distribution is a renormalization factor such that the distribution is only defined from $0 < q < 1$:
+
+\begin{equation}
 %A = \frac{2}{\erf\left(\frac{\mu}{\sigma \sqrt{2}}\right) - \erf\left(\frac{\mu - 1}{\sigma \sqrt{2}}\right)}
-%\end{equation}
+A = \frac{2}{1-\erf\left(\frac{\mu}{\sigma \sqrt{2}}\right)}
+\end{equation}
 
@@
 
-The beta function fit only has two parameters ($a, b$), and was chosen because it has a similar shape to the histogram resulting from the first model and is only defined for $0 < q < 1$.
-We use uniform priors on both $a$ and $b$, resulting in the posterior probability
-
-\begin{equation}
-P_2(a, b | \{\vec{x_k}\}) \propto P_2(q|a, b) 
-\end{equation}
-
-The power law fit has only one parameter ($\gamma$); we use a uniform prior in the fit.
+The lognormal distribution only has two parameters ($\mu, \sigma$), and was chosen because it has a similar shape to the histogram resulting from the first model.
+We use uniform priors on both $\mu$ and $\sigma$, although we note that $\mu$ is compared to $\ln{q}$ and so acts like a log-uniform prior.
+The power law has only one parameter ($\gamma$); we use a uniform prior in the fit.
 
@@
 We show the resulting fits in Figure \ref{fig:mrd}.
-The $1\sigma$ uncertainties in the bin heights from the histogram model are shown as error bars, and we overplot 500 samples of the beta distribution fit to show the spread allowed by the data.
-The best-fit power law is plotted with a green dot-dashed line, as well as the mass ratio distribution expected from random pairing from the Kroupa initial mass function (IMF) in yellow.
+The $1\sigma$ uncertainties in the bin heights from the histogram model are shown as error bars, and we overplot 300 samples of the lognormal distribution fit to show the spread allowed by the data.
+The best-fit power law is plotted with a red dot-dashed line.
+We also estimate the mass ratio distribution expected from random pairing of the Kroupa Initial Mass Function (IMF), and show the result in yellow.
+We estimated the distribution by drawing 100000 primary stars from the IMF with masses between $1.5 < M/M_{\odot} < 20$.
+We then drew companions from the same IMF, with the restriction that the companion has a lower mass than the primary.
+The result plotted in yellow in Figure \ref{fig:mrd} is a gaussian kernel density estimate of the resulting mass ratios, with a bandwidth of $0.05$.
 
@@
 \caption{Mass ratio distribution for our sample.
-The data was fit to a histogram, a beta distribution, and a power law.
+The data was fit to a histogram, a lognormal distribution, and a power law.
 The histogram is shown in the solid blue blocks, with $1 \sigma$ uncertainties marked with error bars.
-The variance of the beta function fit is shown with 500 samples from the posterior probability distribution for the parameters.
-We also show the best-fit power law and the mass ratio distribution resulting from random pairing of the Kroupa initial mass function.}
+The variance of the lognormal  fit is shown with 300 samples from the posterior probability distribution for the parameters in green.
+We also show the best-fit power law and the mass ratio distribution resulting from random pairing of the Kroupa initial mass function.
+Finally, we display the raw mass ratio measurements with associated uncertainties in the cluster of data points near the top of the figure.}
 \label{fig:mrd}
@@
 
-The most striking feature of the mass ratio distribution shown in Figure \ref{fig:mrd} is the turnover at intermediate q, which the beta distribution fit finds occurs at $q = 0.30^{+0.03}_{-0.04}$.
+The most striking feature of the mass ratio distribution shown in Figure \ref{fig:mrd} is the turnover or flattening at intermediate q.
+The maximum of the lognormal distribution occurs at $q = 0.30 \pm 0.03$ and is an estimate of the characteristic scale.
+
 Although the power law fit and the Kroupa IMF are visually very poor fits to the data, we formally compare the models to ensure that the different form is not an artifact of binning or simple noise.
@@
 The integrals are estimated as part of the nested sampling algorithm in the MultiNest code.
-The odds ratio comparing the beta distribution to power law fit is $Z_\mathrm{beta} / Z_\mathrm{power} = 81 \pm 1.3 \e{8}$ indicating a very strong preference for the beta distribution model.
-We also compare to the mass ratio distribution expected for random pairing from the Kroupa IMF.
-In this case, there are no free parameters so the evidence integral just becomes the likelihood function (Equation \ref{eqn:money}).
-The corresponding odds ratio is  $Z_\mathrm{beta} / Z_\mathrm{kroupa} = 325 \pm 3.6 \e{18}$, again indicating a very strong preference for the beta distribution fit.
+The odds ratio comparing the lognormal distribution to power law fit is $Z_\mathrm{lognormal} / Z_\mathrm{power} = 5.1 \pm 0.1 \e{6}$, indicating a very strong preference for the lognormal distribution model.
+We also compare to the mass ratio distribution expected for random pairing from the Kroupa IMF and to a uniform distribution (a special case of the power law).
+In these cases, there are no free parameters so the evidence integral just becomes the likelihood function (Equation \ref{eqn:money}).
+The corresponding odds ratios are  $Z_\mathrm{lognormal} / Z_\mathrm{IMF} = 6.5 \pm 0.1 \e{22}$ and $Z_\mathrm{lognormal} / Z_\mathrm{uniform} = 7.0 \pm 0.1 \e{6}$.
+Both of these again demonstrate a very strong preference of the lognormal distribution.
+
 The extreme unlikeliness of the Kroupa IMF model also indicates that our sample is not significantly biased by foreground or background contaminants.
+In fact, the present-day background star mass function is more bottom heavy than the initial mass function because some of the massive stars have evolved to white dwarfs or ended their lives in a supernova.
+The comparison to a Kroupa IMF therefore \emph{underestimates} the likelihood of background star contamination.
 
@@
 To assess the degree of tension, we use the Anderson-Darling  test \citep{Anderson1954} to find the probability that both their close companion subsample and our companions are drawn from the same parent distribution.
-We only use companions from this work with mean $\overline{q} > 0.15$, since the survey completeness is roughly constant in that range and because the VAST survey subsample makes the same cut.
+We only use companions from this work with mean $\overline{q} > 0.15$ because the VAST survey subsample makes the same cut.
 To account for measurement uncertainties in the mass ratios, we choose from the mass ratio samples ($q_k^{(n)}$, see Section \ref{sec:mrd}) many times and compute the Anderson-Darling test statistic each time.
 Since \citet{DeRosa2014} do not quote uncertainties, we assume uncertainties of $\sigma_q = 0.05$ for all of their measurements.
-The result is $p = 0.02^{+0.02}_{-0.01}$, indicating that it is unlikely that both samples come from the same parent distribution.
-
-The differing results indicate that the mass ratio distribution changes inside $\sim 30-50$ AU, where \citet{DeRosa2014} has low completeness.
-This intrepretation implies that the mass ratio distribution is a very steep power law at wide ($a \gtrsim 150$ AU) separations, flattens out at intermediate separations ($50\ \mathrm{AU} \lesssim a \lesssim 150\ \mathrm{AU}$), and begins to show a preference for $q \sim 0.3$ at close separations ($a \lesssim 50$ AU).
-
-%\subsection{Theoretical Implications}
-
-%TODO: Discuss ways forward.
-Compile table giving the estimated maximum separation from the RVs.
-Promote an imaging survey to follow these up.
-Promote RV monitoring of the detections to get dynamical mass ratios and, more importantly, separations.
-
-%TODO: Discuss physical mechanism to generate a preferrence for $q = 0.3$.
-Saying something about when disk fragments (how much time is left for the companion to accrete)?
-Saying something about migration in the early disk?
-Perhaps the extreme mass-ratio systems migrate inwards as they accrete material.
-If they continue migrating long enough to get much over $q \sim 0.3$, they end up falling into the star?
-
-\subsection{Supplemental Data}
+The result is $p = 0.10^{+0.07}_{-0.04}$; we cannot reject the hypothesis that both samples come from the same distribution.
+
+\subsection{Theoretical Implications}
+\label{subsec:theory}
+
+The mass ratio distribution derived in this work has a very different form than the power law found for companions at wide separations.
+This is likely a result of disk interactions as the two components are accreting.
+The close companions that we detect may form with similar masses to their counterparts at large separations ($a \gtrsim 1000\ AU$), but preferentially accrete matter from the dense primary star disk.
+Since preferential accretion is strongest at the most extreme mass ratios [CITE], the result would be a depletion of low mass ratio companions as they become intermediate to high mass ratio companions.
+The characteristic scale of $\sim 0.3$ that we see in Figure \ref{fig:mrd} would then be related to the disk timescale, since with enough time the preferential accretion would push all companions to $q = 1.0$.
+
+It is also possible that some of the companions found in this work were formed from a gravitationally unstable disk \citep[e.g.][]{Kratter2006, Stamatellos2011}.
+Being a completely different formation mechanism than the way wide companions form, we would expect the mass function to differ.
+Additionally, such companions would undergo the same preferential accretion discussed above.
+This explanation may even be preferable, since it could explain why we see a separation-dependent mass ratio distribution around intermediate-mass stars but not low-mass stars: more massive stars tend to have more massive disks [CITE] that are more likely to fragment.
+
+Large scale simulations are likely needed to distinguish between the two scenarios and fully interpret the results of this survey.
+A significant amount of work has already been put towards this end in the form of radiation hydrodynamic simulations of full giant molecular clouds \citep{Bate2012, Krumholz2012}.
+However, the present simulations do not generate enough stars more massive than the sun to compare binary and multiple star statistics to observations.
+
+\section{Summary}
+
+In this work, we described a binary survey of 341 bright A- and B-type stars.
+We used the direct spectroscopic detection method \citep{Gullikson2016} to find the spectral lines of 64 companions with temperatures ranging from $3600 - 16000\ K$.
+We used the cross-correlation functions to estimate the temperature, surface gravity, and metallicity of most of our sample stars, and converted to mass and age by interpolating Padova stellar evolutionary tracks \citep{Bressan2012}.
+Likewise, we convert the companion temperature measurements to mass by using solar metallicity Dartmough evolutionary tracks [CITE].
+
+We then use the formalism introduced in \citet{Foreman2014}, which self-consistently accounts for measurement errors, to infer the form of the mass ratio distribution (shown in Figure \ref{fig:mrd}).
+Unlike most previous work, we find that a power law is a poor descriptor of the data and find that a lognormal distribution performs much better.
+This result, which only includes close companions since it is a spectroscopic technique, is consistent with the 18 close companions found in the VAST survey \cite{DeRosa2014}.
+However, this result shows much more detail due to a larger number of companions.
+
+We interpret the mass ratio distribution in terms of formation mechanism in Section \ref{subsec:theory}.
+It is likely that the mass ratio distribution we find is largely a result of preferential accretion onto the secondary star, which largely stops when the circumprimary or circumbinary disk dissipates.
 

### 2016-03-08 paper/ms.tex
Updated abstract

@@
 We should therefore expect the mass-ratio distribution of close companions to differ from that of wide companions.
-This prediction is difficult to test with intermediate-mass to massive primary stars because close companions are so much dimmer.
+This prediction is difficult to test with intermediate-mass to massive primary stars using traditional methods because close companions are so much dimmer.
 We present the results of a survey searching for companions to A- and B-type stars using the direct spectral detection technique, which is sensitive to late-type companions within $\sim 1''$ of the primary and which has no inner working angle.
-We estimate the temperatures and masses of the 57 companions , 25 of which are new detections.
-We find that the mass-ratio distribution for our sample has a robust maximum near $q \sim 0.3$.
+We estimate the temperatures and surface gravity of most of the 341 sample stars, and derive their masses and ages.
+We additionally estimate the temperatures and masses of the 64 companions we find, 23 of which are new detections.
+We find that the mass-ratio distribution for our sample has a maximum near $q \sim 0.3$.
 Our mass-ratio distribution has a very different form than in previous work, where it is usually well-described by a power law, and indicates that close companions to intermediate-mass stars experience significantly different accretion histories or formation mechanisms than wide companions.
@@
 Most work has suggested that the disk material will preferentially accrete onto the lower mass companion \citep{Bate1997, BBB2002}; however, recent work has indicated that magnetic disk braking may result in preferential accretion onto the more massive component \citep{Zhao2013} instead.
-In either case, we would expect to find a mass ratio distribution for companions inside a few $100$ AU that differs from that of companions on wider orbits.
+In either case, we would expect to find a mass-ratio distribution for companions inside a few $100$ AU that differs from that of companions on wider orbits.
 
 The mass ratio, period, and eccentricity distributions are fairly well-known for solar type stars \citep{Duquennoy1991, Raghavan2010} and cooler stars \citep{Fischer1992, Delfosse2004}.
-Interestingly, the mass ratio distribution appears to be invariant to separation for these stars \citep{Meyer2013}, contrary to the theoretical expectations.
+Interestingly, the mass-ratio distribution appears to be invariant to separation for these stars \citep{Meyer2013}, contrary to the theoretical expectations.
 All of the distributions are much less certain for more massive stars.
@@
 
-Nonetheless, \citet{DeRosa2014} performed an adaptive optics imaging survey of nearby A-type stars, and found that the mass ratio distribution is well-described by a power law with large slope, indicating a very strong preference for low-mass companions.
-They also found initial evidence that the mass ratio distribution for companions inside $125$ AU has a much shallower power law slope than that of wide companions, and is consistent with flat.
+Nonetheless, \citet{DeRosa2014} performed an adaptive optics imaging survey of nearby A-type stars, and found that the mass-ratio distribution is well-described by a power law with large slope, indicating a very strong preference for low-mass companions.
+They also found initial evidence that the mass-ratio distribution for companions inside $125$ AU has a much shallower power law slope than that of wide companions, and is consistent with flat.
 Their close companion subsample contained only 18 binary systems, and the result is complicated by the inherent difficulty of detecting close companions with low mass ratios in an imaging survey.
@@
 We estimate the mass and age of the primary stars in Section \ref{sec:sp}, and discuss the survey completeness in Section \ref{sec:completeness}.
-Finally, we end with a derivation of the mass ratio distribution from our sample in Section \ref{sec:mrd} and discuss its implications for binary formation in Section \ref{sec:discussion}.
+Finally, we end with a derivation of the mass-ratio distribution from our sample in Section \ref{sec:mrd} and discuss its implications for binary formation in Section \ref{sec:discussion}.
 
@@
 
-We use the methodology developed in \citet{Foreman2014} to perform bayesian inference on the shape and form of the mass ratio distribution.
+We use the methodology developed in \citet{Foreman2014} to perform bayesian inference on the shape and form of the mass-ratio distribution.
 The log-likelihood function in this formalism is derived from modeling the survey as a draw from the inhomogeneous Poisson process with rate density $\Gamma \equiv KQ(q)P(q)$:
@@
 \end{align}
-The smoothing prior is an 7-dimensional gaussian with mean $m$ and covariance matrix $K_{ij}$, and encodes our belief that the mass ratio distribution is a smoothly varying function while leaving enough flexibility to let the data drive the shape of the function.
+The smoothing prior is an 7-dimensional gaussian with mean $m$ and covariance matrix $K_{ij}$, and encodes our belief that the mass-ratio distribution is a smoothly varying function while leaving enough flexibility to let the data drive the shape of the function.
 Since we have introduced three new hyperparameters ($a, m, \tau, \epsilon$), we must apply a prior to them and marginalize over them when estimating the bin heights.
@@
 The best-fit power law is plotted with a red dot-dashed line.
-We also estimate the mass ratio distribution expected from random pairing of the Kroupa Initial Mass Function (IMF), and show the result in yellow.
+We also estimate the mass-ratio distribution expected from random pairing of the Kroupa Initial Mass Function (IMF), and show the result in yellow.
 We estimated the distribution by drawing 100000 primary stars from the IMF with masses between $1.5 < M/M_{\odot} < 20$.
@@
 \includegraphics[width=\columnwidth]{MRD_total.pdf}
-\caption{Mass ratio distribution for our sample.
+\caption{mass-ratio distribution for our sample.
 The data was fit to a histogram, a lognormal distribution, and a power law.
@@
 The variance of the lognormal  fit is shown with 300 samples from the posterior probability distribution for the parameters in green.
-We also show the best-fit power law and the mass ratio distribution resulting from random pairing of the Kroupa initial mass function.
+We also show the best-fit power law and the mass-ratio distribution resulting from random pairing of the Kroupa initial mass function.
 Finally, we display the raw mass ratio measurements with associated uncertainties in the cluster of data points near the top of the figure.}
@@
 
-The most striking feature of the mass ratio distribution shown in Figure \ref{fig:mrd} is the turnover or flattening at intermediate q.
+The most striking feature of the mass-ratio distribution shown in Figure \ref{fig:mrd} is the turnover or flattening at intermediate q.
 The maximum of the lognormal distribution occurs at $q = 0.30 \pm 0.03$ and is an estimate of the characteristic scale.
@@
 The odds ratio comparing the lognormal distribution to power law fit is $Z_\mathrm{lognormal} / Z_\mathrm{power} = 5.1 \pm 0.1 \e{6}$, indicating a very strong preference for the lognormal distribution model.
-We also compare to the mass ratio distribution expected for random pairing from the Kroupa IMF and to a uniform distribution (a special case of the power law).
+We also compare to the mass-ratio distribution expected for random pairing from the Kroupa IMF and to a uniform distribution (a special case of the power law).
 In these cases, there are no free parameters so the evidence integral just becomes the likelihood function (Equation \ref{eqn:money}).
@@
 
-Our mass ratio distribution appears to be in tension with the results of the VAST survey \citep{DeRosa2014}, which finds a nearly flat distribution for close companions.
+Our mass-ratio distribution appears to be in tension with the results of the VAST survey \citep{DeRosa2014}, which finds a nearly flat distribution for close companions.
 However, their subsample of close companions only includes 18 binaries, so it is possible that the different forms are just a result of small number statistics.
@@
 
-The mass ratio distribution derived in this work has a very different form than the power law found for companions at wide separations.
+The mass-ratio distribution derived in this work has a very different form than the power law found for companions at wide separations.
 This is likely a result of disk interactions as the two components are accreting.
@@
 Additionally, such companions would undergo the same preferential accretion discussed above.
-This explanation may even be preferable, since it could explain why we see a separation-dependent mass ratio distribution around intermediate-mass stars but not low-mass stars: more massive stars tend to have more massive disks [CITE] that are more likely to fragment.
+This explanation may even be preferable, since it could explain why we see a separation-dependent mass-ratio distribution around intermediate-mass stars but not low-mass stars: more massive stars tend to have more massive disks [CITE] that are more likely to fragment.
 
@@
 In this work, we described a binary survey of 341 bright A- and B-type stars.
-We used the direct spectroscopic detection method \citep{Gullikson2016} to find the spectral lines of 64 companions with temperatures ranging from $3600 - 16000\ K$.
+We used the direct spectral detection method \citep{Gullikson2016} to find the spectral lines of 64 companions with temperatures ranging from $3600 - 16000\ K$.
 We used the cross-correlation functions to estimate the temperature, surface gravity, and metallicity of most of our sample stars, and converted to mass and age by interpolating Padova stellar evolutionary tracks \citep{Bressan2012}.
@@
 
-We then use the formalism introduced in \citet{Foreman2014}, which self-consistently accounts for measurement errors, to infer the form of the mass ratio distribution (shown in Figure \ref{fig:mrd}).
+We then use the formalism introduced in \citet{Foreman2014}, which self-consistently accounts for measurement errors, to infer the form of the mass-ratio distribution (shown in Figure \ref{fig:mrd}).
 Unlike most previous work, we find that a power law is a poor descriptor of the data and find that a lognormal distribution performs much better.
@@
 
-We interpret the mass ratio distribution in terms of formation mechanism in Section \ref{subsec:theory}.
-It is likely that the mass ratio distribution we find is largely a result of preferential accretion onto the secondary star, which largely stops when the circumprimary or circumbinary disk dissipates.
+We interpret the mass-ratio distribution in terms of formation mechanism in Section \ref{subsec:theory}.
+It is likely that the mass-ratio distribution we find is largely a result of preferential accretion onto the secondary star, which largely stops when the circumprimary or circumbinary disk dissipates.
 

### 2016-03-08 paper/ms.tex
Updated sections 1-3

@@
 Next, we describe the direct spectral detection method and tabulate the companion detections in Section \ref{sec:companions}.
-We estimate the mass and age of the primary stars in Section \ref{sec:sp}, and discuss the survey completeness in Section \ref{sec:completeness}.
+We estimate the mass and age of the sample stars in Section \ref{sec:sp}, and discuss the survey completeness in Section \ref{sec:completeness}.
 Finally, we end with a derivation of the mass-ratio distribution from our sample in Section \ref{sec:mrd} and discuss its implications for binary formation in Section \ref{sec:discussion}.
@@
 The sample is given in Table \ref{tab:sample}.
-The spectral type, coordinates, V magnitude, and parallax are all adopted from the Simbad Database \citep{Simbad}.
+The spectral type, coordinates, V magnitude, and parallax are all adopted from the Simbad Database \citep{Simbad}, while the stellar effective tempreature, surface gravity, masses, and ages are discussed in Section \ref{sec:sp}.
 
@@
 
-IGRINS only has one setting with $R = 40000$.
+IGRINS has a single setting with $R = 40000$.
 It has complete wavelength coverage from $1475-2480$ nm, except in the telluric water band from $1810 - 1930$ nm.
@@
 
-All of the reduced and telluric-corrected spectra used in this study will be released with this work, and will be available at the following url: \url{https://zenodo.org/record/46482}.
-
 \subsection{Imaging Data}
-As part of the follow-up effort, we used the NIRI instrument behind the Altair adaptive optics system at the Gemini North Telescope.
+As part of the follow-up effort, we used the NIRI instrument behind the Altair adaptive optics system on the Gemini North Telescope.
 For each star listed in Table \ref{tab:imaging_obs}, we obtained 25 images in 5 dithering positions.
@@
 
-We have follow-up spectroscopy for 17/27 of the new companions to confirm their existence.
+We have follow-up spectroscopy for 15/23 of the new companions to confirm their existence.
 In most cases, there is a clear shift in the radial velocity of the companion, indicating that it is orbiting the target star and is not a foreground or background contaminant (See Figure \ref{fig:ccf}).
@@
 
-In addition we obtained Gemini/NIRI adaptive optics imaging data for 18 of the northern companions, and were able to resolve 7 of them.
+In addition to the spectroscopic follow-up, we obtained Gemini/NIRI adaptive optics imaging data for 18 of the northern companions, and were able to resolve 7 of them.
 We show the separation, position angle, and magnitude difference measurements in Table \ref{tab:imaging_obs}, and display the images in Figure \ref{fig:images}.
@@
 We calculate the companion mass and uncertainties from 1000 samples of the magnitude difference measurement and the primary star mass, temperature, age, and radius (see Section \ref{sec:sp}).
-For each sample, we use a grid of Kurucz stellar model spectra \citep{Castelli2003}and the pysynphot code\footnote{pysynphot is a python code package to perform synthetic photometry, and is available at this url: \url{https://pypi.python.org/pypi/pysynphot}} to determine the companion temperature needed to replicate the observed magnitude difference.
+For each sample, we use a grid of Kurucz stellar model spectra \citep{Castelli2003}and the pysynphot code\footnote{pysynphot is a python package to perform synthetic photometry, and is available at this url: \url{https://pypi.python.org/pypi/pysynphot}} to determine the companion temperature needed to replicate the observed magnitude difference.
 We estimate the companion radius by interpolating solar metallicity Dartmouth isochrones [CITE] from the companion temperature and system age sample.
@@
 The masses derived from the imaging data have very large uncertainties because the primary star property estimates that they depend on are very uncertain.
+The imaging masses agree with the spectroscopically-derived masses in Table \ref{tab:companions}, with the exception of HIP 115115 which has a much higher mass from the imaging data than the spectroscopic data.
+The spectroscopic masses for all stars are more reliable, since they are less model-dependent.
 

### 2016-03-08 paper/ms.tex
Updated sections 4-5

@@
 For each sample, we use a grid of Kurucz stellar model spectra \citep{Castelli2003}and the pysynphot code\footnote{pysynphot is a python package to perform synthetic photometry, and is available at this url: \url{https://pypi.python.org/pypi/pysynphot}} to determine the companion temperature needed to replicate the observed magnitude difference.
-We estimate the companion radius by interpolating solar metallicity Dartmouth isochrones [CITE] from the companion temperature and system age sample.
+We estimate the companion radius by interpolating solar metallicity Dartmouth isochrones \citep{Dotter2008} from the companion temperature and system age sample.
 We convert the best temperature to a companion mass using the same isochrone grid.
@@
 
-\section{Primary Star Parameters}
+\section{Sample Star Parameters}
 \label{sec:sp}
@@
 
-About half of our detections have robust mass and age estimates for the primary stars from Str\"omgren uvby$\beta$ photometry \citep{David2015}.
+About half of our sample stars have robust mass and age estimates from Str\"omgren uvby$\beta$ photometry \citep{David2015}.
 For those that do not, we estimate the mass and age of the system from our spectra.
-We first cross-correlate the data against a grid of model spectra spanning
+We first cross-correlate the data against a grid of solar metallicity Kurucz model spectra \citep{Castelli2003} spanning
 
@@
 \end{itemize}
-Since the Phoenix model library does not extend to temperatures $T > 12000\ K$, we used Kurucz model spectra \citep{Castelli2003} for this grid.
 
@@
 The near-infrared IGRINS spectra have very few strong metal lines; we use the subset from $1.51 - 1.73 \micron$ that is dominated by hydrogren Brackett lines for these spectra.
-We then estimate the temperature and surface gravity of the primary stars from the CCF with the largest peak.
+Similar to the companion search, we estimate the temperature and surface gravity of the stars from the CCF with the largest peak.
 We adopt the following errors on the temperature and surface gravity:
@@
 \end{align}
-The IGRINS parameters are less reliable because they rely almost solely on the hydrogren Brackett lines that span an entire \'echelle order, so we double the uncertainty on the IGRINS-derived temperature, surface gravity, and metallicity.
+The IGRINS parameters are less reliable because they rely almost solely on the hydrogren Brackett lines that span an entire \'echelle order, so we double the uncertainty on the IGRINS-derived temperature and surface gravity.
 Additionally, we throw out the IGRINS parameters if the star was also observed by one of the optical instruments in our survey.
@@
 We do not give parameters for the few stars that show strong discrepancies with the spectral-type estimate, most of which are early B-stars that have temperatures higher than the maximum grid temperature of $30000\ K$.
-The MCMC samples generated by the isochrones code are available at the following url: \url{https://zenodo.org/record/46482}.
 
@@
 We counted the companion as detected if the highest point in the resulting CCF was found at the correct radial velocity, and if the peak had a significance of $>5\sigma$, where $\sigma$ is the standard deviation of the CCF for points more than $100\ \mathrm{km\ s}^{-1}$ away from the peak.
-We then combined all of the radial velocity trials for each grid point to estimate a probability of detection at that grid point:
+We combined all of the radial velocity trials for each grid point to estimate a probability of detection at that grid point:
 
@@
 Likewise, we assume that if no companions are detected at temperature $T$ and rotation speed $v\sin{i} = 50\ \mathrm{km\ s}^{-1}$, then no companions will be detected at the same temperature and faster rotation speeds (upper left points in Figure \ref{fig:detrate_2d}).
+We tested the former assumption with injection and recovery experiments on a small subset of stars, and found that it is valid.
+
 Figure \ref{fig:detrate_2d} shows a clear diagonal dividing line between hot, slow rotators that are always detected and cool, fast rotators that never are.
-Additionally the figure shows that very fast rotators are never detected, regardless of their temperature, because the signal is completely removed when we high-pass filter the data (see Section \ref{sec:companions}).
+Additionally the figure shows that very fast rotators are never detected, regardless of their temperature, because the signal is completely removed when we unsharp-mask the data (see Section \ref{sec:companions}).
 
@@
 \end{equation} 
-where $Q(T, v\sin{i})$ is the surface plotted in Figure \ref{fig:detrate_2d} and $v_k$ are the samples from the distribution of $v\sin{i}$.
+where $Q(T, v)$ is the surface plotted in Figure \ref{fig:detrate_2d} and $v_k$ are the samples from the distribution of $v\sin{i}$.
 For $T < 6000$ K, we sample $v\sin{i}$ using the gyrochronology relation given in \citet{Barnes2010b}:
@@
 We estimate the convective timescale ($\tau$) by interpolating Table 1 of \citet{Barnes2010a}.
-We then randomly sample the system age $t$ from its probability distribution function (see Section \ref{sec:sp} and Table \ref{tab:sample}).
+We then randomly draw a system age $t$ from its probability distribution function (see Section \ref{sec:sp} and Table \ref{tab:sample}).
 Young stars have rotation periods in the range of 0.2 to 10 days \citep{Bouvier2014}, so we randomly choose an initial rotation period $P_0$ from a log-uniform distribution in this range for each age sample.
 Equation \ref{eqn:gyro} then gives a current rotation period for each sample, which we convert to an equatorial velocity with the stellar radius $R$.
-We estimate the stellar radius by interpolating Dartmouth pre main sequence isochrones [CITE] using the companion temperature and system age.
+We estimate $R$ by interpolating Dartmouth pre main sequence isochrones \citep{Dotter2008} using the companion temperature and system age.
 We finally convert to projected velocity $v\sin{i}$ by randomly sampling a uniform distribution for the inclination $\sin{i}$.
@@
 We detect 15 of the 25 stars in our sample with a hot ($T > 7000\ K$) companion.
-The completeness function for hot, roughly equal-mass companions suggest the probability of detection if $\sim 80\%$, which is incompatible with our low detection rate (p=0.01).
-The discrepancy may be due to an underestimate of the typical rotation rates for hot stars, used when marginalizing out the dependence on $v\sin{i}$.
+The completeness function for hot, roughly equal-mass companions suggest the probability of detection if $\sim 80\%$, which is incompatible with our low detection rate.
+The discrepancy may be due to an underestimate of the typical rotation rates for hot stars, which we use when marginalizing out the dependence on $v\sin{i}$.
 Additionally, rapidly rotating companions, especially when they have a similar temperature to the primary, are more difficult to detect if they have a small radial velocity offset from the primary star.
@@
 We estimate the mass for each detected companion star by sampling the temperatures given in Table \ref{tab:companions} as a gaussian, and converting each temperature sample into a mass sample.
-We do the conversion to mass both by interpolating Table 5 from \citet{Pecaut2013}, and by interpolating from temperature and system age (see Section \ref{sec:sp}) to mass with Dartmouth isochrones [CITE].
+We do the conversion to mass both by interpolating Table 5 from \citet{Pecaut2013}, and by interpolating from temperature and system age (see Section \ref{sec:sp}) to mass with Dartmouth isochrones \citep{Dotter2008}.
 Both methods give similar results in most cases, although the isochrone masses are significantly higher for very young systems, so we adopt the isochronal values in the analysis.
@@
 We used the cross-correlation functions to estimate the temperature, surface gravity, and metallicity of most of our sample stars, and converted to mass and age by interpolating Padova stellar evolutionary tracks \citep{Bressan2012}.
-Likewise, we convert the companion temperature measurements to mass by using solar metallicity Dartmough evolutionary tracks [CITE].
+Likewise, we convert the companion temperature measurements to mass by using solar metallicity Dartmough evolutionary tracks \citep{Dotter2008}.
 

### 2016-03-08 paper/ms.tex
Updated section 6

@@
 We test to determine if the completeness is reasonable at large mass ratios by comparing to known binary systems.
-We detect 15 of the 25 stars in our sample with a hot ($T > 7000\ K$) companion.
+We detect 15 of the 25 stars in our sample with a hot ($T > 7000\ K$) companion in either the Washington Double Star Catalog \citep{WDS} for the Ninth Catalog of Spectroscopic Binary Orbits \citep{SB9}.
 The completeness function for hot, roughly equal-mass companions suggest the probability of detection if $\sim 80\%$, which is incompatible with our low detection rate.
@@
 We do the conversion to mass both by interpolating Table 5 from \citet{Pecaut2013}, and by interpolating from temperature and system age (see Section \ref{sec:sp}) to mass with Dartmouth isochrones \citep{Dotter2008}.
-Both methods give similar results in most cases, although the isochrone masses are significantly higher for very young systems, so we adopt the isochronal values in the analysis.
+Both methods give similar results in most cases.
+Since the isochrone masses are more accurate at young ages, we use them throughout the analysis that follows.
 We sample the mass ratio of the system by dividing the companion mass samples by samples of the primary mass (Section \ref{sec:sp}).
@@
 We do not use systems with more than one companion, unless the wider companion is separated by $ > 10''$ from the primary star.
-We mark the 48 companions we use in the mass ratio analysis with the fourth column of Table \ref{tab:companions}.
-Many of the companions we use in the analysis only have one detection in our data; 12/22 of these are previously known companions and so don't need follow-up to confirm.
+We mark the 50 companions we use in the mass ratio analysis with the fourth column of Table \ref{tab:companions}.
+Many of the companions we use in the analysis only have one detection in our data; 26/36 of these are previously known companions and so don't need follow-up to confirm.
 The remaining 10 are new and unconfirmed detections; these all have very strong CCF signals and are likely to be confirmed with follow-up spectroscopy or imaging.
@@
 
-In the above equation, $\{\vec{x_k}\}$ denotes the full spectrum of star $k$, and $\vec{\theta}$ denotes the parameters for the model we are fitting.
+In the above equation, $\{\vec{x_k}\}$ denotes the data for star $k$, and $\vec{\theta}$ denotes the parameters for the model we are fitting.
 $K=341$ is the total sample size for our survey, $Q(q)$ is the completeness function shown in Figure \ref{fig:completeness}, and $P(q|\vec{\theta})$ is the likelihood function for the mass ratio given the model parameters.
@@
 However, our sample is magnitude-limited and therefore suffers from Malmquist bias.
-There is a higher probability of equal-mass binary systems to occur in our survey because they contribute twice the flux and are therefore more likely to fall under the magnitude limit.
+There is a higher probability for equal-mass binary systems to occur in our survey because they contribute twice the flux and are therefore more likely to fall under the magnitude limit.
 We can calculate the PDF for mass ratio, given that we observed the system, from Bayes' theorem:
@@
 We also estimate the mass-ratio distribution expected from random pairing of the Kroupa Initial Mass Function (IMF), and show the result in yellow.
-We estimated the distribution by drawing 100000 primary stars from the IMF with masses between $1.5 < M/M_{\odot} < 20$.
-We then drew companions from the same IMF, with the restriction that the companion has a lower mass than the primary.
+We estimate the distribution by drawing 100000 primary stars from the IMF with masses between $1.5 < M/M_{\odot} < 20$.
+We then draw companions from the same IMF, with the restriction that the companion has a lower mass than the primary.
 The result plotted in yellow in Figure \ref{fig:mrd} is a gaussian kernel density estimate of the resulting mass ratios, with a bandwidth of $0.05$.

### 2016-03-08 paper/ms.tex
Updated section 7

@@
 The corresponding odds ratios are  $Z_\mathrm{lognormal} / Z_\mathrm{IMF} = 6.5 \pm 0.1 \e{22}$ and $Z_\mathrm{lognormal} / Z_\mathrm{uniform} = 7.0 \pm 0.1 \e{6}$.
-Both of these again demonstrate a very strong preference of the lognormal distribution.
+Both of these again demonstrate a very strong preference for the lognormal distribution.
 
@@
 We only use companions from this work with mean $\overline{q} > 0.15$ because the VAST survey subsample makes the same cut.
-To account for measurement uncertainties in the mass ratios, we choose from the mass ratio samples ($q_k^{(n)}$, see Section \ref{sec:mrd}) many times and compute the Anderson-Darling test statistic each time.
+To account for measurement uncertainties in the mass ratios, we draw from both our mass ratio samples ($q_k^{(n)}$, see Section \ref{sec:mrd}) and the VAST mass ratio values many times and compute the Anderson-Darling test statistic each time.
 Since \citet{DeRosa2014} do not quote uncertainties, we assume uncertainties of $\sigma_q = 0.05$ for all of their measurements.
@@
 The close companions that we detect may form with similar masses to their counterparts at large separations ($a \gtrsim 1000\ AU$), but preferentially accrete matter from the dense primary star disk.
-Since preferential accretion is strongest at the most extreme mass ratios [CITE], the result would be a depletion of low mass ratio companions as they become intermediate to high mass ratio companions.
+The result would be a depletion of low mass ratio companions as they become intermediate to high mass ratio companions.
 The characteristic scale of $\sim 0.3$ that we see in Figure \ref{fig:mrd} would then be related to the disk timescale, since with enough time the preferential accretion would push all companions to $q = 1.0$.
@@
 It is also possible that some of the companions found in this work were formed from a gravitationally unstable disk \citep[e.g.][]{Kratter2006, Stamatellos2011}.
-Being a completely different formation mechanism than the way wide companions form, we would expect the mass function to differ.
+Being a completely different formation mechanism than the way wide companions form, we would expect the initial mass function to differ.
 Additionally, such companions would undergo the same preferential accretion discussed above.
-This explanation may even be preferable, since it could explain why we see a separation-dependent mass-ratio distribution around intermediate-mass stars but not low-mass stars: more massive stars tend to have more massive disks [CITE] that are more likely to fragment.
+This explanation may even be preferable, since it could explain why we see a separation-dependent mass-ratio distribution around intermediate-mass stars but not low-mass stars: more massive stars tend to have more massive disks \citep{Andrews2013} that are more likely to fragment \citep{Kratter2010}.
 
 Large scale simulations are likely needed to distinguish between the two scenarios and fully interpret the results of this survey.
-A significant amount of work has already been put towards this end in the form of radiation hydrodynamic simulations of full giant molecular clouds \citep{Bate2012, Krumholz2012}.
-However, the present simulations do not generate enough stars more massive than the sun to compare binary and multiple star statistics to observations.
+A significant amount of work has already been put towards this end in the form of radiation hydrodynamic simulations of giant molecular clouds \citep{Bate2012, Krumholz2012}.
+However, the present simulations do not generate enough stars more massive than the sun to quantitatively compare binary and multiple star statistics to observations.
 

### 2016-03-08 paper/ms.tex
Updated summary and acknowledgments.

@@
 We used the direct spectral detection method \citep{Gullikson2016} to find the spectral lines of 64 companions with temperatures ranging from $3600 - 16000\ K$.
-We used the cross-correlation functions to estimate the temperature, surface gravity, and metallicity of most of our sample stars, and converted to mass and age by interpolating Padova stellar evolutionary tracks \citep{Bressan2012}.
+We used the cross-correlation functions to estimate the temperature and surface gravity of most of our sample stars, and converted to mass and age by interpolating Padova stellar evolutionary tracks \citep{Bressan2012}.
 Likewise, we convert the companion temperature measurements to mass by using solar metallicity Dartmough evolutionary tracks \citep{Dotter2008}.
@@
 Unlike most previous work, we find that a power law is a poor descriptor of the data and find that a lognormal distribution performs much better.
-This result, which only includes close companions since it is a spectroscopic technique, is consistent with the 18 close companions found in the VAST survey \cite{DeRosa2014}.
+This result, which only includes close companions since it is a spectroscopic technique, is consistent with the 18 close companions found in the VAST survey \citep{DeRosa2014}.
 However, this result shows much more detail due to a larger number of companions.
@@
 In the effort of open and reproducible research, we have made several data products freely available to the community.
-The samples of primary and companion mass and system age are available at \url{https://zenodo.org/record/46340}.
-The files generated by MultiNest, which include samples from the posterior distributions described in Section \ref{sec:mrd}, are available at the same url.
+All of the reduced and telluric-corrected spectra used in this study are available at \url{https://zenodo.org/record/46340}.
+Samples of the primary and companion mass and system age posterior distributions are available at the same url, as are the posterior distributions for the parameters fit in Section \ref{sec:mrd}.
 We additionally provide a series of python libraries and jupyter notebooks with the computer code we used for the analysis on github: \url{https://github.com/kgullikson88/BinaryInference}.
@@
 This research has made use of the SIMBAD database, operated at CDS, Strasbourg, France, and of Astropy, a community-developed core Python package for Astronomy (Astropy Collaboration, 2013).
-It was supported by a start-up grant to Adam Kraus as well as a University of Texas Continuing Fellowship to Kevin Gullikson.
+It was supported by a start-up grant to Adam Kraus as well as a University of Texas Continuing Fellowship and a Dissertation Writing Fellowship to Kevin Gullikson.
 

### 2016-03-08 paper/ms.tex
Discussed solar type detection rate by citing my previous article.

@@
 
+\citet{Gullikson2016} used a very similar method to search for known companions to A- and B-type stars, and found that the detection rate is high for G- and K-dwarf companions but very low for hot companions.
+The search grid used in this work includes much hotter temperatures, and we have several detections of hot companions (see Table \ref{tab:companions}).
 We test to determine if the completeness is reasonable at large mass ratios by comparing to known binary systems.
-We detect 15 of the 25 stars in our sample with a hot ($T > 7000\ K$) companion in either the Washington Double Star Catalog \citep{WDS} for the Ninth Catalog of Spectroscopic Binary Orbits \citep{SB9}.
-The completeness function for hot, roughly equal-mass companions suggest the probability of detection if $\sim 80\%$, which is incompatible with our low detection rate.
+We detect 15 of the 25 stars in our sample with a hot ($T > 7000\ K$) companion in either the Washington Double Star Catalog \citep{WDS} or the Ninth Catalog of Spectroscopic Binary Orbits \citep{SB9}.
+The completeness function for hot, roughly equal-mass companions suggest the probability of detection if $\sim 80\%$, which is still incompatible with our low detection rate.
 The discrepancy may be due to an underestimate of the typical rotation rates for hot stars, which we use when marginalizing out the dependence on $v\sin{i}$.

### 2016-03-15 paper/ms.tex
Moved figure 1.
Fixed table 1 caption.
Updated per Sallys comments

@@
 
-\title{The Inner Mass-Ratio Distribution of Intermediate-Mass Stars}
+\title{The Close Companion Mass-Ratio Distribution of Intermediate-Mass Stars}
 
@@
 We should therefore expect the mass-ratio distribution of close companions to differ from that of wide companions.
-This prediction is difficult to test with intermediate-mass to massive primary stars using traditional methods because close companions are so much dimmer.
+This prediction is difficult to test with intermediate-mass primary stars using traditional methods because the contrast ratios that would be required to detect low-mass companions at narrow working angles are not yet achievable.
 We present the results of a survey searching for companions to A- and B-type stars using the direct spectral detection technique, which is sensitive to late-type companions within $\sim 1''$ of the primary and which has no inner working angle.
@@
 We give the spectroscopic observation log in Table \ref{tab:observations}.
-We calculate the signal-to-noise ratio (the ``snr'' column) for the optical instruments (CHIRON, TS23, and HRS) as the median of the extracted flux divided by it's uncertainty for each pixel from the \'echelle order nearest $675$ nm.
+We calculate the signal-to-noise ratio (the ``snr'' column) for the optical instruments (CHIRON, TS23, and HRS) as the median of the extracted flux divided by its uncertainty for each pixel from the \'echelle order nearest $675$ nm.
 For the IGRINS instrument, we calculate the signal-to-noise ratio from the order nearest $2200$ nm.
@@
 We also derive the projected separation in AU and the companion mass from the images.
-We calculate the separation from the measured angular separation and the Hipparchos parallax \citep{Hipparchos}.
+We calculate the separation from the measured angular separation and the Hipparchos parallax \citep{VanLeeuwen2007}.
 We calculate the companion mass and uncertainties from 1000 samples of the magnitude difference measurement and the primary star mass, temperature, age, and radius (see Section \ref{sec:sp}).
@@
 We quote the magnitude difference and separation of the brightest source in Table \ref{tab:imaging_obs}, but stress that \emph{none} of the visible sources is likely to be the companion we see in the spectroscopic data.
-The two epochs of spectroscopic data show a radial velocity shift of $\Delta v = 30.7\ \mathrm{km\ s}^{-1}$ over the course of roughly one year; this orbital motion is much too large to allow for any of the companions visible in the image (all with separations $ > 1''$ and projected separations $ > 300$ AU).
+The two epochs of spectroscopic data show a radial velocity shift of $\Delta v = 30.7\ \mathrm{km\ s}^{-1}$ over the course of roughly one year; this orbital motion is much too large to be consistent with any of the companions visible in the image (all with separations $ > 1''$ and projected separations $ > 300$ AU).
 
@@
 Finally, we interpolated between the grid points using a linear radial basis function interpolator (Figure \ref{fig:detrate_2d}).
-In order to extrapolate from our grids to estimate the detection rate at high temperature and low $v\sin{i}$ and at low temperature and high $v\sin{i}$, we made the following assumptions about the shape of the two-dimensional detection rate surface: First, we assumed that if all companions are detected at temperature $T=6500$ K and rotation speed $v\sin{i}$, then all companions with the same $v\sin{i}$ and larger temperature will also be detected (lower right points in Figure \ref{fig:detrate_2d}).
-Likewise, we assume that if no companions are detected at temperature $T$ and rotation speed $v\sin{i} = 50\ \mathrm{km\ s}^{-1}$, then no companions will be detected at the same temperature and faster rotation speeds (upper left points in Figure \ref{fig:detrate_2d}).
-We tested the former assumption with injection and recovery experiments on a small subset of stars, and found that it is valid.
+In order to extrapolate from our grids to estimate the detection rate at high temperature and low $v\sin{i}$ and at low temperature and high $v\sin{i}$, we made the following assumptions about the shape of the two-dimensional detection rate surface: First, we assume that if no companions are detected at temperature $T$ and rotation speed $v\sin{i} = 50\ \mathrm{km\ s}^{-1}$, then no companions will be detected at the same temperature and faster rotation speeds (upper left points in Figure \ref{fig:detrate_2d}).
+Likewise, we assumed that if all companions are detected at temperature $T=6500$ K and rotation speed $v\sin{i}$, then all companions with the same $v\sin{i}$ and larger temperature will also be detected (lower right points in Figure \ref{fig:detrate_2d}).
+The detection rate of hot companions is affected by two factors: the increased flux from the companion makes detection easier, while the decreasing number of spectral lines in the companion spectrum makes detection more difficult.
+If the latter factor is more important, then the assumption we made about the shape of the detection surface is incorrect.
+We therefore tested the assumption with a small subset of injection and recovery tests, and found that the second assumption we make is valid.
 
@@
 The gyrochronology relations are invalid for stars with $T \gtrsim 6250\ K$, the canonical limit at which the convective zone is too small to efficiently remove angular momentum to the stellar wind and spin down the star \citep{Pinsonneault2001}.
-\citet{Zorec2012} fit maxwellian distributions to the equatorial velocity of A- and B-type stars in several mass bins.
-For $T > 7000\ K$, we linearly interpolate the fit parameters as a function of mass and sample the resulting maxwellian probability density function.
-
-Typical velocities from the gyrochronology relationships are $10-20 \mathrm{km\ s}^{-1}$, while the maxwellian velocity distributions have typical velocities $\sim 100 \mathrm{km\ s}^{-1}$.
+\citet{Zorec2012} fit Maxwellian distributions to the equatorial velocity of A- and B-type stars in several mass bins.
+For $T > 7000\ K$, we linearly interpolate the fit parameters as a function of mass and sample the resulting Maxwellian probability density function.
+
+Typical velocities from the gyrochronology relationships are $10-20 \mathrm{km\ s}^{-1}$, while the Maxwellian velocity distributions have typical velocities $\sim 100 \mathrm{km\ s}^{-1}$.
 We transition between the two regimes for temperatures in the range $6000\ K < T < 7000\ K$ by first estimating the equatorial velocities from the gyrochronology relationship (Equation \ref{eqn:gyro}) at $T=6000\ K$.
-We then fit the velocities to a maxwellian distribution, and add the result to the tabulated parameters from \citep{Zorec2012}.
+We then fit the velocities to a Maxwellian distribution, and add the result to the tabulated parameters from \citep{Zorec2012}.
 With the extended table, we treat stars in the transition range the same way we treat hot stars.

### 2016-03-15 Completeness.py
Added function for easy gyro calculations.

@@ -68,7 +68,7 @@ def teff2radius(T):
     return retval
 
 
-def lnlike(P, P_0, t, tau, k_C, k_I):
+def lnlike(P, P_0, t, tau, k_C, k_I, *args, **kwargs):
     """
     This is the likelihood function for getting the period out of Equation 19 in Barnes (2010)
     :param P: Period (what we will be solving for)
@@ -89,6 +89,53 @@ def lnlike(P, P_0, t, tau, k_C, k_I):
 
 def poolfcn(args):
     return minimize_scalar(args[0], bracket=args[1], bounds=args[2], method='brent', args=args[3:]).x
+
+
+
+def get_periods_deterministic(ages, P0_vals, T_vals, k_C=0.646, k_I=452, nproc=None, safe=True):
+    """
+    All-important function to get the period distribution out of stuff that I know - parallel version!
+    :param ages: Random samples for the age of the system (Myr)
+    :param P0_min, P0_max: The minimum and maximum values of P0, the initial period. (days)
+                           We will choose random values in equal log-spacing.
+    :param T_star: The temperature of the star, in Kelvin
+    :keyword N_age, N_P0: The number of samples to take in age and initial period
+    :keyword k_C, k_I: The parameters fit in Barnes 2010
+    :keyword safe: Remove the periods with values < 0?
+    """
+
+    # Set up multiprocessing and a fit function with only one argument set
+    pool = multiprocessing.Pool(processes=nproc)
+    def errfcn(P, args):
+        return lnlike(P, *args)
+    bracket = [4.0, 7.0]
+    bounds = [0.1, 100]
+
+    args = []
+    for T_star in T_vals:
+        # Convert temperature to convection turnover timescale
+        tau = teff2tau(T_star)
+        for age in ages:
+            a = [(lnlike, bracket, bounds, P0, age, tau, k_C, k_I, T_star) for P0 in P0_vals]
+            args.extend(a)
+    #    period_list.extend(pool.map(poolfcn, args))
+    period_list = pool.map(poolfcn, args)
+    p0_list = [ag[3] for ag in args]
+    age_list = [ag[4] for ag in args]
+    T_list = [ag[8] for ag in args]
+
+    pool.close()
+    pool.join()
+
+    P = np.array(period_list)
+    if P.ndim > 1:
+        P = P[:, 0]
+    P0 = np.array(p0_list)
+    age = np.array(age_list)
+    teff = np.array(T_list)
+    if safe:
[…]

### 2016-03-15 paper/ms.tex
Fixed last page getting cut off.
Fixed lower case sentence start in fig. 7
Edited abstract wording, and fixed vsini for HIP 38538

@@
 Binary stars and higher-order multiple systems are a ubiquitous outcome of star formation, especially as the system mass increases.
-The distribution of mass ratios is a unique probe into the conditions of the collapsing cloud core and circumstellar disk(s) of the binary fragments.
+The companion mass-ratio distribution is a unique probe into the conditions of the collapsing cloud core and circumstellar disk(s) of the binary fragments.
 Inside $a \sim 1000$ AU the disks from the two forming stars can interact, and additionally companions can form directly through disk fragmentation.
@@
 
+IGRINS has a single setting with $R = 40000$.
+It has complete wavelength coverage from $1475-2480$ nm, except in the telluric water band from $1810 - 1930$ nm.
+Each star is observed in an ABBA nodding mode, and reduced using the standard IGRINS pipeline \citep{IGRINS_plp_v2}.
+The standard pipeline uses atmospheric OH emission lines as well as a Th-Ar calibration frame to calibrate the wavelengths; we further refine the wavelength solution using telluric absorption lines in the science spectrum.
+
+After reducing the data, we fit and remove the telluric spectrum using the TelFit code \citep{Gullikson2014}.
+We fit each \'echelle order affected by telluric absorption independently from each other to get the best removal.
+The telluric correction is critical for IGRINS spectra, where every order is dominated by telluric absorption lines.
+For the optical spectra, it is less critical but allows us to use some of the redder orders than we otherwise would be able to.
+For unsaturated lines, the best-fit telluric model reproduces the data to within $\sim 1-5\%$ of the continuum level.
+
+We give the spectroscopic observation log in Table \ref{tab:observations}.
+We calculate the signal-to-noise ratio (the ``snr'' column) for the optical instruments (CHIRON, TS23, and HRS) as the median of the extracted flux divided by its uncertainty for each pixel from the \'echelle order nearest $675$ nm.
+For the IGRINS instrument, we calculate the signal-to-noise ratio from the order nearest $2200$ nm.
+
+\subsection{Imaging Data}
+As part of the follow-up effort, we used the NIRI instrument behind the Altair adaptive optics system on the Gemini North Telescope.
+For each star listed in Table \ref{tab:imaging_obs}, we obtained 25 images in 5 dithering positions.
+We used the K-continuum band centered on $2.2718\ \mu m$ and a variety of exposure times and dates (listed in Table \ref{tab:imaging_obs}).
+Because the targets are all extremely bright, we used the high read noise and high flux detector settings to allow for very short co-add exposure times.
+We reduced the data using the Gemini set of IRAF tasks, which include steps for nonlinearity correction, flat-fielding, sky subtraction, and co-addition of the dither frames.
+
+We measure the flux and position of both stars by fitting a 2D Moffat function \citep{Moffat1969} to both stars simultaneously, constraining the shape parameters for both functions to be the same.
+The ratio of the amplitudes gives the magnitude difference, and the pixel locations along with the detector pixel scale gives the separation and position angle between the stars.
+We note that the goal of these images was confirmation and we did not observe any reference targets to make a distortion map and correct the image rotation.
+The uncertainty in position angle and to a lesser degree separation quoted in Table \ref{tab:imaging_obs} is likely underestimated.
+
 \begin{figure*}
@@
 \end{figure*}
-
-IGRINS has a single setting with $R = 40000$.
-It has complete wavelength coverage from $1475-2480$ nm, except in the telluric water band from $1810 - 1930$ nm.
-Each star is observed in an ABBA nodding mode, and reduced using the standard IGRINS pipeline \citep{IGRINS_plp_v2}.
-The standard pipeline uses atmospheric OH emission lines as well as a Th-Ar calibration frame to calibrate the wavelengths; we further refine the wavelength solution using telluric absorption lines in the science spectrum.
-
-After reducing the data, we fit and remove the telluric spectrum using the TelFit code \citep{Gullikson2014}.
-We fit each \'echelle order affected by telluric absorption independently from each other to get the best removal.
-The telluric correction is critical for IGRINS spectra, where every order is dominated by telluric absorption lines.
-For the optical spectra, it is less critical but allows us to use some of the redder orders than we otherwise would be able to.
-For unsaturated lines, the best-fit telluric model reproduces the data to within $\sim 1-5\%$ of the continuum level.
-
-We give the spectroscopic observation log in Table \ref{tab:observations}.
-We calculate the signal-to-noise ratio (the ``snr'' column) for the optical instruments (CHIRON, TS23, and HRS) as the median of the extracted flux divided by its uncertainty for each pixel from the \'echelle order nearest $675$ nm.
-For the IGRINS instrument, we calculate the signal-to-noise ratio from the order nearest $2200$ nm.
-
-\subsection{Imaging Data}
-As part of the follow-up effort, we used the NIRI instrument behind the Altair adaptive optics system on the Gemini North Telescope.
-For each star listed in Table \ref{tab:imaging_obs}, we obtained 25 images in 5 dithering positions.
-We used the K-continuum band centered on $2.2718\ \mu m$ and a variety of exposure times and dates (listed in Table \ref{tab:imaging_obs}).
-Because the targets are all extremely bright, we used the high read noise and high flux detector settings to allow for very short co-add exposure times.
-We reduced the data using the Gemini set of IRAF tasks, which include steps for nonlinearity correction, flat-fielding, sky subtraction, and co-addition of the dither frames.
-
-We measure the flux and position of both stars by fitting a 2D Moffat function \citep{Moffat1969} to both stars simultaneously, constraining the shape parameters for both functions to be the same.
-The ratio of the amplitudes gives the magnitude difference, and the pixel locations along with the detector pixel scale gives the separation and position angle between the stars.
-We note that the goal of these images was confirmation and we did not observe any reference targets to make a distortion map and correct the image rotation.
-The uncertainty in position angle and to a lesser degree separation quoted in Table \ref{tab:imaging_obs} is likely underestimated.
 
@@
 
-\subsection{Sensitivity Analysis}
+\subsection{Injection and Recovery Tests}
 
@@
 \includegraphics[width=\columnwidth]{MRD_total.pdf}
-\caption{mass-ratio distribution for our sample.
+\caption{Mass-ratio distribution for our sample.
 The data was fit to a histogram, a lognormal distribution, and a power law.
@@
 IDs: 13A-0139, 13B-0112, 2014A-0260, 14A-0260, 15A-0245; PI: Kevin Gullikson), which is operated by the Association of Universities for Research in Astronomy (AURA) under a cooperative agreement with the National Science Foundation.
+
+\clearpage
+\newpage
 
@@
 The "Ref" column denotes the reference for the stellar effective temperature, surface gravity, mass, and age.
-The references are: [1]: \citep{David2015}; [2]: This study.
-We only estimate stellar parameters for the stars in which we detect a companion.}
+The references are: [1]: \citep{David2015}; [2]: This study.}
 \label{tab:sample}
@@
   HIP 37450 & AB$^{\dagger}$ &     1 & yes &  $16000 \pm 1000$ &     30 &     0.0 &  $4.3^{+0.36}_{-0.43}$ &  $4.7^{+0.71}_{-0.39}$ \\
-  HIP 38538 & AB      &     1 & no &   $6576 \pm 150$ &      30 &    -0.5  &  $1.3^{+0.05}_{-0.05}$ &  $1.3^{+0.09}_{-0.05}$ \\
+  HIP 38538 & AB      &     1 & no &   $6576 \pm 150$ &      75 &    0.0  &  $1.3^{+0.05}_{-0.05}$ &  $1.3^{+0.09}_{-0.05}$ \\
   HIP 38593 & AB$^{\dagger}$ &     2 & yes &  $5398 \pm 112$ &       5 &    -0.5  &  $1.3^{+0.08}_{-0.13}$ &  $0.9^{+0.03}_{-0.03}$ \\

### 2016-03-21 paper/ms.tex
Updated zenodo link

@@
 All of the reduced and telluric-corrected spectra used in this study are available at \url{https://zenodo.org/record/46340}.
-Samples of the primary and companion mass and system age posterior distributions are available at the same url, as are the posterior distributions for the parameters fit in Section \ref{sec:mrd}.
+Samples of the primary and companion mass and system age posterior distributions are available at \url{https://zenodo.org/record/48073}, as are the posterior distributions for the parameters fit in Section \ref{sec:mrd} and every cross-correlation function generated in our analysis.
 We additionally provide a series of python libraries and jupyter notebooks with the computer code we used for the analysis on github: \url{https://github.com/kgullikson88/BinaryInference}.

### 2016-04-13 paper/ms.tex
Added initial responses to major points on referee report.

@@
 Inside $a \sim 1000$ AU the disks from the two forming stars can interact, and additionally companions can form directly through disk fragmentation.
-We should therefore expect the mass-ratio distribution of close companions to differ from that of wide companions.
+We should therefore expect the mass-ratio distribution of close companions ($a \lesssim 100$ AU) to differ from that of wide companions.
 This prediction is difficult to test with intermediate-mass primary stars using traditional methods because the contrast ratios that would be required to detect low-mass companions at narrow working angles are not yet achievable.
@@
 
-The mass ratio, period, and eccentricity distributions are fairly well-known for solar type stars \citep{Duquennoy1991, Raghavan2010} and cooler stars \citep{Fischer1992, Delfosse2004}.
-Interestingly, the mass-ratio distribution appears to be invariant to separation for these stars \citep{Meyer2013}, contrary to the theoretical expectations.
-All of the distributions are much less certain for more massive stars.
+The mass ratio, period, and eccentricity distributions are well-known for solar type stars \citep{Duquennoy1991, Raghavan2010} and cooler stars \citep{Fischer1992, Delfosse2004}.
+Interestingly, \citet{Reggiani2011}, and later \citet{Meyer2013}, found that the mass-ratio distribution of field solar-type and M-dwarf stars is invariant to separation.
+However, the solar-type binary semimajor axis distribution peaks near $45$ AU, and only $\sim 10\%$ of binary systems have separations $a < 100$ AU \citep{Raghavan2010}; the 30 stars used in the analysis by \citet{Reggiani2011} is unsufficient to rule out a separation-variant mass-ratio distribution if it changes outside $a \gtrsim 100$ AU.
+Field M-dwarf binary systems have typical separations of $\sim 5$ AU \citep{Fischer1992}, and so the 27 stars using in the analysis is again insufficient to look for differences outside of $100$ AU.
+
+All of the orbital distributions are much less certain for more massive stars.
 The reason for this is two-fold: first, more massive stars tend to more rare and farther away, meaning many of the companions are angularly close to the very bright primaries and difficult to detect with imaging techniques.
@@
 The sample is given in Table \ref{tab:sample}.
-The spectral type, coordinates, V magnitude, and parallax are all adopted from the Simbad Database \citep{Simbad}, while the stellar effective tempreature, surface gravity, masses, and ages are discussed in Section \ref{sec:sp}.
+The spectral type, coordinates, V magnitude, and parallax are all adopted from the Simbad Database \citep{Simbad}, while the stellar effective temperature, surface gravity, masses, and ages are discussed in Section \ref{sec:sp}.
+
+The sample, being comprised of early-type stars, is heavily biased towards young stars.
+The estimated ages range from about 10 Myr to 1 Gyr, with most falling in the range of a few tens or hundreds of Myrs.
+The sample also mostly contains nearby stars, although the magnitude limit provides a greater extent than a volume-limited survey would have.
+The parallactic distances in our sample range from $\sim 15 - 2000$ pc.
+The maximum detectable separation, which we define as the point at which the companion is no longer guaranteed to fall on the spectrograph slit (see Section \ref{subsec:specdata} for a description of the spectrographs we use), is $\sim 20 - 4000$ AU.
+The median parallactic distance in our sample is $95$ pc, corresponding to a projected separation of $\sim 200$ AU.
+Most of the companions we are able to detect are close enough to have been impacted by the circumprimary disk, with $85\%$ of the sample sensitive to companions inside $100$ AU.
 
@@
 We can therefore measure the companion temperature and, to a lesser degree its metallicity and $v\sin{i}$, in a single spectrum.
-Imperfect stellar models cause a bias between the true companion temperature and the temperature of the Phoenix model which produces the largest CCF peak.
+We calculate the measured temperature ($T_m$) and variance ($\sigma_T^2$) as a weighted sum near the grid point with the highest CCF peak value, weighting by the peak CCF height at each temperature ($C_i$):
+
+\begin{eqnarray}
+\label{eqn:tmeas} 
+T_m &=& \sum_i C_i T_i / \sum_i C_i \\
+\sigma_T^2 &=& \frac{\sum_i C_i (T_i - T_m)^2}{ \sum_i C_i - \sum_i C_i^2 / \sum_i C_i}
+\end{eqnarray}
+Typical uncertainties are on the order of $200$ K. In the case of multiple observations for the same star, we use the variance-weighted mean of the individually measured temperatures.
+
+Imperfect stellar models cause a bias between the true companion temperature and the measured temperature ($T_m$).
 This bias is most pronounced at low temperatures, where the difficult-to-model molecular absorption becomes important.
-We correct for the bias by applying the calibrations developed in \citet{Gullikson2016}.
+We correct for the bias by applying the linear calibrations developed in \citet{Gullikson2016}.
 These calibrations are only valid for companions with $3000 < T_\mathrm{eff} < 7000 K$; for detections at hotter temperatures we assume that the temperature which produces the maximum CCF peak is an \emph{unbiased} estimator of the true companion temperature.
@@
 \begin{itemize}
-\item $7000\ K < T_\mathrm{eff} < 30000\ K$ in steps of $1000\ K$
+\item $7000\ K < T_\mathrm{eff} < 30000\ K$ in steps of $500\ K$ for $T < 10000\ K$, and in steps of $1000\ K$ for hotter templates.
 \item $3.0 < \log{g} < 4.5$ in steps of $0.5$ dex
@@
 Similar to the companion search, we estimate the temperature and surface gravity of the stars from the CCF with the largest peak.
-We adopt the following errors on the temperature and surface gravity:
+We adopt the following errors on the temperature and surface gravity, which are based on the grid step size and are somewhat more pessimistic than typical uncertainties seen in the literature for A- and B-type stars \citep[e.g.][]{Aydi2014, David2015}:
 
@@
 In the above equation, $\{\vec{x_k}\}$ denotes the data for star $k$, and $\vec{\theta}$ denotes the parameters for the model we are fitting.
-$K=341$ is the total sample size for our survey, $Q(q)$ is the completeness function shown in Figure \ref{fig:completeness}, and $P(q|\vec{\theta})$ is the likelihood function for the mass ratio given the model parameters.
+$K=50$ is the number of stars used in the analysis, $Q(q)$ is the completeness function shown in Figure \ref{fig:completeness}, and $P(q|\vec{\theta})$ is the likelihood function for the mass ratio given the model parameters.
 We fit the data to three distinct distributions: a histogram ($P_1$), a lognormal distribution ($P_2$), and a power law ($P_3$):
@@
 
-We show the resulting fits in Figure \ref{fig:mrd}.
+We summarize the parameters in Table \ref{tab:parameters}, and show the resulting fits in Figure \ref{fig:mrd}.
 The $1\sigma$ uncertainties in the bin heights from the histogram model are shown as error bars, and we overplot 300 samples of the lognormal distribution fit to show the spread allowed by the data.
@@
 We only use companions from this work with mean $\overline{q} > 0.15$ because the VAST survey subsample makes the same cut.
+The VAST survey also only included stars with projected separations $a < 125$ AU in their close companion subsample.
+Since we cannot estimate the separation from our data, we do not make such a cut.
+We could make a cut using the \emph{maximum} possible separation, set by the distance and spectrograph slit width, but doing so vastly reduces the number of detections and does not affect the result.
+
 To account for measurement uncertainties in the mass ratios, we draw from both our mass ratio samples ($q_k^{(n)}$, see Section \ref{sec:mrd}) and the VAST mass ratio values many times and compute the Anderson-Darling test statistic each time.
@@
 
+\LongTables
+\begin{deluxetable}{|r|rlll}
+\tabletypesize{\normalsize}
+\tablewidth{0pt}
+\tablecaption{Mass-Ratio Distribution Parameters.}
+\tablehead{
+     \colhead{} & \colhead{} & \colhead{ } & \multicolumn{2}{c}{$1 \sigma$ credible interval} \\
+     \colhead{Model} & \colhead{Parameter} & \colhead{Median Value} & \colhead{Lower} & \colhead{Upper}
+       }
+
+\startdata
+
+Histogram   & $\theta_1$                    & 0.50 & 0.18 & 1.00 \\
+                   & $\theta_2$                    & 1.53 & 1.14 & 1.89 \\
+                   & $\theta_3$                    & 2.17 & 1.80 & 2.65\\
+                   & $\theta_4$                    & 1.42 & 0.98 & 1.81 \\
+                   & $\theta_5$                    & 0.74 & 0.40 & 1.12 \\
+                   & $\theta_6$                    & 0.29 & 0.10 & 0.55 \\
+                   & $\theta_7$                    & 0.16 & 0.06 & 0.33 \\ \hline
+Lognormal  & $\mu$                           & -0.99 & -1.06 & -0.92 \\
+                   & $\sigma$                      & 0.46  &  0.40  &  0.54 \\
+                   & maximum$^{\dagger}$ & 0.30  & 0.27   & 0.33 \\ \hline
+Power Law & $\gamma$                    & 0.29  & 0.15   & 0.42
+
+ \enddata
+
+ \tablecomments{$\dagger$: This parameter is derived from the mean and standard deviation, not fit.}
+ \label{tab:parameters}
+\end{deluxetable}
+
+\clearpage
+\newpage
+
 \newpage

### 2016-04-14 paper/ms.tex
Fixed referee-discovered typos.

@@
 All of the orbital distributions are much less certain for more massive stars.
-The reason for this is two-fold: first, more massive stars tend to more rare and farther away, meaning many of the companions are angularly close to the very bright primaries and difficult to detect with imaging techniques.
+The reason for this is two-fold: first, more massive stars tend to be more distant than sunlike or low-mass stars, meaning many of the companions are angularly close to the primaries and difficult to detect with imaging techniques.
 Second, the primary stars tend to be rapid rotators, which limits radial velocity precision to $\sim 1 \mathrm{km\ s}^{-1}$.
@@
 
-We show the temperature, surface gravity, mass, and age estimates for most of our sample stars Table \ref{tab:sample}.
+We show the temperature, surface gravity, mass, and age estimates for most of our sample stars in Table \ref{tab:sample}.
 We do not give parameters for the few stars that show strong discrepancies with the spectral-type estimate, most of which are early B-stars that have temperatures higher than the maximum grid temperature of $30000\ K$.
@@
 We detect 15 of the 25 stars in our sample with a hot ($T > 7000\ K$) companion in either the Washington Double Star Catalog \citep{WDS} or the Ninth Catalog of Spectroscopic Binary Orbits \citep{SB9}.
-The completeness function for hot, roughly equal-mass companions suggest the probability of detection if $\sim 80\%$, which is still incompatible with our low detection rate.
+The completeness function for hot, roughly equal-mass companions suggests the probability of detection is $\sim 80\%$, which is still incompatible with our low detection rate.
 The discrepancy may be due to an underestimate of the typical rotation rates for hot stars, which we use when marginalizing out the dependence on $v\sin{i}$.
@@
 It is also possible that some of the companions found in this work were formed from a gravitationally unstable disk \citep[e.g.][]{Kratter2006, Stamatellos2011}.
-Being a completely different formation mechanism than the way wide companions form, we would expect the initial mass function to differ.
+Being a completely different formation mechanism than the way wide companions form, we would expect the initial companion mass function to differ.
 Additionally, such companions would undergo the same preferential accretion discussed above.

### 2016-04-19 paper/ms.tex
Version after resubmission to journal.

@@
 \begin{abstract}
-Binary stars and higher-order multiple systems are a ubiquitous outcome of star formation, especially as the system mass increases.
+Binary stars and higher-order multiple systems are an ubiquitous outcome of star formation, especially as the system mass increases.
 The companion mass-ratio distribution is a unique probe into the conditions of the collapsing cloud core and circumstellar disk(s) of the binary fragments.
@@
 We should therefore expect the mass-ratio distribution of close companions ($a \lesssim 100$ AU) to differ from that of wide companions.
-This prediction is difficult to test with intermediate-mass primary stars using traditional methods because the contrast ratios that would be required to detect low-mass companions at narrow working angles are not yet achievable.
-We present the results of a survey searching for companions to A- and B-type stars using the direct spectral detection technique, which is sensitive to late-type companions within $\sim 1''$ of the primary and which has no inner working angle.
+This prediction is difficult to test using traditional methods, especially with intermediate-mass primary stars, for a variety of observational reasons.
+We present the results of a survey searching for companions to A- and B-type stars using the direct spectral detection method, which is sensitive to late-type companions within $\sim 1''$ of the primary and which has no inner working angle.
 We estimate the temperatures and surface gravity of most of the 341 sample stars, and derive their masses and ages.
@@
 Most work has suggested that the disk material will preferentially accrete onto the lower mass companion \citep{Bate1997, BBB2002}; however, recent work has indicated that magnetic disk braking may result in preferential accretion onto the more massive component \citep{Zhao2013} instead.
-In either case, we would expect to find a mass-ratio distribution for companions inside a few $100$ AU that differs from that of companions on wider orbits.
+In either case, we would expect to find a mass-ratio distribution for companions inside a few $100$ AU that differs from that of companions on wider orbits where preferential accretion does not occur.
 
@@
 Interestingly, \citet{Reggiani2011}, and later \citet{Meyer2013}, found that the mass-ratio distribution of field solar-type and M-dwarf stars is invariant to separation.
-However, the solar-type binary semimajor axis distribution peaks near $45$ AU, and only $\sim 10\%$ of binary systems have separations $a < 100$ AU \citep{Raghavan2010}; the 30 stars used in the analysis by \citet{Reggiani2011} is unsufficient to rule out a separation-variant mass-ratio distribution if it changes outside $a \gtrsim 100$ AU.
-Field M-dwarf binary systems have typical separations of $\sim 5$ AU \citep{Fischer1992}, and so the 27 stars using in the analysis is again insufficient to look for differences outside of $100$ AU.
+The field M-dwarf semimajor axis distribution peaks near $\sim 5$ AU \citep{Duchene2013}, with very few companions at separation $\gtrsim 100$ AU; the 27 stars used in the analysis by \citet{Reggiani2011} is unsufficient to compare the mass-ratio distribution inside $\sim 100$ AU with that outside it.
+However, the solar-type period distribution peaks near $45$ AU \citep{Raghavan2010}, with roughly $40\%$ of binary systems on orbits wider than $100$ AU.
+The nondetection of a difference in mass-ratio distribution is significant, although with only 30 stars in the field sample it is difficult to completely rule out that such a difference exists.
 
@@
 The reason for this is two-fold: first, more massive stars tend to be more distant than sunlike or low-mass stars, meaning many of the companions are angularly close to the primaries and difficult to detect with imaging techniques.
-Second, the primary stars tend to be rapid rotators, which limits radial velocity precision to $\sim 1 \mathrm{km\ s}^{-1}$.
-Additionally, radial velocity monitoring can only measure a mass ratio if spectral lines from both components are visible; this typically suffers from the same flux ratio difficulty as imaging techniques.
+Second, the primary stars tend to be rapid rotators, which limits radial velocity precision to $\sim 1 \mathrm{km\ s}^{-1}$ and causes the spectral lines of double-lined systems to blend.
+Radial velocity monitoring can only measure a mass ratio if spectral lines from both components are visible and separable; this typically suffers from the same flux ratio difficulty as imaging techniques.
 
@@
 The estimated ages range from about 10 Myr to 1 Gyr, with most falling in the range of a few tens or hundreds of Myrs.
-The sample also mostly contains nearby stars, although the magnitude limit provides a greater extent than a volume-limited survey would have.
+The sample also mostly contains nearby stars, although the magnitude limit provides a greater extent than a volume-limited survey would.
 The parallactic distances in our sample range from $\sim 15 - 2000$ pc.
@@
 We used the K-continuum band centered on $2.2718\ \mu m$ and a variety of exposure times and dates (listed in Table \ref{tab:imaging_obs}).
-Because the targets are all extremely bright, we used the high read noise and high flux detector settings to allow for very short co-add exposure times.
+Because the targets are all extremely bright, we used the high read noise and high flux detector settings to allow for very short co-add exposure times and to prevent saturation.
 We reduced the data using the Gemini set of IRAF tasks, which include steps for nonlinearity correction, flat-fielding, sky subtraction, and co-addition of the dither frames.
@@
 Being a completely different formation mechanism than the way wide companions form, we would expect the initial companion mass function to differ.
-Additionally, such companions would undergo the same preferential accretion discussed above.
-This explanation may even be preferable, since it could explain why we see a separation-dependent mass-ratio distribution around intermediate-mass stars but not low-mass stars: more massive stars tend to have more massive disks \citep{Andrews2013} that are more likely to fragment \citep{Kratter2010}.
+Such companions would undergo the same preferential accretion discussed above.
 
@@
 \section*{Acknowledgements}
+We would like to thank the anonymous referee for their helpful comments, which have notably improved this work.
 This research has made use of the SIMBAD database, operated at CDS, Strasbourg, France, and of Astropy, a community-developed core Python package for Astronomy (Astropy Collaboration, 2013).
